### 2014-01-09 paper/paper.tex
fixed incorrect density in diff equations Tested everything on crystal.

\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
\usepackage{graphicx}% Include figure files
\usepackage{color}

\newcommand{\red}[1]{{\bf \color{red} #1}}
\newcommand{\blue}[1]{{\bf \color{blue} #1}}
\newcommand{\green}[1]{{\bf \color{green} #1}}

\newcommand{\fixme}[1]{\red{[#1]}}
\newcommand{\davidsays}[1]{{\color{red} [\green{David:} \emph{#1}]}}
\newcommand{\renesays}[1]{{\color{red} [\blue{Rene:} \emph{#1}]}}
\newcommand{\jeffsays}[1]{{\color{red} [\blue{Jeff:} \emph{#1}]}}

\newcommand\micron{\ensuremath{\mu\text{m}}}

\begin{document}
\title{Robustness of MinD oscillation in \emph{Escherichia coli} with
  diverse cell shapes}

\author{Jeff B. Schulte}
\affiliation{Department of Physics, Oregon State University}
\author{Rene W. Zeto}
\affiliation{Department of Physics, Oregon State University}
\author{David Roundy}
\affiliation{Department of Physics, Oregon State University}

\begin{abstract}
  The dynamics of the Min-protein system help Escherichia coli
  bacteria regulate the process of cell division by identifying the
  center of the cell.  We model the Min-protein system in bacteria
  that have been forced into unusual flattened shapes, as have
  recently been experimentally observed.  We find that although the
  presence of Min oscillations is robust in a wide variety of cellular
  configurations, the location of the peaks is strongly affected by
  the cellular shape.  In some cases no periodic oscillations are
  observed.  In particular, we find that cellular shapes observed
  experimentally to present irregular oscillations do so in the
  theoretical model, consistently \fixme{or inconsistently?} with
  experiment.  \fixme{In agreement with previous theoretical and
    experimental results, we observe ``rotating'' behavior in certain
    shapes having three corners.}
\end{abstract}

\maketitle

\section{Introduction}
It is vital that during the process of bacterial cell division, a cell
avoid minicelling, or splitting into daughter cells with lopsided
volumes.  A long FtsZ polymer chain develops on the cell wall, in the
center region of the cell, the region which dictates the plane of
division~\cite{adams2009bacterial, lutkenhaus2007assembly}. Previous
experimental studies have shown that the MinC protein, known to
inhibit the FtZ polymer\cite{shen2010examination}, exhibits pole to
pole oscillatory behavior in conjunction with the MinD and MinE
proteins, while the oscillating MinE tends to be more localized in the
center of the cell~\cite{hu1999topological, fu2001mine,
  shapiro2009and, yu1999ftsz, raskin1999rapid}. The MinC protein will
then have a higher time averaged concentration in the cell poles, as
opposed to the center region of the cell, aiding in prohibiting the
FtZ from developing in the wrong region.

The cell division process must be able to prevent minicelling, even
under irregular conditions. Studies have shown that it is capable of
performing this task for fairly perturbed cell
shapes\cite{touhami2006temperature}. Mannik et al. have done some
early experimental work showing regular oscillations of cell division
systems in bacteria that were physically forced into unusual
shapes. Varma et al. studied one particular example of a perturbed
shape, a three-pronged tube, and found both experimental and
simulation results\cite{varma2008min} supporting the idea that certain
systems inside the cell begin to undergo oscillations inside the
cell. These oscillations seem to seek out the extreme poles in the
cell shape\cite{corbin2002exploring} \cite{juarez2010changes}, and
effectively prevent minicelling in most cases. However, Mannik et
al. have also shown that there are limitations to this
mechanism\cite{mannik2010bacteria} \cite{mannik2009bacterial}. One
instance of this behavior is observable when the cell has been forced
into a flattened, irregular shape. Oscillations in this sort of cell
shape are far from the regular sorts of oscillations seen in the
computational work done by Huang et al\cite{huang2003dynamic}. We seek
to apply a computational model to explore the more extreme or
irregular cell shapes, in order to determine the limits of the steady
cell oscillations seen by Mannik et al.

%is this necessary? was in old paragraph.
%\fixme{this link doesn't work =
%  cite{mannik2012robustness}} \cite{mannik2010bacteria}
%\cite{mannik2009bacterial}

A significant amount of work has been done to develop protein reaction
and diffusion models that exhibit accurate macroscopic dynamics of the
MinD protein system. Early models involved free proteins that affect
each others' rates of diffusion and membrane attachment, but do not
combine into compound states~\cite{meinhardt2001pattern}.  In 2003
Huang improved upon this work with a simple model based on MinD-MinE
combination, ATPase hydrolysis, and MinD membrane attachment that when
simulated, exhibits accurate MinD oscillations in cylindrical
cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is more
likely to attach to the membrane when MinD is already clustered there
(following observed non-linear attachement of minD on the cell
membrane), and is stationary once attached.  A number of studies have
used an approach similar in that they do not rely on the ability of
MinD to move along the walls and
cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
  drew2005polymerization, fange2006noise, kerr2006division}, while
studies have been made as well of models which rely on MinD mobility
and attraction on the cell membrane~\cite{kruse2002dynamic,
  howard2005cellular}.  Variations of the Huang 2003 model that
stochasticly account for variations of molecular interaction
\cite{fange2006noise} and monte-carlo simulations that implement this
stochastic version of Huang's mean field reaction rates confirm the
major results obtained by Huang's model, and more successfully predict
experimentally observed oscillations in round cell
phenotypes~\cite{drew2005polymerization, fange2006noise,
  huang2004min}. Biochemical models of broader scope have also been
used to study the MinD system and show consistent
results.\cite{arjunan2010new}.  However, in general, the results of the
stochastic and monte-carlo simulations are similar to those given by
Huang's mean field results.

Previous studies have been made of the Min system's associtation with
the cell membrane
\cite{hsieh2010direct}\cite{mileykovskaya2003effects}.  Studies have
shown as well that MinD binds preferentially to regions enriched with
cadiolipin, an anionic phospholipid that collects on regions of high
negative curvature. This mechanism has been incorporated into other
models.\cite{drew2005polymerization,cytrynbaum2007multistranded,renner2012mind,renner2012mind}
However, this mechanism of combined clustering, phospholipids and MinD
has not been observed in real cells. \cite{halatek2012highly}

\begin{figure}
  \includegraphics[width=\columnwidth]{reactions}
  \caption{Reactions included in the model of Huang \emph{et
      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
\end{figure}

\section{Model and Methods}
We implement the model of Huang \emph{et al.}  for the behavior of the
MinD and MinE proteins inside the cell~\cite{huang2003dynamic}.
Figure~\ref{fig:reactions} shows the reaction process.  The
cytoplasmic MinD:ADP complex undergoes nucleotide exchange and is
changed into the MinD:ATP complex.  This will naturally diffuse
towards and attach to the cell membrane.  A cytoplasmic MinE will
attach to the wall bound MinD:ATP complex and after a time will
activate ATP hydrolosis.  This breaks up the complex, releasing MinE,
phosphate, and MinD:ADP back into the cell.  The MinD:ADP will undergo
nucleotide exchange and begin again the cyclic process.  This model is
defined by a set of five reaction-diffusion equations:

\begin{multline}
  \frac{\partial \rho_{D:ADP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ADP}-k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
  +\delta(d_w)k_{de}\sigma_{DE},\hspace{3.4cm}
\end{multline}
\begin{multline}
  \frac{\partial \rho_{D:ATP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ATP}+k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
  -\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
\end{multline}
\begin{multline}
  \frac{\partial \rho_E}{\partial t} = \mathcal{D}_E\nabla^2\rho_E+\delta(d_w)k_{de}\sigma_{DE}
  -\delta(d_w)k_E \sigma_D \rho_E
\end{multline}
\begin{multline}
  \frac{\partial \sigma_d}{\partial t} = -k_E\sigma_D\rho_E
  +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
  \label{eq:d-on-wall}
\end{multline}
\begin{multline}
  \frac{\partial \sigma_{DE}}{\partial t} = -k_{de}\sigma_{DE}+k_E\sigma_D\rho_E\hspace{3cm}
  \label{eq:FifthPDE}
\end{multline}

where $\rho$ is cytoplasmic protein density ($\mu m^{-3}$), $\sigma$
is membrane bound density ($\mu m^{-2}$), $\mathcal{D}_D$ and
$\mathcal{D}_{E}$ th diffusions constants for MinD and MinE,
respectively, $k_D^{\textrm{ADP $\rightarrow$ ATP}}$ the rate of
conversion from MinD:ADP to the MinD:ATP complex, $k_D$ the rate of
MinD:ATP attachement to the membrane when no protein is already
attached there, $k_{dD}$ the increase of this rate when MinD:ATP is
present on the membrane, $k_{de}$ the rate of hydrolisis of the
MinD:MinE:ATP complex, $k_E$ the rate of cytoplasmic MinE binding to
membrane bound MinD:ATP complex, and $d_w$ is the distance from the
point in space to the closest wall (which will always be
perpendicular to this distance).  $\delta(d_w)$ has units of
$\mu m^{-1}$ and will be zero everywhere except at the wall.
Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} will only be
relevent at the membrane because the membrane bound density values
will have no meaning in the cytoplasm where there is no membrane.

Our diffusion and reaction rates are shown below.  We are interested
primarily in the effect of cellular shape on the protein
oscillations, so we follow Huang's work\cite{huang2003dynamic} and do
not deviate from the wild type values used in that work.  Huang's
simulations use total MinD and MinE concentrations of $1,000/\mu m$
and $350/\mu m$, respectively, in a cylindrical cell of radius $0.5\mu
m$, and in our (non-cylindrical) cells we use the same number of
proteins per unit volume.  These concentration values are 1273 $\mu
m^{-3}$ and 445 $\mu m^{-3}$, respectively.
\begin{gather*}
  \mathcal{D}_D = \mathcal{D}_{E} = 2.5\micron^2/\text{sec}\\
  k_D^{\textrm{ADP $\rightarrow$ ATP}} = 1/\textrm{sec,  }
  k_D = 0.025 \micron /\textrm{sec}\\
  k_{dD} = 0.0015 \micron^3/ \textrm{sec,  }
  k_{de} = 0.7/\textrm{sec}\\
  k_E = 0.093 \micron^3 /\textrm{sec}.
\end{gather*}
A 3D grid is then constructed in cartesian coordinates, with a grid
spacing of .05\micron. We define our cell shapes and solve the
reaction-diffusion partial differential equations numerically to
observe the time evolution of the MinD and MinE concentrations inside
the cell.

The reactions shown in Figure~\ref{fig:reactions} are cyclical so we
can begin our observations at any stage in the cycle (which is
presented for the natural, pill shapes cell in Fig.~\ref{image-p}
below).  We consider first MinD:ATP floating freely in the cytoplasm.
The protein will not react with any other floating protein, and it
will not spontenously shift back into the MinD:ADP stage of the cycle.
It will diffuse until it attaches to a cell membrane.  This will
happen most rapidly in cytoplasmic regions that are close to membrane
regions of high curvature, where diffusion in a random direction is
more likely to lead to an encounter with a wall.  This effect is made
more pronounced by the MinD:ATP tendency to attract and cluster on the
membrane, as reflected in Equation~\ref{eq:d-on-wall}, which shows
that when adjacent to the membrane, the rate of binding to the
membrane is porportional to the amount of MinD already bound to the
wall.  Initially, then, there is a strong tendency of MinD to cluster
on the polar regions of the cell, where the curvature is highest.

We next see the formation of MinE `rings' on the membranes of the
polar caps.  As the freely diffusing MinE enters the cap portion it
begins to encounter concentrated membrane bound MinD.  The MinE binds
to this MinD and remains for a time on the walls in compound form.
When it is released, it has the two options of diffusing naturally
outward or inward towards the cell.  If it diffuses inward, there is
less cross sectional wall for it to bump into and also less
concentrated MinD:ATP to react with.  If it diffuses outward, the
curvature of the cell wall cuases there to be a greater probability
per unit time that it will encounter the cell membrane (for the same
reason outlined for the MinD:ATP above) where there is more membrane
bound MinD:ATP. If it does diffuse in this directin, it will likely
react with MinD:ATP before getting very far into the encap.  This
process results in the observed qualitative 'encroaching MinE ring'
behavoir that releases MinD:ADP back into the cytoplasm.  This
MinD:ADP will diffuse for a time before spontanosly undergowing
nucleotide exchange and reaching the MinD:ATP state that
can bind to the membrane again.  There is a strong chance that it has
by this time diffused out of the polar region and is on its way to the
opposite polar region of the cell.  If it hasn't then it will reattach
to the MinD:ATP on the cell wall deeper into the endcap and will
eventually be converged upon by the MinE ring, only to be released
again in MinD:ADP form.

Overall this process results in extremely robust oscillatory
behavoir of polar selection and oscillation in a wide variety of cell
shapes.

\section{Cell shapes}

We mean to investigate the geometric limits of the Min system
oscillations, as observed by Mannik \emph{et
  al.}~\cite{mannik2012robustness}, so we model the Min system in a
variety of cell shapes.  We begin with naturally occuring pill-shaped
cells and then proceed to examine a number of flattened pancake-like
shapes, which reflect the experiment of Mannik \emph{et al.}, in which
bacteria were confined within a thin slit~\cite{mannik2012robustness}.
Our pill shapes differ from those of Huang \emph{et al.} in that they
are cylinders with hemisphere endcaps instead of pure cylindrical
shapes.  Our cylinderidrical radius is $0.5\micron$ and the lengths
of our cells (measured between the tips of the endcaps) are
$5\micron$, $4\micron$, $3\micron$, and $2.5\micron$.

With our flattened cell shapes we mean to study cells that are
parrallel to those lodged into crevices by Mannik so we give them
height of $0.25\micron$ \cite{mannik2012robustness}.  Viewed from the top
down the cells will have the shapes described below and viewed from
the side they have at their edges a semicircular protrusion (one may
imagine the edges of a pancake).

Our first group of (three) flattened cell shapes are triangular when
viewed from above.  One of them is equilateral, one has a 3-4-5 right
angle shape, and the last is iscoscolese.

Our second group of (two) flattened cells are designed to replicate
those published by Mannik, in order to compare the results of the
simulation model with the experimental results in that work.

Our third group of (three) flattened cells are our own creations,
designed to investigate different patterns of protein oscillation
behavoir.

Kubitschek has shown in multiple experiments that at the time of cell
division cells have a volume that is within a range of roughly
$1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
  kubitschek1968linear}.  We follow Huang's
simulations\cite{huang2003dynamic} and Mannik's experiments and model
cells that are slightly larger than this range.  Amoung our flattened
cells the two dimensional length scales are tuned so that total cell
volumes are very close to $3\micron^3$. \jeffsays{I'm not sure how
  true this is.  We should go through and check.  There've been a few
  implementations of printouts reporting volume in the cpp}
\section{Specific Results}

\subsection{Pill Shape}

\begin{figure*}
  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500.pdf}
  \caption{Images of the concentration of each species in a natural
    pill-shaped bacterium as a function of time, with darker regions
    indicating higher concentration.  The cells pictured are
    $4\micron$ in length, measured from end to end.  Frames from an animation showing
    a series of contour plots of the concentration of proteins in
    different stages over time.  The order of frames is such that
    individual MinD proteins begin at the bottom of the plot (in the
    MinD:ATP state in the cytoplasm), and progress upward until they
    reach the MinE:MinD:ATP membrane-bound complex.  At that point,
    they will spontaneously dissociate into cytoplasmic MinE (the top
    row) and the starting state of cytoplasmic MinD:ADP.  The
    densities plotted are integrated along the axis orthogonal to the
    page, and the color scale is chosen separately for each species
    with black as the maximum value over space and time.}
  \label{image-p}
\end{figure*}

We begin with the naturally occuring pill cell shape.  We peice this
shape together as two hemispherical endcaps attached on either end of
a cylinder.  This shape follows the early simulations of Huang
\emph{et al.} but differs in that we have added the end caps for a
more natural shape, expecting similar results.  We test cells of
radius $.5\micron$ and of lengths $2\micron$, $3\micron$, and
$5\micron$ measured from the tip of one end cap to the top of the
other. In each case, we observe quick establishement (within a few
periods) of extremely regular oscillatory behavoir that lasts
indefinitely.  The period increases with cell length, as shown in
Table~\ref{tab:pill-periods}, in agreement with the results of Huang
\emph{et al.}.

\begin{table}
  \begin{tabular}{|r|c|c|c|l|}
    \hline
    Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
    \hline
    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
    \hline
  \end{tabular}
  \caption{Period of oscillation according to length of cell for
    pill-shaped cells.}\label{tab:pill-periods}
\end{table}

This simple model is a good starting point for observing in detail the
dynamic interaction between the different stages of protein that lead
to their qualitatively distinct behavoir. Figure \ref{image-p} shows
the process in a series of frames taken from simulation animations.
Each frame is 2.5 seconds ahead of the last, and each image shows a
the concentration of a given state of protein summed over the
coordinate orthogonal to the page.  The color scale for each protein
state is set according to the maximum density observed.

At $t=0$ in Figs.~\ref{image-p}~and~\ref{box-p}, the cytoplasmic MinE
is concentrated in the lower portion of the cell, and is diffusing
upward.  The MinD protein is initially concentrated on the membrane in
the upper portion of the cell.  At the boundary between the
cytoplasmic MinE and the membrane-bound MinD, there is a ring of the
membrane-bound MinE:MinD complex, which is moving towards the upper
end of the cell, removing the MinD from the membrane as it goes.  The
MinD is removed from the membrane in its MinD:ADP form, which begins
to accumulate at the upper end of the cell, peaking peaking at around
10 seconds.

At 15 seconds, the membrane-bound MinD:ATP has been essentially
removed from the top end of the cell, and MinD:ATP has begun to bind
to the membrane in the the lower half of the cell.  At this stage,
there is a high concentration of cytoplasmic MinE at the top of the
cell, and by 16 seconds we begin to see the formation of a MinE ring
just below the center of the cell.  At 18 seconds, the cell has
reached its original state, with MinD:ATP bound to the membrane on the
lower third of the cell, a high concentration of cytoplasmic MinE in
the upper half of the cell, and a MinE ring pushing on the
membrane-bound MinD:ATP.

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-300-50-0-0-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of a natural pill shaped cell.  The cell is the same as is
    shown in Fig.~\ref{image-p}.  The time axis is also identical to
    that shown in Fig.~\ref{image-p}, and shows one period of the
    oscillation after the system has settled down.  The vertical axis
    shows stacked the total number of proteins that are of four
    different compound stages and in the right section of the cell
    (bottom four colors), in the middle of the cell (middle four
    colors) and in the left section of the cell (top four colors). The
    different forms of protein changes while the total number of MinD
    protein in the cell remains constant, shown by the fact that the
    very top line is horizontal.}
  \label{box-p}
\end{figure}

While Fig.~\ref{image-p} is helpful for visualizing
the process occuring in the Min system, it is does not show the
relative number of proteins in each state.  To visualize this
information, we plot in Fig.~\ref{box-p} the fraction of MinD found in
each stage of the cycle in each of three sections of the cell---top,
middle and bottom---as a function of time over one period.  The time
axis is the same as in Fig.~\ref{image-p}.  Looking at the evolution
of the latter, we see an initial high concentration of cytoplasmic
MinD:ATP, as the this protein diffuses into the polar region, followed
by a dip in this and large spike in membrane bound MinD:ATP, as the
protein clusters onto the polar cell wall, followed by a spike in the
memebrane bound MinE:MinD:ATP stage of protein, together with a slight
rise in cytoplasmic MinD:ADP as the MinD dettaches from the wall.

results for pill shaped cell of length
$5\mu$ and radius $.5\mu$.  The plot shows both the transerence
between different stages of protein compound and movement within the
cell.  Starting at the beginning of a period, we can see that first
there is a spike on the left of MinD-ATP attached to the wall that is
accompanied by a growing number of cytoplasmic MinD-ATP and MinD-ADP
that are entering the left section, followed by a high peak in
MinD-MinE-ATP.  This peak gives way through the middle to peaks on the
right side of the cell, the first being a small bump in cytoplasmic
MinD-ATP that dissapears into a much larger spike in wall attached
MinD-ATP, which is followed by a peak in wall attached MinD-MinE-ATP.
The pattern during each period clearly shows the cycle of proteins
rections, as well as the very regular nature of the pole to pole
protein oscillations.

We can see a
clear difference in period between the $5\mu$, $4\mu$, and $2\mu$
length cells.  The oscillation periods for our $4\mu$ show excellent
agreement with the simulations of Huang et all
\cite{huang2003dynamic}.  This is to be expected since we begin our
simulations with their reported wild type concentrations of MinD and
MinE proteins. The periods for the different pill lengths are shown in
the table below.  We can see a direct correltation between size and
period, as the proteins must diffuse further in a longer cell before
they accumulate on the opposite wall.

\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-300-50-0-0-1500}
  \caption{Average protein density per unit area of wall for the wall
    attached stages of the protein cycle.  Shown in the right, middle,
    and left parts of a 5$\micron$ by 1$\micron$ pill shaped cell (above)
    and a 3$\micron$ by 1$\micron$ pill shaped cell (below).}
  \label{ave-per-area-plot-pill}
\end{figure}

Figure \ref{ave-per-area-plot-pill} shows the ave protein per unit
area that is wall attached in the middle, right, and left sections of
the pill shaped cell.  This is an important test of the central idea
behind the utility of the Min protein system.  The system is meant to
place Min proteins on the walls in heavier concentrations in the caps
of the cell and lower concentrations in the middle section, so that
the FtZ polymer may build up along the center walls.  We can see from
the plot of the 3$\micron$ by 1$\micron$ cell that the MinD proteins reach
concentration peaks in the caps that are higher than peaks in the
center.  \fixme{is the next part true?} Integrals of these plotted values show that the time averaged
concentrations are likewise higher in the caps than in the center.

\subsection{Triangular Shapes}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
  \caption{Total protein fluctuation in the right, middle, and left
    parts of an equilateral (top), iscoscolese (middle), and 3-4-5
    (bottom) triangle.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{box-triangle}
\end{figure}

The double pole oscillation pattern, in which one pole is located in a
single corner of the triangle and the other pole is spread out between
the opposite two, can be seen in Figure \ref{box-triangle}.  The
equilateral triangle shows a spike in both the Center and Left
sections at the same time, both showing the familiar sequence of peaks
amoungst the different states of the protein seen in the poles of the
pill shaped bacteria.  A spike in the other corner, showing the common
sequence, occurs during the minima of the former two, wth a higher
concentration at the peak.  A similar pattern is seen in the
iscosolese triangular shape, where interestingly the onset of the
maxima in the single maxima corner (the Left section) builds more
quickly than it fades.  This is presumably becuase as the cytoplasmic
minD:ATP diffuses down a more accute corner, it is sourrounded by
closer cell walls than it would be in a less acute corner, so that the
it is more apt at any diffusive step to make contact and cluster on
the walls.  That particular part of the process is therefore
accelerated, driving the build up of the maxima forward.

The right triangle shows a similar pattern except that here there is
an assymetry between the two corners that maximize at roughly the same
time.  One corner is further from the single maximizing corner and it
consisitently peaks later.  The MinD simply have further to travel
before they maximize there.

For these three sizess and shapes there is not sign that the
oscillation patterns once they are set will break down.

\begin{figure}
%%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
  \caption{Total protein fluctuation of an equilateral triangle with
    larger dimensions (each side is roughly $6\micron$.  The vertical
    axis shows stacked the total number of proteins that are of four
    different compound stages and in the different sections of the
    cell. The time limits have been set to show the broken down
    section of the simulation.}
  \label{box-triangle}

The larger equilateral shape shows the same pattern as the smaller
version does only until fifteen periods, at which point there is a
breakdown of the oscillation pattern.  During the last three stable
periods, the single maximizing corner, the lower left section in the
figure, has a lower peak each period as the membrane bound MinD:ATP in
the other corners lag more and more before being eaten away by the
MinE.  Finally these maxima lag so much that they break down the
regular pattern.  There then occurs about five periods of semi chaotic
behavoir, until it settles back into another stable oscillation that
is similar to the original one, except that a different corner has
been chosen to be the singlular maxima (the right section in the
figure), while the other two corners maximize at the same time.  This
interesting breakdown and recovery shows both the robustness of the
double pole oscilatory tendency and the importance of required
distance of travel for the different proteins.

\end{figure}

Fifteen

\subsection{Randst shape}
\fixme{Cheat sheet for the shapes, need to put these into a big figure
  from the sections output: 96=star shape, 97=sideways sideways
  flying saucer pancake, 98=manniks squished cell, 99=an A}

\subsubsection{Randst-mannik shape}
\begin{figure}
  \includegraphics[width=2.8cm]{../mannik-2.png}
  \includegraphics[width=2.8cm]{../mannik-1.png}
  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1300-2000-9400-1500.pdf}
  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1101-1101-9500-1500.pdf}
  \caption{Arrow plots for our simulation and mannik's experimental}
  \label{arrow-compare-mannik}
\end{figure}

Figure \ref{arrow-compare-mannik} shows a comparison of time maxima
plots with similar plots published by mannik et al.  The sequence of
arrows show a series of global maxima in space and local maxima in
time at their heads, numbered by the sequence in which they occur.
They function as a trace of the path that the traveling maxima take.
We have created for each of the two shapes published by Mannik a
closely resembling shape (shown directly below Mannik's) and a
variation on this shape (shown below that) in order to test the effect
of variations on basic shapes.  The plots of the left shape show that
much of the preffered locations for the proteins to maximize are
similar between this experimental and simulated shape.  The maxima in
the top center of the cell does not seem to appear in the experimental
version.  Also in both of the simulations on the left there don't seem
to be maxima at membrane regions with negative radii of curvature
while the experimental shows a maxima in the bottom center region
right at one of these regions.  The shape on the right compares less
successfully.  Here the simulation shows a limited number of maxima
locations that appear to be quite regular, where mannik's experimental
results show a much more chaotic system.  In particular, the maxima
location on the right wall seems to be very robust.  It acts as one of
the poles do in the pill shapes.  \fixme{I'm now running a sim with a
  slightly different shape to see result} The simulated version has
found a robust two pole pattern, similar to that seen in other shapes.

\subsubsection{Randst-99 our lambda shape}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}arrow-plot-NflD-randst-25-600-800-9800-1500.pdf

  \caption{Total protein fluctuation in the A shaped shape.  The vertical axis shows stacked the total number
    of proteins that are of four different compound stages and in the
    different sections of the cell.}
  \label{total-oscillation-randst-96-plot}
\end{figure}

Our animations for this cell shape show a very interesting pattern.
The maxima oscillates from the right corner to the top corner, then
\emph{back to the right corner} then to the top corner again, then to
the left corner, then back to the top, then to the left, then to the
top again, then back to the right side.

\fixme{running larger and smaller.  Guessing the larger will do pole
  and pole, so talk about in terms of you have huge, pole and pole,
  then once get small enough double oscillations develop.  Why do they
  do that?  And hen you can do image plot for the one with consistent
  double oscillations.  Can right now explain reason for double
  oscillations.  Look at todo.txt.  The slightly varied guassian shape,
  so a little assymetric, doesn't change double oscillation pattern.}

Contour plot frames from the animations show the second maxima in the
lower left corner (immediately following the one in the upper middle
corner) will reside for a bit longer than the left corner maxima
preceding it.  These longer residing maxima will then be followed by a
switch, to the right corner, with a short, less intensive maxima
traveling through the center.  The MinE shows the same pattern. The
MinE that was just concentrated on the left corner during the first
maxima, after releasing the MinD from the membrane there, diffuses up
and attaches to the MinD on the upper corner membrane and begins to
release it.  During this process the MinE starts at the edges and
moves in towards the center of the maxima.  The center of the cup is a
little further away so it attaches to these outer ridges first and
then moves in.  After it eats at the corners and starts moving in the
MinD eventually travels back to set up a maxima in the left corner.
Watching the cytoplasmic MinE, something very interesting: It as well
maximizes twice in the left corner, but during the MinD's first maxima
in the left corner, the MinD has a maxima in the upper corner, and
during the MinD's second left maxima, the MinE travels to the right
corner and has a maxima there.  At the same time (during the second
MinD left corner maxima), there is a large amount of cytoplasmic
MinD:ATP on the right side.  The MinE does this becuase during the
first MinD left corner maxima, the MinE has just come off a maxima in
the right corner.  So it diffuses up to the upper corner and sets up
there.  During the second MinD left corner maxima, the MinE has just
come off the upper corner maxima.  It will diffuse into the right
corner and left corner.  In the left corner it interacts with the MinD
bound to the membrane there.  In the right corner it sits and
eventually diffuses away, but at a somewhat slow pace.  \fixme{An idea
  is that once the MinD travels back from the left corner after its
  second maxima there, it is not able tot set up a maxima in the upper
  corner as easily, since there is left over MinE there, which has
  just traveled from the right corner.  The problem with this is that
  the MinE doesn't seem to be maximized in the upper corner when the
  MinD is traveling back up from the left.}  The other idea is simply
that because the minE is traveling all the way from the right corner,
the longer time it takes to get there simply means that it all
concentrates on the left, leaving the upp and right side completely
open for the build up of MinD.  \fixme{Still dont quite get it but
  take a look at the other simulations and come back.} Actually, you
can see this effect very slightly watching the 98 shape, between the
center cap and the right corner.

Simulations of this shape that has the same height and dimensions .6
times the size (cells roughly $1.6\mu m$ from top to bottom) do not
exhibit the same pattern.  In these the MinD maxima oscillate quickly
back and forth between the two lower corner poles.

Simulations in which the two planar dimensions are 2 and then 3 times
the size (cells roughly $6\micron$ and $9\micron$, respectively, from top
to bottom) show no stable regular periodic pattern \fixme{although
  they haven't really run long enough to exhibit much.  They certainly
  won't show the double oscillation pattern, however.}  The animations
of $6\micron$ cells show that the MinD acts as a sort of traveling
cluster that is constantly being eaten away be MinE behind it.  When
this cluster enters a region of high curvature that ends in a dead end
corner it performs the polar maxima behavoir seen in the other
simulations, regrouping out away from the corner where it travels in
the opposite direction while being ``chased'' away by the MinE that
has itself maximized in the corner.  If it has just maximized in the
top corner, it regroups traveling downward and then naturally splits
into two groups that travel out and form maxima in the two opposite
bottom corners.  After maximizing in these two corners the two groups
recombine again in the center and travel in some direction together as
one cluster.  Simulations of the $9\micron$ cells show a similar roaming
cluster.  Although here, the maxima occur on non-polar walls often,
and will often split into two roaming clusters that interact less
quickly and are less correlated than those seen in the $6\micron$ cell.

It seems that there is an approximate critical cell size for which the
MinD will act in these ``wandering cluster'' formations.  The cell is
large enough so that there is a loss of MinD correlation between the
opposite sides (the protein in the right corner at any time is too far
away from the left to immediately affect the protein there).

\subsubsection{Randst-97-}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-600-9700-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  \caption{Total protein fluctuation in the sideways flying saucer
    pancake cell shape.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{box-97}
\end{figure}

Early on in its simulation the sideways flying saucer pancake shape
shows a clear breakdown of an unstable equilibrium oscillation.  We
have set the intial conditions so that MinD density is highly
concentrated to the left of a dividing line that runs parrallel to the
left vertical side.  For the first number of oscillations the maxima
trade off right to left, from a high peak in the rightward middle
compartment to vertically opposed peaks in the poles of the long axis
of the cell.  This is seen in the first part of Figure~\ref{box-97},
where the lower and upper sections peak in unison, and the middle
right section peaks $\pi$ radians removed from these.  After a few
oscillations the back and forth oscillations tip toward the vertical
direction and the system loses its initial oscillation pattern.  It
falls quickly instead into a back and forth pattern between the two
opposing endcaps.  The oscillation at this point is reminiscent of the
pills shape oscillation, once again showing the robust nature of the
back and forth, two pole pattern.

During each period, directly after one of the polar maxima has
subsided, there is a small spike with the regular maxima pattern (a
spike in membrane bound MinD:ATP immediately followed by a spike in
membrane bound MinD:MinE:ATP) seen in the small middle right
compartment section.  The animations show that the MinD, oscillating
back and forth between the upper and lower poles, seems to catch and
lag in the indentation for a bit before moving on.  Once again the
positive radius of curvature acts as an attractive place for MinD to
cluster on the walls, and it is not released to move on through the
cytoplasm again until MinE has formed its ring and completely reacted
it away.

\subsubsection{Randst-96-Star}
\begin{figure}
  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-700-700-9600-1500}
  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
  \caption{Total protein fluctuation in the star cell shape.  The vertical axis shows stacked the total
    number of proteins that are of four different compound stages and
    in the different sections of the cell.}
  \label{box-96}
\end{figure}

This clover shape finds a regular oscillatory behavoir after about
seven periods that consists of two maxima that peak regularly in the
corners accross from each other at the same times (Figure
\ref{box-96}) and then again opposing maxima that peak at the same
time in the other two corners.\fixme{should try some different
  starting conditions with this to see if there's another patter.}

Looking at at few periods in detail.  We find that there is a small
increase in cytoplasmic MinE always directly before the the beggining
of climb in the membrane bound MinE peak.  Also, there is at any one
time a very large amount more of minE that is membrane bound then
cytoplasmic in any ones section.  A difference of a factor of roughly
20 when membrane MinE is at its peak, and roughly 12 when membrane
MinE is at it's minimum.  There seem to be two modes of oscillation,
each exhibiting a density peak maxima that moves back and forth
diagonaly from one corner to the opposite, as if there were two
overlapping, criss-crossed cells oscillating.  In the box plot this is
seen as roughly coinciding membrane minD peaks in the lower left and
right corners, followed one pi later in peaks in the upper right and
upper left corners.  Interesting that this did not exhibit
counterclockwise motion that Huangs 2008 paper might suggest.  Should
run sims that start in the wacky way that just started running with
triangles.
\newline

We haven't simulated long enough yet, so no real pattern has shown
itself.  There's certainly oscillations, and it's almost as if there's
competing modes - top to bottom, left to right, corner to corner, etc.
Interesting.

\fixme{maybe?}The animations seem to relax into a pattern in which the oscillations
go from the smallest corner, out to the other three, and then back to
the smallest corner?  \fixme{There isn't enough data to see properly
  though, need to run for longer.}

\section{Interpretation of Data}
\section{Conclusion}
\bibliography{paper}

\end{document}

\section*{Appendix}

\section{Below are NOTES for the Writing}

Figure \ref{total-oscillation-triangle-plot} shows the equivalent
motion and transference between compound states for the triangular
states as Figure \ref{total-oscillation-plot} does for the pill shaped
cells.  The equilateral triangular shows that in all three sections
there is a spike in wall attached MinD-ATP directly followed by a
spike in wall attached MinD-MinE-ATP.  The pill had shown a similar
pattern except that the mid section exhibited no such pronounced
spike.  Interestingly, the right and mid sections show spikes at
similar times when compared to the left section spikes, which seem to
oscillate in a manner shifted pi off from the other two.  This
behavoir shows itself in the animations, which show a relaxation into
a stable oscillation from a maxima in one corner to a double maxima in
the other two corners, and back again.  The left section heights are
roughly twice that of the right section heights.  The simulations are
started with higher concentrations of proteins in primarily the right
section, with some overlap into the middle section, so that perhpas
this oscillation pattern seems reasonable.  However, it's interesting
to note that the oscillations, started with assymmetric density, do
not naturally rotate around the corners of the triangle in a circular
pattern.

It seems as well that there is a desired oscillation maxima for the
particular shape and size of the cell, as can be seen by the
relaxation, over the first four periods, to a regular maximal height
of the right and left sections' total protein at the height of each spike.

\fixme{Note to make sure I'm interpreting the iscosolese triangle data
  correctly: the triangle sides are 5,5,3, and the higher density
  starts in the corner that is opposite the short side.  This corner
  is covered by the right section.  I've verified this by looking at
  the protein\_microscopy and drawing a little picture, which is on my
  desk...if you dare look for something on my desk!!!}  The iscosolese
triangle starts its simulation with a higher concentration of protein
in the section that is opposite the shorter side.  It quickly relaxes
into a stable oscillation pattern.  This pattern shows that right
corner section regularly has higher spikes in total protein than the
other sections, and that its spikes appear one pi removed from the
spikes for the other two sections.  This a similar behavoir to that
which is seen in the equilateral triangle, differening in that it
converges more quickly towards this behavoir and that it shows a
greater exageration in the height of protein buildup in the right most
section.

\fixme{Note on interpretation of 3-4-5 triangle: the higher density
  starts to the right of a vertical line that is parrallel to the
  second longest side in the triangle (the longer of the two
  non-hypotonuse sides).  This means the higher concentration covers
  the right angle and also the smaller angle in the triangle} The
3-4-5 triangle exhibits behavoir that I need more data to properly
observe.  I does not converge as quickly as that for the iscosolese or
equilateral triangles.

\end{document}

### 2014-01-31 paper/paper.tex
made cahnges to first parts of paper.  Havent yet done methods-pill section because want to know narrative first Tested everything on node08.

@@
 \section{Introduction}
-It is vital that during the process of bacterial cell division, a cell
+It is vital that during the process of bacterial cell division a cell
 avoid minicelling, or splitting into daughter cells with lopsided
-volumes.  A long FtsZ polymer chain develops on the cell wall, in the
-center region of the cell, the region which dictates the plane of
+volumes.  Instrumental to this process in \emph{Escherichia coli} is a
+long FtsZ polymer chain that develops on the cell wall in the center
+region of the cell, helping dictate the plane of
 division~\cite{adams2009bacterial, lutkenhaus2007assembly}. Previous
@@
 inhibit the FtZ polymer\cite{shen2010examination}, exhibits pole to
-pole oscillatory behavior in conjunction with the MinD and MinE
-proteins, while the oscillating MinE tends to be more localized in the
-center of the cell~\cite{hu1999topological, fu2001mine,
-  shapiro2009and, yu1999ftsz, raskin1999rapid}. The MinC protein will
-then have a higher time averaged concentration in the cell poles, as
-opposed to the center region of the cell, aiding in prohibiting the
-FtZ from developing in the wrong region.
+pole oscillatory behavior in conjunction with the MinD protein and a
+MinE that tends to be more localized in the center of the
+cell~\cite{hu1999topological, fu2001mine, shapiro2009and, yu1999ftsz,
+  raskin1999rapid}. The MinC protein will then have a higher time
+averaged concentration in the cell poles, as opposed to the center
+region of the cell, aiding in prohibiting the FtZ from developing in
+the wrong region.
 
-The cell division process must be able to prevent minicelling, even
-under irregular conditions. Studies have shown that it is capable of
-performing this task for fairly perturbed cell
-shapes\cite{touhami2006temperature}. Mannik et al. have done some
-early experimental work showing regular oscillations of cell division
-systems in bacteria that were physically forced into unusual
-shapes. Varma et al. studied one particular example of a perturbed
-shape, a three-pronged tube, and found both experimental and
-simulation results\cite{varma2008min} supporting the idea that certain
-systems inside the cell begin to undergo oscillations inside the
-cell. These oscillations seem to seek out the extreme poles in the
-cell shape\cite{corbin2002exploring} \cite{juarez2010changes}, and
-effectively prevent minicelling in most cases. However, Mannik et
-al. have also shown that there are limitations to this
-mechanism\cite{mannik2010bacteria} \cite{mannik2009bacterial}. One
-instance of this behavior is observable when the cell has been forced
-into a flattened, irregular shape. Oscillations in this sort of cell
-shape are far from the regular sorts of oscillations seen in the
-computational work done by Huang et al\cite{huang2003dynamic}. We seek
-to apply a computational model to explore the more extreme or
-irregular cell shapes, in order to determine the limits of the steady
-cell oscillations seen by Mannik et al.
-
-%is this necessary? was in old paragraph.
-%\fixme{this link doesn't work =
-%  cite{mannik2012robustness}} \cite{mannik2010bacteria}
-%\cite{mannik2009bacterial}
+Studies have shown that the cell division process is capable of
+preventing minicelling for fairly perturbed cell
+shapes\cite{touhami2006temperature}. Varma et al. studied one
+particular example of a perturbed shape, a three-pronged tube, and
+found both experimental and simulation results\cite{varma2008min} that
+show oscillation. These oscillations seem to seek out the extreme
+poles in the cell shape\cite{corbin2002exploring}
+\cite{juarez2010changes}, and effectively prevent minicelling in most
+cases. However, Mannik et al. have also shown that there are
+limitations to this mechanism\cite{mannik2010bacteria}
+\cite{mannik2009bacterial}. One instance of this behavior is
+observable when the cell has been forced into a flattened, irregular
+shape. Oscillations in this sort of cell shape are far from the
+regular sorts of oscillations seen in the computational work done by
+Huang et al\cite{huang2003dynamic}. We seek to apply a computational
+model to explore the more extreme or irregular cell shapes, in order
+to determine the limits of the steady cell oscillations seen by both
+theory and experiment.
 
@@
 and diffusion models that exhibit accurate macroscopic dynamics of the
-MinD protein system. Early models involved free proteins that affect
+MinD protein system. Early models involve free proteins that affect
 each others' rates of diffusion and membrane attachment, but do not
 combine into compound states~\cite{meinhardt2001pattern}.  In 2003
-Huang improved upon this work with a simple model based on MinD-MinE
-combination, ATPase hydrolysis, and MinD membrane attachment that when
-simulated, exhibits accurate MinD oscillations in cylindrical
-cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is more
-likely to attach to the membrane when MinD is already clustered there
-(following observed non-linear attachement of minD on the cell
-membrane), and is stationary once attached.  A number of studies have
-used an approach similar in that they do not rely on the ability of
-MinD to move along the walls and
+Huang improved upon this work with a simple simulation model based on
+MinD-MinE combination, ATPase hydrolysis, and MinD membrane attachment
+that exhibits accurate MinD oscillations in
+cylindrical cells~\cite{huang2003dynamic}. In this model cytoplasmic
+MinD is more likely to attach to the membrane when MinD is already
+clustered there (following observed non-linear attachement of minD on
+the cell membrane), and is stationary once attached.  A number of
+studies have used an approach similar in that they do not rely on the
+ability of MinD to move along the walls and
 cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
@@
 used to study the MinD system and show consistent
-results.\cite{arjunan2010new}.  However, in general, the results of the
-stochastic and monte-carlo simulations are similar to those given by
-Huang's mean field results.
+results.\cite{arjunan2010new}.  However, in general, the results of
+the stochastic and monte-carlo simulations are similar to those given
+by Huang's mean field results.
 
@@
 
-\section{Model and Methods}
+\section{Model, Methods, and Pill Shaped Cell}
 We implement the model of Huang \emph{et al.}  for the behavior of the
@@
 activate ATP hydrolosis.  This breaks up the complex, releasing MinE,
-phosphate, and MinD:ADP back into the cell.  The MinD:ADP will undergo
+phosphate, and MinD:ADP back into the cytoplasm.  The MinD:ADP will undergo
 nucleotide exchange and begin again the cyclic process.  This model is
@@
 Our diffusion and reaction rates are shown below.  We are interested
-primarily in the effect of cellular shape on the protein
-oscillations, so we follow Huang's work\cite{huang2003dynamic} and do
-not deviate from the wild type values used in that work.  Huang's
-simulations use total MinD and MinE concentrations of $1,000/\mu m$
-and $350/\mu m$, respectively, in a cylindrical cell of radius $0.5\mu
-m$, and in our (non-cylindrical) cells we use the same number of
-proteins per unit volume.  These concentration values are 1273 $\mu
-m^{-3}$ and 445 $\mu m^{-3}$, respectively.
+primarily in the effect of cellular size and shape on the protein
+oscillations, so we follow Huang\cite{huang2003dynamic} and do not
+deviate from the wild type values used in the cited work (see values
+below).  Huang's simulations use total MinD and MinE concentrations of
+$1,000/\mu m$ and $350/\mu m$, respectively, in a cylindrical cell of
+radius $0.5\mu m$, and in our (non-cylindrical) cells we use the same
+number of proteins per unit volume.  These concentration values are
+1273 $\mu m^{-3}$ and 445 $\mu m^{-3}$, respectively.
 \begin{gather*}
@@
 
-\section{Cell shapes}
-
 We mean to investigate the geometric limits of the Min system
@@
   implementations of printouts reporting volume in the cpp}
-\section{Specific Results}
-
-\subsection{Pill Shape}
 
@@
   \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500.pdf}
-  \caption{Images of the concentration of each species in a natural
-    pill-shaped bacterium as a function of time, with darker regions
-    indicating higher concentration.  The cells pictured are
-    $4\micron$ in length, measured from end to end.  Frames from an animation showing
-    a series of contour plots of the concentration of proteins in
-    different stages over time.  The order of frames is such that
+  \caption{Countour plot images of the concentration of each protein
+    species in a natural pill-shaped bacterium at regular intervals in
+    time (one second intervals), with darker regions indicating higher
+    concentration.  The cells pictured are $4\micron$ in length,
+    measured from end to end.  The order of frames is such that
     individual MinD proteins begin at the bottom of the plot (in the
@@
 
+\begin{figure}
+  \includegraphics[width=\columnwidth]{stability-analysis}
+  \caption{Infinite slab stability analysis yields characteristic half
+    wavelengths at which system becomes unstable.}
+    \label{fig:stability-analysis}
+\end{figure}
+
+\section{Theory}
+Stability analysis of the five differential equations in an infinite
+slab show a characteristic half wavelength in perturbative spatial
+oscillations at which the system becomes unstable.  This length is
+dependent upon slab thickness as shown in
+Figure~\ref{fig:stability-analysis}.  When increasing the lengths and
+widths of our simulated flattened cells, the steady, two pole
+oscillations seem to break down when the the shortest distance across
+the cell is approximately equal to the characteristic half wavelength
+at the particular thickness at which we simulate (our simulations of cells
+with thickness $0.25\mu m$ corresponds to half wavelengths of $1.91\mu
+m$).  Huang~\cite{huang2003dynamic} performs a similar analysis for a
+cylindrical shape and finds characteristic half wavelengths of $2\mu
+m$.
+
 \subsection{Randst shape}
@@
   \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1300-2000-9400-1500.pdf}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1101-1101-9500-1500.pdf}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1100-1100-9500-1500.pdf}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1800-2500-9400-1500.pdf}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1800-1800-9500-1500.pdf}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-2300-3300-9400-1500.pdf}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-2800-2800-9500-1500.pdf}
   \caption{Arrow plots for our simulation and mannik's experimental}
@@
 
-Figure \ref{arrow-compare-mannik} shows a comparison of time maxima
+Figure~\ref{arrow-compare-mannik} shows a comparison of time maxima
 plots with similar plots published by mannik et al.  The sequence of
@@
 We have created for each of the two shapes published by Mannik a
-closely resembling shape (shown directly below Mannik's) and a
-variation on this shape (shown below that) in order to test the effect
-of variations on basic shapes.  The plots of the left shape show that
-much of the preffered locations for the proteins to maximize are
-similar between this experimental and simulated shape.  The maxima in
-the top center of the cell does not seem to appear in the experimental
-version.  Also in both of the simulations on the left there don't seem
-to be maxima at membrane regions with negative radii of curvature
-while the experimental shows a maxima in the bottom center region
-right at one of these regions.  The shape on the right compares less
-successfully.  Here the simulation shows a limited number of maxima
-locations that appear to be quite regular, where mannik's experimental
-results show a much more chaotic system.  In particular, the maxima
-location on the right wall seems to be very robust.  It acts as one of
-the poles do in the pill shapes.  \fixme{I'm now running a sim with a
-  slightly different shape to see result} The simulated version has
-found a robust two pole pattern, similar to that seen in other shapes.
+closely resembling shape (shown directly below Mannik's) that is in
+all dimensions the same size as that reported in their experiment.  We
+have also simulated longer and wider versions of these same shapes
+(keeping the cell thickness the same).  Shown in
+Figure~\ref{arrow-compare-mannik} are versions that have 1.3 and 2.0
+times the length and width dimensions.  These plots show
+that there are certain sizes at which the steady, two pole
+oscillations seem to break down, and indeed these lengths seem to be
+roughly those estimated by our 2D stability analysis.  \fixme{Waiting
+  to rewrite this section when more data, at more sizes, becomes
+  available} The plots of the left shape show that much of the
+preffered locations for the proteins to maximize are similar between
+this experimental and simulated shape.  The maxima in the top center
+of the cell does not seem to appear in the experimental version.  Also
+in both of the simulations on the left there don't seem to be maxima
+at membrane regions with negative radii of curvature while the
+experimental shows a maxima in the bottom center region right at one
+of these regions.  The shape on the right compares less successfully.
+Here the simulation shows a limited number of maxima locations that
+appear to be quite regular, where mannik's experimental results show a
+much more chaotic system.  In particular, the maxima location on the
+right wall seems to be very robust.  It acts as one of the poles do in
+the pill shapes.  \fixme{I'm now running a sim with a slightly
+  different shape to see result} The simulated version has found a
+robust two pole pattern, similar to that seen in other shapes.
 

### 2014-02-05 paper/paper.tex
updates to methods and pill section of paper Tested everything on node32.

@@
 number of proteins per unit volume.  These concentration values are
-1273 $\mu m^{-3}$ and 445 $\mu m^{-3}$, respectively.
+1273 $\mu m^{-3}$ and 446 $\mu m^{-3}$, respectively.
 \begin{gather*}
@@
 the cell.
+
+We mean to investigate the geometric limits of the Min system
+oscillations as observed by Mannik \emph{et
+  al.}~\cite{mannik2012robustness}, so we model the Min system in a
+variety of cell shapes and sizes.  Here we present a selection of
+those, first naturally occuring pill-shaped cells and then a
+number of flattened out shapes which reflect the experiments of Mannik
+\emph{et al.}, in which bacteria are confined within a thin slit of
+height $0.25\micron$ ~\cite{mannik2012robustness}. Viewed from the top
+down the cells will have the shapes described below and viewed from
+the side they have at their edges a semicircular protrusion (one may
+imagine the edges of a pancake). Central to our observations are the
+effects of cell size and so we show expanded cells that have the same
+thickness but increased dimensions in the two planar directions.  We
+present two shapes that are designed to replicate those published by
+Mannik, equilateral and iscosolese triangle shapes, and a 'V' shape of
+our own creation in order to best illustrate the effect of cell size
+on oscillation stability.
+
+%% Our pill shapes differ from those of Huang \emph{et al.} in that they
+%% are cylinders with hemisphere endcaps instead of pure cylindrical
+%% shapes.  Our cylinderidrical radius is $0.5\micron$ and the lengths
+%% of our cells (measured between the tips of the endcaps) are
+%% $5\micron$, $4\micron$, $3\micron$, and $2.5\micron$.
+
+Kubitschek has shown in multiple experiments that at the time of cell
+division cells have a volume that is within a range of roughly
+$1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
+  kubitschek1968linear}.  We follow Huang's
+simulations\cite{huang2003dynamic} and Mannik's experiments and model
+cells that are slightly larger than this range.
+
+\begin{figure*}
+  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500.pdf}
+  \caption{Countour plot images of the concentration of each protein
+    species in a natural pill-shaped bacterium at regular intervals in
+    time (one second intervals), with darker regions indicating higher
+    concentration.  The cells pictured are $4\micron$ in length,
+    measured from end to end.  The order of frames is such that
+    individual MinD proteins begin at the bottom of the plot (in the
+    MinD:ATP state in the cytoplasm), and progress upward until they
+    reach the MinE:MinD:ATP membrane-bound complex.  At that point,
+    they will spontaneously dissociate into cytoplasmic MinE (the top
+    row) and the starting state of cytoplasmic MinD:ADP.  The
+    densities plotted are integrated along the axis orthogonal to the
+    page, and the color scale is chosen separately for each species
+    with black as the maximum value over space and time.}
+  \label{image-p}
+\end{figure*}
 
@@
 to this MinD and remains for a time on the walls in compound form.
-When it is released, it has the two options of diffusing naturally
-outward or inward towards the cell.  If it diffuses inward, there is
-less cross sectional wall for it to bump into and also less
-concentrated MinD:ATP to react with.  If it diffuses outward, the
-curvature of the cell wall cuases there to be a greater probability
-per unit time that it will encounter the cell membrane (for the same
-reason outlined for the MinD:ATP above) where there is more membrane
-bound MinD:ATP. If it does diffuse in this directin, it will likely
-react with MinD:ATP before getting very far into the encap.  This
+When released, if it diffuses inward, there is less cross sectional
+wall for it to bump into and also less concentrated MinD:ATP to react
+with, whereas if it diffuses outward the opposite is the case.  This
 process results in the observed qualitative 'encroaching MinE ring'
@@
 MinD:ADP will diffuse for a time before spontanosly undergowing
-nucleotide exchange and reaching the MinD:ATP state that
-can bind to the membrane again.  There is a strong chance that it has
-by this time diffused out of the polar region and is on its way to the
-opposite polar region of the cell.  If it hasn't then it will reattach
-to the MinD:ATP on the cell wall deeper into the endcap and will
-eventually be converged upon by the MinE ring, only to be released
-again in MinD:ADP form.
+nucleotide exchange and reaching the MinD:ATP state that can bind to
+the membrane again.  There is a strong chance that it has by this time
+diffused out of the polar region and is on its way to the opposite
+polar region of the cell.  If it hasn't then it will reattach to the
+MinD:ATP on the cell wall deeper into the endcap and will eventually
+be converged upon by the MinE ring, only to be released again in
+MinD:ADP form.
 
@@
 shapes.
-
-We mean to investigate the geometric limits of the Min system
-oscillations, as observed by Mannik \emph{et
-  al.}~\cite{mannik2012robustness}, so we model the Min system in a
-variety of cell shapes.  We begin with naturally occuring pill-shaped
-cells and then proceed to examine a number of flattened pancake-like
-shapes, which reflect the experiment of Mannik \emph{et al.}, in which
-bacteria were confined within a thin slit~\cite{mannik2012robustness}.
-Our pill shapes differ from those of Huang \emph{et al.} in that they
-are cylinders with hemisphere endcaps instead of pure cylindrical
-shapes.  Our cylinderidrical radius is $0.5\micron$ and the lengths
-of our cells (measured between the tips of the endcaps) are
-$5\micron$, $4\micron$, $3\micron$, and $2.5\micron$.
-
-With our flattened cell shapes we mean to study cells that are
-parrallel to those lodged into crevices by Mannik so we give them
-height of $0.25\micron$ \cite{mannik2012robustness}.  Viewed from the top
-down the cells will have the shapes described below and viewed from
-the side they have at their edges a semicircular protrusion (one may
-imagine the edges of a pancake).
-
-Our first group of (three) flattened cell shapes are triangular when
-viewed from above.  One of them is equilateral, one has a 3-4-5 right
-angle shape, and the last is iscoscolese.
-
-Our second group of (two) flattened cells are designed to replicate
-those published by Mannik, in order to compare the results of the
-simulation model with the experimental results in that work.
-
-Our third group of (three) flattened cells are our own creations,
-designed to investigate different patterns of protein oscillation
-behavoir.
-
-Kubitschek has shown in multiple experiments that at the time of cell
-division cells have a volume that is within a range of roughly
-$1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
-  kubitschek1968linear}.  We follow Huang's
-simulations\cite{huang2003dynamic} and Mannik's experiments and model
-cells that are slightly larger than this range.  Amoung our flattened
-cells the two dimensional length scales are tuned so that total cell
-volumes are very close to $3\micron^3$. \jeffsays{I'm not sure how
-  true this is.  We should go through and check.  There've been a few
-  implementations of printouts reporting volume in the cpp}
-
-\begin{figure*}
-  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500.pdf}
-  \caption{Countour plot images of the concentration of each protein
-    species in a natural pill-shaped bacterium at regular intervals in
-    time (one second intervals), with darker regions indicating higher
-    concentration.  The cells pictured are $4\micron$ in length,
-    measured from end to end.  The order of frames is such that
-    individual MinD proteins begin at the bottom of the plot (in the
-    MinD:ATP state in the cytoplasm), and progress upward until they
-    reach the MinE:MinD:ATP membrane-bound complex.  At that point,
-    they will spontaneously dissociate into cytoplasmic MinE (the top
-    row) and the starting state of cytoplasmic MinD:ADP.  The
-    densities plotted are integrated along the axis orthogonal to the
-    page, and the color scale is chosen separately for each species
-    with black as the maximum value over space and time.}
-  \label{image-p}
-\end{figure*}
 
@@
 
-At $t=0$ in Figs.~\ref{image-p}~and~\ref{box-p}, the cytoplasmic MinE
+At $t=0$ in Figs.~\ref{image-p}, the cytoplasmic MinE
 is concentrated in the lower portion of the cell, and is diffusing
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-300-50-0-0-1500}
-  \caption{Total protein fluctuation in the right, middle, and left
-    parts of a natural pill shaped cell.  The cell is the same as is
-    shown in Fig.~\ref{image-p}.  The time axis is also identical to
-    that shown in Fig.~\ref{image-p}, and shows one period of the
-    oscillation after the system has settled down.  The vertical axis
-    shows stacked the total number of proteins that are of four
-    different compound stages and in the right section of the cell
-    (bottom four colors), in the middle of the cell (middle four
-    colors) and in the left section of the cell (top four colors). The
-    different forms of protein changes while the total number of MinD
-    protein in the cell remains constant, shown by the fact that the
-    very top line is horizontal.}
-  \label{box-p}
-\end{figure}
-
-While Fig.~\ref{image-p} is helpful for visualizing
-the process occuring in the Min system, it is does not show the
-relative number of proteins in each state.  To visualize this
-information, we plot in Fig.~\ref{box-p} the fraction of MinD found in
-each stage of the cycle in each of three sections of the cell---top,
-middle and bottom---as a function of time over one period.  The time
-axis is the same as in Fig.~\ref{image-p}.  Looking at the evolution
-of the latter, we see an initial high concentration of cytoplasmic
-MinD:ATP, as the this protein diffuses into the polar region, followed
-by a dip in this and large spike in membrane bound MinD:ATP, as the
-protein clusters onto the polar cell wall, followed by a spike in the
-memebrane bound MinE:MinD:ATP stage of protein, together with a slight
-rise in cytoplasmic MinD:ADP as the MinD dettaches from the wall.
-
-results for pill shaped cell of length
-$5\mu$ and radius $.5\mu$.  The plot shows both the transerence
-between different stages of protein compound and movement within the
-cell.  Starting at the beginning of a period, we can see that first
-there is a spike on the left of MinD-ATP attached to the wall that is
-accompanied by a growing number of cytoplasmic MinD-ATP and MinD-ADP
-that are entering the left section, followed by a high peak in
-MinD-MinE-ATP.  This peak gives way through the middle to peaks on the
-right side of the cell, the first being a small bump in cytoplasmic
-MinD-ATP that dissapears into a much larger spike in wall attached
-MinD-ATP, which is followed by a peak in wall attached MinD-MinE-ATP.
-The pattern during each period clearly shows the cycle of proteins
-rections, as well as the very regular nature of the pole to pole
-protein oscillations.
-
-We can see a
-clear difference in period between the $5\mu$, $4\mu$, and $2\mu$
-length cells.  The oscillation periods for our $4\mu$ show excellent
-agreement with the simulations of Huang et all
-\cite{huang2003dynamic}.  This is to be expected since we begin our
-simulations with their reported wild type concentrations of MinD and
-MinE proteins. The periods for the different pill lengths are shown in
-the table below.  We can see a direct correltation between size and
-period, as the proteins must diffuse further in a longer cell before
-they accumulate on the opposite wall.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/plots/ave-plot_D--p-300-50-0-0-1500}
-  \caption{Average protein density per unit area of wall for the wall
-    attached stages of the protein cycle.  Shown in the right, middle,
-    and left parts of a 5$\micron$ by 1$\micron$ pill shaped cell (above)
-    and a 3$\micron$ by 1$\micron$ pill shaped cell (below).}
-  \label{ave-per-area-plot-pill}
-\end{figure}
-
-Figure \ref{ave-per-area-plot-pill} shows the ave protein per unit
-area that is wall attached in the middle, right, and left sections of
-the pill shaped cell.  This is an important test of the central idea
-behind the utility of the Min protein system.  The system is meant to
-place Min proteins on the walls in heavier concentrations in the caps
-of the cell and lower concentrations in the middle section, so that
-the FtZ polymer may build up along the center walls.  We can see from
-the plot of the 3$\micron$ by 1$\micron$ cell that the MinD proteins reach
-concentration peaks in the caps that are higher than peaks in the
-center.  \fixme{is the next part true?} Integrals of these plotted values show that the time averaged
-concentrations are likewise higher in the caps than in the center.
-
-\subsection{Triangular Shapes}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
-  \caption{Total protein fluctuation in the right, middle, and left
-    parts of an equilateral (top), iscoscolese (middle), and 3-4-5
-    (bottom) triangle.  The vertical axis shows stacked the total
-    number of proteins that are of four different compound stages and
-    in the different sections of the cell.}
-  \label{box-triangle}
-\end{figure}
-
-The double pole oscillation pattern, in which one pole is located in a
-single corner of the triangle and the other pole is spread out between
-the opposite two, can be seen in Figure \ref{box-triangle}.  The
-equilateral triangle shows a spike in both the Center and Left
-sections at the same time, both showing the familiar sequence of peaks
-amoungst the different states of the protein seen in the poles of the
-pill shaped bacteria.  A spike in the other corner, showing the common
-sequence, occurs during the minima of the former two, wth a higher
-concentration at the peak.  A similar pattern is seen in the
-iscosolese triangular shape, where interestingly the onset of the
-maxima in the single maxima corner (the Left section) builds more
-quickly than it fades.  This is presumably becuase as the cytoplasmic
-minD:ATP diffuses down a more accute corner, it is sourrounded by
-closer cell walls than it would be in a less acute corner, so that the
-it is more apt at any diffusive step to make contact and cluster on
-the walls.  That particular part of the process is therefore
-accelerated, driving the build up of the maxima forward.
-
-The right triangle shows a similar pattern except that here there is
-an assymetry between the two corners that maximize at roughly the same
-time.  One corner is further from the single maximizing corner and it
-consisitently peaks later.  The MinD simply have further to travel
-before they maximize there.
-
-For these three sizess and shapes there is not sign that the
-oscillation patterns once they are set will break down.
-
-\begin{figure}
-%%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
-  \caption{Total protein fluctuation of an equilateral triangle with
-    larger dimensions (each side is roughly $6\micron$.  The vertical
-    axis shows stacked the total number of proteins that are of four
-    different compound stages and in the different sections of the
-    cell. The time limits have been set to show the broken down
-    section of the simulation.}
-  \label{box-triangle}
-
-The larger equilateral shape shows the same pattern as the smaller
-version does only until fifteen periods, at which point there is a
-breakdown of the oscillation pattern.  During the last three stable
-periods, the single maximizing corner, the lower left section in the
-figure, has a lower peak each period as the membrane bound MinD:ATP in
-the other corners lag more and more before being eaten away by the
-MinE.  Finally these maxima lag so much that they break down the
-regular pattern.  There then occurs about five periods of semi chaotic
-behavoir, until it settles back into another stable oscillation that
-is similar to the original one, except that a different corner has
-been chosen to be the singlular maxima (the right section in the
-figure), while the other two corners maximize at the same time.  This
-interesting breakdown and recovery shows both the robustness of the
-double pole oscilatory tendency and the importance of required
-distance of travel for the different proteins.
-
-\end{figure}
-
-Fifteen
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-300-50-0-0-1500}
+%%   \caption{Total protein fluctuation in the right, middle, and left
+%%     parts of a natural pill shaped cell.  The cell is the same as is
+%%     shown in Fig.~\ref{image-p}.  The time axis is also identical to
+%%     that shown in Fig.~\ref{image-p}, and shows one period of the
+%%     oscillation after the system has settled down.  The vertical axis
+%%     shows stacked the total number of proteins that are of four
+%%     different compound stages and in the right section of the cell
+%%     (bottom four colors), in the middle of the cell (middle four
+%%     colors) and in the left section of the cell (top four colors). The
+%%     different forms of protein changes while the total number of MinD
+%%     protein in the cell remains constant, shown by the fact that the
+%%     very top line is horizontal.}
+%%   \label{box-p}
+%% \end{figure}
 
@@
 robust two pole pattern, similar to that seen in other shapes.
+
+\subsection{Triangular Shapes}
+\begin{figure}
+  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
+  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
+  \caption{Total protein fluctuation in the right, middle, and left
+    parts of an equilateral (top), iscoscolese (middle), and 3-4-5
+    (bottom) triangle.  The vertical axis shows stacked the total
+    number of proteins that are of four different compound stages and
+    in the different sections of the cell.}
+  \label{box-triangle}
+\end{figure}
+
+The double pole oscillation pattern, in which one pole is located in a
+single corner of the triangle and the other pole is spread out between
+the opposite two, can be seen in Figure \ref{box-triangle}.  The
+equilateral triangle shows a spike in both the Center and Left
+sections at the same time, both showing the familiar sequence of peaks
+amoungst the different states of the protein seen in the poles of the
+pill shaped bacteria.  A spike in the other corner, showing the common
+sequence, occurs during the minima of the former two, wth a higher
+concentration at the peak.  A similar pattern is seen in the
+iscosolese triangular shape, where interestingly the onset of the
+maxima in the single maxima corner (the Left section) builds more
+quickly than it fades.  This is presumably becuase as the cytoplasmic
+minD:ATP diffuses down a more accute corner, it is sourrounded by
+closer cell walls than it would be in a less acute corner, so that the
+it is more apt at any diffusive step to make contact and cluster on
+the walls.  That particular part of the process is therefore
+accelerated, driving the build up of the maxima forward.
+
+The right triangle shows a similar pattern except that here there is
+an assymetry between the two corners that maximize at roughly the same
+time.  One corner is further from the single maximizing corner and it
+consisitently peaks later.  The MinD simply have further to travel
+before they maximize there.
+
+For these three sizess and shapes there is not sign that the
+oscillation patterns once they are set will break down.
+
+\begin{figure}
+%%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
+  \caption{Total protein fluctuation of an equilateral triangle with
+    larger dimensions (each side is roughly $6\micron$.  The vertical
+    axis shows stacked the total number of proteins that are of four
+    different compound stages and in the different sections of the
+    cell. The time limits have been set to show the broken down
+    section of the simulation.}
+  \label{box-triangle}
+
+The larger equilateral shape shows the same pattern as the smaller
+version does only until fifteen periods, at which point there is a
+breakdown of the oscillation pattern.  During the last three stable
+periods, the single maximizing corner, the lower left section in the
+figure, has a lower peak each period as the membrane bound MinD:ATP in
+the other corners lag more and more before being eaten away by the
+MinE.  Finally these maxima lag so much that they break down the
+regular pattern.  There then occurs about five periods of semi chaotic
+behavoir, until it settles back into another stable oscillation that
+is similar to the original one, except that a different corner has
+been chosen to be the singlular maxima (the right section in the
+figure), while the other two corners maximize at the same time.  This
+interesting breakdown and recovery shows both the robustness of the
+double pole oscilatory tendency and the importance of required
+distance of travel for the different proteins.
+
+\end{figure}
 

### 2014-02-05 paper/paper.tex
more updates to methods and pill section of paper Tested everything on node32.

@@
 
+We begin with the naturally occuring pill cell shape.  We peice this
+shape together as two hemispherical endcaps attached on either end of
+a cylinder.  This shape follows the early simulations of Huang
+\emph{et al.} but differs in that we have added the end caps for a
+more natural shape, expecting similar results.  We test cells of
+radius $.5\micron$ and of lengths $2\micron$, $3\micron$, and
+$5\micron$ measured from the tip of one end cap to the top of the
+other. In each case, we observe quick establishement (within a few
+periods) of extremely regular oscillatory behavoir that lasts
+indefinitely.  The period increases with cell length, as shown in
+Table~\ref{tab:pill-periods}, in agreement with the results of Huang
+\emph{et al.}
+
+\begin{table}
+  \begin{tabular}{|r|c|c|c|l|}
+    \hline
+    Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
+    \hline
+    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
+    \hline
+  \end{tabular}
+  \caption{Period of oscillation according to length of cell for
+    pill-shaped cells.}\label{tab:pill-periods}\fixme{whats the 'sim'
+    here?}
+\end{table}
+
+This simple cell shape is a good starting point for observing in
+detail the dynamic interaction between the different stages of protein
+that lead to their qualitatively distinct behavoir. Figure
+\ref{image-p} shows the process in a series of frames taken from
+simulation animations.  Each frame is 2.5 seconds ahead of the last,
+and each image shows a the concentration of a given state of protein
+summed over the coordinate orthogonal to the page.  The color scale
+for each protein state is set according to the maximum density
+observed.
+
+At $t=0$ in Figs.~\ref{image-p}, the cytoplasmic MinE
+is concentrated in the lower portion of the cell, and is diffusing
+upward.  The MinD protein is initially concentrated on the membrane in
+the upper portion of the cell.  At the boundary between the
+cytoplasmic MinE and the membrane-bound MinD, there is a ring of the
+membrane-bound MinE:MinD complex, which is moving towards the upper
+end of the cell, removing the MinD from the membrane as it goes.  The
+MinD is removed from the membrane in its MinD:ADP form, which begins
+to accumulate at the upper end of the cell, peaking at around
+10 seconds.
+
+At 15 seconds, the membrane-bound MinD:ATP has been essentially
+removed from the top end of the cell, and MinD:ATP has begun to bind
+to the membrane in the the lower half of the cell.  At this stage,
+there is a high concentration of cytoplasmic MinE at the top of the
+cell, and by 16 seconds we begin to see the formation of a MinE ring
+just below the center of the cell.  At 18 seconds, the cell has
+reached its original state, with MinD:ATP bound to the membrane on the
+lower third of the cell, a high concentration of cytoplasmic MinE in
+the upper half of the cell, and a MinE ring pushing on the
+membrane-bound MinD:ATP.
+
 The reactions shown in Figure~\ref{fig:reactions} are cyclical so we
@@
 shapes.
-
-We begin with the naturally occuring pill cell shape.  We peice this
-shape together as two hemispherical endcaps attached on either end of
-a cylinder.  This shape follows the early simulations of Huang
-\emph{et al.} but differs in that we have added the end caps for a
-more natural shape, expecting similar results.  We test cells of
-radius $.5\micron$ and of lengths $2\micron$, $3\micron$, and
-$5\micron$ measured from the tip of one end cap to the top of the
-other. In each case, we observe quick establishement (within a few
-periods) of extremely regular oscillatory behavoir that lasts
-indefinitely.  The period increases with cell length, as shown in
-Table~\ref{tab:pill-periods}, in agreement with the results of Huang
-\emph{et al.}.
-
-\begin{table}
-  \begin{tabular}{|r|c|c|c|l|}
-    \hline
-    Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
-    \hline
-    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
-    \hline
-  \end{tabular}
-  \caption{Period of oscillation according to length of cell for
-    pill-shaped cells.}\label{tab:pill-periods}
-\end{table}
-
-This simple model is a good starting point for observing in detail the
-dynamic interaction between the different stages of protein that lead
-to their qualitatively distinct behavoir. Figure \ref{image-p} shows
-the process in a series of frames taken from simulation animations.
-Each frame is 2.5 seconds ahead of the last, and each image shows a
-the concentration of a given state of protein summed over the
-coordinate orthogonal to the page.  The color scale for each protein
-state is set according to the maximum density observed.
-
-At $t=0$ in Figs.~\ref{image-p}, the cytoplasmic MinE
-is concentrated in the lower portion of the cell, and is diffusing
-upward.  The MinD protein is initially concentrated on the membrane in
-the upper portion of the cell.  At the boundary between the
-cytoplasmic MinE and the membrane-bound MinD, there is a ring of the
-membrane-bound MinE:MinD complex, which is moving towards the upper
-end of the cell, removing the MinD from the membrane as it goes.  The
-MinD is removed from the membrane in its MinD:ADP form, which begins
-to accumulate at the upper end of the cell, peaking peaking at around
-10 seconds.
-
-At 15 seconds, the membrane-bound MinD:ATP has been essentially
-removed from the top end of the cell, and MinD:ATP has begun to bind
-to the membrane in the the lower half of the cell.  At this stage,
-there is a high concentration of cytoplasmic MinE at the top of the
-cell, and by 16 seconds we begin to see the formation of a MinE ring
-just below the center of the cell.  At 18 seconds, the cell has
-reached its original state, with MinD:ATP bound to the membrane on the
-lower third of the cell, a high concentration of cytoplasmic MinE in
-the upper half of the cell, and a MinE ring pushing on the
-membrane-bound MinD:ATP.
 

### 2014-02-05 paper/paper.tex
even more updates to methods and pill section of paper Tested everything on node32.

@@
   \caption{Period of oscillation according to length of cell for
-    pill-shaped cells.}\label{tab:pill-periods}\fixme{whats the 'sim'
-    here?}
+    pill-shaped cells.}\label{tab:pill-periods}\fixme{the 'sim' here
+    means that it's waiting for a simulation.  Not sure where it went
+    but I'm rerunning it.}
 \end{table}
@@
 
-At $t=0$ in Figs.~\ref{image-p}, the cytoplasmic MinE
-is concentrated in the lower portion of the cell, and is diffusing
-upward.  The MinD protein is initially concentrated on the membrane in
-the upper portion of the cell.  At the boundary between the
-cytoplasmic MinE and the membrane-bound MinD, there is a ring of the
-membrane-bound MinE:MinD complex, which is moving towards the upper
-end of the cell, removing the MinD from the membrane as it goes.  The
-MinD is removed from the membrane in its MinD:ADP form, which begins
-to accumulate at the upper end of the cell, peaking at around
-10 seconds.
+At $t=0$ in Figs.~\ref{image-p}, the cytoplasmic MinE is concentrated
+in the lower portion of the cell and is diffusing upward, since it
+will react with and stick to wall-bound MinD that is concentrated on
+the membrane in the upper portion of the cell.  At the boundary
+between the cytoplasmic MinE and the membrane-bound MinD, there is a
+ring of the membrane-bound MinE:MinD complex, which is moving towards
+the upper end of the cell, removing the MinD from the membrane as it
+goes.  The MinD is removed from the membrane in its MinD:ADP form and
+diffuses freely for a time before spontenously undergowing nucleotide
+exchange and shifting back into the MinD:ATP that is able to attach to
+the membrane.  Diffusion away from the end of the cell will bring the
+protein into the MinE ring, where reactions will prevent it from
+collecting for any significant time on the membrane.  Diffusion
+further towards the upper end, however, while the MinE has not yet
+collected there, will allow MinD:ATP to accumulate with the other
+MinD:ATP, peaking at around 10 seconds in Figure~\ref{image-p}.  As
+the MinE ring approaches the end of the cell, seen in the seconds
+following 10, the only freely diffusing MinD:ADP that 'escapes' the
+MinE will be that which has diffused away from the the end of the cell
+and past the MinE ring towards the center.
 
@@
 just below the center of the cell.  At 18 seconds, the cell has
-reached its original state, with MinD:ATP bound to the membrane on the
-lower third of the cell, a high concentration of cytoplasmic MinE in
-the upper half of the cell, and a MinE ring pushing on the
-membrane-bound MinD:ATP.
+reached its original state (reversed directionally), with MinD:ATP
+bound to the membrane on the lower third of the cell, a high
+concentration of cytoplasmic MinE in the upper half of the cell, and a
+MinE ring pushing downward on the membrane-bound MinD:ATP.
 
-The reactions shown in Figure~\ref{fig:reactions} are cyclical so we
-can begin our observations at any stage in the cycle (which is
-presented for the natural, pill shapes cell in Fig.~\ref{image-p}
-below).  We consider first MinD:ATP floating freely in the cytoplasm.
-The protein will not react with any other floating protein, and it
-will not spontenously shift back into the MinD:ADP stage of the cycle.
-It will diffuse until it attaches to a cell membrane.  This will
-happen most rapidly in cytoplasmic regions that are close to membrane
-regions of high curvature, where diffusion in a random direction is
-more likely to lead to an encounter with a wall.  This effect is made
-more pronounced by the MinD:ATP tendency to attract and cluster on the
-membrane, as reflected in Equation~\ref{eq:d-on-wall}, which shows
-that when adjacent to the membrane, the rate of binding to the
-membrane is porportional to the amount of MinD already bound to the
-wall.  Initially, then, there is a strong tendency of MinD to cluster
-on the polar regions of the cell, where the curvature is highest.
-
-We next see the formation of MinE `rings' on the membranes of the
-polar caps.  As the freely diffusing MinE enters the cap portion it
-begins to encounter concentrated membrane bound MinD.  The MinE binds
-to this MinD and remains for a time on the walls in compound form.
-When released, if it diffuses inward, there is less cross sectional
-wall for it to bump into and also less concentrated MinD:ATP to react
-with, whereas if it diffuses outward the opposite is the case.  This
-process results in the observed qualitative 'encroaching MinE ring'
-behavoir that releases MinD:ADP back into the cytoplasm.  This
-MinD:ADP will diffuse for a time before spontanosly undergowing
-nucleotide exchange and reaching the MinD:ATP state that can bind to
-the membrane again.  There is a strong chance that it has by this time
-diffused out of the polar region and is on its way to the opposite
-polar region of the cell.  If it hasn't then it will reattach to the
-MinD:ATP on the cell wall deeper into the endcap and will eventually
-be converged upon by the MinE ring, only to be released again in
-MinD:ADP form.
-
-Overall this process results in extremely robust oscillatory
-behavoir of polar selection and oscillation in a wide variety of cell
-shapes.
-
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-p/plots/box-plot_D--p-300-50-0-0-1500}
-%%   \caption{Total protein fluctuation in the right, middle, and left
-%%     parts of a natural pill shaped cell.  The cell is the same as is
-%%     shown in Fig.~\ref{image-p}.  The time axis is also identical to
-%%     that shown in Fig.~\ref{image-p}, and shows one period of the
-%%     oscillation after the system has settled down.  The vertical axis
-%%     shows stacked the total number of proteins that are of four
-%%     different compound stages and in the right section of the cell
-%%     (bottom four colors), in the middle of the cell (middle four
-%%     colors) and in the left section of the cell (top four colors). The
-%%     different forms of protein changes while the total number of MinD
-%%     protein in the cell remains constant, shown by the fact that the
-%%     very top line is horizontal.}
-%%   \label{box-p}
-%% \end{figure}
+In general process results in extremely robust oscillatory behavoir of
+polar selection and oscillation in a wide variety of cell shapes.
 

### 2014-02-05 paper/paper.tex
added data for other_arrow_plot.py and also mannik section edits to paper Tested everything on node32.

@@
 
-In general process results in extremely robust oscillatory behavoir of
-polar selection and oscillation in a wide variety of cell shapes.
-
 \begin{figure}
@@
 
-\section{Theory}
-Stability analysis of the five differential equations in an infinite
-slab show a characteristic half wavelength in perturbative spatial
+\section{Stability Analysis and Mannik's Experimental Shapes}
+In general we have found that the protein reaction sequence discussed
+above results in extremely robust oscillatory behavoir of polar
+selection and oscillation in a wide variety of cell shapes.  However
+we have found that this robustness is heavily dependent upon cell
+size.  Two pole, regular oscillatory behavoir is found in cells which
+are long enough in one dimension for the reaction chain to be unstable
+but short enough in the perpendicular dimension to be stable.  The
+limits are seen when both dimensions are too short to be unstable, so
+that initial assymetry in protein concentration relaxes into a
+motionless steady state, or when both are too great, so that the
+proteins exhibit much more complex and varied behavoir.
+
+In order to explain this theoretically, we have performed stability
+analysis of the five differential equations in an infinite slab that
+shows a characteristic half wavelength in perturbative spatial
 oscillations at which the system becomes unstable.  This length is
@@
 the cell is approximately equal to the characteristic half wavelength
-at the particular thickness at which we simulate (our simulations of cells
-with thickness $0.25\mu m$ corresponds to half wavelengths of $1.91\mu
-m$).  Huang~\cite{huang2003dynamic} performs a similar analysis for a
-cylindrical shape and finds characteristic half wavelengths of $2\mu
-m$.
+at the particular thickness at which we simulate (our simulations of
+cells with thickness $0.25\mu m$ corresponds to half wavelengths of
+\fixme{check next number} $1.91\mu m$).  Huang~\cite{huang2003dynamic}
+performs a similar analysis for a cylindrical shape and finds
+characteristic half wavelengths of $2\mu m$.
 
-\subsection{Randst shape}
-\fixme{Cheat sheet for the shapes, need to put these into a big figure
-  from the sections output: 96=star shape, 97=sideways sideways
-  flying saucer pancake, 98=manniks squished cell, 99=an A}
-
-\subsubsection{Randst-mannik shape}
 \begin{figure}
@@
 
-Figure~\ref{arrow-compare-mannik} shows a comparison of time maxima
-plots with similar plots published by mannik et al.  The sequence of
-arrows show a series of global maxima in space and local maxima in
-time at their heads, numbered by the sequence in which they occur.
-They function as a trace of the path that the traveling maxima take.
-We have created for each of the two shapes published by Mannik a
-closely resembling shape (shown directly below Mannik's) that is in
-all dimensions the same size as that reported in their experiment.  We
-have also simulated longer and wider versions of these same shapes
-(keeping the cell thickness the same).  Shown in
-Figure~\ref{arrow-compare-mannik} are versions that have 1.3 and 2.0
-times the length and width dimensions.  These plots show
-that there are certain sizes at which the steady, two pole
-oscillations seem to break down, and indeed these lengths seem to be
-roughly those estimated by our 2D stability analysis.  \fixme{Waiting
-  to rewrite this section when more data, at more sizes, becomes
-  available} The plots of the left shape show that much of the
-preffered locations for the proteins to maximize are similar between
-this experimental and simulated shape.  The maxima in the top center
-of the cell does not seem to appear in the experimental version.  Also
-in both of the simulations on the left there don't seem to be maxima
-at membrane regions with negative radii of curvature while the
-experimental shows a maxima in the bottom center region right at one
-of these regions.  The shape on the right compares less successfully.
-Here the simulation shows a limited number of maxima locations that
-appear to be quite regular, where mannik's experimental results show a
-much more chaotic system.  In particular, the maxima location on the
-right wall seems to be very robust.  It acts as one of the poles do in
-the pill shapes.  \fixme{I'm now running a sim with a slightly
-  different shape to see result} The simulated version has found a
-robust two pole pattern, similar to that seen in other shapes.
+Figure~\ref{arrow-compare-mannik} shows plots of total MinD
+concentration maxima that are global in space and local in time.  The
+tip of an arrow represents one of these maxima and the adjacent arrow
+(whose tail is touching the previous arrow's tip) points to the next
+such maxima in time.  Mannik \emph{et al.} have published similar
+plots of two of their cells, and we have attempted to replicate the
+shape of these cells in our simulation in order to compare.  We find
+that when we replicate the size as well as shape of their cells as
+near as possible, we do not see the disordered protein behavoir that
+they observe.  Instead we see a robust ability of the cell to find two
+prefered pole locations and to oscillate maxima back and forth very
+steadily between them.  However, when we keep the same shape but
+increase the size, we see that there is a critical size at which the
+protein dynamics lose their order and become very complex (showing
+hints of prefered wall maxima locations), similar to what Mannik sees
+experimentally.  We find that this critical size matches up well with
+our stability analysis, in that the critical sizes correspond to sizes
+for which the shorter of the two distances across the cell is roughly
+equal to the analysis' half wavelength found for this cell thickness.
 
-\subsection{Triangular Shapes}
+\fixme{I'm also waiting for data to come in that will hopefully show
+  cells so small that no oscillations take place.  We can put this in
+  as well}
+
+\section{Triangular Shapes}
 \begin{figure}

### 2014-02-05 paper/paper.tex
changed result of stability analysis Tested everything on node32.

@@
 cells with thickness $0.25\mu m$ corresponds to half wavelengths of
-\fixme{check next number} $1.91\mu m$).  Huang~\cite{huang2003dynamic}
-performs a similar analysis for a cylindrical shape and finds
-characteristic half wavelengths of $2\mu m$.
+$2.13\mu m$).  Huang~\cite{huang2003dynamic} performs a similar
+analysis for a cylindrical shape and finds characteristic half
+wavelengths of $2\mu m$.
 

### 2014-02-05 paper/paper.tex
updated randst arrow data and commented out triangle writing we had thus far in paper Tested everything on node32.

@@
 \section{Triangular Shapes}
-\begin{figure}
-  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
-  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
-  %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
-  \caption{Total protein fluctuation in the right, middle, and left
-    parts of an equilateral (top), iscoscolese (middle), and 3-4-5
-    (bottom) triangle.  The vertical axis shows stacked the total
-    number of proteins that are of four different compound stages and
-    in the different sections of the cell.}
-  \label{box-triangle}
-\end{figure}
 
-The double pole oscillation pattern, in which one pole is located in a
-single corner of the triangle and the other pole is spread out between
-the opposite two, can be seen in Figure \ref{box-triangle}.  The
-equilateral triangle shows a spike in both the Center and Left
-sections at the same time, both showing the familiar sequence of peaks
-amoungst the different states of the protein seen in the poles of the
-pill shaped bacteria.  A spike in the other corner, showing the common
-sequence, occurs during the minima of the former two, wth a higher
-concentration at the peak.  A similar pattern is seen in the
-iscosolese triangular shape, where interestingly the onset of the
-maxima in the single maxima corner (the Left section) builds more
-quickly than it fades.  This is presumably becuase as the cytoplasmic
-minD:ATP diffuses down a more accute corner, it is sourrounded by
-closer cell walls than it would be in a less acute corner, so that the
-it is more apt at any diffusive step to make contact and cluster on
-the walls.  That particular part of the process is therefore
-accelerated, driving the build up of the maxima forward.
+Still waiting for the triangle data to show what we expect.  We have
+small triangles that gradually go from no oscillations to
+oscillations, but the large triangle data does not yet show
+irregularities.  I have very large simulations running that should
+definitely show this at some point (Give it a few days).
 
-The right triangle shows a similar pattern except that here there is
-an assymetry between the two corners that maximize at roughly the same
-time.  One corner is further from the single maximizing corner and it
-consisitently peaks later.  The MinD simply have further to travel
-before they maximize there.
+%% \begin{figure}
+%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
+%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
+%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
+%%   \caption{Total protein fluctuation in the right, middle, and left
+%%     parts of an equilateral (top), iscoscolese (middle), and 3-4-5
+%%     (bottom) triangle.  The vertical axis shows stacked the total
+%%     number of proteins that are of four different compound stages and
+%%     in the different sections of the cell.}
+%%   \label{box-triangle}
+%% \end{figure}
 
-For these three sizess and shapes there is not sign that the
-oscillation patterns once they are set will break down.
+%% The double pole oscillation pattern, in which one pole is located in a
+%% single corner of the triangle and the other pole is spread out between
+%% the opposite two, can be seen in Figure \ref{box-triangle}.  The
+%% equilateral triangle shows a spike in both the Center and Left
+%% sections at the same time, both showing the familiar sequence of peaks
+%% amoungst the different states of the protein seen in the poles of the
+%% pill shaped bacteria.  A spike in the other corner, showing the common
+%% sequence, occurs during the minima of the former two, wth a higher
+%% concentration at the peak.  A similar pattern is seen in the
+%% iscosolese triangular shape, where interestingly the onset of the
+%% maxima in the single maxima corner (the Left section) builds more
+%% quickly than it fades.  This is presumably becuase as the cytoplasmic
+%% minD:ATP diffuses down a more accute corner, it is sourrounded by
+%% closer cell walls than it would be in a less acute corner, so that the
+%% it is more apt at any diffusive step to make contact and cluster on
+%% the walls.  That particular part of the process is therefore
+%% accelerated, driving the build up of the maxima forward.
 
-\begin{figure}
-%%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
-  \caption{Total protein fluctuation of an equilateral triangle with
-    larger dimensions (each side is roughly $6\micron$.  The vertical
-    axis shows stacked the total number of proteins that are of four
-    different compound stages and in the different sections of the
-    cell. The time limits have been set to show the broken down
-    section of the simulation.}
-  \label{box-triangle}
+%% The right triangle shows a similar pattern except that here there is
+%% an assymetry between the two corners that maximize at roughly the same
+%% time.  One corner is further from the single maximizing corner and it
+%% consisitently peaks later.  The MinD simply have further to travel
+%% before they maximize there.
 
-The larger equilateral shape shows the same pattern as the smaller
-version does only until fifteen periods, at which point there is a
-breakdown of the oscillation pattern.  During the last three stable
-periods, the single maximizing corner, the lower left section in the
-figure, has a lower peak each period as the membrane bound MinD:ATP in
-the other corners lag more and more before being eaten away by the
-MinE.  Finally these maxima lag so much that they break down the
-regular pattern.  There then occurs about five periods of semi chaotic
-behavoir, until it settles back into another stable oscillation that
-is similar to the original one, except that a different corner has
-been chosen to be the singlular maxima (the right section in the
-figure), while the other two corners maximize at the same time.  This
-interesting breakdown and recovery shows both the robustness of the
-double pole oscilatory tendency and the importance of required
-distance of travel for the different proteins.
+%% For these three sizess and shapes there is not sign that the
+%% oscillation patterns once they are set will break down.
 
-\end{figure}
+%% \begin{figure}
+%% %%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
+%%   \caption{Total protein fluctuation of an equilateral triangle with
+%%     larger dimensions (each side is roughly $6\micron$.  The vertical
+%%     axis shows stacked the total number of proteins that are of four
+%%     different compound stages and in the different sections of the
+%%     cell. The time limits have been set to show the broken down
+%%     section of the simulation.}
+%%   \label{box-triangle}
+%% \end{figure}
 
-\subsubsection{Randst-99 our lambda shape}
+%% The larger equilateral shape shows the same pattern as the smaller
+%% version does only until fifteen periods, at which point there is a
+%% breakdown of the oscillation pattern.  During the last three stable
+%% periods, the single maximizing corner, the lower left section in the
+%% figure, has a lower peak each period as the membrane bound MinD:ATP in
+%% the other corners lag more and more before being eaten away by the
+%% MinE.  Finally these maxima lag so much that they break down the
+%% regular pattern.  There then occurs about five periods of semi chaotic
+%% behavoir, until it settles back into another stable oscillation that
+%% is similar to the original one, except that a different corner has
+%% been chosen to be the singlular maxima (the right section in the
+%% figure), while the other two corners maximize at the same time.  This
+%% interesting breakdown and recovery shows both the robustness of the
+%% double pole oscilatory tendency and the importance of required
+%% distance of travel for the different proteins.
+
+\section{Our 'V' Shaped Cells}
 \begin{figure}

### 2014-02-10 paper/paper.tex
put combo plot (not yet fixed up) into paper Tested everything on bennet.
added lower threshhold for mannik shape to paper Tested everything on node08.

@@
 widths of our simulated flattened cells, the steady, two pole
-oscillations seem to break down when the the shortest distance across
-the cell is approximately equal to the characteristic half wavelength
-at the particular thickness at which we simulate (our simulations of
+oscillations seem to break down when the shortest distance across the
+cell is approximately equal to the characteristic half wavelength at
+the particular thickness at which we simulate (our simulations of
 cells with thickness $0.25\mu m$ corresponds to half wavelengths of
 $2.13\mu m$).  Huang~\cite{huang2003dynamic} performs a similar
-analysis for a cylindrical shape and finds characteristic half
-wavelengths of $2\mu m$.
+analysis for a cylindrical shape \fixme{is it cylindrical or 1d?} and
+finds characteristic half wavelengths of $2\mu m$.
 
@@
 equal to the analysis' half wavelength found for this cell thickness.
+
+\begin{figure}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
+  \includegraphics[width=3cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
+  \caption{Box plots of Mannik shapes for sizes at the lower stability
+    threshhold.  Both shapes have longer axis of roughly 2.2$\mu m$.}
+  \label{box-mannik}
+\end{figure}
+Decreasing the cell size in succesive steps, we can see as well the
+critical size at which the cell oscillations are quickly damped out.
+Figure~\ref{box-mannik} shows box plots of the largest cells simulated
+whose oscilltions relax into the steady state solution.  Both have a
+long axis of roughly 2.2$\mu m$, in agreement with theory.
 
@@
 Looking at at few periods in detail.  We find that there is a small
-increase in cytoplasmic MinE always directly before the the beggining
+increase in cytoplasmic MinE always directly before the beggining
 of climb in the membrane bound MinE peak.  Also, there is at any one

### 2014-02-10 paper/paper.tex
added a few figures to paper Tested everything on node23.

@@
 \begin{figure}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
+  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
+  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
   \caption{Box plots of Mannik shapes for sizes at the lower stability
-    threshhold.  Both shapes have longer axis of roughly 2.2$\mu m$.}
+    threshhold.  The vertical axis shows stacked and changing over
+    time the total number of proteins that are of four different
+    compound stages and in the different sections of the cell.  Both
+    shapes have longer axis of roughly 2.2$\mu m$.}
   \label{box-mannik}
@@
 
-\fixme{I'm also waiting for data to come in that will hopefully show
-  cells so small that no oscillations take place.  We can put this in
-  as well}
-
 \section{Triangular Shapes}
@@
 definitely show this at some point (Give it a few days).
+
+\begin{figure}
+  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
+  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
+  \caption{Box plots of triangle shapes for sizes at the lower stability
+    threshhold.  The vertical axis shows stacked and changing over
+    time the total number of proteins that are of four different
+    compound stages and in the different sections of the cell.}
+  \label{box-triangle}
+\end{figure}
 

### 2014-02-21 paper/paper.tex
wrote mannik/stability and triangle sections, added all the relevent data for these sections into the figures of the paper, added all the V shape box data in figures to paper and arrow data to data directory Tested everything on node25.

@@
 above results in extremely robust oscillatory behavoir of polar
-selection and oscillation in a wide variety of cell shapes.  However
-we have found that this robustness is heavily dependent upon cell
-size.  Two pole, regular oscillatory behavoir is found in cells which
-are long enough in one dimension for the reaction chain to be unstable
-but short enough in the perpendicular dimension to be stable.  The
-limits are seen when both dimensions are too short to be unstable, so
-that initial assymetry in protein concentration relaxes into a
-motionless steady state, or when both are too great, so that the
-proteins exhibit much more complex and varied behavoir.
+selection and oscillation in a wide variety of cell shapes.  We have
+also found that while all sizes of cell will in time settle into
+regular oscillations, there are size dependent distinctions in the
+number and placement of the spatial positions of maximization.
+Regular oscillatory behavoir between two poles at opposite ends of the
+longer cellular direction is found in cells which are long enough in
+one dimension for the reaction chain to be unstable but short enough
+in the perpendicular dimension to be stable.  The limits are seen when
+both dimensions are too short to be unstable, so that initial
+assymetry in protein concentration relaxes into a motionless steady
+state (see Figure~\ref{box-mannik}, or when both are too great, so
+that the proteins exhibit more than two poles and those at extreme
+postitions in both dimensions.
 
@@
 analysis of the five differential equations in an infinite slab that
-shows a characteristic half wavelength in perturbative spatial
+show a characteristic half wavelength in perturbative spatial
 oscillations at which the system becomes unstable.  This length is
@@
 Figure~\ref{fig:stability-analysis}.  When increasing the lengths and
-widths of our simulated flattened cells, the steady, two pole
-oscillations seem to break down when the shortest distance across the
-cell is approximately equal to the characteristic half wavelength at
-the particular thickness at which we simulate (our simulations of
-cells with thickness $0.25\mu m$ corresponds to half wavelengths of
-$2.13\mu m$).  Huang~\cite{huang2003dynamic} performs a similar
-analysis for a cylindrical shape \fixme{is it cylindrical or 1d?} and
-finds characteristic half wavelengths of $2\mu m$.
+widths of our simulated flattened cells, the cells stop exhibiting two
+pole oscillalitory behavior and instead exhibit multiple
+positions of maximization when the shortest distance across the cell
+is approximately equal to the characteristic half wavelength at the
+particular thickness at which we simulate (our simulations of cells
+with thickness $0.25\mu m$ corresponds to half wavelengths of $2.13\mu
+m$).  Huang~\cite{huang2003dynamic} performs a similar analysis for a
+cylindrical shape \fixme{is it cylindrical or 1d?} and finds
+characteristic half wavelengths of $2\mu m$.
+
+\begin{figure}
+  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
+  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
+  \caption{Box plots of Mannik shapes for sizes at the lower stability
+    threshhold.  The vertical axis shows stacked and changing over
+    time the total number of proteins that are of four different
+    compound stages and in the different sections of the cell.  Both
+    shapes have longer axis of roughly 2.2$\mu m$.}
+  \label{box-mannik}
+\end{figure}
+
+Decreasing the cell size in succesive steps, we can see the critical
+size at which the cell oscillations are quickly damped out.
+Figure~\ref{box-mannik} shows box plots of the largest cells simulated
+whose oscillations relax into the steady state solution.  Both have a
+long axis of roughly 2.2$\mu m$, in agreement with theory.
 
@@
   \includegraphics[width=2.8cm]{../mannik-1.png}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1300-2000-9400-1500.pdf}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1100-1100-9500-1500.pdf}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1800-2500-9400-1500.pdf}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-1800-1800-9500-1500.pdf}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-2300-3300-9400-1500.pdf}
-  \includegraphics[width=3cm]{../data/shape-randst/plots/arrow-plot-NflD-randst-25-2800-2800-9500-1500.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/paper-arrow-plot}
   \caption{Arrow plots for our simulation and mannik's experimental}
@@
 prefered pole locations and to oscillate maxima back and forth very
-steadily between them.  However, when we keep the same shape but
-increase the size, we see that there is a critical size at which the
-protein dynamics lose their order and become very complex (showing
-hints of prefered wall maxima locations), similar to what Mannik sees
-experimentally.  We find that this critical size matches up well with
-our stability analysis, in that the critical sizes correspond to sizes
-for which the shorter of the two distances across the cell is roughly
-equal to the analysis' half wavelength found for this cell thickness.
-
-\begin{figure}
-  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
-  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
-  \caption{Box plots of Mannik shapes for sizes at the lower stability
-    threshhold.  The vertical axis shows stacked and changing over
-    time the total number of proteins that are of four different
-    compound stages and in the different sections of the cell.  Both
-    shapes have longer axis of roughly 2.2$\mu m$.}
-  \label{box-mannik}
-\end{figure}
-Decreasing the cell size in succesive steps, we can see as well the
-critical size at which the cell oscillations are quickly damped out.
-Figure~\ref{box-mannik} shows box plots of the largest cells simulated
-whose oscilltions relax into the steady state solution.  Both have a
-long axis of roughly 2.2$\mu m$, in agreement with theory.
+steadily between them.  When we increase the size of our cells, we
+indeed see multiple positions of maxima develop, but we never observe
+the random behavoir that they have observed experimentally.  This is
+perhaps due to the exact, continuous method we use when conducting
+simulations.  Stochastic methods would perhaps show more random
+behavoir at these sizes.  We consider this to be a limitation of the
+exact solution method.
 
 \section{Triangular Shapes}
-
-Still waiting for the triangle data to show what we expect.  We have
-small triangles that gradually go from no oscillations to
-oscillations, but the large triangle data does not yet show
-irregularities.  I have very large simulations running that should
-definitely show this at some point (Give it a few days).
 
@@
   \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
-  \caption{Box plots of triangle shapes for sizes at the lower stability
-    threshhold.  The vertical axis shows stacked and changing over
-    time the total number of proteins that are of four different
-    compound stages and in the different sections of the cell.}
+  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
+  \caption{Two box plots of triangle shapes.  The two smaller show
+    sizes at the lower stability threshhold, one just below, one just
+    above.  The larger triangle is the largest simulated. The vertical
+    axis shows stacked and changing over time the total number of
+    proteins that are of four different compound stages and in the
+    different sections of the cell.}
   \label{box-triangle}
@@
 
-%% \begin{figure}
-%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-400-400-400-1500}
-%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-500-300-500-1500}
-%%   %%\includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-480-360-1500}
-%%   \caption{Total protein fluctuation in the right, middle, and left
-%%     parts of an equilateral (top), iscoscolese (middle), and 3-4-5
-%%     (bottom) triangle.  The vertical axis shows stacked the total
-%%     number of proteins that are of four different compound stages and
-%%     in the different sections of the cell.}
-%%   \label{box-triangle}
-%% \end{figure}
+Along with our other shapes we have chosen to simulate both
+equilateral and iscoscolese triangular pancake shapes, since these
+offer in a way the simplest shapes that are geometrically more
+complicated than our pill shapes.
+
+Both triangle types show a similar oscillation pattern.  The
+iscosolese exhibit regular oscillations characterized by one distinct
+pole in the more accute angle of the three, and another 'pole' along
+the opposite wall, peaking in the two more obtuse angles at the same
+time.  The equilateral triangles settle very quickly into the same
+pattern, where the choice of which is one pole corner is dependent
+upon initial conditions.  As with the Mannik simulated shapes, there
+is a critical small size below which the oscillations dampen out and
+will not achieve a regular pattern.  Figure~\ref{box-triangle} shows
+three plots of equilateral triangles.  The two smaller show the
+largest that showed damped out behavoir and the smallest that
+developed regular oscillations.  The larger shows the largest traingle
+that we simulated, showing that at even very large sizes the behavoir
+is consistent and stable.  Above the small size threshold, all
+simulated triangles show regular patterns for as long as simulated
+(roughly 800 seconds).
 
@@
 \begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-500-500-9900-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
-  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}arrow-plot-NflD-randst-25-600-800-9800-1500.pdf
-
-  \caption{Total protein fluctuation in the A shaped shape.  The vertical axis shows stacked the total number
-    of proteins that are of four different compound stages and in the
-    different sections of the cell.}
-  \label{total-oscillation-randst-96-plot}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1500-1500-9900-1500}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1600-1600-9900-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1800-1800-9900-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-2000-2000-9900-1500}
 \end{figure}
@@
 
-\subsubsection{Randst-97-}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-600-9700-1500}
-  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
-  \caption{Total protein fluctuation in the sideways flying saucer
-    pancake cell shape.  The vertical axis shows stacked the total
-    number of proteins that are of four different compound stages and
-    in the different sections of the cell.}
-  \label{box-97}
-\end{figure}
+%% \subsubsection{Randst-97-}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-600-9700-1500}
+%%   %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+%%   \caption{Total protein fluctuation in the sideways flying saucer
+%%     pancake cell shape.  The vertical axis shows stacked the total
+%%     number of proteins that are of four different compound stages and
+%%     in the different sections of the cell.}
+%%   \label{box-97}
+%% \end{figure}
 
-Early on in its simulation the sideways flying saucer pancake shape
-shows a clear breakdown of an unstable equilibrium oscillation.  We
-have set the intial conditions so that MinD density is highly
-concentrated to the left of a dividing line that runs parrallel to the
-left vertical side.  For the first number of oscillations the maxima
-trade off right to left, from a high peak in the rightward middle
-compartment to vertically opposed peaks in the poles of the long axis
-of the cell.  This is seen in the first part of Figure~\ref{box-97},
-where the lower and upper sections peak in unison, and the middle
-right section peaks $\pi$ radians removed from these.  After a few
-oscillations the back and forth oscillations tip toward the vertical
-direction and the system loses its initial oscillation pattern.  It
-falls quickly instead into a back and forth pattern between the two
-opposing endcaps.  The oscillation at this point is reminiscent of the
-pills shape oscillation, once again showing the robust nature of the
-back and forth, two pole pattern.
+%% Early on in its simulation the sideways flying saucer pancake shape
+%% shows a clear breakdown of an unstable equilibrium oscillation.  We
+%% have set the intial conditions so that MinD density is highly
+%% concentrated to the left of a dividing line that runs parrallel to the
+%% left vertical side.  For the first number of oscillations the maxima
+%% trade off right to left, from a high peak in the rightward middle
+%% compartment to vertically opposed peaks in the poles of the long axis
+%% of the cell.  This is seen in the first part of Figure~\ref{box-97},
+%% where the lower and upper sections peak in unison, and the middle
+%% right section peaks $\pi$ radians removed from these.  After a few
+%% oscillations the back and forth oscillations tip toward the vertical
+%% direction and the system loses its initial oscillation pattern.  It
+%% falls quickly instead into a back and forth pattern between the two
+%% opposing endcaps.  The oscillation at this point is reminiscent of the
+%% pills shape oscillation, once again showing the robust nature of the
+%% back and forth, two pole pattern.
 
-During each period, directly after one of the polar maxima has
-subsided, there is a small spike with the regular maxima pattern (a
-spike in membrane bound MinD:ATP immediately followed by a spike in
-membrane bound MinD:MinE:ATP) seen in the small middle right
-compartment section.  The animations show that the MinD, oscillating
-back and forth between the upper and lower poles, seems to catch and
-lag in the indentation for a bit before moving on.  Once again the
-positive radius of curvature acts as an attractive place for MinD to
-cluster on the walls, and it is not released to move on through the
-cytoplasm again until MinE has formed its ring and completely reacted
-it away.
+%% During each period, directly after one of the polar maxima has
+%% subsided, there is a small spike with the regular maxima pattern (a
+%% spike in membrane bound MinD:ATP immediately followed by a spike in
+%% membrane bound MinD:MinE:ATP) seen in the small middle right
+%% compartment section.  The animations show that the MinD, oscillating
+%% back and forth between the upper and lower poles, seems to catch and
+%% lag in the indentation for a bit before moving on.  Once again the
+%% positive radius of curvature acts as an attractive place for MinD to
+%% cluster on the walls, and it is not released to move on through the
+%% cytoplasm again until MinE has formed its ring and completely reacted
+%% it away.
 
-\subsubsection{Randst-96-Star}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-700-700-9600-1500}
-  %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
-  \caption{Total protein fluctuation in the star cell shape.  The vertical axis shows stacked the total
-    number of proteins that are of four different compound stages and
-    in the different sections of the cell.}
-  \label{box-96}
-\end{figure}
+%% \subsubsection{Randst-96-Star}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-700-700-9600-1500}
+%%   %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
+%%   \caption{Total protein fluctuation in the star cell shape.  The vertical axis shows stacked the total
+%%     number of proteins that are of four different compound stages and
+%%     in the different sections of the cell.}
+%%   \label{box-96}
+%% \end{figure}
 
-This clover shape finds a regular oscillatory behavoir after about
-seven periods that consists of two maxima that peak regularly in the
-corners accross from each other at the same times (Figure
-\ref{box-96}) and then again opposing maxima that peak at the same
-time in the other two corners.\fixme{should try some different
-  starting conditions with this to see if there's another patter.}
+%% This clover shape finds a regular oscillatory behavoir after about
+%% seven periods that consists of two maxima that peak regularly in the
+%% corners accross from each other at the same times (Figure
+%% \ref{box-96}) and then again opposing maxima that peak at the same
+%% time in the other two corners.\fixme{should try some different
+%%   starting conditions with this to see if there's another patter.}
 
-Looking at at few periods in detail.  We find that there is a small
-increase in cytoplasmic MinE always directly before the beggining
-of climb in the membrane bound MinE peak.  Also, there is at any one
-time a very large amount more of minE that is membrane bound then
-cytoplasmic in any ones section.  A difference of a factor of roughly
-20 when membrane MinE is at its peak, and roughly 12 when membrane
-MinE is at it's minimum.  There seem to be two modes of oscillation,
-each exhibiting a density peak maxima that moves back and forth
-diagonaly from one corner to the opposite, as if there were two
-overlapping, criss-crossed cells oscillating.  In the box plot this is
-seen as roughly coinciding membrane minD peaks in the lower left and
-right corners, followed one pi later in peaks in the upper right and
-upper left corners.  Interesting that this did not exhibit
-counterclockwise motion that Huangs 2008 paper might suggest.  Should
-run sims that start in the wacky way that just started running with
-triangles.
-\newline
+%% Looking at at few periods in detail.  We find that there is a small
+%% increase in cytoplasmic MinE always directly before the beggining
+%% of climb in the membrane bound MinE peak.  Also, there is at any one
+%% time a very large amount more of minE that is membrane bound then
+%% cytoplasmic in any ones section.  A difference of a factor of roughly
+%% 20 when membrane MinE is at its peak, and roughly 12 when membrane
+%% MinE is at it's minimum.  There seem to be two modes of oscillation,
+%% each exhibiting a density peak maxima that moves back and forth
+%% diagonaly from one corner to the opposite, as if there were two
+%% overlapping, criss-crossed cells oscillating.  In the box plot this is
+%% seen as roughly coinciding membrane minD peaks in the lower left and
+%% right corners, followed one pi later in peaks in the upper right and
+%% upper left corners.  Interesting that this did not exhibit
+%% counterclockwise motion that Huangs 2008 paper might suggest.  Should
+%% run sims that start in the wacky way that just started running with
+%% triangles.
+%% \newline
 
-We haven't simulated long enough yet, so no real pattern has shown
-itself.  There's certainly oscillations, and it's almost as if there's
-competing modes - top to bottom, left to right, corner to corner, etc.
-Interesting.
+%% We haven't simulated long enough yet, so no real pattern has shown
+%% itself.  There's certainly oscillations, and it's almost as if there's
+%% competing modes - top to bottom, left to right, corner to corner, etc.
+%% Interesting.
 
-\fixme{maybe?}The animations seem to relax into a pattern in which the oscillations
-go from the smallest corner, out to the other three, and then back to
-the smallest corner?  \fixme{There isn't enough data to see properly
-  though, need to run for longer.}
+%% \fixme{maybe?}The animations seem to relax into a pattern in which the oscillations
+%% go from the smallest corner, out to the other three, and then back to
+%% the smallest corner?  \fixme{There isn't enough data to see properly
+%%   though, need to run for longer.}
 

### 2014-02-21 paper/arrow-plot.py

@@ -15,12 +15,10 @@ dx=0.05
 #data.  For the 95 shape, the 11.00 11.00 data is real Mannik size and
 #for the 94.00 the 13.00 20.00 data is real Mannik size
 
-# arg_set = ["randst-0.25-11.00-11.00-95.00-15.00","randst-0.25-20.00-20.00-95.00-15.00",
-#            "randst-0.25-21.00-21.00-95.00-15.00","randst-0.25-28.00-28.00-95.00-15.00"]
-
-arg_set = ["randst-0.25-13.00-20.00-94.00-15.00","randst-0.25-15.00-22.00-94.00-15.00",
-           "randst-0.25-16.00-23.00-94.00-15.00","randst-0.25-18.00-25.00-94.00-15.00",
-           "randst-0.25-30.00-40.00-94.00-15.00"]
+arg_set = ["randst-0.25-11.00-11.00-95.00-15.00","randst-0.25-20.00-20.00-95.00-15.00",
+           "randst-0.25-21.00-21.00-95.00-15.00","randst-0.25-28.00-28.00-95.00-15.00",
+           "randst-0.25-13.00-20.00-94.00-15.00","randst-0.25-18.00-25.00-94.00-15.00",
+           "randst-0.25-23.00-33.00-94.00-15.00","randst-0.25-30.00-40.00-94.00-15.00"]
 
 plt.figure()
 
@@ -56,9 +54,22 @@ for i in range(len(arg_set)):
     if len(tails)==0:
         print "The tails in this file has no tails!!"
         exit(1)
+    print tails
+    for k in range(len(tails[:,0])-1,0,-1):
+        if tails[k,3] <0:
+            tails = np.delete(tails,k,0)
+            print k
+        else:
+            print tails[k,3]
+        if tails[k,2] < tails[k-1,2]+3:
+            if tails[k,3] > tails[k-1,3]:
+                tails = np.delete(tails,k-1,0)
+            else:
+                tails = np.delete(tails,k,0)
+    print tails
     tails = tails*dx
-    tails = tails[1:,:] # cut out just the first arrow
-    ax = plt.subplot(2,3,i)
+    tails = tails[22:,:] # cut out just the first arrow
+    ax = plt.subplot(2,4,i)
     ax.set_aspect('equal', 'datalim')
     font=FontProperties()
     font.set_family('serif')

### 2014-02-24 paper/paper.tex
updated box plots to have two periods and paper and jobs for faster make Tested everything on node23.

@@
   \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
-  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
+  %\includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
   \caption{Two box plots of triangle shapes.  The two smaller show
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-500-500-9900-1500}
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
-\end{figure}
-
-\begin{figure}
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
 \end{figure}
 \begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1500-1500-9900-1500}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1600-1600-9900-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1800-1800-9900-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-2000-2000-9900-1500}
 \end{figure}

### 2014-02-24 pyplots/box_plot.py

@@ -173,10 +173,21 @@ def main():
     start_time_as_frac_of_ten = float(load.f_param6)
     end_time_as_frac_of_ten = float(load.f_param7)
     tot_time = len(plotCurveList_D[0])*box_time_step
-    start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
-    end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
-    (start, end) = find_period(plotCurveList_D[len(plotCurveList_D)-2])
+    # start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
+    # end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
+    # (start, end) = find_period(plotCurveList_D[len(plotCurveList_D)-2])
     (start, end) = find_period(np.array(returnData(boxList[len(boxList)-1], 'D_ND')))
+    start = end - 2*(end-start)
+    end = int(tot_time/box_time_step)
+    if (load.f_shape == 'triangle') or (load.f_param4 == '95.00') or (load.f_param4 == '94.00'):
+        start = 0
+        end = int(tot_time*.5/box_time_step)
+
+    periods_file = open('periods.txt','a')
+    periods_file.write('Box period= '+str(box_time_step*(end-start)) +' for simulation '+load.f_shape+
+                       ' '+load.f_param1+' '+load.f_param2+' '+load.f_param3+' '+load.f_param4+' '+
+                       load.f_param5+', with start = '+str(start*box_time_step)+' and end = '+str(end*box_time_step)+'\n')
+    periods_file.close()
 
     # print useful coordination data
     period = timeAxis[end-1] - timeAxis[start]

### 2014-02-25 paper/arrow-plot.py
work on nice mannik plot (needs more work) plus tune colors on boxplot Tested everything on bennet.

@@ -7,6 +7,8 @@ import matplotlib.pyplot as plt
 import numpy as np
 from matplotlib.font_manager import FontProperties
 
+import matplotlib.image as mpimg
+
 #membrane.dat or arrow.dat printed transposed, gotta align them:
 
 dx=0.05
@@ -21,6 +23,31 @@ arg_set = ["randst-0.25-11.00-11.00-95.00-15.00","randst-0.25-20.00-20.00-95.00-
            "randst-0.25-23.00-33.00-94.00-15.00"]#"randst-0.25-30.00-40.00-94.00-15.00"]
 
 plt.figure()
+fig, ax = plt.subplots(figsize=(5,6))
+
+ax.set_frame_on(False)
+ax.get_xaxis().set_visible(False)
+ax.get_yaxis().set_visible(False)
+def plot_mannik():
+    m1=mpimg.imread('mannik-one.png')
+    m2=mpimg.imread('mannik-two.png')
+
+    dx = 7.0/380
+    y1 = -dx*np.arange(0, m1.shape[0])
+    x1 = dx*np.arange(0, m1.shape[1])
+    x1, y1 = np.meshgrid(x1, y1)
+    xcenter = x1[m1[:,:,0] > 0].mean()
+    yoff = 1.7
+    plt.contourf(x1-xcenter, y1-yoff, m1[:,:,1], levels=[0, 0.9], colors=('r', 'w'))
+    plt.contourf(x1-xcenter, y1-yoff, m1[:,:,0], levels=[0, 0.9], colors=('k', 'w'))
+
+    y2 = -dx*np.arange(0, m2.shape[0])
+    x2 = dx*np.arange(0, m2.shape[1])
+    x2, y2 = np.meshgrid(x2, y2)
+    xcenter = x2[m2[:,:,0] > 0].mean()
+    plt.contourf(8+x2-xcenter, y2-yoff, m2[:,:,1], levels=[0, 0.9], colors=('r', 'w'))
+    plt.contourf(8+x2-xcenter, y2-yoff, m2[:,:,0], levels=[0, 0.9], colors=('k', 'w'))
+plot_mannik()
 
 for i in range(len(arg_set)):
     cell_membrane_initial = np.loadtxt("./data/shape-randst/membrane_files/sections-%s.dat" % arg_set[i])
@@ -54,22 +81,25 @@ for i in range(len(arg_set)):
     if len(tails)==0:
         print "The tails in this file has no tails!!"
         exit(1)
[…]

### 2014-02-25 paper/paper.tex
work on nice mannik plot (needs more work) plus tune colors on boxplot Tested everything on bennet.
wrote some of the > shape, am debating about putting in the more complex analysis Tested everything on node23.

@@
 Along with our other shapes we have chosen to simulate both
-equilateral and iscoscolese triangular pancake shapes, since these
+equilateral and iscoscolese triangular flattened shapes, since these
 offer in a way the simplest shapes that are geometrically more
-complicated than our pill shapes.
+complicated than our pills.
 
@@
 will not achieve a regular pattern.  Figure~\ref{box-triangle} shows
-three plots of equilateral triangles.  The two smaller show the
+two plots of equilateral triangles.  The two smaller show the
 largest that showed damped out behavoir and the smallest that
@@
 
-\section{Our 'V' Shaped Cells}
+\section{Our '\textgreater' Shaped Cells}
 \begin{figure}
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
+  \label{>-box}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
+  \label{>-box2}
 \end{figure}
 
-Our animations for this cell shape show a very interesting pattern.
-The maxima oscillates from the right corner to the top corner, then
-\emph{back to the right corner} then to the top corner again, then to
-the left corner, then back to the top, then to the left, then to the
-top again, then back to the right side.
+We have simulated a flattened '>' shape that shows an interesting size
+dependent pattern (seen in Figures~\ref{>-box}~and~\ref{>-box2}).
+When the shape is small enough that the distance from the apex tip to
+the opposite curve is less than our stability limit, a simple, two
+pole oscillation pattern develops and is sustained (where the two
+poles are on opposite leftward corners of the cell).  When the cell is
+increased in size, so that this distance measures approximately equal
+to our stability value, the cell develops a double oscillation in
+time, where the maxima oscillates from the lower corner to the
+rightward apex, then \emph{back to the lower corner} then to the apex
+again, then to the upper corner, then back to the apex, then to the
+upper corner, then to the apex again, then back to the lower corner,
+and continues this pattern indefinately.  Figure~\ref{>-box} shows the
+smaller size, which oscillates simply, and an intermediate size, which
+shows a pattern for which one out of three spikes in the regular
+oscillation is less significant.  This second pattern seems to be a
+precursor to the double oscillation seen in Figure~\ref{>-box2}.  The
+second plot shown in Figure~\ref{>-box2} shows a slighlty larger cell,
+for which the distance measured is larger than our stability limit
+distance.  This shows a very random pattern.
 
@@
 maximizes twice in the left corner, but during the MinD's first maxima
-in the left corner, the MinD has a maxima in the upper corner, and
+in the left corner, the MinE has a maxima in the upper corner, and
 during the MinD's second left maxima, the MinE travels to the right

### 2014-02-26 paper/paper.tex
wrote the > shape section and updated one of the data files for it Tested everything on node22.

@@
 \begin{figure}
-  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
-  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
+%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
+%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
   \caption{Box plots of Mannik shapes for sizes at the lower stability
@@
 \begin{figure}
-  \includegraphics[width=2.8cm]{../mannik-2.png}
-  \includegraphics[width=2.8cm]{../mannik-1.png}
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/paper-arrow-plot}
@@
 \begin{figure}
-  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
-  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
+%  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
+%  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
   %\includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
@@
 
-%% The double pole oscillation pattern, in which one pole is located in a
-%% single corner of the triangle and the other pole is spread out between
-%% the opposite two, can be seen in Figure \ref{box-triangle}.  The
-%% equilateral triangle shows a spike in both the Center and Left
-%% sections at the same time, both showing the familiar sequence of peaks
-%% amoungst the different states of the protein seen in the poles of the
-%% pill shaped bacteria.  A spike in the other corner, showing the common
-%% sequence, occurs during the minima of the former two, wth a higher
-%% concentration at the peak.  A similar pattern is seen in the
-%% iscosolese triangular shape, where interestingly the onset of the
-%% maxima in the single maxima corner (the Left section) builds more
-%% quickly than it fades.  This is presumably becuase as the cytoplasmic
-%% minD:ATP diffuses down a more accute corner, it is sourrounded by
-%% closer cell walls than it would be in a less acute corner, so that the
-%% it is more apt at any diffusive step to make contact and cluster on
-%% the walls.  That particular part of the process is therefore
-%% accelerated, driving the build up of the maxima forward.
-
-%% The right triangle shows a similar pattern except that here there is
-%% an assymetry between the two corners that maximize at roughly the same
-%% time.  One corner is further from the single maximizing corner and it
-%% consisitently peaks later.  The MinD simply have further to travel
-%% before they maximize there.
-
-%% For these three sizess and shapes there is not sign that the
-%% oscillation patterns once they are set will break down.
-
-%% \begin{figure}
-%% %%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
-%%   \caption{Total protein fluctuation of an equilateral triangle with
-%%     larger dimensions (each side is roughly $6\micron$.  The vertical
-%%     axis shows stacked the total number of proteins that are of four
-%%     different compound stages and in the different sections of the
-%%     cell. The time limits have been set to show the broken down
-%%     section of the simulation.}
-%%   \label{box-triangle}
-%% \end{figure}
-
-%% The larger equilateral shape shows the same pattern as the smaller
-%% version does only until fifteen periods, at which point there is a
-%% breakdown of the oscillation pattern.  During the last three stable
-%% periods, the single maximizing corner, the lower left section in the
-%% figure, has a lower peak each period as the membrane bound MinD:ATP in
-%% the other corners lag more and more before being eaten away by the
-%% MinE.  Finally these maxima lag so much that they break down the
-%% regular pattern.  There then occurs about five periods of semi chaotic
-%% behavoir, until it settles back into another stable oscillation that
-%% is similar to the original one, except that a different corner has
-%% been chosen to be the singlular maxima (the right section in the
-%% figure), while the other two corners maximize at the same time.  This
-%% interesting breakdown and recovery shows both the robustness of the
-%% double pole oscilatory tendency and the importance of required
-%% distance of travel for the different proteins.
-
 \section{Our '\textgreater' Shaped Cells}
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
-  \label{>-box}
+  \label{Vbox}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
-  \label{>-box2}
+  \label{Vbox2}
 \end{figure}
 
-We have simulated a flattened '>' shape that shows an interesting size
-dependent pattern (seen in Figures~\ref{>-box}~and~\ref{>-box2}).
-When the shape is small enough that the distance from the apex tip to
-the opposite curve is less than our stability limit, a simple, two
-pole oscillation pattern develops and is sustained (where the two
-poles are on opposite leftward corners of the cell).  When the cell is
-increased in size, so that this distance measures approximately equal
-to our stability value, the cell develops a double oscillation in
-time, where the maxima oscillates from the lower corner to the
-rightward apex, then \emph{back to the lower corner} then to the apex
-again, then to the upper corner, then back to the apex, then to the
-upper corner, then to the apex again, then back to the lower corner,
-and continues this pattern indefinately.  Figure~\ref{>-box} shows the
-smaller size, which oscillates simply, and an intermediate size, which
-shows a pattern for which one out of three spikes in the regular
-oscillation is less significant.  This second pattern seems to be a
-precursor to the double oscillation seen in Figure~\ref{>-box2}.  The
-second plot shown in Figure~\ref{>-box2} shows a slighlty larger cell,
-for which the distance measured is larger than our stability limit
-distance.  This shows a very random pattern.
+We have also simulated a flattened '\textgreater' shape that shows an
+interesting size dependent pattern (seen in
+Figures~\ref{Vbox}~and~\ref{Vbox2}).  When the shape is small enough
+that the distance from the apex tip to the opposite curve is less than
+our stability limit, a simple, two pole oscillation pattern develops
+and is sustained (where the two poles are on opposite leftward corners
+of the cell).  When the cell is increased in size so that this
+distance is approximately equal to our stability value, the cell
+develops a double oscillation in time, where the maxima oscillates
+from the lower corner to the rightward apex, then \emph{back to the
+  lower corner}, then to the apex again, then to the upper corner,
+then back to the apex, then to the upper corner, then to the apex
+again, then back to the lower corner, and continues this pattern
+indefinately.  Figure~\ref{Vbox} shows the smaller size, for which the
+protein oscillates simply, and an intermediate size, which shows a
+pattern for which one out of three spikes in the regular oscillation
+is less significant.  This second pattern seems to be a precursor to
+the double oscillation that seen in Figure~\ref{Vbox2}.  The second
+plot shown in Figure~\ref{Vbox2} shows a slightly larger cell for
+which the distance measured is larger than our stability limit
+distance.  This simulation shows a random pattern.
+
+A detailed analysis of a time series of protein contour plots shows
+that the importance of spatial dimensions is based on the ability of
+protein in different stages to diffuse neccesary distances before
+undergowing certain types of reactions.  The double oscillation
+pattern shows that every time the membrane bound MinD maximizes in the
+upper corner as opposed to the rightward apex, it does so because the
+MinE has not had enough time to diffuse to this upper corner, leaving
+a MinE free zone.  This particular pattern is specific to this shape
+and size, but in general its the restrictions set in place by the
+rates at which proteins diffuse and the distances they cover before
+reacting that dictate their oscillatory bahavoir.
+
+Simulations of this shape in which the two planar dimensions are large
+compared to those shown(roughly $9\micron$ across) show no stable
+regular periodic pattern. Animations show that the MinD acts as a sort
+of traveling cluster that is constantly being eaten away by MinE
+behind it.  When this cluster enters a region of high curvature that
+ends in a dead end corner it performs the polar maxima behavoir seen
+in the other simulations, regrouping out away from the corner where it
+travels in the opposite direction while being ``chased'' away by the
+MinE that itself is currently maximizing in the corner.  The maxima
+occur on non-polar walls often, and will often split into two roaming
+clusters.
+
+\section{Interpretation of Data}
+\section{Conclusion}
+\bibliography{paper}
+
+\end{document}
+
+\section*{Appendix}
+
+\section{Below are NOTES for the Writing}
+
+Figure \ref{total-oscillation-triangle-plot} shows the equivalent
+motion and transference between compound states for the triangular
+states as Figure \ref{total-oscillation-plot} does for the pill shaped
+cells.  The equilateral triangular shows that in all three sections
+there is a spike in wall attached MinD-ATP directly followed by a
+spike in wall attached MinD-MinE-ATP.  The pill had shown a similar
+pattern except that the mid section exhibited no such pronounced
+spike.  Interestingly, the right and mid sections show spikes at
+similar times when compared to the left section spikes, which seem to
+oscillate in a manner shifted pi off from the other two.  This
+behavoir shows itself in the animations, which show a relaxation into
+a stable oscillation from a maxima in one corner to a double maxima in
+the other two corners, and back again.  The left section heights are
+roughly twice that of the right section heights.  The simulations are
+started with higher concentrations of proteins in primarily the right
+section, with some overlap into the middle section, so that perhpas
+this oscillation pattern seems reasonable.  However, it's interesting
+to note that the oscillations, started with assymmetric density, do
+not naturally rotate around the corners of the triangle in a circular
+pattern.
+
+It seems as well that there is a desired oscillation maxima for the
+particular shape and size of the cell, as can be seen by the
+relaxation, over the first four periods, to a regular maximal height
+of the right and left sections' total protein at the height of each spike.
+
+\fixme{Note to make sure I'm interpreting the iscosolese triangle data
+  correctly: the triangle sides are 5,5,3, and the higher density
+  starts in the corner that is opposite the short side.  This corner
+  is covered by the right section.  I've verified this by looking at
+  the protein\_microscopy and drawing a little picture, which is on my
+  desk...if you dare look for something on my desk!!!}  The iscosolese
+triangle starts its simulation with a higher concentration of protein
+in the section that is opposite the shorter side.  It quickly relaxes
+into a stable oscillation pattern.  This pattern shows that right
+corner section regularly has higher spikes in total protein than the
+other sections, and that its spikes appear one pi removed from the
+spikes for the other two sections.  This a similar behavoir to that
+which is seen in the equilateral triangle, differening in that it
+converges more quickly towards this behavoir and that it shows a
+greater exageration in the height of protein buildup in the right most
+section.
+
+\fixme{Note on interpretation of 3-4-5 triangle: the higher density
+  starts to the right of a vertical line that is parrallel to the
+  second longest side in the triangle (the longer of the two
+  non-hypotonuse sides).  This means the higher concentration covers
+  the right angle and also the smaller angle in the triangle} The
+3-4-5 triangle exhibits behavoir that I need more data to properly
+observe.  I does not converge as quickly as that for the iscosolese or
+equilateral triangles.
+
+It seems that there is an approximate critical cell size for which the
+MinD will act in these ``wandering cluster'' formations.  The cell is
+large enough so that there is a loss of MinD correlation between the
+opposite sides (the protein in the right corner at any time is too far
+away from the left to immediately affect the protein there).
 
@@
 
-\section{Interpretation of Data}
-\section{Conclusion}
-\bibliography{paper}
+%% The double pole oscillation pattern, in which one pole is located in a
+%% single corner of the triangle and the other pole is spread out between
+%% the opposite two, can be seen in Figure \ref{box-triangle}.  The
+%% equilateral triangle shows a spike in both the Center and Left
+%% sections at the same time, both showing the familiar sequence of peaks
+%% amoungst the different states of the protein seen in the poles of the
+%% pill shaped bacteria.  A spike in the other corner, showing the common
+%% sequence, occurs during the minima of the former two, wth a higher
+%% concentration at the peak.  A similar pattern is seen in the
+%% iscosolese triangular shape, where interestingly the onset of the
+%% maxima in the single maxima corner (the Left section) builds more
+%% quickly than it fades.  This is presumably becuase as the cytoplasmic
+%% minD:ATP diffuses down a more accute corner, it is sourrounded by
+%% closer cell walls than it would be in a less acute corner, so that the
+%% it is more apt at any diffusive step to make contact and cluster on
+%% the walls.  That particular part of the process is therefore
+%% accelerated, driving the build up of the maxima forward.
+
+%% The right triangle shows a similar pattern except that here there is
+%% an assymetry between the two corners that maximize at roughly the same
+%% time.  One corner is further from the single maximizing corner and it
+%% consisitently peaks later.  The MinD simply have further to travel
+%% before they maximize there.
+
+%% For these three sizess and shapes there is not sign that the
+%% oscillation patterns once they are set will break down.
+
+%% \begin{figure}
+%% %%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
+%%   \caption{Total protein fluctuation of an equilateral triangle with
+%%     larger dimensions (each side is roughly $6\micron$.  The vertical
+%%     axis shows stacked the total number of proteins that are of four
+%%     different compound stages and in the different sections of the
+%%     cell. The time limits have been set to show the broken down
+%%     section of the simulation.}
+%%   \label{box-triangle}
+%% \end{figure}
+
+%% The larger equilateral shape shows the same pattern as the smaller
+%% version does only until fifteen periods, at which point there is a
+%% breakdown of the oscillation pattern.  During the last three stable
+%% periods, the single maximizing corner, the lower left section in the
+%% figure, has a lower peak each period as the membrane bound MinD:ATP in
+%% the other corners lag more and more before being eaten away by the
+%% MinE.  Finally these maxima lag so much that they break down the
+%% regular pattern.  There then occurs about five periods of semi chaotic
+%% behavoir, until it settles back into another stable oscillation that
+%% is similar to the original one, except that a different corner has
+%% been chosen to be the singlular maxima (the right section in the
+%% figure), while the other two corners maximize at the same time.  This
+%% interesting breakdown and recovery shows both the robustness of the
+%% double pole oscilatory tendency and the importance of required
+%% distance of travel for the different proteins.
 
 \end{document}
-
-\section*{Appendix}
-
-\section{Below are NOTES for the Writing}
-
-Figure \ref{total-oscillation-triangle-plot} shows the equivalent
-motion and transference between compound states for the triangular
-states as Figure \ref{total-oscillation-plot} does for the pill shaped
-cells.  The equilateral triangular shows that in all three sections
-there is a spike in wall attached MinD-ATP directly followed by a
-spike in wall attached MinD-MinE-ATP.  The pill had shown a similar
-pattern except that the mid section exhibited no such pronounced
-spike.  Interestingly, the right and mid sections show spikes at
-similar times when compared to the left section spikes, which seem to
-oscillate in a manner shifted pi off from the other two.  This
-behavoir shows itself in the animations, which show a relaxation into
-a stable oscillation from a maxima in one corner to a double maxima in
-the other two corners, and back again.  The left section heights are
-roughly twice that of the right section heights.  The simulations are
-started with higher concentrations of proteins in primarily the right
-section, with some overlap into the middle section, so that perhpas
-this oscillation pattern seems reasonable.  However, it's interesting
-to note that the oscillations, started with assymmetric density, do
-not naturally rotate around the corners of the triangle in a circular
-pattern.
-
-It seems as well that there is a desired oscillation maxima for the
-particular shape and size of the cell, as can be seen by the
-relaxation, over the first four periods, to a regular maximal height
-of the right and left sections' total protein at the height of each spike.
-
-\fixme{Note to make sure I'm interpreting the iscosolese triangle data
-  correctly: the triangle sides are 5,5,3, and the higher density
-  starts in the corner that is opposite the short side.  This corner
-  is covered by the right section.  I've verified this by looking at
-  the protein\_microscopy and drawing a little picture, which is on my
-  desk...if you dare look for something on my desk!!!}  The iscosolese
-triangle starts its simulation with a higher concentration of protein
-in the section that is opposite the shorter side.  It quickly relaxes
-into a stable oscillation pattern.  This pattern shows that right
-corner section regularly has higher spikes in total protein than the
-other sections, and that its spikes appear one pi removed from the
-spikes for the other two sections.  This a similar behavoir to that
-which is seen in the equilateral triangle, differening in that it
-converges more quickly towards this behavoir and that it shows a
-greater exageration in the height of protein buildup in the right most
-section.
-
-\fixme{Note on interpretation of 3-4-5 triangle: the higher density
-  starts to the right of a vertical line that is parrallel to the
-  second longest side in the triangle (the longer of the two
-  non-hypotonuse sides).  This means the higher concentration covers
-  the right angle and also the smaller angle in the triangle} The
-3-4-5 triangle exhibits behavoir that I need more data to properly
-observe.  I does not converge as quickly as that for the iscosolese or
-equilateral triangles.
-
-\end{document}

### 2014-03-03 paper/paper.tex
sketchy thoughts on paper-arrow plot Tested everything on bennet.

@@
 %  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
+  %\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
+  %\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
   \caption{Box plots of Mannik shapes for sizes at the lower stability
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
-  \label{Vbox}
+  \label{fig:Vbox}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
-  \label{Vbox2}
+  \label{fig:Vbox2}
 \end{figure}
@@
 interesting size dependent pattern (seen in
-Figures~\ref{Vbox}~and~\ref{Vbox2}).  When the shape is small enough
+Figures~\ref{fig:Vbox}~and~\ref{fig:Vbox2}).  When the shape is small enough
 that the distance from the apex tip to the opposite curve is less than
@@
 again, then back to the lower corner, and continues this pattern
-indefinately.  Figure~\ref{Vbox} shows the smaller size, for which the
+indefinately.  Figure~\ref{fig:Vbox} shows the smaller size, for which the
 protein oscillates simply, and an intermediate size, which shows a
@@
 is less significant.  This second pattern seems to be a precursor to
-the double oscillation that seen in Figure~\ref{Vbox2}.  The second
-plot shown in Figure~\ref{Vbox2} shows a slightly larger cell for
+the double oscillation that seen in Figure~\ref{fig:Vbox2}.  The second
+plot shown in Figure~\ref{fig:Vbox2} shows a slightly larger cell for
 which the distance measured is larger than our stability limit

### 2014-03-03 paper/arrow-plot.py

@@ -17,9 +17,9 @@ dx=0.05
 #data.  For the 95 shape, the 11.00 11.00 data is real Mannik size and
 #for the 94.00 the 13.00 20.00 data is real Mannik size
 
-arg_set = ["randst-0.25-18.50-18.50-95.00-15.00","randst-0.25-20.00-20.00-95.00-15.00",
-           "randst-0.25-21.00-21.00-95.00-15.00",#"randst-0.25-28.00-28.00-95.00-15.00",
-           "randst-0.25-18.50-28.00-94.00-15.00","randst-0.25-21.00-31.00-94.00-15.00",
+arg_set = ["randst-0.25-18.50-18.50-95.00-15.00",#"randst-0.25-20.00-20.00-95.00-15.00",
+           "randst-0.25-28.00-28.00-95.00-15.00",#"randst-0.25-28.00-28.00-95.00-15.00",
+           "randst-0.25-18.60-28.60-94.00-15.00",#"randst-0.25-21.00-31.00-94.00-15.00",
            "randst-0.25-23.00-33.00-94.00-15.00"]#"randst-0.25-30.00-40.00-94.00-15.00"]
 
 plt.figure()
@@ -37,14 +37,14 @@ def plot_mannik():
     x1 = dx*np.arange(0, m1.shape[1])
     x1, y1 = np.meshgrid(x1, y1)
     xcenter = x1[m1[:,:,0] > 0].mean()
-    y1off = 1.7#1.7 and there was only one yoff, not two
+    y1off = 1.7 # - 4#1.7 and there was only one yoff, not two
     plt.contourf(x1-xcenter, y1-y1off, m1[:,:,1], levels=[0, 0.9], colors=('r', 'w'))
     plt.contourf(x1-xcenter, y1-y1off, m1[:,:,0], levels=[0, 0.9], colors=('k', 'w'))
 
     y2 = -dx*np.arange(0, m2.shape[0])
     x2 = dx*np.arange(0, m2.shape[1])
     x2, y2 = np.meshgrid(x2, y2)
-    y2off = 1.7
+    y2off = 2.1 # - 4.5
     xcenter = x2[m2[:,:,0] > 0].mean()
     plt.contourf(8+x2-xcenter, y2-y2off, m2[:,:,1], levels=[0, 0.9], colors=('r', 'w'))
[…]

### 2014-07-15 paper/paper.tex
reenable plots that I should not have disabled Tested everything on bennet.
added quick explanation of stochastic to paper Tested everything on crystal.

@@
 \begin{multline}
-  \frac{\partial \sigma_d}{\partial t} = -k_E\sigma_D\rho_E
+  \frac{\partial \sigma_D}{\partial t} = -k_E\sigma_D\rho_E
   +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
@@
 A 3D grid is then constructed in cartesian coordinates, with a grid
-spacing of .05\micron. We define our cell shapes and solve the
-reaction-diffusion partial differential equations numerically to
-observe the time evolution of the MinD and MinE concentrations inside
-the cell.
+spacing of .05\micron.
+
+In order to further our understanding of the results of various
+simulation approaches to this system, we have performed both a basic
+finite analysis, deterministic simulation that is spatially and
+temporally discrete, and a stochastic analysis that is spatially
+discrete but continuous in time.  Our stochastic simulation method
+follows the work of Kraus~\cite{kraus1996crosstalk} which in turn
+follows a method introduced by Gillespie~\cite{gillespie1977exact}.
 
@@
 assymetry in protein concentration relaxes into a motionless steady
-state (see Figure~\ref{box-mannik}, or when both are too great, so
+state (see Figure~\ref{box-mannik}), or when both are too great, so
 that the proteins exhibit more than two poles and those at extreme
@@
 %  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
-  %\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
-  %\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
   \caption{Box plots of Mannik shapes for sizes at the lower stability

### 2014-08-05 paper/paper.tex
a few changes

@@
   \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500.pdf}
+  \includegraphics[width=\textwidth]{../data/shape-p/plots/single-image-stoch}
   \caption{Countour plot images of the concentration of each protein
@@
     time (one second intervals), with darker regions indicating higher
-    concentration.  The cells pictured are $4\micron$ in length,
-    measured from end to end.  The order of frames is such that
-    individual MinD proteins begin at the bottom of the plot (in the
-    MinD:ATP state in the cytoplasm), and progress upward until they
-    reach the MinE:MinD:ATP membrane-bound complex.  At that point,
-    they will spontaneously dissociate into cytoplasmic MinE (the top
-    row) and the starting state of cytoplasmic MinD:ADP.  The
+    concentration. The upper plots shows results from the
+    deterministic simulation and the lower shows results from the
+    stochastic simulation.  The cells pictured are $4\micron$ in
+    length, measured from end to end.  The order of frames is such
+    that individual MinD proteins begin at the bottom of the plot (in
+    the MinD:ATP state in the cytoplasm), and progress upward until
+    they reach the MinE:MinD:ATP membrane-bound complex.  At that
+    point, they will spontaneously dissociate into cytoplasmic MinE
+    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
     densities plotted are integrated along the axis orthogonal to the
     page, and the color scale is chosen separately for each species
-    with black as the maximum value over space and time.}
+    with black as the maximum value over space and time.  The
+    stochastic densities are smeared out over space as guassians with
+    characteristic length equal to the Abbe diffraction limit of
+    $600nm$ wavelength light}
   \label{image-p}
@@
 radius $.5\micron$ and of lengths $2\micron$, $3\micron$, and
-$5\micron$ measured from the tip of one end cap to the top of the
-other. In each case, we observe quick establishement (within a few
-periods) of extremely regular oscillatory behavoir that lasts
-indefinitely.  The period increases with cell length, as shown in
+$5\micron$ measured from the tip of one end cap to the tip of the
+other. In each case, we observe in the deterministic simulations a
+quick establishement (within a few periods) of extremely regular
+oscillatory behavoir that lasts indefinitely.  The stochastic results
+show oscillitions that are similarly regular in time, with periods
+that nearly match those of the deterministic (they differ roughly by a
+factor of .05). The stochastic results also show a slight variation in
+the height of the density maxima, but the peaks are still very well
+defined. The period increases with cell length, as shown in
 Table~\ref{tab:pill-periods}, in agreement with the results of Huang
-\emph{et al.}
+\emph{et al.}.  The stochastic simulations show a similar pattern.
+The MinD maxima occur at the ends of the cell in a back and forth
+manner, and with the same approximate period.
 
@@
   \caption{Period of oscillation according to length of cell for
-    pill-shaped cells.}\label{tab:pill-periods}\fixme{the 'sim' here
-    means that it's waiting for a simulation.  Not sure where it went
-    but I'm rerunning it.}
+    pill-shaped cells.}\label{tab:pill-periods}
 \end{table}
@@
 \ref{image-p} shows the process in a series of frames taken from
-simulation animations.  Each frame is 2.5 seconds ahead of the last,
-and each image shows a the concentration of a given state of protein
-summed over the coordinate orthogonal to the page.  The color scale
-for each protein state is set according to the maximum density
+simulation animations for both the deterministic and stochastic
+simulations.  The stochastic concentrations have been 'smeared out' in
+a manner meant to reproduce the images shown by a diffraction limited
+microscope.  The protein densities which are located at specific grid
+points give light to sorrounding grid points with a guassian weighting
+function that has a variance equal to the Abbe diffraction limit of
+$600nm$ wavelength light.  Each frame is 2.5 seconds ahead of the
+last, and each image shows a the concentration of a given state of
+protein summed over the coordinate orthogonal to the page.  The color
+scale for each protein state is set according to the maximum values
 observed.
@@
 
-\section{Stability Analysis and Mannik's Experimental Shapes}
-In general we have found that the protein reaction sequence discussed
-above results in extremely robust oscillatory behavoir of polar
-selection and oscillation in a wide variety of cell shapes.  We have
-also found that while all sizes of cell will in time settle into
-regular oscillations, there are size dependent distinctions in the
-number and placement of the spatial positions of maximization.
-Regular oscillatory behavoir between two poles at opposite ends of the
-longer cellular direction is found in cells which are long enough in
-one dimension for the reaction chain to be unstable but short enough
-in the perpendicular dimension to be stable.  The limits are seen when
+\section{Stability Analysis}
+We have found that in both methods of simulation there is a lower
+length scale that characterizes much of the behavoir.  Regular
+oscillatory behavoir between two poles at opposite ends of the longer
+cellular direction is found in cells which are long enough in one
+dimension for the reaction chain to be unstable but short enough in
+the perpendicular dimension to be stable.  The limits are seen when
 both dimensions are too short to be unstable, so that initial
-assymetry in protein concentration relaxes into a motionless steady
-state (see Figure~\ref{box-mannik}), or when both are too great, so
-that the proteins exhibit more than two poles and those at extreme
-postitions in both dimensions.
+assymetry in protein concentration relaxes into a state of no
+oscillation.  In these cell sizes, the deterministic simulations show
+a motionless steady state and the stochastic simulations show random
+fluctuations without any bulk behavoir (see Figure~\ref{box-mannik}).
 
@@
 widths of our simulated flattened cells, the cells stop exhibiting two
-pole oscillalitory behavior and instead exhibit multiple
-positions of maximization when the shortest distance across the cell
-is approximately equal to the characteristic half wavelength at the
+pole oscillalitory behavior and instead exhibit multiple positions of
+maximization when the shortest distance across the cell is
+approximately equal to the characteristic half wavelength at the
 particular thickness at which we simulate (our simulations of cells
@@
 
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/paper-arrow-plot}
+%%   \caption{Arrow plots for our simulation and mannik's experimental}
+%%   \label{arrow-compare-mannik}
+%% \end{figure}
+
+\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
+In general we have found that the deterministic simulations of the
+protein reaction sequence discussed above results in robust
+oscillatory behavoir of polar selection and oscillation in a wide
+variety of cell shapes.  On the other hand, the stochastic simulations
+show back and forth behavoir that breaks down in more assymetric
+shapes with larger sizes, which is similar to what Mannik has observed
+experimentally.
+
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/paper-arrow-plot}
-  \caption{Arrow plots for our simulation and mannik's experimental}
-  \label{arrow-compare-mannik}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/arrow-400-stoch}
+  \caption{Arrow plots of our stadium shape}
+  \label{stadium-arrow}
 \end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../paper/plot-ave}
+  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1500-95-stoch}
+  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1850-95-stoch}
+  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-95-stoch}
+  \caption{Arrow plots of our randst shape}
+  \label{stadium-arrow}
+\end{figure}
+
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1400-94-stoch}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1860-94-stoch}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-94-stoch}
+%%   \caption{Arrow plots of our randst shape}
+%%   \label{stadium-arrow}
+%% \end{figure}
+
+\fixme{specifically design other arrow plot (with many comparisons) to
+  illustrate point}
 
@@
 
-\section{Triangular Shapes}
+%% \section{Triangular Shapes}
 
-\begin{figure}
-%  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
-%  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
-  %\includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
-  \caption{Two box plots of triangle shapes.  The two smaller show
-    sizes at the lower stability threshhold, one just below, one just
-    above.  The larger triangle is the largest simulated. The vertical
-    axis shows stacked and changing over time the total number of
-    proteins that are of four different compound stages and in the
-    different sections of the cell.}
-  \label{box-triangle}
-\end{figure}
+%% \begin{figure}
+%% %  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
+%% %  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
+%%   \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
+%%   \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
+%%   %\includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
+%%   \caption{Two box plots of triangle shapes.  The two smaller show
+%%     sizes at the lower stability threshhold, one just below, one just
+%%     above.  The larger triangle is the largest simulated. The vertical
+%%     axis shows stacked and changing over time the total number of
+%%     proteins that are of four different compound stages and in the
+%%     different sections of the cell.}
+%%   \label{box-triangle}
+%% \end{figure}
 
-Along with our other shapes we have chosen to simulate both
-equilateral and iscoscolese triangular flattened shapes, since these
-offer in a way the simplest shapes that are geometrically more
-complicated than our pills.
+%% Along with our other shapes we have chosen to simulate both
+%% equilateral and iscoscolese triangular flattened shapes, since these
+%% offer in a way the simplest shapes that are geometrically more
+%% complicated than our pills.
 
-Both triangle types show a similar oscillation pattern.  The
-iscosolese exhibit regular oscillations characterized by one distinct
-pole in the more accute angle of the three, and another 'pole' along
-the opposite wall, peaking in the two more obtuse angles at the same
-time.  The equilateral triangles settle very quickly into the same
-pattern, where the choice of which is one pole corner is dependent
-upon initial conditions.  As with the Mannik simulated shapes, there
-is a critical small size below which the oscillations dampen out and
-will not achieve a regular pattern.  Figure~\ref{box-triangle} shows
-two plots of equilateral triangles.  The two smaller show the
-largest that showed damped out behavoir and the smallest that
-developed regular oscillations.  The larger shows the largest traingle
-that we simulated, showing that at even very large sizes the behavoir
-is consistent and stable.  Above the small size threshold, all
-simulated triangles show regular patterns for as long as simulated
-(roughly 800 seconds).
+%% Both triangle types show a similar oscillation pattern.  The
+%% iscosolese exhibit regular oscillations characterized by one distinct
+%% pole in the more accute angle of the three, and another 'pole' along
+%% the opposite wall, peaking in the two more obtuse angles at the same
+%% time.  The equilateral triangles settle very quickly into the same
+%% pattern, where the choice of which is one pole corner is dependent
+%% upon initial conditions.  As with the Mannik simulated shapes, there
+%% is a critical small size below which the oscillations dampen out and
+%% will not achieve a regular pattern.  Figure~\ref{box-triangle} shows
+%% two plots of equilateral triangles.  The two smaller show the
+%% largest that showed damped out behavoir and the smallest that
+%% developed regular oscillations.  The larger shows the largest traingle
+%% that we simulated, showing that at even very large sizes the behavoir
+%% is consistent and stable.  Above the small size threshold, all
+%% simulated triangles show regular patterns for as long as simulated
+%% (roughly 800 seconds).
 

### 2014-08-05 pyplots/box_plot.py

@@ -350,6 +350,9 @@ def main():
                              alpha=alphaScale_D[k],facecolor=colorScale[j])
             k+=1
     bax.set_xlim(timeAxis[start],timeAxis[end-1])
+    print timeAxis[start]
+    bax.set_xticklabels(np.arange(timeAxis[start]+100, timeAxis[end-1]+100, 0.5))
+    #bax.set_xticklabels(np.arange(0, 10, 0.5))
     bax.get_yaxis().set_visible(False)
     bax.set_ylim(0, 1)
     bax.set_title("MinD protein counts over time")

### 2014-08-07 paper/paper.tex
added a whole bunch of things and edited Makefile so can pull and make paper Tested everything on node21.

@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500.pdf}
-  \includegraphics[width=\textwidth]{../data/shape-p/plots/single-image-stoch}
+  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500-exact}
+  \includegraphics[width=\textwidth]{../data/shape-p/plots/single-image-plot--p-300-50-0-0-1500-full_array}
   \caption{Countour plot images of the concentration of each protein
@@
     characteristic length equal to the Abbe diffraction limit of
-    $600nm$ wavelength light}
+    $600nm$ wavelength light (ends up being about 200nm)\fixme{say
+      something about the axial resolution, which is even more limited
+      than the lateral resolution, which is why we integrate data long
+      axial direction}}
   \label{image-p}
@@
 %  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500-exact}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500-exact}
   \caption{Box plots of Mannik shapes for sizes at the lower stability
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/arrow-400-stoch}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/ave-time/plot-time-averaged-arrow-300-1600-NflD-stad-25-400-150-0-1500-full_array}
   \caption{Arrow plots of our stadium shape}
@@
 
-\section{Our '\textgreater' Shaped Cells}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
-  \label{fig:Vbox}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
-  \label{fig:Vbox2}
-\end{figure}
+%% \section{Our '\textgreater' Shaped Cells}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
+%%   \label{fig:Vbox}
+%% \end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
+%%   \label{fig:Vbox2}
+%% \end{figure}
 
-We have also simulated a flattened '\textgreater' shape that shows an
-interesting size dependent pattern (seen in
-Figures~\ref{fig:Vbox}~and~\ref{fig:Vbox2}).  When the shape is small enough
-that the distance from the apex tip to the opposite curve is less than
-our stability limit, a simple, two pole oscillation pattern develops
-and is sustained (where the two poles are on opposite leftward corners
-of the cell).  When the cell is increased in size so that this
-distance is approximately equal to our stability value, the cell
-develops a double oscillation in time, where the maxima oscillates
-from the lower corner to the rightward apex, then \emph{back to the
-  lower corner}, then to the apex again, then to the upper corner,
-then back to the apex, then to the upper corner, then to the apex
-again, then back to the lower corner, and continues this pattern
-indefinately.  Figure~\ref{fig:Vbox} shows the smaller size, for which the
-protein oscillates simply, and an intermediate size, which shows a
-pattern for which one out of three spikes in the regular oscillation
-is less significant.  This second pattern seems to be a precursor to
-the double oscillation that seen in Figure~\ref{fig:Vbox2}.  The second
-plot shown in Figure~\ref{fig:Vbox2} shows a slightly larger cell for
-which the distance measured is larger than our stability limit
-distance.  This simulation shows a random pattern.
+%% We have also simulated a flattened '\textgreater' shape that shows an
+%% interesting size dependent pattern (seen in
+%% Figures~\ref{fig:Vbox}~and~\ref{fig:Vbox2}).  When the shape is small enough
+%% that the distance from the apex tip to the opposite curve is less than
+%% our stability limit, a simple, two pole oscillation pattern develops
+%% and is sustained (where the two poles are on opposite leftward corners
+%% of the cell).  When the cell is increased in size so that this
+%% distance is approximately equal to our stability value, the cell
+%% develops a double oscillation in time, where the maxima oscillates
+%% from the lower corner to the rightward apex, then \emph{back to the
+%%   lower corner}, then to the apex again, then to the upper corner,
+%% then back to the apex, then to the upper corner, then to the apex
+%% again, then back to the lower corner, and continues this pattern
+%% indefinately.  Figure~\ref{fig:Vbox} shows the smaller size, for which the
+%% protein oscillates simply, and an intermediate size, which shows a
+%% pattern for which one out of three spikes in the regular oscillation
+%% is less significant.  This second pattern seems to be a precursor to
+%% the double oscillation that seen in Figure~\ref{fig:Vbox2}.  The second
+%% plot shown in Figure~\ref{fig:Vbox2} shows a slightly larger cell for
+%% which the distance measured is larger than our stability limit
+%% distance.  This simulation shows a random pattern.
 
-A detailed analysis of a time series of protein contour plots shows
-that the importance of spatial dimensions is based on the ability of
-protein in different stages to diffuse neccesary distances before
-undergowing certain types of reactions.  The double oscillation
-pattern shows that every time the membrane bound MinD maximizes in the
-upper corner as opposed to the rightward apex, it does so because the
-MinE has not had enough time to diffuse to this upper corner, leaving
-a MinE free zone.  This particular pattern is specific to this shape
-and size, but in general its the restrictions set in place by the
-rates at which proteins diffuse and the distances they cover before
-reacting that dictate their oscillatory bahavoir.
+%% A detailed analysis of a time series of protein contour plots shows
+%% that the importance of spatial dimensions is based on the ability of
+%% protein in different stages to diffuse neccesary distances before
+%% undergowing certain types of reactions.  The double oscillation
+%% pattern shows that every time the membrane bound MinD maximizes in the
+%% upper corner as opposed to the rightward apex, it does so because the
+%% MinE has not had enough time to diffuse to this upper corner, leaving
+%% a MinE free zone.  This particular pattern is specific to this shape
+%% and size, but in general its the restrictions set in place by the
+%% rates at which proteins diffuse and the distances they cover before
+%% reacting that dictate their oscillatory bahavoir.
 
-Simulations of this shape in which the two planar dimensions are large
-compared to those shown(roughly $9\micron$ across) show no stable
-regular periodic pattern. Animations show that the MinD acts as a sort
-of traveling cluster that is constantly being eaten away by MinE
-behind it.  When this cluster enters a region of high curvature that
-ends in a dead end corner it performs the polar maxima behavoir seen
-in the other simulations, regrouping out away from the corner where it
-travels in the opposite direction while being ``chased'' away by the
-MinE that itself is currently maximizing in the corner.  The maxima
-occur on non-polar walls often, and will often split into two roaming
-clusters.
+%% Simulations of this shape in which the two planar dimensions are large
+%% compared to those shown(roughly $9\micron$ across) show no stable
+%% regular periodic pattern. Animations show that the MinD acts as a sort
+%% of traveling cluster that is constantly being eaten away by MinE
+%% behind it.  When this cluster enters a region of high curvature that
+%% ends in a dead end corner it performs the polar maxima behavoir seen
+%% in the other simulations, regrouping out away from the corner where it
+%% travels in the opposite direction while being ``chased'' away by the
+%% MinE that itself is currently maximizing in the corner.  The maxima
+%% occur on non-polar walls often, and will often split into two roaming
+%% clusters.
 

### 2014-08-07 paper/plot-arrow-ave.py

@@ -1,0 +1,291 @@
+from __future__ import division
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+from matplotlib.font_manager import FontProperties
+import matplotlib.patheffects
+from mpl_toolkits.axes_grid.anchored_artists import AnchoredSizeBar
+import matplotlib.image as mpimg
+import os
+import sys
+import time
+import imp
+#load = imp.load_source('load', 'pyplots/file_loader.py')
+import math
+import matplotlib.gridspec as gridspec
+
+#create data objects (see file_loader.py)
+
+
+
+  # \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1500-95-stoch}
+  # \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1850-95-stoch}
+  # \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-95-stoch}
+
+
+
+dx =0.05
+dump_time_step = 0.5
+protein_name = "NflD"
+# start_time = float(f_param6)
+# input_end_time = float(f_param7)
+#end_time = int(input_end_time - input_end_time%10)
+
+# arg_set = ["randst-0.25-15.00-15.00-95.00-15.00",
+#            "randst-0.25-18.50-18.50-95.00-15.00",
+#            "randst-0.25-25.00-25.00-95.00-15.00"]
+
+arg_set = ["randst-0.25-18.50-18.50-95.00-15.00"]
+
+bound_times = ["300","1500","300","1100","300","920"]
+
+arrow_files = []
+contour_values = []
+for i in range(len(arg_set)):
+    arrow_files += ['./data/shape-randst/plots/ave-time/maxima-arrowNflD-'+arg_set[i]+'-full_array.dat']
+    contour_values += ['./data/shape-randst/plots/ave-time/contour-values-'+bound_times[i*2]+'-' \
+        +bound_times[i*2+1]+'-NflD-'+arg_set[i]+'-full_array.dat']
+    print arrow_files
+    print contour_values
+
+
+plt.figure(1)
+
+#plt.clf()
+print "len",len(arg_set)
+
+# half_width = float(c_data.shape[1]/max_width)/2.0
+# print half_width
+#gs.update(left=.5-half_width,right=.5+half_width)
+#plt.title("%f"%half_width)
+
+hts = []
+for i in range(len(contour_values)):
[…]

### 2014-08-07 pyplots/box_plot.py

@@ -31,13 +31,19 @@ from mpl_toolkits.axes_grid.anchored_artists import AnchoredSizeBar
 #boxName. returns list of protein counts at each time.
 #box-plot--p-0.50-0.50-0.00-0.00-15.00-exact.dat
 
+sim_type = load.sim_type
+if sim_type == "full_array":
+    sim_type = "-full_array"
+else:
+    sim_type = ""
+
 def returnData(boxName,proteinType):
 
     #open the data file, grab the line with the correct protein type and box partition, load it as a [string] (so we can use list comprehensions)
-    filename = "./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s-%s.dat" % (load.f_shape,load.debug_str,load.hires_str,
+    filename = "./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s%s.dat" % (load.f_shape,load.debug_str,load.hires_str,
                                                                              load.slice_str,load.f_shape,load.f_param1,
                                                                              load.f_param2,load.f_param3,
-                                                                             load.f_param4,load.f_param5,load.sim_type)
+                                                                             load.f_param4,load.f_param5,sim_type)
     print 'loading', filename
     with open(filename,"r") as boxData:
         proteinsOverTime = [line for line in boxData if (proteinType in line) and (boxName in line)]
@@ -108,7 +114,7 @@ def find_period(f):
     return (penultimate_min, lastmin)
 
 def main():
-    filename = "./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5,load.sim_type)
+    filename = "./data/shape-%s/%s%s%sbox-plot--%s-%s-%s-%s-%s-%s%s.dat"%(load.f_shape,load.debug_str,load.hires_str,load.slice_str,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5,sim_type)
     print 'loading', filename
     with open(filename, "r") as boxData:
         fileLines = boxData.readlines()

### 2014-08-07 pyplots/file_loader.py

@@ -54,8 +54,8 @@ class data(object):
         self.filenames = get_filenames(protein,sim_type,start_time,end_time)
         self.tsteps = len(self.filenames)
         self.dataset = np.array([np.loadtxt(file) for file in self.filenames])
-        for file in self.filenames:
-            print 'loading', file
+        # for file in self.filenames:
+        #     print 'loading', file
         self.datashape = self.dataset[0].shape
         self.axes = [[i*dx for i in range(self.datashape[1])],[j*dx for j in range(self.datashape[0])]]
 
@@ -67,9 +67,13 @@ def get_filenames(protein,sim_type,start_time,end_time):
         end_time = 10000
     for f_num in np.arange(start_time,end_time,dump_time_step):
         file_num = round(f_num/dump_time_step)
-        fname = "./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-%03d-%s.dat"% \
-        (f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5,file_num,sim_type)
-        #print fname
+        fname = ""
+        if sim_type == "":
+            fname = "./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-%03d.dat"% \
+                (f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5,file_num)
+        else:
+            fname = "./data/shape-%s/%s%s%s%s-%s-%s-%s-%s-%s-%s-%03d-%s.dat"% \
+                (f_shape,debug_str,hires_str,slice_str,protein,f_shape,f_param1,f_param2,f_param3,f_param4,f_param5,file_num,sim_type)
         if os.path.isfile(fname):
             dat_filenames.append(fname)
     if git_add_files:
@@ -85,7 +89,8 @@ def get_filenames(protein,sim_type,start_time,end_time):
 def print_string(plot_name,p):
     arg = [str(int(100*(float(i)))) for i in sys.argv[2:7]]
     filename = "./data/shape-%s/plots/%s%s%s%s-%s-%s-%s-%s-%s-%s-%s-%s.pdf"% \
-    (f_shape, debug_str, hires_str, slice_str, plot_name, p, f_shape, arg[0], arg[1], arg[2], arg[3], arg[4],sim_type)
[…]

### 2014-08-07 pyplots/image_plot.py

@@ -15,8 +15,8 @@ f_param2 = sys.argv[3]
 f_param3 = sys.argv[4]
 f_param4 = sys.argv[5]
 f_param5 = sys.argv[6]
-start_time = float(sys.argv[7])
-end_time = float(sys.argv[8])
+start_time = float(sys.argv[8])
+end_time = float(sys.argv[9])
 
 
 dump_time_step = 0.5
@@ -39,7 +39,7 @@ proteinLabels = ["MinD:ADP (cyto)",
 proteins = [0]*len(proteinList)
 
 for i in range(len(proteinList)):
-    proteins[i] = load.data(proteinList[i],start_time,end_time)
+    proteins[i] = load.data(proteinList[i],"",start_time,end_time)
 
 plt.figure(figsize=(9,3.5)).patch.set_alpha(0)
 numtimes = int(end_time/dump_time_step)- int(start_time/dump_time_step)
@@ -48,6 +48,8 @@ skip_times = 2 # only plot every skip_times of the snapshots
 dZ = proteins[0].datashape[1]*1.05
 dY = proteins[0].datashape[0]*1.1/skip_times
 kvals = range(0, int(end_time/dump_time_step)-int(start_time/dump_time_step), skip_times)
+
+print "Starting image plot."
 
 for i in range(len(proteins)):
     if (proteinList[i]=="ND" or proteinList[i]=="NDE"):

### 2014-08-07 pyplots/plot-ave-arrow.py

@@ -36,6 +36,9 @@ contour_values = './data/shape-'+f_shape+'/plots/ave-time/contour-values-'+str(i
     +str(end_time)+'-'+protein_name+'-'+f_shape+'-'+f_param1+'-'+f_param2+'-' \
     +f_param3+'-'+f_param4+'-'+dens_factor+'-'+sim_type+'.dat'
 
+print arrow_file
+print contour_values
+
 c_data = np.loadtxt(contour_values)
 a_data = np.loadtxt(arrow_file)
 
@@ -112,6 +115,8 @@ plt.axis('off')
 #plt.title("Time-averaged density from "+str(start_time)+" to "+str(input_end_time))
 #plt.xlabel("Z position")
 #plt.ylabel("Y position")
-plt.savefig('./data/shape-'+f_shape+'/plots/ave-time/plot-time-averaged-arrow-'+str(int(start_time))+'-' \
-                +str(end_time)+'-'+protein_name+'-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-' \
-                +f_param4+'-'+dens_factor+'-'+sim_type+'.pdf')
+save_file_name = './data/shape-'+f_shape+'/plots/ave-time/plot-time-averaged-arrow-'+str(int(start_time))+'-' \
+                +str(end_time)+'-'+protein_name+'-'+f_shape+'-'+str(int(100*float(f_param1)))+'-'+str(int(100*float(f_param2))) \
+                +'-'+str(int(100*float(f_param3)))+'-'+str(int(100*float(f_param4)))+'-'+str(int(100*float(dens_factor)))+'-'+sim_type+'.pdf'
+print save_file_name
+plt.savefig(save_file_name)

### 2014-08-07 pyplots/single-image-creation.py

@@ -1,0 +1,107 @@
+from __future__ import division
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import os
+import sys
+import time
+import file_loader as load
+import Image
+import math
+
+f_shape = sys.argv[1]
+f_param1 = sys.argv[2]
+f_param2 = sys.argv[3]
+f_param3 = sys.argv[4]
+f_param4 = sys.argv[5]
+dens_factor = sys.argv[6]
+sim_type = sys.argv[7]
+f_param6 = sys.argv[8]
+f_param7 = sys.argv[9]
+
+dump_time_step = 0.5
+start_time = float(f_param6)
+end_time = float(f_param7)
+
+# n_sin_theta = 1.5
+# wavelength = .6
+# sigma = wavelength/2.0/n_sin_theta #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+# dis = int(3.5*sigma/0.05) #for now
+# print "wavelength",wavelength
+# print "sigma",sigma
+# print "dis",dis
+
+# for i in np.arange(-dis,dis,1):
+#     for j in np.arange(-dis,dis,1):
+#      #   if 10.0*math.exp( -(i*i+j*j)*.05*.05/2.0/sigma/sigma ) > 7.0:
+#         print "dis ",math.sqrt((i*i+j*j)),"val ",10.0*math.exp( -(i*i+j*j)*.05*.05/2.0/sigma/sigma )
+# print "dis",dis
+# exit(0)
+
+def gaussian_smear(data,wavelength):
+    new = np.zeros_like(data)
+    print "here ",new.shape[0]
+    n_sin_theta = 1.5
+    #sigma below is tha Abbe resolution.  n is the diffraction of the medium, sin_theta the aperture angle
+    #So far I've wiki'd the guassian form of the Airy disk for this
+    sigma = wavelength/2.0/n_sin_theta #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+    dis = int(3.5*sigma/0.05) #for now
+    for num in range(new.shape[0]):
+        print "num ",num," of ",new.shape[0]-1
+        for x in range(new.shape[1]):
+            #print x," of ",new.shape[1]-1
+            for y in range(new.shape[2]):
+                for i in np.arange(-dis,dis,1):
+                    for j in np.arange(-dis,dis,1):
[…]

### 2014-08-07 pyplots/single-image-plot.py

@@ -26,62 +26,45 @@ start_time = float(f_param6)
 end_time = float(f_param7)
 
 
-def gaussian_smear(data,wavelength):
-    new = np.zeros_like(data)
-    new = new[0:len(new)/skip_times]
-    n_sin_theta = 1.5
-    sigma = wavelength/2.0/n_sin_theta #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
-    dis = int(3*sigma/0.05) #for now
-    for num in range(new.shape[0]):
-        print "num ",num," of ",new.shape[0]-1
-        for x in range(new.shape[1]):
-            print x," of ",new.shape[1]-1
-            for y in range(new.shape[2]):
-                for i in np.arange(-dis,dis,1):
-                    for j in np.arange(-dis,dis,1):
-                        if (x+i >= 0 and x+i < new.shape[1]-1 and y+j >= 0 and y+j < new.shape[2]-1):
-                            new[num,x+i,y+j] += data[num*skip_times,x,y]*math.exp( -(i*i+j*j)*.05*.05/sigma/sigma )
-    return new
+proteinList = ["nADP","nATP","ND","NDE","nE",]
+proteinLabels = ["MinD:ADP (cyto)","MinD:ATP (cyto)","MinD:ATP (mem)","MinD:MinE:ATP (mem)","MinD:E (cyto)",]
+
+plt.figure(figsize=(9,3.5))
+times  = np.arange(float(start_time),float(end_time),1.0)
+print "Starting single image plot."
+print times
 
 
 #computes the global maximum over a set of two dimensional arrays (stored as files)
-def timemax(protein):
-    return max([v.max() for v in protein])
-
-proteinList = ["nADP","nATP","ND","NDE","nE",]
-#proteinList = ["nATP"]
-proteinLabels = ["MinD:ADP (cyto)","MinD:ATP (cyto)","MinD:ATP (mem)","MinD:MinE:ATP (mem)","MinD:E (cyto)",]
-
-proteins = [0]*len(proteinList)
-
-for i in range(len(proteinList)):
-    proteins[i] = load.data(proteinList[i],sim_type,start_time,end_time)
+def timemax(data):
+    return max([v.max() for v in data])
 
 plt.figure(figsize=(9,3.5))
 numtimes = int(end_time/dump_time_step)- int(start_time/dump_time_step)
-numproteins = len(proteins)
[…]

### 2014-08-07 weights-new.h

@@ -1,0 +1,60 @@
+#ifndef __WEIGHTS_H_INCLUDED__
+#define __WEIGHTS_H_INCLUDED__
+
+#include <stdio.h>
+#include <math.h>
+
+class weights {
+ public:
+  weights()= {}
+  virtual void update(double w, int i) = 0;
+  int lookup(double p) const = 0;
+  double get_total() = 0;
+  double lookup_prob_for_specific_index(int index) = 0;
+
+  /*Testing Functions*/
+  void update_one_spot_and_look_at_entire_array(double w, int index) = 0;
+  int test_lookup_from_zero_to_one(int num_possibilities) = 0;
+  int test_get_total_matches_summing_up(int num_possibilities) = 0;
+  int test_looking_up_shows_correct_probs(int num_possibilities) = 0;
+  int test_time_of_simulation(int num_possibilities) = 0;
+  int test_of_lookup_prob_for_specific_index(int num_possibilities) = 0;
+};
+
+class fullweights {
+ public:
+  fullweights()= {}
+  void update(double w, int i);
+  int lookup(double p) const;
+  double get_total();
+  double lookup_prob_for_specific_index(int index);
+
+  /*Testing Functions*/
+  void update_one_spot_and_look_at_entire_array(double w, int index);
+  int test_lookup_from_zero_to_one(int num_possibilities);
+  int test_get_total_matches_summing_up(int num_possibilities);
+  int test_looking_up_shows_correct_probs(int num_possibilities);
+  int test_time_of_simulation(int num_possibilities);
+  int test_of_lookup_prob_for_specific_index(int num_possibilities);
+private:
+  data foo;
+};
+
+class halfweights {
+ public:
+  halfweights()= {}
+  void update(double w, int i);
+  int lookup(double p) const;
+  double get_total();
+  double lookup_prob_for_specific_index(int index);
+
+  /*Testing Functions*/
+  void update_one_spot_and_look_at_entire_array(double w, int index);
+  int test_lookup_from_zero_to_one(int num_possibilities);
+  int test_get_total_matches_summing_up(int num_possibilities);
+  int test_looking_up_shows_correct_probs(int num_possibilities);
+  int test_time_of_simulation(int num_possibilities);
+  int test_of_lookup_prob_for_specific_index(int num_possibilities);
+};
+
+#endif

### 2014-08-08 paper/plot-arrow-ave.py
made changes to data used in stad arrow, in plot-arrow-ave eliminated other sizes, and labeling and also updated time_map plotting Tested everything on quipu.

@@ -19,11 +19,6 @@ import matplotlib.gridspec as gridspec
 
 
 
-  # \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1500-95-stoch}
-  # \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1850-95-stoch}
-  # \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-95-stoch}
-
-
 
 dx =0.05
 dump_time_step = 0.5
@@ -32,13 +27,10 @@ protein_name = "NflD"
 # input_end_time = float(f_param7)
 #end_time = int(input_end_time - input_end_time%10)
 
-# arg_set = ["randst-0.25-15.00-15.00-95.00-15.00",
-#            "randst-0.25-18.50-18.50-95.00-15.00",
-#            "randst-0.25-25.00-25.00-95.00-15.00"]
+arg_set = ["randst-0.25-18.50-18.50-95.00-15.00",
+           "randst-0.25-18.60-28.60-94.00-15.00"]
 
-arg_set = ["randst-0.25-18.50-18.50-95.00-15.00"]
-
-bound_times = ["300","1500","300","1100","300","920"]
+bound_times = ["300","1500","300","1100"]
 
 arrow_files = []
 contour_values = []
@@ -67,28 +59,38 @@ for i in range(len(contour_values)):
 if len(contour_values) > 1:
     hts += [hts[1]]
 
-# gs = gridspec.GridSpec(len(arg_set)+1,1,
-#                        height_ratios=hts,
-#                        )
-gs = gridspec.GridSpec(len(arg_set)+1,1)
+gs = gridspec.GridSpec(2,2)
 
-for arg_num in range(len(arg_set)+1):
+for arg_num in range(len(arg_set)+2):
 #    plt.subplot2grid((len(arg_set)+1,1),(arg_num,0),aspect='equal')
-    plt.subplot(gs[arg_num,0],aspect='equal')
     #gs_in = gridspec.GridSpec(arg_num,0)
     #gs_in.update(left=.3+arg_num*.1,right=.8)
-    if arg_num == len(arg_set):
-            m1=mpimg.imread('mannik-1.png')
-            dx = 7.0/380
-            print m1.shape[1]
-            y1 = -dx*np.arange(0, m1.shape[0])
[…]

### 2014-08-08 pyplots/plot-ave-arrow.py

@@ -29,7 +29,7 @@ start_time = float(f_param6)
 input_end_time = float(f_param7)
 end_time = int(input_end_time - input_end_time%10)
 
-arrow_file = './data/shape-'+f_shape+'/plots/ave-time/maxima-arrow'+protein_name+ \
+arrow_file = './data/shape-'+f_shape+'/plots/ave-time/maxima-arrow-'+str(int(start_time))+'-'+protein_name+ \
     '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+dens_factor+'-'+sim_type+'.dat'
 
 contour_values = './data/shape-'+f_shape+'/plots/ave-time/contour-values-'+str(int(start_time))+'-' \
@@ -40,13 +40,15 @@ print arrow_file
 print contour_values
 
 c_data = np.loadtxt(contour_values)
+print os.path.isfile(arrow_file)
 a_data = np.loadtxt(arrow_file)
 
-print a_data[:,0]
+print a_data
+print "this ",a_data[:,0]
 print len(a_data[:,0])
 
 print "hello",str((end_time-start_time)*dump_time_step)
-a_data = a_data[int((start_time-300)/dump_time_step):int((end_time-start_time)/dump_time_step)]
+a_data = a_data[0:int((end_time-start_time)/dump_time_step)]
 
 print a_data[:,0]
 print len(a_data[:,0])
@@ -82,10 +84,6 @@ for i in range(len(a_data[:,1])):
             times = np.append(times,a_data[i,0])
             last_x = a_data[i,2]*dx
             last_y = a_data[i,3]*dx
-            # print ""
-            # print 'v ',a_data[i,1]
-            # print 'x ',a_data[i,2]*dx
-            # print 'y ',a_data[i,3]*dx
 print x_vals
 print y_vals
 
@@ -112,10 +110,7 @@ for i in range(len(x_vals)-1):
                  arrowprops=dict(color='red',shrink=0.01, width=.3, headwidth=5.))
 plt.clim(0,time_max)
 plt.axis('off')
-#plt.title("Time-averaged density from "+str(start_time)+" to "+str(input_end_time))
-#plt.xlabel("Z position")
-#plt.ylabel("Y position")
-save_file_name = './data/shape-'+f_shape+'/plots/ave-time/plot-time-averaged-arrow-'+str(int(start_time))+'-' \
[…]

### 2014-08-08 pyplots/time-averaged-arrow.py

@@ -50,7 +50,7 @@ def gaussian_smear(data,wavelength,protein):
     n_sin_theta = 1.5
     sigma = wavelength/2.0/n_sin_theta #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
     dis = int(3*sigma/0.05) #for now
-    arrow_file = './data/shape-'+f_shape+'/plots/ave-time/maxima-arrow'+str(protein)+ \
+    arrow_file = './data/shape-'+f_shape+'/plots/ave-time/maxima-arrow-'+str(int(input_start_time))+'-'+str(protein)+ \
         '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+dens_factor+'-'+sim_type+'.dat'
     p_file = open(arrow_file,'w')
     p_file.close()

### 2014-08-08 pyplots/time_map.py

@@ -23,13 +23,16 @@ def gaussian_smear(data,wavelength):
     return new
 
 
-for protein in load.proteinList:
+proteinList = ["NflD"]
+
+for protein in proteinList:
     data_file = np.loadtxt("./data/shape-%s/time-map-%s-%s-%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,protein,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5,load.sim_type))
 
     data = gaussian_smear(data_file,.6)
+    timemax = np.max(data)
 
     plt.figure()
-    plt.pcolormesh(data)
+    plt.pcolormesh(data,vmin=0)
     plt.axes().set_aspect('equal')
     plt.xlim(0,data.shape[1])
     plt.ylim(0,data.shape[0])

### 2014-08-11 paper/paper.tex
made changes to data used in stad arrow, in plot-arrow-ave eliminated other sizes, and labeling and also updated time_map plotting Tested everything on quipu.
added some time plots to paper Tested everything on node21.

@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/ave-time/plot-time-averaged-arrow-300-1600-NflD-stad-25-400-150-0-1500-full_array}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/plot-time-averaged-arrow-500-520-NflD-stad-25-400-150-0-1500-full_array}
   \caption{Arrow plots of our stadium shape}
@@
 
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1400-94-stoch}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1860-94-stoch}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-94-stoch}
-%%   \caption{Arrow plots of our randst shape}
-%%   \label{stadium-arrow}
-%% \end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/time-map-NflD-stad-25-600-200-0-1500-full_array}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/time-map-NflD-stad-25-400-150-0-1500-full_array}
+  \caption{Time map plots of our stad shape}
+  \label{time-maps-stad}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-1850-1850-9500-1500-full_array}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-2500-2500-9500-1500-full_array}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-1860-2860-9400-1500-full_array}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-2300-3200-9400-1500-full_array}
+  \caption{Time map plots of our randst shape}
+  \label{time-maps-randst}
+\end{figure}
 

### 2014-08-11 pyplots/time_map.py

@@ -26,7 +26,10 @@ def gaussian_smear(data,wavelength):
 proteinList = ["NflD"]
 
 for protein in proteinList:
-    data_file = np.loadtxt("./data/shape-%s/time-map-%s-%s-%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,protein,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5,load.sim_type))
+    data_file_name = "./data/shape-%s/time-map-%s-%s-%s-%s-%s-%s-%s-%s.dat"%(load.f_shape,protein,load.f_shape,load.f_param1,load.f_param2,load.f_param3,load.f_param4,load.f_param5,load.sim_type)
+    data_file = np.loadtxt(data_file_name)
+
+    print "starting time_map.p for ",data_file_name
 
     data = gaussian_smear(data_file,.6)
     timemax = np.max(data)

### 2014-08-13 paper/paper.tex
work in progress Tested everything on quipu.

@@
     with black as the maximum value over space and time.  The
-    stochastic densities are smeared out over space as guassians with
-    characteristic length equal to the Abbe diffraction limit of
-    $600nm$ wavelength light (ends up being about 200nm)\fixme{say
-      something about the axial resolution, which is even more limited
-      than the lateral resolution, which is why we integrate data long
-      axial direction}}
+    stochastic densities are smeared out over space using a guassians
+    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
   \label{image-p}
@@
 simulation animations for both the deterministic and stochastic
-simulations.  The stochastic concentrations have been 'smeared out' in
-a manner meant to reproduce the images shown by a diffraction limited
-microscope.  The protein densities which are located at specific grid
-points give light to sorrounding grid points with a guassian weighting
-function that has a variance equal to the Abbe diffraction limit of
-$600nm$ wavelength light.  Each frame is 2.5 seconds ahead of the
-last, and each image shows a the concentration of a given state of
-protein summed over the coordinate orthogonal to the page.  The color
-scale for each protein state is set according to the maximum values
-observed.
+simulations.  We have 'smeared out' the stochastic concentrations in a
+manner meant to reproduce the images shown by diffraction limited
+flourescence microscopy.  We do so using the two dimensional gaussian
+approximation developed by Zhang et all~\cite{zhang2007gaussian}.  In
+this approximation we use a numerical aperture value of 1.3, which is
+the same as used by mannik experimentally, and a wavelength of
+$509nm$, typical of green flourescent microscopy.  Each frame is 2.5
+seconds ahead of the last, and each image shows a the concentration of
+a given state of protein summed over the coordinate orthogonal to the
+page.  The color scale for each protein state is set according to the
+maximum values observed.
 

### 2014-08-13 protein_microscopy.cpp

@@ -1008,7 +1008,8 @@ int main (int argc, char *argv[]) {
 
       //begin nATP printing.
       char *outfilenameATP = new char[1024];
-      sprintf(outfilenameATP, "data/shape-%s/%s%s%snATP-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d-%s.dat", mem_f_shape.c_str(),debug_flag_str,hires_flag_str,slice_flag_str,mem_f_shape.c_str(),A,B,C,D,density_factor,k,sim_type.c_str());
+      sprintf(outfilenameATP, "data/shape-%s/%s%s%snATP-%s-%03.2f-%03.2f-%03.2f-%03.2f-%03.2f-%03d-%s.dat",
+              mem_f_shape.c_str(),debug_flag_str,hires_flag_str,slice_flag_str,mem_f_shape.c_str(),A,B,C,D,density_factor,k,sim_type.c_str());
       FILE *nATPfile = fopen((const char *)outfilenameATP,"w");
       delete[] outfilenameATP;
 

### 2014-08-13 pyplots/plot-ave-arrow.py

@@ -64,7 +64,7 @@ for i in range(1,len(a_data[:,0])):
 
 
 time_max = np.max(c_data)
-arrow_cutoff = 3.0*(np.max(a_data[:,1]))/5.0
+arrow_cutoff = 3.2*(np.max(a_data[:,1]))/5.0
 
 high_maximas = np.zeros(0)
 times = np.zeros(0)
@@ -109,7 +109,7 @@ for i in range(len(x_vals)-1):
                  fontsize=7,
                  arrowprops=dict(color='red',shrink=0.01, width=.3, headwidth=5.))
 plt.clim(0,time_max)
-plt.axis('off')
+#plt.axis('off')
 save_file_name = './data/shape-'+f_shape+'/plots/plot-time-averaged-arrow-'+str(int(start_time))+'-' \
                 +str(end_time)+'-'+protein_name+'-'+f_shape+'-'+str(int(100*float(f_param1)))+'-'+str(int(100*float(f_param2))) \
                 +'-'+str(int(100*float(f_param3)))+'-'+str(int(100*float(f_param4)))+'-'+str(int(100*float(dens_factor)))+'-'+sim_type+'.pdf'

### 2014-08-13 pyplots/time-averaged-arrow.py

@@ -47,8 +47,9 @@ if (input_end_time >= total_number_of_files*dump_time_step):
 
 def gaussian_smear(data,wavelength,protein):
     new = np.zeros_like(data[0])
-    n_sin_theta = 1.5
-    sigma = wavelength/2.0/n_sin_theta #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+    N_A = 1.3
+    sigma = .21*wavelength/N_A #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+    print "sigma ",sigma
     dis = int(3*sigma/0.05) #for now
     arrow_file = './data/shape-'+f_shape+'/plots/ave-time/maxima-arrow-'+str(int(input_start_time))+'-'+str(protein)+ \
         '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+dens_factor+'-'+sim_type+'.dat'
@@ -67,9 +68,9 @@ def gaussian_smear(data,wavelength,protein):
                 for i in np.arange(-dis,dis,1):
                     for j in np.arange(-dis,dis,1):
                         if (x+i >= 0 and x+i < new.shape[0]-1 and y+j >= 0 and y+j < new.shape[1]-1):
-                            new[x+i,y+j] += data[num,x,y]*math.exp( -(i*i+j*j)*.05*.05/sigma/sigma )
+                            new[x+i,y+j] += data[num,x,y]*math.exp( -(i*i+j*j)*.05*.05/2.0/sigma/sigma )
                             total_light += new[x+i,y+j]
-                            max_data[x+i,y+j] += data[num,x,y]*math.exp( -(i*i+j*j)*.05*.05/sigma/sigma )
+                            max_data[x+i,y+j] += data[num,x,y]*math.exp( -(i*i+j*j)*.05*.05/2.0/sigma/sigma )
         print "total proteins = ",total_light/(num+1)
         print "total proteins = ",total_proteins
         maxima = 0
@@ -98,4 +99,4 @@ def gaussian_smear(data,wavelength,protein):
 
 
 data = load.data(protein=protein_name, sim_type=sim_type,start_time = input_start_time, end_time = input_end_time)
-smeared_data = gaussian_smear(data.dataset,.6,data.protein) #this is in microns green light at 500nm,
+smeared_data = gaussian_smear(data.dataset,.509,data.protein) #this is in microns green light at 500nm,

### 2014-08-13 pyplots/time_map.py

@@ -11,15 +11,16 @@ import math
 
 def gaussian_smear(data,wavelength):
     new = np.zeros_like(data)
-    n_sin_theta = 1.5
-    sigma = wavelength/2.0/n_sin_theta #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+    N_A = 1.3
+    sigma = .21*wavelength/N_A #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+    print "new way sigma ",sigma
     dis = int(3*sigma/0.05) #for now
     for x in range(new.shape[0]):
         for y in range(new.shape[1]):
             for i in np.arange(-dis,dis,1):
                 for j in np.arange(-dis,dis,1):
                     if (x+i >= 0 and x+i < new.shape[0]-1 and y+j >= 0 and y+j < new.shape[1]-1):
-                        new[x+i,y+j] += data[x,y]*math.exp( -(i*i+j*j)*.05*.05/sigma/sigma )
+                        new[x+i,y+j] += data[x,y]*math.exp( -(i*i+j*j)*.05*.05/2.0/sigma/sigma )
     return new
 
 
@@ -31,7 +32,7 @@ for protein in proteinList:
 
     print "starting time_map.p for ",data_file_name
 
-    data = gaussian_smear(data_file,.6)
+    data = gaussian_smear(data_file,.509)
     timemax = np.max(data)
 
     plt.figure()

### 2014-08-21 paper/paper.tex
made changes necc for Makefile to work with new file structure Tested everything on quipu.

@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{../data/shape-p/plots/image-plot--p-300-50-0-0-1500-exact}
-  \includegraphics[width=\textwidth]{../data/shape-p/plots/single-image-plot--p-300-50-0-0-1500-full_array}
+  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
   \caption{Countour plot images of the concentration of each protein
@@
 %  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500-exact}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500-exact}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-8_00-8_00-95_00-15_00-exact/plots/box-plot_D}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-10_00-17_00-94_00-15_00-exact/plots/box-plot_D}
   \caption{Box plots of Mannik shapes for sizes at the lower stability
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/plot-time-averaged-arrow-500-520-NflD-stad-25-400-150-0-1500-full_array}
+
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-520}
   \caption{Arrow plots of our stadium shape}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/time-map-NflD-stad-25-600-200-0-1500-full_array}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/plots/time-map-NflD-stad-25-400-150-0-1500-full_array}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/NflD-time-map}
   \caption{Time map plots of our stad shape}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-1850-1850-9500-1500-full_array}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-2500-2500-9500-1500-full_array}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-1860-2860-9400-1500-full_array}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/plots/time-map-NflD-randst-25-2300-3200-9400-1500-full_array}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/NflD-time-map}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/NflD-time-map}
   \caption{Time map plots of our randst shape}

### 2014-08-21 paper/plot-arrow-ave.py

@@ -14,6 +14,7 @@ import imp
 #load = imp.load_source('load', 'pyplots/file_loader.py')
 import math
 import matplotlib.gridspec as gridspec
+import re
 
 #create data objects (see file_loader.py)
 
@@ -28,17 +29,24 @@ protein_name = "NflD"
 # input_end_time = float(f_param7)
 #end_time = int(input_end_time - input_end_time%10)
 
-arg_set = ["randst-0.25-18.50-18.50-95.00-15.00",
-           "randst-0.25-18.60-28.60-94.00-15.00"]
+arg_set = ["0.25-18.50-18.50-95.00-15.00-full_array",
+           "0.25-18.60-28.60-94.00-15.00-full_array"]
 
-bound_times = ["300","1500","300","1100"]
+bound_times = ["500","540","500","540"]
 
 arrow_files = []
 contour_values = []
 for i in range(len(arg_set)):
-    arrow_files += ['./data/shape-randst/plots/ave-time/maxima-arrowNflD-'+arg_set[i]+'-full_array.dat']
-    contour_values += ['./data/shape-randst/plots/ave-time/contour-values-'+bound_times[i*2]+'-' \
-        +bound_times[i*2+1]+'-NflD-'+arg_set[i]+'-full_array.dat']
+    job_string = "data/shape-randst/%s/" % (arg_set[i])
+    p = re.compile('[.]')
+    job_string = p.sub('_',job_string)
+    arrow_files += [job_string +'ave-time/ave-time-arrow-'+str(int(bound_times[i*2]))+'-'+protein_name+'.dat']
+    contour_values += [ job_string +'ave-time/contour-values-' + protein_name +'-'+ str(int(bound_times[i*2]))+'-' \
+                            +str(bound_times[i*2+1])+'.dat']
+    print i
+    print arrow_files[i]
+    print contour_values[i]
+
 
 
 plt.figure(1)
@@ -107,7 +115,7 @@ for arg_num in range(len(arg_set)+2):
         # left  = 0.125  # the left side of the subplots of the figure
         # right = 0.9    # the right side of the subplots of the figure
 
-        a_data = a_data[int((start_time-300)/dump_time_step):int((end_time-start_time)/dump_time_step)]
+        a_data = a_data[int((start_time-float(bound_times[arg_num*2]))/dump_time_step):int((end_time-start_time)/dump_time_step)]
 
         last_time = a_data[0,0]
         for i in range(1,len(a_data[:,0])):

### 2014-08-21 pyplots/box_plot.py

@@ -10,7 +10,7 @@ import file_loader as load
 import matplotlib.patheffects
 from matplotlib.font_manager import FontProperties
 from mpl_toolkits.axes_grid.anchored_artists import AnchoredSizeBar
-
+import os
 
 ## WIP!!
 
@@ -31,15 +31,12 @@ from mpl_toolkits.axes_grid.anchored_artists import AnchoredSizeBar
 #boxName. returns list of protein counts at each time.
 #box-plot--p-0.50-0.50-0.00-0.00-15.00-exact.dat
 
+
 sim_type = load.sim_type
-if sim_type == "full_array":
-    sim_type = "-full_array"
-else:
-    sim_type = ""
 
 def returnData(boxName,proteinType):
     #open the data file, grab the line with the correct protein type and box partition, load it as a [string] (so we can use list comprehensions)
-    filename = '.' + job_string + 'box-plot.dat'
+    filename = job_string + 'box-plot.dat'
 
     with open(filename,"r") as boxData:
         proteinsOverTime = [line for line in boxData if (proteinType in line) and (boxName in line)]
@@ -110,7 +107,7 @@ def find_period(f):
     return (penultimate_min, lastmin)
 
 def main():
-    filename = '.' + job_string + 'box-plot.dat'
+    filename = job_string + 'box-plot.dat'
     print "loading ",filename
 
     with open(filename, "r") as boxData:
@@ -238,7 +235,7 @@ def main():
     sectionax = plt.subplot2grid((2,5), (0,4), colspan=1,rowspan=2)
 
     # first plot the section data...
-    filename = '.' + job_string + 'sections.dat'
+    filename = job_string + 'sections.dat'
     sectiondata = np.loadtxt(filename)
 
     def plot_sections(sectionax, sectiondata):
@@ -412,10 +409,18 @@ def main():
     plt.show()
     return 0
 
-job_string = "/data/shape-%s/%s-%s-%s-%s-%s%s/" % (load.f_shape,load.f_param1,load.f_param2,
+job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,load.f_param1,load.f_param2,
                                                    load.f_param3,load.f_param4,load.f_param5,sim_type)
+print job_string
+print sim_type
 p = re.compile('[.]')
 job_string = p.sub('_',job_string)
+
+dir_name = job_string + 'plots'
+
+if not os.path.exists(dir_name):
[…]

### 2014-08-21 pyplots/file_loader.py

@@ -68,11 +68,11 @@ def get_filenames(protein,sim_type,start_time,end_time):
         end_time = 10000
     for f_num in np.arange(start_time,end_time,dump_time_step):
         file_num = round(f_num/dump_time_step)
-        job_string = "/data/shape-%s/%s-%s-%s-%s-%s-%s/" % (f_shape,f_param1,f_param2,
+        job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (f_shape,f_param1,f_param2,
                                                             f_param3,f_param4,f_param5,sim_type)
         p = re.compile('[.]')
         job_string = p.sub('_',job_string)
-        fname = '.' + job_string + protein + '/movie-frame-%05d.dat'%(file_num)
+        fname = job_string + protein + '/movie-frame-%05d.dat'%(file_num)
         print fname
         if os.path.isfile(fname):
             dat_filenames.append(fname)
@@ -87,13 +87,17 @@ def get_filenames(protein,sim_type,start_time,end_time):
 
 #function for easier plot name printing. probably should be renamed itself.
 def print_string(plot_name,protein):
-    job_string = "/data/shape-%s/%s-%s-%s-%s-%s-%s/" % (f_shape,sys.argv[2],sys.argv[3],sys.argv[4],sys.argv[5],sys.argv[6],sim_type)
+    job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (f_shape,sys.argv[2],sys.argv[3],sys.argv[4],sys.argv[5],sys.argv[6],sim_type)
     p = re.compile('[.]')
     job_string = p.sub('_',job_string)
+    dir_name = job_string + 'plots'
+    if not os.path.exists(dir_name):
+        print "making directory "+dir_name+" because doesnt exist"
+        os.makedirs(dir_name)
     filename = ''
     if (protein == ''):
-        filename = '.' + job_string + 'plots/' + plot_name + '.pdf'
+        filename = job_string + 'plots/' + plot_name + '.pdf'
     else:
-        filename = '.' + job_string + 'plots/' + protein + '-' + plot_name + '.pdf'
+        filename = job_string + 'plots/' + protein + '-' + plot_name + '.pdf'
     print "printing to ",filename
     return filename

### 2014-08-21 pyplots/image_plot.py

@@ -85,6 +85,8 @@ cax = divider.append_axes("right", "3%", pad="1%")
 cbar = plt.colorbar(cax=cax,ticks=[0,maxval])
 cbar.ax.set_yticklabels(['0', 'max'])
 
+
 #plt.colorbar(ticks=[])
 plt.tight_layout()
+print load.print_string("image-plot","")
 plt.savefig(load.print_string("image-plot",""))

### 2014-08-21 pyplots/plot-ave-arrow.py

@@ -22,10 +22,11 @@ f_param7 = sys.argv[9]
 
 #create data objects (see file_loader.py)
 
+print "starting plot ave arrow"
 dx =0.05
 dump_time_step = 0.5
 protein_name = "NflD"
-job_string = "/data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,f_param1,f_param2,
+job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,f_param1,f_param2,
                                                     f_param3,f_param4,dens_factor,sim_type)
 p = re.compile('[.]')
 job_string = p.sub('_',job_string)
@@ -33,9 +34,10 @@ job_string = p.sub('_',job_string)
 start_time = float(f_param6)
 input_end_time = float(f_param7)
 end_time = 0
-for end in np.arange(int(start_time+20),int(input_end_time),20):
-    contour_values = '.'+ job_string +'ave-time/contour-values-' + protein_name +'-'+ str(int(start_time))+'-' \
+for end in np.arange(int(start_time+20),int(input_end_time+20),20):
+    contour_values = job_string +'ave-time/contour-values-' + protein_name +'-'+ str(int(start_time))+'-' \
         +str(end)+'.dat'
+    print contour_values
     if os.path.isfile(contour_values):
         end_time = end
 
@@ -43,22 +45,18 @@ if end_time == 0:
     print "there are no contour files that work for these times!"
     exit(1)
 
-contour_values = '.'+ job_string +'ave-time/contour-values-' + protein_name +'-'+ str(int(start_time))+'-' \
+contour_values = job_string +'ave-time/contour-values-' + protein_name +'-'+ str(int(start_time))+'-' \
     +str(end_time)+'.dat'
 print "actually using end time of " + str(end_time) + " because that's the highest that exists"
 print contour_values
 
-arrow_file = '.'+ job_string +'ave-time/ave-time-arrow-'+str(int(start_time))+'-'+str(protein_name)+'.dat'
+arrow_file = job_string +'ave-time/ave-time-arrow-'+str(int(start_time))+'-'+str(protein_name)+'.dat'
 print arrow_file
 
 
 num = 0
 while (start_time + num/2 < end_time):
     num += 40
-    print end_time
-    print start_time
-    print num/2
-    print ""
 num -= 40
 
 print arrow_file
[…]

### 2014-08-21 pyplots/single-image-creation.py

@@ -33,9 +33,11 @@ job_string = p.sub('_',job_string)
 proteinList = ["nADP","nATP","ND","NDE","nE",]
 proteins = [0]*len(proteinList)
 
+
 for i in range(len(proteins)):
     directory = '.' + job_string + str(proteinList[i]) + '/images'
     print directory
+    print os.path.isdir(directory)
     if (not os.path.isdir(directory)):
         os.makedirs(directory)
 

### 2014-08-21 pyplots/single-image-plot.py

@@ -26,7 +26,7 @@ skip_times = 2 # only plot every skip_times of the snapshots (which are seperate
 start_time = float(f_param6)
 end_time = float(f_param7)
 
-job_string = "/data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,load.f_param1,load.f_param2,
+job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,load.f_param1,load.f_param2,
                                                    load.f_param3,load.f_param4,load.f_param5,sim_type)
 p = re.compile('[.]')
 job_string = p.sub('_',job_string)
@@ -56,7 +56,7 @@ for i in range(len(proteinList)):
 #generate a sequence of .png's for each file (printed time step). these will be used to create a gif.
     smeared_data = [0]*len(times)
     for j in range(len(times)):
-        image_data_file = '.' + job_string +str(proteinList[i])+'/images/single-'+str(times[j])+'.dat'
+        image_data_file = job_string +str(proteinList[i])+'/images/single-'+str(times[j])+'.dat'
         smeared_data[j] = np.loadtxt(image_data_file) #this is in microns green light at 500nm,
     dZ = smeared_data[0].shape[1]*1.05
     dY = smeared_data[0].shape[0]*2.00/skip_times

### 2014-08-21 pyplots/time-averaged-arrow.py

@@ -35,12 +35,19 @@ if (input_start_time > input_end_time):
     exit(1)
 
 
-job_string = "/data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,f_param1,f_param2,
+job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,f_param1,f_param2,
                                                     f_param3,f_param4,dens_factor,sim_type)
+
+p = re.compile('[.]')
+job_string = p.sub('_',job_string)
+dir_name = job_string + 'ave-time'
+
+if not os.path.exists(dir_name):
+    print "making directory "+dir_name+" because doesnt exist"
+    os.makedirs(dir_name)
+
 for i in range(0,20000):
-    p = re.compile('[.]')
-    job_string = p.sub('_',job_string)
-    fname = '.' + job_string + protein_name + '/movie-frame-%05d.dat'%(i)
+    fname = job_string + protein_name + '/movie-frame-%05d.dat'%(i)
 
     total_number_of_files += 1
     if (not os.path.isfile(fname)):
@@ -48,6 +55,8 @@ for i in range(0,20000):
         break
 if (input_end_time >= total_number_of_files*dump_time_step):
     print "For ", fname
+    print input_end_time
+    print total_number_of_files*dump_time_step
     print "This end_time is too great, there are only enough files to support a end_time less than ", total_number_of_files*dump_time_step
     exit(1)
 
@@ -58,7 +67,7 @@ def gaussian_smear(data,wavelength,protein):
     sigma = .21*wavelength/N_A #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
     print "sigma ",sigma
     dis = int(3*sigma/0.05) #for now
-    arrow_file = '.'+ job_string +'ave-time/ave-time-arrow-'+str(int(input_start_time))+'-'+str(protein)+'.dat'
+    arrow_file = job_string +'ave-time/ave-time-arrow-'+str(int(input_start_time))+'-'+str(protein)+'.dat'
     print arrow_file
     p_file = open(arrow_file,'w')
     p_file.close()
@@ -93,7 +102,7 @@ def gaussian_smear(data,wavelength,protein):
         p_file.write('%g %g %g %g\n'%(input_start_time+num*dump_time_step,maxima,max_x,max_y))
         p_file.close()
         if (num%40 == 0 and num > 1):
[…]

### 2014-08-21 pyplots/time_map.py

@@ -28,11 +28,11 @@ def gaussian_smear(data,wavelength):
 proteinList = ['NflD']
 
 for protein in proteinList:
-    job_string = "/data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,load.f_param1,load.f_param2,
+    job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,load.f_param1,load.f_param2,
                                                        load.f_param3,load.f_param4,load.f_param5,load.sim_type)
     p = re.compile('[.]')
     job_string = p.sub('_',job_string)
-    data_filename = '.' + job_string + protein + '/' + 'time-map.dat'
+    data_filename = job_string + protein + '/' + 'time-map.dat'
     data_file = np.loadtxt(data_filename)
 
     print "starting time_map.p for ",data_filename

### 2014-08-21 run_simulations.sh

@@ -1,16 +1,19 @@
 #!/bin/bash
 
-srun --job-name="sim p 3.00 0.50 15.00 full" ./protein_microscopy p 3.00 0.50 0.00 0.00 15.00 1.00 full_array -dump &
-srun --job-name="sim p 3.00 0.50 15.00 exact" ./protein_microscopy p 3.00 0.50 0.00 0.00 15.00 1.00 exact -dump &
+# srun --job-name="sim p 3.00 0.50 15.00 full" ./protein_microscopy p 3.00 0.50 0.00 0.00 15.00 1.00 full_array -dump &
+# srun --job-name="sim p 3.00 0.50 15.00 exact" ./protein_microscopy p 3.00 0.50 0.00 0.00 15.00 1.00 exact -dump &
 
-srun --job-name="sim randst 0.25 18.50 18.50 95.00 15.00 1.35 full" ./protein_microscopy randst 0.25 18.50 18.50 95.00 15.00 1.35 full_array -dump &
-srun --job-name="sim randst 0.25 18.50 18.50 95.00 15.00 1.35 exact" ./protein_microscopy randst 0.25 18.50 18.50 95.00 15.00 1.35 exact -dump &
+# srun --job-name="sim randst 0.25 18.50 18.50 95.00 15.00 1.35 full" ./protein_microscopy randst 0.25 18.50 18.50 95.00 15.00 1.35 full_array -dump &
+# srun --job-name="sim randst 0.25 18.50 18.50 95.00 15.00 1.35 exact" ./protein_microscopy randst 0.25 18.50 18.50 95.00 15.00 1.35 exact -dump &
 
-srun --job-name="sim randst 0.25 18.60 28.60 94.00 15.00 1.53 full" ./protein_microscopy randst 0.25 18.60 28.60 94.00 15.00 1.53 full_array -dump &
-srun --job-name="sim randst 0.25 18.60 28.60 94.00 15.00 1.53 exact" ./protein_microscopy randst 0.25 18.60 28.60 94.00 15.00 1.53 exact -dump &
+# srun --job-name="sim randst 0.25 18.60 28.60 94.00 15.00 1.53 full" ./protein_microscopy randst 0.25 18.60 28.60 94.00 15.00 1.53 full_array -dump &
[…]

### 2014-08-26 paper/paper.tex
added deterministic data to plot-arrow-ave Tested everything on wentworth.

@@
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-In general we have found that the deterministic simulations of the
-protein reaction sequence discussed above results in robust
-oscillatory behavoir of polar selection and oscillation in a wide
-variety of cell shapes.  On the other hand, the stochastic simulations
-show back and forth behavoir that breaks down in more assymetric
-shapes with larger sizes, which is similar to what Mannik has observed
-experimentally.
+We have inspected movies made
+We have found that the deterministic simulations of the protein
+reaction sequence discussed above results in robust oscillatory
+behavoir of polar selection and oscillation in a wide variety of cell
+shapes.  This differs with Mannik's experimental findings that show
+much less regular behavoir, with a large variation in the location of
+maxima.  On the other hand, our stochastic simulations show irregular
+behavoir in the irregular shapes and more regular, pole to pole
+oscillations in the pill and stadium shaped cells.
+
+Figure \ref{randst-plot-ave} shows a comparison of irregular shapes
+simulated with the stochastic method and with the deterministic
+method, along with a plot taken from Mannik showing the location of
+sequential MinD maxima in the experimental cells.  Like Manniks, the
+tips of the arrows in our plots show subsequent maxima, and the data
+overlays a color plot of time averaged MinD concentration.  These
+plots illustrate the adequacy of the stochastic method and inadequacy
+of the deterministic one.  The stochastic plots show similar random behavoir to Manniks
 
 \begin{figure}
-
   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-520}
@@
   \caption{Arrow plots of our randst shape}
-  \label{stadium-arrow}
+  \label{randst-plot-ave}
 \end{figure}

### 2014-08-26 paper/plot-arrow-ave.py

@@ -30,9 +30,11 @@ protein_name = "NflD"
 #end_time = int(input_end_time - input_end_time%10)
 
 arg_set = ["0.25-18.50-18.50-95.00-15.00-full_array",
-           "0.25-18.60-28.60-94.00-15.00-full_array"]
+           "0.25-18.60-28.60-94.00-15.00-full_array",
+           "0.25-18.50-18.50-95.00-15.00-exact",
+           "0.25-18.60-28.60-94.00-15.00-exact"]
 
-bound_times = ["500","540","500","540"]
+bound_times = ["500","1500","500","540","500","520","500","520"]
 
 arrow_files = []
 contour_values = []
@@ -67,13 +69,15 @@ for i in range(len(contour_values)):
 if len(contour_values) > 1:
     hts += [hts[1]]
 
-gs = gridspec.GridSpec(2,2)
+gs = gridspec.GridSpec(len(arg_set)+2,2)
+plt.subplots_adjust(wspace=.01)#left=.3,right=.7)
+#gs.tight_layout(w_pad=.2)
 
 for arg_num in range(len(arg_set)+2):
 #    plt.subplot2grid((len(arg_set)+1,1),(arg_num,0),aspect='equal')
     #gs_in = gridspec.GridSpec(arg_num,0)
     #gs_in.update(left=.3+arg_num*.1,right=.8)
-    if arg_num == 2:
+    if arg_num == len(arg_set):
         plt.subplot(gs[0,0],aspect='equal')
         m1=mpimg.imread('mannik-1.png')
         dx = 7.0/380
@@ -85,7 +89,7 @@ for arg_num in range(len(arg_set)+2):
         y1off = 1.7#1.7 and there was only one yoff, not two
         plt.contourf(x1-xcenter, y1-y1off, m1[:,:,1], levels=[0, 0.9], colors=('r', 'w'))
         plt.contourf(x1-xcenter, y1-y1off, m1[:,:,0], levels=[0, 0.9], colors=('k', 'w'))
-    elif arg_num == 3:
+    elif arg_num == len(arg_set)+1:
         plt.subplot(gs[0,1],aspect='equal')
         m1=mpimg.imread('mannik-2.png')
         dx = 7.0/380
@@ -98,22 +102,12 @@ for arg_num in range(len(arg_set)+2):
[…]

### 2014-08-28 paper/paper.tex
added some plots to the paper and altered pretty much every plot in the paper Tested everything on quipu.

@@
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-We have inspected movies made
-We have found that the deterministic simulations of the protein
-reaction sequence discussed above results in robust oscillatory
-behavoir of polar selection and oscillation in a wide variety of cell
-shapes.  This differs with Mannik's experimental findings that show
-much less regular behavoir, with a large variation in the location of
-maxima.  On the other hand, our stochastic simulations show irregular
-behavoir in the irregular shapes and more regular, pole to pole
-oscillations in the pill and stadium shaped cells.
+We have made and studied movies that show the change in concentration
+of MinD over time We have found that the deterministic simulations of
+the protein reaction sequence discussed above results in robust
+oscillatory behavoir of polar selection and oscillation in a wide
+variety of cell shapes.  This differs with Mannik's experimental
+findings that show much less regular behavoir, with a large variation
+in the location of maxima.  On the other hand, our stochastic
+simulations show irregular behavoir in the irregular shapes and more
+regular, pole to pole oscillations in the pill and stadium shaped
+cells.
 
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-520}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
   \caption{Arrow plots of our stadium shape}
   \label{stadium-arrow}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
+  \caption{Arrow plots of our pill shape}
+  \label{pill-arrow}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
+  \caption{box plots of Mannik's shapes}
+  \label{box-mannik}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
+  \caption{box plots of stadium shape}
+  \label{box-stadium}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/NflD-time-map}
+  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/NflD-time-map}
   \caption{Time map plots of our randst shape}

### 2014-08-28 paper/plot-arrow-ave.py

@@ -34,7 +34,8 @@ arg_set = ["0.25-18.50-18.50-95.00-15.00-full_array",
            "0.25-18.50-18.50-95.00-15.00-exact",
            "0.25-18.60-28.60-94.00-15.00-exact"]
 
-bound_times = ["500","1500","500","540","500","520","500","520"]
+bound_times = ["500","1900","500","980","500","1800","500","1400"]
+arrow_cutoffs = [3.0/5.0,2.5/5.0,2.0/5.0,3.0/5.0]
 
 arrow_files = []
 contour_values = []
@@ -56,27 +57,14 @@ plt.figure(1)
 #plt.clf()
 print "len",len(arg_set)
 
-# half_width = float(c_data.shape[1]/max_width)/2.0
-# print half_width
-#gs.update(left=.5-half_width,right=.5+half_width)
-#plt.title("%f"%half_width)
 
-hts = []
 for i in range(len(contour_values)):
     c_data = np.loadtxt(contour_values[i])
-    hts += [float(c_data.shape[1])]
-
-if len(contour_values) > 1:
-    hts += [hts[1]]
 
 gs = gridspec.GridSpec(len(arg_set)+2,2)
 plt.subplots_adjust(left=.1,right=.9,top=1.0,bottom=-.9)#left=.3,right=.7)
-#gs.tight_layout(w_pad=.2)
 
 for arg_num in range(len(arg_set)+2):
-#    plt.subplot2grid((len(arg_set)+1,1),(arg_num,0),aspect='equal')
-    #gs_in = gridspec.GridSpec(arg_num,0)
-    #gs_in.update(left=.3+arg_num*.1,right=.8)
     if arg_num == len(arg_set):
         plt.subplot(gs[0,0],aspect='equal')
         m1=mpimg.imread('mannik-1.png')
@@ -111,6 +99,8 @@ for arg_num in range(len(arg_set)+2):
 
         a_data = a_data[int((start_time-float(bound_times[arg_num*2]))/dump_time_step):int((end_time-start_time)/dump_time_step)]
 
+        print a_data
+
         last_time = a_data[0,0]
         for i in range(1,len(a_data[:,0])):
             if (a_data[i,0] <= last_time):
@@ -121,7 +111,7 @@ for arg_num in range(len(arg_set)+2):
                 exit(0)
 
         time_max = np.max(c_data)
-        arrow_cutoff = 3.0*(np.max(a_data[:,1]))/5.0
[…]

### 2014-08-28 pyplots/box_plot.py

@@ -1,7 +1,7 @@
 from __future__ import division
 import numpy as np
 import matplotlib
-matplotlib.use("Agg")
+#matplotlib.use("Agg")
 import matplotlib.pyplot as plt
 import sys
 import pylab
@@ -176,8 +176,8 @@ def main():
 
     #begin messy code (to deal with matplotlib) - don't judge me
 
-    start_time_as_frac_of_ten = float(load.f_param6)
-    end_time_as_frac_of_ten = float(load.f_param7)
+    start_time_as_frac_of_ten = float(sys.argv[8])
+    end_time_as_frac_of_ten = float(sys.argv[9])
     tot_time = float(len(plotCurveList_D[0]))*box_time_step
     start = int(tot_time*start_time_as_frac_of_ten/10.0/box_time_step)
     end = int(tot_time*end_time_as_frac_of_ten/10.0/box_time_step)
@@ -375,6 +375,8 @@ def main():
 
     print load.print_string("box-plot_D","")
     plt.savefig(load.print_string("box-plot_D",""))
+    #plt.show()
+
     plt.figure()
 
     #f, (bax,sectionax) = plt.subplots(1, 2)
@@ -405,8 +407,6 @@ def main():
     bax.set_ylabel("Fraction of proteins")
     bax.legend(plotNameList_E,bbox_to_anchor=(0.3,-0.05,1.0,1.0),loc="lower right",prop={'size':8}).draw_frame(False)
     plt.savefig(load.print_string("box-plot_E",""))
-
-    plt.show()
     return 0
 
 job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,load.f_param1,load.f_param2,

### 2014-08-28 pyplots/plot-ave-arrow.py

@@ -1,7 +1,7 @@
 from __future__ import division
 import numpy as np
 import matplotlib
-matplotlib.use('Agg')
+#matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 import os
 import sys
@@ -31,13 +31,19 @@ job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,f_param1,f_param
 p = re.compile('[.]')
 job_string = p.sub('_',job_string)
 
+dir_name = job_string + 'plots'
+if not os.path.exists(dir_name):
+    print "making directory "+dir_name+" because doesnt exist"
+    os.makedirs(dir_name)
+
+
 start_time = float(f_param6)
 input_end_time = float(f_param7)
 end_time = 0
+contour_values = ""
 for end in np.arange(int(start_time+20),int(input_end_time+20),20):
     contour_values = job_string +'ave-time/contour-values-' + protein_name +'-'+ str(int(start_time))+'-' \
         +str(end)+'.dat'
-    print contour_values
     if os.path.isfile(contour_values):
         end_time = end
 
@@ -45,36 +51,17 @@ if end_time == 0:
     print "there are no contour files that work for these times!"
     exit(1)
 
-contour_values = job_string +'ave-time/contour-values-' + protein_name +'-'+ str(int(start_time))+'-' \
-    +str(end_time)+'.dat'
 print "actually using end time of " + str(end_time) + " because that's the highest that exists"
 print contour_values
 
 arrow_file = job_string +'ave-time/ave-time-arrow-'+str(int(start_time))+'-'+str(protein_name)+'.dat'
 print arrow_file
 
-
-num = 0
-while (start_time + num/2 < end_time):
-    num += 40
-num -= 40
-
-print arrow_file
-print contour_values
-
 c_data = np.loadtxt(contour_values)
-print os.path.isfile(arrow_file)
 a_data = np.loadtxt(arrow_file)
 
-print a_data
-print "this ",a_data[:,0]
-print len(a_data[:,0])
-
-print "hello",str((end_time-start_time)*dump_time_step)
-a_data = a_data[0:int((end_time-start_time)/dump_time_step)]
-
-print a_data[:,0]
-print len(a_data[:,0])
+print "here!!! ",contour_values
[…]

### 2014-08-28 pyplots/single-image-creation.py

@@ -59,11 +59,10 @@ for i in range(len(proteins)):
 def gaussian_smear(data,wavelength):
     new = np.zeros_like(data)
     print "here ",new.shape[0]
-    n_sin_theta = 1.5
-    #sigma below is tha Abbe resolution.  n is the diffraction of the medium, sin_theta the aperture angle
-    #So far I've wiki'd the guassian form of the Airy disk for this
-    sigma = wavelength/2.0/n_sin_theta #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
-    dis = int(3.5*sigma/0.05) #for now
+    N_A = 1.3
+    sigma = .21*wavelength/N_A #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+    print "new way sigma ",sigma
+    dis = int(3*sigma/0.05) #for now
     for num in range(new.shape[0]):
         print "num ",num," of ",new.shape[0]-1
         for x in range(new.shape[1]):
@@ -86,7 +85,7 @@ times  = np.arange(float(start_time),float(end_time),dump_time_step)
 
 for i in range(len(proteins)):
     print proteinList[i]
-    smeared_data = gaussian_smear(proteins[i].dataset,.6) #this is in microns green light at 500nm,
+    smeared_data = gaussian_smear(proteins[i].dataset,.509) #this is in microns green light at 500nm,
     for j in range(len(times)):
         image_data_file = '.' + job_string +str(proteinList[i])+'/images/single-'+str(times[j])+'.dat'
         p_file = open(image_data_file,'w')

### 2014-08-28 pyplots/time-averaged-arrow.py

@@ -75,7 +75,6 @@ def gaussian_smear(data,wavelength,protein):
     last_max_y = 0
     for num in range(data.shape[0]):
         total_proteins = 0
-        total_light = 0
         max_data = np.zeros_like(data[0])
         print "num ",num
         for x in range(new.shape[0]):
@@ -85,9 +84,7 @@ def gaussian_smear(data,wavelength,protein):
                     for j in np.arange(-dis,dis,1):
                         if (x+i >= 0 and x+i < new.shape[0]-1 and y+j >= 0 and y+j < new.shape[1]-1):
                             new[x+i,y+j] += data[num,x,y]*math.exp( -(i*i+j*j)*.05*.05/2.0/sigma/sigma )
-                            total_light += new[x+i,y+j]
                             max_data[x+i,y+j] += data[num,x,y]*math.exp( -(i*i+j*j)*.05*.05/2.0/sigma/sigma )
-        print "total proteins = ",total_light/(num+1)
         print "total proteins = ",total_proteins
         maxima = 0
         max_x = 0

### 2014-08-28 paper/paper.tex
added captions to paper, added scale bar to plot-arrow-ave Tested everything on quipu.

@@
 
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/paper-arrow-plot}
-%%   \caption{Arrow plots for our simulation and mannik's experimental}
-%%   \label{arrow-compare-mannik}
-%% \end{figure}
+\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
+We have made and studied different plots and movies that show the
+change in concentration of MinD over time We have found that the
+deterministic simulations of the protein reaction sequence discussed
+above results in robust oscillatory behavoir of polar selection and
+oscillation in a wide variety of cell shapes.  This differs with
+Mannik's experimental findings that show much less regular behavoir,
+with a large variation in the location of maxima.  On the other hand,
+our stochastic simulations show irregular behavoir in the irregular
+shapes and more regular, pole to pole oscillations in the pill and
+stadium shaped cells.
 
-\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-We have made and studied movies that show the change in concentration
-of MinD over time We have found that the deterministic simulations of
-the protein reaction sequence discussed above results in robust
-oscillatory behavoir of polar selection and oscillation in a wide
-variety of cell shapes.  This differs with Mannik's experimental
-findings that show much less regular behavoir, with a large variation
-in the location of maxima.  On the other hand, our stochastic
-simulations show irregular behavoir in the irregular shapes and more
-regular, pole to pole oscillations in the pill and stadium shaped
-cells.
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{../paper/plot-ave}
+  \caption{Arrows depicting global maxima in space and local maxima in
+    time overlayed on color plots of time averaged total MinD density.
+    At this point the data is over varying amounts of time but its all
+    roughly 1000 seconds\fixme{fix this}.  The top row shows plots
+    published by Mannik of the MinD maxima behavoir and the bottom two
+    rows show our pancake shapes that are designed to have the same
+    shape.  The middle row shows results from the stochastic
+    simulation and the bottom shows results from the deterministic.
+    We can see that the stochastic method shows behavoir that is
+    similar to experiment while the deterministic method shows
+    maximization that is too regular and robust.}
+  \label{randst-plot-ave}
+\end{figure}
 
@@
 method, along with a plot taken from Mannik showing the location of
-sequential MinD maxima in the experimental cells.  Like Manniks, the
+sequential MinD maxima in the experimental cells.  Like Mannik's, the
 tips of the arrows in our plots show subsequent maxima, and the data
@@
   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
-  \caption{Arrow plots of our stadium shape}
-  \label{stadium-arrow}
-\end{figure}
-
-\begin{figure}
   \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
-  \caption{Arrow plots of our pill shape}
-  \label{pill-arrow}
+  \caption{Arrows depicting global maxima in space and local maxima in
+    time overlayed on color plots of time averaged total MinD
+    density.\fixme{how much of time of data is shown?}.  Although
+    there is variation in the specific location of maxima on each edge
+    of the cell, the behavoir for both of these regular shapes is
+    robust and exhibits a back and forth oscillatory manner.  The
+    wildtype pill shape behavoir matches well with experiment.
+    Regular pancake shapes have not been observed experimentally, but
+    our stochastic simulations would suggest that they would exhibit
+    regular robust oscillations similar to the pill shapes.  This is
+    in contrast to the behavoir of Mannik cells seen in
+    Figure~{randst-plot-ave}}
+  \label{arrow-pill-stadium}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
-  \caption{box plots of Mannik's shapes}
+  \caption{A comparison of our box plots that show a disparity between
+    the behavoir of the stochastic and deterministic simulations in
+    our Mannik cells.  The deterministic show a regular, robust
+    oscillatory behavoir between the two ends of the cell. The
+    stochastic simulation do show a general back and forth tendency
+    between two ends of the cell, but it is not robust and tends to
+    break down.}
   \label{box-mannik}
@@
   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
-  \caption{box plots of stadium shape}
+  \caption{A comparison of our box plots that show the similarity
+    between the stadium shapes simulated stochastically and
+    deterministically.  Both show regular oscillatory maxima with
+    similar periods.  This is in contrast to our boxpplot comparison
+    of one of the Mannik shapes in Figure~\ref{box-mannik}}
   \label{box-stadium}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../paper/plot-ave}
-  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1500-95-stoch}
-  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-1850-95-stoch}
-  %% \includegraphics[width=\columnwidth]{../data/shape-randst/plots/arrow-2500-95-stoch}
-  \caption{Arrow plots of our randst shape}
-  \label{randst-plot-ave}
 \end{figure}

### 2014-08-28 paper/plot-arrow-ave.py

@@ -1,7 +1,7 @@
 from __future__ import division
 import numpy as np
 import matplotlib
-matplotlib.use('Agg')
+#matplotlib.use('Agg')
 import matplotlib.pyplot as plt
 from matplotlib.font_manager import FontProperties
 import matplotlib.patheffects
@@ -46,16 +46,12 @@ for i in range(len(arg_set)):
     arrow_files += [job_string +'ave-time/ave-time-arrow-'+str(int(bound_times[i*2]))+'-'+protein_name+'.dat']
     contour_values += [ job_string +'ave-time/contour-values-' + protein_name +'-'+ str(int(bound_times[i*2]))+'-' \
                             +str(bound_times[i*2+1])+'.dat']
-    print i
-    print arrow_files[i]
-    print contour_values[i]
 
 
 
 plt.figure(1)
 
 #plt.clf()
-print "len",len(arg_set)
 
 
 for i in range(len(contour_values)):
@@ -66,12 +62,12 @@ plt.subplots_adjust(left=.1,right=.9,top=1.0,bottom=-.9)#left=.3,right=.7)
 
 for arg_num in range(len(arg_set)+2):
     if arg_num == len(arg_set):
+        gs.update(wspace=0)
         plt.subplot(gs[0,0],aspect='equal')
         m1=mpimg.imread('mannik-1.png')
-        #dx = 7.0/380
         print "shape, ",m1.shape[1]
-        y1 = -dx*np.arange(0, m1.shape[0])
-        x1 = dx*np.arange(0, m1.shape[1])
+        y1 = -np.arange(0, m1.shape[0])
+        x1 = np.arange(0, m1.shape[1])
         x1, y1 = np.meshgrid(x1, y1)
         xcenter = x1[m1[:,:,0] > 0].mean()
         y1off = 1.7#1.7 and there was only one yoff, not two
@@ -80,17 +76,27 @@ for arg_num in range(len(arg_set)+2):
     elif arg_num == len(arg_set)+1:
         plt.subplot(gs[0,1],aspect='equal')
         m1=mpimg.imread('mannik-2.png')
-        dx = 7.0/380
         print m1.shape[1]
-        y1 = -dx*np.arange(0, m1.shape[0])
-        x1 = dx*np.arange(0, m1.shape[1])
+        y1 = -np.arange(0, m1.shape[0])
+        x1 = np.arange(0, m1.shape[1])
         x1, y1 = np.meshgrid(x1, y1)
[…]

### 2014-08-28 paper/paper.tex
wrote text in Mannik and stadium shape section Tested everything on quipu.

@@
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-We have made and studied different plots and movies that show the
-change in concentration of MinD over time We have found that the
+We have made and studied different types of plots and movies that show
+the change in concentration of MinD over time. We have found that the
 deterministic simulations of the protein reaction sequence discussed
@@
 shapes and more regular, pole to pole oscillations in the pill and
-stadium shaped cells.
+stadium shaped cells, agreeing well with Mannik's experimental
+findings.
+
+Figure~{arrow-pill-stadium} and Figure~{randst-plot-ave} show color
+plots of time-averaged MinD overlayed by arrows depicting sequential
+maxima that are global in space and local in time.  Our shapes that
+designed to look like Mannik cells show well the inadequacy of the
+deterministic method of simulation and conversely the accuracy of the
+stochastic method.  The stochastic method movies (and arrow plots of
+Figure~{randst-plot-ave}) show irregular location of maxima that is
+similar to what is observed experimentally by Mannik. There is a
+general bias towards back and forth behavoir, which can be seen in the
+box plots of Figure~{box-mannik}, but the behavoir is irregular and
+the location of the maxima vary a significant amount.  On the other
+hand, the deterministic simulations show behavoir that is much too
+regular, exhibiting locations of maxima that do not vary.  The
+deterministic method is seen to be inadequate.
 
@@
     time overlayed on color plots of time averaged total MinD density.
-    At this point the data is over varying amounts of time but its all
-    roughly 1000 seconds\fixme{fix this}.  The top row shows plots
-    published by Mannik of the MinD maxima behavoir and the bottom two
-    rows show our pancake shapes that are designed to have the same
-    shape.  The middle row shows results from the stochastic
-    simulation and the bottom shows results from the deterministic.
-    We can see that the stochastic method shows behavoir that is
-    similar to experiment while the deterministic method shows
-    maximization that is too regular and robust.}
+    A density threshold is chosen and only maxima above this threshold
+    are shown. The plots serve to illistrate what is observed in our
+    movies.  At this point the data is over varying amounts of time
+    but its all roughly 1000 seconds\fixme{fix this}.  The top row
+    shows plots published by Mannik of the MinD maxima behavoir and
+    the bottom two rows show our pancake shapes that are designed to
+    have the same shape.  The middle row shows results from the
+    stochastic simulation and the bottom shows results from the
+    deterministic.  We can see that the stochastic method shows
+    behavoir that is similar to experiment while the deterministic
+    method shows maximization that is too regular and robust.}
   \label{randst-plot-ave}
-\end{figure}
-
-Figure \ref{randst-plot-ave} shows a comparison of irregular shapes
-simulated with the stochastic method and with the deterministic
-method, along with a plot taken from Mannik showing the location of
-sequential MinD maxima in the experimental cells.  Like Mannik's, the
-tips of the arrows in our plots show subsequent maxima, and the data
-overlays a color plot of time averaged MinD concentration.  These
-plots illustrate the adequacy of the stochastic method and inadequacy
-of the deterministic one.  The stochastic plots show similar random behavoir to Manniks
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
-  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
-  \caption{Arrows depicting global maxima in space and local maxima in
-    time overlayed on color plots of time averaged total MinD
-    density.\fixme{how much of time of data is shown?}.  Although
-    there is variation in the specific location of maxima on each edge
-    of the cell, the behavoir for both of these regular shapes is
-    robust and exhibits a back and forth oscillatory manner.  The
-    wildtype pill shape behavoir matches well with experiment.
-    Regular pancake shapes have not been observed experimentally, but
-    our stochastic simulations would suggest that they would exhibit
-    regular robust oscillations similar to the pill shapes.  This is
-    in contrast to the behavoir of Mannik cells seen in
-    Figure~{randst-plot-ave}}
-  \label{arrow-pill-stadium}
 \end{figure}
@@
 
+Our simulations of pill shapes show behavoir that is once again well
+matched by experiment, but this time the deterministic method seems to
+be as aduaquet as the stochastic in giving accurate results.  The
+experimental cells show regular back and forth behavoir, as do both
+simulations.  In this case the natural bias of the deterministic
+method towards robustness and regularity works in its favor.
+
+Judging that at this point that we have a fair idea of how our two
+methods compare in terms of experimental acuracy, we are intersted to
+investigate the limits of the break down of regular activity, by
+simulating large, regular, 'stadium' shapes.  These shapes have the
+flattened, pancake like form of our irregularly shaped cells, but from
+the top down they look as pills do. In two dimensions they are
+composed of a rectangle with two half ellipse connected on either end.
+They are also made to have a large volume similar to the Mannik
+shapes.
+
+We find that both the stochastic and the deterministic solutions show
+regular show back and forth behavoir in the stadium shaped cells, as
+can be seen Figure~{box-stadium}.  This suggests that it is the
+irregular shape of the Mannik cells,, not the size or their flattened
+nature, that causes these cells be exhibit irregularity in MinD
+oscillations.
+
 \begin{figure}
@@
 \end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
+  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
+  \caption{Arrows depicting global maxima in space and local maxima in
+    time overlayed on color plots of time averaged total MinD
+    density. A density threshold is chosen and only maxima above this
+    threshold are shown. The plots serve to illistrate what is
+    observed in our movies. \fixme{how much of time of data is
+      shown?}.  Although there is variation in the specific location
+    of maxima on each edge of the cell, the behavoir for both of these
+    regular shapes is robust and exhibits a back and forth oscillatory
+    manner.  The wildtype pill shape behavoir matches well with
+    experiment.  Regular pancake shapes have not been observed
+    experimentally, but our stochastic simulations would suggest that
+    they would exhibit regular robust oscillations similar to the pill
+    shapes.  This is in contrast to the behavoir of Mannik cells seen
+    in Figure~{randst-plot-ave}}
+  \label{arrow-pill-stadium}
+\end{figure}
+
+Figure \ref{randst-plot-ave} shows a comparison of irregular shapes
+simulated with the stochastic method and with the deterministic
+method, along with a plot taken from Mannik showing the location of
+sequential MinD maxima in the experimental cells.  Like Mannik's, the
+tips of the arrows in our plots show subsequent maxima, and the data
+overlays a color plot of time averaged MinD concentration.  These
+plots illustrate the adequacy of the stochastic method and inadequacy
+of the deterministic one.  The stochastic plots show similar random behavoir to Manniks
 

### 2014-08-29 paper/paper.tex
edited text in Mannik section and adjusted size of paper/plot-arrow Tested everything on quipu.

@@
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-We have made and studied different types of plots and movies that show
-the change in concentration of MinD over time. We have found that the
-deterministic simulations of the protein reaction sequence discussed
-above results in robust oscillatory behavoir of polar selection and
-oscillation in a wide variety of cell shapes.  This differs with
-Mannik's experimental findings that show much less regular behavoir,
-with a large variation in the location of maxima.  On the other hand,
-our stochastic simulations show irregular behavoir in the irregular
-shapes and more regular, pole to pole oscillations in the pill and
-stadium shaped cells, agreeing well with Mannik's experimental
-findings.
+We have made and studied plots and movies of the MinD in a number of
+simulated cell shapes and sizes. We have found that the deterministic
+simulations of the protein reaction sequence discussed above results
+in robust oscillatory behavoir of polar selection and oscillation in
+not only symmetrical shapes, such as the wild type pill shape, but
+also in very assymetrical, flatttened cells, such as those studied by
+Mannik.  This differs with Mannik's experimental findings that show
+much less regular behavoir, with a large variation in the location of
+maxima.  On the other hand, our stochastic simulations show both
+irregular behavoir in the assymetrical shapes and more regular, pole
+to pole oscillations in the symmetric pill and stadium shaped cells,
+agreeing well with Mannik's experimental findings.
 
@@
 maxima that are global in space and local in time.  Our shapes that
-designed to look like Mannik cells show well the inadequacy of the
+are designed to look like Mannik cells show well the inadequacy of the
 deterministic method of simulation and conversely the accuracy of the
-stochastic method.  The stochastic method movies (and arrow plots of
+stochastic method.  Our stochastic method movies (and arrow plots of
 Figure~{randst-plot-ave}) show irregular location of maxima that is
@@
 hand, the deterministic simulations show behavoir that is much too
-regular, exhibiting locations of maxima that do not vary.  The
-deterministic method is seen to be inadequate.
+regular when compared with experiment, exhibiting locations of maxima
+that do not vary.  The deterministic method is seen to be inadequate.
 
@@
 Judging that at this point that we have a fair idea of how our two
-methods compare in terms of experimental acuracy, we are intersted to
+methods compare in terms of experimental acuracy, we are interested to
 investigate the limits of the break down of regular activity, by
 simulating large, regular, 'stadium' shapes.  These shapes have the
-flattened, pancake like form of our irregularly shaped cells, but from
-the top down they look as pills do. In two dimensions they are
-composed of a rectangle with two half ellipse connected on either end.
-They are also made to have a large volume similar to the Mannik
-shapes.
+flattened, pancake like form of the assymetric cells, but from the top
+down they look as pills do. In two dimensions they are composed of a
+rectangle with two half ellipse connected on either end.  They are
+also made to have a large volume that is similar to the Mannik shapes.
 

### 2014-08-29 paper/plot-arrow-ave.py

@@ -34,8 +34,8 @@ arg_set = ["0.25-18.50-18.50-95.00-15.00-full_array",
            "0.25-18.50-18.50-95.00-15.00-exact",
            "0.25-18.60-28.60-94.00-15.00-exact"]
 
-bound_times = ["500","1900","500","980","500","1800","500","1400"]
-arrow_cutoffs = [3.0/5.0,2.5/5.0,2.0/5.0,3.0/5.0]
+bound_times = ["500","1400","500","980","500","1400","500","1400"]
+arrow_cutoffs = [2.4/5.0,2.4/5.0,2.2/5.0,3.0/5.0]
 
 arrow_files = []
 contour_values = []
@@ -86,22 +86,44 @@ for arg_num in range(len(arg_set)+2):
         plt.contourf(x1-xcenter, y1-y1off, m1[:,:,0], levels=[0, 0.9], colors=('k', 'w'))
     else:
         ax = plt.subplot(gs[int(arg_num/2)+1,arg_num%2],aspect='equal')
-        if arg_num == len(arg_set)-1 or arg_num == len(arg_set)-2:
+        if arg_num == len(arg_set)-2:
             ax.add_artist(AnchoredSizeBar(
                     ax.transData,
                     5, # length of the bar in the data reference
                     "5$\mu$", # label of the bar
                     # bbox_to_anchor=(0.,0.,1.,1.),
                     loc=8, # 'best', # location (lower right)
-                    borderpad=-1.8, sep=3, 
+                    borderpad=-1.8, sep=3,
                     frameon=False
                     ))
-
+        elif arg_num == len(arg_set)-1:
+            ax.add_artist(AnchoredSizeBar(
+                    ax.transData,
+                    6, # length of the bar in the data reference
+                    "6$\mu$", # label of the bar
+                    # bbox_to_anchor=(0.,0.,1.,1.),
+                    loc=8, # 'best', # location (lower right)
+                    borderpad=-1.8, sep=3,
+                    frameon=False
+                    ))
         print int(arg_num/2)+1,"",arg_num%2
-        c_data = np.loadtxt(contour_values[arg_num])
+        first_c_data = np.loadtxt(contour_values[arg_num])
         a_data = np.loadtxt(arrow_files[arg_num])
         start_time = float(bound_times[arg_num*2])
[…]

### 2014-08-29 paper/paper.tex
fixed figure reference in paper Tested everything on quipu.

@@
 
-Figure~{arrow-pill-stadium} and Figure~{randst-plot-ave} show color
+Figure~\ref{arrow-pill-stadium} and Figure~\ref{randst-plot-ave} show color
 plots of time-averaged MinD overlayed by arrows depicting sequential
@@
 stochastic method.  Our stochastic method movies (and arrow plots of
-Figure~{randst-plot-ave}) show irregular location of maxima that is
+Figure~\ref{randst-plot-ave}) show irregular location of maxima that is
 similar to what is observed experimentally by Mannik. There is a
 general bias towards back and forth behavoir, which can be seen in the
-box plots of Figure~{box-mannik}, but the behavoir is irregular and
+box plots of Figure~\ref{box-mannik}, but the behavoir is irregular and
 the location of the maxima vary a significant amount.  On the other
@@
 Judging that at this point that we have a fair idea of how our two
-methods compare in terms of experimental acuracy, we are interested to
-investigate the limits of the break down of regular activity, by
-simulating large, regular, 'stadium' shapes.  These shapes have the
-flattened, pancake like form of the assymetric cells, but from the top
-down they look as pills do. In two dimensions they are composed of a
-rectangle with two half ellipse connected on either end.  They are
-also made to have a large volume that is similar to the Mannik shapes.
+methods compare with experiment, we investigate the limits of the
+break down of regular activity, by simulating large, regular,
+'stadium' shapes.  These shapes have the flattened, pancake like form
+of the assymetric cells, but from the top down they look as pills
+do. In two dimensions they are composed of a rectangle with two half
+ellipse connected on either end.  They are also made to have a large
+volume that is similar to the Mannik shapes.
 
 We find that both the stochastic and the deterministic solutions show
-regular show back and forth behavoir in the stadium shaped cells, as
-can be seen Figure~{box-stadium}.  This suggests that it is the
-irregular shape of the Mannik cells,, not the size or their flattened
-nature, that causes these cells be exhibit irregularity in MinD
-oscillations.
+regular back and forth oscillations the stadium shaped cells, as can
+be seen Figure~\ref{box-stadium}.  This suggests that it is the irregular,
+assymetric shape of the Mannik cells, not their size or their
+flattened nature, that causes these cells to exhibit irregularity in
+MinD oscillations.
 
@@
     shapes.  This is in contrast to the behavoir of Mannik cells seen
-    in Figure~{randst-plot-ave}}
+    in Figure~\ref{randst-plot-ave}}
   \label{arrow-pill-stadium}
@@
 
-Figure \ref{randst-plot-ave} shows a comparison of irregular shapes
+Figure~\ref{randst-plot-ave} shows a comparison of irregular shapes
 simulated with the stochastic method and with the deterministic
@@
 plots illustrate the adequacy of the stochastic method and inadequacy
-of the deterministic one.  The stochastic plots show similar random behavoir to Manniks
+of the deterministic one.  The stochastic plots show similar random
+behavoir to Manniks
 

### 2014-08-29 paper/paper.tex
text editing in paper Tested everything on quipu.

@@
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
+\fixme{should I say anything about different/large sizes?}
 We have made and studied plots and movies of the MinD in a number of
@@
 maxima.  On the other hand, our stochastic simulations show both
-irregular behavoir in the assymetrical shapes and more regular, pole
-to pole oscillations in the symmetric pill and stadium shaped cells,
-agreeing well with Mannik's experimental findings.
+robust pole to pole oscillations in the symmetric cells and irregular
+behavoir in the assymetrical shapes, agreeing well with Mannik's
+experimental findings.
 
-Figure~\ref{arrow-pill-stadium} and Figure~\ref{randst-plot-ave} show color
-plots of time-averaged MinD overlayed by arrows depicting sequential
-maxima that are global in space and local in time.  Our shapes that
-are designed to look like Mannik cells show well the inadequacy of the
-deterministic method of simulation and conversely the accuracy of the
-stochastic method.  Our stochastic method movies (and arrow plots of
-Figure~\ref{randst-plot-ave}) show irregular location of maxima that is
-similar to what is observed experimentally by Mannik. There is a
+Figure~\ref{arrow-pill-stadium} and Figure~\ref{randst-plot-ave} show
+color plots of time-averaged MinD overlayed by arrows depicting
+sequential maxima that are global in space and local in time.  Our
+stochastic method movies (and arrow plots of
+Figure~\ref{randst-plot-ave}) show irregular location of maxima that
+is similar to what is observed experimentally by Mannik. There is a
 general bias towards back and forth behavoir, which can be seen in the
-box plots of Figure~\ref{box-mannik}, but the behavoir is irregular and
-the location of the maxima vary a significant amount.  On the other
-hand, the deterministic simulations show behavoir that is much too
-regular when compared with experiment, exhibiting locations of maxima
-that do not vary.  The deterministic method is seen to be inadequate.
+box plots of Figure~\ref{box-mannik}, but the behavoir is irregular
+and the location of the maxima vary a significant amount.  On the
+other hand, the deterministic simulations show behavoir that is much
+too regular when compared with experiment, exhibiting locations of
+maxima that do not vary.  The deterministic method is seen to be
+inadequate.
 
@@
 
-Our simulations of pill shapes show behavoir that is once again well
-matched by experiment, but this time the deterministic method seems to
-be as aduaquet as the stochastic in giving accurate results.  The
-experimental cells show regular back and forth behavoir, as do both
-simulations.  In this case the natural bias of the deterministic
-method towards robustness and regularity works in its favor.
-
 Judging that at this point that we have a fair idea of how our two
@@
 We find that both the stochastic and the deterministic solutions show
-regular back and forth oscillations the stadium shaped cells, as can
-be seen Figure~\ref{box-stadium}.  This suggests that it is the irregular,
-assymetric shape of the Mannik cells, not their size or their
-flattened nature, that causes these cells to exhibit irregularity in
-MinD oscillations.
+regular back and forth oscillations in the stadium shaped cells, as
+can be seen Figure~\ref{box-stadium}.  This suggests that it is the
+irregular, assymetric shape of the Mannik cells, not their size or
+their flattened nature, that causes these cells to exhibit
+irregularity in MinD oscillations.
 
@@
 \end{figure}
-
-Figure~\ref{randst-plot-ave} shows a comparison of irregular shapes
-simulated with the stochastic method and with the deterministic
-method, along with a plot taken from Mannik showing the location of
-sequential MinD maxima in the experimental cells.  Like Mannik's, the
-tips of the arrows in our plots show subsequent maxima, and the data
-overlays a color plot of time averaged MinD concentration.  These
-plots illustrate the adequacy of the stochastic method and inadequacy
-of the deterministic one.  The stochastic plots show similar random
-behavoir to Manniks
 
@@
 \section{Conclusion}
+No conclusion :(
 \bibliography{paper}
@@
 
-%% \subsubsection{Randst-97-}
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-800-600-9700-1500}
-%%   %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
-%%   \caption{Total protein fluctuation in the sideways flying saucer
-%%     pancake cell shape.  The vertical axis shows stacked the total
-%%     number of proteins that are of four different compound stages and
-%%     in the different sections of the cell.}
-%%   \label{box-97}
-%% \end{figure}
-
-%% Early on in its simulation the sideways flying saucer pancake shape
-%% shows a clear breakdown of an unstable equilibrium oscillation.  We
-%% have set the intial conditions so that MinD density is highly
-%% concentrated to the left of a dividing line that runs parrallel to the
-%% left vertical side.  For the first number of oscillations the maxima
-%% trade off right to left, from a high peak in the rightward middle
-%% compartment to vertically opposed peaks in the poles of the long axis
-%% of the cell.  This is seen in the first part of Figure~\ref{box-97},
-%% where the lower and upper sections peak in unison, and the middle
-%% right section peaks $\pi$ radians removed from these.  After a few
-%% oscillations the back and forth oscillations tip toward the vertical
-%% direction and the system loses its initial oscillation pattern.  It
-%% falls quickly instead into a back and forth pattern between the two
-%% opposing endcaps.  The oscillation at this point is reminiscent of the
-%% pills shape oscillation, once again showing the robust nature of the
-%% back and forth, two pole pattern.
-
-%% During each period, directly after one of the polar maxima has
-%% subsided, there is a small spike with the regular maxima pattern (a
-%% spike in membrane bound MinD:ATP immediately followed by a spike in
-%% membrane bound MinD:MinE:ATP) seen in the small middle right
-%% compartment section.  The animations show that the MinD, oscillating
-%% back and forth between the upper and lower poles, seems to catch and
-%% lag in the indentation for a bit before moving on.  Once again the
-%% positive radius of curvature acts as an attractive place for MinD to
-%% cluster on the walls, and it is not released to move on through the
-%% cytoplasm again until MinE has formed its ring and completely reacted
-%% it away.
-
-%% \subsubsection{Randst-96-Star}
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-700-700-9600-1500}
-%%   %%\includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9600-1500}
-%%   \caption{Total protein fluctuation in the star cell shape.  The vertical axis shows stacked the total
-%%     number of proteins that are of four different compound stages and
-%%     in the different sections of the cell.}
-%%   \label{box-96}
-%% \end{figure}
-
-%% This clover shape finds a regular oscillatory behavoir after about
-%% seven periods that consists of two maxima that peak regularly in the
-%% corners accross from each other at the same times (Figure
-%% \ref{box-96}) and then again opposing maxima that peak at the same
-%% time in the other two corners.\fixme{should try some different
-%%   starting conditions with this to see if there's another patter.}
-
-%% Looking at at few periods in detail.  We find that there is a small
-%% increase in cytoplasmic MinE always directly before the beggining
-%% of climb in the membrane bound MinE peak.  Also, there is at any one
-%% time a very large amount more of minE that is membrane bound then
-%% cytoplasmic in any ones section.  A difference of a factor of roughly
-%% 20 when membrane MinE is at its peak, and roughly 12 when membrane
-%% MinE is at it's minimum.  There seem to be two modes of oscillation,
-%% each exhibiting a density peak maxima that moves back and forth
-%% diagonaly from one corner to the opposite, as if there were two
-%% overlapping, criss-crossed cells oscillating.  In the box plot this is
-%% seen as roughly coinciding membrane minD peaks in the lower left and
-%% right corners, followed one pi later in peaks in the upper right and
-%% upper left corners.  Interesting that this did not exhibit
-%% counterclockwise motion that Huangs 2008 paper might suggest.  Should
-%% run sims that start in the wacky way that just started running with
-%% triangles.
-%% \newline
-
-%% We haven't simulated long enough yet, so no real pattern has shown
-%% itself.  There's certainly oscillations, and it's almost as if there's
-%% competing modes - top to bottom, left to right, corner to corner, etc.
-%% Interesting.
-
-%% \fixme{maybe?}The animations seem to relax into a pattern in which the oscillations
-%% go from the smallest corner, out to the other three, and then back to
-%% the smallest corner?  \fixme{There isn't enough data to see properly
-%%   though, need to run for longer.}
-
-%% The double pole oscillation pattern, in which one pole is located in a
-%% single corner of the triangle and the other pole is spread out between
-%% the opposite two, can be seen in Figure \ref{box-triangle}.  The
-%% equilateral triangle shows a spike in both the Center and Left
-%% sections at the same time, both showing the familiar sequence of peaks
-%% amoungst the different states of the protein seen in the poles of the
-%% pill shaped bacteria.  A spike in the other corner, showing the common
-%% sequence, occurs during the minima of the former two, wth a higher
-%% concentration at the peak.  A similar pattern is seen in the
-%% iscosolese triangular shape, where interestingly the onset of the
-%% maxima in the single maxima corner (the Left section) builds more
-%% quickly than it fades.  This is presumably becuase as the cytoplasmic
-%% minD:ATP diffuses down a more accute corner, it is sourrounded by
-%% closer cell walls than it would be in a less acute corner, so that the
-%% it is more apt at any diffusive step to make contact and cluster on
-%% the walls.  That particular part of the process is therefore
-%% accelerated, driving the build up of the maxima forward.
-
-%% The right triangle shows a similar pattern except that here there is
-%% an assymetry between the two corners that maximize at roughly the same
-%% time.  One corner is further from the single maximizing corner and it
-%% consisitently peaks later.  The MinD simply have further to travel
-%% before they maximize there.
-
-%% For these three sizess and shapes there is not sign that the
-%% oscillation patterns once they are set will break down.
-
-%% \begin{figure}
-%% %%  \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-600-600-600-1500}
-%%   \caption{Total protein fluctuation of an equilateral triangle with
-%%     larger dimensions (each side is roughly $6\micron$.  The vertical
-%%     axis shows stacked the total number of proteins that are of four
-%%     different compound stages and in the different sections of the
-%%     cell. The time limits have been set to show the broken down
-%%     section of the simulation.}
-%%   \label{box-triangle}
-%% \end{figure}
-
-%% The larger equilateral shape shows the same pattern as the smaller
-%% version does only until fifteen periods, at which point there is a
-%% breakdown of the oscillation pattern.  During the last three stable
-%% periods, the single maximizing corner, the lower left section in the
-%% figure, has a lower peak each period as the membrane bound MinD:ATP in
-%% the other corners lag more and more before being eaten away by the
-%% MinE.  Finally these maxima lag so much that they break down the
-%% regular pattern.  There then occurs about five periods of semi chaotic
-%% behavoir, until it settles back into another stable oscillation that
-%% is similar to the original one, except that a different corner has
-%% been chosen to be the singlular maxima (the right section in the
-%% figure), while the other two corners maximize at the same time.  This
-%% interesting breakdown and recovery shows both the robustness of the
-%% double pole oscilatory tendency and the importance of required
-%% distance of travel for the different proteins.
-
 \end{document}

### 2014-08-29 paper/paper.tex
altered bound on plot-ave and edited text in paper Tested everything on quipu.

@@
 \section{Stability Analysis}
+\label{sec:stability-analysis}
 We have found that in both methods of simulation there is a lower
@@
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-\fixme{should I say anything about different/large sizes?}
-We have made and studied plots and movies of the MinD in a number of
-simulated cell shapes and sizes. We have found that the deterministic
-simulations of the protein reaction sequence discussed above results
-in robust oscillatory behavoir of polar selection and oscillation in
-not only symmetrical shapes, such as the wild type pill shape, but
-also in very assymetrical, flatttened cells, such as those studied by
-Mannik.  This differs with Mannik's experimental findings that show
-much less regular behavoir, with a large variation in the location of
-maxima.  On the other hand, our stochastic simulations show both
-robust pole to pole oscillations in the symmetric cells and irregular
-behavoir in the assymetrical shapes, agreeing well with Mannik's
-experimental findings.
+\fixme{should I say anything about different/large sizes?}  We have
+made movies out of color plots of MinD concentration, integrated along
+the flattened axis, in which each frame is seperated in simulation
+time by a half second. Our simulations include the two flattened cell
+shapes that are reported in Manniks paper, a few other 'irregular'
+shapes of our own creation, triangle shaped flattened cells, and a
+symetric 'stadium' shaped cell. For each of these shapes we have
+varied the size, from roughly twice the dimensions of Mannik's
+reported cells down to the smaller sizes refered to in
+section~\ref{sec:stability-analysis}.
+
+We have found that the deterministic simulations of the protein
+reaction sequence discussed above results in robust oscillatory
+behavoir of polar selection and oscillation in not only symmetrical
+shapes, such as the wild type pill shape, but also in very
+assymetrical, flatttened cells, such as those studied by Mannik.  This
+differs with Mannik's experimental findings that show much less
+regular behavoir, with a large variation in the location of maxima.
+On the other hand, our stochastic simulations show both robust pole to
+pole oscillations in the symmetric cells and irregular behavoir in the
+assymetrical shapes, agreeing well with Mannik's experimental
+findings.
 
@@
 
+\section{Interpretation of Data}
+\section{Conclusion}
+No conclusion :(
+\bibliography{paper}
+
+\end{document}
+
+\section*{Appendix}
+
+\section{Below are NOTES for the Writing}
+
 %% \section{Triangular Shapes}
@@
 %% clusters.
-
-\section{Interpretation of Data}
-\section{Conclusion}
-No conclusion :(
-\bibliography{paper}
-
-\end{document}
-
-\section*{Appendix}
-
-\section{Below are NOTES for the Writing}
 

### 2014-08-29 paper/plot-arrow-ave.py

@@ -34,8 +34,8 @@ arg_set = ["0.25-18.50-18.50-95.00-15.00-full_array",
            "0.25-18.50-18.50-95.00-15.00-exact",
            "0.25-18.60-28.60-94.00-15.00-exact"]
 
-bound_times = ["500","1400","120","740","500","1400","500","1400"]
-arrow_cutoffs = [2.4/5.0,2.4/5.0,2.2/5.0,2.8/5.0]
+bound_times = ["500","1500","120","1000","500","1500","500","1400"]
+arrow_cutoffs = [2.4/5.0,2.5/5.0,2.2/5.0,2.9/5.0]
 
 arrow_files = []
 contour_values = []

### 2014-08-29 paper/paper.tex
paper edits Tested everything on quipu.

@@
 behavoir of polar selection and oscillation in not only symmetrical
-shapes, such as the wild type pill shape, but also in very
-assymetrical, flatttened cells, such as those studied by Mannik.  This
-differs with Mannik's experimental findings that show much less
-regular behavoir, with a large variation in the location of maxima.
-On the other hand, our stochastic simulations show both robust pole to
-pole oscillations in the symmetric cells and irregular behavoir in the
-assymetrical shapes, agreeing well with Mannik's experimental
-findings.
+shapes, such as the wildtype pill shape, but also in very
+assymetrical, flatttened cells, such as those studied by Mannik.
+After the lower stability limit of
+section~\ref{sec:stability-analysis} has been surpassed, this
+qualitative behavoir doesn't seem to have size dependence until cells
+reach sizes that have more than twice the dimensions of the Mannik
+cells.  At this point the robust oscillations, while still evident,
+begin to lose their consistanty.  The Mannik reported cells already
+seem to be rather large (wild type cells are typically smaller than
+those observed my Mannik
+\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
+so we left off simulating cells any larger than twice this size.
+
+This differs with Mannik's experimental findings
+that show much less regular behavoir, with a large variation in the
+location of maxima.  On the other hand, our stochastic simulations
+show both robust pole to pole oscillations in the symmetric cells and
+irregular behavoir in the assymetrical shapes, agreeing well with
+Mannik's experimental findings.
 
@@
     are shown. The plots serve to illistrate what is observed in our
-    movies.  At this point the data is over varying amounts of time
-    but its all roughly 1000 seconds\fixme{fix this}.  The top row
-    shows plots published by Mannik of the MinD maxima behavoir and
-    the bottom two rows show our pancake shapes that are designed to
-    have the same shape.  The middle row shows results from the
-    stochastic simulation and the bottom shows results from the
-    deterministic.  We can see that the stochastic method shows
+    movies.  The simulation time covered in these is 1000 seconds
+    \fixme{this is not true yet - need to change the data once its
+      finished right now 2 of them are 1000 the others are like 980}.
+    The top row shows plots published by Mannik of the MinD maxima
+    behavoir and the bottom two rows show our pancake shapes that are
+    designed to have the same shape.  The middle row shows results
+    from the stochastic simulation and the bottom shows results from
+    the deterministic.  We can see that the stochastic method shows
     behavoir that is similar to experiment while the deterministic

### 2014-08-29 paper/plot-arrow-ave.py

@@ -192,5 +192,5 @@ plt.ylabel("Y grid position")
 
 plt.savefig('./paper/plot-ave.pdf')
 
-plt.show()
+#plt.show()
 

### 2014-08-29 paper/paper.tex
more paper edits Tested everything on quipu.

@@
 \cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
-so we left off simulating cells any larger than twice this size.
+so we left off simulating cells any larger than twice this size. The
+movies show sharp peaks of MinD in specific locatations, typically at
+the edges of the cell and in regions of high radius of curvature,
+followed by a spreading out of the MinD out into the cell, with no
+real bias towards any location, until it aggregates again in a
+specific location at the opposite edge of the cell, maximizing there.
+The pattern is repeated again and again with surprising consistency,
+which can be seen on the right of Figure~\ref{box-mannik}.  This is
+the same plotting method as our box plots above, here showing
+stochastic and deterministic simulations of cells that are the same
+shape and size of one of Mannik's reported cells.
 
-This differs with Mannik's experimental findings
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
+  \caption{A comparison of our box plots that show a disparity between
+    the behavoir of the stochastic and deterministic simulations in
+    our Mannik cells.  The deterministic show a regular, robust
+    oscillatory behavoir between the two ends of the cell. The
+    stochastic simulation do show a general back and forth tendency
+    between two ends of the cell, but it is not robust and tends to
+    break down.}
+  \label{box-mannik}
+\end{figure}
+
+The findings differ with Mannik's experimental findings
 that show much less regular behavoir, with a large variation in the
@@
   \label{randst-plot-ave}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
-  \caption{A comparison of our box plots that show a disparity between
-    the behavoir of the stochastic and deterministic simulations in
-    our Mannik cells.  The deterministic show a regular, robust
-    oscillatory behavoir between the two ends of the cell. The
-    stochastic simulation do show a general back and forth tendency
-    between two ends of the cell, but it is not robust and tends to
-    break down.}
-  \label{box-mannik}
 \end{figure}

### 2014-08-29 paper/paper.tex
not much committing because Im about to go to a meeting Tested everything on quipu.

@@
 
-The findings differ with Mannik's experimental findings
-that show much less regular behavoir, with a large variation in the
-location of maxima.  On the other hand, our stochastic simulations
-show both robust pole to pole oscillations in the symmetric cells and
-irregular behavoir in the assymetrical shapes, agreeing well with
-Mannik's experimental findings.
+The results of these simulations differ significantly with Mannik's
+experimental results that show much less regular behavoir, with a
+large variation in the location of maxima.
+
+On the other hand, our stochastic simulations show both robust pole to
+pole oscillations in the symmetric cells and irregular behavoir in the
+assymetrical shapes, agreeing well with Mannik's experimental
+findings.
 

### 2014-09-04 paper/plot-arrow-ave.py
updating for meeting Tested everything on wentworth.

@@ -49,8 +49,8 @@ arg_set = ["randst/0.25-18.50-18.50-95.00-15.00-exact",
 
 #rot_theta = [math.pi/2.0,math.pi/3.0,math.pi/4.0,math.pi/5.0,7.0*math.pi/6.0,21.0*math.pi/9.0]
 
-bound_times = [500,1000,500,1000,500,1000,500,980,500,1000,500,780,500,1000,500,780,500,1000,500,1000]
-arrow_goals = [20, 16, 16, 14, 19, 18, 18, 16, 24, 24]
+bound_times = [500,1000,500,1000,500,1000,500,980,500,1000,500,780,500,1000,500,780,500,700,500,700]
+arrow_goals = [20, 16, 16, 14, 19, 18, 18, 16, 5, 5]
 
 col_0x = 1.0
 col_1x = 8.0

### 2014-09-04 pyplots/movie-image-creation.py

@@ -101,8 +101,9 @@ def timemin(data):
 
 def gaussian_smear(data,wavelength):
     new = np.zeros_like(data)
-    n_sin_theta = 1.5
-    sigma = wavelength/2.0/n_sin_theta #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+    N_A = 1.3
+    sigma = .21*wavelength/N_A #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
+    print "sigma ",sigma
     dis = int(3*sigma/0.05) #for now
     for num in range(new.shape[0]):
         print 'num = '+str(num)
@@ -130,21 +131,23 @@ def contourplt(protein,video_number):
     print "smeared_data.shape[2] ",smeared_data.shape[2]
     print type(smeared_data[0])
 
-    Z, Y = np.meshgrid(np.arange(0,smeared_data.shape[2]*0.05,0.05), np.arange(0,(smeared_data.shape[1]-.9)*0.05,0.05))
-    print "Z ",len(Z)
-    print "Z0 ",len(Z[0])
+    Z, Y = np.meshgrid(np.arange(0,(smeared_data.shape[2]-.9)*0.05,0.05), np.arange(0,(smeared_data.shape[1]-.9)*0.05,0.05))
+
+    print "Z.shape[0] ",Z.shape[0]
+    print "Z.shape[1] ",Z.shape[1]
+
     print len(smeared_data[0])
     print len(smeared_data[0][0])
 #generate a sequence of .png's for each file (printed time step). these will be used to create a gif.
     for k in range(int(starting_video_number/dump_time_step), int(starting_video_number/dump_time_step) + len(protein.dataset), 1):
         #page = protein.dataset[k]
-        print './data/shape-'+f_shape+'/plots/images/'+load.debug_str+load.hires_str+load.slice_str+'tp_'+str(k)+'-'+str(protein.protein)+ \
-                        '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+dens_factor+'-'+sim_type+'.png'
+        # print './data/shape-'+f_shape+'/plots/images/'+load.debug_str+load.hires_str+load.slice_str+'tp_'+str(k)+'-'+str(protein.protein)+ \
+        #                 '-'+f_shape+'-'+f_param1+'-'+f_param2+'-'+f_param3+'-'+f_param4+'-'+dens_factor+'-'+sim_type+'.png'
         plt.clf()
[…]

### 2014-09-04 pyplots/movie-maker.py

@@ -60,7 +60,7 @@ if (end_time >= total_number_of_files*dump_time_step):
     print "there are only enough files to support a total time of less than ", total_number_of_files*dump_time_step
     exit(1)
 
-num_in_a_video = 400
+num_in_a_video = 2000
 number_of_videos = 1 + int( (end_time-start_time)/float(dump_time_step)/float(num_in_a_video) )
 
 print num_in_a_video

### 2014-09-05 paper/paper.tex
updating for meeting Tested everything on wentworth.
beautify arrow plot for paper Tested everything on bennet.

@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
   \caption{A comparison of our box plots that show a disparity between
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
-  \includegraphics[width=\columnwidth]{../paper/plot-ave}
-  \caption{Arrows depicting global maxima in space and local maxima in
+  \includegraphics[width=\textwidth]{../paper/plot-ave}
+  \caption{\fixme{Look into unifying the color scale, and adding a
+      scale bar.} Arrows depicting global maxima in space and local
+    maxima in
     time overlayed on color plots of time averaged total MinD density.
@@
   \label{randst-plot-ave}
-\end{figure}
+\end{figure*}
 

### 2014-09-05 paper/plot-arrow-ave.py

@@ -54,19 +54,23 @@ arrow_goals = [20, 16, 16, 14, 19, 18, 18, 16, 5, 5]
 
 col_0x = 1.0
 col_1x = 8.0
-col_2x = 15.0
-col_3x = 21.0
-col_4x = 26.5
+col_2x = -5.5
+col_3x = 14.5
+col_4x = col_3x + 5.5
+
+left_annotate_x = -8.5
+bottom_annotate_y = -1.7
 
 row_0y = 1.0
 row_1y = 6.0
+row_my = 10.5
 
 x_position_m1 = col_0x
-y_position_m1 = 13.0
+y_position_m1 = row_my
 x_position_m2 = col_1x
-y_position_m2 = 13.0
+y_position_m2 = row_my
 x_position_m3 = col_4x
-y_position_m3 = 13.0
+y_position_m3 = row_my
 
 X_position = [col_0x,col_0x,col_1x,col_1x,col_2x,col_2x,col_3x,col_3x,col_4x,col_4x]
 Y_position = [row_0y,row_1y,row_0y,row_1y,row_0y,row_1y,row_0y,row_1y,row_0y,row_1y]
@@ -92,44 +96,15 @@ for i in range(len(arg_set)):
                             +str(bound_times[i*2+1])+'.dat']
 
 
-plt.figure(1, figsize=(8,5))
-plt.axes().set_aspect('equal', 'datalim')
+plt.figure(1, figsize=(8,3.4))
+#plt.axes().set_aspect('equal', 'datalim')
+plt.axes().set_aspect('equal')
+plt.axis('off')
 
 data = [0]*(len(arg_set)+2)
 print len(data)
 for arg_num in range(len(arg_set)):
     data[arg_num] = np.loadtxt(contour_values[arg_num])
-
-
-mannik_micron = 5.0/1012
-m1=mpimg.imread('mannik-1.png')
-m1x = -np.arange(-m1.shape[0]/2, m1.shape[0]/2)*mannik_micron
-m1y = np.arange(-m1.shape[1]/2, m1.shape[1]/2)*mannik_micron
-M1x, M1y = np.meshgrid(m1y, m1x)
-M1xrot = M1x*math.cos(mannik_rot_theta[0]) - M1y*math.sin(mannik_rot_theta[0]) + x_position_m1
-M1yrot = M1x*math.sin(mannik_rot_theta[0]) + M1y*math.cos(mannik_rot_theta[0]) + y_position_m1
[…]

### 2014-09-05 paper/plot-arrow-ave.py
minor edits, color on single plots, 350 second intervals on paper/plot Tested everything on quipu.

@@ -50,7 +50,9 @@ arg_set = ["randst/0.25-18.50-18.50-95.00-15.00-exact",
 #rot_theta = [math.pi/2.0,math.pi/3.0,math.pi/4.0,math.pi/5.0,7.0*math.pi/6.0,21.0*math.pi/9.0]
 
 bound_times = [500,1000,500,1000,500,1000,500,980,500,780,500,1000,500,780,500,1000,500,700,500,700]
-arrow_goals = [20, 16, 16, 14, 19, 18, 18, 16, 5, 5]
+bound_times = [500,850,500,850,500,850,500,850,500,850,500,850,500,850,500,850,500,840,500,840]
+arrow_goals = [20, 16, 16, 14, 19, 18, 18, 16, 11, 11]
+arrow_goals = [13, 11, 12, 12, 9, 16, 9, 15, 18, 18]
 
 col_0x = 1.0
 col_1x = 8.0

### 2014-09-05 pyplots/single-image-creation.py

@@ -85,9 +85,10 @@ times  = np.arange(float(start_time),float(end_time),dump_time_step)
 
 for i in range(len(proteins)):
     print proteinList[i]
-    smeared_data = gaussian_smear(proteins[i].dataset,.509) #this is in microns green light at 500nm,
+    smeared_data = gaussian_smear(proteins[i].dataset,.650) #this is in microns green light at 500nm,
     for j in range(len(times)):
         image_data_file = '.' + job_string +str(proteinList[i])+'/images/single-'+str(times[j])+'.dat'
+        #image_data_file = '.' + job_string +str(proteinList[i])+'/images/real-gauss-single-'+str(times[j])+'.dat'
         p_file = open(image_data_file,'w')
         p_file.close()
         p_file = open(image_data_file,'a')

### 2014-09-05 pyplots/single-image-plot.py

@@ -57,6 +57,7 @@ for i in range(len(proteinList)):
     smeared_data = [0]*len(times)
     for j in range(len(times)):
         image_data_file = job_string +str(proteinList[i])+'/images/single-'+str(times[j])+'.dat'
+        #image_data_file = job_string +str(proteinList[i])+'/images/real-gauss-single-'+str(times[j])+'.dat'
         smeared_data[j] = np.loadtxt(image_data_file) #this is in microns green light at 500nm,
     dZ = smeared_data[0].shape[1]*1.05
     dY = smeared_data[0].shape[0]*2.00/skip_times
@@ -65,9 +66,25 @@ for i in range(len(proteinList)):
     maxval = timemax(smeared_data)
     mylevels = np.linspace(0,(1+1.0/nlevels)*maxval,nlevels)
     for k in range(len(smeared_data)):
+        #print i, ' ',k
         page = smeared_data[k]
         page[page>maxval] = maxval
-        plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page, cmap=plt.cm.hot_r, levels=mylevels)
+        cdata = np.array([[0  ,1,1,1],
+                          [.01 ,1,1,1],
+                          [.25,0.8,.8,1],
+                          [.5 ,0,.8,.8],
+                          [.7 ,1,1,0],
+                          [.85 ,1,0,0],
+                          [1  ,0,0,0]])
+        cdict = {'red':   [], 'green': [], 'blue':  []}
+        for xi in range(cdata.shape[0]):
+            cdict['red']   += [(cdata[xi, 0], cdata[xi, 1], cdata[xi, 1])]
+            cdict['green'] += [(cdata[xi, 0], cdata[xi, 2], cdata[xi, 2])]
+            cdict['blue']  += [(cdata[xi, 0], cdata[xi, 3], cdata[xi, 3])]
+        cmap = matplotlib.colors.LinearSegmentedColormap('mine', cdict)
+        plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page, cmap=cmap, levels=mylevels)
+        #plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page, cmap=plt.cm.hot_r, levels=mylevels)
+
 plt.axes().get_yaxis().set_ticks([(i+0.5)*dZ for i in range(len(proteinList))])
[…]

### 2014-09-05 pyplots/time-averaged-arrow.py

@@ -98,7 +98,7 @@ def gaussian_smear(data,wavelength,protein):
         p_file = open(arrow_file,'a')
         p_file.write('%g %g %g %g\n'%(input_start_time+num*dump_time_step,maxima,max_x,max_y))
         p_file.close()
-        if (num%40 == 0 and num > 1):
+        if (num%20 == 0 and num > 1):
             contour_values = job_string +'ave-time/contour-values-' + str(protein) +'-'+ str(int(input_start_time))+'-' \
                 +str(int(input_start_time+num*dump_time_step))+'.dat'
             print contour_values

### 2014-09-05 paper/paper.tex
minor edits, color on single plots, 350 second intervals on paper/plot Tested everything on quipu.
plotocide Tested everything on quipu.

@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{stability-analysis}
-  \caption{Infinite slab stability analysis yields characteristic half
-    wavelengths at which system becomes unstable.}
-    \label{fig:stability-analysis}
-\end{figure}
-
 \section{Stability Analysis}
@@
 characteristic half wavelengths of $2\mu m$.
-
-\begin{figure}
-%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-800-800-9500-1500}
-%  \includegraphics[width=4.2cm]{../data/shape-randst/plots/box-plot_D--randst-25-1000-1700-9400-1500}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-8_00-8_00-95_00-15_00-exact/plots/box-plot_D}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-10_00-17_00-94_00-15_00-exact/plots/box-plot_D}
-  \caption{Box plots of Mannik shapes for sizes at the lower stability
-    threshhold.  The vertical axis shows stacked and changing over
-    time the total number of proteins that are of four different
-    compound stages and in the different sections of the cell.  Both
-    shapes have longer axis of roughly 2.2$\mu m$.}
-  \label{box-mannik}
-\end{figure}
 
@@
   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
+  \caption{A comparison of our box plots that show a disparity between
+    the behavoir of the stochastic and deterministic simulations in
+    our Mannik cells.  The deterministic show a regular, robust
+    oscillatory behavoir between the two ends of the cell. The
+    stochastic simulation do show a general back and forth tendency
+    between two ends of the cell, but it is not robust and tends to
+    break down.}
+  \label{box-mannik}
+\end{figure}
+\begin{figure}
   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
-  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/plot-time-averaged-arrow-NflD-500-2000}
-  \caption{Arrows depicting global maxima in space and local maxima in
-    time overlayed on color plots of time averaged total MinD
-    density. A density threshold is chosen and only maxima above this
-    threshold are shown. The plots serve to illistrate what is
-    observed in our movies. \fixme{how much of time of data is
-      shown?}.  Although there is variation in the specific location
-    of maxima on each edge of the cell, the behavoir for both of these
-    regular shapes is robust and exhibits a back and forth oscillatory
-    manner.  The wildtype pill shape behavoir matches well with
-    experiment.  Regular pancake shapes have not been observed
-    experimentally, but our stochastic simulations would suggest that
-    they would exhibit regular robust oscillations similar to the pill
-    shapes.  This is in contrast to the behavoir of Mannik cells seen
-    in Figure~\ref{randst-plot-ave}}
-  \label{arrow-pill-stadium}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/NflD-time-map}
-  \caption{Time map plots of our stad shape}
-  \label{time-maps-stad}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/NflD-time-map}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/NflD-time-map}
-  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/NflD-time-map}
-  \caption{Time map plots of our randst shape}
-  \label{time-maps-randst}
-\end{figure}
-
 \fixme{specifically design other arrow plot (with many comparisons) to
@@
 
-%% \section{Triangular Shapes}
-
-%% \begin{figure}
-%% %  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
-%% %  \includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
-%%   \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-233-233-233-1500}
-%%   \includegraphics[width=\columnwidth]{../data/shape-triangle/plots/box-plot_D--triangle-25-266-266-266-1500}
-%%   %\includegraphics[width=4.2cm]{../data/shape-triangle/plots/box-plot_D--triangle-25-800-800-800-1500}
-%%   \caption{Two box plots of triangle shapes.  The two smaller show
-%%     sizes at the lower stability threshhold, one just below, one just
-%%     above.  The larger triangle is the largest simulated. The vertical
-%%     axis shows stacked and changing over time the total number of
-%%     proteins that are of four different compound stages and in the
-%%     different sections of the cell.}
-%%   \label{box-triangle}
-%% \end{figure}
-
-%% Along with our other shapes we have chosen to simulate both
-%% equilateral and iscoscolese triangular flattened shapes, since these
-%% offer in a way the simplest shapes that are geometrically more
-%% complicated than our pills.
-
-%% Both triangle types show a similar oscillation pattern.  The
-%% iscosolese exhibit regular oscillations characterized by one distinct
-%% pole in the more accute angle of the three, and another 'pole' along
-%% the opposite wall, peaking in the two more obtuse angles at the same
-%% time.  The equilateral triangles settle very quickly into the same
-%% pattern, where the choice of which is one pole corner is dependent
-%% upon initial conditions.  As with the Mannik simulated shapes, there
-%% is a critical small size below which the oscillations dampen out and
-%% will not achieve a regular pattern.  Figure~\ref{box-triangle} shows
-%% two plots of equilateral triangles.  The two smaller show the
-%% largest that showed damped out behavoir and the smallest that
-%% developed regular oscillations.  The larger shows the largest traingle
-%% that we simulated, showing that at even very large sizes the behavoir
-%% is consistent and stable.  Above the small size threshold, all
-%% simulated triangles show regular patterns for as long as simulated
-%% (roughly 800 seconds).
-
-%% \section{Our '\textgreater' Shaped Cells}
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-525-525-9900-1500}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-550-550-9900-1500}
-%%   \label{fig:Vbox}
-%% \end{figure}
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-600-600-9900-1500}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/plots/box-plot_D--randst-25-1400-1400-9900-1500}
-%%   \label{fig:Vbox2}
-%% \end{figure}
-
-%% We have also simulated a flattened '\textgreater' shape that shows an
-%% interesting size dependent pattern (seen in
-%% Figures~\ref{fig:Vbox}~and~\ref{fig:Vbox2}).  When the shape is small enough
-%% that the distance from the apex tip to the opposite curve is less than
-%% our stability limit, a simple, two pole oscillation pattern develops
-%% and is sustained (where the two poles are on opposite leftward corners
-%% of the cell).  When the cell is increased in size so that this
-%% distance is approximately equal to our stability value, the cell
-%% develops a double oscillation in time, where the maxima oscillates
-%% from the lower corner to the rightward apex, then \emph{back to the
-%%   lower corner}, then to the apex again, then to the upper corner,
-%% then back to the apex, then to the upper corner, then to the apex
-%% again, then back to the lower corner, and continues this pattern
-%% indefinately.  Figure~\ref{fig:Vbox} shows the smaller size, for which the
-%% protein oscillates simply, and an intermediate size, which shows a
-%% pattern for which one out of three spikes in the regular oscillation
-%% is less significant.  This second pattern seems to be a precursor to
-%% the double oscillation that seen in Figure~\ref{fig:Vbox2}.  The second
-%% plot shown in Figure~\ref{fig:Vbox2} shows a slightly larger cell for
-%% which the distance measured is larger than our stability limit
-%% distance.  This simulation shows a random pattern.
-
-%% A detailed analysis of a time series of protein contour plots shows
-%% that the importance of spatial dimensions is based on the ability of
-%% protein in different stages to diffuse neccesary distances before
-%% undergowing certain types of reactions.  The double oscillation
-%% pattern shows that every time the membrane bound MinD maximizes in the
-%% upper corner as opposed to the rightward apex, it does so because the
-%% MinE has not had enough time to diffuse to this upper corner, leaving
-%% a MinE free zone.  This particular pattern is specific to this shape
-%% and size, but in general its the restrictions set in place by the
-%% rates at which proteins diffuse and the distances they cover before
-%% reacting that dictate their oscillatory bahavoir.
-
-%% Simulations of this shape in which the two planar dimensions are large
-%% compared to those shown(roughly $9\micron$ across) show no stable
-%% regular periodic pattern. Animations show that the MinD acts as a sort
-%% of traveling cluster that is constantly being eaten away by MinE
-%% behind it.  When this cluster enters a region of high curvature that
-%% ends in a dead end corner it performs the polar maxima behavoir seen
-%% in the other simulations, regrouping out away from the corner where it
-%% travels in the opposite direction while being ``chased'' away by the
-%% MinE that itself is currently maximizing in the corner.  The maxima
-%% occur on non-polar walls often, and will often split into two roaming
-%% clusters.
-
-Figure \ref{total-oscillation-triangle-plot} shows the equivalent
-motion and transference between compound states for the triangular
-states as Figure \ref{total-oscillation-plot} does for the pill shaped
-cells.  The equilateral triangular shows that in all three sections
-there is a spike in wall attached MinD-ATP directly followed by a
-spike in wall attached MinD-MinE-ATP.  The pill had shown a similar
-pattern except that the mid section exhibited no such pronounced
-spike.  Interestingly, the right and mid sections show spikes at
-similar times when compared to the left section spikes, which seem to
-oscillate in a manner shifted pi off from the other two.  This
-behavoir shows itself in the animations, which show a relaxation into
-a stable oscillation from a maxima in one corner to a double maxima in
-the other two corners, and back again.  The left section heights are
-roughly twice that of the right section heights.  The simulations are
-started with higher concentrations of proteins in primarily the right
-section, with some overlap into the middle section, so that perhpas
-this oscillation pattern seems reasonable.  However, it's interesting
-to note that the oscillations, started with assymmetric density, do
-not naturally rotate around the corners of the triangle in a circular
-pattern.
-
-It seems as well that there is a desired oscillation maxima for the
-particular shape and size of the cell, as can be seen by the
-relaxation, over the first four periods, to a regular maximal height
-of the right and left sections' total protein at the height of each spike.
-
-\fixme{Note to make sure I'm interpreting the iscosolese triangle data
-  correctly: the triangle sides are 5,5,3, and the higher density
-  starts in the corner that is opposite the short side.  This corner
-  is covered by the right section.  I've verified this by looking at
-  the protein\_microscopy and drawing a little picture, which is on my
-  desk...if you dare look for something on my desk!!!}  The iscosolese
-triangle starts its simulation with a higher concentration of protein
-in the section that is opposite the shorter side.  It quickly relaxes
-into a stable oscillation pattern.  This pattern shows that right
-corner section regularly has higher spikes in total protein than the
-other sections, and that its spikes appear one pi removed from the
-spikes for the other two sections.  This a similar behavoir to that
-which is seen in the equilateral triangle, differening in that it
-converges more quickly towards this behavoir and that it shows a
-greater exageration in the height of protein buildup in the right most
-section.
-
-\fixme{Note on interpretation of 3-4-5 triangle: the higher density
-  starts to the right of a vertical line that is parrallel to the
-  second longest side in the triangle (the longer of the two
-  non-hypotonuse sides).  This means the higher concentration covers
-  the right angle and also the smaller angle in the triangle} The
-3-4-5 triangle exhibits behavoir that I need more data to properly
-observe.  I does not converge as quickly as that for the iscosolese or
-equilateral triangles.
-
-It seems that there is an approximate critical cell size for which the
-MinD will act in these ``wandering cluster'' formations.  The cell is
-large enough so that there is a loss of MinD correlation between the
-opposite sides (the protein in the right corner at any time is too far
-away from the left to immediately affect the protein there).
-
-\fixme{running larger and smaller.  Guessing the larger will do pole
-  and pole, so talk about in terms of you have huge, pole and pole,
-  then once get small enough double oscillations develop.  Why do they
-  do that?  And hen you can do image plot for the one with consistent
-  double oscillations.  Can right now explain reason for double
-  oscillations.  Look at todo.txt.  The slightly varied guassian shape,
-  so a little assymetric, doesn't change double oscillation pattern.}
-
-Contour plot frames from the animations show the second maxima in the
-lower left corner (immediately following the one in the upper middle
-corner) will reside for a bit longer than the left corner maxima
-preceding it.  These longer residing maxima will then be followed by a
-switch, to the right corner, with a short, less intensive maxima
-traveling through the center.  The MinE shows the same pattern. The
-MinE that was just concentrated on the left corner during the first
-maxima, after releasing the MinD from the membrane there, diffuses up
-and attaches to the MinD on the upper corner membrane and begins to
-release it.  During this process the MinE starts at the edges and
-moves in towards the center of the maxima.  The center of the cup is a
-little further away so it attaches to these outer ridges first and
-then moves in.  After it eats at the corners and starts moving in the
-MinD eventually travels back to set up a maxima in the left corner.
-Watching the cytoplasmic MinE, something very interesting: It as well
-maximizes twice in the left corner, but during the MinD's first maxima
-in the left corner, the MinE has a maxima in the upper corner, and
-during the MinD's second left maxima, the MinE travels to the right
-corner and has a maxima there.  At the same time (during the second
-MinD left corner maxima), there is a large amount of cytoplasmic
-MinD:ATP on the right side.  The MinE does this becuase during the
-first MinD left corner maxima, the MinE has just come off a maxima in
-the right corner.  So it diffuses up to the upper corner and sets up
-there.  During the second MinD left corner maxima, the MinE has just
-come off the upper corner maxima.  It will diffuse into the right
-corner and left corner.  In the left corner it interacts with the MinD
-bound to the membrane there.  In the right corner it sits and
-eventually diffuses away, but at a somewhat slow pace.  \fixme{An idea
-  is that once the MinD travels back from the left corner after its
-  second maxima there, it is not able tot set up a maxima in the upper
-  corner as easily, since there is left over MinE there, which has
-  just traveled from the right corner.  The problem with this is that
-  the MinE doesn't seem to be maximized in the upper corner when the
-  MinD is traveling back up from the left.}  The other idea is simply
-that because the minE is traveling all the way from the right corner,
-the longer time it takes to get there simply means that it all
-concentrates on the left, leaving the upp and right side completely
-open for the build up of MinD.  \fixme{Still dont quite get it but
-  take a look at the other simulations and come back.} Actually, you
-can see this effect very slightly watching the 98 shape, between the
-center cap and the right corner.
-
-Simulations of this shape that has the same height and dimensions .6
-times the size (cells roughly $1.6\mu m$ from top to bottom) do not
-exhibit the same pattern.  In these the MinD maxima oscillate quickly
-back and forth between the two lower corner poles.
-
-Simulations in which the two planar dimensions are 2 and then 3 times
-the size (cells roughly $6\micron$ and $9\micron$, respectively, from top
-to bottom) show no stable regular periodic pattern \fixme{although
-  they haven't really run long enough to exhibit much.  They certainly
-  won't show the double oscillation pattern, however.}  The animations
-of $6\micron$ cells show that the MinD acts as a sort of traveling
-cluster that is constantly being eaten away be MinE behind it.  When
-this cluster enters a region of high curvature that ends in a dead end
-corner it performs the polar maxima behavoir seen in the other
-simulations, regrouping out away from the corner where it travels in
-the opposite direction while being ``chased'' away by the MinE that
-has itself maximized in the corner.  If it has just maximized in the
-top corner, it regroups traveling downward and then naturally splits
-into two groups that travel out and form maxima in the two opposite
-bottom corners.  After maximizing in these two corners the two groups
-recombine again in the center and travel in some direction together as
-one cluster.  Simulations of the $9\micron$ cells show a similar roaming
-cluster.  Although here, the maxima occur on non-polar walls often,
-and will often split into two roaming clusters that interact less
-quickly and are less correlated than those seen in the $6\micron$ cell.
-
-It seems that there is an approximate critical cell size for which the
-MinD will act in these ``wandering cluster'' formations.  The cell is
-large enough so that there is a loss of MinD correlation between the
-opposite sides (the protein in the right corner at any time is too far
-away from the left to immediately affect the protein there).
-
 \end{document}

### 2014-09-06 paper/paper.tex
more work on color maps Tested everything on bennet.

@@
   \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-  \caption{Countour plot images of the concentration of each protein
+  \caption{\fixme{We should figure out units and use the same levels
+      as in the main plot.  I also want to figure out why the two
+      plots look different, and make them the same size.  Can we just
+      do the gaussian} Contour plot images of the concentration of each protein
     species in a natural pill-shaped bacterium at regular intervals in

### 2014-09-06 paper/mycolormap.py

@@ -1,0 +1,19 @@
+import numpy as np
+import matplotlib
+
+cdata = np.array([[0  ,1,1,1],
+                  [.02 ,1,1,1],
+                  [.25,0.2,.2,1],
+                  [.35 ,0,.8,0],
+                  [.5 ,1,1,0],
+                  [.7 ,1,0,0],
+                  [1  ,0,0,0]])
+cdict = {'red':   [], 'green': [], 'blue':  []}
+for i in range(cdata.shape[0]):
+    cdict['red']   += [(cdata[i, 0], cdata[i, 1], cdata[i, 1])]
+    cdict['green'] += [(cdata[i, 0], cdata[i, 2], cdata[i, 2])]
+    cdict['blue']  += [(cdata[i, 0], cdata[i, 3], cdata[i, 3])]
+cmap = matplotlib.colors.LinearSegmentedColormap('mine', cdict)
+
+pancake_levels = np.arange(0, 41.0, 1)
+pill_levels = np.arange(0, 81.0, 1)

### 2014-09-06 paper/plot-arrow-ave.py

@@ -14,6 +14,7 @@ import imp
 import math
 import matplotlib.gridspec as gridspec
 import re
+import mycolormap
 
 dx =0.05
 dump_time_step = 0.5
@@ -162,14 +163,13 @@ for arg_num in range(len(arg_set)):
         cdict['red']   += [(cdata[i, 0], cdata[i, 1], cdata[i, 1])]
         cdict['green'] += [(cdata[i, 0], cdata[i, 2], cdata[i, 2])]
         cdict['blue']  += [(cdata[i, 0], cdata[i, 3], cdata[i, 3])]
-    cmap = matplotlib.colors.LinearSegmentedColormap('mine', cdict)
     time_max = np.max(data[arg_num])
 
-    levels = np.arange(0,time_max+1.0,1)
+    levels = mycolormap.pancake_levels
     levels = np.arange(0, 41.0, 1)
     if 'p/' in arg_set[arg_num]:
-        levels = np.arange(0, 81.0, 1)
-    cs = ax.contourf(Xrot, Yrot, data[arg_num], cmap=cmap, origin='lower',levels=levels)
+        levels = mycolormap.pill_levels
+    cs = ax.contourf(Xrot, Yrot, data[arg_num], cmap=mycolormap.cmap, origin='lower',levels=levels)
 
     if arg_num in [1,8]:
         if arg_num == 1:

### 2014-09-06 pyplots/image_plot.py

@@ -8,6 +8,7 @@ import sys
 import time
 import file_loader as load
 import Image
+import mycolormap
 
 f_shape = sys.argv[1]
 f_param1 = sys.argv[2]
@@ -66,7 +67,7 @@ for i in range(len(proteins)):
     for k in kvals:
         page = proteins[i].dataset[k]
         page[page>maxval] = maxval
-        plt.contourf(Y+k*dY, proteins[0].datashape[1]-Z+i*dZ, page, cmap=plt.cm.hot_r, levels=mylevels)
+        plt.contourf(Y+k*dY, proteins[0].datashape[1]-Z+i*dZ, page, cmap=mycolormap.cmap, levels=mylevels)
 plt.axes().get_yaxis().set_ticks([(i+0.5)*dZ for i in range(len(proteinList))])
 plt.axes().get_yaxis().set_ticklabels(proteinLabels)
 plt.axes().get_xaxis().set_ticks([(0.5+k)*dY for k in kvals[::int(2.5*skip_times)]])

### 2014-09-06 pyplots/mycolormap.py

@@ -1,0 +1,1 @@
+../paper/mycolormap.py

### 2014-09-06 pyplots/single-image-plot.py

@@ -10,6 +10,7 @@ import file_loader as load
 import Image
 import math
 import re
+import mycolormap
 
 f_shape = sys.argv[1]
 f_param1 = sys.argv[2]
@@ -69,20 +70,8 @@ for i in range(len(proteinList)):
         #print i, ' ',k
         page = smeared_data[k]
         page[page>maxval] = maxval
-        cdata = np.array([[0  ,1,1,1],
-                          [.01 ,1,1,1],
-                          [.25,0.8,.8,1],
-                          [.5 ,0,.8,.8],
-                          [.7 ,1,1,0],
-                          [.85 ,1,0,0],
-                          [1  ,0,0,0]])
-        cdict = {'red':   [], 'green': [], 'blue':  []}
-        for xi in range(cdata.shape[0]):
-            cdict['red']   += [(cdata[xi, 0], cdata[xi, 1], cdata[xi, 1])]
-            cdict['green'] += [(cdata[xi, 0], cdata[xi, 2], cdata[xi, 2])]
-            cdict['blue']  += [(cdata[xi, 0], cdata[xi, 3], cdata[xi, 3])]
-        cmap = matplotlib.colors.LinearSegmentedColormap('mine', cdict)
-        plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page, cmap=cmap, levels=mylevels)
+
+        plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page, cmap=mycolormap.cmap, levels=mylevels)
         #plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page, cmap=plt.cm.hot_r, levels=mylevels)
 
 plt.axes().get_yaxis().set_ticks([(i+0.5)*dZ for i in range(len(proteinList))])

### 2014-09-08 paper/paper.tex
work on getting contour plots unified (incomplete) Tested everything on bennet.

@@
   \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
   \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
@@
   \includegraphics[width=\textwidth]{../paper/plot-ave}
-  \caption{\fixme{Look into unifying the color scale, and adding a
-      scale bar.} Arrows depicting global maxima in space and local
+  \caption{Arrows depicting global maxima in space and local
     maxima in

### 2014-09-08 paper/mycolormap.py

@@ -15,5 +15,5 @@ for i in range(cdata.shape[0]):
     cdict['blue']  += [(cdata[i, 0], cdata[i, 3], cdata[i, 3])]
 cmap = matplotlib.colors.LinearSegmentedColormap('mine', cdict)
 
-pancake_levels = np.arange(0, 41.0, 1)
-pill_levels = np.arange(0, 81.0, 1)
+pancake_levels = np.arange(0, 961, 20)
+pill_levels = np.arange(0, 701, 20)

### 2014-09-08 paper/plot-arrow-ave.py

@@ -58,9 +58,9 @@ col_0x = 0.0          # -5.0
 col_1x = col_0x + 4.5 # 1.0
 col_2x = col_1x + 4.0 # 8.0
 col_3x = col_2x + 4.0 # 14.5
-color_bar_x = col_3x + 2.5
-col_4x = color_bar_x + 3
-pill_bar_x = col_4x + 2
+color_bar_x = col_3x + 1.5
+col_4x = color_bar_x + 4.0
+pill_bar_x = col_4x + 1.0
 
 left_annotate_x = col_0x - 3
 bottom_annotate_y = row_0y - 4
@@ -71,7 +71,7 @@ x_position_m2 = col_2x
 y_position_m2 = row_my
 
 viewport_xmin = left_annotate_x - 4
-viewport_xmax = pill_bar_x + 2
+viewport_xmax = pill_bar_x + 4.0
 viewport_ymin = bottom_annotate_y
 viewport_ymax = row_my + 4
 
@@ -166,10 +166,13 @@ for arg_num in range(len(arg_set)):
     time_max = np.max(data[arg_num])
 
     levels = mycolormap.pancake_levels
-    levels = np.arange(0, 41.0, 1)
+    scaling = 1
+    barlabel = 'molecules/square micron'
     if 'p/' in arg_set[arg_num]:
         levels = mycolormap.pill_levels
-    cs = ax.contourf(Xrot, Yrot, data[arg_num], cmap=mycolormap.cmap, origin='lower',levels=levels)
+        scaling = 1e-3
+        barlabel = 'thousand molecules/square micron'
+    cs = ax.contourf(Xrot, Yrot, data[arg_num]*scaling, cmap=mycolormap.cmap, origin='lower', levels=levels)
 
     if arg_num in [1,8]:
         if arg_num == 1:
@@ -178,7 +181,8 @@ for arg_num in range(len(arg_set)):
         else:
             axColor = plt.axes([in_viewport_x(pill_bar_x), in_viewport_y(color_bar_y),
                                 0.02, in_viewport_y(color_bar_height)])
-        plt.colorbar(cs, cax=axColor)
+        cb = plt.colorbar(cs, cax=axColor)
+        cb.set_label(barlabel)
 
     ax.add_artist(matplotlib.patches.Rectangle((col_1x-1.5,row_my), 3, 0.1, facecolor='b'))
     ax.text(col_1x, row_my - 0.3, r'$3\mu$',

### 2014-09-08 pyplots/image_plot.py

@@ -61,13 +61,14 @@ for i in range(len(proteins)):
     #minval = timemin(proteins[i].dataset[int(start_time/dump_time_step):])
     nlevels = 20
     mylevels = np.linspace(0,(1+1.0/nlevels)*maxval,nlevels)
+    mylevels = mycolormap.pill_levels
     Z, Y = np.meshgrid(np.arange(0,proteins[i].dataset[0].shape[1],1),
                        np.arange(0,proteins[i].dataset[0].shape[0],1))
 #generate a sequence of .png's for each file (printed time step). these will be used to create a gif.
     for k in kvals:
         page = proteins[i].dataset[k]
         page[page>maxval] = maxval
-        plt.contourf(Y+k*dY, proteins[0].datashape[1]-Z+i*dZ, page, cmap=mycolormap.cmap, levels=mylevels)
+        plt.contourf(Y+k*dY, proteins[0].datashape[1]-Z+i*dZ, page/1e3, cmap=mycolormap.cmap, levels=mylevels)
 plt.axes().get_yaxis().set_ticks([(i+0.5)*dZ for i in range(len(proteinList))])
 plt.axes().get_yaxis().set_ticklabels(proteinLabels)
 plt.axes().get_xaxis().set_ticks([(0.5+k)*dY for k in kvals[::int(2.5*skip_times)]])
@@ -83,8 +84,10 @@ plt.xlabel('time (s)')
 from mpl_toolkits.axes_grid1 import make_axes_locatable
 divider = make_axes_locatable(plt.gca())
 cax = divider.append_axes("right", "3%", pad="1%")
-cbar = plt.colorbar(cax=cax,ticks=[0,maxval])
-cbar.ax.set_yticklabels(['0', 'max'])
+# cbar = plt.colorbar(cax=cax,ticks=[0,maxval])
+# cbar.ax.set_yticklabels(['0', 'max'])
+cbar = plt.colorbar(cax=cax)
+cbar.ax.set_label('thousand molecules per square micron')
 
 
 #plt.colorbar(ticks=[])

### 2014-09-08 pyplots/single-image-plot.py

@@ -59,22 +59,24 @@ for i in range(len(proteinList)):
     for j in range(len(times)):
         image_data_file = job_string +str(proteinList[i])+'/images/single-'+str(times[j])+'.dat'
         #image_data_file = job_string +str(proteinList[i])+'/images/real-gauss-single-'+str(times[j])+'.dat'
-        temp =  = np.loadtxt(image_data_file) #this is in microns green light at 500nm,
-        smeared_data[j] = np.zeros((temp.shape[0], temp.shape[1]))
-        smeared_data[j][:,:] = smeared_data[j][::4,::4] # keep every fourth data point
+        temp = np.loadtxt(image_data_file) #this is in microns green light at 500nm,
+        smeared_data[j] = np.zeros_like(temp[::4,::4])
+        smeared_data[j][:,:] = temp[::4,::4] # keep every fourth data point
     dZ = smeared_data[0].shape[1]*1.05
     dY = smeared_data[0].shape[0]*2.00/skip_times
     Z, Y = np.meshgrid(np.arange(0,smeared_data[0].shape[1],1),
                        np.arange(0,smeared_data[0].shape[0],1))
     maxval = timemax(smeared_data)
+    print 'maxval for', proteinList[i], 'is', maxval
     mylevels = np.linspace(0,(1+1.0/nlevels)*maxval,nlevels)
-    mylevels = mycolormap.pill_levels
+    #mylevels = mycolormap.pill_levels
+    mylevels = np.arange(0, 1401, 10)
     for k in range(len(smeared_data)):
         #print i, ' ',k
         page = smeared_data[k]
         page[page>maxval] = maxval
 
-        plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page/1e3, cmap=mycolormap.cmap, levels=mylevels)
+        plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page, cmap=mycolormap.cmap, levels=mylevels) # FIXME levels=mylevels
         #plt.contourf(Y+k*dY, smeared_data[0].shape[1]-Z+i*dZ, page, cmap=plt.cm.hot_r, levels=mylevels)
 
 plt.axes().get_yaxis().set_ticks([(i+0.5)*dZ for i in range(len(proteinList))])
@@ -100,5 +102,6 @@ cbar.ax.set_label('thousand molecules per square micron')
 
 #plt.colorbar(ticks=[])
 plt.tight_layout()
[…]

### 2014-09-09 pyplots/single-image-creation.py
automatically run single-image-creation.py to generate data for image. Tested everything on bennet.

@@ -50,7 +50,6 @@ def gaussian_smear(data,wavelength):
     sigma = .21*wavelength/N_A #n_sin_theta can reach 1.4 to 1.6 in modern optics according to wikipedia
     dis = int(3*sigma/dx) #for now
     for num in range(new.shape[0]):
-        print 'num ',num
         norm = 0
         for i in np.arange(-dis,dis,1):
             xstart = 0

### 2014-09-10 paper/paper.tex
automatically run single-image-creation.py to generate data for image. Tested everything on bennet.
make color plots nicer Tested everything on bennet.

@@
 \begin{figure*}
-  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
-  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
+  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
   \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-  \caption{\fixme{We should figure out units and use the same levels
-      as in the main plot.  I also want to figure out why the two
-      plots look different, and make them the same size.  Can we just
-      do the gaussian} Contour plot images of the concentration of each protein
+  \caption{Contour plot images of the concentration of each protein
     species in a natural pill-shaped bacterium at regular intervals in

### 2014-09-10 paper/mycolormap.py

@@ -16,4 +16,4 @@ for i in range(cdata.shape[0]):
 cmap = matplotlib.colors.LinearSegmentedColormap('mine', cdict)
 
 pancake_levels = np.arange(0, 961, 20)
-pill_levels = np.arange(0, 701000, 20000)
+pill_levels = np.arange(0, 2001, 50)

### 2014-09-10 paper/plot-arrow-ave.py

@@ -109,7 +109,6 @@ ax.set_aspect('equal')
 ax.set_axis_off()
 
 data = [0]*(len(arg_set)+2)
-print len(data)
 for arg_num in range(len(arg_set)):
     data[arg_num] = np.loadtxt(contour_values[arg_num])
 
@@ -141,11 +140,11 @@ for arg_num in range(len(arg_set)):
                    [eigvec1[1,0], eigvec2[1,0]]])
     R = np.matrix([[0,-1],
                    [1, 0]])*R
-    print 'R', arg_set[arg_num], '\n', R
+    #print 'R', arg_set[arg_num], '\n', R
     Q = np.matrix([[Qxx, Qxy],
                    [Qxy, Qyy]])
-    print 'Q\n', Q
-    print 'diagonalized Q\n', np.transpose(R)*Q*R
+    #print 'Q\n', Q
+    #print 'diagonalized Q\n', np.transpose(R)*Q*R
 
     # Now let's rotate our coordinate system.
     Xrot = R[0,0]*X + R[1,0]*Y + X_position[arg_num]
@@ -164,6 +163,7 @@ for arg_num in range(len(arg_set)):
         cdict['green'] += [(cdata[i, 0], cdata[i, 2], cdata[i, 2])]
         cdict['blue']  += [(cdata[i, 0], cdata[i, 3], cdata[i, 3])]
     time_max = np.max(data[arg_num])
+    print 'time_max is', time_max
 
     levels = mycolormap.pancake_levels
     scaling = 1

### 2014-09-10 pyplots/single-image-plot.py

@@ -69,8 +69,8 @@ for i in range(len(proteinList)):
     maxval = timemax(smeared_data)
     print 'maxval for', proteinList[i], 'is', maxval
     mylevels = np.linspace(0,(1+1.0/nlevels)*maxval,nlevels)
-    #mylevels = mycolormap.pill_levels
-    mylevels = np.arange(0, 1401, 10)
+    mylevels = mycolormap.pill_levels
+    mylevels = np.arange(0, 1801, 10)
     for k in range(len(smeared_data)):
         #print i, ' ',k
         page = smeared_data[k]
@@ -98,7 +98,7 @@ cax = divider.append_axes("right", "3%", pad="1%")
 # cbar = plt.colorbar(cax=cax,ticks=[0,maxval])
 # cbar.ax.set_yticklabels(['0', 'max'])
 cbar = plt.colorbar(cax=cax)
-cbar.set_label('molecules per square micron')
+cbar.set_label('molecules/$\mu^2$')
 
 #plt.colorbar(ticks=[])
 plt.tight_layout()

### 2014-09-10 paper/paper.tex
major edits to text in paper Tested everything on quipu.

--- 2014-09-08 paper/paper.tex
@@
 regular sorts of oscillations seen in the computational work done by
-Huang et al\cite{huang2003dynamic}. We seek to apply a computational
-model to explore the more extreme or irregular cell shapes, in order
-to determine the limits of the steady cell oscillations seen by both
-theory and experiment.
+Huang et al\cite{huang2003dynamic}, who simulate more regular
+shapes. Thus there is an opportunity here to test previously used
+simulation models against more extreme experimental cases than have
+been seen thus far.  In this paper we apply a deterministic method and
+a stochastic method of simulation and compare them against Mannik's
+experimental findings.
 
@@
 combine into compound states~\cite{meinhardt2001pattern}.  In 2003
-Huang improved upon this work with a simple simulation model based on
-MinD-MinE combination, ATPase hydrolysis, and MinD membrane attachment
-that exhibits accurate MinD oscillations in
-cylindrical cells~\cite{huang2003dynamic}. In this model cytoplasmic
-MinD is more likely to attach to the membrane when MinD is already
-clustered there (following observed non-linear attachement of minD on
-the cell membrane), and is stationary once attached.  A number of
-studies have used an approach similar in that they do not rely on the
-ability of MinD to move along the walls and
+Huang improved upon this work with a simple and very successful
+simulation model based on MinD-MinE combination, ATPase hydrolysis,
+and MinD membrane attachment that exhibits accurate MinD oscillations
+in cylindrical cells~\cite{huang2003dynamic}. In this model
+cytoplasmic MinD is more likely to attach to the membrane when MinD is
+already clustered there (following observed non-linear attachement of
+minD on the cell membrane), and is stationary once attached.  A number
+of studies have used an approach similar in that they do not rely on
+the ability of MinD to move along the walls and
 cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
@@
 and attraction on the cell membrane~\cite{kruse2002dynamic,
-  howard2005cellular}.  Variations of the Huang 2003 model that
-stochasticly account for variations of molecular interaction
-\cite{fange2006noise} and monte-carlo simulations that implement this
-stochastic version of Huang's mean field reaction rates confirm the
-major results obtained by Huang's model, and more successfully predict
-experimentally observed oscillations in round cell
+  howard2005cellular}.  Experimental studies of the Min system's
+association with the cell membrane have also been
+made~\cite{hsieh2010direct}\cite{mileykovskaya2003effects}.
+
+Variations of the Huang 2003 model that stochasticly account for
+variations of molecular interaction \cite{fange2006noise} and
+monte-carlo simulations that implement this stochastic version of
+Huang's mean field reaction rates confirm the major results obtained
+by Huang's model, and more successfully predict experimentally
+observed oscillations in round cell
 phenotypes~\cite{drew2005polymerization, fange2006noise,
@@
 results.\cite{arjunan2010new}.  However, in general, the results of
-the stochastic and monte-carlo simulations are similar to those given
-by Huang's mean field results.
+the stochastic and monte-carlo simulations have so far yeilded similar
+results to those given by Huang's original, deterministic method of
+simulation.\fixme{Look at the papers again to verify and this and also
+  figure out and cite who says that the stochastic and the
+  deterministic methods of simulation have given similar results.
+  Saying more about these discussions is needed here, I think.
+  Something to the effect that until now there's no compelling reason
+  to avoid the deterministic simulations.}
 
-Previous studies have been made of the Min system's associtation with
-the cell membrane
-\cite{hsieh2010direct}\cite{mileykovskaya2003effects}.  Studies have
-shown as well that MinD binds preferentially to regions enriched with
-cadiolipin, an anionic phospholipid that collects on regions of high
-negative curvature. This mechanism has been incorporated into other
+\fixme{Following paragraph is awkward, and I don't think it's needed.}
+Studies have shown as well that MinD binds preferentially to regions
+enriched with cadiolipin, an anionic phospholipid that collects on
+regions of high negative curvature. This mechanism has been
+incorporated into other
 models.\cite{drew2005polymerization,cytrynbaum2007multistranded,renner2012mind,renner2012mind}
@@
 
-\section{Model, Methods, and Pill Shaped Cell}
-We implement the model of Huang \emph{et al.}  for the behavior of the
-MinD and MinE proteins inside the cell~\cite{huang2003dynamic}.
-Figure~\ref{fig:reactions} shows the reaction process.  The
-cytoplasmic MinD:ADP complex undergoes nucleotide exchange and is
-changed into the MinD:ATP complex.  This will naturally diffuse
-towards and attach to the cell membrane.  A cytoplasmic MinE will
-attach to the wall bound MinD:ATP complex and after a time will
-activate ATP hydrolosis.  This breaks up the complex, releasing MinE,
-phosphate, and MinD:ADP back into the cytoplasm.  The MinD:ADP will undergo
-nucleotide exchange and begin again the cyclic process.  This model is
-defined by a set of five reaction-diffusion equations:
+\section{Model, Methods, and Cell Shapes}
+We implement the reaction-diffusion model of Huang \emph{et
+  al.}~\cite{huang2003dynamic}.  Figure~\ref{fig:reactions} shows the
+reaction process.  The cytoplasmic MinD:ADP complex undergoes
+nucleotide exchange and is changed into the MinD:ATP complex.  This
+will naturally diffuse and attach to the cell membrane.  A cytoplasmic
+MinE will attach to the wall bound MinD:ATP complex and after a time
+will activate ATP hydrolosis.  This breaks up the complex, releasing
+MinE, phosphate, and MinD:ADP back into the cytoplasm.  The MinD:ADP
+will undergo nucleotide exchange and begin again the cyclic process.
+The model is defined by a set of five reaction-diffusion equations:
 
@@
 number of proteins per unit volume.  These concentration values are
-1273 $\mu m^{-3}$ and 446 $\mu m^{-3}$, respectively.
+1273 $\mu m^{-3}$ and 446 $\mu m^{-3}$, respectively. \fixme{It's been
+  a while so might want to check this to make sure it's true.}
 \begin{gather*}
@@
 
-In order to further our understanding of the results of various
-simulation approaches to this system, we have performed both a basic
-finite analysis, deterministic simulation that is spatially and
-temporally discrete, and a stochastic analysis that is spatially
-discrete but continuous in time.  Our stochastic simulation method
-follows the work of Kraus~\cite{kraus1996crosstalk} which in turn
-follows a method introduced by Gillespie~\cite{gillespie1977exact}.
+We have performed both a basic finite analysis, deterministic
+simulation that is spatially and temporally discrete, and a stochastic
+analysis that is spatially discrete but continuous in time.  Our
+stochastic simulation method follows the work of
+Kraus~\cite{kraus1996crosstalk} which in turn follows a method
+introduced by Gillespie~\cite{gillespie1977exact}.
 
@@
 variety of cell shapes and sizes.  Here we present a selection of
-those, first naturally occuring pill-shaped cells and then a
-number of flattened out shapes which reflect the experiments of Mannik
-\emph{et al.}, in which bacteria are confined within a thin slit of
-height $0.25\micron$ ~\cite{mannik2012robustness}. Viewed from the top
-down the cells will have the shapes described below and viewed from
-the side they have at their edges a semicircular protrusion (one may
-imagine the edges of a pancake). Central to our observations are the
-effects of cell size and so we show expanded cells that have the same
-thickness but increased dimensions in the two planar directions.  We
-present two shapes that are designed to replicate those published by
-Mannik, equilateral and iscosolese triangle shapes, and a 'V' shape of
-our own creation in order to best illustrate the effect of cell size
-on oscillation stability.
+these, first naturally occuring pill-shaped cells and then a number of
+flattened out shapes which reflect the experiments of Mannik \emph{et
+  al.}, in which bacteria are confined within a thin slit of height
+$0.25\micron$ ~\cite{mannik2012robustness}. Viewed from the top down
+the cells will show the shapes described below and viewed from the
+side they show at their edges a semicircular protrusion (one may
+imagine the shape of a pancake). We have simulated and analyzed a
+number of these flattened shapes in addition to those shown below,
+including equilateral and iscosolese triangle shapes, shapes shaped
+like greater than signs, '$>$', and four-pronged 'starfish' shapes.
+For all of these we have varied the cell size, expanding the two
+dimensions that are tangent to the flattened surface from very small,
+'steady state' scales (which we discuss below) to scales twice that of
+the published Mannik shapes.  Our conclusions are based on all of this
+data, but we present here specific, illustrative examples: two
+flattened shapes that are designed to replicate those published by
+Mannik and two 'stadium' shapes that respectively have the same
+quadrupole moments of the two Mannik shapes.
 
@@
 
+\fixme{Is the following Kubitscheck paragraph needed?}
 Kubitschek has shown in multiple experiments that at the time of cell
@@
 
+\section{Naturally Occuring Pill Shaped Cells}
 \begin{figure*}
-  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
-  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
+  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
   \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
@@
 \emph{et al.} but differs in that we have added the end caps for a
-more natural shape, expecting similar results.  We test cells of
-radius $.5\micron$ and of lengths $2\micron$, $3\micron$, and
-$5\micron$ measured from the tip of one end cap to the tip of the
-other. In each case, we observe in the deterministic simulations a
-quick establishement (within a few periods) of extremely regular
-oscillatory behavoir that lasts indefinitely.  The stochastic results
-show oscillitions that are similarly regular in time, with periods
-that nearly match those of the deterministic (they differ roughly by a
-factor of .05). The stochastic results also show a slight variation in
-the height of the density maxima, but the peaks are still very well
-defined. The period increases with cell length, as shown in
+more natural shape, expecting similar results.
+
+This simple cell shape is a good starting point for observing in
+detail the dynamic interaction between the different stages of protein
+that lead to their qualitatively distinct behavoir. Figure
+\ref{image-p} shows the process in a series of frames taken from
+simulation animations for both the deterministic and stochastic
+simulations.  We have 'smeared out' the stochastic concentrations in a
+manner meant to reproduce the images shown by diffraction limited
+flourescence microscopy.  We do so using the two dimensional gaussian
+approximation developed by Zhang et all~\cite{zhang2007gaussian}.  In
+this approximation we use a numerical aperture value of 1.3, which is
+the same as used by mannik experimentally, and a wavelength of
+$650nm$.  Each frame is 2.5 seconds ahead of the last, and each image
+shows the concentration of a given state of protein (of the five
+described in the reaction model) summed over the coordinate orthogonal
+to the page.  The color scale for each protein state is set according
+to the maximum values observed.
+
+Figure~\ref{image-p} begins about 300 seconds into the simulation and
+shows a typical period of oscillation that in the pill shape repeates
+itself with a high degree of regularity, for both the deterministic
+and stochastic simulations.  At $t=0$ the cytoplasmic MinE is
+concentrated in the upper portion of the cell and is diffusing
+downward, where it will react with and stick to wall-bound MinD that
+is concentrated on the membrane in the lower portion of the cell.
+This process is in fact already well on its way, as seen by the
+significant concentration of wall bound MinD:MinE which is creeping
+down to the lower corner, removing the MinD from the membrane as it
+goes.  The removed MinD (cytoplasmic MinD:ADP) diffuses freely for a
+time before spontenously undergowing nucleotide exchange and shifting
+back into the MinD:ATP that is able to attach to the membrane.
+Diffusing a small distance away from the bottom of the cell will bring
+the protein into the MinE collection, where reactions will prevent it
+from collecting for any significant time on the membrane.  Diffusing
+further towards the upper end, however, while the MinE has not yet
+collected there, will allow MinD:ATP to accumulate with the other
+MinD:ATP, which is seen at seconds 10 through 15 in
+Figure~\ref{image-p}.  Eventually the MinE creeps all the way down to
+the bottom of the cell where it slowly runs out of wall bound MinD to
+react with, before diffusing back up and starting again on the upper
+portion of the cell. This is seen in seconds 15 through 20 in the
+figure.  \fixme{There is another paragraph after this in the latex
+  that I commented out because I thought we might be spending too much
+  time on the description}
+
+%%  At 15 seconds, the membrane-bound MinD:ATP has
+%% been essentially removed from the top end of the cell, and MinD:ATP
+%% has begun to bind to the membrane in the the lower half of the cell.
+%% At this stage, there is a high concentration of cytoplasmic MinE at
+%% the top of the cell, and by 16 seconds we begin to see the formation
+%% of a MinE ring just below the center of the cell.  At 18 seconds, the
+%% cell has reached its original state (reversed directionally), with
+%% MinD:ATP bound to the membrane on the lower third of the cell, a high
+%% concentration of cytoplasmic MinE in the upper half of the cell, and a
+%% MinE ring pushing downward on the membrane-bound MinD:ATP.
+
+We test cells of radius $.5\micron$ and of lengths $2\micron$,
+$3\micron$, and $5\micron$ measured from the tip of one end cap to the
+tip of the other. In each case, we observe in the deterministic
+simulations a quick establishement (within a few periods) of extremely
+regular oscillatory behavoir that lasts indefinitely.  The stochastic
+results show oscillitions that are similarly regular in time, with
+periods that nearly match those of the deterministic (they differ
+roughly by a factor of .05)\fixme{does this square with the
+  correlation data periods?}.
+
+While the stochastic results show periods that seem to have a high
+degree of regularity as well as similarity to the deterministic
+results, they do differ in the precise locations of the maxima.  While
+the deterministic simulations show maxima that are every time
+concentrated in the center of one of the cell ends, with a symmetric
+smear of protein going out laterally to either side, the stochastic
+simulations show maxima that, while always located somehwere in the
+end region of the cell, occur at different positions within this
+region.  This is reflected in Figure~\ref{image-p}, which shows
+periods that are the same and qualitative behavoir that is
+approximately the same, but also that there is variation in the
+details of the stochastic simulation maxima location.
+
+The period increases with cell length, as shown in
 Table~\ref{tab:pill-periods}, in agreement with the results of Huang
@@
 \end{table}
-
-This simple cell shape is a good starting point for observing in
-detail the dynamic interaction between the different stages of protein
-that lead to their qualitatively distinct behavoir. Figure
-\ref{image-p} shows the process in a series of frames taken from
-simulation animations for both the deterministic and stochastic
-simulations.  We have 'smeared out' the stochastic concentrations in a
-manner meant to reproduce the images shown by diffraction limited
-flourescence microscopy.  We do so using the two dimensional gaussian
-approximation developed by Zhang et all~\cite{zhang2007gaussian}.  In
-this approximation we use a numerical aperture value of 1.3, which is
-the same as used by mannik experimentally, and a wavelength of
-$509nm$, typical of green flourescent microscopy.  Each frame is 2.5
-seconds ahead of the last, and each image shows a the concentration of
-a given state of protein summed over the coordinate orthogonal to the
-page.  The color scale for each protein state is set according to the
-maximum values observed.
-
-At $t=0$ in Figs.~\ref{image-p}, the cytoplasmic MinE is concentrated
-in the lower portion of the cell and is diffusing upward, since it
-will react with and stick to wall-bound MinD that is concentrated on
-the membrane in the upper portion of the cell.  At the boundary
-between the cytoplasmic MinE and the membrane-bound MinD, there is a
-ring of the membrane-bound MinE:MinD complex, which is moving towards
-the upper end of the cell, removing the MinD from the membrane as it
-goes.  The MinD is removed from the membrane in its MinD:ADP form and
-diffuses freely for a time before spontenously undergowing nucleotide
-exchange and shifting back into the MinD:ATP that is able to attach to
-the membrane.  Diffusion away from the end of the cell will bring the
-protein into the MinE ring, where reactions will prevent it from
-collecting for any significant time on the membrane.  Diffusion
-further towards the upper end, however, while the MinE has not yet
-collected there, will allow MinD:ATP to accumulate with the other
-MinD:ATP, peaking at around 10 seconds in Figure~\ref{image-p}.  As
-the MinE ring approaches the end of the cell, seen in the seconds
-following 10, the only freely diffusing MinD:ADP that 'escapes' the
-MinE will be that which has diffused away from the the end of the cell
-and past the MinE ring towards the center.
-
-At 15 seconds, the membrane-bound MinD:ATP has been essentially
-removed from the top end of the cell, and MinD:ATP has begun to bind
-to the membrane in the the lower half of the cell.  At this stage,
-there is a high concentration of cytoplasmic MinE at the top of the
-cell, and by 16 seconds we begin to see the formation of a MinE ring
-just below the center of the cell.  At 18 seconds, the cell has
-reached its original state (reversed directionally), with MinD:ATP
-bound to the membrane on the lower third of the cell, a high
-concentration of cytoplasmic MinE in the upper half of the cell, and a
-MinE ring pushing downward on the membrane-bound MinD:ATP.
 

### 2014-09-10 paper/paper.tex
more edits to paper Tested everything on quipu.

@@
 
-\section{Naturally Occuring Pill Shaped Cells}
 \begin{figure*}
@@
 \end{figure*}
+\section{Naturally Occuring Pill Shaped Cells}
 
@@
 We test cells of radius $.5\micron$ and of lengths $2\micron$,
-$3\micron$, and $5\micron$ measured from the tip of one end cap to the
-tip of the other. In each case, we observe in the deterministic
-simulations a quick establishement (within a few periods) of extremely
-regular oscillatory behavoir that lasts indefinitely.  The stochastic
-results show oscillitions that are similarly regular in time, with
-periods that nearly match those of the deterministic (they differ
-roughly by a factor of .05)\fixme{does this square with the
-  correlation data periods?}.
+$3\micron$, $4\micron$, and $5\micron$ measured from the tip of one
+end cap to the tip of the other \fixme{I'm running the 2,3,5 pills
+  again to make sure that everything in this paragraph is true}. In
+each case, we observe in the deterministic simulations a quick
+establishement (within a few periods) of extremely regular oscillatory
+behavoir that lasts indefinitely.  The stochastic results show
+oscillitions that are similarly regular in time, with periods that
+nearly match those of the deterministic (they differ roughly by a
+factor of .05) \fixme{does this square with the correlation data
+  periods?}. The regularity of the pill shape cell periods is
+discussed below, in our analysis of time correlation data \fixme{not
+  written yet}.  These periods increase with cell length, as shown in
+Table~\ref{tab:pill-periods}, in agreement with the results of Huang
+\emph{et al.}.
 
@@
 
-The period increases with cell length, as shown in
-Table~\ref{tab:pill-periods}, in agreement with the results of Huang
-\emph{et al.}.  The stochastic simulations show a similar pattern.
-The MinD maxima occur at the ends of the cell in a back and forth
-manner, and with the same approximate period.
-
 \begin{table}
   \begin{tabular}{|r|c|c|c|l|}
-    \hline
-    Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\
-    \hline
-    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2}
-    \hline
+    \hline Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\ \hline
+    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2} \hline
   \end{tabular}
@@
 
-\section{Stability Analysis}
-\label{sec:stability-analysis}
-We have found that in both methods of simulation there is a lower
-length scale that characterizes much of the behavoir.  Regular
-oscillatory behavoir between two poles at opposite ends of the longer
-cellular direction is found in cells which are long enough in one
-dimension for the reaction chain to be unstable but short enough in
-the perpendicular dimension to be stable.  The limits are seen when
-both dimensions are too short to be unstable, so that initial
-assymetry in protein concentration relaxes into a state of no
-oscillation.  In these cell sizes, the deterministic simulations show
-a motionless steady state and the stochastic simulations show random
-fluctuations without any bulk behavoir (see Figure~\ref{box-mannik}).
-
-In order to explain this theoretically, we have performed stability
-analysis of the five differential equations in an infinite slab that
-show a characteristic half wavelength in perturbative spatial
-oscillations at which the system becomes unstable.  This length is
-dependent upon slab thickness as shown in
-Figure~\ref{fig:stability-analysis}.  When increasing the lengths and
-widths of our simulated flattened cells, the cells stop exhibiting two
-pole oscillalitory behavior and instead exhibit multiple positions of
-maximization when the shortest distance across the cell is
-approximately equal to the characteristic half wavelength at the
-particular thickness at which we simulate (our simulations of cells
-with thickness $0.25\mu m$ corresponds to half wavelengths of $2.13\mu
-m$).  Huang~\cite{huang2003dynamic} performs a similar analysis for a
-cylindrical shape \fixme{is it cylindrical or 1d?} and finds
-characteristic half wavelengths of $2\mu m$.
-
-Decreasing the cell size in succesive steps, we can see the critical
-size at which the cell oscillations are quickly damped out.
-Figure~\ref{box-mannik} shows box plots of the largest cells simulated
-whose oscillations relax into the steady state solution.  Both have a
-long axis of roughly 2.2$\mu m$, in agreement with theory.
+\fixme{Originally the 'Stability Analysis' section came next.  I would
+  like to still mention the results of this, since Huang only did the
+  analysis on the cylinders, and we've done it on the flattened shapes
+  and shown that it works with those too.  But I don't know where to
+  fit in the paragraph or so that it would take.  For now I've just
+  put the whole section at the end of the paper.}
 
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-\fixme{should I say anything about different/large sizes?}  We have
-made movies out of color plots of MinD concentration, integrated along
-the flattened axis, in which each frame is seperated in simulation
-time by a half second. Our simulations include the two flattened cell
-shapes that are reported in Manniks paper, a few other 'irregular'
-shapes of our own creation, triangle shaped flattened cells, and a
-symetric 'stadium' shaped cell. For each of these shapes we have
-varied the size, from roughly twice the dimensions of Mannik's
-reported cells down to the smaller sizes refered to in
-section~\ref{sec:stability-analysis}.
+
+We have made and analyzed movies out of color plots of MinD
+concentration that are constructed as those in Figure~\ref{image-p},
+integrated along the flattened axis, in which each frame is seperated
+in simulation time by a half second. Figure~\ref{randst-plot-ave}
+illustrates what is seen in these movies. In his work Mannik presents
+arrow plots in which the arrow heads show the location of sequential
+MinD maxima within the cell. His plots for his two abnormal cell
+shapes are shown in the upper 'experiment' section of
+Figure~\ref{randst-plot-ave}.  Following this, we have created plots
+that show maxima that are global in space and local in time.  Of these
+maxima we only show those which have greater concentration than a
+chosen cutoff concentration, and also ignore maxima that appear
+temporalily and spatially adjacent to preceding maxima, in order to
+stop single spikes from appearing as many adjecent ones.  The overal
+effect is to accurately describe what is seen in our movies.
 
@@
 After the lower stability limit of
-section~\ref{sec:stability-analysis} has been surpassed, this
-qualitative behavoir doesn't seem to have size dependence until cells
-reach sizes that have more than twice the dimensions of the Mannik
-cells.  At this point the robust oscillations, while still evident,
-begin to lose their consistanty.  The Mannik reported cells already
-seem to be rather large (wild type cells are typically smaller than
-those observed my Mannik
+section~\ref{sec:stability-analysis} \fixme{this needs to be covered}
+has been surpassed, this qualitative behavoir doesn't seem to have
+size dependence until cells reach sizes that have more than twice the
+dimensions of the Mannik cells.  At this point the robust
+oscillations, while still evident, begin to lose their consistanty.
+The Mannik reported cells already seem to be rather large (wild type
+cells are typically smaller than those observed my Mannik
 \cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
-so we left off simulating cells any larger than twice this size. The
-movies show sharp peaks of MinD in specific locatations, typically at
+so we left off simulating cells any larger than twice this size.
+
+The movies show sharp peaks of MinD in specific locatations, typically at
 the edges of the cell and in regions of high radius of curvature,
@@
 
-\section{Interpretation of Data}
+\fixme{should I say anything about different/large sizes?}
+
+\section{Stability Analysis}
+\label{sec:stability-analysis}
+We have found that in both methods of simulation there is a lower
+length scale that characterizes much of the behavoir.  Regular
+oscillatory behavoir between two poles at opposite ends of the longer
+cellular direction is found in cells which are long enough in one
+dimension for the reaction chain to be unstable but short enough in
+the perpendicular dimension to be stable.  The limits are seen when
+both dimensions are too short to be unstable, so that initial
+assymetry in protein concentration relaxes into a state of no
+oscillation.  In these cell sizes, the deterministic simulations show
+a motionless steady state and the stochastic simulations show random
+fluctuations without any bulk behavoir (see Figure~\ref{box-mannik}).
+
+In order to explain this theoretically, we have performed stability
+analysis of the five differential equations in an infinite slab that
+show a characteristic half wavelength in perturbative spatial
+oscillations at which the system becomes unstable.  This length is
+dependent upon slab thickness as shown in
+Figure~\ref{fig:stability-analysis}.  When increasing the lengths and
+widths of our simulated flattened cells, the cells stop exhibiting two
+pole oscillalitory behavior and instead exhibit multiple positions of
+maximization when the shortest distance across the cell is
+approximately equal to the characteristic half wavelength at the
+particular thickness at which we simulate (our simulations of cells
+with thickness $0.25\mu m$ corresponds to half wavelengths of $2.13\mu
+m$).  Huang~\cite{huang2003dynamic} performs a similar analysis for a
+cylindrical shape \fixme{is it cylindrical or 1d?} and finds
+characteristic half wavelengths of $2\mu m$.
+
+Decreasing the cell size in succesive steps, we can see the critical
+size at which the cell oscillations are quickly damped out.
+Figure~\ref{box-mannik} shows box plots of the largest cells simulated
+whose oscillations relax into the steady state solution.  Both have a
+long axis of roughly 2.2$\mu m$, in agreement with theory.
+
 \section{Conclusion}

### 2014-09-11 paper/paper.tex

@@
   \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-  \caption{\fixme{We should figure out units and use the same levels
-      as in the main plot.  I also want to figure out why the two
-      plots look different, and make them the same size.  Can we just
-      do the gaussian} Contour plot images of the concentration of each protein
+  \caption{Contour plot images of the concentration of each protein
     species in a natural pill-shaped bacterium at regular intervals in

### 2014-09-11 paper/paper.tex
edits to mannik section of paper and small print statement added to dens-corr Tested everything on quipu.

@@
 
-We have made and analyzed movies out of color plots of MinD
-concentration that are constructed as those in Figure~\ref{image-p},
-integrated along the flattened axis, in which each frame is seperated
-in simulation time by a half second. Figure~\ref{randst-plot-ave}
-illustrates what is seen in these movies. In his work Mannik presents
-arrow plots in which the arrow heads show the location of sequential
-MinD maxima within the cell. His plots for his two abnormal cell
-shapes are shown in the upper 'experiment' section of
-Figure~\ref{randst-plot-ave}.  Following this, we have created plots
-that show maxima that are global in space and local in time.  Of these
-maxima we only show those which have greater concentration than a
-chosen cutoff concentration, and also ignore maxima that appear
-temporalily and spatially adjacent to preceding maxima, in order to
-stop single spikes from appearing as many adjecent ones.  The overal
-effect is to accurately describe what is seen in our movies.
-
-We have found that the deterministic simulations of the protein
-reaction sequence discussed above results in robust oscillatory
-behavoir of polar selection and oscillation in not only symmetrical
-shapes, such as the wildtype pill shape, but also in very
-assymetrical, flatttened cells, such as those studied by Mannik.
-After the lower stability limit of
-section~\ref{sec:stability-analysis} \fixme{this needs to be covered}
-has been surpassed, this qualitative behavoir doesn't seem to have
-size dependence until cells reach sizes that have more than twice the
-dimensions of the Mannik cells.  At this point the robust
-oscillations, while still evident, begin to lose their consistanty.
-The Mannik reported cells already seem to be rather large (wild type
-cells are typically smaller than those observed my Mannik
-\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
-so we left off simulating cells any larger than twice this size.
-
-The movies show sharp peaks of MinD in specific locatations, typically at
-the edges of the cell and in regions of high radius of curvature,
-followed by a spreading out of the MinD out into the cell, with no
-real bias towards any location, until it aggregates again in a
-specific location at the opposite edge of the cell, maximizing there.
-The pattern is repeated again and again with surprising consistency,
-which can be seen on the right of Figure~\ref{box-mannik}.  This is
-the same plotting method as our box plots above, here showing
-stochastic and deterministic simulations of cells that are the same
-shape and size of one of Mannik's reported cells.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
-  \caption{A comparison of our box plots that show a disparity between
-    the behavoir of the stochastic and deterministic simulations in
-    our Mannik cells.  The deterministic show a regular, robust
-    oscillatory behavoir between the two ends of the cell. The
-    stochastic simulation do show a general back and forth tendency
-    between two ends of the cell, but it is not robust and tends to
-    break down.}
-  \label{box-mannik}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
-  \caption{A comparison of our box plots that show a disparity between
-    the behavoir of the stochastic and deterministic simulations in
-    our Mannik cells.  The deterministic show a regular, robust
-    oscillatory behavoir between the two ends of the cell. The
-    stochastic simulation do show a general back and forth tendency
-    between two ends of the cell, but it is not robust and tends to
-    break down.}
-  \label{box-mannik}
-\end{figure}
-
-The results of these simulations differ significantly with Mannik's
-experimental results that show much less regular behavoir, with a
-large variation in the location of maxima.
-
-On the other hand, our stochastic simulations show both robust pole to
-pole oscillations in the symmetric cells and irregular behavoir in the
-assymetrical shapes, agreeing well with Mannik's experimental
-findings.
-
-Figure~\ref{arrow-pill-stadium} and Figure~\ref{randst-plot-ave} show
-color plots of time-averaged MinD overlayed by arrows depicting
-sequential maxima that are global in space and local in time.  Our
-stochastic method movies (and arrow plots of
-Figure~\ref{randst-plot-ave}) show irregular location of maxima that
-is similar to what is observed experimentally by Mannik. There is a
-general bias towards back and forth behavoir, which can be seen in the
-box plots of Figure~\ref{box-mannik}, but the behavoir is irregular
-and the location of the maxima vary a significant amount.  On the
-other hand, the deterministic simulations show behavoir that is much
-too regular when compared with experiment, exhibiting locations of
-maxima that do not vary.  The deterministic method is seen to be
-inadequate.
-
 \begin{figure*}
@@
 \end{figure*}
+
+We have made and analyzed movies out of color plots of MinD
+concentration that are constructed as those in Figure~\ref{image-p},
+integrated along the flattened axis, in which each frame is seperated
+in simulation time by a half second. Figure~\ref{randst-plot-ave}
+illustrates what is seen in these movies. In his work Mannik presents
+arrow plots in which the arrow heads show the location of sequential
+MinD maxima within the cell. His plots for his two abnormal cell
+shapes are shown in the upper 'experiment' section of
+Figure~\ref{randst-plot-ave}.  Following this, we have created plots
+that show maxima that are global in space and local in time.  Of these
+maxima we only show those which have greater concentration than a
+chosen cutoff concentration, and also ignore maxima that appear
+temporaly and spatially adjacent to preceding maxima, in order to
+stop single spikes from appearing as many adjecent ones.  The overall
+effect is to accurately describe what is seen in our movies.
+
+We have found that the deterministic simulations of the protein
+reaction sequence discussed above results in robust oscillatory
+behavoir of polar selection and oscillation in not only symmetrical
+shapes, such as the wildtype pill shape, but also in very
+assymetrical, flatttened cells, such as those studied by Mannik.
+After the lower size stability limit of
+section~\ref{sec:stability-analysis} \fixme{this needs to be covered}
+has been surpassed, this qualitative behavoir doesn't seem to have
+size dependence until cells reach sizes that have more than twice the
+dimensions of the Mannik cells.  At this point the robust
+oscillations, while still evident, begin to lose their consistency.
+The Mannik reported cells already seem to be rather large (wild type
+cells are typically smaller than those observed my Mannik
+\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
+so we left off simulating cells any larger than twice this size.
+
+Looking at Mannik's shape A in Figure~\ref{randst-plot-ave}, we can
+see that the deterministic simulation selects out two poles, one at
+either end of the cell, and that the MinD does not ever maximize in
+any other location.  All of the flattened cells shown in the figure
+span a time of 350s (as do Mannik's plots), which corresponds to
+\fixme{number of periods} periods for shape A.  The movies show sharp
+peaks at these poles, followed by a spreading out of the MinD out into
+the cell, with no real bias towards any location, until it aggregates
+again at the opposite pole, maximizing there.  The pattern is repeated
+again and again with surprising consistency, \fixme{talk about the
+  time correlation for the deterministic, once the plots are added.}
+
+The results of these deterministic simulations for shape A differ
+significantly with Mannik's experimental results that show much less
+regular behavoir, with a large variation in the location of maxima,
+shown in the experiment section of Figure~\ref{randst-plot-ave}.
+
+The deterministic results of shape B are slightly different, as can be
+seen in the figure.  Here we can see that the proteins maximize on the
+rightward cell wall while on the way to their corner maxima locations.
+Watching the movies, the proteins seem to travel along the wall, from
+corner to corner and back.  This behavoir is still more irregular than
+that of the Mannik experiments, which seem to show some right-left
+back and forth behavoir in a few areas, as opposed to the straight
+pole to pole (traveling along the wall).
+
+These comparisons illustrate our first finding, which is that in
+irregular cell shapes, the deterministic method of simulation is indeed
+inadequate in representing and predicting experimental behavoir.
+
+On the other hand, our stochastic simulations show both robust pole to
+pole oscillations in the symmetric cells and irregular behavoir in the
+assymetrical shapes, agreeing well with Mannik's experimental
+findings.
+
+Figure~\ref{arrow-pill-stadium} and Figure~\ref{randst-plot-ave} show
+color plots of time-averaged MinD overlayed by arrows depicting
+sequential maxima that are global in space and local in time.  Our
+stochastic method movies (and arrow plots of
+Figure~\ref{randst-plot-ave}) show irregular location of maxima that
+is similar to what is observed experimentally by Mannik. There is a
+general bias towards back and forth behavoir, which can be seen in the
+box plots of Figure~\ref{box-mannik}, but the behavoir is irregular
+and the location of the maxima vary a significant amount.  On the
+other hand, the deterministic simulations show behavoir that is much
+too regular when compared with experiment, exhibiting locations of
+maxima that do not vary.  The deterministic method is seen to be
+inadequate.
 
@@
   \label{box-stadium}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
+  \caption{A comparison of our box plots that show a disparity between
+    the behavoir of the stochastic and deterministic simulations in
+    our Mannik cells.  The deterministic show a regular, robust
+    oscillatory behavoir between the two ends of the cell. The
+    stochastic simulation do show a general back and forth tendency
+    between two ends of the cell, but it is not robust and tends to
+    break down.}
+  \label{box-mannik}
+\end{figure}
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
+  \caption{A comparison of our box plots that show a disparity between
+    the behavoir of the stochastic and deterministic simulations in
+    our Mannik cells.  The deterministic show a regular, robust
+    oscillatory behavoir between the two ends of the cell. The
+    stochastic simulation do show a general back and forth tendency
+    between two ends of the cell, but it is not robust and tends to
+    break down.}
+  \label{box-mannik}
 \end{figure}

### 2014-09-11 correlation_box.sh

@@ -8,8 +8,8 @@ echo starting !
 # srun --job-name="corr randst 18.60 28.60 94.00 full_array 0.00 1020.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 0.00 1020.00 &
 # srun --job-name="corr randst 18.60 28.60 94.00 exact 0.00 1800.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 exact 0.00 1800.00 &
 
-# srun --job-name="corr stad 2.35 1.32 full 0.00 10000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 full_array 0.00 10000.00 &
-# srun --job-name="corr stad 2.35 1.32 exact 0.00 6000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 exact 0.00 6000.00 &
+srun --job-name="corr stad 2.35 1.32 full 0.00 10000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 full_array 0.00 13500.00 &
+srun --job-name="corr stad 2.35 1.32 exact 0.00 6000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 exact 0.00 8400.00 &
 
 # srun --job-name="corr stad 2.92 1.18 full 0.00 1410.00" python pyplots/density-correlation.py stad 0.25 2.92 1.18 0.00 15.00 full_array 0.00 1410.00 &
 # srun --job-name="corr stad 2.92 1.18 exact 0.00 910.00" python pyplots/density-correlation.py stad 0.25 2.92 1.18 0.00 15.00 exact 0.00 910.00 &

### 2014-09-11 pyplots/density-correlation.py

@@ -34,6 +34,7 @@ dt = time_step*print_denominator
 #following version of readbox selects out NflD
 def readbox(name):
     data = np.loadtxt(name, converters = {0: ignoreme, 1: ignoreme})
+    print 'data.shape[1]*dt = ',data.shape[1]*dt
     data_stop_index = int(end/dt)
     print 'start time = 0, end_time = ',end
     print 'this is the time covered by the entire data set that youre using'

### 2014-09-16 paper/paper.tex
Added correlation plots to paper and accompanying data git, removed boxplots from paper Tested everything on quipu.

@@
 
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation-rl.pdf}
+  \caption{No caption}
+  \label{corr-pill}
+\end{figure}
+
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
-  \caption{A comparison of our box plots that show the similarity
-    between the stadium shapes simulated stochastically and
-    deterministically.  Both show regular oscillatory maxima with
-    similar periods.  This is in contrast to our boxpplot comparison
-    of one of the Mannik shapes in Figure~\ref{box-mannik}}
-  \label{box-stadium}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
+%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
+%%   \caption{A comparison of our box plots that show the similarity
+%%     between the stadium shapes simulated stochastically and
+%%     deterministically.  Both show regular oscillatory maxima with
+%%     similar periods.  This is in contrast to our boxpplot comparison
+%%     of one of the Mannik shapes in Figure~\ref{box-mannik}}
+%%   \label{box-stadium}
+%% \end{figure}
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
-  \caption{A comparison of our box plots that show a disparity between
-    the behavoir of the stochastic and deterministic simulations in
-    our Mannik cells.  The deterministic show a regular, robust
-    oscillatory behavoir between the two ends of the cell. The
-    stochastic simulation do show a general back and forth tendency
-    between two ends of the cell, but it is not robust and tends to
-    break down.}
-  \label{box-mannik}
-\end{figure}
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
-  \caption{A comparison of our box plots that show a disparity between
-    the behavoir of the stochastic and deterministic simulations in
-    our Mannik cells.  The deterministic show a regular, robust
-    oscillatory behavoir between the two ends of the cell. The
-    stochastic simulation do show a general back and forth tendency
-    between two ends of the cell, but it is not robust and tends to
-    break down.}
-  \label{box-mannik}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
+%%   \caption{A comparison of our box plots that show a disparity between
+%%     the behavoir of the stochastic and deterministic simulations in
+%%     our Mannik cells.  The deterministic show a regular, robust
+%%     oscillatory behavoir between the two ends of the cell. The
+%%     stochastic simulation do show a general back and forth tendency
+%%     between two ends of the cell, but it is not robust and tends to
+%%     break down.}
+%%   \label{box-mannik}
+%% \end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
+%%   \caption{A comparison of our box plots that show a disparity between
+%%     the behavoir of the stochastic and deterministic simulations in
+%%     our Mannik cells.  The deterministic show a regular, robust
+%%     oscillatory behavoir between the two ends of the cell. The
+%%     stochastic simulation do show a general back and forth tendency
+%%     between two ends of the cell, but it is not robust and tends to
+%%     break down.}
+%%   \label{box-mannik}
+%% \end{figure}
 
@@
 \fixme{should I say anything about different/large sizes?}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation-rl.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation-rl.pdf}
+  \caption{Correlation for A shapes}
+  \label{corr-A}
+\end{figure}
 
@@
 No conclusion :(
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation-rl.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation-rl.pdf}
+  \caption{Correlation for B shapes}
+  \label{corr-B}
+\end{figure}
+
 \bibliography{paper}

### 2014-09-16 correlation_box.sh

@@ -5,7 +5,7 @@ echo starting !
 # srun --job-name="corr randst 18.50 18.50 95.00 full_array 0.00 4500.00" python pyplots/density-correlation.py randst 0.25 18.50 18.50 95.00 15.00 full_array 0.00 4500.00 &
 # srun --job-name="corr randst 18.50 18.50 95.00 exact 0.00 5000.00" python pyplots/density-correlation.py randst 0.25 18.50 18.50 95.00 15.00 exact 0.00 5000.00 &
 
-# srun --job-name="corr randst 18.60 28.60 94.00 full_array 0.00 1020.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 0.00 1020.00 &
+# srun --job-name="corr randst 18.60 28.60 94.00 full_array 0.00 1020.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 0.00 1000.00 &
 # srun --job-name="corr randst 18.60 28.60 94.00 exact 0.00 1800.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 exact 0.00 1800.00 &
 
 # srun --job-name="corr stad 2.35 1.32 full 0.00 10000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 full_array 0.00 13500.00 &
@@ -42,29 +42,29 @@ echo starting !
 #     echo $i
 # done
 
-srun --job-name="corr p 3.00 0.50 full 0.00 6000.00" python pyplots/density-correlation.py p 3.00 0.50 0.00 0.00 15.00 full_array 0.00 600.00 &
-srun --job-name="corr p 3.00 0.50 exact 0.00 6000.00" python pyplots/density-correlation.py p 3.00 0.50 0.00 0.00 15.00 exact 0.00 1000.00 &
-cd ../new-protein-0
-srun --job-name="corr p 3.00 0.50 full 0.00 6000.00" python pyplots/density-correlation.py p 3.00 0.50 0.00 0.00 15.00 full_array 0.00 300.00 &
-srun --job-name="corr p 3.00 0.50 exact 0.00 6000.00" python pyplots/density-correlation.py p 3.00 0.50 0.00 0.00 15.00 exact 0.00 1000.00 &
-cd ../new-protein-1
[…]

### 2014-09-16 pyplots/correlation-plot.py

@@ -14,7 +14,7 @@ start = float(sys.argv[8])
 end  = float(sys.argv[9])
 
 if (sys.argv[10] != "auto") and (sys.argv[10] != "rl"):
-    print 'The last command line argument, after the time, should be either \"auto\" or \"rl\"'
+    print 'The command line argument, after the time, should be either \"auto\" or \"rl\"'
     print 'for auto-correlation or right-left correlation'
     exit(1)
 corr_type = sys.argv[10]
@@ -26,13 +26,13 @@ print_denominator = 1000;
 dt = time_step*print_denominator
 
 def notify_reading_file(f):
-    #print 'reading', f
-    #assert os.system('git add -f %s' % f) == 0, "Couldn't git add %s!" % f
+    print 'reading', f
+    assert os.system('git add -f %s' % f) == 0, "Couldn't git add %s!" % f
     pass
 
 #########################################
 
-num_of_data_files = 2
+num_of_data_files = 1
 def create_data_array(sim_type):
     data_array = []
     init_weight_array = []
@@ -54,6 +54,8 @@ def create_data_array(sim_type):
             elif corr_type == "rl":
                 data_file = '../new-protein-%d/'%(i) + job_string + 'fast-correlation-right-left.dat'
         notify_reading_file(data_file)
+        print 'loading ',data_file
+#        if data_file == ""
         new_data = np.loadtxt(data_file,skiprows=1)
         time_of_total_data = np.loadtxt(data_file)[0][1] - np.loadtxt(data_file)[0][0]
         init_weight_array.append(-new_data[0] + time_of_total_data) # the new_data[0] is an array of the times
@@ -115,7 +117,8 @@ for i in range(len(correlation_arrays)):
 #Following is for the decay modelling:
 max_Cs = []
 max_times = []
-num_calc_periods = 5
+num_calc_periods = int(sys.argv[11])
+
 for i in range(3,len(time_array[3:-3])):
     if (correlation_arrays[0][i] >= correlation_arrays[0][i-1]) and (correlation_arrays[0][i] > correlation_arrays[0][i+1]):
         if (correlation_arrays[0][i] >= correlation_arrays[0][i-2]) and (correlation_arrays[0][i] >= correlation_arrays[0][i+2]):
@@ -125,9 +128,7 @@ for i in range(3,len(time_array[3:-3])):
                 if len(max_Cs) > num_calc_periods:
                     break
 
-
-
[…]

### 2014-09-16 pyplots/density-correlation.py

@@ -28,15 +28,16 @@ dt = time_step*print_denominator
 
 #following version of readbox selects out NflD
 def readbox(name):
-    for i in range(100,10000,22):
-        try:
-            data = np.loadtxt(name, usecols=tuple(range(0,int(i/dt))), converters = {0:ignoreme, 1:ignoreme})
-        except (ValueError,IndexError):
-            data = np.loadtxt(name, usecols=tuple(range(0,int((i-22)/dt))), converters = {0:ignoreme, 1:ignoreme})
-            print "The end of the data in use occurs at %d seconds"%(i-22)
-            break
+    data = np.loadtxt(name, converters = {0:ignoreme, 1:ignoreme})
+    # for i in range(100,10000,22):
+    #     try:
+    #         data = np.loadtxt(name, usecols=tuple(range(0,int(i/dt))), converters = {0:ignoreme, 1:ignoreme})
+    #     except (ValueError,IndexError):
+    #         data = np.loadtxt(name, usecols=tuple(range(0,int((i-22)/dt))), converters = {0:ignoreme, 1:ignoreme})
+    #         print "The end of the data in use occurs at %d seconds"%(i-22)
+    #         break
     global end
-    end = (len(data[0])*dt)-10 #a bit lesst than full data set by default
+    end = (len(data[0])*dt)-10 #a bit less than full data set by default
     if len(sys.argv) > 9:
         end  = float(sys.argv[9])
     data_stop_index = int(end/dt)

### 2014-09-16 paper/paper.tex
minor figure tweak and shift figures around Tested everything on bennet.

@@
 
+\begin{figure*}
+  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
+  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+  \caption{Contour plot images of the concentration of each protein
+    species in a natural pill-shaped bacterium at regular intervals in
+    time (one second intervals), with darker regions indicating higher
+    concentration. The upper plots shows results from the
+    deterministic simulation and the lower shows results from the
+    stochastic simulation.  The cells pictured are $4\micron$ in
+    length, measured from end to end.  The order of frames is such
+    that individual MinD proteins begin at the bottom of the plot (in
+    the MinD:ATP state in the cytoplasm), and progress upward until
+    they reach the MinE:MinD:ATP membrane-bound complex.  At that
+    point, they will spontaneously dissociate into cytoplasmic MinE
+    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
+    densities plotted are integrated along the axis orthogonal to the
+    page, and the color scale is chosen separately for each species
+    with black as the maximum value over space and time.  The
+    stochastic densities are smeared out over space using a guassians
+    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
+  \label{image-p}
+\end{figure*}
+
 We mean to investigate the geometric limits of the Min system
@@
 
-\begin{figure*}
-  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
-  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
-  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-  \caption{Contour plot images of the concentration of each protein
-    species in a natural pill-shaped bacterium at regular intervals in
-    time (one second intervals), with darker regions indicating higher
-    concentration. The upper plots shows results from the
-    deterministic simulation and the lower shows results from the
-    stochastic simulation.  The cells pictured are $4\micron$ in
-    length, measured from end to end.  The order of frames is such
-    that individual MinD proteins begin at the bottom of the plot (in
-    the MinD:ATP state in the cytoplasm), and progress upward until
-    they reach the MinE:MinD:ATP membrane-bound complex.  At that
-    point, they will spontaneously dissociate into cytoplasmic MinE
-    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
-    densities plotted are integrated along the axis orthogonal to the
-    page, and the color scale is chosen separately for each species
-    with black as the maximum value over space and time.  The
-    stochastic densities are smeared out over space using a guassians
-    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
-  \label{image-p}
-\end{figure*}
 \section{Naturally Occuring Pill Shaped Cells}
@@
 
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation-rl.pdf}
+  \caption{No caption}
+  \label{corr-pill}
+\end{figure}
+
 While the stochastic results show periods that seem to have a high
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation-rl.pdf}
-  \caption{No caption}
-  \label{corr-pill}
-\end{figure}
-
-\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-
 \begin{figure*}
@@
 
-We have made and analyzed movies out of color plots of MinD
+\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
+
+We have made and analyzed movies out of the MinD
 concentration that are constructed as those in Figure~\ref{image-p},

### 2014-09-16 pyplots/correlation-plot.py

@@ -156,7 +156,8 @@ if (corr_type == "rl"):
     for i in range(len(correlation_arrays)):
         pylab.subplot(211)
         print 'oeriod ',period
-        pylab.title('Stochastic Correlation '+sys.argv[1]+' '+sys.argv[5]+' rate = %.3g sec^-1'%(rate)+' period = %.3g sec'%(period))
+        pylab.title('Stochastic %s %s 1/rate = %.3g sec period = %.3g sec (ratio %.2g)'
+                    % (sys.argv[1], sys.argv[5], 1/rate, period, 1/(rate*period)))
         pylab.plot(time_array,correlation_arrays[i],color=colors[i],label=labels[i])
         pylab.xlim(0,time_array[-1])
         pylab.ylim(np.amin(correlation_arrays),np.amax(correlation_arrays))

### 2014-09-16 paper/paper.tex
minor figure tweak and shift figures around Tested everything on bennet.
moved stability analysis to last paragraph in methods section of paper and small spelling fix in correlation plotting Tested everything on wentworth.

--- 2014-09-16 paper/paper.tex
@@
 \section{Introduction}
-It is vital that during the process of bacterial cell division a cell
-avoid minicelling, or splitting into daughter cells with lopsided
-volumes.  Instrumental to this process in \emph{Escherichia coli} is a
-long FtsZ polymer chain that develops on the cell wall in the center
-region of the cell, helping dictate the plane of
-division~\cite{adams2009bacterial, lutkenhaus2007assembly}. Previous
-experimental studies have shown that the MinC protein, known to
-inhibit the FtZ polymer\cite{shen2010examination}, exhibits pole to
-pole oscillatory behavior in conjunction with the MinD protein and a
-MinE that tends to be more localized in the center of the
-cell~\cite{hu1999topological, fu2001mine, shapiro2009and, yu1999ftsz,
-  raskin1999rapid}. The MinC protein will then have a higher time
-averaged concentration in the cell poles, as opposed to the center
-region of the cell, aiding in prohibiting the FtZ from developing in
-the wrong region.
+\fixme{Huang and those who reference him use the terms 'numerical
+  deterministic reaction-diffusion model' and 'stochastic version of
+  this model' for the stochastic.} It is vital that during the process
+of bacterial cell division a cell avoid minicelling, or splitting into
+daughter cells with lopsided volumes.  Instrumental to this process in
+\emph{Escherichia coli} is a long FtsZ polymer chain that develops on
+the cell wall in the center region of the cell, helping dictate the
+plane of division~\cite{adams2009bacterial,
+  lutkenhaus2007assembly}. Previous experimental studies have shown
+that the MinC protein, known to inhibit the FtZ
+polymer\cite{shen2010examination}, exhibits pole to pole oscillatory
+behavior in conjunction with the MinD protein and a MinE that tends to
+be more localized in the center of the cell~\cite{hu1999topological,
+  fu2001mine, shapiro2009and, yu1999ftsz, raskin1999rapid}. The MinC
+protein will then have a higher time averaged concentration in the
+cell poles, as opposed to the center region of the cell, aiding in
+prohibiting the FtZ from developing in the wrong region.
 
@@
 \end{figure*}
+
+Huang \emph{et al} ~\cite{huang2003dynamic} has has performed a linear
+stability analysis on the model which shows an upper limit on a steady
+state solution of $2\mu m$.  Cells with dimensions longer than this
+are unstable and show oscillatory behavoir in this direction, where
+cells that are shorter relax into a motionless steady state.  We have
+similarly performed a stability analysis in an infinite slab with a
+thickness equal to our flattened cells ($0.25\mu m$) and have found
+that an equivalent stability limit for half wavelengths is $2.13\mu
+m$. As expected, when decreasing the lengths and widths of our
+simulated flattened cells so that the shortest distance across the
+cell is less than this length, the cells stop exhibiting any
+oscillalitory behavior.  The deterministic simulations relax into a
+motionless state and the stochastic simulations exhibit multiple
+random locations of small maximization.
+
 \section{Naturally Occuring Pill Shaped Cells}
@@
 
-\section{Stability Analysis}
-\label{sec:stability-analysis}
-We have found that in both methods of simulation there is a lower
-length scale that characterizes much of the behavoir.  Regular
-oscillatory behavoir between two poles at opposite ends of the longer
-cellular direction is found in cells which are long enough in one
-dimension for the reaction chain to be unstable but short enough in
-the perpendicular dimension to be stable.  The limits are seen when
-both dimensions are too short to be unstable, so that initial
-assymetry in protein concentration relaxes into a state of no
-oscillation.  In these cell sizes, the deterministic simulations show
-a motionless steady state and the stochastic simulations show random
-fluctuations without any bulk behavoir (see Figure~\ref{box-mannik}).
-
-In order to explain this theoretically, we have performed stability
-analysis of the five differential equations in an infinite slab that
-show a characteristic half wavelength in perturbative spatial
-oscillations at which the system becomes unstable.  This length is
-dependent upon slab thickness as shown in
-Figure~\ref{fig:stability-analysis}.  When increasing the lengths and
-widths of our simulated flattened cells, the cells stop exhibiting two
-pole oscillalitory behavior and instead exhibit multiple positions of
-maximization when the shortest distance across the cell is
-approximately equal to the characteristic half wavelength at the
-particular thickness at which we simulate (our simulations of cells
-with thickness $0.25\mu m$ corresponds to half wavelengths of $2.13\mu
-m$).  Huang~\cite{huang2003dynamic} performs a similar analysis for a
-cylindrical shape \fixme{is it cylindrical or 1d?} and finds
-characteristic half wavelengths of $2\mu m$.
-
-Decreasing the cell size in succesive steps, we can see the critical
-size at which the cell oscillations are quickly damped out.
-Figure~\ref{box-mannik} shows box plots of the largest cells simulated
-whose oscillations relax into the steady state solution.  Both have a
-long axis of roughly 2.2$\mu m$, in agreement with theory.
-
 \section{Conclusion}

### 2014-09-16 pyplots/correlation-plot.py

@@ -155,7 +155,7 @@ if (corr_type == "rl"):
     pylab.figure()
     for i in range(len(correlation_arrays)):
         pylab.subplot(211)
-        print 'oeriod ',period
+        print 'period ',period
         pylab.title('Stochastic Correlation '+sys.argv[1]+' '+sys.argv[5]+' rate = %.3g sec^-1'%(rate)+' period = %.3g sec'%(period))
         pylab.plot(time_array,correlation_arrays[i],color=colors[i],label=labels[i])
         pylab.xlim(0,time_array[-1])

### 2014-09-16 paper/paper.tex

@@
 arrow plots in which the arrow heads show the location of sequential
-MinD maxima within the cell. His plots for his two abnormal cell
-shapes are shown in the upper 'experiment' section of
+MinD maxima within the cell.  These experimental plots for two abnormal cell
+shapes are shown in the upper `experiment' section of
 Figure~\ref{randst-plot-ave}.  Following this, we have created plots

### 2014-09-16 paper/paper.tex
write comparison and conclusion (with fixmes) Tested everything on bennet.

@@
 
-\section{Model, Methods, and Cell Shapes}
+\section{Model, Methods, and Cell Shapes}\label{sec:model-method-shapes}
 We implement the reaction-diffusion model of Huang \emph{et
@@
 flattened shapes that are designed to replicate those published by
-Mannik and two 'stadium' shapes that respectively have the same
+Mannik and two `stadium' shapes that respectively have the same
 quadrupole moments of the two Mannik shapes.
@@
   \includegraphics[width=\textwidth]{../paper/plot-ave}
-  \caption{Arrows depicting global maxima in space and local
-    maxima in
-    time overlayed on color plots of time averaged total MinD density.
-    A density threshold is chosen and only maxima above this threshold
-    are shown. The plots serve to illistrate what is observed in our
-    movies.  The simulation time covered in these is 1000 seconds
-    \fixme{this is not true yet - need to change the data once its
-      finished right now 2 of them are 1000 the others are like 980}.
-    The top row shows plots published by Mannik of the MinD maxima
-    behavoir and the bottom two rows show our pancake shapes that are
-    designed to have the same shape.  The middle row shows results
-    from the stochastic simulation and the bottom shows results from
-    the deterministic.  We can see that the stochastic method shows
-    behavoir that is similar to experiment while the deterministic
-    method shows maximization that is too regular and robust.}
+  \caption{We display here arrows depicting successive maxima in space
+    and and time overlayed on a color plot of the total MinD density
+    averaged over the same time period.  The simulation time covered
+    for the flattened cells is \fixme{340} seconds, which is the same
+    period of time depicted in the experimental data plots of Mannik
+    \emph{et al.}~\cite{mannik2012robustness}.  For the wild type pill
+    shape, we only cover \fixme{???} seconds, in order to provide a
+    useful comparison due to its shorter oscillation period.  The top
+    row shows plots published by Mannik of the MinD maxima behavoir
+    and the bottom two rows show our simulations using the stochastic
+    and deterministic algorithms, respectively.  We simulated
+    approximations to the two shapes observed by Mannik, which we call
+    \emph{shape A} and \emph{shape B}.  In addition, we studied two
+    flattened stadium shapes which we call \emph{stadium A} and
+    \emph{stadium B} corresponding in aspect ratio and thickness to
+    the two experimental shapes.  The spatial length scale of all the
+    figures shown was identical. Each of the flattened cell shapes
+    uses the same color scale for the number of proteins per unit
+    area.  Finally, we display the natural pill shape, which was also
+    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
+    different color scale to reflect the thicker cell containing more
+    proteins per cross-sectional area.  }
   \label{randst-plot-ave}
@@
 
-We have made and analyzed movies out of the MinD
-concentration that are constructed as those in Figure~\ref{image-p},
-integrated along the flattened axis, in which each frame is seperated
-in simulation time by a half second. Figure~\ref{randst-plot-ave}
-illustrates what is seen in these movies. In his work Mannik presents
+As describe in Section~\ref{sec:model-method-shapes}, we will focus on
+simulation of four flattened cell shapes: two shapes copied from
+Mannik's experiment~\cite{mannik2012robustness} (shape~\emph{A} and
+shape~\emph{B}), and for comparison two symmetrical stadium shapes
+that have the identical aspect ratio, thickness and volume (stadium
+\emph{A} and stadium \emph{B}).  These stadium shapes enable us to
+distinguish between the effect of cellular irregularity and that of
+overall size and aspect ratio.  We note that shape \emph{B} is more
+irregular than shape \emph{A}, and in particular features a prominant
+region of concavity on its left-hand side.  For each of these shapes
+(in addition to the wild type pill shape discussed previously) we have
+simulated in excess of \fixme{???} seconds of evolution of the MinD
+system using both the deterministic model of Huang~\fixme{cite} and
+the stochastic model of Huang~\fixme{cite}.
+
+From each of these flattened simulations, we have chosen a typical 350
+second segment to compare with the results of Mannik exemplified in
 arrow plots in which the arrow heads show the location of sequential
-MinD maxima within the cell.  These experimental plots for two abnormal cell
-shapes are shown in the upper `experiment' section of
-Figure~\ref{randst-plot-ave}.  Following this, we have created plots
-that show maxima that are global in space and local in time.  Of these
-maxima we only show those which have greater concentration than a
-chosen cutoff concentration, and also ignore maxima that appear
-temporaly and spatially adjacent to preceding maxima, in order to
-stop single spikes from appearing as many adjecent ones.  The overall
-effect is to accurately describe what is seen in our movies.
+MinD maxima within the cell (over the same time
+interval)~\cite{mannik2012robustness}.  This comparison is shown in
+Fig.~\ref{randst-plot-ave}.  In addition to arrows between successive
+maxima in space and time, we plot as a colored background the density
+of MinD protiens averaged over the same time period.  We note that we
+have manually verified that our (computer-generated) arrow plots also
+reflect a human interpretation of a movie of the same data.  Finally,
+for comparison we present the same plot for a wild-type cell, with a
+time period of \fixme{???}  seconds to account for its short period of
+oscillation.  In every case, including the wild type pill shape, we
+see irregularity in the location of the maxima when using the
+stochastic approach.  The deterministic method shows uniformly bipolar
+oscillation, with the exception of shape \emph{B}, which develops weak
+intermediate maxima on the right-hand edge of the cell.
 
-We have found that the deterministic simulations of the protein
-reaction sequence discussed above results in robust oscillatory
-behavoir of polar selection and oscillation in not only symmetrical
-shapes, such as the wildtype pill shape, but also in very
-assymetrical, flatttened cells, such as those studied by Mannik.
-After the lower size stability limit of
-section~\ref{sec:stability-analysis} \fixme{this needs to be covered}
-has been surpassed, this qualitative behavoir doesn't seem to have
-size dependence until cells reach sizes that have more than twice the
-dimensions of the Mannik cells.  At this point the robust
-oscillations, while still evident, begin to lose their consistency.
-The Mannik reported cells already seem to be rather large (wild type
-cells are typically smaller than those observed my Mannik
-\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}),
-so we left off simulating cells any larger than twice this size.
-
-Looking at Mannik's shape A in Figure~\ref{randst-plot-ave}, we can
-see that the deterministic simulation selects out two poles, one at
-either end of the cell, and that the MinD does not ever maximize in
-any other location.  All of the flattened cells shown in the figure
-span a time of 350s (as do Mannik's plots), which corresponds to
-\fixme{number of periods} periods for shape A.  The movies show sharp
-peaks at these poles, followed by a spreading out of the MinD out into
-the cell, with no real bias towards any location, until it aggregates
-again at the opposite pole, maximizing there.  The pattern is repeated
-again and again with surprising consistency, \fixme{talk about the
-  time correlation for the deterministic, once the plots are added.}
-
-The results of these deterministic simulations for shape A differ
-significantly with Mannik's experimental results that show much less
-regular behavoir, with a large variation in the location of maxima,
-shown in the experiment section of Figure~\ref{randst-plot-ave}.
-
-The deterministic results of shape B are slightly different, as can be
-seen in the figure.  Here we can see that the proteins maximize on the
-rightward cell wall while on the way to their corner maxima locations.
-Watching the movies, the proteins seem to travel along the wall, from
-corner to corner and back.  This behavoir is still more irregular than
-that of the Mannik experiments, which seem to show some right-left
-back and forth behavoir in a few areas, as opposed to the straight
-pole to pole (traveling along the wall).
-
-These comparisons illustrate our first finding, which is that in
-irregular cell shapes, the deterministic method of simulation is indeed
-inadequate in representing and predicting experimental behavoir.
-
-On the other hand, our stochastic simulations show both robust pole to
-pole oscillations in the symmetric cells and irregular behavoir in the
-assymetrical shapes, agreeing well with Mannik's experimental
-findings.
-
-Figure~\ref{arrow-pill-stadium} and Figure~\ref{randst-plot-ave} show
-color plots of time-averaged MinD overlayed by arrows depicting
-sequential maxima that are global in space and local in time.  Our
-stochastic method movies (and arrow plots of
-Figure~\ref{randst-plot-ave}) show irregular location of maxima that
-is similar to what is observed experimentally by Mannik. There is a
-general bias towards back and forth behavoir, which can be seen in the
-box plots of Figure~\ref{box-mannik}, but the behavoir is irregular
-and the location of the maxima vary a significant amount.  On the
-other hand, the deterministic simulations show behavoir that is much
-too regular when compared with experiment, exhibiting locations of
-maxima that do not vary.  The deterministic method is seen to be
-inadequate.
-
-Judging that at this point that we have a fair idea of how our two
-methods compare with experiment, we investigate the limits of the
-break down of regular activity, by simulating large, regular,
-'stadium' shapes.  These shapes have the flattened, pancake like form
-of the assymetric cells, but from the top down they look as pills
-do. In two dimensions they are composed of a rectangle with two half
-ellipse connected on either end.  They are also made to have a large
-volume that is similar to the Mannik shapes.
-
-We find that both the stochastic and the deterministic solutions show
-regular back and forth oscillations in the stadium shaped cells, as
-can be seen Figure~\ref{box-stadium}.  This suggests that it is the
-irregular, assymetric shape of the Mannik cells, not their size or
-their flattened nature, that causes these cells to exhibit
-irregularity in MinD oscillations.
-
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-full_array/plots/box-plot_D}
-%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-5_50-1_00-0_00-15_00-exact/plots/box-plot_D}
-%%   \caption{A comparison of our box plots that show the similarity
-%%     between the stadium shapes simulated stochastically and
-%%     deterministically.  Both show regular oscillatory maxima with
-%%     similar periods.  This is in contrast to our boxpplot comparison
-%%     of one of the Mannik shapes in Figure~\ref{box-mannik}}
-%%   \label{box-stadium}
-%% \end{figure}
-
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/box-plot_D}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-exact/plots/box-plot_D}
-%%   \caption{A comparison of our box plots that show a disparity between
-%%     the behavoir of the stochastic and deterministic simulations in
-%%     our Mannik cells.  The deterministic show a regular, robust
-%%     oscillatory behavoir between the two ends of the cell. The
-%%     stochastic simulation do show a general back and forth tendency
-%%     between two ends of the cell, but it is not robust and tends to
-%%     break down.}
-%%   \label{box-mannik}
-%% \end{figure}
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/box-plot_D}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-exact/plots/box-plot_D}
-%%   \caption{A comparison of our box plots that show a disparity between
-%%     the behavoir of the stochastic and deterministic simulations in
-%%     our Mannik cells.  The deterministic show a regular, robust
-%%     oscillatory behavoir between the two ends of the cell. The
-%%     stochastic simulation do show a general back and forth tendency
-%%     between two ends of the cell, but it is not robust and tends to
-%%     break down.}
-%%   \label{box-mannik}
-%% \end{figure}
-
-\fixme{specifically design other arrow plot (with many comparisons) to
-  illustrate point}
-
-Figure~\ref{arrow-compare-mannik} shows plots of total MinD
-concentration maxima that are global in space and local in time.  The
-tip of an arrow represents one of these maxima and the adjacent arrow
-(whose tail is touching the previous arrow's tip) points to the next
-such maxima in time.  Mannik \emph{et al.} have published similar
-plots of two of their cells, and we have attempted to replicate the
-shape of these cells in our simulation in order to compare.  We find
-that when we replicate the size as well as shape of their cells as
-near as possible, we do not see the disordered protein behavoir that
-they observe.  Instead we see a robust ability of the cell to find two
-prefered pole locations and to oscillate maxima back and forth very
-steadily between them.  When we increase the size of our cells, we
-indeed see multiple positions of maxima develop, but we never observe
-the random behavoir that they have observed experimentally.  This is
-perhaps due to the exact, continuous method we use when conducting
-simulations.  Stochastic methods would perhaps show more random
-behavoir at these sizes.  We consider this to be a limitation of the
-exact solution method.
-
-\fixme{should I say anything about different/large sizes?}
+%% We found that the deterministic simulations of the MinD system results
+%% in robust and regular oscillatory behavoir of polar selection and
+%% oscillation in not only symmetrical shapes, such as the wildtype pill
+%% shape, but also in very assymetrical, flatttened cells, such as those
+%% observed by Mannik.  We also examined larger and smaller versions of
+%% these shapes, and found this behavior to be very robust, from the
+%% minimum size to sustain oscillation (around \fixme{???} $\mu$m) up to
+%% around twice the cell size reported by Mannik.  At larger sizes than
+%% this, less regular oscillations occur using the deterministic method,
+%% but we note that the cells reported by Mannik are already considerably
+%% larger in volume than typical wild type
+%% cells~\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}.
 
@@
   \caption{Correlation for A shapes}
-  \label{corr-A}
+  \label{fig:corr-pancake-A}
 \end{figure}
 
+The predictions of the stochastic as seen in
+Fig.~\ref{randst-plot-ave} are roughly similar to the experimental
+results in terms of irregularity of the locations of maxima, although
+there are locations on the edges of the cells where experiment shows
+maxima occuring that we never see in our simulations, suggesting that
+the model does not precisely reflect the experiment.  We also note
+that the stadium shapes in Fig.~\ref{randst-plot-ave} appear
+qualitatively similar to the irregular shapes in terms of the
+locations of their maxima.  From these results, we conclude that the
+deterministic method is inadequate to explain experimental
+observations of the locations of density maxima of the MinD protein.
+
+However, Fig.~\ref{randst-plot-ave} leaves unclear the importance of
+irregularity versus overall thickness and aspect ratio in developing
+an understanding of the origin of the experimentally observed
+behavior.  Although in the movies the stadiums appear to display a
+more regular bipolar oscillation, the arrow plots do not provide a
+convincing demonstration.  To illustrate the difference in behavior
+between shape \emph{A} and stadium \emph{A}, we return in
+Fig.~\ref{fig:corr-pancake-A} to the correlation function between the
+number of proteins in a segment at the top of the cell and the number
+of proteins in a segment at the bottom of the cell.  We computed these
+correlation functions using over \fixme{???} seconds of simulation.
+We found with the stochastic method that the experimental shape
+\emph{A} has a coherence time of under 4 periods, while the
+corresponding stadium \emph{A} has a coherence time of 10 periods.  In
+each case, the deterministic method is perfectly periodic. This
+confirms that using the stochastic method the stadium shape does
+indeed have a far more regular bipolar oscillation than the irregular
+shape \emph{A}.  When we compare shape \emph{B} and stadium \emph{B},
+we see a similar effect, although both coherence times are somewhat
+smaller (2.7 and 6.2, respectively).  From these results we conclude
+that the irregularity seen experimentally is indeed exacerbated by the
+irregular shapes taken on by the cells forced into a thin slit.
+
 \section{Conclusion}
-No conclusion :(
+We have simulated flattened cell shapes similar to those observed
+experimentally by Mannik \emph{et al.}.  We find that the
+deterministic method~\fixme{cite} predicts behavior that completely
+contradicts what is seen experimentally: it predicts stable and
+periodic bipolar oscillation, with a minor intermediate maximum
+appearing in shape \emph{B}.  Thus we conclude that this method is
+inconsistent with experiment, and should not be relied upon for
+predictions of the behavior of the MinD system.
+
+In contrast, the stochastic method~\fixme{cite} predicts spatially
+irregular formation of maxima for all the flattened cells that we
+studied.  In order to better understand the irregular oscillations
+observed in experiment, we simulated flattened ``stadium'' shapes in
+order to distinguish between the effect of flattening and the effect
+of irregular shape.  We found that although the stadium cells
+exhibited somewhat more irregular locations of maxima than the
+wild-type cells, their oscillation was far more periodic and bipolar
+than the irregular cell shapes observed experimentally.  Thus we
+confirm that the disruption of the MinD oscillations seen by Mannik
+\emph{et al.} is largely due to the irregularity of cell shapes
+observed.
+
+\bibliography{paper}
+
 \begin{figure}
@@
 \end{figure}
-
-\bibliography{paper}
 

### 2014-09-17 paper/paper.tex
minor edit suggested by Jeff Tested everything on bennet.
edits to introduction in paper Tested everything on crystal.

@@
 the cell wall in the center region of the cell, helping dictate the
-plane of division~\cite{adams2009bacterial,
-  lutkenhaus2007assembly}. Previous experimental studies have shown
-that the MinC protein, known to inhibit the FtZ
-polymer\cite{shen2010examination}, exhibits pole to pole oscillatory
-behavior in conjunction with the MinD protein and a MinE that tends to
-be more localized in the center of the cell~\cite{hu1999topological,
-  fu2001mine, shapiro2009and, yu1999ftsz, raskin1999rapid}. The MinC
-protein will then have a higher time averaged concentration in the
-cell poles, as opposed to the center region of the cell, aiding in
-prohibiting the FtZ from developing in the wrong region.
+plane of
+division~\cite{adams2009bacterial,lutkenhaus2007assembly}. Previous
+experimental studies have shown that the MinC protein, known to
+inhibit the FtZ polymer\cite{shen2010examination}, exhibits pole to
+pole oscillatory behavior between both ends of the wild-type
+pill-shaped cell.  It thus has a higher time averaged concentration in
+the cell poles than in the center region, which aides in prohibiting
+the FtZ from developing in the wrong region.  The MinC is recruited to
+these poles by MinD, which ineracts with another protein, MinE, that
+is neccesary for MinD oscillation.~\cite{hu1999topological,
+  fu2001mine, shapiro2009and, yu1999ftsz, raskin1999rapid}.
 
-Studies have shown that the cell division process is capable of
-preventing minicelling for fairly perturbed cell
-shapes\cite{touhami2006temperature}. Varma et al. studied one
-particular example of a perturbed shape, a three-pronged tube, and
-found both experimental and simulation results\cite{varma2008min} that
-show oscillation. These oscillations seem to seek out the extreme
-poles in the cell shape\cite{corbin2002exploring}
-\cite{juarez2010changes}, and effectively prevent minicelling in most
-cases. However, Mannik et al. have also shown that there are
-limitations to this mechanism\cite{mannik2010bacteria}
-\cite{mannik2009bacterial}. One instance of this behavior is
-observable when the cell has been forced into a flattened, irregular
-shape. Oscillations in this sort of cell shape are far from the
-regular sorts of oscillations seen in the computational work done by
-Huang et al\cite{huang2003dynamic}, who simulate more regular
-shapes. Thus there is an opportunity here to test previously used
-simulation models against more extreme experimental cases than have
-been seen thus far.  In this paper we apply a deterministic method and
-a stochastic method of simulation and compare them against Mannik's
-experimental findings.
+Previous studies have shown that the minD protein system is capable of
+exhibiting oscillations in round shapes as well as in connected three
+pronged tube shapes~\cite{varma2008min}, in which the oscillations
+seem to seek out the extreme poles in the
+cell~\cite{corbin2002exploring} \cite{juarez2010changes}. However,
+Mannik \emph{et al.} have also shown that there are limitations to
+this capability~\cite{mannik2010bacteria}
+\cite{mannik2009bacterial}. They have experimentally forced E. Coli
+cells into flattened irregular shapes of $0.25\mu m$
+thickness. Oscillations in this type of cell shape lose their
+regularity, both temporally and spatially. This allows for an
+opportunity to test previously studied MinD simulation models against
+more extreme experimental cases than have been seen thus far.
 
@@
 association with the cell membrane have also been
-made~\cite{hsieh2010direct}\cite{mileykovskaya2003effects}.
+made~\cite{hsieh2010direct,mileykovskaya2003effects}.
 
 Variations of the Huang 2003 model that stochasticly account for
-variations of molecular interaction \cite{fange2006noise} and
-monte-carlo simulations that implement this stochastic version of
-Huang's mean field reaction rates confirm the major results obtained
-by Huang's model, and more successfully predict experimentally
-observed oscillations in round cell
-phenotypes~\cite{drew2005polymerization, fange2006noise,
-  huang2004min}. Biochemical models of broader scope have also been
-used to study the MinD system and show consistent
-results.\cite{arjunan2010new}.  However, in general, the results of
-the stochastic and monte-carlo simulations have so far yeilded similar
-results to those given by Huang's original, deterministic method of
-simulation.\fixme{Look at the papers again to verify and this and also
-  figure out and cite who says that the stochastic and the
-  deterministic methods of simulation have given similar results.
-  Saying more about these discussions is needed here, I think.
-  Something to the effect that until now there's no compelling reason
-  to avoid the deterministic simulations.}
+variations of molecular
+interaction~\cite{kerr2006division,fange2006noise} and monte-carlo
+simulations that implement this stochastic version of Huang's mean
+field reaction rates confirm the major results obtained by Huang's
+model, and more successfully predict experimentally observed
+oscillations in round cell phenotypes~\cite{fange2006noise,
+  huang2004min}. The successful simulations of three pronged cells
+mentioned above are stochastic
+simulations~\cite{varma2008min}. Biochemical models of broader scope
+have also been used to study the MinD system and show consistent
+results~\cite{arjunan2010new}.
+
+\fixme{There are not any direct comparisons of the deterministic and
+  stochastic methods that I can find other than the fange2006 paper
+  cited above for the round cells.  Those showed that the
+  deterministic couldn't predict oscillations in perfectly round
+  cells, but could in almost round ellipses.  It seems that once the
+  stochastic methods began to be used, nobody really used the
+  deterministic method any longer.  Not sure what to say about this in
+  order to introduce what we do here properly.}
+
+In this paper we apply a deterministic method and a stochastic method
+of simulation and compare them against Mannik's experimental findings.
 

### 2014-09-17 paper/paper.tex
changes to pill section of paper Tested everything on crystal.

@@
 each case, we observe in the deterministic simulations a quick
-establishement (within a few periods) of extremely regular oscillatory
-behavoir that lasts indefinitely.  The stochastic results show
-oscillitions that are similarly regular in time, with periods that
-nearly match those of the deterministic (they differ roughly by a
-factor of .05) \fixme{does this square with the correlation data
-  periods?}. The regularity of the pill shape cell periods is
-discussed below, in our analysis of time correlation data \fixme{not
-  written yet}.  These periods increase with cell length, as shown in
-Table~\ref{tab:pill-periods}, in agreement with the results of Huang
-\emph{et al.}.
+establishement (within a few periods) of regular oscillatory behavoir
+that lasts indefinitely.  This temporal regularity can be seen in
+Figure~\ref{corr-pill}, which shows the temporal correlation of the
+total MinD protein located in the the two polar sections of the cell.
+In the stochastic simulations the pills exhibit coherence times of
+over 7 periods and the determinisitic version cohere indefinately.
 
@@
 simulations show maxima that, while always located somehwere in the
-end region of the cell, occur at different positions within this
+polar region of the cell, occur at different positions within this
 region.  This is reflected in Figure~\ref{image-p}, which shows
@@
 details of the stochastic simulation maxima location.
+
+\fixme{Is the table of the cell periods needed? I'm not sure if we
+  have a experiment to compare this to} The stochastic results show
+oscillitions that are similarly regular in time, with periods that
+nearly match those of the deterministic (they differ roughly by a
+factor of .05) \fixme{does this square with the correlation data
+  periods?}. The regularity of the pill shape cell periods is
+discussed below, in our analysis of time correlation data \fixme{not
+  written yet}.  These periods increase with cell length, as shown in
+Table~\ref{tab:pill-periods}, in agreement with the results of Huang
+\emph{et al.}.
 
@@
 \end{table}
-
-\fixme{Originally the 'Stability Analysis' section came next.  I would
-  like to still mention the results of this, since Huang only did the
-  analysis on the cylinders, and we've done it on the flattened shapes
-  and shown that it works with those too.  But I don't know where to
-  fit in the paragraph or so that it would take.  For now I've just
-  put the whole section at the end of the paper.}
 

### 2014-09-17 correlation_box.sh

@@ -2,20 +2,20 @@
 
 echo starting !
 
-# srun --job-name="corr randst 18.50 18.50 95.00 full_array 0.00 4500.00" python pyplots/density-correlation.py randst 0.25 18.50 18.50 95.00 15.00 full_array 0.00 4500.00 &
-# srun --job-name="corr randst 18.50 18.50 95.00 exact 0.00 5000.00" python pyplots/density-correlation.py randst 0.25 18.50 18.50 95.00 15.00 exact 0.00 5000.00 &
+srun --job-name="corr randst 18.50 18.50 95.00 full_array 0.00 4500.00" python pyplots/density-correlation.py randst 0.25 18.50 18.50 95.00 15.00 full_array 0.00 &
+srun --job-name="corr randst 18.50 18.50 95.00 exact 0.00 5000.00" python pyplots/density-correlation.py randst 0.25 18.50 18.50 95.00 15.00 exact 0.00 &
 
-# srun --job-name="corr randst 18.60 28.60 94.00 full_array 0.00 1020.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 0.00 1000.00 &
-# srun --job-name="corr randst 18.60 28.60 94.00 exact 0.00 1800.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 exact 0.00 1800.00 &
+srun --job-name="corr randst 18.60 28.60 94.00 full_array 0.00 1020.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 0.00 &
+srun --job-name="corr randst 18.60 28.60 94.00 exact 0.00 1800.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 exact 0.00 &
 
-# srun --job-name="corr stad 2.35 1.32 full 0.00 10000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 full_array 0.00 13500.00 &
-# srun --job-name="corr stad 2.35 1.32 exact 0.00 6000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 exact 0.00 8400.00 &
[…]

### 2014-09-18 paper/paper.tex
rewrote correlation programs to do things a better way.  added data necc for committing, changed makefile to demand these data files, change the correlation included in paper accordingly Tested everything on quipu.

@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation-rl.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
   \caption{No caption}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation-rl.pdf}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation-rl.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
   \caption{Correlation for A shapes}
@@
 \begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation-rl.pdf}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation-rl.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
   \caption{Correlation for B shapes}

### 2014-09-18 paper/paper.tex
edits to paper after printed out read through Tested everything on quipu.

@@
 experimental studies have shown that the MinC protein, known to
-inhibit the FtZ polymer\cite{shen2010examination}, exhibits pole to
-pole oscillatory behavior between both ends of the wild-type
+inhibit the FtZ polymer\cite{shen2010examination}, exhibits regular
+pole to pole oscillatory behavior between both ends of the wild-type
 pill-shaped cell.  It thus has a higher time averaged concentration in
@@
 Previous studies have shown that the minD protein system is capable of
-exhibiting oscillations in round shapes as well as in connected three
-pronged tube shapes~\cite{varma2008min}, in which the oscillations
-seem to seek out the extreme poles in the
+exhibiting oscillations in round shapes \fixme{citation needed}as well
+as in connected three pronged tube shapes~\cite{varma2008min}, in
+which the oscillations seem to seek out the extreme poles in the
 cell~\cite{corbin2002exploring} \cite{juarez2010changes}. However,
@@
 opportunity to test previously studied MinD simulation models against
-more extreme experimental cases than have been seen thus far.
+more extreme experimental cases than have been seen thus
+far. \fixme{Perhaps this sentence should come later after we've
+  introduced the simulation research that's been done.}
 
 A significant amount of work has been done to develop protein reaction
-and diffusion models that exhibit accurate macroscopic dynamics of the
-MinD protein system. Early models involve free proteins that affect
-each others' rates of diffusion and membrane attachment, but do not
-combine into compound states~\cite{meinhardt2001pattern}.  In 2003
-Huang improved upon this work with a simple and very successful
-simulation model based on MinD-MinE combination, ATPase hydrolysis,
-and MinD membrane attachment that exhibits accurate MinD oscillations
-in cylindrical cells~\cite{huang2003dynamic}. In this model
-cytoplasmic MinD is more likely to attach to the membrane when MinD is
-already clustered there (following observed non-linear attachement of
-minD on the cell membrane), and is stationary once attached.  A number
-of studies have used an approach similar in that they do not rely on
-the ability of MinD to move along the walls and
+and diffusion simulation models that exhibit accurate macroscopic
+dynamics of the MinD protein system. Early models involve free
+proteins that affect each others' rates of diffusion and membrane
+attachment, but do not combine into compound
+states~\cite{meinhardt2001pattern}.  In 2003 Huang improved upon this
+work with a simple and very successful simulation model based on
+MinD-MinE combination, ATPase hydrolysis, and MinD membrane attachment
+that exhibits accurate MinD oscillations in cylindrical
+cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is more
+likely to attach to the membrane when MinD is already clustered there
+(following observed non-linear attachement of minD on the cell
+membrane), and is stationary once attached.  A number of studies have
+used an approach similar in that they do not rely on the ability of
+MinD to move along the walls and
 cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
@@
 Variations of the Huang 2003 model that stochasticly account for
-variations of molecular
-interaction~\cite{kerr2006division,fange2006noise} and monte-carlo
+molecular interaction and
+diffusion~\cite{kerr2006division,fange2006noise} and monte-carlo
 simulations that implement this stochastic version of Huang's mean
-field reaction rates confirm the major results obtained by Huang's
-model, and more successfully predict experimentally observed
-oscillations in round cell phenotypes~\cite{fange2006noise,
-  huang2004min}. The successful simulations of three pronged cells
-mentioned above are stochastic
+field reaction rates \fixme{citation needed on the monte-carlo method}
+confirm the major results obtained by Huang's model, and more
+successfully predict experimentally observed oscillations in round
+cell phenotypes~\cite{fange2006noise, huang2004min}. The successful
+simulations of three pronged cells mentioned above are stochastic
 simulations~\cite{varma2008min}. Biochemical models of broader scope
@@
 relevent at the membrane because the membrane bound density values
-will have no meaning in the cytoplasm where there is no membrane.
+will have no meaning in the cytoplasm.
 
@@
 oscillations, so we follow Huang\cite{huang2003dynamic} and do not
-deviate from the wild type values used in the cited work (see values
-below).  Huang's simulations use total MinD and MinE concentrations of
-$1,000/\mu m$ and $350/\mu m$, respectively, in a cylindrical cell of
-radius $0.5\mu m$, and in our (non-cylindrical) cells we use the same
-number of proteins per unit volume.  These concentration values are
-1273 $\mu m^{-3}$ and 446 $\mu m^{-3}$, respectively. \fixme{It's been
-  a while so might want to check this to make sure it's true.}
+deviate from the wild type values used in the cited work.
+
 \begin{gather*}
@@
 \end{gather*}
-A 3D grid is then constructed in cartesian coordinates, with a grid
-spacing of .05\micron.
 
-We have performed both a basic finite analysis, deterministic
-simulation that is spatially and temporally discrete, and a stochastic
-analysis that is spatially discrete but continuous in time.  Our
-stochastic simulation method follows the work of
+Huang's simulations use total MinD and MinE concentrations of
+$1,000/\mu m$ and $350/\mu m$, respectively, in a cylindrical cell of
+radius $0.5\mu m$, and in our (non-cylindrical) cells we use the same
+number of proteins per unit volume.  These concentration values are
+1273 $\mu m^{-3}$ and 446 $\mu m^{-3}$, respectively. \fixme{It's been
+  a while so might want to check this to make sure it's true.}  A 3D
+grid is then constructed in cartesian coordinates, with a grid spacing
+of .05\micron.
+
+We have performed both a basic finite analysis, numerical,
+deterministic simulation that is spatially and temporally discrete,
+and a stochastic analysis that is spatially discrete but continuous in
+time.  Our stochastic simulation method follows the work of
 Kraus~\cite{kraus1996crosstalk} which in turn follows a method
 introduced by Gillespie~\cite{gillespie1977exact}.
-
-\begin{figure*}
-  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
-  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
-  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-  \caption{Contour plot images of the concentration of each protein
-    species in a natural pill-shaped bacterium at regular intervals in
-    time (one second intervals), with darker regions indicating higher
-    concentration. The upper plots shows results from the
-    deterministic simulation and the lower shows results from the
-    stochastic simulation.  The cells pictured are $4\micron$ in
-    length, measured from end to end.  The order of frames is such
-    that individual MinD proteins begin at the bottom of the plot (in
-    the MinD:ATP state in the cytoplasm), and progress upward until
-    they reach the MinE:MinD:ATP membrane-bound complex.  At that
-    point, they will spontaneously dissociate into cytoplasmic MinE
-    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
-    densities plotted are integrated along the axis orthogonal to the
-    page, and the color scale is chosen separately for each species
-    with black as the maximum value over space and time.  The
-    stochastic densities are smeared out over space using a guassians
-    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
-  \label{image-p}
-\end{figure*}
 
@@
 flattened shapes that are designed to replicate those published by
-Mannik and two `stadium' shapes that respectively have the same
-quadrupole moments of the two Mannik shapes.
+Mannik and two `stadium' shapes that respectively have the same aspect
+ration, thickness, and volume as the two Mannik shapes.  Viewed from
+the top down, the stadium shapes appear as rectangles with
+semi-circular end caps on their long axis ends.
 
@@
 
-Huang \emph{et al} ~\cite{huang2003dynamic} has has performed a linear
+Huang \emph{et al} ~\cite{huang2003dynamic} has performed a linear
 stability analysis on the model which shows an upper limit on a steady
-state solution of $2\mu m$.  Cells with dimensions longer than this
-are unstable and show oscillatory behavoir in this direction, where
-cells that are shorter relax into a motionless steady state.  We have
-similarly performed a stability analysis in an infinite slab with a
-thickness equal to our flattened cells ($0.25\mu m$) and have found
-that an equivalent stability limit for half wavelengths is $2.13\mu
-m$. As expected, when decreasing the lengths and widths of our
-simulated flattened cells so that the shortest distance across the
-cell is less than this length, the cells stop exhibiting any
-oscillalitory behavior.  The deterministic simulations relax into a
-motionless state and the stochastic simulations exhibit multiple
-random locations of small maximization.
+state solution of a $2\mu m$ wavelength.  Cells with dimensions longer
+than this are unstable and show oscillatory behavoir in this
+direction, while cells that are shorter relax into a motionless steady
+state.  We have similarly performed a stability analysis in an
+infinite slab with a thickness equal to that of our flattened cells'
+($0.25\mu m$) and have found that an equivalent stability limit for
+half wavelengths is $2.13\mu m$. As expected, when decreasing the
+lengths and widths of our simulated flattened cells so that the
+longest distance across the cell is less than this length, the cells
+stop exhibiting any oscillalitory behavior.  The deterministic
+simulations relax into a motionless state and the stochastic
+simulations exhibit multiple random locations of small maximization.
 
@@
 
-In contrast, the stochastic method~\fixme{cite} predicts spatially
+As found in previous studies~\fixme{cite}, we observe that the
+stochastic method predicts behavior in wild type cells that is
+consistent both with experiment and with the deterministic method.  In
+contrast, the stochastic method~\fixme{cite} predicts spatially
 irregular formation of maxima for all the flattened cells that we
@@
 \emph{et al.} is largely due to the irregularity of cell shapes
-observed.
+observed, as opposed to the size or aspect ratio.
 

### 2014-09-18 paper/paper.tex
more edits to paper, this time the mannik section, and updated data Tested everything on quipu.

@@
 
-Huang \emph{et al} ~\cite{huang2003dynamic} has performed a linear
+Huang \emph{et al}~\cite{huang2003dynamic} has performed a linear
 stability analysis on the model which shows an upper limit on a steady
@@
 As describe in Section~\ref{sec:model-method-shapes}, we will focus on
-simulation of four flattened cell shapes: two shapes copied from
-Mannik's experiment~\cite{mannik2012robustness} (shape~\emph{A} and
+simulation of four illustrative flattened cell shapes: two shapes
+created to replicate those published by
+Mannik~\cite{mannik2012robustness} (shape~\emph{A} and
 shape~\emph{B}), and for comparison two symmetrical stadium shapes
 that have the identical aspect ratio, thickness and volume (stadium
-\emph{A} and stadium \emph{B}).  These stadium shapes enable us to
-distinguish between the effect of cellular irregularity and that of
-overall size and aspect ratio.  We note that shape \emph{B} is more
-irregular than shape \emph{A}, and in particular features a prominant
-region of concavity on its left-hand side.  For each of these shapes
-(in addition to the wild type pill shape discussed previously) we have
-simulated in excess of \fixme{???} seconds of evolution of the MinD
-system using both the deterministic model of Huang~\fixme{cite} and
-the stochastic model of Huang~\fixme{cite}.
+\emph{A} and stadium \emph{B}).  These can be seen in
+Figure~\ref{randst-plot-ave}.  These stadium shapes enable us to
+distinguish between the effect of cellular shape irregularity and
+assymetry, and that of overall size and aspect ratio.  We note that
+shape \emph{B} is more irregular than shape \emph{A}, and in
+particular features a prominant region of concavity on its left-hand
+side.  For each of these shapes (in addition to the wild type pill
+shape discussed previously) we have simulated in excess of \fixme{???}
+seconds of evolution of the MinD system using the deterministic method
+of Huang's model~\cite{huang2003dynamic}, as well as the stochastic
+method.
 
@@
 time period of \fixme{???}  seconds to account for its short period of
-oscillation.  In every case, including the wild type pill shape, we
-see irregularity in the location of the maxima when using the
-stochastic approach.  The deterministic method shows uniformly bipolar
-oscillation, with the exception of shape \emph{B}, which develops weak
-intermediate maxima on the right-hand edge of the cell.
+oscillation.
+
+In every case, including the wild type pill shape, we see irregularity
+in the location of the maxima when using the stochastic approach.  The
+deterministic method shows uniformly bipolar oscillation, with the
+exception of shape \emph{B}, which develops weak intermediate maxima
+on the right-hand edge of the cell.  From these results, we conclude
+that the deterministic method is inadequate to explain experimental
+observations of the locations of density maxima of the MinD protein.
 
@@
 qualitatively similar to the irregular shapes in terms of the
-locations of their maxima.  From these results, we conclude that the
-deterministic method is inadequate to explain experimental
-observations of the locations of density maxima of the MinD protein.
+locations of their maxima.
 

### 2014-09-18 paper/paper.tex
small edit to intro Tested everything on quipu.

@@
   cited above for the round cells.  Those showed that the
-  deterministic couldn't predict oscillations in perfectly round
-  cells, but could in almost round ellipses.  It seems that once the
+  deterministic sims are 'bistable' - one type of initial conditions
+  (MinD starting on walls on one side) show oscillations, another type
+  (half cyto is filled with 3/4 of MinD) don't.  Huang in 2004 paper
+  cited above uses numerical determinisitc and finds that it can show
+  oscillations in round cells as well, but right now I can't find it
+  and the journal doesn't give me access to it.  predict oscillations
+  in perfectly round cells unless noise was added to the simulation,
+  but could in almost round ellipses.  It seems that once the
   stochastic methods began to be used, nobody really used the

### 2014-09-18 paper/paper.tex
added citations Tested everything on quipu.

@@
 these poles by MinD, which ineracts with another protein, MinE, that
-is neccesary for MinD oscillation.~\cite{hu1999topological,
-  fu2001mine, shapiro2009and, yu1999ftsz, raskin1999rapid}.
+is neccesary for MinD
+oscillation.~\cite{hu1999topological,fu2001mine,shapiro2009and,yu1999ftsz,raskin1999rapid,meacci2005min,raskin1999minde}.
 
 Previous studies have shown that the minD protein system is capable of
-exhibiting oscillations in round shapes \fixme{citation needed}as well
+exhibiting oscillations in round shapes \cite{fange2006noise}as well
 as in connected three pronged tube shapes~\cite{varma2008min}, in

### 2014-09-18 paper/paper.tex
removed quick reference to a monte-carlo way of simulating that I now cant find Tested everything on quipu.

@@
 molecular interaction and
-diffusion~\cite{kerr2006division,fange2006noise} and monte-carlo
-simulations that implement this stochastic version of Huang's mean
-field reaction rates \fixme{citation needed on the monte-carlo method}
-confirm the major results obtained by Huang's model, and more
-successfully predict experimentally observed oscillations in round
-cell phenotypes~\cite{fange2006noise, huang2004min}. The successful
+diffusion~\cite{kerr2006division,fange2006noise} confirm the major
+results obtained by Huang's model, and more successfully predict
+experimentally observed oscillations in round cell
+phenotypes~\cite{fange2006noise, huang2004min}. The successful
 simulations of three pronged cells mentioned above are stochastic

### 2014-09-19 paper/paper.tex
changes to intro of paper, changed verbiage to model from method throughout paper, and updated some data Tested everything on quipu.

@@
 Variations of the Huang 2003 model that stochasticly account for
-molecular interaction and
-diffusion~\cite{kerr2006division,fange2006noise} confirm the major
-results obtained by Huang's model, and more successfully predict
-experimentally observed oscillations in round cell
-phenotypes~\cite{fange2006noise, huang2004min}. The successful
-simulations of three pronged cells mentioned above are stochastic
-simulations~\cite{varma2008min}. Biochemical models of broader scope
-have also been used to study the MinD system and show consistent
-results~\cite{arjunan2010new}.
+molecular interaction and diffusion~\cite{fange2006noise} and
+monte-carlo simulations that implement this stochastic version of
+Huang's mean field reaction rates~\cite{kerr2006division} broadly
+confirm the major results obtained by Huang's model.  However, they
+more successfully predict experimentally observed oscillations in
+round cell phenotypes~\cite{fange2006noise, huang2004min} and
+variations in other
+quantities~\cite{kruse2007experimentalist}\fixme{If going to use this
+  sentence should list these and reference properly?}. Both
+deterministic and stochastic models are widely used throughout systems
+biology~\cite{lawson2013spatial,robb2014stochastic,oguz2014stochastic,fu2013deterministic,rudiger2014stochastic},
+and it's important to better understand their limitations.  Manniks'
+experiments allow for a new distinct opportunity to test these two
+approaches further.
+%% Biochemical models of broader scope have also been
+%% used to study the MinD system and show consistent
+%% results~\cite{arjunan2010new}.
 
-\fixme{There are not any direct comparisons of the deterministic and
-  stochastic methods that I can find other than the fange2006 paper
-  cited above for the round cells.  Those showed that the
-  deterministic sims are 'bistable' - one type of initial conditions
-  (MinD starting on walls on one side) show oscillations, another type
-  (half cyto is filled with 3/4 of MinD) don't.  Huang in 2004 paper
-  cited above uses numerical determinisitc and finds that it can show
-  oscillations in round cells as well, but right now I can't find it
-  and the journal doesn't give me access to it.  predict oscillations
-  in perfectly round cells unless noise was added to the simulation,
-  but could in almost round ellipses.  It seems that once the
-  stochastic methods began to be used, nobody really used the
-  deterministic method any longer.  Not sure what to say about this in
-  order to introduce what we do here properly.}
+%% \fixme{There are not any direct comparisons of the deterministic and
+%%   stochastic models that I can find other than the fange2006 paper
+%%   cited above for the round cells.  Those showed that the
+%%   deterministic sims are 'bistable' - one type of initial conditions
+%%   (MinD starting on walls on one side) show oscillations, another type
+%%   (half cyto is filled with 3/4 of MinD) don't.  Huang in 2004 paper
+%%   cited above uses numerical determinisitc and finds that it can show
+%%   oscillations in round cells as well, but right now I can't find it
+%%   and the journal doesn't give me access to it.  predict oscillations
+%%   in perfectly round cells unless noise was added to the simulation,
+%%   but could in almost round ellipses.  It seems that once the
+%%   stochastic models began to be used, nobody really used the
+%%   deterministic model any longer.  Not sure what to say about this in
+%%   order to introduce what we do here properly.}
 
-In this paper we apply a deterministic method and a stochastic method
+In this paper we apply a deterministic model and a stochastic model
 of simulation and compare them against Mannik's experimental findings.
@@
 We have performed both a basic finite analysis, numerical,
-deterministic simulation that is spatially and temporally discrete,
-and a stochastic analysis that is spatially discrete but continuous in
-time.  Our stochastic simulation method follows the work of
+deterministic model simulation that is spatially and temporally
+discrete, and a stochastic analysis that is spatially discrete but
+continuous in time.  Our stochastic model follows the work of
 Kraus~\cite{kraus1996crosstalk} which in turn follows a method
@@
     concentration. The upper plots shows results from the
-    deterministic simulation and the lower shows results from the
-    stochastic simulation.  The cells pictured are $4\micron$ in
+    deterministic model and the lower shows results from the
+    stochastic model.  The cells pictured are $4\micron$ in
     length, measured from end to end.  The order of frames is such
@@
 longest distance across the cell is less than this length, the cells
-stop exhibiting any oscillalitory behavior.  The deterministic
-simulations relax into a motionless state and the stochastic
-simulations exhibit multiple random locations of small maximization.
+stop exhibiting any oscillalitory behavior.  The deterministic model
+relaxes into a motionless state and the stochastic model exhibits
+multiple random locations of small maximization.
 
@@
 simulation animations for both the deterministic and stochastic
-simulations.  We have 'smeared out' the stochastic concentrations in a
+models.  We have 'smeared out' the stochastic concentrations in a
 manner meant to reproduce the images shown by diffraction limited
@@
 itself with a high degree of regularity, for both the deterministic
-and stochastic simulations.  At $t=0$ the cytoplasmic MinE is
+and stochastic models.  At $t=0$ the cytoplasmic MinE is
 concentrated in the upper portion of the cell and is diffusing
@@
   again to make sure that everything in this paragraph is true}. In
-each case, we observe in the deterministic simulations a quick
+each case, we observe in the deterministic model a quick
 establishement (within a few periods) of regular oscillatory behavoir
@@
 total MinD protein located in the the two polar sections of the cell.
-In the stochastic simulations the pills exhibit coherence times of
-over 7 periods and the determinisitic version cohere indefinately.
+In the case of the stochastic model the pills exhibit coherence times
+of over 7 periods and in the case of the determinisitic model cohere
+indefinately.
 
@@
 results, they do differ in the precise locations of the maxima.  While
-the deterministic simulations show maxima that are every time
+the deterministic model shows maxima that are every time
 concentrated in the center of one of the cell ends, with a symmetric
 smear of protein going out laterally to either side, the stochastic
-simulations show maxima that, while always located somehwere in the
-polar region of the cell, occur at different positions within this
-region.  This is reflected in Figure~\ref{image-p}, which shows
-periods that are the same and qualitative behavoir that is
-approximately the same, but also that there is variation in the
-details of the stochastic simulation maxima location.
+model shows maxima that, while always located somehwere in the polar
+region of the cell, occur at different positions within this region.
+This is reflected in Figure~\ref{image-p}, which shows periods that
+are the same and qualitative behavoir that is approximately the same,
+but also that there is variation in the details of the stochastic
+model maxima location.
 
@@
     and the bottom two rows show our simulations using the stochastic
-    and deterministic algorithms, respectively.  We simulated
+    and deterministic models, respectively.  We simulated
     approximations to the two shapes observed by Mannik, which we call
@@
 shape discussed previously) we have simulated in excess of \fixme{???}
-seconds of evolution of the MinD system using the deterministic method
-of Huang's model~\cite{huang2003dynamic}, as well as the stochastic
-method.
+seconds of evolution of the MinD system using the deterministic
+version of Huang's model~\cite{huang2003dynamic}, as well as the
+stochastic model.
 
@@
 In every case, including the wild type pill shape, we see irregularity
-in the location of the maxima when using the stochastic approach.  The
-deterministic method shows uniformly bipolar oscillation, with the
+in the location of the maxima when using the stochastic model.  The
+deterministic model shows uniformly bipolar oscillation, with the
 exception of shape \emph{B}, which develops weak intermediate maxima
 on the right-hand edge of the cell.  From these results, we conclude
-that the deterministic method is inadequate to explain experimental
+that the deterministic model is inadequate to explain experimental
 observations of the locations of density maxima of the MinD protein.
@@
 
-The predictions of the stochastic as seen in
+The predictions of the stochastic model as seen in
 Fig.~\ref{randst-plot-ave} are roughly similar to the experimental
@@
 correlation functions using over \fixme{???} seconds of simulation.
-We found with the stochastic method that the experimental shape
+We found with the stochastic model that the experimental shape
 \emph{A} has a coherence time of under 4 periods, while the
 corresponding stadium \emph{A} has a coherence time of 10 periods.  In
-each case, the deterministic method is perfectly periodic. This
-confirms that using the stochastic method the stadium shape does
-indeed have a far more regular bipolar oscillation than the irregular
-shape \emph{A}.  When we compare shape \emph{B} and stadium \emph{B},
-we see a similar effect, although both coherence times are somewhat
-smaller (2.7 and 6.2, respectively).  From these results we conclude
-that the irregularity seen experimentally is indeed exacerbated by the
+each case, the deterministic model is perfectly periodic. This
+confirms that with the stochastic model the stadium shape does indeed
+have a far more regular bipolar oscillation than the irregular shape
+\emph{A}.  When we compare shape \emph{B} and stadium \emph{B}, we see
+a similar effect, although both coherence times are somewhat smaller
+(2.7 and 6.2, respectively).  From these results we conclude that the
+irregularity seen experimentally is indeed exacerbated by the
 irregular shapes taken on by the cells forced into a thin slit.
@@
 experimentally by Mannik \emph{et al.}.  We find that the
-deterministic method~\fixme{cite} predicts behavior that completely
+deterministic model~\fixme{cite} predicts behavior that completely
 contradicts what is seen experimentally: it predicts stable and
@@
 As found in previous studies~\fixme{cite}, we observe that the
-stochastic method predicts behavior in wild type cells that is
-consistent both with experiment and with the deterministic method.  In
-contrast, the stochastic method~\fixme{cite} predicts spatially
+stochastic model predicts behavior in wild type cells that is
+consistent both with experiment and with the deterministic model.  In
+contrast, the stochastic model~\fixme{cite} predicts spatially
 irregular formation of maxima for all the flattened cells that we

### 2014-09-19 paper/paper.tex
edited Mannik paragrph in Introduction Tested everything on quipu.

@@
 which the oscillations seem to seek out the extreme poles in the
-cell~\cite{corbin2002exploring} \cite{juarez2010changes}. However,
-Mannik \emph{et al.} have also shown that there are limitations to
-this capability~\cite{mannik2010bacteria}
-\cite{mannik2009bacterial}. They have experimentally forced E. Coli
-cells into flattened irregular shapes of $0.25\mu m$
-thickness. Oscillations in this type of cell shape lose their
-regularity, both temporally and spatially. This allows for an
-opportunity to test previously studied MinD simulation models against
-more extreme experimental cases than have been seen thus
-far. \fixme{Perhaps this sentence should come later after we've
-  introduced the simulation research that's been done.}
+cell~\cite{corbin2002exploring,juarez2010changes}.
+
+However, Mannik \emph{et al.} have also shown that there are
+limitations to this robust capability to
+oscillate~\cite{mannik2010bacteria,mannik2009bacterial}. They have
+experimentally forced E. Coli cells into silicon microfabricated
+channels of $0.25\mu m$ thickness. Upon entering the channels, the
+cells undergo a rapid mechanical deformation in which they widen along
+their short axis parallel to the channel plane, followed by a slower,
+broadening out along both free axes.  This deformation results in very
+wide (they can reach widths of over $5\mu m$), flattened cells that
+when view from the top down show very irregular and assymetric shapes.
+While these cells are still able to divide into surprisingly equal
+volumes, the MinD oscillations within lose their regularity, both
+temporally and spatially. Seen with flourescent microscopy (after
+using common genetic techniques to allow the cells to flouresce), the
+MinD seem to maximize in multiple locations within the cell, in a
+seemingly random sequence. This allows for an opportunity to test
+previously studied MinD simulation models against more extreme
+experimental cases than have been seen thus far. \fixme{Perhaps this
+  sentence should come later after we've introduced the simulation
+  research that's been done.}
 

### 2014-09-19 paper/paper.tex
various tweaks to paper from reading it over Tested everything on bennet.

@@
 experimentally forced E. Coli cells into silicon microfabricated
-channels of $0.25\mu m$ thickness. Upon entering the channels, the
+channels of $0.25\micron$ thickness. Upon entering the channels, the
 cells undergo a rapid mechanical deformation in which they widen along
@@
 broadening out along both free axes.  This deformation results in very
-wide (they can reach widths of over $5\mu m$), flattened cells that
+wide (they can reach widths of over $5\micron$), flattened cells that
 when view from the top down show very irregular and assymetric shapes.
@@
 \end{multline}
-
-where $\rho$ is cytoplasmic protein density ($\mu m^{-3}$), $\sigma$
-is membrane bound density ($\mu m^{-2}$), $\mathcal{D}_D$ and
+where $\rho$ is cytoplasmic protein density ($\micron^{-3}$), $\sigma$
+is membrane bound density ($\micron^{-2}$), $\mathcal{D}_D$ and
 $\mathcal{D}_{E}$ th diffusions constants for MinD and MinE,
@@
 membrane bound MinD:ATP complex, and $d_w$ is the distance from the
-point in space to the closest wall (which will always be
-perpendicular to this distance).  $\delta(d_w)$ has units of
-$\mu m^{-1}$ and will be zero everywhere except at the wall.
-Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} will only be
-relevent at the membrane because the membrane bound density values
-will have no meaning in the cytoplasm.
+point in space to the closest wall.  The Dirac delta function
+$\delta(d_w)$ has units of $\micron^{-1}$ and is zero everywhere except
+at the wall.  Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} are
+only relevent at the membrane because the membrane-bound density
+values have no meaning in the cytoplasm.
 
@@
 Huang's simulations use total MinD and MinE concentrations of
-$1,000/\mu m$ and $350/\mu m$, respectively, in a cylindrical cell of
-radius $0.5\mu m$, and in our (non-cylindrical) cells we use the same
+$1,000/\micron$ and $350/\micron$, respectively, in a cylindrical cell of
+radius $0.5\micron$, and in our (non-cylindrical) cells we use the same
 number of proteins per unit volume.  These concentration values are
-1273 $\mu m^{-3}$ and 446 $\mu m^{-3}$, respectively. \fixme{It's been
-  a while so might want to check this to make sure it's true.}  A 3D
-grid is then constructed in cartesian coordinates, with a grid spacing
-of .05\micron.
+$1273\micron^{-3}$ and $446\micron^{-3}$, respectively. \fixme{It's been
+  a while so might want to check this to make sure it's true.}  We
+construct a 3D grid in cartesian coordinates, with a grid spacing of
+.05\micron.
 
@@
 oscillations as observed by Mannik \emph{et
-  al.}~\cite{mannik2012robustness}, so we model the Min system in a
-variety of cell shapes and sizes.  Here we present a selection of
-these, first naturally occuring pill-shaped cells and then a number of
-flattened out shapes which reflect the experiments of Mannik \emph{et
-  al.}, in which bacteria are confined within a thin slit of height
-$0.25\micron$ ~\cite{mannik2012robustness}. Viewed from the top down
-the cells will show the shapes described below and viewed from the
-side they show at their edges a semicircular protrusion (one may
-imagine the shape of a pancake). We have simulated and analyzed a
-number of these flattened shapes in addition to those shown below,
-including equilateral and iscosolese triangle shapes, shapes shaped
-like greater than signs, '$>$', and four-pronged 'starfish' shapes.
-For all of these we have varied the cell size, expanding the two
-dimensions that are tangent to the flattened surface from very small,
-'steady state' scales (which we discuss below) to scales twice that of
-the published Mannik shapes.  Our conclusions are based on all of this
-data, but we present here specific, illustrative examples: two
-flattened shapes that are designed to replicate those published by
-Mannik and two `stadium' shapes that respectively have the same aspect
-ration, thickness, and volume as the two Mannik shapes.  Viewed from
-the top down, the stadium shapes appear as rectangles with
-semi-circular end caps on their long axis ends.
+  al.}~\cite{mannik2012robustness}, so we model the Min system in
+several cell shapes and sizes.  Here we present a selection of these,
+beginning with naturally occuring pill-shaped cells, followed by a
+number of flattened out shapes which reflect the experiments of Mannik
+\emph{et al.}, in which bacteria are confined within a thin slit of
+height $0.25\micron$ ~\cite{mannik2012robustness}.  Viewed from the
+top down the cells have the shapes described below and viewed from the
+side they have at their edges a semicircular protrusion (one may
+imagine the shape of a pancake).
+%
+In this paper we focus on four specific flattened cell shapes.  Two of
+these shapes replicate those published by Mannik, and the other two
+are `stadium' shapes that respectively have the same aspect ratio,
+thickness, and volume as the two Mannik shapes.  Viewed from the top
+down, these stadium shapes appear as rectangles with semi-circular end
+caps on the long axis ends.
 
@@
 
-\fixme{Is the following Kubitscheck paragraph needed?}
-Kubitschek has shown in multiple experiments that at the time of cell
-division cells have a volume that is within a range of roughly
-$1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
-  kubitschek1968linear}.  We follow Huang's
-simulations\cite{huang2003dynamic} and Mannik's experiments and model
-cells that are slightly larger than this range.
+%% \fixme{Is the following Kubitscheck paragraph needed?}
+%% Kubitschek has shown in multiple experiments that at the time of cell
+%% division cells have a volume that is within a range of roughly
+%% $1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
+%%   kubitschek1968linear}.  We follow Huang's
+%% simulations\cite{huang2003dynamic} and Mannik's experiments and model
+%% cells that are slightly larger than this range.
 
@@
   %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
-  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}
-  \includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+  \begin{center}
+    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
+    \vspace{-2.5em}
+    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+    \vspace{-3em}
+  \end{center}
   \caption{Contour plot images of the concentration of each protein
@@
     deterministic model and the lower shows results from the
-    stochastic model.  The cells pictured are $4\micron$ in
-    length, measured from end to end.  The order of frames is such
-    that individual MinD proteins begin at the bottom of the plot (in
-    the MinD:ATP state in the cytoplasm), and progress upward until
-    they reach the MinE:MinD:ATP membrane-bound complex.  At that
-    point, they will spontaneously dissociate into cytoplasmic MinE
-    (the top row) and the starting state of cytoplasmic MinD:ADP.  The
+    stochastic model.  The cells pictured are $4\micron$ in length,
+    measured from end to end.  The order of frames is such that
+    individual MinD proteins begin at the bottom of the plot (in the
+    MinD:ATP state in the cytoplasm), and progress upward until they
+    reach the MinE:MinD:ATP membrane-bound complex.  At that point,
+    they will spontaneously dissociate into cytoplasmic MinE (the top
+    row) and the starting state of cytoplasmic MinD:ADP.  The
     densities plotted are integrated along the axis orthogonal to the
-    page, and the color scale is chosen separately for each species
-    with black as the maximum value over space and time.  The
-    stochastic densities are smeared out over space using a guassians
-    approximation developed by Zhang et all~\cite{zhang2007gaussian}}.
+    page.  The stochastic densities are broadened using the gaussian
+    smearing approach of Zhang \emph{et
+      al.}~\cite{zhang2007gaussian}}.
   \label{image-p}
@@
 stability analysis on the model which shows an upper limit on a steady
-state solution of a $2\mu m$ wavelength.  Cells with dimensions longer
-than this are unstable and show oscillatory behavoir in this
+state solution of a $2\micron$ wavelength.  Cells with dimensions longer
+than this show spontaneous oscillatory behavoir in this
 direction, while cells that are shorter relax into a motionless steady
 state.  We have similarly performed a stability analysis in an
-infinite slab with a thickness equal to that of our flattened cells'
-($0.25\mu m$) and have found that an equivalent stability limit for
-half wavelengths is $2.13\mu m$. As expected, when decreasing the
+infinite slab with a thickness equal to that of our flattened cells
+($0.25\micron$) and have found that an equivalent stability limit for
+half wavelength is $2.13\micron$. As expected, when decreasing the
 lengths and widths of our simulated flattened cells so that the
 longest distance across the cell is less than this length, the cells
-stop exhibiting any oscillalitory behavior.  The deterministic model
+stop exhibiting any oscillatory behavior.  The deterministic model
 relaxes into a motionless state and the stochastic model exhibits
-multiple random locations of small maximization.
+random fluctuations without spatial oscillations.
+
+\fixme{WHERE TO SAY??? : I think we should describe the ``starry
+  night'' effect in the stochastic model.}
 
@@
 flourescence microscopy.  We do so using the two dimensional gaussian
-approximation developed by Zhang et all~\cite{zhang2007gaussian}.  In
+approximation developed by Zhang \emph{et al.}~\cite{zhang2007gaussian}.  In
 this approximation we use a numerical aperture value of 1.3, which is
-the same as used by mannik experimentally, and a wavelength of
+the same as used by Mannik experimentally, and a wavelength of
 $650nm$.  Each frame is 2.5 seconds ahead of the last, and each image
@@
 described in the reaction model) summed over the coordinate orthogonal
-to the page.  The color scale for each protein state is set according
-to the maximum values observed.
+to the page.
 
 Figure~\ref{image-p} begins about 300 seconds into the simulation and
-shows a typical period of oscillation that in the pill shape repeates
-itself with a high degree of regularity, for both the deterministic
-and stochastic models.  At $t=0$ the cytoplasmic MinE is
+shows one period of oscillation.  At $t=0$ the cytoplasmic MinE is
 concentrated in the upper portion of the cell and is diffusing
@@
 goes.  The removed MinD (cytoplasmic MinD:ADP) diffuses freely for a
-time before spontenously undergowing nucleotide exchange and shifting
+time before spontenously undergoing nucleotide exchange and shifting
 back into the MinD:ATP that is able to attach to the membrane.
 Diffusing a small distance away from the bottom of the cell will bring
-the protein into the MinE collection, where reactions will prevent it
+the protein into the MinE \fixme{collection ??}, where reactions will prevent it
 from collecting for any significant time on the membrane.  Diffusing
@@
 
-We test cells of radius $.5\micron$ and of lengths $2\micron$,
-$3\micron$, $4\micron$, and $5\micron$ measured from the tip of one
-end cap to the tip of the other \fixme{I'm running the 2,3,5 pills
-  again to make sure that everything in this paragraph is true}. In
-each case, we observe in the deterministic model a quick
-establishement (within a few periods) of regular oscillatory behavoir
-that lasts indefinitely.  This temporal regularity can be seen in
-Figure~\ref{corr-pill}, which shows the temporal correlation of the
-total MinD protein located in the the two polar sections of the cell.
-In the case of the stochastic model the pills exhibit coherence times
-of over 7 periods and in the case of the determinisitic model cohere
-indefinately.
-
 \begin{figure}
@@
 \end{figure}
+
+\fixme{add explanation of correlation function somewhere in the
+  following paragraph.  The math could go in theory/methods section.}
+{
+  \color{red}
+  \begin{equation}
+    C(\tau) = \frac{\int
+      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
+      (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
+    }{
+      \int
+      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
+      (N_{\textit{bottom}}(t) - \bar N_{\textit{bottom}})dt
+    }
+  \end{equation}
+  \begin{equation}
+    C(\tau) \propto \int
+      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
+      (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
+  \end{equation}
+  where...
+  \begin{equation}
+    C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
+  \end{equation}
+  where $T$ is the period and $\tau_0$ is the coherence time.
+}
+
+We present simulations of a cell with radius $.5\micron$ and length
+$4\micron$, measured from the tip of one end cap to the tip of the
+other. We observe in the deterministic model a quick establishement
+(within a few periods) of regular oscillatory behavoir that lasts
+indefinitely.  This temporal regularity can be seen in
+Figure~\ref{corr-pill}, which shows the temporal correlation of the
+total MinD protein located in the the two polar sections of the cell.
+In the case of the stochastic model the pill exhibits coherence times
+of over 7 periods and in the case of the determinisitic model
+oscillate indefinately with complete coherence.
 
@@
 but also that there is variation in the details of the stochastic
-model maxima location.
-
-\fixme{Is the table of the cell periods needed? I'm not sure if we
-  have a experiment to compare this to} The stochastic results show
-oscillitions that are similarly regular in time, with periods that
-nearly match those of the deterministic (they differ roughly by a
-factor of .05) \fixme{does this square with the correlation data
-  periods?}. The regularity of the pill shape cell periods is
-discussed below, in our analysis of time correlation data \fixme{not
-  written yet}.  These periods increase with cell length, as shown in
-Table~\ref{tab:pill-periods}, in agreement with the results of Huang
-\emph{et al.}.
-
-\begin{table}
-  \begin{tabular}{|r|c|c|c|l|}
-    \hline Length($\mu$) & 2.50 & 3.00 & 4.00 & 5.00\\ \hline
-    Period(sec) & sim & 33 & 38 & 48 \\ \cline{2-2} \hline
-  \end{tabular}
-  \caption{Period of oscillation according to length of cell for
-    pill-shaped cells.}\label{tab:pill-periods}
-\end{table}
+model maxima location.  \fixme{I think we should discuss stochastic
+  picture earlier.}
 
@@
   \centering
-  \includegraphics[width=\textwidth]{../paper/plot-ave}
+  \includegraphics[width=0.8\textwidth]{../paper/plot-ave}
   \caption{We display here arrows depicting successive maxima in space
@@
 that have the identical aspect ratio, thickness and volume (stadium
-\emph{A} and stadium \emph{B}).  These can be seen in
-Figure~\ref{randst-plot-ave}.  These stadium shapes enable us to
-distinguish between the effect of cellular shape irregularity and
-assymetry, and that of overall size and aspect ratio.  We note that
-shape \emph{B} is more irregular than shape \emph{A}, and in
-particular features a prominant region of concavity on its left-hand
-side.  For each of these shapes (in addition to the wild type pill
-shape discussed previously) we have simulated in excess of \fixme{???}
-seconds of evolution of the MinD system using the deterministic
-version of Huang's model~\cite{huang2003dynamic}, as well as the
-stochastic model.
+\emph{A} and stadium \emph{B}), shown in Figure~\ref{randst-plot-ave}.
+These stadium shapes enable us to distinguish between the effect of
+cellular shape irregularity and assymetry, and that of overall size
+and aspect ratio.  We note that shape \emph{B} is more irregular than
+shape \emph{A}, and in particular features a prominant region of
+concavity on its left-hand side.  For each of these shapes (in
+addition to the wild type pill shape discussed previously) we have
+simulated in excess of \fixme{???}  seconds of evolution of the MinD
+system using the deterministic version of Huang's
+model~\cite{huang2003dynamic}, as well as the stochastic model.
 
@@
 MinD maxima within the cell (over the same time
-interval)~\cite{mannik2012robustness}.  This comparison is shown in
-Fig.~\ref{randst-plot-ave}.  In addition to arrows between successive
-maxima in space and time, we plot as a colored background the density
-of MinD protiens averaged over the same time period.  We note that we
-have manually verified that our (computer-generated) arrow plots also
-reflect a human interpretation of a movie of the same data.  Finally,
-for comparison we present the same plot for a wild-type cell, with a
-time period of \fixme{???}  seconds to account for its short period of
-oscillation.
+interval)~\cite{mannik2012robustness}.  In addition to arrows between
+successive maxima in space and time, we plot as a colored background
+the density of MinD protiens averaged over the same time period.  We
+note that we have manually verified that our (computer-generated)
+arrow plots also reflect a human interpretation of a movie of the same
+data.  Finally, for comparison we present the same plot for a
+wild-type cell, with a time period of \fixme{???}  seconds to account
+for its short period of oscillation.
 

### 2014-09-19 pyplots/single-image-plot.py

@@ -102,5 +102,5 @@ cbar.set_label('molecules/$\mu^2$')
 #plt.colorbar(ticks=[])
 plt.tight_layout()
 print 'saving as', load.print_string("single-image-plot","")
-plt.savefig(load.print_string("single-image-plot",""))
+plt.savefig(load.print_string("single-image-plot",""), transparent=True)
 #plt.savefig(load.print_string("real-gauss-single-image-plot",""))

### 2014-09-19 paper/paper.tex
rewrote section describing movie pill plots Tested everything on quipu.

@@
 
-This simple cell shape is a good starting point for observing in
-detail the dynamic interaction between the different stages of protein
-that lead to their qualitatively distinct behavoir. Figure
-\ref{image-p} shows the process in a series of frames taken from
-simulation animations for both the deterministic and stochastic
-models.  We have 'smeared out' the stochastic concentrations in a
-manner meant to reproduce the images shown by diffraction limited
+Figure~\ref{image-p} shows a series of color plots of protein cycle
+stage concentration for both the deterministic and stochastic
+models. The cells shown are $4\micron$ in length, measured from end to
+end.  We have 'smeared out' the stochastic concentrations in a manner
+meant to reproduce the images shown by diffraction limited
 flourescence microscopy.  We do so using the two dimensional gaussian
-approximation developed by Zhang \emph{et al.}~\cite{zhang2007gaussian}.  In
-this approximation we use a numerical aperture value of 1.3, which is
-the same as used by Mannik experimentally, and a wavelength of
-$650nm$.  Each frame is 2.5 seconds ahead of the last, and each image
-shows the concentration of a given state of protein (of the five
-described in the reaction model) summed over the coordinate orthogonal
-to the page.
+approximation developed by Zhang \emph{et
+  al.}~\cite{zhang2007gaussian}.  In this approximation we use a
+numerical aperture value of 1.3, which is the same as used by Mannik
+experimentally, and a wavelength of $650nm$.  Each frame is 2.5
+seconds ahead of the last, and each image shows the concentration of a
+given state of protein (of the five described in the reaction model)
+summed over the coordinate orthogonal to the page.
 
 Figure~\ref{image-p} begins about 300 seconds into the simulation and
-shows one period of oscillation.  At $t=0$ the cytoplasmic MinE is
-concentrated in the upper portion of the cell and is diffusing
-downward, where it will react with and stick to wall-bound MinD that
-is concentrated on the membrane in the lower portion of the cell.
-This process is in fact already well on its way, as seen by the
-significant concentration of wall bound MinD:MinE which is creeping
-down to the lower corner, removing the MinD from the membrane as it
-goes.  The removed MinD (cytoplasmic MinD:ADP) diffuses freely for a
-time before spontenously undergoing nucleotide exchange and shifting
-back into the MinD:ATP that is able to attach to the membrane.
-Diffusing a small distance away from the bottom of the cell will bring
-the protein into the MinE \fixme{collection ??}, where reactions will prevent it
-from collecting for any significant time on the membrane.  Diffusing
-further towards the upper end, however, while the MinE has not yet
-collected there, will allow MinD:ATP to accumulate with the other
-MinD:ATP, which is seen at seconds 10 through 15 in
-Figure~\ref{image-p}.  Eventually the MinE creeps all the way down to
-the bottom of the cell where it slowly runs out of wall bound MinD to
-react with, before diffusing back up and starting again on the upper
-portion of the cell. This is seen in seconds 15 through 20 in the
-figure.  \fixme{There is another paragraph after this in the latex
-  that I commented out because I thought we might be spending too much
-  time on the description}
+shows one period of oscillation.  At $t=0$ there is a high
+concentration of MinD:ATP that has accumulated on the membrane in the
+lower section of the cell. An important aspect of Huang's model is
+that the MinD is attracted to and sticks to the membrane nonlinearly:
+as it accumulates there it begins to 'recruit' other MinD that is
+diffusing in the cytoplasm nearby, causing peaks in concentration to
+build up on the walls.  Meanwhile, the MinE is creeping downward as it
+reacts with the membrane-bound MinD, forming the MinD:MinE:ATP
+complex, breaks it apart, and then diffuses downward a bit more before
+it again reacts with membrane-bound MinD.  This process can seen by
+the famous MinE 'rings' shown in the deterministic model plots, from 0
+seconds to 4 seconds.  The appearence of these rings in the
+deterministic model along side their less convincing appearence in the
+stochastic model highlights an advantage of the deterministic model:
+the idealization of deterministic data allows one to see macroscopic
+patterns that might otherwise be missed.  In the stochastic model the
+MinE still exhibits higher concentrations in the same regions
+throughout the process, but what would ideally be a 'ring' pattern is
+instead an assymetric collection of maxima.
+
+During the formation of these rings, MinE that is diffusing in the
+cytoplasm in the upper portion of the cell will naturally diffuse
+downward, where there is membrane-bound MinD to react with, causing a
+depletion of MinE in the upper portion of the cell.  As the MinE ring
+converges upon the lower end of the cell, MinD that has been released
+is able to diffuse upward, past the ring, while still in its MinD:ADP
+state.  It then undergoes nucleotide exchange, resulting in MinD:ATP,
+which is ready to accumulate on the walls in the upper portion of the
+cell, where the MinE has been depleted.  This can be seen in seconds
+10 through 20 in both models, and the subsequent MinE ring
+formation and movement upward (beginning the same process in the
+opposite direction) can be seen in seconds 15 through 23.
+
+%% is concentrated in the
+%% upper portion of the cell and is diffusing downward, where it will
+%% react with and stick to wall-bound MinD that is concentrated on the
+%% membrane in the lower portion of the cell.  This process is in fact
+%% already well on its way, as seen by the significant concentration of
+%% wall bound MinD:MinE which is creeping down to the lower corner,
+%% removing the MinD from the membrane as it goes.  The removed MinD
+%% (cytoplasmic MinD:ADP) diffuses freely for a time before spontenously
+%% undergoing nucleotide exchange and shifting back into the MinD:ATP
+%% that is able to attach to the membrane.  Diffusing a small distance
+%% away from the bottom of the cell will bring the protein into the MinE
+%% \fixme{collection ??}, where reactions will prevent it from collecting
+%% for any significant time on the membrane.  Diffusing further towards
+%% the upper end, however, while the MinE has not yet collected there,
+%% will allow MinD:ATP to accumulate with the other MinD:ATP, which is
+%% seen at seconds 10 through 15 in Figure~\ref{image-p}.  Eventually the
+%% MinE creeps all the way down to the bottom of the cell where it slowly
+%% runs out of wall bound MinD to react with, before diffusing back up
+%% and starting again on the upper portion of the cell. This is seen in
+%% seconds 15 through 20 in the figure.  \fixme{There is another
+%%   paragraph after this in the latex that I commented out because I
+%%   thought we might be spending too much time on the description}
 

### 2014-09-19 paper/paper.tex
edits in the introduction section. Tested everything on bennet.

--- 2014-09-19 paper/paper.tex
@@
 \section{Introduction}
-\fixme{Huang and those who reference him use the terms 'numerical
-  deterministic reaction-diffusion model' and 'stochastic version of
-  this model' for the stochastic.} It is vital that during the process
-of bacterial cell division a cell avoid minicelling, or splitting into
-daughter cells with lopsided volumes.  Instrumental to this process in
-\emph{Escherichia coli} is a long FtsZ polymer chain that develops on
-the cell wall in the center region of the cell, helping dictate the
-plane of
-division~\cite{adams2009bacterial,lutkenhaus2007assembly}. Previous
+%% \fixme{Huang and those who reference him use the terms 'numerical
+%%   deterministic reaction-diffusion model' and 'stochastic version of
+%%   this model' for the stochastic.}
+It is vital that during the process of bacterial cell division a cell
+avoid minicelling, or splitting into daughter cells with lopsided
+volumes.  Instrumental to this process in \emph{Escherichia coli} is a
+long FtsZ polymer chain that develops on the cell wall in the center
+region of the cell, helping dictate the plane of
+division~\cite{adams2009bacterial, lutkenhaus2007assembly}. Previous
 experimental studies have shown that the MinC protein, known to
-inhibit the FtZ polymer\cite{shen2010examination}, exhibits regular
+inhibit the FtZ polymer~\cite{shen2010examination}, exhibits regular
 pole to pole oscillatory behavior between both ends of the wild-type
@@
 these poles by MinD, which ineracts with another protein, MinE, that
-is neccesary for MinD
-oscillation.~\cite{hu1999topological,fu2001mine,shapiro2009and,yu1999ftsz,raskin1999rapid,meacci2005min,raskin1999minde}.
+is neccesary for MinD oscillation.~\cite{hu1999topological,
+  fu2001mine, shapiro2009and, yu1999ftsz, raskin1999rapid,
+  meacci2005min, raskin1999minde}.
 
-Previous studies have shown that the minD protein system is capable of
-exhibiting oscillations in round shapes \cite{fange2006noise}as well
-as in connected three pronged tube shapes~\cite{varma2008min}, in
-which the oscillations seem to seek out the extreme poles in the
-cell~\cite{corbin2002exploring,juarez2010changes}.
+Previous studies have shown experimentally that the MinD protein
+system is capable of exhibiting oscillations in round
+shapes~\cite{fange2006noise} as well as in connected three pronged
+tube shapes~\cite{varma2008min}, in which the oscillations seem to
+seek out the extreme poles in the cell~\cite{corbin2002exploring,
+  juarez2010changes}.  One conclusion of these studies has been that
+the MinD system robustly forms bipolar oscillations regardless of
+variations in cellular shape.
 
-However, Mannik \emph{et al.} have also shown that there are
+However, Mannik \emph{et al.} have recently shown that there are
 limitations to this robust capability to
-oscillate~\cite{mannik2010bacteria,mannik2009bacterial}. They have
+oscillate~\cite{mannik2010bacteria, mannik2009bacterial}. They have
 experimentally forced E. Coli cells into silicon microfabricated
 channels of $0.25\micron$ thickness. Upon entering the channels, the
-cells undergo a rapid mechanical deformation in which they widen along
-their short axis parallel to the channel plane, followed by a slower,
-broadening out along both free axes.  This deformation results in very
-wide (they can reach widths of over $5\micron$), flattened cells that
-when view from the top down show very irregular and assymetric shapes.
-While these cells are still able to divide into surprisingly equal
-volumes, the MinD oscillations within lose their regularity, both
-temporally and spatially. Seen with flourescent microscopy (after
+cells undergo a mechanical deformation in which they both widen and
+lengthen within the plane of the channel.  This deformation results in
+very wide (they can reach widths of over $5\micron$) flattened cells
+that when viewed from the top down show irregular and asymmetric
+shapes.  While these cells are still able to divide into surprisingly
+equal volumes, the MinD oscillations in these cells is irregular,
+both temporally and spatially. Seen with flourescent microscopy (after
 using common genetic techniques to allow the cells to flouresce), the
@@
 previously studied MinD simulation models against more extreme
-experimental cases than have been seen thus far. \fixme{Perhaps this
-  sentence should come later after we've introduced the simulation
-  research that's been done.}
+experimental cases than have been seen thus far.
 
-A significant amount of work has been done to develop protein reaction
-and diffusion simulation models that exhibit accurate macroscopic
-dynamics of the MinD protein system. Early models involve free
-proteins that affect each others' rates of diffusion and membrane
-attachment, but do not combine into compound
+A number of models of the MinD protein system have been developed,
+which accurately describe the dynamics using simulations of protein
+reaction and diffusion.
+%
+Early models involved free proteins that affect each others' rates of
+diffusion and membrane attachment, but do not combine into compound
 states~\cite{meinhardt2001pattern}.  In 2003 Huang improved upon this
@@
 that exhibits accurate MinD oscillations in cylindrical
-cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is more
-likely to attach to the membrane when MinD is already clustered there
+cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is
+recruited to the membrane by MinD is already clustered there
 (following observed non-linear attachement of minD on the cell
@@
 association with the cell membrane have also been
-made~\cite{hsieh2010direct,mileykovskaya2003effects}.
+made~\fixme{finding what results? We don't want to just list what has
+  been done, but rather to summarize the state of
+  knowledge.}~\cite{hsieh2010direct, mileykovskaya2003effects}.
 
-Variations of the Huang 2003 model that stochasticly account for
-molecular interaction and diffusion~\cite{fange2006noise} and
-monte-carlo simulations that implement this stochastic version of
-Huang's mean field reaction rates~\cite{kerr2006division} broadly
-confirm the major results obtained by Huang's model.  However, they
-more successfully predict experimentally observed oscillations in
-round cell phenotypes~\cite{fange2006noise, huang2004min} and
-variations in other
-quantities~\cite{kruse2007experimentalist}\fixme{If going to use this
-  sentence should list these and reference properly?}. Both
-deterministic and stochastic models are widely used throughout systems
-biology~\cite{lawson2013spatial,robb2014stochastic,oguz2014stochastic,fu2013deterministic,rudiger2014stochastic},
-and it's important to better understand their limitations.  Manniks'
-experiments allow for a new distinct opportunity to test these two
-approaches further.
-%% Biochemical models of broader scope have also been
-%% used to study the MinD system and show consistent
-%% results~\cite{arjunan2010new}.
+There are only on the order of 1000 MinD proteins in a given cell,
+which means that stochastic fluctuation can be expected to play a
+large role.  To treat this, there have been a number of variations of
+the Huang 2003 model that stochastically treat molecular interaction
+and diffusion~\cite{fange2006noise, kerr2006division}.  These studies
+largely confirm the results of Huang's model, when applied to the
+wild-type phenotype.  However, the stochastic models more successfully
+predict experimentally observed oscillations in round cell
+phenotypes~\cite{fange2006noise, huang2004min}, and enable prediction
+of fluctuations in the predicted
+behavior~\cite{kruse2007experimentalist}.  Both deterministic and
+stochastic models are widely used throughout systems
+biology~\cite{lawson2013spatial, robb2014stochastic,
+  oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
+have unique advantages and limitations.  The deterministic approach
+has an advantage in providing a simple prediction of average behavior,
+while the stochastic approach enables prediction of fluctuations from
+that mean, and reduces sensitivity to initial conditions.
 
@@
 
-In this paper we apply a deterministic model and a stochastic model
-of simulation and compare them against Mannik's experimental findings.
-
-\fixme{Following paragraph is awkward, and I don't think it's needed.}
-Studies have shown as well that MinD binds preferentially to regions
-enriched with cadiolipin, an anionic phospholipid that collects on
-regions of high negative curvature. This mechanism has been
-incorporated into other
-models.\cite{drew2005polymerization,cytrynbaum2007multistranded,renner2012mind,renner2012mind}
-However, this mechanism of combined clustering, phospholipids and MinD
-has not been observed in real cells. \cite{halatek2012highly}
+In this paper we use Huang's 2003 model~\cite{huang2003dynamic} in
+both deterministic and stochastic variants to study flattened cells
+similar to those observed by Mannik~\cite{mannik2009bacterial}.
 

### 2014-09-19 paper/paper.tex
wrote description of the pill correlation plot Tested everything on quipu.

--- 2014-09-19 paper/paper.tex
@@
   \begin{equation}
-    C(\tau) = \frac{\int
-      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
-      (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
-    }{
-      \int
-      (N_{\textit{top}}(t) - \bar N_{\textit{top}})
-      (N_{\textit{bottom}}(t) - \bar N_{\textit{bottom}})dt
-    }
-  \end{equation}
-  \begin{equation}
     C(\tau) \propto \int
@@
 
-We present simulations of a cell with radius $.5\micron$ and length
-$4\micron$, measured from the tip of one end cap to the tip of the
-other. We observe in the deterministic model a quick establishement
-(within a few periods) of regular oscillatory behavoir that lasts
-indefinitely.  This temporal regularity can be seen in
-Figure~\ref{corr-pill}, which shows the temporal correlation of the
-total MinD protein located in the the two polar sections of the cell.
-In the case of the stochastic model the pill exhibits coherence times
-of over 7 periods and in the case of the determinisitic model
-oscillate indefinately with complete coherence.
+Figure~\ref{corr-pill} shows a plot of the time correlation between
+the total MinD found in the two opposite polar regions.  This
+normalized value is given by
+\begin{equation}
+  C(\tau) = \frac{\int
+    (N_{\textit{top}}(t) - \bar N_{\textit{top}})
+    (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
+  }{
+    \int
+    (N_{\textit{top}}(t) - \bar N_{\textit{top}})
+    (N_{\textit{bottom}}(t) - \bar N_{\textit{bottom}})dt
+  }
+\end{equation}
+where $N_{\textit{top}}(t)$ and $N_{\textit{bottom}}(t)$ are the total
+MinD proteins in the outer sections of a cell that has been divided
+into thirds along its long axis.  These plots heolp us in studying the
+periods and the regularity and stability of oscillations.  We have
+fitted them to a simple exponential decay model (akin to that of
+monochromatic light), given by the equation
+\begin{equation}
+  C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
+\end{equation}
+where $T$ is the period and $\tau_0$ is the coherence time.  In the
+case of the stochastic model the pill exhibits coherence times of over
+7 periods and in the case of the determinisitic model oscillate
+indefinately with complete coherence.
 
-While the stochastic results show periods that seem to have a high
-degree of regularity as well as similarity to the deterministic
-results, they do differ in the precise locations of the maxima.  While
-the deterministic model shows maxima that are every time
-concentrated in the center of one of the cell ends, with a symmetric
-smear of protein going out laterally to either side, the stochastic
-model shows maxima that, while always located somehwere in the polar
-region of the cell, occur at different positions within this region.
-This is reflected in Figure~\ref{image-p}, which shows periods that
-are the same and qualitative behavoir that is approximately the same,
-but also that there is variation in the details of the stochastic
-model maxima location.  \fixme{I think we should discuss stochastic
-  picture earlier.}
+\fixme{Do we want anything from the following paragrph?}While the
+stochastic results show periods that seem to have a high degree of
+regularity as well as similarity to the deterministic results, they do
+differ in the precise locations of the maxima.  While the
+deterministic model shows maxima that are every time concentrated in
+the center of one of the cell ends, with a symmetric smear of protein
+going out laterally to either side, the stochastic model shows maxima
+that, while always located somehwere in the polar region of the cell,
+occur at different positions within this region.  This is reflected in
+Figure~\ref{image-p}, which shows periods that are the same and
+qualitative behavoir that is approximately the same, but also that
+there is variation in the details of the stochastic model maxima
+location.  \fixme{I think we should discuss stochastic picture
+  earlier.}
 

### 2014-09-19 paper/paper.tex
decide on tau_c for coherence time Tested everything on bennet.

@@
 
-\fixme{add explanation of correlation function somewhere in the
-  following paragraph.  The math could go in theory/methods section.}
-{
-  \color{red}
+Figure~\ref{corr-pill} shows a plot of the time correlation between
+the total MinD found in the two opposite polar regions.  This
+normalized value is given by
 \begin{equation}
@@
   (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
-  \end{equation}
-  where...
-  \begin{equation}
-    C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
-  \end{equation}
-  where $T$ is the period and $\tau_0$ is the coherence time.
-}
-
-Figure~\ref{corr-pill} shows a plot of the time correlation between
-the total MinD found in the two opposite polar regions.  This
-normalized value is given by
-\begin{equation}
-  C(\tau) = \frac{\int
-    (N_{\textit{top}}(t) - \bar N_{\textit{top}})
-    (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
-  }{
-    \int
-    (N_{\textit{top}}(t) - \bar N_{\textit{top}})
-    (N_{\textit{bottom}}(t) - \bar N_{\textit{bottom}})dt
-  }
 \end{equation}
@@
 \begin{equation}
-  C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_0}}
+  C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_c}}
 \end{equation}
-where $T$ is the period and $\tau_0$ is the coherence time.  In the
+where $T$ is the period and $\tau_c$ is the coherence time.  In the
 case of the stochastic model the pill exhibits coherence times of over

### 2014-09-19 pyplots/correlation-plot.py

@@ -110,24 +110,23 @@ for i in range(1,num_plots):
     pylab.plot(time_array,data_full[i],colors[i],label='stochastic')
     pylab.xlim(0,time_array[-1])
     pylab.ylim(np.amin(data_full[i]),np.amax(data_full[i]))
-    pylab.ylabel('Left-Right Correlation')
 
 if not plot_final_version:
     pylab.plot(time_array,decay,colors[0],label='decay')
 
-pylab.title('%s %s 1/rate = %.3g sec period = %.3g sec (ratio %.2g)'
+pylab.title(r'%s %s $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
             % (sys.argv[1], sys.argv[5], 1/rate, period, 1/(rate*period)))
 
     #data_full = data_full/np.amax(data_full)
 #pylab.subplot(212)
-colors = ['k:','r--','m--.']
+colors = ['k:','r:','m--.']
 for i in range(1,num_plots):
     pylab.plot(time_array,data_exact[i],colors[i],label='deterministic')
     pylab.xlim(0,time_array[-1])
     pylab.ylim(np.amin(data_exact[i]),np.amax(data_exact[i]))
-    pylab.ylabel('Left-Right Correlation')
 
-plt.xlabel('time (sec)')
+pylab.ylabel('$C(t)$')
+plt.xlabel('$t$ (sec)')
 plt.legend()
 
 for string in ["full_array","exact"]:

### 2014-09-19 paper/paper.tex
minor edits to Intro Tested everything on quipu.

@@
 tube shapes~\cite{varma2008min}, in which the oscillations seem to
-seek out the extreme poles in the cell~\cite{corbin2002exploring,
-  juarez2010changes}.  One conclusion of these studies has been that
-the MinD system robustly forms bipolar oscillations regardless of
-variations in cellular shape.
+seek out the extreme poles in the
+cell~\cite{juarez2010changes,corbin2002exploring}.  One conclusion of
+these studies has been that the MinD system robustly forms bipolar
+oscillations regardless of variations in cellular shape.
 
@@
 very wide (they can reach widths of over $5\micron$) flattened cells
-that when viewed from the top down show irregular and asymmetric
+that when viewed from the top down have irregular and asymmetric
 shapes.  While these cells are still able to divide into surprisingly
-equal volumes, the MinD oscillations in these cells is irregular,
+equal volumes, the MinD oscillations in these cells are irregular,
 both temporally and spatially. Seen with flourescent microscopy (after
@@
 cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is
-recruited to the membrane by MinD is already clustered there
+recruited to the membrane by MinD that is already clustered there
 (following observed non-linear attachement of minD on the cell
-membrane), and is stationary once attached.  A number of studies have
-used an approach similar in that they do not rely on the ability of
-MinD to move along the walls and
-cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
+membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
+once attached.  A number of studies have used an approach similar in
+that they do not rely on the ability of MinD to move along the walls
+and cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
   drew2005polymerization, fange2006noise, kerr2006division}, while
@@
 and attraction on the cell membrane~\cite{kruse2002dynamic,
-  howard2005cellular}.  Experimental studies of the Min system's
-association with the cell membrane have also been
-made~\fixme{finding what results? We don't want to just list what has
-  been done, but rather to summarize the state of
-  knowledge.}~\cite{hsieh2010direct, mileykovskaya2003effects}.
+  howard2005cellular}.
 

### 2014-09-19 paper/paper.tex
first stab at the abstract Tested everything on quipu.

@@
 \begin{abstract}
-  The dynamics of the Min-protein system help Escherichia coli
-  bacteria regulate the process of cell division by identifying the
-  center of the cell.  We model the Min-protein system in bacteria
-  that have been forced into unusual flattened shapes, as have
-  recently been experimentally observed.  We find that although the
-  presence of Min oscillations is robust in a wide variety of cellular
-  configurations, the location of the peaks is strongly affected by
-  the cellular shape.  In some cases no periodic oscillations are
-  observed.  In particular, we find that cellular shapes observed
-  experimentally to present irregular oscillations do so in the
-  theoretical model, consistently \fixme{or inconsistently?} with
-  experiment.  \fixme{In agreement with previous theoretical and
-    experimental results, we observe ``rotating'' behavior in certain
-    shapes having three corners.}
+  The dynamics of the Min-protein system help \emph{Escherichia coli}
+  regulate the process of cell division by identifying the center of
+  the cell.  While this system usually exhibits robust polar
+  oscillations in a variety of cell shapes, new experiments have shown
+  that when the cells are mechanically deformed into wide, flattened
+  out, irregular shapes, the robust regularity of this oscillatory
+  behavoir is no longer seen. Here we study widely used stochastic and
+  deterministic models of Min-system simulation within these new cell
+  shapes.  The deterministic model is seen to be largely inadequate in
+  reproducing the qualitatively irregular behavoir, while the
+  stochastic model, based on the same differential equations, is able
+  to accurately predict what has been seen.  We also conclude that it
+  is indeed the irregularity of the cell shape that is responsible for
+  the irregular oscillation behavoir, as opposed to the newly deformed
+  cells' increased width and altered aspect ratio.
 \end{abstract}

### 2014-09-19 paper/paper.tex
small edit to abstract Tested everything on quipu.

@@
   deterministic models of Min-system simulation within these new cell
-  shapes.  The deterministic model is seen to be largely inadequate in
-  reproducing the qualitatively irregular behavoir, while the
+  shapes.  We find that the deterministic model is largely inadequate
+  in reproducing the qualitatively irregular behavoir, while the
   stochastic model, based on the same differential equations, is able
-  to accurately predict what has been seen.  We also conclude that it
-  is indeed the irregularity of the cell shape that is responsible for
+  to accurately predict what has been seen.  We also find that it is
+  indeed the irregularity of the cell shape that is responsible for
   the irregular oscillation behavoir, as opposed to the newly deformed

### 2014-09-19 paper/paper.tex
edits to pill section (no more fixmes!!!) Tested everything on bennet.

@@
   \end{center}
-  \caption{Contour plot images of the concentration of each protein
-    species in a natural pill-shaped bacterium at regular intervals in
-    time (one second intervals), with darker regions indicating higher
-    concentration. The upper plots shows results from the
-    deterministic model and the lower shows results from the
-    stochastic model.  The cells pictured are $4\micron$ in length,
-    measured from end to end.  The order of frames is such that
-    individual MinD proteins begin at the bottom of the plot (in the
-    MinD:ATP state in the cytoplasm), and progress upward until they
-    reach the MinE:MinD:ATP membrane-bound complex.  At that point,
-    they will spontaneously dissociate into cytoplasmic MinE (the top
-    row) and the starting state of cytoplasmic MinD:ADP.  The
-    densities plotted are integrated along the axis orthogonal to the
-    page.  The stochastic densities are broadened using the gaussian
-    smearing approach of Zhang \emph{et
-      al.}~\cite{zhang2007gaussian}}.
+  \caption{Images of the concentration of each protein species in a
+    natural pill-shaped bacterium at one-second time intervals. The
+    upper plots shows results from the deterministic model and the
+    lower shows results from the stochastic model.  The order of
+    frames is such that individual MinD proteins begin at the bottom
+    of the plot (in the MinD:ATP state in the cytoplasm), and progress
+    upward until they reach the MinE:MinD:ATP membrane-bound complex.
+    At that point, they will spontaneously dissociate into cytoplasmic
+    MinE (the top row) and the starting state of cytoplasmic
+    MinD:ADP.}.
   \label{image-p}
@@
 
-Huang \emph{et al}~\cite{huang2003dynamic} has performed a linear
+Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
 stability analysis on the model which shows an upper limit on a steady
@@
 
-We begin with the naturally occuring pill cell shape.  We peice this
-shape together as two hemispherical endcaps attached on either end of
-a cylinder.  This shape follows the early simulations of Huang
-\emph{et al.} but differs in that we have added the end caps for a
-more natural shape, expecting similar results.
+We begin with the naturally occuring pill cell shape.  We piece this
+shape together as a cylinder with hemispherical endcaps.  This shape
+follows the early simulations of Huang \emph{et al.} but differs in
+that we have added the end caps for a more natural shape, expecting
+similar results.
 
-Figure~\ref{image-p} shows a series of color plots of protein cycle
-stage concentration for both the deterministic and stochastic
-models. The cells shown are $4\micron$ in length, measured from end to
-end.  We have 'smeared out' the stochastic concentrations in a manner
-meant to reproduce the images shown by diffraction limited
-flourescence microscopy.  We do so using the two dimensional gaussian
-approximation developed by Zhang \emph{et
-  al.}~\cite{zhang2007gaussian}.  In this approximation we use a
-numerical aperture value of 1.3, which is the same as used by Mannik
+Figure~\ref{image-p} shows a series of color plots of the density of
+proteins at each stage of the reaction cycle. The cells shown are
+$4\micron$ in length, measured from end to end.  We have `smeared out'
+the stochastic concentrations in a manner meant to reproduce the
+images shown by diffraction limited flourescence microscopy.  We do so
+using the two dimensional gaussian approximation developed by Zhang
+\emph{et al.}~\cite{zhang2007gaussian}.  In this approximation we use
+a numerical aperture value of 1.3, which is the same as used by Mannik
 experimentally, and a wavelength of $650nm$.  Each frame is 2.5
@@
 shows one period of oscillation.  At $t=0$ there is a high
-concentration of MinD:ATP that has accumulated on the membrane in the
-lower section of the cell. An important aspect of Huang's model is
-that the MinD is attracted to and sticks to the membrane nonlinearly:
-as it accumulates there it begins to 'recruit' other MinD that is
-diffusing in the cytoplasm nearby, causing peaks in concentration to
-build up on the walls.  Meanwhile, the MinE is creeping downward as it
-reacts with the membrane-bound MinD, forming the MinD:MinE:ATP
-complex, breaks it apart, and then diffuses downward a bit more before
-it again reacts with membrane-bound MinD.  This process can seen by
-the famous MinE 'rings' shown in the deterministic model plots, from 0
-seconds to 4 seconds.  The appearence of these rings in the
-deterministic model along side their less convincing appearence in the
+concentration of MinD:ATP that has accumulated on the membrane at the
+bottom of the cell. An important aspect of Huang's model is that the
+MinD is attracted to and sticks to the membrane nonlinearly: as it
+accumulates there it begins to `recruit' other MinD that is diffusing
+in the cytoplasm nearby, causing peaks in concentration to build up on
+the walls.  Meanwhile, the MinE is creeping downward as is bound to
+the membrane-bound MinD, forming the MinD:MinE:ATP complex, then
+breaks it apart and diffuses downward a bit more before it again
+reacts with membrane-bound MinD.  This process can seen in the form of
+the well-known ``MinE rings'' (actually, MinE bound to MinD on the
+membrane).  These rings are visible in the deterministic model plots
+as a green band on the walls from 0 seconds to 4 seconds (and later
+from 15 to 23 seconds).  The appearence of these rings in the
+deterministic model along side their less obvious appearence in the
 stochastic model highlights an advantage of the deterministic model:
-the idealization of deterministic data allows one to see macroscopic
-patterns that might otherwise be missed.  In the stochastic model the
-MinE still exhibits higher concentrations in the same regions
-throughout the process, but what would ideally be a 'ring' pattern is
-instead an assymetric collection of maxima.
+the idealization of deterministic data allows one to see patterns in
+the averaged behavior that might otherwise be missed.  In the
+stochastic model the MinE still exhibits higher concentrations in the
+same regions throughout the process, but what would ideally be a
+``ring'' pattern is instead an asymmetric collection of maxima, which
+would become a ring after phase-locked averaging.
 
@@
 cytoplasm in the upper portion of the cell will naturally diffuse
-downward, where there is membrane-bound MinD to react with, causing a
+downward, where there is membrane-bound MinD to react with, leading to a
 depletion of MinE in the upper portion of the cell.  As the MinE ring
@@
 is able to diffuse upward, past the ring, while still in its MinD:ADP
-state.  It then undergoes nucleotide exchange, resulting in MinD:ATP,
-which is ready to accumulate on the walls in the upper portion of the
+state.  After it undergoes nucleotide exchange, resulting in MinD:ATP,
+it is ready to accumulate on the walls in at the top of the
 cell, where the MinE has been depleted.  This can be seen in seconds
-10 through 20 in both models, and the subsequent MinE ring
+10 through 20 in both models, followed by the subsequent MinE ring
 formation and movement upward (beginning the same process in the
@@
 
-Figure~\ref{corr-pill} shows a plot of the time correlation between
-the total MinD found in the two opposite polar regions.  This
-normalized value is given by
+It is clear from Fig.~\ref{image-p} that the stochastic simulation
+results in a protein distribution that is spatially regular than the
+deterministic model predicts.  In fact, when viewed as a movie (see
+supplementary material), the stochastic model exhibits a ``starry
+night'' effect, as recruitment leads to clusters of MinD forming on
+the wall and then subsequently dissipating.  This naturally leads to
+irregularity in the temporal periodicity of the system, which we
+quantify by examining the temporal correlation function of the total
+MinD found in two opposite polar regions.
+%
+This correlation function, which is displayed in Fig.~\ref{corr-pill},
+is given by
 \begin{equation}
@@
 where $N_{\textit{top}}(t)$ and $N_{\textit{bottom}}(t)$ are the total
-MinD proteins in the outer sections of a cell that has been divided
-into thirds along its long axis.  These plots heolp us in studying the
-periods and the regularity and stability of oscillations.  We have
-fitted them to a simple exponential decay model (akin to that of
-monochromatic light), given by the equation
+MinD proteins in the top and bottom sections of a cell that has been
+divided into thirds along its long axis.  These plots help us in
+studying the periods and the regularity and stability of oscillations.
+These curves are well fit with a simple exponential decoherence model,
+given by the equation
 \begin{equation}
@@
 where $T$ is the period and $\tau_c$ is the coherence time.  In the
-case of the stochastic model the pill exhibits coherence times of over
-7 periods and in the case of the determinisitic model oscillate
-indefinately with complete coherence.
-
-\fixme{Do we want anything from the following paragrph?}While the
-stochastic results show periods that seem to have a high degree of
-regularity as well as similarity to the deterministic results, they do
-differ in the precise locations of the maxima.  While the
-deterministic model shows maxima that are every time concentrated in
-the center of one of the cell ends, with a symmetric smear of protein
-going out laterally to either side, the stochastic model shows maxima
-that, while always located somehwere in the polar region of the cell,
-occur at different positions within this region.  This is reflected in
-Figure~\ref{image-p}, which shows periods that are the same and
-qualitative behavoir that is approximately the same, but also that
-there is variation in the details of the stochastic model maxima
-location.  \fixme{I think we should discuss stochastic picture
-  earlier.}
+case of the stochastic model the pill exhibits coherence times of
+about 7 periods and in the case of the determinisitic model oscillate
+indefinitely with complete coherence, indicating that its behavior is
+perfectly periodic.
 

### 2014-10-02 paper/paper.tex
edits to paper in mannik section Tested everything on quipu.

@@
 Huang's simulations use total MinD and MinE concentrations of
-$1,000/\micron$ and $350/\micron$, respectively, in a cylindrical cell of
-radius $0.5\micron$, and in our (non-cylindrical) cells we use the same
-number of proteins per unit volume.  These concentration values are
-$1273\micron^{-3}$ and $446\micron^{-3}$, respectively. \fixme{It's been
-  a while so might want to check this to make sure it's true.}  We
+$1,000/\micron$ and $350/\micron$, respectively, in a cylindrical cell
+of radius $0.5\micron$, and in our (non-cylindrical) cells we use the
+same number of proteins per unit volume.  These concentration values
+are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We
 construct a 3D grid in cartesian coordinates, with a grid spacing of
@@
 random fluctuations without spatial oscillations.
-
-\fixme{WHERE TO SAY??? : I think we should describe the ``starry
-  night'' effect in the stochastic model.}
 
@@
     averaged over the same time period.  The simulation time covered
-    for the flattened cells is \fixme{340} seconds, which is the same
+    for the flattened cells is 350 seconds, which is the same
     period of time depicted in the experimental data plots of Mannik
     \emph{et al.}~\cite{mannik2012robustness}.  For the wild type pill
-    shape, we only cover \fixme{???} seconds, in order to provide a
+    shape, we only cover 250 seconds, in order to provide a
     useful comparison due to its shorter oscillation period.  The top
@@
 addition to the wild type pill shape discussed previously) we have
-simulated in excess of \fixme{???}  seconds of evolution of the MinD
+simulated in excess of 15000 seconds of evolution of the MinD
 system using the deterministic version of Huang's
@@
 From each of these flattened simulations, we have chosen a typical 350
-second segment to compare with the results of Mannik exemplified in
-arrow plots in which the arrow heads show the location of sequential
-MinD maxima within the cell (over the same time
-interval)~\cite{mannik2012robustness}.  In addition to arrows between
-successive maxima in space and time, we plot as a colored background
-the density of MinD protiens averaged over the same time period.  We
-note that we have manually verified that our (computer-generated)
-arrow plots also reflect a human interpretation of a movie of the same
-data.  Finally, for comparison we present the same plot for a
-wild-type cell, with a time period of \fixme{???}  seconds to account
-for its short period of oscillation.
+second segment to compare with the puplished results of
+Mannik~\cite{mannik2012robustness}, exemplified in arrow plots in
+which the arrow heads show the location of sequential MinD maxima
+within the cell (in Fig.~\ref{randst-plot-ave}).  In addition to
+arrows between successive maxima in space and time, we plot as a
+colored background the density of MinD protiens averaged over the same
+time period.  We note that we have manually verified that our
+(computer-generated) arrow plots also reflect a human interpretation
+of a movie of the same data.  Finally, for comparison we present the
+same plot for a wild-type cell, with a time period of 250 seconds to
+account for its short period of oscillation.
 
@@
 
-The predictions of the stochastic model as seen in
-Fig.~\ref{randst-plot-ave} are roughly similar to the experimental
-results in terms of irregularity of the locations of maxima, although
-there are locations on the edges of the cells where experiment shows
-maxima occuring that we never see in our simulations, suggesting that
-the model does not precisely reflect the experiment.  We also note
-that the stadium shapes in Fig.~\ref{randst-plot-ave} appear
-qualitatively similar to the irregular shapes in terms of the
-locations of their maxima.
+The predictions of the stochastic model are roughly similar to the
+experimental results in terms of irregularity of the locations of
+maxima, although there are locations on the edges of the cells where
+experiment shows maxima occuring that we never see in our simulations,
+suggesting that the model does not precisely reflect the experiment.
+We also note that the stadium shapes in Fig.~\ref{randst-plot-ave}
+appear to have maxima location irregularity that is qualitatively
+similar to our mannik shapes and to experiment.
 
-However, Fig.~\ref{randst-plot-ave} leaves unclear the importance of
+However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
 irregularity versus overall thickness and aspect ratio in developing
 an understanding of the origin of the experimentally observed
-behavior.  Although in the movies the stadiums appear to display a
-more regular bipolar oscillation, the arrow plots do not provide a
-convincing demonstration.  To illustrate the difference in behavior
-between shape \emph{A} and stadium \emph{A}, we return in
-Fig.~\ref{fig:corr-pancake-A} to the correlation function between the
-number of proteins in a segment at the top of the cell and the number
-of proteins in a segment at the bottom of the cell.  We computed these
-correlation functions using over \fixme{???} seconds of simulation.
-We found with the stochastic model that the experimental shape
-\emph{A} has a coherence time of under 4 periods, while the
-corresponding stadium \emph{A} has a coherence time of 10 periods.  In
-each case, the deterministic model is perfectly periodic. This
-confirms that with the stochastic model the stadium shape does indeed
-have a far more regular bipolar oscillation than the irregular shape
-\emph{A}.  When we compare shape \emph{B} and stadium \emph{B}, we see
-a similar effect, although both coherence times are somewhat smaller
-(2.7 and 6.2, respectively).  From these results we conclude that the
-irregularity seen experimentally is indeed exacerbated by the
-irregular shapes taken on by the cells forced into a thin slit.
+behavior.  Although in the movies the stadiums appear to display, on
+average over long time scales, a more regular bipolar oscillation than
+the irregular mannik shapes, the limited time range of the arrow plots
+(350 seconds) is inadequate when studying this difference in behavoir.
+We therefore return to the correlation function between the number of
+proteins in a segment at the top of the cell and the number of
+proteins in a segment at the bottom of the cell.  For each shape we
+computed these correlation functions using the entirety of our over
+15000 seconds of simulation data. Fig.~\ref{fig:corr-pancake-A} shows
+this plot for mannik \emph{A} and stadium \emph{A}.  E. Coli cell
+doubling times vary widely under alternate conditions, but will often
+be between 20 minutes to 100 minutes~\cite{pierucci1972chromosome},
+while flourescent microscopy experiments have shown that the FtsZ ring
+builds itself with a half life of roughly 30
+seconds~\cite{stricker2002rapid}.  Here we plot correlations of
+correlation times that range from 0 up to 600, a biologically relevent
+timescale.
+
+We see that both in the mannik \emph{A} and stadium \emph{A}, the
+deterministic model is perfectly periodic.  The vary slight drop in
+correlation visible in the deterministic data is most likely due to
+the fact that even with our large amount of simulation time, the end
+of the simulation (sudden cutoff) will still have an effect. Both the
+deterministic and stochastic model correlations have the same number
+of proteins in their cells, and have been normalized with the same
+normalization factor, so that they can be directly compared against
+eachother.  At $\tau=0$, the stochastic correlation is already seen to
+be lower than the deterministic, reflecting the fact that the
+stochastic data now and then shows maxima or minima at both ends
+simultaneously.  the stochastic model that the experimental shape
+\emph{A} has a coherence time of 4.7 periods, while the corresponding
+stadium \emph{A} has a coherence time of just over 6. This difference
+in coherence time is not as extreme as we initially guessed, and it
+shows that the regularity in the cells is not overly sensitive to the
+regularity and symmetry of the shape.  It seems that it is the size
+and aspect ratio that are more important in dictating the regularity
+of bipolar oscillation.
 
@@
 experimentally by Mannik \emph{et al.}.  We find that the
-deterministic model~\fixme{cite} predicts behavior that completely
-contradicts what is seen experimentally: it predicts stable and
-periodic bipolar oscillation, with a minor intermediate maximum
+deterministic model~\cite{huang2003dynamic} predicts behavior that
+completely contradicts what is seen experimentally: it predicts stable
+and periodic bipolar oscillation, with a minor intermediate maximum
 appearing in shape \emph{B}.  Thus we conclude that this method is
@@
 
-As found in previous studies~\fixme{cite}, we observe that the
-stochastic model predicts behavior in wild type cells that is
-consistent both with experiment and with the deterministic model.  In
-contrast, the stochastic model~\fixme{cite} predicts spatially
-irregular formation of maxima for all the flattened cells that we
-studied.  In order to better understand the irregular oscillations
-observed in experiment, we simulated flattened ``stadium'' shapes in
-order to distinguish between the effect of flattening and the effect
-of irregular shape.  We found that although the stadium cells
-exhibited somewhat more irregular locations of maxima than the
-wild-type cells, their oscillation was far more periodic and bipolar
-than the irregular cell shapes observed experimentally.  Thus we
-confirm that the disruption of the MinD oscillations seen by Mannik
-\emph{et al.} is largely due to the irregularity of cell shapes
-observed, as opposed to the size or aspect ratio.
+As found in previous studies~\cite{fange2006noise, varma2008min,
+  kruse2007experimentalist}, we observe that the stochastic model
+predicts qualitative behavior in wild type cells that is broadly
+consistent both with experiment and with the deterministic
+model. However, even in these simple pill-shaped cells the stochastic
+model shows more variation in the location of MinD maxima on either
+end of the cell. This model also predicts spatially irregular
+formation of maxima for all the flattened cells that we studied.  In
+order to better understand the irregular oscillations observed in
+experiment, we simulated flattened ``stadium'' shapes in order to
+distinguish between the effect of flattening and the effect of
+irregular shape.  We did not find a significant difference in the
+coherence of bipolar oscillations within these stadium shapes and the
+irregular shapes published by Mannik \emph{et al.}.  Thus we conclude
+that the disruption of the MinD oscillations seen by Mannik \emph{et
+  al.}  is largely due to the aspect ratio of the cell shape, as
+opposed to its irregularity.
 
@@
 
+%% mannik B 11500 seconds, mannik A 15600 seconds, stadium A 19120  seconds, pill 19990 seconds
+%% = simulation time that deterministic correlation data covers.
+
 \end{document}

### 2014-10-02 paper/paper.tex
edited conclusion in paper and normalized correlation plots, edited their titles and added captions to them as well Tested everything on wentworth.

@@
 oscillations, so we follow Huang\cite{huang2003dynamic} and do not
-deviate from the wild type values used in the cited work.
+deviate from the wild-type values used in the cited work.
 
@@
   \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
-  \caption{No caption}
+  \caption{Temporal correlation function of the total MinD found in
+    two opposite polar regions of the pill shaped cell, shown against
+    the correlation time.  Data for both the the determinisitic and
+    stochastic models are shown.  The stochastic model shows an
+    oscillation period of 39.5 seconds and decay time of 307 seconds,
+    so that it takes roughly 7.8 periods for the behavoir to
+    decohere.}
   \label{corr-pill}
@@
     period of time depicted in the experimental data plots of Mannik
-    \emph{et al.}~\cite{mannik2012robustness}.  For the wild type pill
+    \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
     shape, we only cover 250 seconds, in order to provide a
@@
 concavity on its left-hand side.  For each of these shapes (in
-addition to the wild type pill shape discussed previously) we have
+addition to the wild-type pill shape discussed previously) we have
 simulated in excess of 15000 seconds of evolution of the MinD
@@
 
-In every case, including the wild type pill shape, we see irregularity
+In every case, including the wild-type pill shape, we see irregularity
 in the location of the maxima when using the stochastic model.  The
@@
   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
-  \caption{Correlation for A shapes}
+  \caption{Temporal correlation function of the total MinD found in
+    two opposite polar regions of the mannik \emph{A} (above) and the
+    stadium \emph{A} (below) cell shapes, shown against the
+    correlation time.  Data for both the the determinisitic and
+    stochastic models are shown.  For mannik \emph{A}, the stochastic
+    model shows an oscillation period of 53.1 seconds and decay time
+    of 248 seconds, so that it takes roughly 4.7 periods for the
+    behavoir to decohere.  For the stadium \emph{A}, the same model
+    shows an oscillation period of 51 seconds and decay time of 313
+    seconds, so that it takes roughly 6.1 periods for the behavoir to
+    decohere.}
   \label{fig:corr-pancake-A}
@@
   kruse2007experimentalist}, we observe that the stochastic model
-predicts qualitative behavior in wild type cells that is broadly
+predicts qualitative behavior in wild-type cells that is broadly
 consistent both with experiment and with the deterministic

### 2014-10-02 pyplots/correlation-plot.py

@@ -91,9 +91,10 @@ for i in range(len(decay)):
 
 ####################################
 
-# normalization = np.amax(np.absolute(data_full[1]))
-# data_full[1] = data_full[1]/normalization
-# decay = decay/normalization
+normalization = np.amax(np.absolute(data_exact[1]))
+data_full[1] = data_full[1]/normalization
+data_exact[1] = data_exact[1]/normalization
+decay = decay/normalization
 
 # data_full[2] = data_full[2]/np.amax(np.absolute(data_full[2]))
 # data_exact[1] = data_exact[1]/np.amax(np.absolute(data_exact[1]))
@@ -121,6 +122,20 @@ if not plot_final_version:
 
 pylab.title(r'%s %s $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
             % (sys.argv[1], sys.argv[5], 1/rate, period, 1/(rate*period)))
+if sys.argv[1] == 'randst' and sys.argv[5] == '95.00':
+    # pylab.title(r'Temporal correlation of mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+    #             % (1/rate, period, 1/(rate*period)))
+    pylab.title(r'Temporal correlation of mannik A')
+elif sys.argv[1] == 'stad' and sys.argv[4] == '1.32':
+    # pylab.title(r'Temporal correlation of stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+    #             % (1/rate, period, 1/(rate*period)))
+    pylab.title(r'Temporal correlation of stadium A')
+elif sys.argv[1] == 'p':
+    # pylab.title(r'Temporal correlation of pill-shaped cell, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+    #             % (1/rate, period, 1/(rate*period)))
+    pylab.title(r'Temporal correlation of wild-type pill shape')
+
+
 
     #data_full = data_full/np.amax(data_full)
 #pylab.subplot(212)

### 2014-10-02 paper/paper.tex
edited abstract and small edits in pill section of paper Tested everything on wentworth.

@@
   to accurately predict what has been seen.  We also find that it is
-  indeed the irregularity of the cell shape that is responsible for
-  the irregular oscillation behavoir, as opposed to the newly deformed
-  cells' increased width and altered aspect ratio.
+  the newly deformed cells' increased width and altered aspect ratio
+  that is responsible for the irregular oscillation behavoir, as
+  opposed to the irregularity of the cell shape.
 \end{abstract}
@@
 in the cytoplasm nearby, causing peaks in concentration to build up on
-the walls.  Meanwhile, the MinE is creeping downward as is bound to
-the membrane-bound MinD, forming the MinD:MinE:ATP complex, then
-breaks it apart and diffuses downward a bit more before it again
-reacts with membrane-bound MinD.  This process can seen in the form of
-the well-known ``MinE rings'' (actually, MinE bound to MinD on the
+the walls.  Meanwhile, the MinE creeps downward as it reacts with the
+membrane-bound MinD, forming the MinD:MinE:ATP complex, then breaks it
+apart and diffuses downward a bit more before it again reacts with
+membrane-bound MinD.  This process can be seen in the form of the
+well-known ``MinE rings'' (actually, MinE bound to MinD on the
 membrane).  These rings are visible in the deterministic model plots
@@
 It is clear from Fig.~\ref{image-p} that the stochastic simulation
-results in a protein distribution that is spatially regular than the
-deterministic model predicts.  In fact, when viewed as a movie (see
-supplementary material), the stochastic model exhibits a ``starry
+results in a protein distribution that is less spatially regular than
+the deterministic model predicts.  In fact, when viewed as a movie
+(see supplementary material), the stochastic model exhibits a ``starry
 night'' effect, as recruitment leads to clusters of MinD forming on
@@
 case of the stochastic model the pill exhibits coherence times of
-about 7 periods and in the case of the determinisitic model oscillate
+about 8 periods and in the case of the determinisitic model oscillate
 indefinitely with complete coherence, indicating that its behavior is

### 2014-10-28 paper/paper.tex
editted paper and some of the labelling on plots after revising Davids comments and reading through it myself Tested everything on crystal.

@@
 pill-shaped cell.  It thus has a higher time averaged concentration in
-the cell poles than in the center region, which aides in prohibiting
+the cell poles than in the center region, which aides in preventing
 the FtZ from developing in the wrong region.  The MinC is recruited to
-these poles by MinD, which ineracts with another protein, MinE, that
-is neccesary for MinD oscillation.~\cite{hu1999topological,
-  fu2001mine, shapiro2009and, yu1999ftsz, raskin1999rapid,
-  meacci2005min, raskin1999minde}.
+these poles by MinD, which itself interacts with another protein,
+MinE, in such a fashion as to exhibit pole to pole oscillatory
+behavoir.~\cite{hu1999topological, fu2001mine, shapiro2009and,
+  yu1999ftsz, raskin1999rapid, meacci2005min, raskin1999minde}.
 
-Previous studies have shown experimentally that the MinD protein
-system is capable of exhibiting oscillations in round
+Previous experimental studies have shown that the MinD protein system
+is capable of exhibiting oscillations in round
 shapes~\cite{fange2006noise} as well as in connected three pronged
@@
 oscillate~\cite{mannik2010bacteria, mannik2009bacterial}. They have
-experimentally forced E. Coli cells into silicon microfabricated
-channels of $0.25\micron$ thickness. Upon entering the channels, the
-cells undergo a mechanical deformation in which they both widen and
-lengthen within the plane of the channel.  This deformation results in
-very wide (they can reach widths of over $5\micron$) flattened cells
-that when viewed from the top down have irregular and asymmetric
-shapes.  While these cells are still able to divide into surprisingly
-equal volumes, the MinD oscillations in these cells are irregular,
-both temporally and spatially. Seen with flourescent microscopy (after
-using common genetic techniques to allow the cells to flouresce), the
-MinD seem to maximize in multiple locations within the cell, in a
-seemingly random sequence. This allows for an opportunity to test
-previously studied MinD simulation models against more extreme
-experimental cases than have been seen thus far.
+experimentally forced \emph{E. coli} cells into microfabricated
+silicon channels of $0.25\micron$ thickness. Upon entering the
+channels, the cells undergo a mechanical deformation in which they
+both widen and lengthen within the plane of the channel.  This
+deformation results in very wide (they can reach widths of over
+$5\micron$) flattened cells that when viewed from the top down have
+irregular and asymmetric shapes.  While these cells are still able to
+divide into surprisingly equal volumes, the MinD oscillations in these
+cells are irregular, both temporally and spatially. Seen with
+flourescent microscopy, the MinD maximize in multiple locations within
+the cell, in a seemingly random sequence. These experiments allow for
+an opportunity to test MinD simulation models against more extreme
+cases than have been seen thus far.
 
 A number of models of the MinD protein system have been developed,
-which accurately describe the dynamics using simulations of protein
-reaction and diffusion.
+which accurately describe the dynamics using simulations of
+reaction-diffusion equations.
 %
@@
 the Huang 2003 model that stochastically treat molecular interaction
-and diffusion~\cite{fange2006noise, kerr2006division}.  These studies
-largely confirm the results of Huang's model, when applied to the
-wild-type phenotype.  However, the stochastic models more successfully
-predict experimentally observed oscillations in round cell
+and diffusion~\cite{fange2006noise, kerr2006division}\fixme{talk about
+  this awkward sentence}.  These studies largely confirm the results
+of Huang's model when applied to the wild-type, pill-shaped phenotype.
+However, the stochastic models more successfully predict
+experimentally observed oscillations in round cell
 phenotypes~\cite{fange2006noise, huang2004min}, and enable prediction
@@
 is membrane bound density ($\micron^{-2}$), $\mathcal{D}_D$ and
-$\mathcal{D}_{E}$ th diffusions constants for MinD and MinE,
-respectively, $k_D^{\textrm{ADP $\rightarrow$ ATP}}$ the rate of
-conversion from MinD:ADP to the MinD:ATP complex, $k_D$ the rate of
+$\mathcal{D}_{E}$ are the diffusions constants for MinD and MinE,
+respectively, $k_D^{\textrm{ADP $\rightarrow$ ATP}}$ is the rate of
+conversion from MinD:ADP to the MinD:ATP complex, $k_D$ is the rate of
 MinD:ATP attachement to the membrane when no protein is already
-attached there, $k_{dD}$ the increase of this rate when MinD:ATP is
-present on the membrane, $k_{de}$ the rate of hydrolisis of the
-MinD:MinE:ATP complex, $k_E$ the rate of cytoplasmic MinE binding to
-membrane bound MinD:ATP complex, and $d_w$ is the distance from the
+attached there, $k_{dD}$ is the increase of this rate when MinD:ATP is
+present on the membrane, $k_{de}$ is the rate of hydrolisis of the
+MinD:MinE:ATP complex, $k_E$ is the rate of cytoplasmic MinE binding
+to membrane bound MinD:ATP complex, and $d_w$ is the distance from the
 point in space to the closest wall.  The Dirac delta function
-$\delta(d_w)$ has units of $\micron^{-1}$ and is zero everywhere except
-at the wall.  Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} are
-only relevent at the membrane because the membrane-bound density
-values have no meaning in the cytoplasm.
+$\delta(d_w)$, which we need to describe the location of the membrane,
+has units of $\micron^{-1}$ and is zero everywhere except at the wall.
+Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} are only relevent
+at the membrane because the membrane-bound density values have no
+meaning in the cytoplasm.
 
@@
 same number of proteins per unit volume.  These concentration values
-are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We
-construct a 3D grid in cartesian coordinates, with a grid spacing of
-.05\micron.
+are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We perform
+simulations with a 3D grid in cartesian coordinates that has a grid
+spacing of .05\micron.
 
-We have performed both a basic finite analysis, numerical,
-deterministic model simulation that is spatially and temporally
-discrete, and a stochastic analysis that is spatially discrete but
-continuous in time.  Our stochastic model follows the work of
-Kraus~\cite{kraus1996crosstalk} which in turn follows a method
-introduced by Gillespie~\cite{gillespie1977exact}.
+We have performed both a numerical, deterministic model simulation
+that is spatially and temporally discrete, and a stochastic simulation
+that is spatially discrete but continuous in time.  Our stochastic
+model follows the work of Kraus~\cite{kraus1996crosstalk} which in
+turn follows a method introduced by
+Gillespie~\cite{gillespie1977exact}.
 
@@
 oscillations as observed by Mannik \emph{et
-  al.}~\cite{mannik2012robustness}, so we model the Min system in
-several cell shapes and sizes.  Here we present a selection of these,
-beginning with naturally occuring pill-shaped cells, followed by a
-number of flattened out shapes which reflect the experiments of Mannik
-\emph{et al.}, in which bacteria are confined within a thin slit of
-height $0.25\micron$ ~\cite{mannik2012robustness}.  Viewed from the
-top down the cells have the shapes described below and viewed from the
-side they have at their edges a semicircular protrusion (one may
-imagine the shape of a pancake).
+  al.}~\cite{mannik2012robustness}, so we have modeled the Min system
+in several cell shapes and sizes.  Here we present a selection of
+these, beginning with naturally occuring pill-shaped cells, followed
+by a number of flattened out shapes which reflect the experiments of
+Mannik \emph{et al.}, in which bacteria are confined within a thin
+slit of height $0.25\micron$ ~\cite{mannik2012robustness}.  Viewed
+from the top down the cells have the shapes described below and viewed
+from the side they have at their edges a semicircular protrusion (one
+may imagine the shape of a pancake).
 %
@@
     \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
-    \vspace{-2.5em}
+    \vspace{-1.5em}
     \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
@@
 stability analysis on the model which shows an upper limit on a steady
-state solution of a $2\micron$ wavelength.  Cells with dimensions longer
-than this show spontaneous oscillatory behavoir in this
+state solution of a $2\micron$ half wavelength.  Cells with dimensions
+longer than this show spontaneous oscillatory behavoir in this
 direction, while cells that are shorter relax into a motionless steady
@@
 Figure~\ref{image-p} shows a series of color plots of the density of
-proteins at each stage of the reaction cycle. The cells shown are
-$4\micron$ in length, measured from end to end.  We have `smeared out'
-the stochastic concentrations in a manner meant to reproduce the
-images shown by diffraction limited flourescence microscopy.  We do so
-using the two dimensional gaussian approximation developed by Zhang
-\emph{et al.}~\cite{zhang2007gaussian}.  In this approximation we use
-a numerical aperture value of 1.3, which is the same as used by Mannik
-experimentally, and a wavelength of $650nm$.  Each frame is 2.5
-seconds ahead of the last, and each image shows the concentration of a
-given state of protein (of the five described in the reaction model)
-summed over the coordinate orthogonal to the page.
+proteins at each stage of the reaction cycle. Deterministic simulation
+data is shown above and stochastic simulation data is shown below.
+The cells shown are $4\micron$ in length, measured from end to end.
+We have `smeared out' the stochastic concentrations in a manner meant
+to reproduce the images shown by diffraction limited flourescence
+microscopy.  We do so using the two dimensional gaussian approximation
+developed by Zhang \emph{et al.}~\cite{zhang2007gaussian}.  In this
+approximation we use a numerical aperture value of 1.3, which is the
+same as used by Mannik experimentally, and a wavelength of $650nm$.
+Each frame is 2.5 seconds ahead of the last, and each image shows the
+concentration of a given state of protein (of the five described in
+the reaction model) summed over the coordinate normal to the page.
 
@@
 
-During the formation of these rings, MinE that is diffusing in the
-cytoplasm in the upper portion of the cell will naturally diffuse
-downward, where there is membrane-bound MinD to react with, leading to a
+During the formation of these rings, cytoplasmic MinE is diffusing in
+the upper portion of the cell and will naturally progress downward,
+where there is membrane-bound MinD to react with, leading to a
 depletion of MinE in the upper portion of the cell.  As the MinE ring
@@
 is able to diffuse upward, past the ring, while still in its MinD:ADP
-state.  After it undergoes nucleotide exchange, resulting in MinD:ATP,
-it is ready to accumulate on the walls in at the top of the
-cell, where the MinE has been depleted.  This can be seen in seconds
-10 through 20 in both models, followed by the subsequent MinE ring
-formation and movement upward (beginning the same process in the
-opposite direction) can be seen in seconds 15 through 23.
+state and unable to bind to the membrane.  After it undergoes
+nucleotide exchange, resulting in MinD:ATP, it is ready to accumulate
+on the walls in at the top of the cell, where the MinE has been
+depleted.  This can be seen in seconds 10 through 20 in both models,
+followed by the subsequent MinE ring formation and movement upward
+(beginning the same process in the opposite direction) that can be
+seen in seconds 15 through 23.
 
@@
   \caption{Temporal correlation function of the total MinD found in
-    two opposite polar regions of the pill shaped cell, shown against
+    two opposite polar regions of the pill-shaped cell, shown against
     the correlation time.  Data for both the the determinisitic and
     stochastic models are shown.  The stochastic model shows an
-    oscillation period of 39.5 seconds and decay time of 307 seconds,
-    so that it takes roughly 7.8 periods for the behavoir to
-    decohere.}
+    oscillation period of 39.5 seconds and decay time of 307 seconds.}
   \label{corr-pill}
@@
 where $N_{\textit{top}}(t)$ and $N_{\textit{bottom}}(t)$ are the total
-MinD proteins in the top and bottom sections of a cell that has been
-divided into thirds along its long axis.  These plots help us in
-studying the periods and the regularity and stability of oscillations.
-These curves are well fit with a simple exponential decoherence model,
-given by the equation
+MinD proteins in the top and bottom thirds of a cell.  These plots
+help us in studying the periods and the regularity and stability of
+oscillations.  These curves are well fit with a simple decoherence
+model, given by the equation
 \begin{equation}
@@
 
-As describe in Section~\ref{sec:model-method-shapes}, we will focus on
-simulation of four illustrative flattened cell shapes: two shapes
-created to replicate those published by
+As described in Section~\ref{sec:model-method-shapes}, we will focus
+on simulation of four illustrative flattened cell shapes: two shapes
+created to replicate those shapes observed experimentally by
 Mannik~\cite{mannik2012robustness} (shape~\emph{A} and
@@
 addition to the wild-type pill shape discussed previously) we have
-simulated in excess of 15000 seconds of evolution of the MinD
-system using the deterministic version of Huang's
-model~\cite{huang2003dynamic}, as well as the stochastic model.
+simulated in excess of 15000 seconds (over four hours) of evolution of
+the MinD system using the deterministic version of Huang's
+model~\cite{huang2003dynamic}, and much more than this using the
+stochastic model. \fixme{is this sentence ok?}
 
@@
   \caption{Temporal correlation function of the total MinD found in
-    two opposite polar regions of the mannik \emph{A} (above) and the
+    two opposite polar regions of the shape \emph{A} (above) and the
     stadium \emph{A} (below) cell shapes, shown against the
     correlation time.  Data for both the the determinisitic and
-    stochastic models are shown.  For mannik \emph{A}, the stochastic
+    stochastic models are shown.  For shape \emph{A}, the stochastic
     model shows an oscillation period of 53.1 seconds and decay time
-    of 248 seconds, so that it takes roughly 4.7 periods for the
+    of 246 seconds, so that it takes roughly 4.6 periods for the
     behavoir to decohere.  For the stadium \emph{A}, the same model
-    shows an oscillation period of 51 seconds and decay time of 313
-    seconds, so that it takes roughly 6.1 periods for the behavoir to
+    shows an oscillation period of 51 seconds and decay time of 323
+    seconds, so that it takes roughly 6.3 periods for the behavoir to
     decohere.}
@@
 appear to have maxima location irregularity that is qualitatively
-similar to our mannik shapes and to experiment.
+similar to our Mannik shapes and to experiment.
 
 However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
-irregularity versus overall thickness and aspect ratio in developing
-an understanding of the origin of the experimentally observed
-behavior.  Although in the movies the stadiums appear to display, on
-average over long time scales, a more regular bipolar oscillation than
-the irregular mannik shapes, the limited time range of the arrow plots
-(350 seconds) is inadequate when studying this difference in behavoir.
-We therefore return to the correlation function between the number of
-proteins in a segment at the top of the cell and the number of
-proteins in a segment at the bottom of the cell.  For each shape we
-computed these correlation functions using the entirety of our over
-15000 seconds of simulation data. Fig.~\ref{fig:corr-pancake-A} shows
-this plot for mannik \emph{A} and stadium \emph{A}.  E. Coli cell
-doubling times vary widely under alternate conditions, but will often
-be between 20 minutes to 100 minutes~\cite{pierucci1972chromosome},
-while flourescent microscopy experiments have shown that the FtsZ ring
+cell shape irregularity versus overall size and aspect ratio in
+developing an understanding of the origin of the experimentally
+observed behavior.  Although in the movies the stadiums appear to
+display, on average over long time scales, a more regular bipolar
+oscillation than the irregular mannik shapes, the limited time range
+of the arrow plots (350 seconds) is inadequate when studying this
+difference in behavoir.  We therefore return to the correlation
+function between the number of proteins in a segment at the top of the
+cell and the number of proteins in a segment at the bottom of the
+cell.  For each shape we computed these correlation functions using
+the entirety of our over 15000 seconds of simulation
+data. Fig.~\ref{fig:corr-pancake-A} shows this plot for shape \emph{A}
+and stadium \emph{A}.  E. Coli cell doubling times vary widely
+depending on environmental conditions, but will often be between 20
+minutes to 100 minutes~\cite{pierucci1972chromosome}, while
+flourescent microscopy experiments have shown that the FtsZ ring
 builds itself with a half life of roughly 30
 seconds~\cite{stricker2002rapid}.  Here we plot correlations of
-correlation times that range from 0 up to 600, a biologically relevent
+correlation times up to 600 seconds, a biologically relevent
 timescale.
 
-We see that both in the mannik \emph{A} and stadium \emph{A}, the
-deterministic model is perfectly periodic.  The vary slight drop in
-correlation visible in the deterministic data is most likely due to
-the fact that even with our large amount of simulation time, the end
-of the simulation (sudden cutoff) will still have an effect. Both the
-deterministic and stochastic model correlations have the same number
-of proteins in their cells, and have been normalized with the same
-normalization factor, so that they can be directly compared against
-eachother.  At $\tau=0$, the stochastic correlation is already seen to
-be lower than the deterministic, reflecting the fact that the
-stochastic data now and then shows maxima or minima at both ends
-simultaneously.  the stochastic model that the experimental shape
-\emph{A} has a coherence time of 4.7 periods, while the corresponding
-stadium \emph{A} has a coherence time of just over 6. This difference
-in coherence time is not as extreme as we initially guessed, and it
-shows that the regularity in the cells is not overly sensitive to the
-regularity and symmetry of the shape.  It seems that it is the size
-and aspect ratio that are more important in dictating the regularity
-of bipolar oscillation.
+We see that both in the shape \emph{A} and stadium \emph{A}, the
+deterministic model is perfectly periodic.  Both the deterministic and
+stochastic model correlations have the same number of proteins in
+their cells, and have been normalized with the same normalization
+factor, so that they can be directly compared against eachother.  At
+$\tau=0$, the stochastic correlation is already seen to be lower than
+the deterministic, reflecting the fact that the stochastic data
+sometimes shows maxima or minima at both ends simultaneously.  The
+stochastic simulation of shape \emph{A} has a coherence time of 4.6
+periods, while the corresponding simulation of stadium \emph{A} has a
+coherence time of 6.3 periods.  This moderate difference in coherence
+time shows that the regularity in cell oscillation is not overly
+sensitive to the regularity and symmetry of the shape.  It seems that
+it is the size and aspect ratio that are more important in dictating
+the regularity of bipolar oscillation.
 
@@
 We have simulated flattened cell shapes similar to those observed
-experimentally by Mannik \emph{et al.}.  We find that the
-deterministic model~\cite{huang2003dynamic} predicts behavior that
-completely contradicts what is seen experimentally: it predicts stable
-and periodic bipolar oscillation, with a minor intermediate maximum
-appearing in shape \emph{B}.  Thus we conclude that this method is
-inconsistent with experiment, and should not be relied upon for
-predictions of the behavior of the MinD system.
+experimentally by Mannik \emph{et al.}, with a stochastic and a
+deterministic version of Huang's widely used reaction-diffusion
+model. We find that the deterministic model~\cite{huang2003dynamic}
+predicts behavior that contradicts what is seen experimentally, namely
+robust and periodic bipolar oscillation in irregularly shaped cells,
+with a minor intermediate maximum appearing in shape \emph{B}.  Thus
+we conclude that this method is inconsistent with experiment, and
+should not be relied upon for predictions of the behavior of the MinD
+system.
 
@@
   kruse2007experimentalist}, we observe that the stochastic model
-predicts qualitative behavior in wild-type cells that is broadly
-consistent both with experiment and with the deterministic
+predicts qualitative behavior in wild-type, pill-shaped cells that is
+broadly consistent both with experiment and with the deterministic
 model. However, even in these simple pill-shaped cells the stochastic
-model shows more variation in the location of MinD maxima on either
-end of the cell. This model also predicts spatially irregular
-formation of maxima for all the flattened cells that we studied.  In
-order to better understand the irregular oscillations observed in
-experiment, we simulated flattened ``stadium'' shapes in order to
-distinguish between the effect of flattening and the effect of
-irregular shape.  We did not find a significant difference in the
+model shows variation in the location of MinD maxima on either end of
+the cell. This model also predicts spatially irregular formation of
+maxima for all the flattened cells that we studied, in agreement with
+experiment.  In order to better understand the irregular oscillations
+observed in experiment, we simulated flattened ``stadium'' shapes in
+order to distinguish between the effect of flattening and the effect
+of irregular shape.  We did not find a significant difference in the
 coherence of bipolar oscillations within these stadium shapes and the
-irregular shapes published by Mannik \emph{et al.}.  Thus we conclude
+irregular shapes observed by Mannik \emph{et al.}.  Thus we conclude
 that the disruption of the MinD oscillations seen by Mannik \emph{et
-  al.}  is largely due to the aspect ratio of the cell shape, as
-opposed to its irregularity.
+  al.}  is largely due to the flattened cell shape and greater than
+average size, as opposed to its irregularity.
 

### 2014-10-28 pyplots/correlation-plot.py

@@ -123,16 +123,16 @@ if not plot_final_version:
 pylab.title(r'%s %s $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
             % (sys.argv[1], sys.argv[5], 1/rate, period, 1/(rate*period)))
 if sys.argv[1] == 'randst' and sys.argv[5] == '95.00':
-    # pylab.title(r'Temporal correlation of mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-    #             % (1/rate, period, 1/(rate*period)))
+    #pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+    #            % (1/rate, period, 1/(rate*period)))
     pylab.title(r'Temporal correlation of mannik A')
 elif sys.argv[1] == 'stad' and sys.argv[4] == '1.32':
-    # pylab.title(r'Temporal correlation of stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-    #             % (1/rate, period, 1/(rate*period)))
+    #pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+    #            % (1/rate, period, 1/(rate*period)))
     pylab.title(r'Temporal correlation of stadium A')
 elif sys.argv[1] == 'p':
-    # pylab.title(r'Temporal correlation of pill-shaped cell, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-    #             % (1/rate, period, 1/(rate*period)))
+    #pylab.title(r'pill-shaped cell, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+    #            % (1/rate, period, 1/(rate*period)))
     pylab.title(r'Temporal correlation of wild-type pill shape')
 
 
@@ -146,7 +146,7 @@ for i in range(1,num_plots):
     pylab.ylim(np.amin(data_exact[i]),np.amax(data_exact[i]))
 
 pylab.ylabel('$C(t)$')
-plt.xlabel('$t$ (sec)')
+plt.xlabel(r'$\tau$ (sec)')
 plt.legend()
 
 for string in ["full_array","exact"]:

### 2014-10-28 pyplots/density-correlation.py

@@ -35,7 +35,7 @@ def adjust_data_files(sim_type):
     elif sim_type == "full_array":
         return [10,0,1,2,3,4,5]
     else:
-        data_files = [10,0,1,2,3,4,5]
+        data_files = [0,1,2,3,4,5]
         longest_data_size = 0
         longest_data_num = 30
         for i in data_files:
@@ -52,7 +52,6 @@ def adjust_data_files(sim_type):
                     print '\n',data_file, ' doesnt exist so we cant load it'
                     exit(0)
             data = np.loadtxt(data_file, converters = {0:ignoreme, 1:ignoreme})
-            print data_file
             print 'total time covered by file = ',len(data[0])*dt
             if len(data[0]) > longest_data_size:
                 longest_data_size = len(data[0])

### 2014-10-28 pyplots/single-image-plot.py

@@ -85,6 +85,13 @@ plt.axes().get_xaxis().set_ticklabels(range(len(smeared_data))[::int(2.5*skip_ti
 plt.axes().set_aspect('equal')
 plt.axes().get_yaxis().set_ticks_position('none')
 plt.axes().get_xaxis().set_ticks_position('none')
+if sim_type == 'full_array':
+    plt.axes().set_title('Stochastic Model',x=.2)
+elif sim_type == 'exact':
+    plt.axes().set_title('Deterministic Model',x=.2)
+else:
+    print '\nSomething went wrong while writing the title of the plots\n\n'
+    exit(1)
 plt.xlabel('time (s)')
 
 # I got the colorbar bit here from

### 2014-10-29 paper/paper.tex

@@
 these poles by MinD, which itself interacts with another protein,
-MinE, in such a fashion as to exhibit pole to pole oscillatory
-behavoir.~\cite{hu1999topological, fu2001mine, shapiro2009and,
+MinE, in a system which exhibits pole-to-pole oscillatory
+behavoir~\cite{hu1999topological, fu2001mine, shapiro2009and,
   yu1999ftsz, raskin1999rapid, meacci2005min, raskin1999minde}.
@@
 large role.  To treat this, there have been a number of variations of
-the Huang 2003 model that stochastically treat molecular interaction
-and diffusion~\cite{fange2006noise, kerr2006division}\fixme{talk about
-  this awkward sentence}.  These studies largely confirm the results
+the Huang 2003 model that stochastically simulate the same
+reaction-diffusion equations~\cite{fange2006noise, kerr2006division}.
+These studies largely confirm the results
 of Huang's model when applied to the wild-type, pill-shaped phenotype.
@@
 \end{multline}
-where $\rho$ is cytoplasmic protein density ($\micron^{-3}$), $\sigma$
-is membrane bound density ($\micron^{-2}$), $\mathcal{D}_D$ and
+where $\rho$ is cytoplasmic protein density (proteins$/\micron^{3}$), $\sigma$
+is membrane bound density (proteins$/\micron^{2}$), $\mathcal{D}_D$ and
 $\mathcal{D}_{E}$ are the diffusions constants for MinD and MinE,
@@
 Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
-stability analysis on the model which shows an upper limit on a steady
-state solution of a $2\micron$ half wavelength.  Cells with dimensions
-longer than this show spontaneous oscillatory behavoir in this
-direction, while cells that are shorter relax into a motionless steady
-state.  We have similarly performed a stability analysis in an
-infinite slab with a thickness equal to that of our flattened cells
-($0.25\micron$) and have found that an equivalent stability limit for
-half wavelength is $2.13\micron$. As expected, when decreasing the
-lengths and widths of our simulated flattened cells so that the
-longest distance across the cell is less than this length, the cells
-stop exhibiting any oscillatory behavior.  The deterministic model
-relaxes into a motionless state and the stochastic model exhibits
-random fluctuations without spatial oscillations.
+stability analysis on a cylindrical model which shows an upper limit
+on a steady state solution of a $2\micron$ half wavelength.  Cells
+with dimensions longer than this show spontaneous oscillatory behavoir
+in this direction, while cells that are shorter relax into a
+motionless steady state.  We have similarly performed a linear
+stability analysis on an infinite slab with a thickness equal to that
+of our flattened cells ($0.25\micron$) and have found that an
+equivalent stability limit for half wavelength is $2.13\micron$. As
+expected, when decreasing the lengths and widths of our simulated
+flattened cells so that the longest distance across the cell is less
+than this length, the cells stop exhibiting any oscillatory behavior.
+The deterministic model relaxes into a motionless state and the
+stochastic model exhibits random fluctuations without spatial
+oscillations.
 
@@
     stochastic models are shown.  The stochastic model shows an
-    oscillation period of 39.5 seconds and decay time of 307 seconds.}
+    oscillation period of 39.5 seconds and decay time of 307 seconds.
+    The correlation functions are scaled to have the same initial
+    value.}
   \label{corr-pill}
@@
     correlation time.  Data for both the the determinisitic and
-    stochastic models are shown.  For shape \emph{A}, the stochastic
-    model shows an oscillation period of 53.1 seconds and decay time
-    of 246 seconds, so that it takes roughly 4.6 periods for the
-    behavoir to decohere.  For the stadium \emph{A}, the same model
-    shows an oscillation period of 51 seconds and decay time of 323
-    seconds, so that it takes roughly 6.3 periods for the behavoir to
-    decohere.}
+    stochastic models are shown, and the correlation functions are
+    scaled to have the same initial value.  For shape \emph{A}, the
+    stochastic model shows an oscillation period of 53.1 seconds and
+    decay time of 246 seconds, so that it takes roughly 4.6 periods
+    for the behavoir to decohere.  For the stadium \emph{A}, the same
+    model shows an oscillation period of 51 seconds and decay time of
+    323 seconds, so that it takes roughly 6.3 periods for the behavoir
+    to decohere.}
   \label{fig:corr-pancake-A}
@@
 their cells, and have been normalized with the same normalization
-factor, so that they can be directly compared against eachother.  At
-$\tau=0$, the stochastic correlation is already seen to be lower than
-the deterministic, reflecting the fact that the stochastic data
-sometimes shows maxima or minima at both ends simultaneously.  The
+factor, so that they can be directly compared against eachother.  The
 stochastic simulation of shape \emph{A} has a coherence time of 4.6

### 2014-10-29 paper/paper.tex
changes to movie scripts and small changes to text of paper Tested everything on crystal.

@@
 addition to the wild-type pill shape discussed previously) we have
-simulated in excess of 15000 seconds (over four hours) of evolution of
+simulated in excess of 15000 seconds (over 4 hours) of evolution of
 the MinD system using the deterministic version of Huang's
-model~\cite{huang2003dynamic}, and much more than this using the
-stochastic model. \fixme{is this sentence ok?}
+model~\cite{huang2003dynamic}, and in excess of 100000 seconds (over
+27 hours) using the stochastic model.
 
@@
 cell and the number of proteins in a segment at the bottom of the
-cell.  For each shape we computed these correlation functions using
-the entirety of our over 15000 seconds of simulation
-data. Fig.~\ref{fig:corr-pancake-A} shows this plot for shape \emph{A}
-and stadium \emph{A}.  E. Coli cell doubling times vary widely
-depending on environmental conditions, but will often be between 20
-minutes to 100 minutes~\cite{pierucci1972chromosome}, while
+cell.  Fig.~\ref{fig:corr-pancake-A} shows this plot for shape
+\emph{A} and stadium \emph{A}.  E. Coli cell doubling times vary
+widely depending on environmental conditions, but will often be
+between 20 minutes to 100 minutes~\cite{pierucci1972chromosome}, while
 flourescent microscopy experiments have shown that the FtsZ ring

### 2014-10-29 movie_shell.sh

@@ -29,11 +29,11 @@ echo starting!
 # data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf: pyplots/correlation-plot.py \
 
 
-srun --job-name="mov-im-create p 3.00 0.50 full 500 750" python pyplots/movie-image-creation.py p 3.00 0.50 0.00 0.00 15.00 full_array 500.00 750.00 &
-srun --job-name="mov-im-create randst 18.60 28.60 full 500 850" python pyplots/movie-image-creation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 500.00 850.00 &
-srun --job-name="mov-im-create randst 18.50 18.50 full 500 850" python pyplots/movie-image-creation.py randst 0.25 18.50 18.50 95.00 15.00 full_array 500.00 850.00 &
-srun --job-name="mov-im-create stad 2.92 1.18 full 500 850" python pyplots/movie-image-creation.py stad 0.25 2.92 1.18 0.00 15.00 full_array 500.00 850.00 &
-srun --job-name="mov-im-create stad 2.35 1.32 full 500 850" python pyplots/movie-image-creation.py stad 0.25 2.35 1.32 0.00 15.00 full_array 500.00 850.00 &
+srun --job-name="mov-im-create p 3.00 0.50 full 500 1000" python pyplots/movie-image-creation.py p 3.00 0.50 0.00 0.00 15.00 full_array 500.00 1000.00 &
+srun --job-name="mov-im-create randst 18.60 28.60 full 500 1000" python pyplots/movie-image-creation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 500.00 1000.00 &
+srun --job-name="mov-im-create randst 18.50 18.50 full 500 1000" python pyplots/movie-image-creation.py randst 0.25 18.50 18.50 95.00 15.00 full_array 500.00 1000.00 &
+srun --job-name="mov-im-create stad 2.92 1.18 full 500 1000" python pyplots/movie-image-creation.py stad 0.25 2.92 1.18 0.00 15.00 full_array 500.00 1000.00 &
+srun --job-name="mov-im-create stad 2.35 1.32 full 500 1000" python pyplots/movie-image-creation.py stad 0.25 2.35 1.32 0.00 15.00 full_array 500.00 1000.00 &
 
[…]

### 2014-10-29 pyplots/movie-image-creation.py

@@ -69,7 +69,7 @@ if (input_end_time >= total_number_of_files*dump_time_step):
 
 
 time_left = input_end_time - input_start_time
-video_limit = 400 #time of each gif created
+video_limit = 500 #time of each gif created
 full_video_list = []#list of video_limit long movies
 exact_video_list = []#list of video_limit long movies
 video_number = 0
@@ -199,10 +199,11 @@ def contourplt(full_protein,exact_protein,video_number):
         #big_sub.axis('off')
         big_sub.set_xticks([])
         big_sub.set_yticks([])
-        plt.ylabel('Color scales shown in molecules$/\mu m^2$ ')
+        big_sub.set_ylabel('Color scales shown in molecules$/\mu m^2$ ')
         big_sub.yaxis.set_label_position("right")
-        plt.title('%d seconds'%(index - int(input_start_time/dump_time_step)))
-        big_sub.set_title('%d seconds'%(index - int(input_start_time/dump_time_step)),x=0.44,y=1.01)
+        plt.title('%d seconds'%int(dump_time_step*(index - int(input_start_time/dump_time_step))))
+
+
         # big_sub.yaxis.set_visible(False)
         # big_sub.xaxis.set_visible(False)
 
@@ -213,7 +214,6 @@ def contourplt(full_protein,exact_protein,video_number):
                               cmap=plt.cm.jet,origin='lower',levels=my_full_color_levels)
         cbar = plt.colorbar(CS)
         plt.clim(full_minval,full_maxval)
-        plt.title("Stochastic Simulation of 3.00 $\mu m$ Pill Shaped Cell")
 
         sub2 = fig.add_subplot(212,aspect='equal')
         sub2.yaxis.set_visible(False)
@@ -223,6 +223,30 @@ def contourplt(full_protein,exact_protein,video_number):
         plt.clim(exact_minval,exact_maxval)
         plt.title("Deterministic Simulation of 3.00 $\mu m$ Pill Shaped Cell")
         cbar = plt.colorbar(CS)
+
+        if load.f_shape == 'p':
+            big_sub.set_title('%d seconds'%(index - int(input_start_time/dump_time_step)),x=0.44,y=1.01)
+            sub1.set_title("Stochastic Simulation of 3.00 $\mu m$ Pill Shaped Cell")
+            sub2.set_title("Deterministic Simulation of 3.00 $\mu m$ Pill Shaped Cell")
+        elif load.f_shape == 'randst':
+            if f_param4 == '95.00':
[…]

### 2014-10-29 pyplots/movie-maker.py

@@ -76,7 +76,23 @@ for video_num in range(number_of_videos):
     file_names = ""
     for i in range(start_file,end_file):
         file_names += '.' + job_string + protein_name + '/images/frame-%05d.png '%(i)
-    os.system('convert -delay 20 '+file_names+ '.' + job_string + 'plots/density-movie-'+str(protein_name) \
+    cell_shape = ''
+    if load.f_shape == 'p':
+        cell_shape = 'pill-'
+    elif load.f_shape == 'randst':
+        if f_param4 == '95.00':
+            cell_shape = 'shape-A-'
+        if f_param4 == '94.00':
+            cell_shape = 'shape-B-'
+    elif load.f_shape == 'stad':
+        if f_param2 == '2.35':
+            cell_shape = 'stadium-A-'
+        if f_param2 == '2.92':
+            cell_shape = 'stadium-B-'
+    print cell_shape
+    # os.system('convert -delay 20 '+file_names+ '.' + job_string + 'plots/density-movie-total-MinD-'+\
+    #               +str(int(start_file*dump_time_step))+ '-' +str(int(end_file*dump_time_step))+'.mp4')
+    os.system('convert -delay 30 '+file_names+ './movies/density-movie-total-MinD-'+cell_shape\
                   +str(int(start_file*dump_time_step))+ '-' +str(int(end_file*dump_time_step))+'.mp4')
 
 

### 2014-10-31 paper/paper.tex

@@
 \section{Introduction}
-%% \fixme{Huang and those who reference him use the terms 'numerical
-%%   deterministic reaction-diffusion model' and 'stochastic version of
-%%   this model' for the stochastic.}
 It is vital that during the process of bacterial cell division a cell
@@
     stochastic models are shown.  The stochastic model shows an
-    oscillation period of 39.5 seconds and decay time of 307 seconds.
+    oscillation period of 39.5 seconds and coherence time of 307 seconds.
     The correlation functions are scaled to have the same initial
@@
     stochastic model shows an oscillation period of 53.1 seconds and
-    decay time of 246 seconds, so that it takes roughly 4.6 periods
+    coherence time of 246 seconds, so that it takes roughly 4.6 periods
     for the behavoir to decohere.  For the stadium \emph{A}, the same
-    model shows an oscillation period of 51 seconds and decay time of
+    model shows an oscillation period of 51 seconds and coherence time of
     323 seconds, so that it takes roughly 6.3 periods for the behavoir
@@
 seconds~\cite{stricker2002rapid}.  Here we plot correlations of
-correlation times up to 600 seconds, a biologically relevent
+correlation times up to 500 seconds, a biologically relevent
 timescale.
+
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
+%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
+%%   \caption{Correlation for B shapes}
+%%   \label{corr-B}
+%% \end{figure}
 
@@
 periods, while the corresponding simulation of stadium \emph{A} has a
-coherence time of 6.3 periods.  This moderate difference in coherence
-time shows that the regularity in cell oscillation is not overly
-sensitive to the regularity and symmetry of the shape.  It seems that
-it is the size and aspect ratio that are more important in dictating
-the regularity of bipolar oscillation.
+coherence time of 6.3 periods.
+%
+The correlation function for stadium \emph{B} (5.5 periods, not shown)
+is similar to that of stadium~\emph{A}, with similar coherence time,
+while shape~\emph{B} exhibits a lower coherence time (2.2 periods).
+In the deterministic model, shape~\emph{B} is not precisely periodic
+on biologically relevant timescales, which is reflected in
+Fig.~\ref{randst-plot-ave}, in which the arrows describing the
+deterministic model applied to shape \emph{B} show minor maxima
+forming on the right-hand side of the cell, in contrast to the regular
+polar maxima formed by shape~\emph{A} and the two stadiums.
+%
+From the stochastic correlation data, we conclude that irregularity of
+shape has only a moderate affect on the temporal regularity of the
+oscillatory behavior, leaving the polar oscillation largely intact,
+with even the very distorted shape~\emph{B} exhibiting only a factor
+of two greater decoherence.
 
 \section{Conclusion}
+
+\fixme{Stochastic model successfully explains experiment.}
+
+\fixme{Deterministic is terrible.}
+%
 We have simulated flattened cell shapes similar to those observed
@@
 
+\fixme{What is the point here? Should it be cut?}
+%
 As found in previous studies~\cite{fange2006noise, varma2008min,
@@
 maxima for all the flattened cells that we studied, in agreement with
-experiment.  In order to better understand the irregular oscillations
-observed in experiment, we simulated flattened ``stadium'' shapes in
-order to distinguish between the effect of flattening and the effect
-of irregular shape.  We did not find a significant difference in the
-coherence of bipolar oscillations within these stadium shapes and the
-irregular shapes observed by Mannik \emph{et al.}.  Thus we conclude
-that the disruption of the MinD oscillations seen by Mannik \emph{et
-  al.}  is largely due to the flattened cell shape and greater than
-average size, as opposed to its irregularity.
+experiment.
+
+\fixme{Observations of irregularity would be seen even in regularly
+  shaped flattened or pancake cells.}
+%
+In order to understand the irregular MinD oscillations observed in
+experiments with flattened cells, we simulated flattened ``stadium''
+shapes in order to distinguish between the effect of flattening and
+the effect of irregular shape.  We did not find a significant
+difference in the coherence of bipolar oscillations within these
+stadium shapes and the irregular shapes observed by Mannik \emph{et
+  al.}.  Thus we conclude that the disruption of the MinD oscillations
+seen by Mannik \emph{et al.}  is largely due to the flattened cell
+shape and greater than average size, as opposed to its irregularity.
+
+\fixme{Talk about flattened cells throughout vs. irregular cells.}
 
 \bibliography{paper}
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
-  \caption{Correlation for B shapes}
-  \label{corr-B}
-\end{figure}
 

### 2014-11-04 paper/paper.tex
edits to conclusion, a few edits in the middle of paper, and edits in the abstract, along with a small change to title of corr plots Tested everything on crystal.

@@
   to accurately predict what has been seen.  We also find that it is
-  the newly deformed cells' increased width and altered aspect ratio
-  that is responsible for the irregular oscillation behavoir, as
-  opposed to the irregularity of the cell shape.
+  the flattened nature of the newly deformed cells' shape that is
+  responsible for the irregular oscillation behavoir, as opposed to
+  its irregularity and asymmetry.
 \end{abstract}
@@
 These stadium shapes enable us to distinguish between the effect of
-cellular shape irregularity and assymetry, and that of overall size
-and aspect ratio.  We note that shape \emph{B} is more irregular than
-shape \emph{A}, and in particular features a prominant region of
-concavity on its left-hand side.  For each of these shapes (in
-addition to the wild-type pill shape discussed previously) we have
-simulated in excess of 15000 seconds (over 4 hours) of evolution of
-the MinD system using the deterministic version of Huang's
-model~\cite{huang2003dynamic}, and in excess of 100000 seconds (over
-27 hours) using the stochastic model.
+flattening the cell and the cell shape's irregularity and asymmetry.
+We note that shape \emph{B} is more irregular than shape \emph{A}, and
+in particular features a prominant region of concavity on its
+left-hand side.  For each of these shapes (in addition to the
+wild-type pill shape discussed previously) we have simulated in excess
+of 15000 seconds (over 4 hours) of evolution of the MinD system using
+the deterministic version of Huang's model~\cite{huang2003dynamic},
+and in excess of 100000 seconds (over 27 hours) using the stochastic
+model.
 
@@
 However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
-cell shape irregularity versus overall size and aspect ratio in
-developing an understanding of the origin of the experimentally
-observed behavior.  Although in the movies the stadiums appear to
-display, on average over long time scales, a more regular bipolar
-oscillation than the irregular mannik shapes, the limited time range
-of the arrow plots (350 seconds) is inadequate when studying this
-difference in behavoir.  We therefore return to the correlation
+the flattening of the cell versus cell shape irregularity and
+asymmetry in developing an understanding of the origin of the
+experimentally observed behavior.  Although in the movies the stadiums
+appear to display, on average over long time scales, a more regular
+bipolar oscillation than the irregular mannik shapes, the limited time
+range of the arrow plots (350 seconds) is inadequate when studying
+this difference in behavoir.  We therefore return to the correlation
 function between the number of proteins in a segment at the top of the
@@
 %
-The correlation function for stadium \emph{B} (5.5 periods, not shown)
-is similar to that of stadium~\emph{A}, with similar coherence time,
-while shape~\emph{B} exhibits a lower coherence time (2.2 periods).
-In the deterministic model, shape~\emph{B} is not precisely periodic
-on biologically relevant timescales, which is reflected in
+The correlation function for stadium \emph{B} is similar to that of
+stadium~\emph{A}, with similar coherence time (5.5 periods, not
+shown), while shape~\emph{B} exhibits a lower coherence time (2.2
+periods).  In the deterministic model, shape~\emph{B} is not precisely
+periodic on biologically relevant timescales, which is reflected in
 Fig.~\ref{randst-plot-ave}, in which the arrows describing the
@@
 shape has only a moderate affect on the temporal regularity of the
-oscillatory behavior, leaving the polar oscillation largely intact,
-with even the very distorted shape~\emph{B} exhibiting only a factor
-of two greater decoherence.
+oscillatory behavior, with even the very distorted shape~\emph{B}
+exhibiting only a factor of two greater decoherence.
 
@@
 
-\fixme{Stochastic model successfully explains experiment.}
-
-\fixme{Deterministic is terrible.}
-%
 We have simulated flattened cell shapes similar to those observed
 experimentally by Mannik \emph{et al.}, with a stochastic and a
-deterministic version of Huang's widely used reaction-diffusion
-model. We find that the deterministic model~\cite{huang2003dynamic}
+deterministic version of Huang's widely used reaction-diffusion model.
+We find that the stochastic model predicts experimentally accurate
+qualitative behavoir in both the wild-type, pill-shaped cells (as
+found in previous studies~\cite{fange2006noise, varma2008min,
+  kruse2007experimentalist}), as well as in the new, flattened,
+irregularly shaped cells.  These flattened cells invariably show
+spatially irregular formation of maxima that is also seen
+experimentally.
+
+We find that the deterministic model~\cite{huang2003dynamic}
 predicts behavior that contradicts what is seen experimentally, namely
@@
 
-\fixme{What is the point here? Should it be cut?}
-%
-As found in previous studies~\cite{fange2006noise, varma2008min,
-  kruse2007experimentalist}, we observe that the stochastic model
-predicts qualitative behavior in wild-type, pill-shaped cells that is
-broadly consistent both with experiment and with the deterministic
-model. However, even in these simple pill-shaped cells the stochastic
-model shows variation in the location of MinD maxima on either end of
-the cell. This model also predicts spatially irregular formation of
-maxima for all the flattened cells that we studied, in agreement with
-experiment.
-
-\fixme{Observations of irregularity would be seen even in regularly
-  shaped flattened or pancake cells.}
-%
 In order to understand the irregular MinD oscillations observed in
@@
 shapes in order to distinguish between the effect of flattening and
-the effect of irregular shape.  We did not find a significant
-difference in the coherence of bipolar oscillations within these
-stadium shapes and the irregular shapes observed by Mannik \emph{et
-  al.}.  Thus we conclude that the disruption of the MinD oscillations
-seen by Mannik \emph{et al.}  is largely due to the flattened cell
-shape and greater than average size, as opposed to its irregularity.
-
-\fixme{Talk about flattened cells throughout vs. irregular cells.}
+the effect of irregular shape.  We found only a moderate difference in
+the coherence of bipolar oscillations within these stadium shapes and
+the irregular shapes observed by Mannik \emph{et al.}, and have
+observed visually the same qualitative spatially irregular formation
+of maxima in both.  Thus we conclude that the disruption of the MinD
+oscillations seen by Mannik \emph{et al.}  is largely due to the
+flattening of the cell shape, as opposed to its irregularity.
 

### 2014-11-04 pyplots/correlation-plot.py

@@ -126,7 +126,7 @@ pylab.title(r'%s %s $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
 if sys.argv[1] == 'randst' and sys.argv[5] == '95.00':
     #pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
     #            % (1/rate, period, 1/(rate*period)))
-    pylab.title(r'Temporal correlation of mannik A')
+    pylab.title(r'Temporal correlation of shape A')
 elif sys.argv[1] == 'stad' and sys.argv[4] == '1.32':
     #pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
     #            % (1/rate, period, 1/(rate*period)))

### 2014-11-04 paper/paper.tex
edit conclusion Tested everything on bennet.

@@
 
-We have simulated flattened cell shapes similar to those observed
-experimentally by Mannik \emph{et al.}, with a stochastic and a
-deterministic version of Huang's widely used reaction-diffusion model.
-We find that the stochastic model predicts experimentally accurate
-qualitative behavoir in both the wild-type, pill-shaped cells (as
-found in previous studies~\cite{fange2006noise, varma2008min,
-  kruse2007experimentalist}), as well as in the new, flattened,
-irregularly shaped cells.  These flattened cells invariably show
-spatially irregular formation of maxima that is also seen
-experimentally.
+We find agreement between our stochastic simulations and experiments
+showing disrupted bipolar MinD oscillation in asymmetric flattened
+E. coli cells~\cite{mannik2012robustness}.  As observed
+experimentally, our simulations predict that MinD maxima will form in
+a spatially irregular sequence of locations.  This result builds upon
+existing results showing that this model is effective in a variety of
+wild-type and mutated cell shapes~\cite{fange2006noise, varma2008min,
+  kruse2007experimentalist}, and reinforces that the stochastic
+variation of Huang's 2003 model~\cite{fange2006noise,
+  kerr2006division} has considerable predictive power beyond the
+standard wild-type cell.
 
-We find that the deterministic model~\cite{huang2003dynamic}
-predicts behavior that contradicts what is seen experimentally, namely
-robust and periodic bipolar oscillation in irregularly shaped cells,
-with a minor intermediate maximum appearing in shape \emph{B}.  Thus
-we conclude that this method is inconsistent with experiment, and
-should not be relied upon for predictions of the behavior of the MinD
-system.
+%
+%% We have simulated flattened cell shapes similar to those observed
+%% experimentally by Mannik \emph{et al.}, with a stochastic and a
+%% deterministic version of Huang's widely used reaction-diffusion model.
+%% %
+%% We find that the stochastic model predicts experimentally accurate
+%% qualitative behavoir in both the wild-type, pill-shaped cells (as
+%% found in previous studies~\cite{fange2006noise, varma2008min,
+%%   kruse2007experimentalist}), as well as in the new, flattened,
+%% irregularly shaped cells.  These flattened cells invariably show
+%% spatially irregular formation of maxima as has been observed
+%% experimentally.
 
-In order to understand the irregular MinD oscillations observed in
-experiments with flattened cells, we simulated flattened ``stadium''
-shapes in order to distinguish between the effect of flattening and
-the effect of irregular shape.  We found only a moderate difference in
-the coherence of bipolar oscillations within these stadium shapes and
-the irregular shapes observed by Mannik \emph{et al.}, and have
-observed visually the same qualitative spatially irregular formation
-of maxima in both.  Thus we conclude that the disruption of the MinD
-oscillations seen by Mannik \emph{et al.}  is largely due to the
-flattening of the cell shape, as opposed to its irregularity.
+In contrast to the stochastic model, the original deterministic
+version of the model~\cite{huang2003dynamic} predicts behavior that
+contradicts experimental observations, namely robust and periodic
+bipolar oscillation in irregularly shaped cells, with a minor
+intermediate maximum appearing in shape \emph{B}.  Thus we conclude
+that this method is inconsistent with experiment, and cannot be
+relied upon for predictions of the behavior of the MinD system.
+\fixme{Confirm others? What failures have already been seen? Is this
+  the most dramatic?}
+
+We find that flattened but regular and symmetric cells exhibit MinD
+oscillations that are qualitatively similar to the oscillations
+observed experimentally (and in our simulation) in irregular and
+asymmetric cells.  This demonstrates that asymmetry is not required in
+order to induce spatially irregular MinD oscillations.  In addition,
+the temporal regularity of oscillations is only moderately affected by
+irregularity in the shape of flattened cells.  Thus we conclude
+that it is the flattening of the cells rather than their irregular
+shape that primarily causes the spatial irregularity of maxima which
+is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.
+%% %
+%% In order to understand the irregular MinD oscillations observed in
+%% experiments with flattened cells, we simulated flattened ``stadium''
+%% shapes in order to distinguish between the effect of flattening and
+%% the effect of irregular shape.
+%% %
+%% We found only a moderate difference in the coherence of bipolar
+%% oscillations within these stadium shapes and the irregular shapes
+%% observed by Mannik \emph{et al.}, and have observed visually the same
+%% qualitative spatially irregular formation of maxima in both.  Thus we
+%% conclude that the disruption of the MinD oscillations seen by Mannik
+%% \emph{et al.}  is largely due to the flattening of the cell shape, as
+%% opposed to its irregularity.
 

### 2014-11-04 paper/paper.tex
rewrote abstract, added two sentences to conclusion, and minor change in introduction Tested everything on crystal.

@@
   that when the cells are mechanically deformed into wide, flattened
-  out, irregular shapes, the robust regularity of this oscillatory
-  behavoir is no longer seen. Here we study widely used stochastic and
-  deterministic models of Min-system simulation within these new cell
-  shapes.  We find that the deterministic model is largely inadequate
-  in reproducing the qualitatively irregular behavoir, while the
-  stochastic model, based on the same differential equations, is able
-  to accurately predict what has been seen.  We also find that it is
-  the flattened nature of the newly deformed cells' shape that is
-  responsible for the irregular oscillation behavoir, as opposed to
-  its irregularity and asymmetry.
+  out, irregular shapes, the spatial regularity of these oscillations
+  breaks down. Here we study widely used stochastic and deterministic
+  models of Min-system simulation within these new cell shapes.  We
+  find that the deterministic model is decidedly inadequate to
+  reproduce the experimentally observed behavoir, while the stochastic
+  model, based on the same differential equations, is able to do so
+  accurately.  We also find that it is the flattening rather than the
+  irregularity and asymmetry of the cell shape that causes the
+  irregular oscillation behavoir.
 \end{abstract}
@@
 recruited to the membrane by MinD that is already clustered there
-(following observed non-linear attachement of minD on the cell
+(following observed non-linear attachement of MinD on the cell
 membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
@@
 reaction-diffusion equations~\cite{fange2006noise, kerr2006division}.
-These studies largely confirm the results
-of Huang's model when applied to the wild-type, pill-shaped phenotype.
-However, the stochastic models more successfully predict
+These studies largely confirm the results of Huang's deterministic
+model when applied to the wild-type, pill-shaped phenotype.  However,
+the stochastic models are slightly more successful in predicting
 experimentally observed oscillations in round cell
-phenotypes~\cite{fange2006noise, huang2004min}, and enable prediction
-of fluctuations in the predicted
+phenotypes~\cite{fange2006noise, huang2004min}, and they enable
+prediction of fluctuations in the predicted
 behavior~\cite{kruse2007experimentalist}.  Both deterministic and
@@
 intermediate maximum appearing in shape \emph{B}.  Thus we conclude
-that this method is inconsistent with experiment, and cannot be
-relied upon for predictions of the behavior of the MinD system.
-\fixme{Confirm others? What failures have already been seen? Is this
-  the most dramatic?}
+that this method is inconsistent with experiment, and cannot be relied
+upon for predictions of the behavior of the MinD system.  This is the
+most clear example of the inadequacy of the deterministic simulation
+method in reproducing experimental behavoir of the MinD system to
+date.  Until now the results of deterministic and stochastic
+simulation have largely coincided, with the stochastic method showing
+minor differences in behavoir when compared to deterministic
+models~\cite{kerr2006division, fange2006noise, huang2004min,
+  kruse2007experimentalist}.
 

### 2014-11-04 paper/paper-one.tex
added my best attempt at putting everything into pnas format, added style file cls file and changes to Makefile Tested everything on crystal.

--- 2014-11-04 paper/paper.tex
@@
-\documentclass[letterpaper,twocolumn,amsmath,amssymb,pre]{revtex4-1}
-\usepackage{graphicx}% Include figure files
-\usepackage{color}
+%% PNAStwoS.tex
+%% Sample file to use for PNAS articles prepared in LaTeX
+%% For two column PNAS articles
+%% Version: Apr 15, 2008
+
+%% BASIC CLASS FILE
+\documentclass{pnastwo}
+
+%% ADDITIONAL OPTIONAL STYLE FILES
+%\usepackage[dvips]{graphicx}
+%\usepackage{pnastwoF}
+\usepackage{amssymb,amsfonts,amsmath}
 
@@
 
+%% OPTIONAL MACRO DEFINITIONS
+%\def\s{\sigma}
+
+%%%%%%%%%%%%
+%% For PNAS Only:
+\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
+\copyrightyear{2008}
+\issuedate{Issue Date}
+\volume{Volume}
+\issuenumber{Issue Number}
+%\setcounter{page}{2687} %Set page number here if desired
+%%%%%%%%%%%%
+
 \begin{document}
-\title{Robustness of MinD oscillation in \emph{Escherichia coli} with
+
+\title{Robustness of MinD oscillation in \textbf{\emph{Escherichia coli}} with
   diverse cell shapes}
 
-\author{Jeff B. Schulte}
-\affiliation{Department of Physics, Oregon State University}
-\author{Rene W. Zeto}
-\affiliation{Department of Physics, Oregon State University}
-\author{David Roundy}
-\affiliation{Department of Physics, Oregon State University}
+\author{Jeff B. Schulte\affil{1}{Department of Physics, Oregon State University},
+Rene W. Zeto\affil{1}{}
+\and
+David Roundy\affil{1}{}}
 
+\contributor{Submitted to Proceedings of the National Academy of Sciences
+of the United States of America}
+
+\maketitle
+
+\begin{article}
 \begin{abstract}
@@
 
-\maketitle
+\keywords{MinD | oscillation | stochastic | deterministic | simulation}
 
-\section{Introduction}
-It is vital that during the process of bacterial cell division a cell
+\abbreviations{SAM, self-assembled monolayer; OTS,
+octadecyltrichlorosilane}
+
+\dropcap{I}t is vital that during the process of bacterial cell division a cell
 avoid minicelling, or splitting into daughter cells with lopsided
@@
 
-%% \fixme{There are not any direct comparisons of the deterministic and
-%%   stochastic models that I can find other than the fange2006 paper
-%%   cited above for the round cells.  Those showed that the
-%%   deterministic sims are 'bistable' - one type of initial conditions
-%%   (MinD starting on walls on one side) show oscillations, another type
-%%   (half cyto is filled with 3/4 of MinD) don't.  Huang in 2004 paper
-%%   cited above uses numerical determinisitc and finds that it can show
-%%   oscillations in round cells as well, but right now I can't find it
-%%   and the journal doesn't give me access to it.  predict oscillations
-%%   in perfectly round cells unless noise was added to the simulation,
-%%   but could in almost round ellipses.  It seems that once the
-%%   stochastic models began to be used, nobody really used the
-%%   deterministic model any longer.  Not sure what to say about this in
-%%   order to introduce what we do here properly.}
-
 In this paper we use Huang's 2003 model~\cite{huang2003dynamic} in
@@
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{reactions}
-  \caption{Reactions included in the model of Huang \emph{et
-      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{reactions}
+%%   \caption{Reactions included in the model of Huang \emph{et
+%%       al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
+%% \end{figure}
 
@@
 
-%% Our pill shapes differ from those of Huang \emph{et al.} in that they
-%% are cylinders with hemisphere endcaps instead of pure cylindrical
-%% shapes.  Our cylinderidrical radius is $0.5\micron$ and the lengths
-%% of our cells (measured between the tips of the endcaps) are
-%% $5\micron$, $4\micron$, $3\micron$, and $2.5\micron$.
-
-%% \fixme{Is the following Kubitscheck paragraph needed?}
-%% Kubitschek has shown in multiple experiments that at the time of cell
-%% division cells have a volume that is within a range of roughly
-%% $1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
-%%   kubitschek1968linear}.  We follow Huang's
-%% simulations\cite{huang2003dynamic} and Mannik's experiments and model
-%% cells that are slightly larger than this range.
-
-\begin{figure*}
-  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
-  \begin{center}
-    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
-    \vspace{-1.5em}
-    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-    \vspace{-3em}
-  \end{center}
-  \caption{Images of the concentration of each protein species in a
-    natural pill-shaped bacterium at one-second time intervals. The
-    upper plots shows results from the deterministic model and the
-    lower shows results from the stochastic model.  The order of
-    frames is such that individual MinD proteins begin at the bottom
-    of the plot (in the MinD:ATP state in the cytoplasm), and progress
-    upward until they reach the MinE:MinD:ATP membrane-bound complex.
-    At that point, they will spontaneously dissociate into cytoplasmic
-    MinE (the top row) and the starting state of cytoplasmic
-    MinD:ADP.}.
-  \label{image-p}
-\end{figure*}
+%% \begin{figure*}
+%%   %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+%%   \begin{center}
+%%     \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
+%%     \vspace{-1.5em}
+%%     \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+%%     \vspace{-1.5em}
+%%   \end{center}
+%%   \caption{Images of the concentration of each protein species in a
+%%     natural pill-shaped bacterium at one-second time intervals. The
+%%     upper plots shows results from the deterministic model and the
+%%     lower shows results from the stochastic model.  The order of
+%%     frames is such that individual MinD proteins begin at the bottom
+%%     of the plot (in the MinD:ATP state in the cytoplasm), and progress
+%%     upward until they reach the MinE:MinD:ATP membrane-bound complex.
+%%     At that point, they will spontaneously dissociate into cytoplasmic
+%%     MinE (the top row) and the starting state of cytoplasmic
+%%     MinD:ADP.}.
+%%   \label{image-p}
+%% \end{figure*}
 
@@
 \section{Naturally Occuring Pill Shaped Cells}
+
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
+%%   \caption{Temporal correlation function of the total MinD found in
+%%     two opposite polar regions of the pill-shaped cell, shown against
+%%     the correlation time.  Data for both the the determinisitic and
+%%     stochastic models are shown.  The stochastic model shows an
+%%     oscillation period of 39.5 seconds and coherence time of 307 seconds.
+%%     The correlation functions are scaled to have the same initial
+%%     value.}
+%%   \label{corr-pill}
+%% \end{figure}
 
@@
 
-%% is concentrated in the
-%% upper portion of the cell and is diffusing downward, where it will
-%% react with and stick to wall-bound MinD that is concentrated on the
-%% membrane in the lower portion of the cell.  This process is in fact
-%% already well on its way, as seen by the significant concentration of
-%% wall bound MinD:MinE which is creeping down to the lower corner,
-%% removing the MinD from the membrane as it goes.  The removed MinD
-%% (cytoplasmic MinD:ADP) diffuses freely for a time before spontenously
-%% undergoing nucleotide exchange and shifting back into the MinD:ATP
-%% that is able to attach to the membrane.  Diffusing a small distance
-%% away from the bottom of the cell will bring the protein into the MinE
-%% \fixme{collection ??}, where reactions will prevent it from collecting
-%% for any significant time on the membrane.  Diffusing further towards
-%% the upper end, however, while the MinE has not yet collected there,
-%% will allow MinD:ATP to accumulate with the other MinD:ATP, which is
-%% seen at seconds 10 through 15 in Figure~\ref{image-p}.  Eventually the
-%% MinE creeps all the way down to the bottom of the cell where it slowly
-%% runs out of wall bound MinD to react with, before diffusing back up
-%% and starting again on the upper portion of the cell. This is seen in
-%% seconds 15 through 20 in the figure.  \fixme{There is another
-%%   paragraph after this in the latex that I commented out because I
-%%   thought we might be spending too much time on the description}
-
-%%  At 15 seconds, the membrane-bound MinD:ATP has
-%% been essentially removed from the top end of the cell, and MinD:ATP
-%% has begun to bind to the membrane in the the lower half of the cell.
-%% At this stage, there is a high concentration of cytoplasmic MinE at
-%% the top of the cell, and by 16 seconds we begin to see the formation
-%% of a MinE ring just below the center of the cell.  At 18 seconds, the
-%% cell has reached its original state (reversed directionally), with
-%% MinD:ATP bound to the membrane on the lower third of the cell, a high
-%% concentration of cytoplasmic MinE in the upper half of the cell, and a
-%% MinE ring pushing downward on the membrane-bound MinD:ATP.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
-  \caption{Temporal correlation function of the total MinD found in
-    two opposite polar regions of the pill-shaped cell, shown against
-    the correlation time.  Data for both the the determinisitic and
-    stochastic models are shown.  The stochastic model shows an
-    oscillation period of 39.5 seconds and coherence time of 307 seconds.
-    The correlation functions are scaled to have the same initial
-    value.}
-  \label{corr-pill}
-\end{figure}
-
 It is clear from Fig.~\ref{image-p} that the stochastic simulation
@@
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{../paper/plot-ave}
-  \caption{We display here arrows depicting successive maxima in space
-    and and time overlayed on a color plot of the total MinD density
-    averaged over the same time period.  The simulation time covered
-    for the flattened cells is 350 seconds, which is the same
-    period of time depicted in the experimental data plots of Mannik
-    \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
-    shape, we only cover 250 seconds, in order to provide a
-    useful comparison due to its shorter oscillation period.  The top
-    row shows plots published by Mannik of the MinD maxima behavoir
-    and the bottom two rows show our simulations using the stochastic
-    and deterministic models, respectively.  We simulated
-    approximations to the two shapes observed by Mannik, which we call
-    \emph{shape A} and \emph{shape B}.  In addition, we studied two
-    flattened stadium shapes which we call \emph{stadium A} and
-    \emph{stadium B} corresponding in aspect ratio and thickness to
-    the two experimental shapes.  The spatial length scale of all the
-    figures shown was identical. Each of the flattened cell shapes
-    uses the same color scale for the number of proteins per unit
-    area.  Finally, we display the natural pill shape, which was also
-    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
-    different color scale to reflect the thicker cell containing more
-    proteins per cross-sectional area.  }
-  \label{randst-plot-ave}
-\end{figure*}
+%% \begin{figure*}
+%%   \centering
+%%   \includegraphics[width=0.8\textwidth]{../paper/plot-ave}
+%%   \caption{We display here arrows depicting successive maxima in space
+%%     and and time overlayed on a color plot of the total MinD density
+%%     averaged over the same time period.  The simulation time covered
+%%     for the flattened cells is 350 seconds, which is the same
+%%     period of time depicted in the experimental data plots of Mannik
+%%     \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
+%%     shape, we only cover 250 seconds, in order to provide a
+%%     useful comparison due to its shorter oscillation period.  The top
+%%     row shows plots published by Mannik of the MinD maxima behavoir
+%%     and the bottom two rows show our simulations using the stochastic
+%%     and deterministic models, respectively.  We simulated
+%%     approximations to the two shapes observed by Mannik, which we call
+%%     \emph{shape A} and \emph{shape B}.  In addition, we studied two
+%%     flattened stadium shapes which we call \emph{stadium A} and
+%%     \emph{stadium B} corresponding in aspect ratio and thickness to
+%%     the two experimental shapes.  The spatial length scale of all the
+%%     figures shown was identical. Each of the flattened cell shapes
+%%     uses the same color scale for the number of proteins per unit
+%%     area.  Finally, we display the natural pill shape, which was also
+%%     featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
+%%     different color scale to reflect the thicker cell containing more
+%%     proteins per cross-sectional area.  }
+%%   \label{randst-plot-ave}
+%% \end{figure*}
+
+%% \begin{figure}
+%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
+%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
+%%   \caption{Temporal correlation function of the total MinD found in
+%%     two opposite polar regions of the shape \emph{A} (above) and the
+%%     stadium \emph{A} (below) cell shapes, shown against the
+%%     correlation time.  Data for both the the determinisitic and
+%%     stochastic models are shown, and the correlation functions are
+%%     scaled to have the same initial value.  For shape \emph{A}, the
+%%     stochastic model shows an oscillation period of 53.1 seconds and
+%%     coherence time of 246 seconds, so that it takes roughly 4.6 periods
+%%     for the behavoir to decohere.  For the stadium \emph{A}, the same
+%%     model shows an oscillation period of 51 seconds and coherence time of
+%%     323 seconds, so that it takes roughly 6.3 periods for the behavoir
+%%     to decohere.}
+%%   \label{fig:corr-pancake-A}
+%% \end{figure}
 
 \section{Comparison of Mannik's Experimental and Our Stadium Shapes}
-
 As described in Section~\ref{sec:model-method-shapes}, we will focus
@@
 %% cells~\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}.
-
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
-  \caption{Temporal correlation function of the total MinD found in
-    two opposite polar regions of the shape \emph{A} (above) and the
-    stadium \emph{A} (below) cell shapes, shown against the
-    correlation time.  Data for both the the determinisitic and
-    stochastic models are shown, and the correlation functions are
-    scaled to have the same initial value.  For shape \emph{A}, the
-    stochastic model shows an oscillation period of 53.1 seconds and
-    coherence time of 246 seconds, so that it takes roughly 4.6 periods
-    for the behavoir to decohere.  For the stadium \emph{A}, the same
-    model shows an oscillation period of 51 seconds and coherence time of
-    323 seconds, so that it takes roughly 6.3 periods for the behavoir
-    to decohere.}
-  \label{fig:corr-pancake-A}
-\end{figure}
 
@@
 is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.
-%% %
-%% In order to understand the irregular MinD oscillations observed in
-%% experiments with flattened cells, we simulated flattened ``stadium''
-%% shapes in order to distinguish between the effect of flattening and
-%% the effect of irregular shape.
-%% %
-%% We found only a moderate difference in the coherence of bipolar
-%% oscillations within these stadium shapes and the irregular shapes
-%% observed by Mannik \emph{et al.}, and have observed visually the same
-%% qualitative spatially irregular formation of maxima in both.  Thus we
-%% conclude that the disruption of the MinD oscillations seen by Mannik
-%% \emph{et al.}  is largely due to the flattening of the cell shape, as
-%% opposed to its irregularity.
 
-\bibliography{paper}
+\bibliographystyle{plain}
+\bibliography{paper-one}
+\end{article}
+
+%\section*{Appendix}
+\begin{acknowledgments}
+This work was partially supported by
+Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
+J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
+\end{acknowledgments}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{reactions}
+  \caption{Reactions included in the model of Huang \emph{et
+      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
+\end{figure}
+
+\begin{figure*}
+  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+  \begin{center}
+    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
+    \vspace{-1.5em}
+    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+    \vspace{-1.5em}
+  \end{center}
+  \caption{Images of the concentration of each protein species in a
+    natural pill-shaped bacterium at one-second time intervals. The
+    upper plots shows results from the deterministic model and the
+    lower shows results from the stochastic model.  The order of
+    frames is such that individual MinD proteins begin at the bottom
+    of the plot (in the MinD:ATP state in the cytoplasm), and progress
+    upward until they reach the MinE:MinD:ATP membrane-bound complex.
+    At that point, they will spontaneously dissociate into cytoplasmic
+    MinE (the top row) and the starting state of cytoplasmic
+    MinD:ADP.}.
+  \label{image-p}
+\end{figure*}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
+  \caption{Temporal correlation function of the total MinD found in
+    two opposite polar regions of the pill-shaped cell, shown against
+    the correlation time.  Data for both the the determinisitic and
+    stochastic models are shown.  The stochastic model shows an
+    oscillation period of 39.5 seconds and coherence time of 307 seconds.
+    The correlation functions are scaled to have the same initial
+    value.}
+  \label{corr-pill}
+\end{figure}
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=0.8\textwidth]{../paper/plot-ave}
+  \caption{We display here arrows depicting successive maxima in space
+    and and time overlayed on a color plot of the total MinD density
+    averaged over the same time period.  The simulation time covered
+    for the flattened cells is 350 seconds, which is the same
+    period of time depicted in the experimental data plots of Mannik
+    \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
+    shape, we only cover 250 seconds, in order to provide a
+    useful comparison due to its shorter oscillation period.  The top
+    row shows plots published by Mannik of the MinD maxima behavoir
+    and the bottom two rows show our simulations using the stochastic
+    and deterministic models, respectively.  We simulated
+    approximations to the two shapes observed by Mannik, which we call
+    \emph{shape A} and \emph{shape B}.  In addition, we studied two
+    flattened stadium shapes which we call \emph{stadium A} and
+    \emph{stadium B} corresponding in aspect ratio and thickness to
+    the two experimental shapes.  The spatial length scale of all the
+    figures shown was identical. Each of the flattened cell shapes
+    uses the same color scale for the number of proteins per unit
+    area.  Finally, we display the natural pill shape, which was also
+    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
+    different color scale to reflect the thicker cell containing more
+    proteins per cross-sectional area.  }
+  \label{randst-plot-ave}
+\end{figure*}
+
+\begin{figure}
+  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
+  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
+  \caption{Temporal correlation function of the total MinD found in
+    two opposite polar regions of the shape \emph{A} (above) and the
+    stadium \emph{A} (below) cell shapes, shown against the
+    correlation time.  Data for both the the determinisitic and
+    stochastic models are shown, and the correlation functions are
+    scaled to have the same initial value.  For shape \emph{A}, the
+    stochastic model shows an oscillation period of 53.1 seconds and
+    coherence time of 246 seconds, so that it takes roughly 4.6 periods
+    for the behavoir to decohere.  For the stadium \emph{A}, the same
+    model shows an oscillation period of 51 seconds and coherence time of
+    323 seconds, so that it takes roughly 6.3 periods for the behavoir
+    to decohere.}
+  \label{fig:corr-pancake-A}
+\end{figure}
 
 \end{document}
-
-\section*{Appendix}
-
-\section{Below are NOTES for the Writing}
-
-%% mannik B 11500 seconds, mannik A 15600 seconds, stadium A 19120  seconds, pill 19990 seconds
-%% = simulation time that deterministic correlation data covers.
-
-\end{document}

### 2014-11-05 paper/PNASTMPL.TEX
more work on making PNAS formatting beautiful and correct Tested everything on bennet.

%% PNAStwoS.tex
%% Sample file to use for PNAS articles prepared in LaTeX
%% For two column PNAS articles
%% Version1: Apr 15, 2008
%% Version2: Oct 04, 2013

%% BASIC CLASS FILE
\documentclass{pnastwo}

%% ADDITIONAL OPTIONAL STYLE FILES Font specification

%\usepackage{pnastwoF}

%% OPTIONAL MACRO DEFINITIONS
\def\s{\sigma}
%%%%%%%%%%%%
%% For PNAS Only:
\url{www.pnas.org/cgi/doi/10.1073/pnas.0709640104}
\copyrightyear{2008}
\issuedate{Issue Date}
\volume{Volume}
\issuenumber{Issue Number}
%\setcounter{page}{2687} %Set page number here if desired
%%%%%%%%%%%%

\begin{document}

\title{Almost sharp fronts for the surface geostrophic equation}

\author{Roberta Graff\affil{1}{University of Cambridge, Cambridge,
United Kingdom},
Javier de Ruiz Garcia\affil{2}{Universidad de Murcia, Bioquimica y Biologia
Molecular, Murcia, Spain},
\and
Franklin Sonnery\affil{2}{}}

\contributor{Submitted to Proceedings of the National Academy of Sciences
of the United States of America}

%%%Newly updated.
%%% If significance statement need, then can use the below command otherwise just delete it.
\significancetext{RJSM and ACAC developed the concept of the study. RJSM conducted the analysis, data interpretation and drafted the manuscript. AGB contributed to the development of the statistical methods, data interpretation and drafting of the manuscript.}

\maketitle

\begin{article}
\begin{abstract}
{We use heat kernels or eigenfunctions of the Laplacian to construct
local coordinates on large classes of Euclidean domains and Riemannian
manifolds (not necessarily smooth, e.g. with $\mathcal{C}^\alpha$
metric). These coordinates are bi-Lipschitz on large neighborhoods of
the domain or manifold, with  constants controlling the distortion and
the size of the neighborhoods that depend only on natural geometric
properties of the domain or manifold. The proof of these results relies
on novel estimates, from above and below, for the heat kernel and its
gradient, as well as for the eigenfunctions of the Laplacian and their
gradient, that hold in the non-smooth category, and are stable with
respect to perturbations within this category. Finally, these coordinate
systems are intrinsic and efficiently computable, and are of value in
applications.}
\end{abstract}

\keywords{monolayer | structure | x-ray reflectivity | molecular electronics}

\abbreviations{SAM, self-assembled monolayer; OTS, octadecyltrichlorosilane}

\dropcap{I}n this article we study the evolution of ``almost-sharp'' fronts
for the surface quasi-geostrophic equation. This 2-D active scalar
equation reads for the surface quasi-geostrophic equation.
\begin{equation}
\mfrac{D \theta}{Dt}=\mfrac{\pr \theta}{\pr t} + u\cdot \nabla
\theta=0 \label{qg1}
\end{equation}
where,
\begin{equation}
 u=(u_1,u_2)=(-\mfrac{\pr \psi}{\pr y},\mfrac{\pr \psi}{\pr
x})\label{qg2} \end{equation}
and,
\begin{equation} (-\triangle)^{\f12}\psi=\theta \, ,\label{qg3} \end{equation}
For simplicity we are considering fronts on the cylinder, i.e. we
take $(x,y)$ in $\mathbb{R}/_{\displaystyle{\mathbb{Z}}}\times
\mathbb{R}$. In this setting we define $-\triangle^{-\f12}$ that
comes from inverting the third equation by convolution with the
kernel. To avoid irrelevant considerations at $\infty$ we
will take $\eta$ to be compactly supported
\[
\mfrac{\chi(u,v)}{(u^2+v^2)^{\f12}}+\eta(u,v)
\]
where $\chi (x,y)\ \epsilon\ C^{\infty}_{0},\,\,
\chi(x,y)=1 \hspace{8pt} \mbox{in} \hspace{5pt} |x-y|\leq r \,\,
\mbox{and}\,\, supp \chi$ is contained in $  \{|x-y|\leq R\} $
with $0<r<R<\frac{1}{2}$. Also $ \eta\ \epsilon\ C^{\infty}_0$,
$\eta(0,0)=0 $.

The main mathematical interest in the quasi-geostrophic equation
lies in its strong similarities with the 3-Euler equations. These
results were first proved by Constantin, Majda and Tabak, see
\cite{1}, \cite{2} and \cite{3} for more details. There
are several other research lines for this equation, both
theoretical and numerical. See  \cite{4}, \cite{5}, and
\cite{6}.
The question
about the regularity of the solutions for QG  remains as an open
problem.

Recently one of the authors has obtained the equation for the
evolution of sharp fronts (in the periodic setting), proving its
local well-posedness for that equation. (see \cite{ZhaZha} and
\cite{TSL} for more details). This is a problem in contour
dynamics. Contour dynamics for other fluid equations has been
studied extensively.

\section{Analysis of almost sharp fronts}
We begin our analysis on almost sharp fronts for the
quasi-geostrophic equation recalling the notion of weak solution.

For these solutions we have the following

\begin{definition}
A bounded function $\theta$ is a weak solution of QG if for any
$\phi\,\epsilon\,
C_0^{\infty}(\fdb\times\mathbb{R}\times[0,\vep])$ we have
\begin{eqnarray}
&&  \int_{\mathbb{R}^+\times\fd\times\mathbb{R}} \hspace{-25pt}
 \theta(x,y,t)\, \pr_t \phi
\,(x,y,t) dy dx dt+\nonumber\\
  & +&\int_{\mathbb{R}^+\times\fd\times\mathbb{R}}
\hspace{-26pt} \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t)
dydxdt = 0 \label{weaksol} \end{eqnarray}
where $u$ is determined by equations \eqref{qg2} and \eqref{qg3}.
\end{definition}

\subsection{Data Sources}
We are interested in studying the evolution of almost sharp fronts
for the QG equation. These are weak solutions of the equation with
large gradient ($\sim \displaystyle{ \inlinefrac{1}{\delta}}$, where $2
\delta$ is the thickness of the transition layer for $\theta$).

\section{Discussion}
\subsection{Cylindrical Case}
We are going to consider the cylindrical case here. We consider a
transition layer of thickness smaller than $2\delta$ in which
 $\theta$ changes from 0 to 1. (see Figure \ref{afoto}).That means we are considering $\theta$  of the form
\[
\theta  = 1   \mbox{ if }\quad  y\geq \varphi(x,t)+\delta
\]
\[
\theta \mbox{ bounded} \mbox{ if }\quad |\varphi(x,t)-y|\leq\delta
\]
\be \theta = 0  \mbox{ if }\quad  y\leq \varphi(x,t)-\delta
\label{theta} \ee
where $\varphi$ is a smooth periodic function and
$0<\delta<\frac{1}{2}$.

%For these solutions we have the following

\begin{theorem}
If the active scalar $\theta$ is as in \eqref{theta} and satisfies
the equation \eqref{weaksol}, then $\varphi$ satisfies the
equation
\begin{eqnarray}
\mfrac{\pr \varphi}{\pr t}(x,t)&=&\hspace{-2pt}\dst
\int_{\fd}\mfrac{\mfrac{\pr \varphi}{\pr x}(x,t)-\mfrac{\pr
\varphi}{\pr
u}(u,t)}{[(x-u)^{2}+(\varphi(x,t)-\varphi(u,t))^{2}]^{\f12}}\nonumber\\
&&
\chi(x-u,\varphi(x,t)-\varphi(u,t)) du \hspace{3pt} +
\nonumber\\
&+&\dst \int_{\fd} \Big{[}\mfrac{\pr \varphi} {\pr
x}(x,t)-\mfrac{\pr \varphi}{\pr u} (u,t)\Big{]}
\nonumber\\&&
\eta(x-u,\varphi(x,t)-\varphi(u,t)) du + Error
\end{eqnarray}
with $|Error|\leq C\, \delta | log\delta| $ where $C$ depends only
on $\|\theta\|_{L^{\infty}}$ and $\|
\nabla\varphi\|_{L^{\infty}}$.
\end{theorem}

\begin{remark}
Note that equation \eqref{theta} specifies  the function $\varphi$
up to an error of order $\delta$. Theorem 1 provides an evolution
equation for the function $\varphi$ up to an error of order
$\delta |log \delta|$.
\end{remark}

In order to analyze the evolution of the ``almost-sharp'' front we
substitute the above expression for $\theta$ in the definition of
a weak solution (see \eqref{weaksol}). We use the notation $X =O(
Y)$ to indicate that $|X|\leq C |Y|$ where the constant $C$
depends only on $\|\theta\|_{L^{\infty}}$, $\|
\nabla\varphi\|_{L^{\infty}}$ and $\|\phi\|_{C^1}$, where $\phi$
is a test function appearing in Definition 1.

We consider the 3 different regions defined by the form on
$\theta$. Since $\theta=0$ in the region I the contribution from
that region is 0, i.e.
\[
  \int_{I\times \mathbb{R}}
 \theta(x,y,t)\, \pr_t \phi
\,(x,y,t) dy dx dt+  \]
\[
   +\int_{I\times \mathbb{R}}
 \theta\,(x,y,t) u(x,y,t)\cdot\nabla\phi\,(x,y,t) dydxdt = 0
\]

As for the region II
\[
\int_{II\times \mathbb{R}} \theta (x,y,t) \pr_t\phi (x,y,t)dx dy
dt = O(\delta)
\]
since $\theta$ is bounded and hence $O(1)$, and the area of the
region II is $O(\delta)$. As for the second term
\[
\int_{II\times \mathbb{R}} u \theta \nabla \phi dx dy dt =
O(\delta log(\delta))
\]

To see this, we fix $t$. We must estimate
\[
\int_{\mathbb{R}^2} u\cdot(\mathbb{1}_{II}\theta\nabla\phi) dx dy
\]
We are left to estimate the terms
\[
\int_{III\times \mathbb{R}} \theta \pr_t\phi dx dy
dt+\int_{III\times \mathbb{R}} \theta u_f\cdot \nabla \phi dx dy
dt=:A+B
\]

\subsection{Observations}
The following observations can be made form the numerical experiments
described in this section, and are consistent with the results
of more extensive experimentation performed by the authors:
\begin{itemize}
\item The CPU times in Tables 1--3 are compatible with the estimates in
formulae {\bf 14}, {\bf 16}, and {\bf 23}.
\item
The precision produced by each of Algorithms {\bf I} and {\bf II}
is similar to that provided by formula {\bf 3}, even when
$\omega_{k+1}$ is close to the machine precision.
\end{itemize}

\begin{materials}
\section{Digital RNA SNP Analysis} A real-time PCR assay was designed
to amplify {\it PLAC4} mRNA, with the two SNP alleles being discriminated
by TaqMan probes. {\it PLAC4} mRNA concentrations were quantified in
extracted RNA samples followed by dilutions to approximately one target
template molecule of either type (i.e., either allele) per well.
Details are given in the {\it SI Materials and Methods}.

\section{Digital RCD Analysis} Extracted DNA was quantified by
spectrophotometry (NanoDrop Technologies, Wilmington, DE) and diluted to a
concentration of
approximately one target template from either chr21 or ch1 per well.
\end{materials}

\appendix[Estimating the Spectral Norm of a Matrix]
In this appendix we describe a method for the estimation of the spectral norm
of matrix $A$. The method does not require access to the individual
entries of $A$; it requires only applications of $A$ and $A$* to vectors.
It is a version of the classical power method. Its probabilistic
analysis summarized below was introduced fairly recently in refs. 13
and 14. This appendix is included here for completeness.

\appendix
This is an example of an appendix without a title.

\begin{acknowledgments}
This work was partially supported by
Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
\end{acknowledgments}

\begin{thebibliography}{10}
\bibitem{BN}
M.~Belkin and P.~Niyogi, {\em Using manifold structure for partially
  labelled classification}, Advances in NIPS, 15 (2003).

\bibitem{BBG:EmbeddingRiemannianManifoldHeatKernel}
P.~B\'erard, G.~Besson, and S.~Gallot, {\em Embedding {R}iemannian
  manifolds by their heat kernel}, Geom. and Fun. Anal., 4 (1994),
  pp.~374--398.

\bibitem{CLAcha1}
R.R.~Coifman and S.~Lafon, {\em Diffusion maps}, Appl. Comp. Harm. Anal.,
  21 (2006), pp.~5--30.

\bibitem{DiffusionPNAS}
R.R.~Coifman, S.~Lafon, A.~Lee, M.~Maggioni, B.~Nadler, F.~Warner, and
  S.~Zucker, {\em Geometric diffusions as a tool for harmonic analysis and
  structure definition of data. {P}art {I}: Diffusion maps}, Proc. of Nat.
  Acad. Sci.,  (2005), pp.~7426--7431.

\bibitem{Clementi:LowDimensionaFreeEnergyLandscapesProteinFolding}
P.~Das, M.~Moll, H.~Stamati, L.~Kavraki, and C.~Clementi, {\em
  Low-dimensional, free-energy landscapes of protein-folding reactions by
  nonlinear dimensionality reduction}, P.N.A.S., 103 (2006), pp.~9885--9890.

\bibitem{DoGri}
D.~Donoho and C.~Grimes, {\em Hessian eigenmaps: new locally linear
  embedding techniques for high-dimensional data}, Proceedings of the National
  Academy of Sciences, 100 (2003), pp.~5591--5596.

\bibitem{DoGri:WhenDoesIsoMap}
D.~L. Donoho and C.~Grimes, {\em When does isomap recover natural
  parameterization of families of articulated images?}, Tech. Report Tech. Rep.
  2002-27, Department of Statistics, Stanford University, August 2002.

\bibitem{GruterWidman:GreenFunction}
M.~Gr\"uter and K.-O. Widman, {\em The {G}reen function for uniformly
  elliptic equations}, Man. Math., 37 (1982), pp.~303--342.

\bibitem{Simon:NeumannEssentialSpectrum}
R.~Hempel, L.~Seco, and B.~Simon, {\em The essential spectrum of neumann
  laplacians on some bounded singular domains}, 1991.

\bibitem{1}
Kadison, R.\ V.\ and Singer, I.\ M.\ (1959)
Extensions of pure states, {\it Amer.\ J.\ Math.\ \bf
81}, 383-400.

\bibitem{2}
Anderson, J.\ (1981) A conjecture concerning the pure states of
$B(H)$ and a related theorem. in {\it Topics in Modern Operator
Theory}, Birkha\"user, pp.\ 27-43.

\bibitem{3}
Anderson, J.\ (1979) Extreme points in sets of
positive linear maps on $B(H)$. {\it J.\ Funct.\
Anal.\
\bf 31}, 195-217.

\bibitem{4}
Anderson, J.\ (1979) Pathology in the Calkin algebra. {\it J.\
Operator Theory \bf 2}, 159-167.

\bibitem{5}
Johnson, B.\ E.\ and Parrott, S.\ K.\ (1972) Operators commuting
with a von Neumann algebra modulo the set of compact operators.
{\it J.\ Funct.\ Anal.\ \bf 11}, 39-61.

\bibitem{6}
Akemann, C.\ and Weaver, N.\ (2004) Consistency of a
counterexample to Naimark's problem. {\it Proc.\ Nat.\ Acad.\
Sci.\ USA \bf 101}, 7522-7525.

\bibitem{TSL}
J.~Tenenbaum, V.~de~Silva, and J.~Langford, {\em A global geometric
  framework for nonlinear dimensionality reduction}, Science, 290 (2000),
  pp.~2319--2323.

\bibitem{ZhaZha}
Z.~Zhang and H.~Zha, {\em Principal manifolds and nonlinear dimension
  reduction via local tangent space alignement}, Tech. Report CSE-02-019,
  Department of computer science and engineering, Pennsylvania State
  University, 2002.
\end{thebibliography}

\end{article}

\begin{figure}
\centerline{\includegraphics[width=.4\textwidth]{figsamp.eps}}
\caption{LKB1 phosphorylates Thr-172 of AMPK$\alpha$ \textit{in vitro}
and activates its kinase activity.}\label{afoto}
\end{figure}

\begin{figure*}[ht]
\begin{center}
\centerline{\includegraphics[width=.7\textwidth]{figsamp.eps}}
\caption{LKB1 phosphorylates Thr-172 of AMPK$\alpha$ \textit{in vitro}
and activates its kinase activity.}\label{afoto2}
\end{center}
\end{figure*}

\begin{table}[h]
\caption{Repeat length of longer allele by age of onset class.
This is what happens when the text continues.}
\begin{tabular}{@{\vrule height 10.5pt depth4pt  width0pt}lrcccc}
&\multicolumn5c{Repeat length}\\
\noalign{\vskip-11pt}
Age of onset,\\
\cline{2-6}
\vrule depth 6pt width 0pt years&\multicolumn1c{\it n}&Mean&SD&Range&Median\\
\hline
Juvenile, 2$-$20&40&60.15& 9.32&43$-$86&60\\
Typical, 21$-$50&377&45.72&2.97&40$-$58&45\\
Late, $>$50&26&41.85&1.56&40$-$45&42\tablenote{The no. of wells for all samples was 384. Genotypes were
determined by mass spectrometric assay. The $m_t$ value indicates the
average number of wells positive for the over represented allele.}
\\
\hline
\end{tabular}
\end{table}

\begin{table*}[ht]
\caption{Summary of the experimental results}
\begin{tabular*}{\hsize}
{@{\extracolsep{\fill}}rrrrrrrrrrrrr}
\multicolumn{3}{l}{Parameters}&
\multicolumn{5}{c}{Averaged Results}&
\multicolumn{5}{c}{Comparisons}\cr
\hline
\multicolumn1c{$n$}&\multicolumn1c{$S^*_{MAX}$}&
\multicolumn1c{$t_1$}&\multicolumn1c{\ $r_1$}&
\multicolumn1c{\ $m_1$}&\multicolumn1c{$t_2$}&
\multicolumn1c{$r_2$}&\multicolumn1c{$m_2$}
&\multicolumn1c{$t_{lb}$}&\multicolumn1c{\ \ $t_1/t_2$}&
$r_1/r_2$&$m_1/m_2$&
$t_1/t_{lb}$\cr
\hline
10\tablenote{Stanford Synchrotron Radiation Laboratory (Stanford University,
Stanford, CA)}&1\quad &4&.0007&4&4&.0020&4&4&1.000&.333&1.000&1.000\cr
10\tablenote{$R_{\rm FREE}=R$ factor for the $\sim 5$\% of the randomly
chosen unique ref\/lections not used in the ref\/inement.}&5\quad &50&.0008&8&50&.0020&12&49&.999&.417&.698&1.020\cr
100\tablenote{Calculated for all observed data}&20\quad &2840975&.0423&95&2871117&.1083&521&---&
.990&.390&.182&---\ \ \cr
\hline
\end{tabular*}
\end{table*}

\end{document}

### 2014-11-05 paper/paper-MinD.tex
more work on making PNAS formatting beautiful and correct Tested everything on bennet.

--- 2014-11-04 paper/paper-one.tex
@@
 
-\title{Robustness of MinD oscillation in \textbf{\emph{Escherichia coli}} with
+\title{Robustness of MinD oscillation in \emph{Escherichia coli} with
   diverse cell shapes}
@@
 of the United States of America}
+
+\significancetext{In order to determine blah de blah...}
 
@@
 
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{reactions}
-%%   \caption{Reactions included in the model of Huang \emph{et
-%%       al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
-%% \end{figure}
+\begin{figure}
+  \includegraphics[width=8.7cm]{reactions}
+  \caption{Reactions included in the model of Huang \emph{et
+      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
+\end{figure}
 
@@
 
-%% \begin{figure*}
-%%   %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
-%%   \begin{center}
-%%     \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
-%%     \vspace{-1.5em}
-%%     \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-%%     \vspace{-1.5em}
-%%   \end{center}
-%%   \caption{Images of the concentration of each protein species in a
-%%     natural pill-shaped bacterium at one-second time intervals. The
-%%     upper plots shows results from the deterministic model and the
-%%     lower shows results from the stochastic model.  The order of
-%%     frames is such that individual MinD proteins begin at the bottom
-%%     of the plot (in the MinD:ATP state in the cytoplasm), and progress
-%%     upward until they reach the MinE:MinD:ATP membrane-bound complex.
-%%     At that point, they will spontaneously dissociate into cytoplasmic
-%%     MinE (the top row) and the starting state of cytoplasmic
-%%     MinD:ADP.}.
-%%   \label{image-p}
-%% \end{figure*}
+\begin{figure*}
+  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+  \begin{center}
+    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
+    \vspace{-1.5em}
+    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+    \vspace{-1.5em}
+  \end{center}
+  \caption{Images of the concentration of each protein species in a
+    natural pill-shaped bacterium at one-second time intervals. The
+    upper plots shows results from the deterministic model and the
+    lower shows results from the stochastic model.  The order of
+    frames is such that individual MinD proteins begin at the bottom
+    of the plot (in the MinD:ATP state in the cytoplasm), and progress
+    upward until they reach the MinE:MinD:ATP membrane-bound complex.
+    At that point, they will spontaneously dissociate into cytoplasmic
+    MinE (the top row) and the starting state of cytoplasmic
+    MinD:ADP.}.
+  \label{image-p}
+\end{figure*}
 
@@
 
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
-%%   \caption{Temporal correlation function of the total MinD found in
-%%     two opposite polar regions of the pill-shaped cell, shown against
-%%     the correlation time.  Data for both the the determinisitic and
-%%     stochastic models are shown.  The stochastic model shows an
-%%     oscillation period of 39.5 seconds and coherence time of 307 seconds.
-%%     The correlation functions are scaled to have the same initial
-%%     value.}
-%%   \label{corr-pill}
-%% \end{figure}
+\begin{figure}
+  \begin{center}
+    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
+  \end{center}
+  \caption{Temporal correlation function of the total MinD found in
+    two opposite polar regions of the pill-shaped cell, shown against
+    the correlation time.  Data for both the the determinisitic and
+    stochastic models are shown.  The stochastic model shows an
+    oscillation period of 39.5 seconds and coherence time of 307 seconds.
+    The correlation functions are scaled to have the same initial
+    value.}
+  \label{corr-pill}
+\end{figure}
 
@@
 
-%% \begin{figure*}
-%%   \centering
-%%   \includegraphics[width=0.8\textwidth]{../paper/plot-ave}
-%%   \caption{We display here arrows depicting successive maxima in space
-%%     and and time overlayed on a color plot of the total MinD density
-%%     averaged over the same time period.  The simulation time covered
-%%     for the flattened cells is 350 seconds, which is the same
-%%     period of time depicted in the experimental data plots of Mannik
-%%     \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
-%%     shape, we only cover 250 seconds, in order to provide a
-%%     useful comparison due to its shorter oscillation period.  The top
-%%     row shows plots published by Mannik of the MinD maxima behavoir
-%%     and the bottom two rows show our simulations using the stochastic
-%%     and deterministic models, respectively.  We simulated
-%%     approximations to the two shapes observed by Mannik, which we call
-%%     \emph{shape A} and \emph{shape B}.  In addition, we studied two
-%%     flattened stadium shapes which we call \emph{stadium A} and
-%%     \emph{stadium B} corresponding in aspect ratio and thickness to
-%%     the two experimental shapes.  The spatial length scale of all the
-%%     figures shown was identical. Each of the flattened cell shapes
-%%     uses the same color scale for the number of proteins per unit
-%%     area.  Finally, we display the natural pill shape, which was also
-%%     featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
-%%     different color scale to reflect the thicker cell containing more
-%%     proteins per cross-sectional area.  }
-%%   \label{randst-plot-ave}
-%% \end{figure*}
+\begin{figure*}
+  \centering
+  \includegraphics[width=16cm]{../paper/plot-ave}
+  \caption{We display here arrows depicting successive maxima in space
+    and and time overlayed on a color plot of the total MinD density
+    averaged over the same time period.  The simulation time covered
+    for the flattened cells is 350 seconds, which is the same
+    period of time depicted in the experimental data plots of Mannik
+    \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
+    shape, we only cover 250 seconds, in order to provide a
+    useful comparison due to its shorter oscillation period.  The top
+    row shows plots published by Mannik of the MinD maxima behavoir
+    and the bottom two rows show our simulations using the stochastic
+    and deterministic models, respectively.  We simulated
+    approximations to the two shapes observed by Mannik, which we call
+    \emph{shape A} and \emph{shape B}.  In addition, we studied two
+    flattened stadium shapes which we call \emph{stadium A} and
+    \emph{stadium B} corresponding in aspect ratio and thickness to
+    the two experimental shapes.  The spatial length scale of all the
+    figures shown was identical. Each of the flattened cell shapes
+    uses the same color scale for the number of proteins per unit
+    area.  Finally, we display the natural pill shape, which was also
+    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
+    different color scale to reflect the thicker cell containing more
+    proteins per cross-sectional area.  }
+  \label{randst-plot-ave}
+\end{figure*}
 
-%% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
-%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
-%%   \caption{Temporal correlation function of the total MinD found in
-%%     two opposite polar regions of the shape \emph{A} (above) and the
-%%     stadium \emph{A} (below) cell shapes, shown against the
-%%     correlation time.  Data for both the the determinisitic and
-%%     stochastic models are shown, and the correlation functions are
-%%     scaled to have the same initial value.  For shape \emph{A}, the
-%%     stochastic model shows an oscillation period of 53.1 seconds and
-%%     coherence time of 246 seconds, so that it takes roughly 4.6 periods
-%%     for the behavoir to decohere.  For the stadium \emph{A}, the same
-%%     model shows an oscillation period of 51 seconds and coherence time of
-%%     323 seconds, so that it takes roughly 6.3 periods for the behavoir
-%%     to decohere.}
-%%   \label{fig:corr-pancake-A}
-%% \end{figure}
+\begin{figure}
+  \begin{center}
+    \includegraphics[height=6.4cm]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
+    \includegraphics[height=6.4cm]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
+  \end{center}
+  \caption{Temporal correlation function of the total MinD found in
+    two opposite polar regions of the shape \emph{A} (above) and the
+    stadium \emph{A} (below) cell shapes, shown against the
+    correlation time.  Data for both the the determinisitic and
+    stochastic models are shown, and the correlation functions are
+    scaled to have the same initial value.  For shape \emph{A}, the
+    stochastic model shows an oscillation period of 53.1 seconds and
+    coherence time of 246 seconds, so that it takes roughly 4.6 periods
+    for the behavoir to decohere.  For the stadium \emph{A}, the same
+    model shows an oscillation period of 51 seconds and coherence time of
+    323 seconds, so that it takes roughly 6.3 periods for the behavoir
+    to decohere.}
+  \label{fig:corr-pancake-A}
+\end{figure}
 
@@
 %% \begin{figure}
-%%   \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
-%%   \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
+%%   \includegraphics[width=8.7cm]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
+%%   \includegraphics[width=8.7cm]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
 %%   \caption{Correlation for B shapes}
@@
 
+%% %\section*{Appendix}
+%% \begin{acknowledgments}
+%% This work was partially supported by
+%% Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
+%% J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
+%% \end{acknowledgments}
+
 \bibliographystyle{plain}
-\bibliography{paper-one}
+\bibliography{paper-MinD}
 \end{article}
 
-%\section*{Appendix}
-\begin{acknowledgments}
-This work was partially supported by
-Spanish Ministry of Science and Technology Grant BFM2002-02042 (to D.C. and
-J.L.R.) and by National Science Foundation Grand DMS-0245242 (to C.F.).
-\end{acknowledgments}
+%% \clearpage
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{reactions}
-  \caption{Reactions included in the model of Huang \emph{et
-      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=8.7cm]{reactions}
+%%   \caption{Reactions included in the model of Huang \emph{et
+%%       al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
+%% \end{figure}
 
-\begin{figure*}
-  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
-  \begin{center}
-    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
-    \vspace{-1.5em}
-    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-    \vspace{-1.5em}
-  \end{center}
-  \caption{Images of the concentration of each protein species in a
-    natural pill-shaped bacterium at one-second time intervals. The
-    upper plots shows results from the deterministic model and the
-    lower shows results from the stochastic model.  The order of
-    frames is such that individual MinD proteins begin at the bottom
-    of the plot (in the MinD:ATP state in the cytoplasm), and progress
-    upward until they reach the MinE:MinD:ATP membrane-bound complex.
-    At that point, they will spontaneously dissociate into cytoplasmic
-    MinE (the top row) and the starting state of cytoplasmic
-    MinD:ADP.}.
-  \label{image-p}
-\end{figure*}
+%% \begin{figure*}
+%%   %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+%%   \begin{center}
+%%     \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
+%%     \vspace{-1.5em}
+%%     \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+%%     \vspace{-1.5em}
+%%   \end{center}
+%%   \caption{Images of the concentration of each protein species in a
+%%     natural pill-shaped bacterium at one-second time intervals. The
+%%     upper plots shows results from the deterministic model and the
+%%     lower shows results from the stochastic model.  The order of
+%%     frames is such that individual MinD proteins begin at the bottom
+%%     of the plot (in the MinD:ATP state in the cytoplasm), and progress
+%%     upward until they reach the MinE:MinD:ATP membrane-bound complex.
+%%     At that point, they will spontaneously dissociate into cytoplasmic
+%%     MinE (the top row) and the starting state of cytoplasmic
+%%     MinD:ADP.}.
+%%   \label{image-p}
+%% \end{figure*}
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
-  \caption{Temporal correlation function of the total MinD found in
-    two opposite polar regions of the pill-shaped cell, shown against
-    the correlation time.  Data for both the the determinisitic and
-    stochastic models are shown.  The stochastic model shows an
-    oscillation period of 39.5 seconds and coherence time of 307 seconds.
-    The correlation functions are scaled to have the same initial
-    value.}
-  \label{corr-pill}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=8.7cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
+%%   \caption{Temporal correlation function of the total MinD found in
+%%     two opposite polar regions of the pill-shaped cell, shown against
+%%     the correlation time.  Data for both the the determinisitic and
+%%     stochastic models are shown.  The stochastic model shows an
+%%     oscillation period of 39.5 seconds and coherence time of 307 seconds.
+%%     The correlation functions are scaled to have the same initial
+%%     value.}
+%%   \label{corr-pill}
+%% \end{figure}
 
-\begin{figure*}
-  \centering
-  \includegraphics[width=0.8\textwidth]{../paper/plot-ave}
-  \caption{We display here arrows depicting successive maxima in space
-    and and time overlayed on a color plot of the total MinD density
-    averaged over the same time period.  The simulation time covered
-    for the flattened cells is 350 seconds, which is the same
-    period of time depicted in the experimental data plots of Mannik
-    \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
-    shape, we only cover 250 seconds, in order to provide a
-    useful comparison due to its shorter oscillation period.  The top
-    row shows plots published by Mannik of the MinD maxima behavoir
-    and the bottom two rows show our simulations using the stochastic
-    and deterministic models, respectively.  We simulated
-    approximations to the two shapes observed by Mannik, which we call
-    \emph{shape A} and \emph{shape B}.  In addition, we studied two
-    flattened stadium shapes which we call \emph{stadium A} and
-    \emph{stadium B} corresponding in aspect ratio and thickness to
-    the two experimental shapes.  The spatial length scale of all the
-    figures shown was identical. Each of the flattened cell shapes
-    uses the same color scale for the number of proteins per unit
-    area.  Finally, we display the natural pill shape, which was also
-    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
-    different color scale to reflect the thicker cell containing more
-    proteins per cross-sectional area.  }
-  \label{randst-plot-ave}
-\end{figure*}
+%% \begin{figure*}
+%%   \centering
+%%   \includegraphics[width=0.8\textwidth]{../paper/plot-ave}
+%%   \caption{We display here arrows depicting successive maxima in space
+%%     and and time overlayed on a color plot of the total MinD density
+%%     averaged over the same time period.  The simulation time covered
+%%     for the flattened cells is 350 seconds, which is the same
+%%     period of time depicted in the experimental data plots of Mannik
+%%     \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
+%%     shape, we only cover 250 seconds, in order to provide a
+%%     useful comparison due to its shorter oscillation period.  The top
+%%     row shows plots published by Mannik of the MinD maxima behavoir
+%%     and the bottom two rows show our simulations using the stochastic
+%%     and deterministic models, respectively.  We simulated
+%%     approximations to the two shapes observed by Mannik, which we call
+%%     \emph{shape A} and \emph{shape B}.  In addition, we studied two
+%%     flattened stadium shapes which we call \emph{stadium A} and
+%%     \emph{stadium B} corresponding in aspect ratio and thickness to
+%%     the two experimental shapes.  The spatial length scale of all the
+%%     figures shown was identical. Each of the flattened cell shapes
+%%     uses the same color scale for the number of proteins per unit
+%%     area.  Finally, we display the natural pill shape, which was also
+%%     featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
+%%     different color scale to reflect the thicker cell containing more
+%%     proteins per cross-sectional area.  }
+%%   \label{randst-plot-ave}
+%% \end{figure*}
 
-\begin{figure}
-  \includegraphics[width=\columnwidth]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
-  \includegraphics[width=\columnwidth]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
-  \caption{Temporal correlation function of the total MinD found in
-    two opposite polar regions of the shape \emph{A} (above) and the
-    stadium \emph{A} (below) cell shapes, shown against the
-    correlation time.  Data for both the the determinisitic and
-    stochastic models are shown, and the correlation functions are
-    scaled to have the same initial value.  For shape \emph{A}, the
-    stochastic model shows an oscillation period of 53.1 seconds and
-    coherence time of 246 seconds, so that it takes roughly 4.6 periods
-    for the behavoir to decohere.  For the stadium \emph{A}, the same
-    model shows an oscillation period of 51 seconds and coherence time of
-    323 seconds, so that it takes roughly 6.3 periods for the behavoir
-    to decohere.}
-  \label{fig:corr-pancake-A}
-\end{figure}
+%% \begin{figure}
+%%   \includegraphics[width=8.7cm]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}
+%%   \includegraphics[width=8.7cm]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
+%%   \caption{Temporal correlation function of the total MinD found in
+%%     two opposite polar regions of the shape \emph{A} (above) and the
+%%     stadium \emph{A} (below) cell shapes, shown against the
+%%     correlation time.  Data for both the the determinisitic and
+%%     stochastic models are shown, and the correlation functions are
+%%     scaled to have the same initial value.  For shape \emph{A}, the
+%%     stochastic model shows an oscillation period of 53.1 seconds and
+%%     coherence time of 246 seconds, so that it takes roughly 4.6 periods
+%%     for the behavoir to decohere.  For the stadium \emph{A}, the same
+%%     model shows an oscillation period of 51 seconds and coherence time of
+%%     323 seconds, so that it takes roughly 6.3 periods for the behavoir
+%%     to decohere.}
+%%   \label{fig:corr-pancake-A}
+%% \end{figure}
 

### 2014-11-05 paper/paper-MinD.tex
add notes and significance Tested everything on bennet.

@@
 
-\significancetext{In order to determine blah de blah...}
+\significancetext{When an E. Coli cell divides it must split into two
+  relatively equal volumes in order to survive.  One mechanism that
+  aids in this process is a system of proteins that oscillate between
+  cell ends and help the original cell divide along it’s center.  A
+  recent experiment found that by drastically deforming these cells
+  this oscillation can be disrupted.  We examine these oscillations in
+  similarly deformed cells computationally, using two widely used
+  simulation models, and find good agreement using one of them.  The
+  other model fails in a manner far more dramatic than has been
+  previously observed.  Furthermore, we find that the effect observed
+  experimentally in asymmetric and flattened cells is primarily a
+  result of the flattening, not the asymmetry.  }
 
@@
 
-\keywords{MinD | oscillation | stochastic | deterministic | simulation}
+\keywords{\fixme{E. Coli | MinD | oscillation | stochastic | deterministic | simulation}}
 
-\abbreviations{SAM, self-assembled monolayer; OTS,
-octadecyltrichlorosilane}
+\abbreviations{\fixme{SAM, self-assembled monolayer; OTS,
+octadecyltrichlorosilane}}
 
@@
 cases than have been seen thus far.
+
+\fixme{look for easily cut citations.}
 

### 2014-11-06 paper/paper-MinD.tex
dos2unix and edit abstract of paper-MinD Tested everything on bennet.

@@
   regulate the process of cell division by identifying the center of
-  the cell.  While this system usually exhibits robust polar
-  oscillations in a variety of cell shapes, new experiments have shown
-  that when the cells are mechanically deformed into wide, flattened
-  out, irregular shapes, the spatial regularity of these oscillations
-  breaks down. Here we study widely used stochastic and deterministic
-  models of Min-system simulation within these new cell shapes.  We
-  find that the deterministic model is decidedly inadequate to
-  reproduce the experimentally observed behavoir, while the stochastic
-  model, based on the same differential equations, is able to do so
-  accurately.  We also find that it is the flattening rather than the
-  irregularity and asymmetry of the cell shape that causes the
-  irregular oscillation behavoir.
+  the cell.  While this system usually exhibits robust bipolar
+  oscillations in a variety of cell shapes, recent experiments have
+  shown that when the cells are mechanically deformed into wide,
+  flattened out, irregular shapes, the spatial regularity of these
+  oscillations breaks down. We employ widely used stochastic and
+  deterministic models of Min-system to simulate cells with flattened
+  cell shapes.  The deterministic model predicts strong bipolar
+  oscillations, in contradiction with the experimentally observed
+  behavoir, while the stochastic model, which is based on the same
+  reaction-diffusion equations, does predict spatially irregular
+  oscillations as observed in experiment.  We further report
+  simulations of symmetric but flattened cell shapes, and find that it
+  is the flattening rather than the asymmetry of the cell shapes that
+  causes the irregular oscillation behavoir.
 \end{abstract}

### 2014-11-07 paper/paper-MinD.tex
changes to paper for page limits Tested everything on crystal.

--- 2014-11-05 paper/paper-MinD.tex
@@
 
-\keywords{\fixme{E. Coli | MinD | oscillation | stochastic | deterministic | simulation}}
+\keywords{MinD | \emph{Escherichia coli} | stochastic | deterministic }
 
-\abbreviations{\fixme{SAM, self-assembled monolayer; OTS,
-octadecyltrichlorosilane}}
+%% \abbreviations{SAM, self-assembled monolayer; OTS,
+%% octadecyltrichlorosilane}
 
-\dropcap{I}t is vital that during the process of bacterial cell division a cell
-avoid minicelling, or splitting into daughter cells with lopsided
-volumes.  Instrumental to this process in \emph{Escherichia coli} is a
-long FtsZ polymer chain that develops on the cell wall in the center
-region of the cell, helping dictate the plane of
-division~\cite{adams2009bacterial, lutkenhaus2007assembly}. Previous
-experimental studies have shown that the MinC protein, known to
-inhibit the FtZ polymer~\cite{shen2010examination}, exhibits regular
-pole to pole oscillatory behavior between both ends of the wild-type
-pill-shaped cell.  It thus has a higher time averaged concentration in
-the cell poles than in the center region, which aides in preventing
-the FtZ from developing in the wrong region.  The MinC is recruited to
-these poles by MinD, which itself interacts with another protein,
-MinE, in a system which exhibits pole-to-pole oscillatory
-behavoir~\cite{hu1999topological, fu2001mine, shapiro2009and,
-  yu1999ftsz, raskin1999rapid, meacci2005min, raskin1999minde}.
+\dropcap{I}t is vital that during the process of bacterial cell
+division a cell avoid minicelling, or splitting into daughter cells
+with lopsided volumes.  Instrumental to this process in
+\emph{Escherichia coli} is a long FtsZ polymer chain that develops on
+the cell wall in the center region of the cell, helping dictate the
+plane of division~\cite{adams2009bacterial,
+  lutkenhaus2007assembly}. Previous experimental studies have shown
+that the MinC protein, known to inhibit the FtZ
+polymer~\cite{shen2010examination}, exhibits regular pole to pole
+oscillatory behavior between both ends of the wild-type pill-shaped
+cell.  It thus has a higher time averaged concentration in the cell
+poles than in the center region, which aides in preventing the FtZ
+from developing in the wrong region.  The MinC is recruited to these
+poles by MinD, which itself interacts with another protein, MinE, in a
+system which exhibits pole-to-pole oscillatory
+behavoir~\cite{shapiro2009and, yu1999ftsz,
+  meacci2005min,huang2003dynamic,kerr2006division,mannik2009bacterial}.
+%% \cite{hu1999topological, fu2001mine, shapiro2009and,
+%%   yu1999ftsz, raskin1999rapid, meacci2005min, raskin1999minde}.
 
@@
 tube shapes~\cite{varma2008min}, in which the oscillations seem to
-seek out the extreme poles in the
-cell~\cite{juarez2010changes,corbin2002exploring}.  One conclusion of
-these studies has been that the MinD system robustly forms bipolar
+seek out the extreme poles in the cell.  One conclusion of these
+studies has been that the MinD system robustly forms bipolar
 oscillations regardless of variations in cellular shape.
@@
 cases than have been seen thus far.
-
-\fixme{look for easily cut citations.}
 
@@
 
+%% biology~\cite{lawson2013spatial, robb2014stochastic,
+%%   oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
 In this paper we use Huang's 2003 model~\cite{huang2003dynamic} in

### 2014-11-07 paper/paper-MinD.tex
changes with Jeff on abstract Tested everything on bennet.

@@
   regulate the process of cell division by identifying the center of
-  the cell.  While this system usually exhibits robust polar
-  oscillations in a variety of cell shapes, new experiments have shown
-  that when the cells are mechanically deformed into wide, flattened
-  out, irregular shapes, the spatial regularity of these oscillations
-  breaks down. Here we study widely used stochastic and deterministic
-  models of Min-system simulation within these new cell shapes.  We
-  find that the deterministic model is decidedly inadequate to
-  reproduce the experimentally observed behavoir, while the stochastic
-  model, based on the same differential equations, is able to do so
-  accurately.  We also find that it is the flattening rather than the
-  irregularity and asymmetry of the cell shape that causes the
-  irregular oscillation behavoir.
+  the cell.  While this system usually exhibits robust bipolar
+  oscillations in a variety of cell shapes, recent experiments have
+  shown that when the cells are mechanically deformed into wide,
+  flattened out, irregular shapes, the spatial regularity of these
+  oscillations breaks down. We employ widely used stochastic and
+  deterministic models of the Min system to simulate cells with flattened
+  shapes.  The deterministic model predicts strong bipolar
+  oscillations, in contradiction with the experimentally observed
+  behavoir, while the stochastic model, which is based on the same
+  reaction-diffusion equations, does predict spatially irregular
+  oscillations as observed in experiment.  We further report
+  simulations of symmetric but flattened cell shapes, and find that it
+  is the flattening rather than the asymmetry of the cell shapes that
+  causes the irregular oscillation behavoir.
 \end{abstract}

### 2014-11-07 paper/paper-MinD.tex
edits of conclusions Tested everything on bennet.

@@
 version of the model~\cite{huang2003dynamic} predicts behavior that
-contradicts experimental observations, namely robust and periodic
-bipolar oscillation in irregularly shaped cells, with a minor
-intermediate maximum appearing in shape \emph{B}.  Thus we conclude
-that this method is inconsistent with experiment, and cannot be relied
-upon for predictions of the behavior of the MinD system.  This is the
-most clear example of the inadequacy of the deterministic simulation
-method in reproducing experimental behavoir of the MinD system to
-date.  Until now the results of deterministic and stochastic
-simulation have largely coincided, with the stochastic method showing
-minor differences in behavoir when compared to deterministic
+contradicts experimental observations.  Specifically, the
+deterministic model predicts robust and periodic bipolar oscillation
+in irregularly shaped cells, with a minor intermediate maximum
+appearing in shape \emph{B}.  Thus we conclude that this method is
+inconsistent with experiment, and cannot be relied upon for
+predictions of the behavior of the MinD system.  This is the most
+clear example of the inadequacy of the deterministic simulation method
+in reproducing experimental behavoir of the MinD system to date.
+Until now the results of deterministic and stochastic simulation have
+largely coincided, with the stochastic method showing minor
+differences in behavoir when compared to deterministic
 models~\cite{kerr2006division, fange2006noise, huang2004min,
@@
 the temporal regularity of oscillations is only moderately affected by
-irregularity in the shape of flattened cells.  Thus we conclude
-that it is the flattening of the cells rather than their irregular
-shape that primarily causes the spatial irregularity of maxima which
-is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.
+irregularity in the shape of flattened cells.  Thus we conclude that
+it is the flattening of the cells rather than their irregular shape
+that primarily causes the disruption of regular bipolar oscillation
+which is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.
 

### 2014-11-07 paper/paper-MinD.tex
add SI descriptions to the paper Tested everything on bennet.

@@
 
+\section*{Supplementary Information 1}
+
+Movie that shows the evolution of MinD density over a 250 second
+interval in a wild-type, pill-shaped cell.  There is one frame for
+every half second of simulation time. Above are results from the
+stochastic model and below are results from the deterministic model.
+The density shown is integrated over the direction normal to the
+screen, so that the data is shown in molecules/$\micron^2$.
+
+\section*{Supplementary Information 2}
+
+Movie that shows the evolution of MinD density over a 350 second
+interval in the shape A cell.  There is one frame for every half
+second of simulation time. Above are results from the stochastic model
+and below are results from the deterministic model.  The density shown
+is integrated over the direction normal to the screen, so that the
+data is shown in molecules/$\micron^2$.
+
+\section*{Supplementary Information 3}
+
+Movie that shows the evolution of MinD density over a 350 second
+interval in the shape B cell.  There is one frame for every half
+second of simulation time. Above are results from the stochastic model
+and below are results from the deterministic model.  The density shown
+is integrated over the direction normal to the screen, so that the
+data is shown in molecules/$\micron^2$.
+
+\section*{Supplementary Information 4}
+
+Movie that shows the evolution of MinD density over a 350 second
+interval in the stadium A cell.  There is one frame for every half
+second of simulation time. Above are results from the stochastic model
+and below are results from the deterministic model.  The density shown
+is integrated over the direction normal to the screen, so that the
+data is shown in molecules/$\micron^2$.
+
+\section*{Supplementary Information 5}
+Movie that shows the evolution of MinD density over a 350 second
+interval in the stadium B cell.  There is one frame for every half
+second of simulation time. Above are results from the stochastic model
+and below are results from the deterministic model.  The density shown
+is integrated over the direction normal to the screen, so that the
+data is shown in molecules/$\micron^2$.
+
 \end{document}

### 2014-11-08 paper/paper-MinD.tex
final changes before we submitted Tested everything on bennet.

@@
 \usepackage{amssymb,amsfonts,amsmath}
+\usepackage{cite}
 
@@
 
-\title{Robustness of MinD oscillation in \emph{Escherichia coli} with
-  diverse cell shapes}
+\title{Theoretical prediction of disrupted Min oscillation in
+  flattened \emph{Escherichia coli}}
 
@@
   oscillations, in contradiction with the experimentally observed
-  behavoir, while the stochastic model, which is based on the same
+  behavior, while the stochastic model, which is based on the same
   reaction-diffusion equations, does predict spatially irregular
@@
   is the flattening rather than the asymmetry of the cell shapes that
-  causes the irregular oscillation behavoir.
+  causes the irregular oscillation behavior.
 \end{abstract}
@@
   lutkenhaus2007assembly}. Previous experimental studies have shown
-that the MinC protein, known to inhibit the FtZ
+that the MinC protein, known to inhibit the FtsZ
 polymer~\cite{shen2010examination}, exhibits regular pole to pole
@@
 cell.  It thus has a higher time averaged concentration in the cell
-poles than in the center region, which aides in preventing the FtZ
+poles than in the center region, which aides in preventing the FtsZ
 from developing in the wrong region.  The MinC is recruited to these
@@
 system which exhibits pole-to-pole oscillatory
-behavoir~\cite{shapiro2009and, yu1999ftsz,
+behavior~\cite{shapiro2009and, yu1999ftsz,
   meacci2005min,huang2003dynamic,kerr2006division,mannik2009bacterial}.
@@
 cells are irregular, both temporally and spatially. Seen with
-flourescent microscopy, the MinD maximize in multiple locations within
+fluorescent microscopy, the MinD maximize in multiple locations within
 the cell, in a seemingly random sequence. These experiments allow for
@@
 recruited to the membrane by MinD that is already clustered there
-(following observed non-linear attachement of MinD on the cell
+(following observed non-linear attachment of MinD on the cell
 membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
@@
 both deterministic and stochastic variants to study flattened cells
-similar to those observed by Mannik~\cite{mannik2009bacterial}.
+similar to those observed by Mannik \emph{et
+  al.}~\cite{mannik2009bacterial}.
 
@@
 MinE will attach to the wall bound MinD:ATP complex and after a time
-will activate ATP hydrolosis.  This breaks up the complex, releasing
+will activate ATP hydrolysis.  This breaks up the complex, releasing
 MinE, phosphate, and MinD:ADP back into the cytoplasm.  The MinD:ADP
@@
 is membrane bound density (proteins$/\micron^{2}$), $\mathcal{D}_D$ and
-$\mathcal{D}_{E}$ are the diffusions constants for MinD and MinE,
+$\mathcal{D}_{E}$ are the diffusion constants for MinD and MinE,
 respectively, $k_D^{\textrm{ADP $\rightarrow$ ATP}}$ is the rate of
 conversion from MinD:ADP to the MinD:ATP complex, $k_D$ is the rate of
-MinD:ATP attachement to the membrane when no protein is already
+MinD:ATP attachment to the membrane when no protein is already
 attached there, $k_{dD}$ is the increase of this rate when MinD:ATP is
-present on the membrane, $k_{de}$ is the rate of hydrolisis of the
+present on the membrane, $k_{de}$ is the rate of hydrolysis of the
 MinD:MinE:ATP complex, $k_E$ is the rate of cytoplasmic MinE binding
@@
 has units of $\micron^{-1}$ and is zero everywhere except at the wall.
-Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} are only relevent
+Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} are only relevant
 at the membrane because the membrane-bound density values have no
@@
 are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We perform
-simulations with a 3D grid in cartesian coordinates that has a grid
+simulations with a 3D grid in Cartesian coordinates that has a grid
 spacing of .05\micron.
@@
 in several cell shapes and sizes.  Here we present a selection of
-these, beginning with naturally occuring pill-shaped cells, followed
+these, beginning with naturally occurring pill-shaped cells, followed
 by a number of flattened out shapes which reflect the experiments of
@@
 In this paper we focus on four specific flattened cell shapes.  Two of
-these shapes replicate those published by Mannik, and the other two
-are `stadium' shapes that respectively have the same aspect ratio,
-thickness, and volume as the two Mannik shapes.  Viewed from the top
-down, these stadium shapes appear as rectangles with semi-circular end
-caps on the long axis ends.
+these shapes replicate those published by Mannik \emph{et al.}, and
+the other two are `stadium' shapes that respectively have the same
+aspect ratio, thickness, and volume as the two cell shapes
+experimentally observed by Mannik \emph{et
+  al.}~\cite{mannik2012robustness}.  Viewed from the top down, these
+stadium shapes appear as rectangles with semi-circular end caps on the
+long axis ends.
 
@@
 on a steady state solution of a $2\micron$ half wavelength.  Cells
-with dimensions longer than this show spontaneous oscillatory behavoir
+with dimensions longer than this show spontaneous oscillatory behavior
 in this direction, while cells that are shorter relax into a
@@
 
-\section{Naturally Occuring Pill Shaped Cells}
+\section{Naturally Occurring Pill Shaped Cells}
 
@@
     two opposite polar regions of the pill-shaped cell, shown against
-    the correlation time.  Data for both the the determinisitic and
+    the correlation time.  Data for both the the deterministic and
     stochastic models are shown.  The stochastic model shows an
@@
 
-We begin with the naturally occuring pill cell shape.  We piece this
-shape together as a cylinder with hemispherical endcaps.  This shape
+We begin with the naturally occurring pill cell shape.  We piece this
+shape together as a cylinder with hemispherical end caps.  This shape
 follows the early simulations of Huang \emph{et al.} but differs in
@@
 We have `smeared out' the stochastic concentrations in a manner meant
-to reproduce the images shown by diffraction limited flourescence
-microscopy.  We do so using the two dimensional gaussian approximation
+to reproduce the images shown by diffraction limited fluorescence
+microscopy.  We do so using the two dimensional Gaussian approximation
 developed by Zhang \emph{et al.}~\cite{zhang2007gaussian}.  In this
@@
 as a green band on the walls from 0 seconds to 4 seconds (and later
-from 15 to 23 seconds).  The appearence of these rings in the
-deterministic model along side their less obvious appearence in the
+from 15 to 23 seconds).  The appearance of these rings in the
+deterministic model along side their less obvious appearance in the
 stochastic model highlights an advantage of the deterministic model:
@@
 case of the stochastic model the pill exhibits coherence times of
-about 8 periods and in the case of the determinisitic model oscillate
+about 8 periods and in the case of the deterministic model oscillate
 indefinitely with complete coherence, indicating that its behavior is
@@
     useful comparison due to its shorter oscillation period.  The top
-    row shows plots published by Mannik of the MinD maxima behavoir
+    row shows plots published by Mannik \emph{et al.} of the MinD maxima behavior
     and the bottom two rows show our simulations using the stochastic
@@
     coherence time of 246 seconds, so that it takes roughly 4.6 periods
-    for the behavoir to decohere.  For the stadium \emph{A}, the same
+    for the behavior to decohere.  For the stadium \emph{A}, the same
     model shows an oscillation period of 51 seconds and coherence time of
-    323 seconds, so that it takes roughly 6.3 periods for the behavoir
+    323 seconds, so that it takes roughly 6.3 periods for the behavior
     to decohere.}
@@
 created to replicate those shapes observed experimentally by
-Mannik~\cite{mannik2012robustness} (shape~\emph{A} and
+Mannik \emph{et al.}~\cite{mannik2012robustness} (shape~\emph{A} and
 shape~\emph{B}), and for comparison two symmetrical stadium shapes
@@
 We note that shape \emph{B} is more irregular than shape \emph{A}, and
-in particular features a prominant region of concavity on its
+in particular features a prominent region of concavity on its
 left-hand side.  For each of these shapes (in addition to the
@@
 From each of these flattened simulations, we have chosen a typical 350
-second segment to compare with the puplished results of
-Mannik~\cite{mannik2012robustness}, exemplified in arrow plots in
+second segment to compare with the published results of
+Mannik \emph{et al.}~\cite{mannik2012robustness}, exemplified in arrow plots in
 which the arrow heads show the location of sequential MinD maxima
@@
 arrows between successive maxima in space and time, we plot as a
-colored background the density of MinD protiens averaged over the same
+colored background the density of MinD proteins averaged over the same
 time period.  We note that we have manually verified that our
@@
 maxima, although there are locations on the edges of the cells where
-experiment shows maxima occuring that we never see in our simulations,
+experiment shows maxima occurring that we never see in our simulations,
 suggesting that the model does not precisely reflect the experiment.
@@
 appear to have maxima location irregularity that is qualitatively
-similar to our Mannik shapes and to experiment.
+similar to our irregular shapes and to experiment.
 
@@
 experimentally observed behavior.  Although in the movies the stadiums
-appear to display, on average over long time scales, a more regular
-bipolar oscillation than the irregular mannik shapes, the limited time
-range of the arrow plots (350 seconds) is inadequate when studying
-this difference in behavoir.  We therefore return to the correlation
-function between the number of proteins in a segment at the top of the
-cell and the number of proteins in a segment at the bottom of the
-cell.  Fig.~\ref{fig:corr-pancake-A} shows this plot for shape
-\emph{A} and stadium \emph{A}.  E. Coli cell doubling times vary
+appear to display, on average over long time scales, a somewhat more
+regular oscillation than appears in the irregular shapes \emph{A} and
+\emph{B}, the limited time range of the arrow plots (350 seconds) is
+inadequate to make this comparison.  We therefore return to the
+correlation function between the number of proteins in a segment at
+the top of the cell and the number of proteins in a segment at the
+bottom of the cell.  Fig.~\ref{fig:corr-pancake-A} shows this plot for
+shape \emph{A} and stadium \emph{A}.  E. Coli cell doubling times vary
 widely depending on environmental conditions, but will often be
 between 20 minutes to 100 minutes~\cite{pierucci1972chromosome}, while
-flourescent microscopy experiments have shown that the FtsZ ring
+fluorescent microscopy experiments have shown that the FtsZ ring
 builds itself with a half life of roughly 30
 seconds~\cite{stricker2002rapid}.  Here we plot correlations of
-correlation times up to 500 seconds, a biologically relevent
+correlation times up to 500 seconds, a biologically relevant
 timescale.
@@
 their cells, and have been normalized with the same normalization
-factor, so that they can be directly compared against eachother.  The
+factor, so that they can be directly compared against each other.  The
 stochastic simulation of shape \emph{A} has a coherence time of 4.6
@@
 clear example of the inadequacy of the deterministic simulation method
-in reproducing experimental behavoir of the MinD system to date.
+in reproducing experimental behavior of the MinD system to date.
 Until now the results of deterministic and stochastic simulation have
 largely coincided, with the stochastic method showing minor
-differences in behavoir when compared to deterministic
+differences in behavior when compared to deterministic
 models~\cite{kerr2006division, fange2006noise, huang2004min,
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{pnas2011}
 \bibliography{paper-MinD}

### 2015-01-13 paper/paper-MinD.tex
start draft for next version of paper for PLOS computational biology Tested everything on bennet.

@@
 
+\fixme{THE FOLLOWING NEEDS much CHANGING.  Many reaction-diffusion
+  models have been proposed... There are several newer models that
+  incorporate new experimental results.}
+%
 A number of models of the MinD protein system have been developed,
@@
 large role.  To treat this, there have been a number of variations of
-the Huang 2003 model that stochastically simulate the same
+the Huang 2003 model that stochastically simulate the same \fixme{similar}
 reaction-diffusion equations~\cite{fange2006noise, kerr2006division}.
@@
 similar to those observed by Mannik \emph{et
-  al.}~\cite{mannik2009bacterial}.
+  al.}~\cite{mannik2009bacterial}.  \fixme{Some weak
+  justification... it has been widely used.}
 
@@
 night'' effect, as recruitment leads to clusters of MinD forming on
-the wall and then subsequently dissipating.  This naturally leads to
-irregularity in the temporal periodicity of the system, which we
-quantify by examining the temporal correlation function of the total
-MinD found in two opposite polar regions.
+the wall and then subsequently dissipating.  \fixme{Talk about
+  membrane diffusion blurring out the starry night.}  This naturally
+leads to irregularity in the temporal periodicity of the system, which
+we quantify by examining the temporal correlation function of the
+total MinD found in two opposite polar regions.
 %
@@
   kerr2006division} has considerable predictive power beyond the
-standard wild-type cell.
+standard wild-type cell.  \fixme{Discuss which of these are likely to
+  map to more recent models.}
 

### 2015-01-13 paper/plos.tex
start draft for next version of paper for PLOS computational biology Tested everything on bennet.

% Template for PLoS
% Version 3.0 December 2014
%
% To compile to pdf, run:
% latex plos.template
% bibtex plos.template
% latex plos.template
% latex plos.template
% dvipdf plos.template
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file and leave only
% the final text of your manuscript.
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% See http://www.plosone.org/static/figureGuidelines for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - tabs/spacing/line breaks within cells to alter layout or alignment
% - vertically-merged cells (no tabular environments within tabular environments, do not use \multirow)
% - colors, shading, or graphic objects
% See http://www.plosone.org/static/figureGuidelines#tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://www.plosone.org/static/latexGuidelines
%
% Please be sure to include all portions of an equation in the math environment.
%
% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% fixltx2e package for \textsubscript
\usepackage{fixltx2e}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% rotating package for sideways tables
\usepackage{rotating}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2009}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Leave date blank
\date{}

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\lhead{\includegraphics[natwidth=1.3in,natheight=0.4in]{PLOSlogo.png}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

\begin{document}
\vspace*{0.35in}

% Title must be 150 characters or less
\begin{flushleft}
{\Large
\textbf\newline{Theoretical prediction of disrupted Min oscillation in
  flattened \emph{Escherichia coli}}
}
\newline
% Insert Author names, affiliations and corresponding author email.
\\
Jeff B. Schulte\textsuperscript{1,*},
Rene W. Zeto\textsuperscript{1},
David Roundy\textsuperscript{1}
\\
\bf{1} Dept. of Physics/Oregon State University/Corvallis, Oregon, USA
\\

% Insert additional author notes using the symbols described below. Insert symbol callouts after author names as necessary.
% 
% Remove or comment out the author notes below if they aren't used.
%

* E-mail: Corresponding schuljef@physics.oregonstate.edu
\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
  The dynamics of the Min-protein system help \emph{Escherichia coli}
  regulate the process of cell division by identifying the center of
  the cell.  While this system usually exhibits robust bipolar
  oscillations in a variety of cell shapes, recent experiments have
  shown that when the cells are mechanically deformed into wide,
  flattened out, irregular shapes, the spatial regularity of these
  oscillations breaks down. We employ widely used stochastic and
  deterministic models of the Min system to simulate cells with flattened
  shapes.  The deterministic model predicts strong bipolar
  oscillations, in contradiction with the experimentally observed
  behavior, while the stochastic model, which is based on the same
  reaction-diffusion equations, does predict spatially irregular
  oscillations as observed in experiment.  We further report
  simulations of symmetric but flattened cell shapes, and find that it
  is the flattening rather than the asymmetry of the cell shapes that
  causes the irregular oscillation behavior.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author Summary}
  When an E. Coli cell divides it must split into two relatively equal
  volumes in order to survive.  One mechanism that aids in this
  process is a system of proteins that oscillate between cell ends and
  help the original cell divide along its center.  A recent
  experiment found that by drastically deforming these cells this
  oscillation can be disrupted.  We examine these oscillations in
  similarly deformed cells computationally, using two widely used
  simulation models, and find good agreement using one of them.  The
  other model fails in a manner far more dramatic than has been
  previously observed.  Furthermore, we find that the effect observed
  experimentally in asymmetric and flattened cells is primarily a
  result of the flattening, not the asymmetry.

\linenumbers

\section*{Introduction}
Lorem ipsum dolor sit~\cite{huang2003dynamic} amet, consectetur adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed sem. Nullam Eq.~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{mannik2009bacterial} Nunc convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
\begin{equation}\label{eq:schemeP}
D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}},
D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
\end{equation}

% You may title this section "Methods" or "Models". 
% "Models" is not a valid title for PLoS ONE authors. However, PLoS ONE
% authors may use "Analysis" 
\section*{Materials and Methods}
\subsection*{Etiam eget sapien nibh.}

Nulla mi mi, Figure~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\begin{figure}[h]
\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}
Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

\begin{enumerate}
\item{react}
\item{diffuse free particles}
\item{increment time by dt and go to 1}
\end{enumerate}

% Results and Discussion can be combined.
\section*{Results}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\caption{
{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
\begin{tabular}{|l|l|l|l|l|l|l|l|}
\hline
\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
\end{tabular}
\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
\end{flushleft}
\label{table1}
\end{adjustwidth}
\end{table}

\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}

Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit. Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat.

Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.

\subsection*{Sed ac quam id nisi malesuada congue.}

Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
\subsection*{Subsection 1}
Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\subsection*{Subsection 2}
\paragraph{3rd Level Heading.} Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\section*{Discussion}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent faucibus semper libero.

\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}

CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque. Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.

Sed non aliquet felis. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Mauris commodo justo ac dui pretium imperdiet. Sed suscipit iaculis mi at feugiat. Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna. Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl. Ut ornare mauris tellus, vel dapibus arcu suscipit sed. Nam condimentum sem eget mollis euismod. Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex. Nunc est dui, sodales sed mauris nec, auctor sagittis leo. Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor. For more information, see \nameref{S1_Text}.

\section*{Supporting Information}

% Include only the SI item label in the subsection heading. Use the \nameref{label} command to cite SI items in the text.
\subsection*{S1 Video}
\label{S1_Video}
{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Text}
\label{S1_Text}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Fig}
\label{S1_Fig}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

\subsection*{S1 Table}
\label{S1_Table}
{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida. Etiam eget sapien nibh. Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula. Curabitur fringilla pulvinar lectus consectetur pellentesque.

% Do NOT remove this, even if you are not including acknowledgments.
\section*{Acknowledgments}
Cras egestas velit mauris, eu mollis turpis pellentesque sit amet. Interdum et malesuada fames ac ante ipsum primis in faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada congue. Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.

\nolinenumbers

% Compile your BiBTeX database using our plos2009.bst
% style file and paste the contents of your .bbl file
% here.

\bibliography{paper-MinD}

\end{document}

### 2015-01-14 paper/plos.tex
moved text over into plos.tex, modified intro to discuss newer models briefly, updated bib Tested everything on crystal.

@@
 % amsmath and amssymb packages, useful for mathematical formulas and symbols
-\usepackage{amsmath,amssymb}
+\usepackage{amsmath,amssymb,amsfonts}
 
@@
 \usepackage{rotating}
+
+%Author's added to template:
+\usepackage{color}
+\newcommand\micron{\ensuremath{\mu\text{m}}}
+\newcommand{\red}[1]{{\bf \color{red} #1}}
+\newcommand{\fixme}[1]{\red{[#1]}}
 
@@
 \section*{Introduction}
-Lorem ipsum dolor sit~\cite{huang2003dynamic} amet, consectetur adipiscing elit.
-Curabitur eget porta erat.
-Morbi consectetur est vel gravida pretium.
-Suspendisse ut dui eu ante cursus gravida non sed sem.
-Nullam Eq.~(\ref{eq:schemeP}) sapien tellus, commodo id velit id, eleifend volutpat quam.
-Phasellus mauris velit, dapibus finibus elementum vel, pulvinar non tellus.
-Nunc pellentesque pretium diam, quis maximus dolor faucibus id.~\cite{mannik2009bacterial} Nunc convallis sodales ante, ut ullamcorper est egestas vitae.
-Nam sit amet enim ultrices, ultrices elit pulvinar, volutpat risus.
-\begin{equation}\label{eq:schemeP}
-D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}},
-D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
-\end{equation}
+It is vital that during the process of bacterial cell
+division a cell avoid minicelling, or splitting into daughter cells
+with lopsided volumes.  Instrumental to this process in
+\emph{Escherichia coli} is a long FtsZ polymer chain that develops on
+the cell wall in the center region of the cell, helping dictate the
+plane of division~\cite{adams2009bacterial,
+  lutkenhaus2007assembly}. Previous experimental studies have shown
+that the MinC protein, known to inhibit the FtsZ
+polymer~\cite{shen2010examination}, exhibits regular pole to pole
+oscillatory behavior between both ends of the wild-type pill-shaped
+cell.  It thus has a higher time averaged concentration in the cell
+poles than in the center region, which aides in preventing the FtsZ
+from developing in the wrong region.  The MinC is recruited to these
+poles by MinD, which itself interacts with another protein, MinE, in a
+system which exhibits pole-to-pole oscillatory
+behavior~\cite{shapiro2009and, yu1999ftsz,
+  meacci2005min,huang2003dynamic,kerr2006division,mannik2009bacterial}.
+%% \cite{hu1999topological, fu2001mine, shapiro2009and,
+%%   yu1999ftsz, raskin1999rapid, meacci2005min, raskin1999minde}.
+
+Previous experimental studies have shown that the MinD protein system
+is capable of exhibiting oscillations in round
+shapes~\cite{fange2006noise} as well as in connected three pronged
+tube shapes~\cite{varma2008min}, in which the oscillations seem to
+seek out the extreme poles in the cell.  One conclusion of these
+studies has been that the MinD system robustly forms bipolar
+oscillations regardless of variations in cellular shape.
+
+However, Mannik \emph{et al.} have recently shown that there are
+limitations to this robust capability to
+oscillate~\cite{mannik2010bacteria, mannik2009bacterial}. They have
+experimentally forced \emph{E. coli} cells into microfabricated
+silicon channels of $0.25\micron$ thickness. Upon entering the
+channels, the cells undergo a mechanical deformation in which they
+both widen and lengthen within the plane of the channel.  This
+deformation results in very wide (they can reach widths of over
+$5\micron$) flattened cells that when viewed from the top down have
+irregular and asymmetric shapes.  While these cells are still able to
+divide into surprisingly equal volumes, the MinD oscillations in these
+cells are irregular, both temporally and spatially. Seen with
+fluorescent microscopy, the MinD maximize in multiple locations within
+the cell, in a seemingly random sequence. These experiments allow for
+an opportunity to test MinD simulation models against more extreme
+cases than have been seen thus far.
+
+\fixme{THE FOLLOWING NEEDS much CHANGING.  Many reaction-diffusion
+  models have been proposed... There are several newer models that
+  incorporate new experimental results.}
+%
+A number of models of the MinD protein system have been developed that
+accurately describe its basic oscillatory nature.
+%
+Early models involved free proteins that affect each others' rates of
+diffusion and membrane attachment, but do not combine into compound
+states~\cite{meinhardt2001pattern}.  In 2003 Huang improved upon this
+approach with a simple and very successful simulation model based on
+MinD-MinE combination, ATPase hydrolysis, and MinD membrane attachment
+that exhibits accurate MinD oscillations in cylindrical
+cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is
+recruited to the membrane by MinD that is already clustered there
+(following observed non-linear attachment of MinD on the cell
+membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
+once attached.
+%
+Some of these models
+\cite{fange2006noise,bonny2013membrane,halatek2012highly} modify the
+Huang model cited above to more accurately treat experimental findings
+published after his 2003 paper \cite{Meacci2007,Loose2011}. They
+introduce diffusion along the membrane that is two to three orders of
+magnitude lower than that within the cytoplasm, revise the process of
+MinD recruitment to the membrane, and change some of the constants
+used in the model. The Bonny 2013 model assumes an instantaneous
+nucleotide exchange rate at one point in the reaction cycle, and
+relies upon MinE’s ability to independently remain attached to the
+membrane in a manner that allows it to react with a number of MinD
+proteins before disassociating.
+%
+
+%%  A number of studies have used an approach similar in
+%% that they do not rely on the ability of MinD to move along the walls
+%% and cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
+%%   drew2005polymerization, fange2006noise, kerr2006division}, while
+%% studies have been made as well of models which rely on MinD mobility
+%% and attraction on the cell membrane~\cite{kruse2002dynamic,
+%%   howard2005cellular}.
+
+There are only on the order of 1000 MinD proteins in a given cell,
+which means that stochastic fluctuation can be expected to play a
+large role.  To treat this, there have been a number of variations of
+the Huang 2003 model that stochastically simulate the same \fixme{similar}
+reaction-diffusion equations~\cite{fange2006noise, kerr2006division}.
+These studies largely confirm the results of Huang's deterministic
+model when applied to the wild-type, pill-shaped phenotype.  However,
+the stochastic models are slightly more successful in predicting
+experimentally observed oscillations in round cell
+phenotypes~\cite{fange2006noise, huang2004min}, and they enable
+prediction of fluctuations in the predicted
+behavior~\cite{kruse2007experimentalist}.  Both deterministic and
+stochastic models are widely used throughout systems
+biology~\cite{lawson2013spatial, robb2014stochastic,
+  oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
+have unique advantages and limitations.  The deterministic approach
+has an advantage in providing a simple prediction of average behavior,
+while the stochastic approach enables prediction of fluctuations from
+that mean, and reduces sensitivity to initial conditions.
+
+%% biology~\cite{lawson2013spatial, robb2014stochastic,
+%%   oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
+In this paper we use Huang's 2003 model~\cite{huang2003dynamic} in
+both deterministic and stochastic variants to study flattened cells
+similar to those observed by Mannik \emph{et
+  al.}~\cite{mannik2009bacterial}.  \fixme{Some weak
+  justification... it has been widely used.}
+
+\begin{figure}
+  \includegraphics[width=8.7cm]{reactions}
+  \caption{Reactions included in the model of Huang \emph{et
+      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
+\end{figure}
+
+%% Lorem ipsum dolor sit~\cite{huang2003dynamic} amet, consectetur
+%% adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel
+%% gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed
+%% sem. Nullam Eq.~(\ref{eq:schemeP}) sapien tellus, commodo id velit id,
+%% eleifend volutpat quam. Phasellus mauris velit, dapibus finibus
+%% elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam,
+%% quis maximus dolor faucibus id.~\cite{mannik2009bacterial} Nunc
+%% convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet
+%% enim ultrices, ultrices elit pulvinar, volutpat risus.
+%% \begin{equation}\label{eq:schemeP}
+%% D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}},
+%% D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
+%% \end{equation}
 
@@
 \section*{Materials and Methods}
-\subsection*{Etiam eget sapien nibh.}
+\subsection*{Model and Cell Shapes}
+\label{sec:model-method-shapes}
+We implement the reaction-diffusion model of Huang \emph{et
+  al.}~\cite{huang2003dynamic}.  Figure~\ref{fig:reactions} shows the
+reaction process.  The cytoplasmic MinD:ADP complex undergoes
+nucleotide exchange and is changed into the MinD:ATP complex.  This
+will naturally diffuse and attach to the cell membrane.  A cytoplasmic
+MinE will attach to the wall bound MinD:ATP complex and after a time
+will activate ATP hydrolysis.  This breaks up the complex, releasing
+MinE, phosphate, and MinD:ADP back into the cytoplasm.  The MinD:ADP
+will undergo nucleotide exchange and begin again the cyclic process.
+The model is defined by a set of five reaction-diffusion equations:
 
-Nulla mi mi, Figure~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+\begin{multline}
+  \frac{\partial \rho_{D:ADP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ADP}-k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
+  +\delta(d_w)k_{de}\sigma_{DE},\hspace{3.4cm}
+\end{multline}
+\begin{multline}
+  \frac{\partial \rho_{D:ATP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ATP}+k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
+  -\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
+\end{multline}
+\begin{multline}
+  \frac{\partial \rho_E}{\partial t} = \mathcal{D}_E\nabla^2\rho_E+\delta(d_w)k_{de}\sigma_{DE}
+  -\delta(d_w)k_E \sigma_D \rho_E
+\end{multline}
+\begin{multline}
+  \frac{\partial \sigma_D}{\partial t} = -k_E\sigma_D\rho_E
+  +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
+  \label{eq:d-on-wall}
+\end{multline}
+\begin{multline}
+  \frac{\partial \sigma_{DE}}{\partial t} = -k_{de}\sigma_{DE}+k_E\sigma_D\rho_E\hspace{3cm}
+  \label{eq:FifthPDE}
+\end{multline}
+where $\rho$ is cytoplasmic protein density (proteins$/\micron^{3}$), $\sigma$
+is membrane bound density (proteins$/\micron^{2}$), $\mathcal{D}_D$ and
+$\mathcal{D}_{E}$ are the diffusion constants for MinD and MinE,
+respectively, $k_D^{\textrm{ADP $\rightarrow$ ATP}}$ is the rate of
+conversion from MinD:ADP to the MinD:ATP complex, $k_D$ is the rate of
+MinD:ATP attachment to the membrane when no protein is already
+attached there, $k_{dD}$ is the increase of this rate when MinD:ATP is
+present on the membrane, $k_{de}$ is the rate of hydrolysis of the
+MinD:MinE:ATP complex, $k_E$ is the rate of cytoplasmic MinE binding
+to membrane bound MinD:ATP complex, and $d_w$ is the distance from the
+point in space to the closest wall.  The Dirac delta function
+$\delta(d_w)$, which we need to describe the location of the membrane,
+has units of $\micron^{-1}$ and is zero everywhere except at the wall.
+Equations \ref{eq:d-on-wall} and \ref{eq:FifthPDE} are only relevant
+at the membrane because the membrane-bound density values have no
+meaning in the cytoplasm.
 
-\begin{figure}[h]
-\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}
-Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
-\label{fig1}
+Our diffusion and reaction rates are shown below.  We are interested
+primarily in the effect of cellular size and shape on the protein
+oscillations, so we follow Huang\cite{huang2003dynamic} and do not
+deviate from the wild-type values used in the cited work.
+
+\begin{gather*}
+  \mathcal{D}_D = \mathcal{D}_{E} = 2.5\micron^2/\text{sec}\\
+  k_D^{\textrm{ADP $\rightarrow$ ATP}} = 1/\textrm{sec,  }
+  k_D = 0.025 \micron /\textrm{sec}\\
+  k_{dD} = 0.0015 \micron^3/ \textrm{sec,  }
+  k_{de} = 0.7/\textrm{sec}\\
+  k_E = 0.093 \micron^3 /\textrm{sec}.
+\end{gather*}
+
+Huang's simulations use total MinD and MinE concentrations of
+$1,000/\micron$ and $350/\micron$, respectively, in a cylindrical cell
+of radius $0.5\micron$, and in our (non-cylindrical) cells we use the
+same number of proteins per unit volume.  These concentration values
+are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We perform
+simulations with a 3D grid in Cartesian coordinates that has a grid
+spacing of .05\micron.
+
+We have performed both a numerical, deterministic model simulation
+that is spatially and temporally discrete, and a stochastic simulation
+that is spatially discrete but continuous in time.  Our stochastic
+model follows the work of Kraus~\cite{kraus1996crosstalk} which in
+turn follows a method introduced by
+Gillespie~\cite{gillespie1977exact}.
+
+We mean to investigate the geometric limits of the Min system
+oscillations as observed by Mannik \emph{et
+  al.}~\cite{mannik2012robustness}, so we have modeled the Min system
+in several cell shapes and sizes.  Here we present a selection of
+these, beginning with naturally occurring pill-shaped cells, followed
+by a number of flattened out shapes which reflect the experiments of
+Mannik \emph{et al.}, in which bacteria are confined within a thin
+slit of height $0.25\micron$ ~\cite{mannik2012robustness}.  Viewed
+from the top down the cells have the shapes described below and viewed
+from the side they have at their edges a semicircular protrusion (one
+may imagine the shape of a pancake).
+%
+In this paper we focus on four specific flattened cell shapes.  Two of
+these shapes replicate those published by Mannik \emph{et al.}, and
+the other two are `stadium' shapes that respectively have the same
+aspect ratio, thickness, and volume as the two cell shapes
+experimentally observed by Mannik \emph{et
+  al.}~\cite{mannik2012robustness}.  Viewed from the top down, these
+stadium shapes appear as rectangles with semi-circular end caps on the
+long axis ends.
+
+\begin{figure*}
+  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
+  \begin{center}
+    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
+    \vspace{-1.5em}
+    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+    \vspace{-1.5em}
+  \end{center}
+  \caption{Images of the concentration of each protein species in a
+    natural pill-shaped bacterium at one-second time intervals. The
+    upper plots shows results from the deterministic model and the
+    lower shows results from the stochastic model.  The order of
+    frames is such that individual MinD proteins begin at the bottom
+    of the plot (in the MinD:ATP state in the cytoplasm), and progress
+    upward until they reach the MinE:MinD:ATP membrane-bound complex.
+    At that point, they will spontaneously dissociate into cytoplasmic
+    MinE (the top row) and the starting state of cytoplasmic
+    MinD:ADP.}.
+  \label{image-p}
+\end{figure*}
+
+Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
+stability analysis on a cylindrical model which shows an upper limit
+on a steady state solution of a $2\micron$ half wavelength.  Cells
+with dimensions longer than this show spontaneous oscillatory behavior
+in this direction, while cells that are shorter relax into a
+motionless steady state.  We have similarly performed a linear
+stability analysis on an infinite slab with a thickness equal to that
+of our flattened cells ($0.25\micron$) and have found that an
+equivalent stability limit for half wavelength is $2.13\micron$. As
+expected, when decreasing the lengths and widths of our simulated
+flattened cells so that the longest distance across the cell is less
+than this length, the cells stop exhibiting any oscillatory behavior.
+The deterministic model relaxes into a motionless state and the
+stochastic model exhibits random fluctuations without spatial
+oscillations.
+
+%% Nulla mi mi, Figure~\ref{fig1} venenatis sed ipsum varius, volutpat
+%% euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem
+%% et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur
+%% adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id
+%% massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce
+%% fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel
+%% sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id,
+%% cursus neque. Praesent faucibus semper libero.
+
+%% \begin{figure}[h]
+%% \caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis
+%%     sed ipsum varius, volutpat euismod diam.}  Figure Caption Proin
+%%   rutrum vel massa non gravida. Quisque tempor sem et dignissim
+%%   rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing
+%%   elit.}
+%% \label{fig1}
+%% \end{figure}
+
+%% \begin{enumerate}
+%% \item{react}
+%% \item{diffuse free particles}
+%% \item{increment time by dt and go to 1}
+%% \end{enumerate}
+
+% Results and Discussion can be combined.
+\section*{Results and Discussion}
+\subsection*{Naturally Occurring Pill Shaped Cells}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
+  \end{center}
+  \caption{Temporal correlation function of the total MinD found in
+    two opposite polar regions of the pill-shaped cell, shown against
+    the correlation time.  Data for both the the deterministic and
+    stochastic models are shown.  The stochastic model shows an
+    oscillation period of 39.5 seconds and coherence time of 307 seconds.
+    The correlation functions are scaled to have the same initial
+    value.}
+  \label{corr-pill}
 \end{figure}
 
-\begin{enumerate}
-\item{react}
-\item{diffuse free particles}
-\item{increment time by dt and go to 1}
-\end{enumerate}
+We begin with the naturally occurring pill cell shape.  We piece this
+shape together as a cylinder with hemispherical end caps.  This shape
+follows the early simulations of Huang \emph{et al.} but differs in
+that we have added the end caps for a more natural shape, expecting
+similar results.
 
-% Results and Discussion can be combined.
-\section*{Results}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+Figure~\ref{image-p} shows a series of color plots of the density of
+proteins at each stage of the reaction cycle. Deterministic simulation
+data is shown above and stochastic simulation data is shown below.
+The cells shown are $4\micron$ in length, measured from end to end.
+We have `smeared out' the stochastic concentrations in a manner meant
+to reproduce the images shown by diffraction limited fluorescence
+microscopy.  We do so using the two dimensional Gaussian approximation
+developed by Zhang \emph{et al.}~\cite{zhang2007gaussian}.  In this
+approximation we use a numerical aperture value of 1.3, which is the
+same as used by Mannik experimentally, and a wavelength of $650nm$.
+Each frame is 2.5 seconds ahead of the last, and each image shows the
+concentration of a given state of protein (of the five described in
+the reaction model) summed over the coordinate normal to the page.
 
-\begin{table}[!ht]
-\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-\caption{
-{\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-\begin{tabular}{|l|l|l|l|l|l|l|l|}
-\hline
-\multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-$cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-$cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-$cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-\end{tabular}
-\begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
+Figure~\ref{image-p} begins about 300 seconds into the simulation and
+shows one period of oscillation.  At $t=0$ there is a high
+concentration of MinD:ATP that has accumulated on the membrane at the
+bottom of the cell. An important aspect of Huang's model is that the
+MinD is attracted to and sticks to the membrane nonlinearly: as it
+accumulates there it begins to `recruit' other MinD that is diffusing
+in the cytoplasm nearby, causing peaks in concentration to build up on
+the walls.  Meanwhile, the MinE creeps downward as it reacts with the
+membrane-bound MinD, forming the MinD:MinE:ATP complex, then breaks it
+apart and diffuses downward a bit more before it again reacts with
+membrane-bound MinD.  This process can be seen in the form of the
+well-known ``MinE rings'' (actually, MinE bound to MinD on the
+membrane).  These rings are visible in the deterministic model plots
+as a green band on the walls from 0 seconds to 4 seconds (and later
+from 15 to 23 seconds).  The appearance of these rings in the
+deterministic model along side their less obvious appearance in the
+stochastic model highlights an advantage of the deterministic model:
+the idealization of deterministic data allows one to see patterns in
+the averaged behavior that might otherwise be missed.  In the
+stochastic model the MinE still exhibits higher concentrations in the
+same regions throughout the process, but what would ideally be a
+``ring'' pattern is instead an asymmetric collection of maxima, which
+would become a ring after phase-locked averaging.
+
+During the formation of these rings, cytoplasmic MinE is diffusing in
+the upper portion of the cell and will naturally progress downward,
+where there is membrane-bound MinD to react with, leading to a
+depletion of MinE in the upper portion of the cell.  As the MinE ring
+converges upon the lower end of the cell, MinD that has been released
+is able to diffuse upward, past the ring, while still in its MinD:ADP
+state and unable to bind to the membrane.  After it undergoes
+nucleotide exchange, resulting in MinD:ATP, it is ready to accumulate
+on the walls in at the top of the cell, where the MinE has been
+depleted.  This can be seen in seconds 10 through 20 in both models,
+followed by the subsequent MinE ring formation and movement upward
+(beginning the same process in the opposite direction) that can be
+seen in seconds 15 through 23.
+
+It is clear from Fig.~\ref{image-p} that the stochastic simulation
+results in a protein distribution that is less spatially regular than
+the deterministic model predicts.  In fact, when viewed as a movie
+(see supplementary material), the stochastic model exhibits a ``starry
+night'' effect, as recruitment leads to clusters of MinD forming on
+the wall and then subsequently dissipating.  \fixme{Talk about
+  membrane diffusion blurring out the starry night.}  This naturally
+leads to irregularity in the temporal periodicity of the system, which
+we quantify by examining the temporal correlation function of the
+total MinD found in two opposite polar regions.
+%
+This correlation function, which is displayed in Fig.~\ref{corr-pill},
+is given by
+\begin{equation}
+  C(\tau) \propto \int
+  (N_{\textit{top}}(t) - \bar N_{\textit{top}})
+  (N_{\textit{bottom}}(t+\tau) - \bar N_{\textit{bottom}})dt
+\end{equation}
+where $N_{\textit{top}}(t)$ and $N_{\textit{bottom}}(t)$ are the total
+MinD proteins in the top and bottom thirds of a cell.  These plots
+help us in studying the periods and the regularity and stability of
+oscillations.  These curves are well fit with a simple decoherence
+model, given by the equation
+\begin{equation}
+  C(\tau) = -\cos\left(\frac{2\pi\tau}{T}\right) e^{-\frac{\tau}{\tau_c}}
+\end{equation}
+where $T$ is the period and $\tau_c$ is the coherence time.  In the
+case of the stochastic model the pill exhibits coherence times of
+about 8 periods and in the case of the deterministic model oscillate
+indefinitely with complete coherence, indicating that its behavior is
+perfectly periodic.
+
+\begin{figure*}
+  \centering
+  \includegraphics[width=16cm]{../paper/plot-ave}
+  \caption{We display here arrows depicting successive maxima in space
+    and and time overlayed on a color plot of the total MinD density
+    averaged over the same time period.  The simulation time covered
+    for the flattened cells is 350 seconds, which is the same
+    period of time depicted in the experimental data plots of Mannik
+    \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
+    shape, we only cover 250 seconds, in order to provide a
+    useful comparison due to its shorter oscillation period.  The top
+    row shows plots published by Mannik \emph{et al.} of the MinD maxima behavior
+    and the bottom two rows show our simulations using the stochastic
+    and deterministic models, respectively.  We simulated
+    approximations to the two shapes observed by Mannik, which we call
+    \emph{shape A} and \emph{shape B}.  In addition, we studied two
+    flattened stadium shapes which we call \emph{stadium A} and
+    \emph{stadium B} corresponding in aspect ratio and thickness to
+    the two experimental shapes.  The spatial length scale of all the
+    figures shown was identical. Each of the flattened cell shapes
+    uses the same color scale for the number of proteins per unit
+    area.  Finally, we display the natural pill shape, which was also
+    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
+    different color scale to reflect the thicker cell containing more
+    proteins per cross-sectional area.  }
+  \label{randst-plot-ave}
+\end{figure*}
+
+\begin{figure}
+  \begin{center}
+    \includegraphics[height=6.4cm]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
+    \includegraphics[height=6.4cm]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
+  \end{center}
+  \caption{Temporal correlation function of the total MinD found in
+    two opposite polar regions of the shape \emph{A} (above) and the
+    stadium \emph{A} (below) cell shapes, shown against the
+    correlation time.  Data for both the the determinisitic and
+    stochastic models are shown, and the correlation functions are
+    scaled to have the same initial value.  For shape \emph{A}, the
+    stochastic model shows an oscillation period of 53.1 seconds and
+    coherence time of 246 seconds, so that it takes roughly 4.6 periods
+    for the behavior to decohere.  For the stadium \emph{A}, the same
+    model shows an oscillation period of 51 seconds and coherence time of
+    323 seconds, so that it takes roughly 6.3 periods for the behavior
+    to decohere.}
+  \label{fig:corr-pancake-A}
+\end{figure}
+
+%% \begin{table}[!ht]
+%% \begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
+%% \caption{
+%% {\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
+%% \begin{tabular}{|l|l|l|l|l|l|l|l|}
+%% \hline
+%% \multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
+%% $cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
+%% $cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
+%% $cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
+%% \end{tabular}
+%% \begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
 Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-\end{flushleft}
-\label{table1}
-\end{adjustwidth}
-\end{table}
+%% \end{flushleft}
+%% \label{table1}
+%% \end{adjustwidth}
+%% \end{table}
 
-\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}
+\subsection*{Comparison of Mannik's Experimental and Our Stadium Shapes}
 
-Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
+As described in Section~\ref{sec:model-method-shapes}, we will focus
+on simulation of four illustrative flattened cell shapes: two shapes
+created to replicate those shapes observed experimentally by
+Mannik \emph{et al.}~\cite{mannik2012robustness} (shape~\emph{A} and
+shape~\emph{B}), and for comparison two symmetrical stadium shapes
+that have the identical aspect ratio, thickness and volume (stadium
+\emph{A} and stadium \emph{B}), shown in Figure~\ref{randst-plot-ave}.
+These stadium shapes enable us to distinguish between the effect of
+flattening the cell and the cell shape's irregularity and asymmetry.
+We note that shape \emph{B} is more irregular than shape \emph{A}, and
+in particular features a prominent region of concavity on its
+left-hand side.  For each of these shapes (in addition to the
+wild-type pill shape discussed previously) we have simulated in excess
+of 15000 seconds (over 4 hours) of evolution of the MinD system using
+the deterministic version of Huang's model~\cite{huang2003dynamic},
+and in excess of 100000 seconds (over 27 hours) using the stochastic
+model.
 
-Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
-Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-Nam condimentum sem eget mollis euismod.
-Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
-Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
-Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
+From each of these flattened simulations, we have chosen a typical 350
+second segment to compare with the published results of
+Mannik \emph{et al.}~\cite{mannik2012robustness}, exemplified in arrow plots in
+which the arrow heads show the location of sequential MinD maxima
+within the cell (in Fig.~\ref{randst-plot-ave}).  In addition to
+arrows between successive maxima in space and time, we plot as a
+colored background the density of MinD proteins averaged over the same
+time period.  We note that we have manually verified that our
+(computer-generated) arrow plots also reflect a human interpretation
+of a movie of the same data.  Finally, for comparison we present the
+same plot for a wild-type cell, with a time period of 250 seconds to
+account for its short period of oscillation.
 
-\subsection*{Sed ac quam id nisi malesuada congue.}
+In every case, including the wild-type pill shape, we see irregularity
+in the location of the maxima when using the stochastic model.  The
+deterministic model shows uniformly bipolar oscillation, with the
+exception of shape \emph{B}, which develops weak intermediate maxima
+on the right-hand edge of the cell.  From these results, we conclude
+that the deterministic model is inadequate to explain experimental
+observations of the locations of density maxima of the MinD protein.
 
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+%% We found that the deterministic simulations of the MinD system results
+%% in robust and regular oscillatory behavoir of polar selection and
+%% oscillation in not only symmetrical shapes, such as the wildtype pill
+%% shape, but also in very assymetrical, flatttened cells, such as those
+%% observed by Mannik.  We also examined larger and smaller versions of
+%% these shapes, and found this behavior to be very robust, from the
+%% minimum size to sustain oscillation (around \fixme{???} $\mu$m) up to
+%% around twice the cell size reported by Mannik.  At larger sizes than
+%% this, less regular oscillations occur using the deterministic method,
+%% but we note that the cells reported by Mannik are already considerably
+%% larger in volume than typical wild type
+%% cells~\cite{kubitschek1990cell,kubitschek1968linear,mannik2012robustness}.
 
-% Please do not create a heading level below \subsection. For 3rd level headings, use \paragraph{}.
-\subsection*{Subsection 1}
-Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+The predictions of the stochastic model are roughly similar to the
+experimental results in terms of irregularity of the locations of
+maxima, although there are locations on the edges of the cells where
+experiment shows maxima occurring that we never see in our simulations,
+suggesting that the model does not precisely reflect the experiment.
+We also note that the stadium shapes in Fig.~\ref{randst-plot-ave}
+appear to have maxima location irregularity that is qualitatively
+similar to our irregular shapes and to experiment.
 
-\subsection*{Subsection 2}
+However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
+the flattening of the cell versus cell shape irregularity and
+asymmetry in developing an understanding of the origin of the
+experimentally observed behavior.  Although in the movies the stadiums
+appear to display, on average over long time scales, a somewhat more
+regular oscillation than appears in the irregular shapes \emph{A} and
+\emph{B}, the limited time range of the arrow plots (350 seconds) is
+inadequate to make this comparison.  We therefore return to the
+correlation function between the number of proteins in a segment at
+the top of the cell and the number of proteins in a segment at the
+bottom of the cell.  Fig.~\ref{fig:corr-pancake-A} shows this plot for
+shape \emph{A} and stadium \emph{A}.  E. Coli cell doubling times vary
+widely depending on environmental conditions, but will often be
+between 20 minutes to 100 minutes~\cite{pierucci1972chromosome}, while
+fluorescent microscopy experiments have shown that the FtsZ ring
+builds itself with a half life of roughly 30
+seconds~\cite{stricker2002rapid}.  Here we plot correlations of
+correlation times up to 500 seconds, a biologically relevant
+timescale.
+
+%% \begin{figure}
+%%   \includegraphics[width=8.7cm]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
+%%   \includegraphics[width=8.7cm]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
+%%   \caption{Correlation for B shapes}
+%%   \label{corr-B}
+%% \end{figure}
+
+We see that both in the shape \emph{A} and stadium \emph{A}, the
+deterministic model is perfectly periodic.  Both the deterministic and
+stochastic model correlations have the same number of proteins in
+their cells, and have been normalized with the same normalization
+factor, so that they can be directly compared against each other.  The
+stochastic simulation of shape \emph{A} has a coherence time of 4.6
+periods, while the corresponding simulation of stadium \emph{A} has a
+coherence time of 6.3 periods.
+%
+The correlation function for stadium \emph{B} is similar to that of
+stadium~\emph{A}, with similar coherence time (5.5 periods, not
+shown), while shape~\emph{B} exhibits a lower coherence time (2.2
+periods).  In the deterministic model, shape~\emph{B} is not precisely
+periodic on biologically relevant timescales, which is reflected in
+Fig.~\ref{randst-plot-ave}, in which the arrows describing the
+deterministic model applied to shape \emph{B} show minor maxima
+forming on the right-hand side of the cell, in contrast to the regular
+polar maxima formed by shape~\emph{A} and the two stadiums.
+%
+From the stochastic correlation data, we conclude that irregularity of
+shape has only a moderate affect on the temporal regularity of the
+oscillatory behavior, with even the very distorted shape~\emph{B}
+exhibiting only a factor of two greater decoherence.
+
 \paragraph{3rd Level Heading.} Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
@@
 
-\section*{Discussion}
-Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
+\section*{Conclusion}
+We find agreement between our stochastic simulations and experiments
+showing disrupted bipolar MinD oscillation in asymmetric flattened
+E. coli cells~\cite{mannik2012robustness}.  As observed
+experimentally, our simulations predict that MinD maxima will form in
+a spatially irregular sequence of locations.  This result builds upon
+existing results showing that this model is effective in a variety of
+wild-type and mutated cell shapes~\cite{fange2006noise, varma2008min,
+  kruse2007experimentalist}, and reinforces that the stochastic
+variation of Huang's 2003 model~\cite{fange2006noise,
+  kerr2006division} has considerable predictive power beyond the
+standard wild-type cell.  \fixme{Discuss which of these are likely to
+  map to more recent models.}
 
-\subsection*{\lorem\ and \ipsum\ Nunc blandit a tortor.}
+%
+%% We have simulated flattened cell shapes similar to those observed
+%% experimentally by Mannik \emph{et al.}, with a stochastic and a
+%% deterministic version of Huang's widely used reaction-diffusion model.
+%% %
+%% We find that the stochastic model predicts experimentally accurate
+%% qualitative behavoir in both the wild-type, pill-shaped cells (as
+%% found in previous studies~\cite{fange2006noise, varma2008min,
+%%   kruse2007experimentalist}), as well as in the new, flattened,
+%% irregularly shaped cells.  These flattened cells invariably show
+%% spatially irregular formation of maxima as has been observed
+%% experimentally.
 
-CO\textsubscript{2} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-Quisque augue sem, tincidunt sit amet feugiat eget, ullamcorper sed velit.
+In contrast to the stochastic model, the original deterministic
+version of the model~\cite{huang2003dynamic} predicts behavior that
+contradicts experimental observations.  Specifically, the
+deterministic model predicts robust and periodic bipolar oscillation
+in irregularly shaped cells, with a minor intermediate maximum
+appearing in shape \emph{B}.  Thus we conclude that this method is
+inconsistent with experiment, and cannot be relied upon for
+predictions of the behavior of the MinD system.  This is the most
+clear example of the inadequacy of the deterministic simulation method
+in reproducing experimental behavior of the MinD system to date.
+Until now the results of deterministic and stochastic simulation have
+largely coincided, with the stochastic method showing minor
+differences in behavior when compared to deterministic
+models~\cite{kerr2006division, fange2006noise, huang2004min,
+  kruse2007experimentalist}.
 
-Sed non aliquet felis.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Mauris commodo justo ac dui pretium imperdiet.
-Sed suscipit iaculis mi at feugiat.
-Ut neque ipsum, luctus id lacus ut, laoreet scelerisque urna.
-Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-Nam condimentum sem eget mollis euismod.
-Nullam dui urna, gravida venenatis dui et, tincidunt sodales ex.
-Nunc est dui, sodales sed mauris nec, auctor sagittis leo.
-Aliquam tincidunt, ex in facilisis elementum, libero lectus luctus est, non vulputate nisl augue at dolor.
-For more information, see \nameref{S1_Text}.
+We find that flattened but regular and symmetric cells exhibit MinD
+oscillations that are qualitatively similar to the oscillations
+observed experimentally (and in our simulation) in irregular and
+asymmetric cells.  This demonstrates that asymmetry is not required in
+order to induce spatially irregular MinD oscillations.  In addition,
+the temporal regularity of oscillations is only moderately affected by
+irregularity in the shape of flattened cells.  Thus we conclude that
+it is the flattening of the cells rather than their irregular shape
+that primarily causes the disruption of regular bipolar oscillation
+which is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.
 

### 2015-01-14 paper/plos.tex
a few minor edits with Jeff Tested everything on bennet.

@@
 
-\fixme{THE FOLLOWING NEEDS much CHANGING.  Many reaction-diffusion
-  models have been proposed... There are several newer models that
-  incorporate new experimental results.}
-%
 A number of models of the MinD protein system have been developed that
@@
 %
-Some of these models
-\cite{fange2006noise,bonny2013membrane,halatek2012highly} modify the
-Huang model cited above to more accurately treat experimental findings
-published after his 2003 paper \cite{Meacci2007,Loose2011}. They
-introduce diffusion along the membrane that is two to three orders of
-magnitude lower than that within the cytoplasm, revise the process of
-MinD recruitment to the membrane, and change some of the constants
-used in the model. The Bonny 2013 model assumes an instantaneous
-nucleotide exchange rate at one point in the reaction cycle, and
-relies upon MinE’s ability to independently remain attached to the
-membrane in a manner that allows it to react with a number of MinD
-proteins before disassociating.
+Several models
+\cite{fange2006noise,bonny2013membrane,halatek2012highly} modify
+Huang's original model to more accurately treat experimental findings
+published after his 2003 paper \cite{Meacci2007,Loose2011}. These
+models introduce slow diffusion along the membrane (two to three
+orders of magnitude slower than that within the cytoplasm), revise the
+process of MinD recruitment to the membrane, and change some of the
+constants used in the model. The Bonny 2013 model assumes an
+instantaneous nucleotide exchange rate, and allows MinE to remain
+independently attached to the membrane after dissasociating with
+MinD~\cite{bonny2013membrane}.
 %
@@
 %%   oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
-In this paper we use Huang's 2003 model~\cite{huang2003dynamic} in
-both deterministic and stochastic variants to study flattened cells
-similar to those observed by Mannik \emph{et
-  al.}~\cite{mannik2009bacterial}.  \fixme{Some weak
-  justification... it has been widely used.}
+In this paper we use Huang's original 2003
+model~\cite{huang2003dynamic}, which has been widely
+used~\cite{hattne2005stochastic} \fixme{search for more}, in both
+deterministic and stochastic variants to study flattened cells similar
+to those observed by Mannik \emph{et al.}~\cite{mannik2009bacterial}.
+\fixme{Some weak justification... it has been widely used.}
 

### 2015-01-14 paper/plos.tex
add lots of fixmes from referees Tested everything on bennet.

@@
 \linenumbers
+
+\fixme{
+  First referee:
+  \begin{enumerate}
+  \item Add discussion of ``platform'' --- wrote our own code,
+    publically available (cite github?).
+  \item Make 3D geometries available? Cite that the publically
+    available code can generate them?
+  \item Claims differential equations aren't needed.
+  \item Claims wild-type movie-ish plot not needed.
+  \item Points out problems with Huang 2003:
+    \begin{enumerate}
+    \item Lacks diffusion on the membrane
+    \item Underestimates diffusion in cytoplasm by a factor of 5-6.5.
+    \item Uses MinD-ADP -> MinD-ATP that is 3 times lower than
+      experimental bound.
+    \item (Still debated) No evidence that DE recruits to membrane.
+    \item Works in only a limited part of parameters phase space, and
+      could not account for important things like
+      temperature-independence.
+    \end{enumerate}
+  \item Height should be bigger to compare with experiment.  0.4-0.6
+    microns.  \textcolor{blue}{HIGH PRIORITY!!! to figure this out}
+
+    The 0.25 micron height of the cells used in this study does not
+    represent the experimental settings well. The simulations are
+    based on the flattened cell shapes reported from the experiments
+    by Mannik et al 2009 and 2012. In these experimental studies,
+    E. coli were shown to be able to grow in channels as low as 0.6
+    micron in hard silicon structures, and no more than 0.4 micron
+    (see Mannik 2009). Indeed, 0.25 micron channels were constructed
+    with PDMS ceilings, which is a rather flexible polymer allowing
+    bacteria to deform it to effectively higher channels. Thus the
+    simulations would be more realistic if performed in the range of
+    0.4-0.6 micron thickness.
+
+    \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
+      then we and you observe it growing in a .25 micron flexible
+      channel, it presumably must be able to grow because it deformed
+      the channel to larger than .3 microns.}
+  \item Starry night in the wild-type cells is a problem.
+  \item Better explanation of correlation function (which is
+    interesting!).
+  \item Shape A is the interesting bit in our main figure.
+  \item Would like more analysis of stochastic locations in different
+    geometries.  Clusters?  Could add more geometries?
+  \item Bold conclusions about flattening.  Talk about both width and
+    thickness.  Compare Halatek 2012.  Wants systematically more
+    geometries again.
+  \item Is doubtful of our correlation plots relative to those of
+    Fange and Elf 2006.
+  \item Clarify (esp in conclusions) what we mean by flattening and
+    irregular shape.  ``breaking the cylindrical symmetry and
+    flattening the cells.'' versus ``breaking the mirror plane
+    symmetry of the cross-section of a flattned cell.''
+  \item[TODO suggestion] Switch to Halatek and Frey
+  \item[TODO suggestion] Thoroughly explor shape parameter space
+  \item[TODO suggestion] Check robustness of our conclusions with
+    respect to changes in (reaction-diffusion?) parameters.
+  \item Check order of figures and their references.
+  \item Cite biological (non-computational) works e.g. Corbin 2008.
+  \end{enumerate}
+  Second referee:
+  \begin{enumerate}
+  \item Nitpicks about language of deterministic model versus
+    stochastic model.  (Read carefully)
+  \item Explain in greater detail the obviousness (maybe) that the
+    deterministic approach doesn't have fluctuations.  RESPOND:
+    chaotic systems do deterministically result in fluctuations.
+    Explain this somewhere, and discuss triviality of the conclusion
+    that deterministic is wrong because it does not exhibit these
+    irregularities.
+  \item Would like temporal averages over cell-cycle time scales.
+  \item More discussion of how flattening leads to spatial
+    irregularities.  Compare with large nearly spherical e. coli Shih
+    2005.  See also Halatek and Frey 2012 for rotating oscillation
+    axis due to destabilization of short modes.  How does this connect
+    with our stability analysis?
+  \item Should mention more recent revisions of the model.
+  \item Fange and Elf do not use the same reaction-diffusion
+    equations.
+  \item Clarify statement about 1000 proteins and stochastic
+    fluctuation.  Reword about a continuum description omitting
+    information?
+  \item Do not call Huang parameters ``wild type values.''  They are
+    fitted parameters.
+  \item Add methods section for numerics (deterministic).
+  \item Add details of the linear stability analysis.
+  \end{enumerate}
+}
+
+\fixme{Redo stability analysis with larger thickness, whatever we pick.}
 

### 2015-01-16 paper/plos.tex
edited intro to reference thicker silicon slits and added some references Tested everything on crystal.

@@
 limitations to this robust capability to
-oscillate~\cite{mannik2010bacteria, mannik2009bacterial}. They have
-experimentally forced \emph{E. coli} cells into microfabricated
-silicon channels of $0.25\micron$ thickness. Upon entering the
-channels, the cells undergo a mechanical deformation in which they
-both widen and lengthen within the plane of the channel.  This
-deformation results in very wide (they can reach widths of over
+oscillate~\cite{mannik2012robustness,mannik2009bacterial,mannik2010bacteria}. They
+have experimentally forced \emph{E. coli} cells into microfabricated
+channels of $0.25\micron$ thickness, in which they area able to grow
+and divide. The channels, which are covered in a layer of PDMS, are
+deformable to some degree.  Experiments with a different geometry that
+is constructed without PDMS show that it's reasonable to assume the
+bacteria deform the PDMS channels to a thickness of at least
+$0.4\micron$~\cite{mannik2009bacterial,mannik2010bacteria}.
+
+Upon entering the channels, the cells undergo a mechanical deformation
+in which they both widen and lengthen within the plane of the channel.
+This deformation results in very wide (they can reach widths of over
 $5\micron$) flattened cells that when viewed from the top down have
@@
 Huang's original model to more accurately treat experimental findings
-published after his 2003 paper \cite{Meacci2007,Loose2011}. These
-models introduce slow diffusion along the membrane (two to three
-orders of magnitude slower than that within the cytoplasm), revise the
-process of MinD recruitment to the membrane, and change some of the
-constants used in the model. The Bonny 2013 model assumes an
-instantaneous nucleotide exchange rate, and allows MinE to remain
-independently attached to the membrane after dissasociating with
-MinD~\cite{bonny2013membrane}.
+published after his 2003 paper
+\cite{meacci2006mobility,loose2011min}. These models introduce slow
+diffusion along the membrane (two to three orders of magnitude slower
+than that within the cytoplasm), revise the process of MinD
+recruitment to the membrane, and change some of the constants used in
+the model. The Bonny 2013 model assumes an instantaneous nucleotide
+exchange rate, and allows MinE to remain independently attached to the
+membrane after dissasociating with MinD~\cite{bonny2013membrane}.
 %
@@
 model~\cite{huang2003dynamic}, which has been widely
-used~\cite{hattne2005stochastic} \fixme{search for more}, in both
-deterministic and stochastic variants to study flattened cells similar
-to those observed by Mannik \emph{et al.}~\cite{mannik2009bacterial}.
-\fixme{Some weak justification... it has been widely used.}
+used~\cite{hattne2005stochastic} \fixme{search for more} in both
+deterministic and stochastic variants, to study flattened cells of
+$0.4\micron$ thickness that are similar to those observed by Mannik
+\emph{et al.}~\cite{mannik2009bacterial}.  \fixme{Some weak
+  justification... it has been widely used.}
 

### 2015-03-16 paper/paper-MinD.tex
moved text over into plos.tex, modified intro to discuss newer models briefly, updated bib Tested everything on crystal.
modified and added a lot of things after switching over to .4 microns thickness, edited paper Tested everything on crystal.

@@
 %% PNAStwoS.tex
-%% Sample file to use for PNAS articles prepared in LaTeX
+%% Sample file to usse for PNAS articles prepared in LaTeX
 %% For two column PNAS articles
@@
 \begin{document}
+
+\fixme{
+  First referee:
+  \begin{enumerate}
+  \item \blue{David} Add discussion of ``platform'' --- wrote our own code,
+    publically available (cite github?).
+  \item \blue{David} Make 3D geometries available? Cite that the publically
+    available code can generate them?
+  \item Claims differential equations aren't needed.
+  \item Claims wild-type movie-ish plot not needed.
+  \item Points out problems with Huang 2003:
+    \begin{enumerate}
+    \item Lacks diffusion on the membrane. Supported by Meacci 2006,
+      which experimentally tries to measure diffusion on membrane, has
+      a tough time, but shows that definitely diffuses.
+    \item Underestimates diffusion in cytoplasm by a factor of 5-6.5.
+      Supported by Meacci 2006, who concludes a rate of 16 microns
+      squared per sec for MinD and 10 microns squared per sec for
+      MinE.
+    \item Uses MinD-ADP -> MinD-ATP that is 3 times lower than
+      experimental bound. Halatek uses ADP->ATP of 1/6 s-1. They cite
+      Meacci 2006, who state that there is a lower bound on reference
+      time of 3 seconds, so this constant has an upper bound of 1/3
+      s-1.
+    \item (Still debated) No evidence that DE recruits to membrane.
+    \item Works in only a limited part of parameters phase space, and
+      could not account for important things like
+      temperature-independence.
+    \end{enumerate}
+  \item \blue{David} - Height should be bigger to compare
+    with experiment.  0.4-0.6 microns.  \textcolor{blue}{HIGH
+      PRIORITY!!!  to figure this out}
+
+    The 0.25 micron height of the cells used in this study does not
+    represent the experimental settings well. The simulations are
+    based on the flattened cell shapes reported from the experiments
+    by Mannik et al 2009 and 2012. In these experimental studies,
+    E. coli were shown to be able to grow in channels as low as 0.6
+    micron in hard silicon structures, and no more than 0.4 micron
+    (see Mannik 2009). Indeed, 0.25 micron channels were constructed
+    with PDMS ceilings, which is a rather flexible polymer allowing
+    bacteria to deform it to effectively higher channels. Thus the
+    simulations would be more realistic if performed in the range of
+    0.4-0.6 micron thickness.
+
+    \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
+      then we and you observe it growing in a .25 micron flexible
+      channel, it presumably must be able to grow because it deformed
+      the channel to larger than .3 microns.}
+  \item Starry night in the wild-type cells is a problem.
+  \item Better explanation of correlation function (which is
+    interesting!).
+  \item Shape A is the interesting bit in our main figure.
+  \item Would like more analysis of stochastic locations in different
+    geometries.  Clusters?  Could add more geometries?
+  \item Bold conclusions about flattening.  Talk about both width and
+    thickness.  Compare Halatek 2012.  Wants systematically more
+    geometries again.
+  \item Is doubtful of our correlation plots relative to those of
+    Fange and Elf 2006.
+  \item Clarify (esp in conclusions) what we mean by flattening and
+    irregular shape.  ``breaking the cylindrical symmetry and
+    flattening the cells.'' versus ``breaking the mirror plane
+    symmetry of the cross-section of a flattned cell.''
+  \item[TODO suggestion] Switch to Halatek and Frey
+  \item[TODO suggestion] Thoroughly explor shape parameter space
+  \item[TODO suggestion] Check robustness of our conclusions with
+    respect to changes in (reaction-diffusion?) parameters.
+  \item Check order of figures and their references.
+  \item Cite biological (non-computational) works e.g. Corbin 2008.
+  \end{enumerate}
+  Second referee:
+  \begin{enumerate}
+  \item Nitpicks about language of deterministic model versus
+    stochastic model.  (Read carefully)
+  \item Explain in greater detail the obviousness (maybe) that the
+    deterministic approach doesn't have fluctuations.  RESPOND:
+    chaotic systems do deterministically result in fluctuations.
+    Explain this somewhere, and discuss triviality of the conclusion
+    that deterministic is wrong because it does not exhibit these
+    irregularities.
+  \item Would like temporal averages over cell-cycle time scales.
+  \item More discussion of how flattening leads to spatial
+    irregularities.  Compare with large nearly spherical e. coli Shih
+    2005.  See also Halatek and Frey 2012 for rotating oscillation
+    axis due to destabilization of short modes.  How does this connect
+    with our stability analysis?
+  \item Should mention more recent revisions of the model.
+  \item Fange and Elf do not use the same reaction-diffusion
+    equations.
+  \item Clarify statement about 1000 proteins and stochastic
+    fluctuation.  Reword about a continuum description omitting
+    information?
+  \item Do not call Huang parameters ``wild type values.''  They are
+    fitted parameters.
+  \item Add methods section for numerics (deterministic).
+  \item Add details of the linear stability analysis.
+  \end{enumerate}
+}
+
+\fixme{Redo stability analysis with larger thickness, whatever we pick.}
 
@@
 experimentally forced \emph{E. coli} cells into microfabricated
-silicon channels of $0.25\micron$ thickness. Upon entering the
-channels, the cells undergo a mechanical deformation in which they
-both widen and lengthen within the plane of the channel.  This
-deformation results in very wide (they can reach widths of over
-$5\micron$) flattened cells that when viewed from the top down have
-irregular and asymmetric shapes.  While these cells are still able to
-divide into surprisingly equal volumes, the MinD oscillations in these
-cells are irregular, both temporally and spatially. Seen with
-fluorescent microscopy, the MinD maximize in multiple locations within
-the cell, in a seemingly random sequence. These experiments allow for
-an opportunity to test MinD simulation models against more extreme
-cases than have been seen thus far.
+silicon channels of thickness less than that of the natural diameter
+of the cells. Upon entering the channels, the cells undergo a
+mechanical deformation in which they both widen and lengthen within
+the plane of the channel.  This deformation results in very wide (they
+can reach widths of over $5\micron$) flattened cells that when viewed
+from the top down have irregular and asymmetric shapes.  While these
+cells are still able to divide into surprisingly equal volumes, the
+MinD oscillations in these cells are irregular, both temporally and
+spatially. Seen with fluorescent microscopy, the MinD maximize in
+multiple locations within the cell, in a seemingly random
+sequence. These experiments allow for an opportunity to test MinD
+simulation models against more extreme cases than have been seen thus
+far.
 
@@
 oscillations, so we follow Huang\cite{huang2003dynamic} and do not
-deviate from the wild-type values used in the cited work.
+deviate from the perameter values used in the cited work.
 
@@
 same number of proteins per unit volume.  These concentration values
-are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We perform
-simulations with a 3D grid in Cartesian coordinates that has a grid
-spacing of .05\micron.
+are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. \blue{(1,2)}
+We have chosen to write our own simulation platform and membrane
+creation tools from scratch, instead of using existing available
+software used in previous studies\fixme{cite previous studies}. We
+believe there is value in re-creating results with alternative
+software.  Our simulations take place within a three-dimensional
+Cartesian grid that has a grid spacing of .05\micron, and our cell
+shapes are specified by positions and thicknesses of a series of
+gaussians.  Our code is publically available on github.com~\fixme{cite
+  github account in references?}
 
@@
 by a number of flattened out shapes which reflect the experiments of
-Mannik \emph{et al.}, in which bacteria are confined within a thin
-slit of height $0.25\micron$ ~\cite{mannik2012robustness}.  Viewed
-from the top down the cells have the shapes described below and viewed
-from the side they have at their edges a semicircular protrusion (one
-may imagine the shape of a pancake).
+Mannik \emph{et al.}, in which bacteria are confined within thin
+slits.  \blue{(6)}These slits begin with a width of .25\micron, but
+they are coated with a PDMS lining that the cells are able to deform,
+while tests with pure silicon, non-deformable slits show that the
+greatest thickness for which cells are able to penetrate is
+.4\micron~\cite{mannik2012robustness,mannik2009bacterial}.  We
+therefore assume that the PDMS slits have been deformed to this
+thickness and here simulate flattened cells with a thickness of
+.4\micron.  Viewed from the top down the cells have the shapes
+described below and viewed from the side they have at their edges a
+semicircular protrusion (one may imagine the shape of a pancake).
 %
@@
     stochastic models are shown.  The stochastic model shows an
-    oscillation period of 39.5 seconds and coherence time of 307 seconds.
-    The correlation functions are scaled to have the same initial
-    value.}
+    oscillation period of \fixme{following not correct anymore} 39.5
+    seconds and coherence time of 307 seconds.  The correlation
+    functions are scaled to have the same initial value.}
   \label{corr-pill}
@@
   \begin{center}
-    \includegraphics[height=6.4cm]{../data/shape-randst/0_25-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
-    \includegraphics[height=6.4cm]{../data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
+    \includegraphics[height=6.4cm]{../data/shape-randst/0_40-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
+    \includegraphics[height=6.4cm]{../data/shape-stad/0_40-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
   \end{center}
@@
     stochastic model shows an oscillation period of 53.1 seconds and
-    coherence time of 246 seconds, so that it takes roughly 4.6 periods
-    for the behavior to decohere.  For the stadium \emph{A}, the same
-    model shows an oscillation period of 51 seconds and coherence time of
-    323 seconds, so that it takes roughly 6.3 periods for the behavior
-    to decohere.}
+    coherence time of 246 seconds, so that it takes roughly 4.6
+    periods for the behavior to decohere.  For the stadium \emph{A},
+    the same model shows an oscillation period of \fixme{following not
+      correct anymore} 51 seconds and coherence time of 323 seconds,
+    so that it takes roughly 6.3 periods for the behavior to
+    decohere.}
   \label{fig:corr-pancake-A}
@@
 
-%% \begin{figure}
-%%   \includegraphics[width=8.7cm]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
-%%   \includegraphics[width=8.7cm]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
-%%   \caption{Correlation for B shapes}
-%%   \label{corr-B}
-%% \end{figure}
+\begin{figure}
+  \includegraphics[width=8.7cm]{../data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
+  \includegraphics[width=8.7cm]{../data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
+  \caption{Correlation for B shapes}
+  \label{corr-B}
+\end{figure}
 

### 2015-03-16 paper/paper.tex
added my best attempt at putting everything into pnas format, added style file cls file and changes to Makefile Tested everything on crystal.
modified and added a lot of things after switching over to .4 microns thickness, edited paper Tested everything on crystal.

@@
 \begin{document}
+
+\fixme{
+  First referee:
+  \begin{enumerate}
+  \item Add discussion of ``platform'' --- wrote our own code,
+    publically available (cite github?).
+  \item Make 3D geometries available? Cite that the publically
+    available code can generate them?
+  \item Claims differential equations aren't needed.
+  \item Claims wild-type movie-ish plot not needed.
+  \item Points out problems with Huang 2003:
+    \begin{enumerate}
+    \item Lacks diffusion on the membrane
+    \item Underestimates diffusion in cytoplasm by a factor of 5-6.5.
+    \item Uses MinD-ADP -> MinD-ATP that is 3 times lower than
+      experimental bound.
+    \item (Still debated) No evidence that DE recruits to membrane.
+    \item Works in only a limited part of parameters phase space, and
+      could not account for important things like
+      temperature-independence.
+    \end{enumerate}
+  \item Height should be bigger to compare with experiment.  0.4-0.6
+    microns.  \textcolor{blue}{HIGH PRIORITY!!! to figure this out}
+
+    The 0.25 micron height of the cells used in this study does not
+    represent the experimental settings well. The simulations are
+    based on the flattened cell shapes reported from the experiments
+    by Mannik et al 2009 and 2012. In these experimental studies,
+    E. coli were shown to be able to grow in channels as low as 0.6
+    micron in hard silicon structures, and no more than 0.4 micron
+    (see Mannik 2009). Indeed, 0.25 micron channels were constructed
+    with PDMS ceilings, which is a rather flexible polymer allowing
+    bacteria to deform it to effectively higher channels. Thus the
+    simulations would be more realistic if performed in the range of
+    0.4-0.6 micron thickness.
+
+    \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
+      then we and you observe it growing in a .25 micron flexible
+      channel, it presumably must be able to grow because it deformed
+      the channel to larger than .3 microns.}
+  \item Starry night in the wild-type cells is a problem.
+  \item Better explanation of correlation function (which is
+    interesting!).
+  \item Shape A is the interesting bit in our main figure.
+  \item Would like more analysis of stochastic locations in different
+    geometries.  Clusters?  Could add more geometries?
+  \item Bold conclusions about flattening.  Talk about both width and
+    thickness.  Compare Halatek 2012.  Wants systematically more
+    geometries again.
+  \item Is doubtful of our correlation plots relative to those of
+    Fange and Elf 2006.
+  \item Clarify (esp in conclusions) what we mean by flattening and
+    irregular shape.  ``breaking the cylindrical symmetry and
+    flattening the cells.'' versus ``breaking the mirror plane
+    symmetry of the cross-section of a flattned cell.''
+  \item[TODO suggestion] Switch to Halatek and Frey
+  \item[TODO suggestion] Thoroughly explor shape parameter space
+  \item[TODO suggestion] Check robustness of our conclusions with
+    respect to changes in (reaction-diffusion?) parameters.
+  \item Check order of figures and their references.
+  \item Cite biological (non-computational) works e.g. Corbin 2008.
+  \end{enumerate}
+  Second referee:
+  \begin{enumerate}
+  \item Nitpicks about language of deterministic model versus
+    stochastic model.  (Read carefully)
+  \item Explain in greater detail the obviousness (maybe) that the
+    deterministic approach doesn't have fluctuations.  RESPOND:
+    chaotic systems do deterministically result in fluctuations.
+    Explain this somewhere, and discuss triviality of the conclusion
+    that deterministic is wrong because it does not exhibit these
+    irregularities.
+  \item Would like temporal averages over cell-cycle time scales.
+  \item More discussion of how flattening leads to spatial
+    irregularities.  Compare with large nearly spherical e. coli Shih
+    2005.  See also Halatek and Frey 2012 for rotating oscillation
+    axis due to destabilization of short modes.  How does this connect
+    with our stability analysis?
+  \item Should mention more recent revisions of the model.
+  \item Fange and Elf do not use the same reaction-diffusion
+    equations.
+  \item Clarify statement about 1000 proteins and stochastic
+    fluctuation.  Reword about a continuum description omitting
+    information?
+  \item Do not call Huang parameters ``wild type values.''  They are
+    fitted parameters.
+  \item Add methods section for numerics (deterministic).
+  \item Add details of the linear stability analysis.
+  \end{enumerate}
+}
+
+\fixme{Redo stability analysis with larger thickness, whatever we pick.}
 \title{Robustness of MinD oscillation in \emph{Escherichia coli} with
@@
   regulate the process of cell division by identifying the center of
-  the cell.  While this system usually exhibits robust polar
-  oscillations in a variety of cell shapes, new experiments have shown
-  that when the cells are mechanically deformed into wide, flattened
-  out, irregular shapes, the spatial regularity of these oscillations
-  breaks down. Here we study widely used stochastic and deterministic
-  models of Min-system simulation within these new cell shapes.  We
-  find that the deterministic model is decidedly inadequate to
-  reproduce the experimentally observed behavoir, while the stochastic
-  model, based on the same differential equations, is able to do so
-  accurately.  We also find that it is the flattening rather than the
-  irregularity and asymmetry of the cell shape that causes the
-  irregular oscillation behavoir.
+  the cell.  While this system usually exhibits robust bipolar
+  oscillations in a variety of cell shapes, recent experiments have
+  shown that when the cells are mechanically deformed into wide,
+  flattened out, irregular shapes, the spatial regularity of these
+  oscillations breaks down. We employ widely used stochastic and
+  deterministic models of the Min system to simulate cells with flattened
+  shapes.  The deterministic model predicts strong bipolar
+  oscillations, in contradiction with the experimentally observed
+  behavior, while the stochastic model, which is based on the same
+  reaction-diffusion equations, does predict spatially irregular
+  oscillations as observed in experiment.  We further report
+  simulations of symmetric but flattened cell shapes, and find that it
+  is the flattening rather than the asymmetry of the cell shapes that
+  causes the irregular oscillation behavior.
 \end{abstract}
@@
 \section{Introduction}
-It is vital that during the process of bacterial cell division a cell
-avoid minicelling, or splitting into daughter cells with lopsided
-volumes.  Instrumental to this process in \emph{Escherichia coli} is a
-long FtsZ polymer chain that develops on the cell wall in the center
-region of the cell, helping dictate the plane of
-division~\cite{adams2009bacterial, lutkenhaus2007assembly}. Previous
-experimental studies have shown that the MinC protein, known to
-inhibit the FtZ polymer~\cite{shen2010examination}, exhibits regular
-pole to pole oscillatory behavior between both ends of the wild-type
-pill-shaped cell.  It thus has a higher time averaged concentration in
-the cell poles than in the center region, which aides in preventing
-the FtZ from developing in the wrong region.  The MinC is recruited to
-these poles by MinD, which itself interacts with another protein,
-MinE, in a system which exhibits pole-to-pole oscillatory
-behavoir~\cite{hu1999topological, fu2001mine, shapiro2009and,
-  yu1999ftsz, raskin1999rapid, meacci2005min, raskin1999minde}.
+
+It is vital that during the process of bacterial cell
+division a cell avoid minicelling, or splitting into daughter cells
+with lopsided volumes.  Instrumental to this process in
+\emph{Escherichia coli} is a long FtsZ polymer chain that develops on
+the cell wall in the center region of the cell, helping dictate the
+plane of division~\cite{adams2009bacterial,
+  lutkenhaus2007assembly}. Previous experimental studies have shown
+that the MinC protein, known to inhibit the FtsZ
+polymer~\cite{shen2010examination}, exhibits regular pole to pole
+oscillatory behavior between both ends of the wild-type pill-shaped
+cell.  It thus has a higher time averaged concentration in the cell
+poles than in the center region, which aides in preventing the FtsZ
+from developing in the wrong region.  The MinC is recruited to these
+poles by MinD, which itself interacts with another protein, MinE, in a
+system which exhibits pole-to-pole oscillatory
+behavior~\cite{shapiro2009and, yu1999ftsz,
+  meacci2005min,huang2003dynamic,kerr2006division,mannik2009bacterial}.
+%% \cite{hu1999topological, fu2001mine, shapiro2009and,
+%%   yu1999ftsz, raskin1999rapid, meacci2005min, raskin1999minde}.
 
@@
 
-A number of models of the MinD protein system have been developed,
-which accurately describe the dynamics using simulations of
-reaction-diffusion equations.
+A number of models of the MinD protein system have been developed that
+accurately describe its basic oscillatory nature.
 %
@@
 states~\cite{meinhardt2001pattern}.  In 2003 Huang improved upon this
-work with a simple and very successful simulation model based on
+approach with a simple and very successful simulation model based on
 MinD-MinE combination, ATPase hydrolysis, and MinD membrane attachment
@@
 recruited to the membrane by MinD that is already clustered there
-(following observed non-linear attachement of MinD on the cell
+(following observed non-linear attachment of MinD on the cell
 membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
-once attached.  A number of studies have used an approach similar in
-that they do not rely on the ability of MinD to move along the walls
-and cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
-  drew2005polymerization, fange2006noise, kerr2006division}, while
-studies have been made as well of models which rely on MinD mobility
-and attraction on the cell membrane~\cite{kruse2002dynamic,
-  howard2005cellular}.
+once attached.
+%
+Several models
+\cite{fange2006noise,bonny2013membrane,halatek2012highly} modify
+Huang's original model to more accurately treat experimental findings
+published after his 2003 paper
+\cite{meacci2006mobility,loose2011min}. These models introduce slow
+diffusion along the membrane (two to three orders of magnitude slower
+than that within the cytoplasm), revise the process of MinD
+recruitment to the membrane, and change some of the constants used in
+the model. The Bonny 2013 model assumes an instantaneous nucleotide
+exchange rate, and allows MinE to remain independently attached to the
+membrane after dissasociating with MinD~\cite{bonny2013membrane}.
+%
+
+%%  A number of studies have used an approach similar in
+%% that they do not rely on the ability of MinD to move along the walls
+%% and cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
+%%   drew2005polymerization, fange2006noise, kerr2006division}, while
+%% studies have been made as well of models which rely on MinD mobility
+%% and attraction on the cell membrane~\cite{kruse2002dynamic,
+%%   howard2005cellular}.
 
@@
 
-%% \fixme{There are not any direct comparisons of the deterministic and
-%%   stochastic models that I can find other than the fange2006 paper
-%%   cited above for the round cells.  Those showed that the
-%%   deterministic sims are 'bistable' - one type of initial conditions
-%%   (MinD starting on walls on one side) show oscillations, another type
-%%   (half cyto is filled with 3/4 of MinD) don't.  Huang in 2004 paper
-%%   cited above uses numerical determinisitc and finds that it can show
-%%   oscillations in round cells as well, but right now I can't find it
-%%   and the journal doesn't give me access to it.  predict oscillations
-%%   in perfectly round cells unless noise was added to the simulation,
-%%   but could in almost round ellipses.  It seems that once the
-%%   stochastic models began to be used, nobody really used the
-%%   deterministic model any longer.  Not sure what to say about this in
-%%   order to introduce what we do here properly.}
-
-In this paper we use Huang's 2003 model~\cite{huang2003dynamic} in
-both deterministic and stochastic variants to study flattened cells
-similar to those observed by Mannik~\cite{mannik2009bacterial}.
+%% biology~\cite{lawson2013spatial, robb2014stochastic,
+%%   oguz2014stochastic, fu2013deterministic, rudiger2014stochastic}, and
+In this paper we use Huang's original 2003
+model~\cite{huang2003dynamic}, which has been widely
+used~\cite{hattne2005stochastic} \fixme{search for more} in both
+deterministic and stochastic variants, to study flattened cells of
+$0.4\micron$ thickness that are similar to those observed by Mannik
+\emph{et al.}~\cite{mannik2009bacterial}.  \fixme{Some weak
+  justification... it has been widely used.}
 
 \begin{figure}
-  \includegraphics[width=\columnwidth]{reactions}
+  \includegraphics[width=8.7cm]{reactions}
   \caption{Reactions included in the model of Huang \emph{et
@@
 \section{Model, Methods, and Cell Shapes}\label{sec:model-method-shapes}
+\subsection*{Model and Cell Shapes}
+\label{sec:model-method-shapes}
 We implement the reaction-diffusion model of Huang \emph{et
@@
 In this paper we focus on four specific flattened cell shapes.  Two of
-these shapes replicate those published by Mannik, and the other two
-are `stadium' shapes that respectively have the same aspect ratio,
-thickness, and volume as the two Mannik shapes.  Viewed from the top
-down, these stadium shapes appear as rectangles with semi-circular end
-caps on the long axis ends.
-
-%% Our pill shapes differ from those of Huang \emph{et al.} in that they
-%% are cylinders with hemisphere endcaps instead of pure cylindrical
-%% shapes.  Our cylinderidrical radius is $0.5\micron$ and the lengths
-%% of our cells (measured between the tips of the endcaps) are
-%% $5\micron$, $4\micron$, $3\micron$, and $2.5\micron$.
-
-%% \fixme{Is the following Kubitscheck paragraph needed?}
-%% Kubitschek has shown in multiple experiments that at the time of cell
-%% division cells have a volume that is within a range of roughly
-%% $1\micron^3$ to $2\micron^3$~\cite{kubitschek1990cell,
-%%   kubitschek1968linear}.  We follow Huang's
-%% simulations\cite{huang2003dynamic} and Mannik's experiments and model
-%% cells that are slightly larger than this range.
+these shapes replicate those published by Mannik \emph{et al.}, and
+the other two are `stadium' shapes that respectively have the same
+aspect ratio, thickness, and volume as the two cell shapes
+experimentally observed by Mannik \emph{et
+  al.}~\cite{mannik2012robustness}.  Viewed from the top down, these
+stadium shapes appear as rectangles with semi-circular end caps on the
+long axis ends.
 
@@
   \begin{center}
-    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
+    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
     \vspace{-1.5em}
-    \includegraphics[width=0.8\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-    \vspace{-3em}
+    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+    \vspace{-1.5em}
   \end{center}
@@
 oscillations.
+
+%% Nulla mi mi, Figure~\ref{fig1} venenatis sed ipsum varius, volutpat
+%% euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem
+%% et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur
+%% adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id
+%% massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce
+%% fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel
+%% sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id,
+%% cursus neque. Praesent faucibus semper libero.
+
+%% \begin{figure}[h]
+%% \caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis
+%%     sed ipsum varius, volutpat euismod diam.}  Figure Caption Proin
+%%   rutrum vel massa non gravida. Quisque tempor sem et dignissim
+%%   rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing
+%%   elit.}
+%% \label{fig1}
+%% \end{figure}
+
+%% \begin{enumerate}
+%% \item{react}
+%% \item{diffuse free particles}
+%% \item{increment time by dt and go to 1}
+%% \end{enumerate}
+
+% Results and Discussion can be combined.
 
@@
 
+\bibliographystyle{plain}
 \bibliography{paper}

### 2015-03-16 correlation_box.sh

@@ -2,19 +2,19 @@
 
 echo starting !
 
-srun --job-name="corr randst 18.50 18.50 95.00 full_array 0.00 4500.00" python pyplots/density-correlation.py randst 0.25 18.50 18.50 95.00 15.00 full_array 0.00 &
-#srun --job-name="corr randst 18.50 18.50 95.00 exact 0.00 5000.00" python pyplots/density-correlation.py randst 0.25 18.50 18.50 95.00 15.00 exact 0.00 &
+#srun --job-name="corr randst 18.50 95.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 full_array 0.00 &
+srun --job-name="corr randst 18.50 95.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 exact 0.00 &
 
-srun --job-name="corr randst 18.60 28.60 94.00 full_array 0.00 1020.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 0.00 &
-#srun --job-name="corr randst 18.60 28.60 94.00 exact 0.00 1800.00" python pyplots/density-correlation.py randst 0.25 18.60 28.60 94.00 15.00 exact 0.00 &
+srun --job-name="corr randst 18.60 94.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 full_array 0.00 &
+srun --job-name="corr randst 18.60 94.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 exact 0.00 &
 
-srun --job-name="corr stad 2.35 1.32 full 0.00 10000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 full_array 0.00 &
-#srun --job-name="corr stad 2.35 1.32 exact 0.00 6000.00" python pyplots/density-correlation.py stad 0.25 2.35 1.32 0.00 15.00 exact 0.00 &
+srun --job-name="corr stad 2.35 1.32 full 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 full_array 0.00 &
[…]

### 2015-03-16 new-script.py

@@ -1,0 +1,9 @@
+from __future__ import division
+import numpy as np
+import matplotlib.pyplot as plt
+
+data = np.loadtxt("arrow-file.txt")
+print data[:,1]
+sorted_data = np.sort(data[:,1])
+plt.plot(sorted_data[::-1])
+plt.show()

### 2015-03-16 paper/plot-arrow-ave.py

@@ -27,25 +27,20 @@ protein_name = "NflD"
 arrow_file = open('arrow-file.txt','w')
 
 
-# arg_set = ["randst/0.25-18.50-18.50-95.00-15.00-full_array",
-#            "randst/0.25-18.60-28.60-94.00-15.00-full_array",
-#            "stad/0.25-3.00-1.18-0.00-15.00-full_array",
-#            "randst/0.25-18.50-18.50-95.00-15.00-exact",
-#            "randst/0.25-18.60-28.60-94.00-15.00-exact",
-#            "stad/0.25-3.00-1.18-0.00-15.00-exact"]
-arg_set = ["randst/0.25-18.50-18.50-95.00-15.00-exact",
-           "randst/0.25-18.50-18.50-95.00-15.00-full_array",
-           "randst/0.25-18.60-28.60-94.00-15.00-exact",
-           "randst/0.25-18.60-28.60-94.00-15.00-full_array",
-           "stad/0.25-2.35-1.32-0.00-15.00-exact",
-           "stad/0.25-2.35-1.32-0.00-15.00-full_array",
-           "stad/0.25-2.92-1.18-0.00-15.00-exact",
-           "stad/0.25-2.92-1.18-0.00-15.00-full_array",
+arg_set = ["randst/0.40-18.50-18.50-95.00-15.00-exact",
+           "randst/0.40-18.50-18.50-95.00-15.00-full_array",
+           "randst/0.40-18.60-28.60-94.00-15.00-exact",
+           "randst/0.40-18.60-28.60-94.00-15.00-full_array",
+           "stad/0.40-2.35-1.32-0.00-15.00-exact",
+           "stad/0.40-2.35-1.32-0.00-15.00-full_array",
+           "stad/0.40-2.92-1.18-0.00-15.00-exact",
+           "stad/0.40-2.92-1.18-0.00-15.00-full_array",
            "p/3.00-0.50-0.00-0.00-15.00-exact",
            "p/3.00-0.50-0.00-0.00-15.00-full_array"]
 
 bound_times = [500,850,500,850,500,850,500,850,500,850,500,850,500,850,500,850,500,750,500,750]
-arrow_goals = [13, 12, 10, 11, 13, 12, 13, 15, 12, 10]
+#arrow_goals = [13, 12, 10, 11, 13, 12, 13, 15, 12, 10]
+arrow_goals = [10, 12, 11, 10, 12, 13, 11, 12, 12, 10]
 
 row_0y = 0.0          # 1.0
[…]

### 2015-03-16 protein.h

@@ -21,8 +21,9 @@ const double rate_E = .093; // (um)^3 s^-1
 
 enum reaction {ADP_to_ATP, DE_to_ADP_E, ATP_to_D, E_D_to_DE, X_ADP_pos, X_ADP_neg, Y_ADP_pos, Y_ADP_neg, Z_ADP_pos,
                Z_ADP_neg, X_ATP_pos, X_ATP_neg, Y_ATP_pos, Y_ATP_neg, Z_ATP_pos, Z_ATP_neg, X_E_pos, X_E_neg,
-               Y_E_pos, Y_E_neg, Z_E_pos, Z_E_neg};
-const int num_pos_reactions = Z_E_neg+1;
+               Y_E_pos, Y_E_neg, Z_E_pos, Z_E_neg, X_MemD_pos, X_MemD_neg, Y_MemD_pos, Y_MemD_neg, Z_MemD_pos, Z_MemD_neg,
+               X_MemDE_pos, X_MemDE_neg, Y_MemDE_pos, Y_MemDE_neg, Z_MemDE_pos, Z_MemDE_neg};
+const int num_pos_reactions = Z_MemDE_neg+1;
 const int d[6][3] =
   {
     {1,0,0},

### 2015-03-16 protein_membrane.cpp

@@ -135,19 +135,19 @@ double mem_f(double x, double y, double z) {
     else if(mem_f_shape=="TIE_fighter") f_2d = f_2D_TIE_fighter(y,z);
     else if(mem_f_shape=="randst") {
       f_2d = f_2D_randst(y,z);
-      for (double yd = y-((A-.25)/2.0); yd <= y+((A-.25)/2.0); yd+=dx/4.0) {
-        for (double zd = z-((A-.25)/2.0); zd <= z+((A-.25)/2.0); zd+=dx/4.0) {
-          if (f_2D_randst(yd,zd) > 0.0) f_2d = 0.1;
-        }
-      }
+      // for (double yd = y-((A-.25)/2.0); yd <= y+((A-.25)/2.0); yd+=dx/4.0) {
+      //   for (double zd = z-((A-.25)/2.0); zd <= z+((A-.25)/2.0); zd+=dx/4.0) {
+      //     if (f_2D_randst(yd,zd) > 0.0) f_2d = 0.1;
+      //   }
+      // }
     }
     else if(mem_f_shape=="stad") {
       f_2d = f_2D_stad(y,z);
-      for (double yd = y-((A-.25)/2.0); yd <= y+((A-.25)/2.0); yd+=dx/4.0) {
-        for (double zd = z-((A-.25)/2.0); zd <= z+((A-.25)/2.0); zd+=dx/4.0) {
-          if (f_2D_stad(yd,zd) > 0.0) f_2d = 0.1;
-        }
-      }
+      // for (double yd = y-((A-.25)/2.0); yd <= y+((A-.25)/2.0); yd+=dx/4.0) {
+      //   for (double zd = z-((A-.25)/2.0); zd <= z+((A-.25)/2.0); zd+=dx/4.0) {
+      //     if (f_2D_stad(yd,zd) > 0.0) f_2d = 0.1;
+      //   }
+      // }
     }
     else {
       printf("somethings wrong with the shape argument!!!");
@@ -168,19 +168,19 @@ double mem_f(double x, double y, double z) {
           if(mem_f_shape=="triangle") f0 = f_2D_triangle(y0,z0);
           if(mem_f_shape=="randst") {
             f0 = f_2D_randst(y0,z0);
-            for (double yd = y0-((A-.25)/2.0); yd <= y0+((A-.25)/2.0); yd+=dx/4.0) {
-              for (double zd = z0-((A-.25)/2.0); zd <= z0+((A-.25)/2.0); zd+=dx/4.0) {
[…]

### 2015-03-16 pyplots/density-correlation.py

@@ -30,35 +30,40 @@ longest_data_len = 0
 
 
 def adjust_data_files(sim_type):
-    if sim_type == "full_array" and sys.argv[1] == "stad" and sys.argv[3] == "2.92":
-        return [0,1,2,3,4,5]
-    elif sim_type == "full_array":
-        return [10,0,1,2,3,4,5]
+    print sim_type
+    if sim_type == "full_array":
+        if sys.argv[1] == "stad":
+            return [10,0,1,2]
+        elif sys.argv[1] == "randst":
+            return [10,0,1,2]
     else:
-        data_files = [0,1,2,3,4,5]
-        longest_data_size = 0
-        longest_data_num = 30
-        for i in data_files:
-            job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (sys.argv[1],sys.argv[2],sys.argv[3],sys.argv[4],
-                                                               sys.argv[5],sys.argv[6],sim_type)
-            p = re.compile('[.]')
-            job_string = p.sub('_',job_string)
-            data_file = ''
-            if i == 10:
-                data_file = job_string + 'box-plot.dat'
-            else:
-                data_file = '../new-protein-%d/'%(i) + job_string + 'box-plot.dat'
-                if not os.path.isfile(data_file):
-                    print '\n',data_file, ' doesnt exist so we cant load it'
-                    exit(0)
-            data = np.loadtxt(data_file, converters = {0:ignoreme, 1:ignoreme})
-            print 'total time covered by file = ',len(data[0])*dt
-            if len(data[0]) > longest_data_size:
-                longest_data_size = len(data[0])
-                longest_data_num = i
-    print 'longest data number is %d and it covers %g seconds of data'%(longest_data_num,longest_data_size*dt)
-    return [longest_data_num]
-
+        return [10]
+    #     data_files = [10]
+    #     print "full array directories used are:"
+    #     for d in data_files:
+    #         print 'data files using are ',d
+    #     longest_data_size = 0
+    #     longest_data_num = 30
+    #     for i in data_files:
+    #         job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (sys.argv[1],sys.argv[2],sys.argv[3],sys.argv[4],
+    #                                                            sys.argv[5],sys.argv[6],sim_type)
+    #         p = re.compile('[.]')
+    #         job_string = p.sub('_',job_string)
+    #         data_file = ''
[…]

### 2015-03-16 pyplots/intel-correlation-plot.py

@@ -116,7 +116,7 @@ for i in range(1,num_plots):
     print 'period ',period
     pylab.plot(time_array,data_full[i],colors[i],label='stochastic')
     pylab.xlim(0,time_array[-1])
-    #pylab.ylim(np.amin(data_full[i]),np.amax(data_full[i]))
+    pylab.ylim(np.amin(data_full[i]),np.amax(data_full[i]))
 
 if not plot_final_version:
     pylab.plot(time_array,decay,colors[0],label='decay')
@@ -126,11 +126,11 @@ pylab.title(r'%s %s $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
 if sys.argv[1] == 'randst' and sys.argv[5] == '95.00':
     #pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
     #            % (1/rate, period, 1/(rate*period)))
-    pylab.title(r'Temporal correlation of shape A')
+    pylab.title(r'Temporal correlation of shape A,  $\tau_c = %.3g$ sec'%(1/rate))
 elif sys.argv[1] == 'stad' and sys.argv[4] == '1.32':
     #pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
     #            % (1/rate, period, 1/(rate*period)))
-    pylab.title(r'Temporal correlation of stadium A')
+    pylab.title(r'Temporal correlation of stadium A,  $\tau_c = %.3g$ sec'%(1/rate))
 elif sys.argv[1] == 'p':
     #pylab.title(r'pill-shaped cell, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
     #            % (1/rate, period, 1/(rate*period)))
@@ -144,23 +144,29 @@ colors = ['k:','r:','m--.']
 for i in range(1,num_plots):
     pylab.plot(time_array,data_exact[i],colors[i],label='deterministic')
     pylab.xlim(0,time_array[-1])
-    #pylab.ylim(np.amin(data_exact[i]),np.amax(data_exact[i]))
+    pylab.ylim(np.amin(data_exact[i]),np.amax(data_exact[i]))
 
 pylab.ylabel(r'$C(\tau)$')
 plt.xlabel(r'$\tau$ (sec)')
 plt.legend()
 
[…]

### 2015-03-16 pyplots/intel-single-image-plot.py

@@ -1,0 +1,114 @@
+from __future__ import division
+import numpy as np
+import matplotlib
+matplotlib.use('Agg')
+import matplotlib.pyplot as plt
+import os
+import sys
+import time
+import file_loader as load
+import Image
+import math
+import re
+import mycolormap
+
+f_shape = sys.argv[1]
+f_param1 = sys.argv[2]
+f_param2 = sys.argv[3]
+f_param3 = sys.argv[4]
+f_param4 = sys.argv[5]
+dens_factor = sys.argv[6]
+sim_type = sys.argv[7]
+f_param6 = sys.argv[8]
+f_param7 = sys.argv[9]
+
+dump_time_step = 0.5
+skip_times = 2 # only plot every skip_times of the snapshots (which are seperated by dump_time_steps (.5) simulation seconds.)
+start_time = float(f_param6)
+end_time = float(f_param7)
+
+job_string = "data/shape-%s/%s-%s-%s-%s-%s-%s/" % (load.f_shape,load.f_param1,load.f_param2,
+                                                   load.f_param3,load.f_param4,load.f_param5,sim_type)
+p = re.compile('[.]')
+job_string = p.sub('_',job_string)
+
+proteinList = ["ND","NDE"]
+proteinLabels = ["MinD:ADP (cyto)","MinD:ATP (cyto)","MinD:ATP (mem)","MinD:MinE:ATP (mem)","MinD:E (cyto)",]
+
+plt.figure(figsize=(9,3.5))
+times  = np.arange(float(start_time),float(end_time),1.0)
+print "Starting single image plot."
+print times
+
+
+#computes the global maximum over a set of two dimensional arrays (stored as files)
+def timemax(data):
+    return max([v.max() for v in data])
+
+plt.figure(figsize=(9,3.5))
+numtimes = int(end_time/dump_time_step)- int(start_time/dump_time_step)
+numproteins = len(proteinList)
+
+#axes = plt.subplot(1, 1, 1, axisbg='black')
+
+for i in range(len(proteinList)):
+    print proteinList[i]
+    nlevels = 20
+#generate a sequence of .png's for each file (printed time step). these will be used to create a gif.
+    smeared_data = [0]*len(times)
+    for j in range(len(times)):
+        image_data_file = job_string +str(proteinList[i])+'/images/single-'+str(times[j])+'.dat'
[…]

### 2015-03-16 quick-lazy-script.sh

@@ -1,0 +1,27 @@
+#!/bin/bash
+
+echo '\n'
+echo ls -trlh data/shape-randst/0_40-18_60-28_60-94_00-15_00-exact/
+ls -trlh data/shape-randst/0_40-18_60-28_60-94_00-15_00-exact/
+echo '\n'
+echo ls -trlh data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/
+ls -trlh data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/
+echo '\n'
+echo ls -trlh data/shape-randst/0_40-18_50-18_50-95_00-15_00-exact/
+ls -trlh data/shape-randst/0_40-18_50-18_50-95_00-15_00-exact/
+echo '\n'
+echo ls -trlh data/shape-randst/0_40-18_50-18_50-95_00-15_00-full_array/
+ls -trlh data/shape-randst/0_40-18_50-18_50-95_00-15_00-full_array/
+echo '\n'
+echo ls -trlh data/shape-stad/0_40-2_92-1_18-0_00-15_00-exact/
+ls -trlh data/shape-stad/0_40-2_92-1_18-0_00-15_00-exact/
+echo '\n'
+echo ls -trlh data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/
+ls -trlh data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/
+echo '\n'
+echo ls -trlh data/shape-stad/0_40-2_35-1_32-0_00-15_00-exact/
+ls -trlh data/shape-stad/0_40-2_35-1_32-0_00-15_00-exact/
+echo '\n'
+echo ls -trlh data/shape-stad/0_40-2_35-1_32-0_00-15_00-full_array/
+ls -trlh data/shape-stad/0_40-2_35-1_32-0_00-15_00-full_array/
+

### 2015-03-16 run_simulations.sh

@@ -1,5 +1,27 @@
 #!/bin/bash
 
+
+srun --mem=7000 --job-name="sim randst 0.40 18.60 94.00 1.42 exact" ./protein_microscopy randst 0.40 18.60 28.60 94.00 15.00 1.42 exact -dump &
+#srun --job-name="sim randst 0.40 18.50 95.00 1.35 exact" ./protein_microscopy randst 0.40 18.50 18.50 95.00 15.00 1.35 exact -dump &
+
+# srun --job-name="sim randst 0.40 18.50 95.00 1.35 full" ./protein_microscopy randst 0.40 18.50 18.50 95.00 15.00 1.35 full_array -dump &
+# srun --job-name="sim randst 0.40 18.50 95.00 1.35 exact" ./protein_microscopy randst 0.40 18.50 18.50 95.00 15.00 1.35 exact -dump &
+# srun --job-name="sim randst 0.40 18.60 94.00 1.42 exact" ./protein_microscopy randst 0.40 18.60 28.60 94.00 15.00 1.42 exact -dump &
+
+
+# srun --job-name="sim randst 0.40 18.50 18.50 95.00 15.00 1.35 full" ./protein_microscopy randst 0.40 18.50 18.50 95.00 15.00 1.35 full_array -dump &
+
+
+# srun --job-name="sim randst 0.40 18.60 28.60 94.00 15.00 1.53 full" ./protein_microscopy randst 0.40 18.60 28.60 94.00 15.00 1.53 full_array -dump &
+# srun --job-name="sim randst 0.40 18.60 28.60 94.00 15.00 1.53 exact" ./protein_microscopy randst 0.40 18.60 28.60 94.00 15.00 1.53 exact -dump &
+
+#srun --job-name="sim stad 0.40 2.35 1.32 15.00 full" ./protein_microscopy stad 0.40 2.35 1.32 0.00 15.00 1.0 full_array -dump &
+#srun --job-name="sim stad 0.40 2.35 1.32 15.00 exact" ./protein_microscopy stad 0.40 2.35 1.32 0.00 15.00 1.0 exact -dump &
+
+#srun --job-name="sim stad 0.40 2.92 1.18 15.00 full" ./protein_microscopy stad 0.40 2.92 1.18 0.00 15.00 1.0 full_array -dump &
[…]

### 2015-03-16 paper/paper-MinD.tex
a few edits to paper Tested everything on crystal.

@@
 recruited to the membrane by MinD that is already clustered there
-(following observed non-linear attachment of MinD on the cell
+(following experimentally observed non-linear attachment of MinD on the cell
 membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
@@
 point in space to the closest wall.  The Dirac delta function
-$\delta(d_w)$, which we need to describe the location of the membrane,
+$\delta(d_w)$, which we use to describe the location of the membrane,
 has units of $\micron^{-1}$ and is zero everywhere except at the wall.
@@
 same number of proteins per unit volume.  These concentration values
-are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. \blue{(1,2)}
-We have chosen to write our own simulation platform and membrane
-creation tools from scratch, instead of using existing available
-software used in previous studies\fixme{cite previous studies}. We
-believe there is value in re-creating results with alternative
-software.  Our simulations take place within a three-dimensional
-Cartesian grid that has a grid spacing of .05\micron, and our cell
-shapes are specified by positions and thicknesses of a series of
-gaussians.  Our code is publically available on github.com~\fixme{cite
+are $1273\micron^{-3}$ and $446\micron^{-3}$,
+respectively. \blue{(1,2)} We have chosen to write our own simulation
+platform and membrane creation tools from scratch, instead of using
+existing available software used in previous studies\fixme{cite
+  previous studies}. We believe there is value in re-creating results
+with alternative software.  Our simulations take place within a
+three-dimensional Cartesian grid that has a grid spacing of
+.05\micron, and our cell shapes are specified as the zero of an
+analytic function which can generate the geometry presented in this
+paper.  Our code is publically available on github.com~\fixme{cite
   github account in references?}
@@
 Mannik \emph{et al.}, in which bacteria are confined within thin
-slits.  \blue{(6)}These slits begin with a width of .25\micron, but
-they are coated with a PDMS lining that the cells are able to deform,
-while tests with pure silicon, non-deformable slits show that the
-greatest thickness for which cells are able to penetrate is
+slits.  \blue{(6)}These slits are fabricated with a width of
+.25\micron, but they are coated with a PDMS lining that the cells are
+able to deform, raising uncertainty in the actual cell thickness.
+Tests with pure silicon, non-deformable slits show that the greatest
+thickness for which cells are able to penetrate is
 .4\micron~\cite{mannik2012robustness,mannik2009bacterial}.  We
 therefore assume that the PDMS slits have been deformed to this
-thickness and here simulate flattened cells with a thickness of
-.4\micron.  Viewed from the top down the cells have the shapes
-described below and viewed from the side they have at their edges a
-semicircular protrusion (one may imagine the shape of a pancake).
+thickness and simulate flattened cells with a thickness of .4\micron.
+Viewed from the top down the cells have the shapes described below and
+viewed from the side they have at their edges a semicircular
+cross-section (one may imagine the shape of a pancake).
 %
@@
     stochastic models are shown.  The stochastic model shows an
-    oscillation period of \fixme{following not correct anymore} 39.5
-    seconds and coherence time of 307 seconds.  The correlation
-    functions are scaled to have the same initial value.}
+    oscillation period of 39.5 seconds and coherence time of 307
+    seconds.  The correlation functions are scaled to have the same
+    initial value.}
   \label{corr-pill}
@@
 it is the flattening of the cells rather than their irregular shape
-that primarily causes the disruption of regular bipolar oscillation
-which is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.
+viewed from above that primarily causes the disruption of regular
+bipolar oscillation which is observed by Mannik \emph{et
+  al.}~\cite{mannik2012robustness}.
 

### 2015-03-16 paper/paper-MinD.tex
eddited stability analysis in paper Tested everything on crystal.

@@
 stability analysis on an infinite slab with a thickness equal to that
-of our flattened cells ($0.25\micron$) and have found that an
-equivalent stability limit for half wavelength is $2.13\micron$. As
-expected, when decreasing the lengths and widths of our simulated
-flattened cells so that the longest distance across the cell is less
-than this length, the cells stop exhibiting any oscillatory behavior.
-The deterministic model relaxes into a motionless state and the
-stochastic model exhibits random fluctuations without spatial
-oscillations.
+of our flattened cells ($0.40\micron$).  We first solve the model's
+five differential equations for the steady state solution, using for
+our concentrations of MinD and MinE the same as the total in
+simulation.  We then add small, spatially harmonic density
+perturbations to the density, throwing away any terms that are
+nonlinear in perturbation.  The sign of the eigenvalues of the
+resulting matrix informs us whether harmonic perturbations at a
+specified wavelength will evolve toward the steady state solution or
+not, so picking a wavelength that ensures all eigenvalues are of the
+correct sign allows for an upper stability limit. Through this method
+we arrive at an upper half wavelength stability limit of $1.56\micron$
+for our $0.40\micron$ flattened cells. As expected, when decreasing
+the lengths and widths of our simulated flattened cells so that the
+longest distance across the cell is less than this length, the cells
+stop exhibiting any oscillatory behavior.  The deterministic model
+relaxes into a motionless state and the stochastic model exhibits
+random fluctuations without spatial oscillations.
 

### 2015-03-16 paper/paper-MinD.tex
change to title of section in paper Tested everything on crystal.

@@
 
-\section{Comparison of Mannik's Experimental and Our Stadium Shapes}
+\section{Comparison of Experimental and Stadium Shapes}
 As described in Section~\ref{sec:model-method-shapes}, we will focus

### 2015-03-16 paper/paper-MinD.tex
edit stability analysis section Tested everything on bennet.

@@
 on a steady state solution of a $2\micron$ half wavelength.  Cells
-with dimensions longer than this show spontaneous oscillatory behavior
-in this direction, while cells that are shorter relax into a
-motionless steady state.  We have similarly performed a linear
-stability analysis on an infinite slab with a thickness equal to that
-of our flattened cells ($0.40\micron$).  We first solve the model's
-five differential equations for the steady state solution, using for
-our concentrations of MinD and MinE the same as the total in
-simulation.  We then add small, spatially harmonic density
-perturbations to the density, throwing away any terms that are
-nonlinear in perturbation.  The sign of the eigenvalues of the
-resulting matrix informs us whether harmonic perturbations at a
-specified wavelength will evolve toward the steady state solution or
-not, so picking a wavelength that ensures all eigenvalues are of the
-correct sign allows for an upper stability limit. Through this method
-we arrive at an upper half wavelength stability limit of $1.56\micron$
-for our $0.40\micron$ flattened cells. As expected, when decreasing
-the lengths and widths of our simulated flattened cells so that the
-longest distance across the cell is less than this length, the cells
-stop exhibiting any oscillatory behavior.  The deterministic model
-relaxes into a motionless state and the stochastic model exhibits
-random fluctuations without spatial oscillations.
+with dimensions longer than this spontaneously develop spatial
+oscillations, while cells that are shorter relax into a homogeneous
+steady state.  We have performed a similar linear stability analysis
+on an infinite slab with a thickness equal to that of our flattened
+cells ($0.40\micron$).  We first solve the model's five differential
+equations for the steady state solution, under the constraint that the
+total number MinD and MinE molecules matches our simulation.  We write
+down as a matrix the linear response of the time derivatives of the
+density to small, spatially harmonic density perturbations around the
+steady-state density.  The system is stable at this wavelength
+provided all eigenvalues of the matrix are negative, indicating that
+all perturbations with this wavelength will decay.  We find the
+stability limit by searching for the largest wavelength at which the
+system is stable.  Through this method we arrive at an upper half
+wavelength stability limit of $1.56\micron$ for our $0.40\micron$
+flattened cells. As expected, when decreasing the lengths and widths
+of our simulated flattened cells so that the longest distance across
+the cell is less than this length, the cells stop exhibiting any
+oscillatory behavior.  The deterministic model relaxes into a
+motionless state and the stochastic model exhibits random fluctuations
+without spatial oscillations.
 

### 2015-03-17 paper/paper-MinD.tex
switched changes over to plos.tex, adjusted figures to fit better Tested everything on crystal.

@@
     \begin{enumerate}
-    \item Lacks diffusion on the membrane. Supported by Meacci 2006,
-      which experimentally tries to measure diffusion on membrane, has
-      a tough time, but shows that definitely diffuses.
+    \item \blue{David.  I've added a paragraph discussing the starry
+      night in the context of the membrane diffusion.  I didn't say
+      anything about a one half period allowing diffusion to smear an
+      entire pole, because it seems to contradict the next paragraph.
+      What do you think?} Lacks diffusion on the membrane. Supported
+      by Meacci 2006, which experimentally tries to measure diffusion
+      on membrane, has a tough time, but shows that definitely
+      diffuses.
     \item Underestimates diffusion in cytoplasm by a factor of 5-6.5.
@@
 are $1273\micron^{-3}$ and $446\micron^{-3}$,
-respectively. \blue{(1,2)} We have chosen to write our own simulation
+respectively.  We have chosen to write our own simulation
 platform and membrane creation tools from scratch, instead of using
 existing available software used in previous studies\fixme{cite
-  previous studies}. We believe there is value in re-creating results
-with alternative software.  Our simulations take place within a
+  previous studies} (we believe there is value in re-creating results
+with alternative software).  Our simulations take place within a
 three-dimensional Cartesian grid that has a grid spacing of
@@
 
-It is clear from Fig.~\ref{image-p} that the stochastic simulation
+\blue{(5a)} Both Fig.~\ref{image-p} and its associated movies (see
+supplementary material), show that the stochastic model exhibits a
+``starry night'' effect characterized by spatially fixed points of
+protein density build up, as recruitment leads to clusters of MinD
+forming on the wall and then subsequently dissipating.  We attribute
+this effect to the fact that the Huang model does not include
+diffusion along the membrane, which has been experimentally verified
+yet found to be two orders of magnitude less than diffusion in the
+cytoplasm~\cite{meacci2005min}. Even ignoring this effect, however, it
+is clear from Fig.~\ref{image-p} that the stochastic simulation
 results in a protein distribution that is less spatially regular than
-the deterministic model predicts.  In fact, when viewed as a movie
-(see supplementary material), the stochastic model exhibits a ``starry
-night'' effect, as recruitment leads to clusters of MinD forming on
-the wall and then subsequently dissipating.  \fixme{Talk about
-  membrane diffusion blurring out the starry night.}  This naturally
-leads to irregularity in the temporal periodicity of the system, which
-we quantify by examining the temporal correlation function of the
-total MinD found in two opposite polar regions.
+the deterministic model predicts.  This naturally leads to
+irregularity in the temporal periodicity of the system, which we
+quantify by examining the temporal correlation function of the total
+MinD found in two opposite polar regions.
 %
@@
 in the location of the maxima when using the stochastic model.  The
-deterministic model shows uniformly bipolar oscillation, with the
-exception of shape \emph{B}, which develops weak intermediate maxima
-on the right-hand edge of the cell.  From these results, we conclude
-that the deterministic model is inadequate to explain experimental
-observations of the locations of density maxima of the MinD protein.
+deterministic model shows uniformly bipolar oscillation.  From these
+results, we conclude that the deterministic model is inadequate to
+explain experimental observations of the locations of density maxima
+of the MinD protein.
 

### 2015-03-17 paper/plos.tex
switched changes over to plos.tex, adjusted figures to fit better Tested everything on crystal.

@@
 \newcommand\micron{\ensuremath{\mu\text{m}}}
-\newcommand{\red}[1]{{\bf \color{red} #1}}
+%%\newcommand{\red}[1]{{\bf \color{red} #1}}
 \newcommand{\fixme}[1]{\red{[#1]}}
@@
 %% END MACROS SECTION
+\newcommand{\red}[1]{{\bf \color{red} #1}}
+\newcommand{\blue}[1]{{\bf \color{blue} #1}}
+\newcommand{\green}[1]{{\bf \color{green} #1}}
 
@@
 
+\red{Huh}
+
 \fixme{
@@
     \begin{enumerate}
-    \item Lacks diffusion on the membrane
+    \item \blue{David.  I've added some sentences discussing the
+      starry night in the context of the membrane diffusion.  I didn't
+      say anything about a one half period allowing diffusion to smear
+      an entire pole, because it seems to contradict the second part
+      of this paragraph.  What do you think?} Lacks diffusion on the
+      membrane. Supported by Meacci 2006, which experimentally tries
+      to measure diffusion on membrane, has a tough time, but shows
+      that definitely diffuses.
     \item Underestimates diffusion in cytoplasm by a factor of 5-6.5.
+      Supported by Meacci 2006, who concludes a rate of 16 microns
+      squared per sec for MinD and 10 microns squared per sec for
+      MinE.
     \item Uses MinD-ADP -> MinD-ATP that is 3 times lower than
-      experimental bound.
+      experimental bound. Halatek uses ADP->ATP of 1/6 s-1. They cite
+      Meacci 2006, who state that there is a lower bound on reference
+      time of 3 seconds, so this constant has an upper bound of 1/3
+      s-1.
     \item (Still debated) No evidence that DE recruits to membrane.
@@
   \item Height should be bigger to compare with experiment.  0.4-0.6
-    microns.  \textcolor{blue}{HIGH PRIORITY!!! to figure this out}
-
-    The 0.25 micron height of the cells used in this study does not
-    represent the experimental settings well. The simulations are
-    based on the flattened cell shapes reported from the experiments
-    by Mannik et al 2009 and 2012. In these experimental studies,
-    E. coli were shown to be able to grow in channels as low as 0.6
-    micron in hard silicon structures, and no more than 0.4 micron
-    (see Mannik 2009). Indeed, 0.25 micron channels were constructed
-    with PDMS ceilings, which is a rather flexible polymer allowing
-    bacteria to deform it to effectively higher channels. Thus the
-    simulations would be more realistic if performed in the range of
-    0.4-0.6 micron thickness.
+    microns.  The 0.25 micron height of the cells used in this study
+    does not represent the experimental settings well. The simulations
+    are based on the flattened cell shapes reported from the
+    experiments by Mannik et al 2009 and 2012. In these experimental
+    studies, E. coli were shown to be able to grow in channels as low
+    as 0.6 micron in hard silicon structures, and no more than 0.4
+    micron (see Mannik 2009). Indeed, 0.25 micron channels were
+    constructed with PDMS ceilings, which is a rather flexible polymer
+    allowing bacteria to deform it to effectively higher
+    channels. Thus the simulations would be more realistic if
+    performed in the range of 0.4-0.6 micron thickness.
 
@@
   \item Add details of the linear stability analysis.
+  \item (From jeff): still need to fix periods on correlation plots
   \end{enumerate}
@@
 have experimentally forced \emph{E. coli} cells into microfabricated
-channels of $0.25\micron$ thickness, in which they area able to grow
-and divide. The channels, which are covered in a layer of PDMS, are
-deformable to some degree.  Experiments with a different geometry that
-is constructed without PDMS show that it's reasonable to assume the
-bacteria deform the PDMS channels to a thickness of at least
-$0.4\micron$~\cite{mannik2009bacterial,mannik2010bacteria}.
-
-Upon entering the channels, the cells undergo a mechanical deformation
-in which they both widen and lengthen within the plane of the channel.
-This deformation results in very wide (they can reach widths of over
+channels of thickness less than that of the natural diameter of the
+cells, in which they area able to grow and divide. Upon entering the
+channels, the cells undergo a mechanical deformation in which they
+both widen and lengthen within the plane of the channel.  This
+deformation results in very wide (they can reach widths of over
 $5\micron$) flattened cells that when viewed from the top down have
@@
 
-%% Lorem ipsum dolor sit~\cite{huang2003dynamic} amet, consectetur
-%% adipiscing elit. Curabitur eget porta erat. Morbi consectetur est vel
-%% gravida pretium. Suspendisse ut dui eu ante cursus gravida non sed
-%% sem. Nullam Eq.~(\ref{eq:schemeP}) sapien tellus, commodo id velit id,
-%% eleifend volutpat quam. Phasellus mauris velit, dapibus finibus
-%% elementum vel, pulvinar non tellus. Nunc pellentesque pretium diam,
-%% quis maximus dolor faucibus id.~\cite{mannik2009bacterial} Nunc
-%% convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet
-%% enim ultrices, ultrices elit pulvinar, volutpat risus.
-%% \begin{equation}\label{eq:schemeP}
-%% D_{coll} = \frac{D_f+\frac{[S]^2}{K_D S_T} D_S} {1+\frac{[S]^2}{K_D S_T}},
-%% D_{sm} = \frac{D_f+ \frac{[S]}{K_D} D_S}{1+\frac{[S]}{K_D}},
-%% \end{equation}
-
 % You may title this section "Methods" or "Models". 
@@
 
-\begin{multline}
-  \frac{\partial \rho_{D:ADP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ADP}-k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
-  +\delta(d_w)k_{de}\sigma_{DE},\hspace{3.4cm}
-\end{multline}
-\begin{multline}
-  \frac{\partial \rho_{D:ATP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ATP}+k_D^{ADP\rightarrow ATP}\rho_{D:ADP}\\
-  -\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
-\end{multline}
-\begin{multline}
+\begin{align}
+  \frac{\partial \rho_{D:ADP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ADP}-k_D^{ADP\rightarrow ATP}\rho_{D:ADP}+\delta(d_w)k_{de}\sigma_{DE},\hspace{3.4cm}
+\end{align}
+\begin{align}
+  \frac{\partial \rho_{D:ATP}}{\partial t} = \mathcal{D}_D\nabla^2\rho_{D:ATP}+k_D^{ADP\rightarrow ATP}\rho_{D:ADP}-\delta(d_w)[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
+\end{align}
+\begin{align}
   \frac{\partial \rho_E}{\partial t} = \mathcal{D}_E\nabla^2\rho_E+\delta(d_w)k_{de}\sigma_{DE}
   -\delta(d_w)k_E \sigma_D \rho_E
-\end{multline}
-\begin{multline}
-  \frac{\partial \sigma_D}{\partial t} = -k_E\sigma_D\rho_E
+\end{align}
+\begin{align}
+  \frac{\partial \sigma_D}{\partial t} &= -k_E\sigma_D\rho_E
   +[k_D+k_{dD}(\sigma_D+\sigma_{DE})]\rho_{D:ATP}
   \label{eq:d-on-wall}
-\end{multline}
-\begin{multline}
-  \frac{\partial \sigma_{DE}}{\partial t} = -k_{de}\sigma_{DE}+k_E\sigma_D\rho_E\hspace{3cm}
+\end{align}
+\begin{align}
+  \frac{\partial \sigma_{DE}}{\partial t} &= -k_{de}\sigma_{DE}+k_E\sigma_D\rho_E\hspace{3cm}
   \label{eq:FifthPDE}
-\end{multline}
+\end{align}
 where $\rho$ is cytoplasmic protein density (proteins$/\micron^{3}$), $\sigma$
@@
 same number of proteins per unit volume.  These concentration values
-are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We perform
-simulations with a 3D grid in Cartesian coordinates that has a grid
-spacing of .05\micron.
+are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We have
+chosen to write our own simulation platform and membrane creation
+tools from scratch, instead of using existing available software used
+in previous studies\fixme{cite previous studies} (we believe there is
+value in re-creating results with alternative software).  Our
+simulations take place within a three-dimensional Cartesian grid that
+has a grid spacing of .05\micron, and our cell shapes are specified as
+the zero of an analytic function which can generate the geometry
+presented in this paper.  Our code is publically available on
+github.com~\fixme{cite github account in references? Yes!}
 
@@
 Mannik \emph{et al.}, in which bacteria are confined within a thin
-slit of height $0.25\micron$ ~\cite{mannik2012robustness}.  Viewed
-from the top down the cells have the shapes described below and viewed
-from the side they have at their edges a semicircular protrusion (one
-may imagine the shape of a pancake).
+slits.  These slits are fabricated with a width of .25\micron, but
+they are coated with a PDMS lining that the cells are able to deform,
+raising uncertainty in the actual cell thickness.  Tests with pure
+silicon, non-deformable slits show that the greatest thickness for
+which cells are able to penetrate is
+.4\micron~\cite{mannik2012robustness,mannik2009bacterial}.  We
+therefore assume that the PDMS slits have been deformed to this
+thickness and simulate flattened cells with a thickness of .4\micron.
+Viewed from the top down the cells have the shapes described below and
+viewed from the side they have at their edges a semicircular
+cross-section (one may imagine the shape of a pancake).
 %
@@
   \begin{center}
+    \hspace{-3.5cm}
     \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
     \vspace{-1.5em}
+    \hspace{-3.5cm}
     \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
@@
 on a steady state solution of a $2\micron$ half wavelength.  Cells
-with dimensions longer than this show spontaneous oscillatory behavior
-in this direction, while cells that are shorter relax into a
-motionless steady state.  We have similarly performed a linear
-stability analysis on an infinite slab with a thickness equal to that
-of our flattened cells ($0.25\micron$) and have found that an
-equivalent stability limit for half wavelength is $2.13\micron$. As
-expected, when decreasing the lengths and widths of our simulated
-flattened cells so that the longest distance across the cell is less
-than this length, the cells stop exhibiting any oscillatory behavior.
-The deterministic model relaxes into a motionless state and the
-stochastic model exhibits random fluctuations without spatial
-oscillations.
-
-%% Nulla mi mi, Figure~\ref{fig1} venenatis sed ipsum varius, volutpat
-%% euismod diam. Proin rutrum vel massa non gravida. Quisque tempor sem
-%% et dignissim rutrum. Lorem ipsum dolor sit amet, consectetur
-%% adipiscing elit. Morbi at justo vitae nulla elementum commodo eu id
-%% massa. In vitae diam ac augue semper tincidunt eu ut eros. Fusce
-%% fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel
-%% sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id,
-%% cursus neque. Praesent faucibus semper libero.
-
-%% \begin{figure}[h]
-%% \caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis
-%%     sed ipsum varius, volutpat euismod diam.}  Figure Caption Proin
-%%   rutrum vel massa non gravida. Quisque tempor sem et dignissim
-%%   rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing
-%%   elit.}
-%% \label{fig1}
-%% \end{figure}
-
-%% \begin{enumerate}
-%% \item{react}
-%% \item{diffuse free particles}
-%% \item{increment time by dt and go to 1}
-%% \end{enumerate}
+with dimensions longer than this spontaneously develop spatial
+oscillations, while cells that are shorter relax into a homogeneous
+steady state.  We have performed a similar linear stability analysis
+on an infinite slab with a thickness equal to that of our flattened
+cells ($0.40\micron$).  We first solve the model's five differential
+equations for the steady state solution, under the constraint that the
+total number MinD and MinE molecules matches our simulation.  We write
+down as a matrix the linear response of the time derivatives of the
+density to small, spatially harmonic density perturbations around the
+steady-state density.  The system is stable at this wavelength
+provided all eigenvalues of the matrix are negative, indicating that
+all perturbations with this wavelength will decay.  We find the
+stability limit by searching for the largest wavelength at which the
+system is stable.  Through this method we arrive at an upper half
+wavelength stability limit of $1.56\micron$ for our $0.40\micron$
+flattened cells. As expected, when decreasing the lengths and widths
+of our simulated flattened cells so that the longest distance across
+the cell is less than this length, the cells stop exhibiting any
+oscillatory behavior.  The deterministic model relaxes into a
+motionless state and the stochastic model exhibits random fluctuations
+without spatial oscillations.
 
@@
   \centering
+  \hspace{-3cm}
   \includegraphics[width=16cm]{../paper/plot-ave}
@@
     stochastic model shows an oscillation period of 53.1 seconds and
-    coherence time of 246 seconds, so that it takes roughly 4.6 periods
-    for the behavior to decohere.  For the stadium \emph{A}, the same
-    model shows an oscillation period of 51 seconds and coherence time of
-    323 seconds, so that it takes roughly 6.3 periods for the behavior
-    to decohere.}
+    coherence time of 246 seconds, so that it takes roughly 4.6
+    periods for the behavior to decohere.  For the stadium \emph{A},
+    the same model shows an oscillation period of 51 seconds and
+    coherence time of 323 seconds, so that it takes roughly 6.3
+    periods for the behavior to decohere.}
   \label{fig:corr-pancake-A}
@@
 
-%% \begin{table}[!ht]
-%% \begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
-%% \caption{
-%% {\bf Table caption Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.}}
-%% \begin{tabular}{|l|l|l|l|l|l|l|l|}
-%% \hline
-%% \multicolumn{4}{|l|}{\bf Heading1} & \multicolumn{4}{|l|}{\bf Heading2}\\ \hline
-%% $cell1 row1$ & cell2 row 1 & cell3 row 1 & cell4 row 1 & cell5 row 1 & cell6 row 1 & cell7 row 1 & cell8 row 1\\ \hline
-%% $cell1 row2$ & cell2 row 2 & cell3 row 2 & cell4 row 2 & cell5 row 2 & cell6 row 2 & cell7 row 2 & cell8 row 2\\ \hline
-%% $cell1 row3$ & cell2 row 3 & cell3 row 3 & cell4 row 3 & cell5 row 3 & cell6 row 3 & cell7 row 3 & cell8 row 3\\ \hline
-%% \end{tabular}
-%% \begin{flushleft} Table notes Phasellus venenatis, tortor nec vestibulum mattis, massa tortor interdum felis, nec pellentesque metus tortor nec nisl.
-Ut ornare mauris tellus, vel dapibus arcu suscipit sed.
-%% \end{flushleft}
-%% \label{table1}
-%% \end{adjustwidth}
-%% \end{table}
-
-\subsection*{Comparison of Mannik's Experimental and Our Stadium Shapes}
+\subsection*{Comparison of Experimental and Stadium Shapes}
 
@@
 
-%% \begin{figure}
-%%   \includegraphics[width=8.7cm]{../data/shape-randst/0_25-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
-%%   \includegraphics[width=8.7cm]{../data/shape-stad/0_25-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
-%%   \caption{Correlation for B shapes}
-%%   \label{corr-B}
-%% \end{figure}
-
 We see that both in the shape \emph{A} and stadium \emph{A}, the
@@
 exhibiting only a factor of two greater decoherence.
-
-\paragraph{3rd Level Heading.} Nulla mi mi, venenatis sed ipsum varius, volutpat euismod diam.
-Proin rutrum vel massa non gravida.
-Quisque tempor sem et dignissim rutrum.
-Lorem ipsum dolor sit amet, consectetur adipiscing elit.
-Morbi at justo vitae nulla elementum commodo eu id massa.
-In vitae diam ac augue semper tincidunt eu ut eros.
-Fusce fringilla erat porttitor lectus cursus, vel sagittis arcu lobortis.
-Aliquam in enim semper, aliquam massa id, cursus neque.
-Praesent faucibus semper libero.
 
@@
 
+\begin{figure}
+  \hspace{-3cm}
+  \includegraphics[width=8.7cm]{../data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
+  \includegraphics[width=8.7cm]{../data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
+  \caption{Correlation for B shapes}
+  \label{corr-B}
+\end{figure}
+
 \section*{Supporting Information}
@@
 \subsection*{S1 Video}
-\label{S1_Video}
-{\bf Bold the first sentence.}  Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\subsection*{S1 Text}
-\label{S1_Text}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\subsection*{S1 Fig}
-\label{S1_Fig}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
-
-\subsection*{S1 Table}
-\label{S1_Table}
-{\bf Lorem Ipsum.} Maecenas convallis mauris sit amet sem ultrices gravida.
-Etiam eget sapien nibh.
-Sed ac ipsum eget enim egestas ullamcorper nec euismod ligula.
-Curabitur fringilla pulvinar lectus consectetur pellentesque.
+\label{movie-MinD-density-pill}
+{\bf Movie that shows the evolution of MinD density over a 250 second
+  interval in a wild-type, pill-shaped cell.}  There is one frame for
+every half second of simulation time. Above are results from the
+stochastic model and below are results from the deterministic model.
+The density shown is integrated over the direction normal to the
+screen, so that the data is shown in molecules/$\micron^2$.
+
+\subsection*{S2 Video}
+\label{movie-MinD-density-shape-A}
+{\bf Movie that shows the evolution of MinD density over a 350 second
+  interval in the shape A cell.}  There is one frame for every half
+second of simulation time. Above are results from the stochastic model
+and below are results from the deterministic model.  The density shown
+is integrated over the direction normal to the screen, so that the
+data is shown in molecules/$\micron^2$.
+
+\subsection*{S3 Video}
+\label{movie-MinD-density-shape-B}
+{\bf Movie that shows the evolution of MinD density over a 350 second
+  interval in the shape B cell.}  There is one frame for every half
+second of simulation time. Above are results from the stochastic model
+and below are results from the deterministic model.  The density shown
+is integrated over the direction normal to the screen, so that the
+data is shown in molecules/$\micron^2$.
+
+\subsection*{S4 Video}
+\label{movie-MinD-density-stadium-A}
+{\bf Movie that shows the evolution of MinD density over a 350 second
+  interval in the stadium A cell.}  There is one frame for every half
+second of simulation time. Above are results from the stochastic model
+and below are results from the deterministic model.  The density shown
+is integrated over the direction normal to the screen, so that the
+data is shown in molecules/$\micron^2$.
+
+\subsection*{S5 Video}
+\label{movie-MinD-density-stadium-B}
+{\bf Movie that shows the evolution of MinD density over a 350 second
+  interval in the stadium B cell.}  There is one frame for every half
+second of simulation time. Above are results from the stochastic model
+and below are results from the deterministic model.  The density shown
+is integrated over the direction normal to the screen, so that the
+data is shown in molecules/$\micron^2$.
 
@@
 \section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit amet.
-Interdum et malesuada fames ac ante ipsum primis in faucibus.
-Nam id pretium nisi.
-Sed ac quam id nisi malesuada congue.
-Sed interdum aliquet augue, at pellentesque quam rhoncus vitae.
+Cras egestas velit mauris, eu mollis turpis pellentesque sit
+amet. Interdum et malesuada fames ac ante ipsum primis in
+faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada
+congue. Sed interdum aliquet augue, at pellentesque quam rhoncus
+vitae.
 

### 2015-03-17 correlation_box.sh

@@ -2,17 +2,17 @@
 
 echo starting !
 
-#srun --job-name="corr randst 18.50 95.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 full_array 0.00 &
-srun --job-name="corr randst 18.50 95.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 exact 0.00 &
+srun --job-name="corr randst 18.50 95.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 full_array 0.00 &
+#srun --job-name="corr randst 18.50 95.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 exact 0.00 &
 
-srun --job-name="corr randst 18.60 94.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 full_array 0.00 &
-srun --job-name="corr randst 18.60 94.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 exact 0.00 &
+#srun --job-name="corr randst 18.60 94.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 full_array 0.00 &
+#srun --job-name="corr randst 18.60 94.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 exact 0.00 &
 
 srun --job-name="corr stad 2.35 1.32 full 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 full_array 0.00 &
-srun --job-name="corr stad 2.35 exact 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 exact 0.00 &
+#srun --job-name="corr stad 2.35 exact 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 exact 0.00 &
 
-srun --job-name="corr stad 2.92 1.18 full 0.00" python pyplots/density-correlation.py stad 0.40 2.92 1.18 0.00 15.00 full_array 0.00 &
[…]

### 2015-03-17 paper/plos.tex
more edits to paper Tested everything on crystal.

@@
   \begin{enumerate}
-  \item Add discussion of ``platform'' --- wrote our own code,
+  \item \blue{Done} Add discussion of ``platform'' --- wrote our own code,
     publically available (cite github?).
-  \item Make 3D geometries available? Cite that the publically
+  \item \blue{Done} Make 3D geometries available? Cite that the publically
     available code can generate them?
@@
     \end{enumerate}
-  \item Height should be bigger to compare with experiment.  0.4-0.6
+  \item \blue{Done} Height should be bigger to compare with experiment.  0.4-0.6
     microns.  The 0.25 micron height of the cells used in this study
@@
       the channel to larger than .3 microns.}
-  \item Starry night in the wild-type cells is a problem.
+  \item \blue{David} Starry night in the wild-type cells is a problem.
   \item Better explanation of correlation function (which is
@@
     stochastic model.  (Read carefully)
-  \item Explain in greater detail the obviousness (maybe) that the
+  \item \blue{David} Explain in greater detail the obviousness (maybe) that the
     deterministic approach doesn't have fluctuations.  RESPOND:
@@
     with our stability analysis?
-  \item Should mention more recent revisions of the model.
+  \item \blue{David} Should mention more recent revisions of the model.
   \item Fange and Elf do not use the same reaction-diffusion
@@
     information?
-  \item Do not call Huang parameters ``wild type values.''  They are
+  \item \blue{Done} Do not call Huang parameters ``wild type values.''  They are
     fitted parameters.
   \item Add methods section for numerics (deterministic).
-  \item Add details of the linear stability analysis.
-  \item (From jeff): still need to fix periods on correlation plots
+  \item \blue{Done} Add details of the linear stability analysis.
+  \item \blue{David} Still need to fix periods on.  \blue{About this
+    point - I updated the data and it seems the result is defferent
+    from before - the stadium shapes seem to be temporally correlated
+    for much longer compared with the shape A than before.}
+    correlation plots
   \end{enumerate}
 }
-
-\fixme{Redo stability analysis with larger thickness, whatever we pick.}
 
@@
 %
-Several models
+\blue{(5)} Several models
 \cite{fange2006noise,bonny2013membrane,halatek2012highly} modify
@@
 oscillations, so we follow Huang\cite{huang2003dynamic} and do not
-deviate from the wild-type values used in the cited work.
+deviate from the \blue{(8)} parameter values used in the cited work.
 
@@
 same number of proteins per unit volume.  These concentration values
-are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We have
-chosen to write our own simulation platform and membrane creation
-tools from scratch, instead of using existing available software used
-in previous studies\fixme{cite previous studies} (we believe there is
-value in re-creating results with alternative software).  Our
-simulations take place within a three-dimensional Cartesian grid that
-has a grid spacing of .05\micron, and our cell shapes are specified as
-the zero of an analytic function which can generate the geometry
-presented in this paper.  Our code is publically available on
-github.com~\fixme{cite github account in references? Yes!}
+are $1273\micron^{-3}$ and $446\micron^{-3}$,
+respectively. \blue{(1,2)} We have chosen to write our own simulation
+platform and membrane creation tools from scratch, instead of using
+existing available software used in previous studies\fixme{cite
+  previous studies} (we believe there is value in re-creating results
+with alternative software).  Our simulations take place within a
+three-dimensional Cartesian grid that has a grid spacing of
+.05\micron, and our cell shapes are specified as the zero of an
+analytic function which can generate the geometry presented in this
+paper.  Our code is publically available on github.com~\fixme{cite
+  github account in references? Yes!}
 
@@
 
-Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
+\blue{(10)}  Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
 stability analysis on a cylindrical model which shows an upper limit
@@
 
-\blue{(5a)} Both Fig.~\ref{image-p} and its associated movies (see
+\blue{(5a),(7)} Both Fig.~\ref{image-p} and its associated movies (see
 supplementary material), show that the stochastic model exhibits a
@@
   \hspace{-3cm}
+  \vspace{1cm}
   \includegraphics[width=16cm]{../paper/plot-ave}
@@
 in the location of the maxima when using the stochastic model.  The
-deterministic model shows uniformly bipolar oscillation, with the
-exception of shape \emph{B}, which develops weak intermediate maxima
-on the right-hand edge of the cell.  From these results, we conclude
-that the deterministic model is inadequate to explain experimental
+deterministic model shows uniformly bipolar oscillation. \blue{(2)}
+It's worth pointing out that this is a significant result, since for
+irregular shapes it would be reasonable to hypothesize a chaotic
+system, which would be shown by irregular determinisitic data.  From
+these results and how they compare with experiment, we conclude that
+the deterministic model is inadequate to explain experimental
 observations of the locations of density maxima of the MinD protein.
@@
 deterministic model predicts robust and periodic bipolar oscillation
-in irregularly shaped cells, with a minor intermediate maximum
-appearing in shape \emph{B}.  Thus we conclude that this method is
+in irregularly shaped cells.  Thus we conclude that this method is
 inconsistent with experiment, and cannot be relied upon for

### 2015-03-17 correlation_box.sh

@@ -2,16 +2,16 @@
 
 echo starting !
 
-srun --job-name="corr randst 18.50 95.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 full_array 0.00 &
+run --job-name="corr randst 18.50 95.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 full_array 0.00 &
 #srun --job-name="corr randst 18.50 95.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 exact 0.00 &
 
-#srun --job-name="corr randst 18.60 94.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 full_array 0.00 &
+srun --job-name="corr randst 18.60 94.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 full_array 0.00 &
 #srun --job-name="corr randst 18.60 94.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 exact 0.00 &
 
-srun --job-name="corr stad 2.35 1.32 full 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 full_array 0.00 &
+#srun --job-name="corr stad 2.35 1.32 full 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 full_array 0.00 &
 #srun --job-name="corr stad 2.35 exact 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 exact 0.00 &
 
-#srun --job-name="corr stad 2.92 1.18 full 0.00" python pyplots/density-correlation.py stad 0.40 2.92 1.18 0.00 15.00 full_array 0.00 &
+srun --job-name="corr stad 2.92 1.18 full 0.00" python pyplots/density-correlation.py stad 0.40 2.92 1.18 0.00 15.00 full_array 0.00 &
 #srun --job-name="corr stad 2.92 exact 0.00" python pyplots/density-correlation.py stad 0.40 2.92 1.18 0.00 15.00 exact 0.00
 
 #srun --job-name="corr p 3.00 0.50 full 0.00 6000.00" python pyplots/density-correlation.py p 3.00 0.50 0.00 0.00 15.00 full_array 0.00 &

### 2015-03-17 pyplots/correlation-plot.py

@@ -124,17 +124,17 @@ if not plot_final_version:
 pylab.title(r'%s %s $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
             % (sys.argv[1], sys.argv[5], 1/rate, period, 1/(rate*period)))
 if sys.argv[1] == 'randst' and sys.argv[5] == '95.00':
-    #pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-    #            % (1/rate, period, 1/(rate*period)))
-    pylab.title(r'Temporal correlation of shape A')
+    pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+                % (1/rate, period, 1/(rate*period)))
+    #pylab.title(r'Temporal correlation of shape A')
 elif sys.argv[1] == 'stad' and sys.argv[4] == '1.32':
-    #pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-    #            % (1/rate, period, 1/(rate*period)))
-    pylab.title(r'Temporal correlation of stadium A')
+    pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+                % (1/rate, period, 1/(rate*period)))
+    #pylab.title(r'Temporal correlation of stadium A')
 elif sys.argv[1] == 'p':
-    #pylab.title(r'pill-shaped cell, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-    #            % (1/rate, period, 1/(rate*period)))
-    pylab.title(r'Temporal correlation of wild-type pill shape')
+    pylab.title(r'pill-shaped cell, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+                % (1/rate, period, 1/(rate*period)))
+    #pylab.title(r'Temporal correlation of wild-type pill shape')
 
 
 

### 2015-03-18 paper/plos.tex
tiny change on paper Tested everything on crystal.

@@
   \item \blue{Done} Add details of the linear stability analysis.
-  \item \blue{David} Still need to fix periods on.  \blue{About this
-    point - I updated the data and it seems the result is defferent
-    from before - the stadium shapes seem to be temporally correlated
-    for much longer compared with the shape A than before.}
-    correlation plots
+  \item \blue{David} Still need to fix periods on correlation plots.
+    \blue{About this point - I updated the data and it seems the
+      result is defferent from before - the stadium shapes seem to be
+      temporally correlated for much longer compared with the shape A
+      than before.}
   \end{enumerate}

### 2015-03-18 paper/plos.tex
a few edits in response to Jeff

@@
 an opportunity to test MinD simulation models against more extreme
-cases than have been seen thus far.
+cases than have been seen thus far.  \fixme{\blue{(2)} An additional
+  interesting question is whether the irregularity observed by Mannik
+  \emph{et al.} indicates that the MinD system can become chaotic (as
+  in e.g. Ref.~\citenum{kuramoto1978diffusion}), or if this
+irregularity is the result of a stochastic but nonchaotic process.}
+\fixme{Jeff, please skim this chaos citation, which I cannot access
+  from here.}
 
@@
 recruitment to the membrane, and change some of the constants used in
-the model. The Bonny 2013 model assumes an instantaneous nucleotide
-exchange rate, and allows MinE to remain independently attached to the
-membrane after dissasociating with MinD~\cite{bonny2013membrane}.
+the model.  In addition, Bonny \emph{et al.} assume an instantaneous
+nucleotide exchange rate, and allows MinE to remain independently
+attached to the membrane after dissasociating with
+MinD~\cite{bonny2013membrane}.
 %
@@
 protein density build up, as recruitment leads to clusters of MinD
-forming on the wall and then subsequently dissipating.  We attribute
-this effect to the fact that the Huang model does not include
-diffusion along the membrane, which has been experimentally verified
-yet found to be two orders of magnitude less than diffusion in the
-cytoplasm~\cite{meacci2005min}. Even ignoring this effect, however, it
-is clear from Fig.~\ref{image-p} that the stochastic simulation
-results in a protein distribution that is less spatially regular than
-the deterministic model predicts.  This naturally leads to
-irregularity in the temporal periodicity of the system, which we
-quantify by examining the temporal correlation function of the total
-MinD found in two opposite polar regions.
+forming on the wall and then subsequently dissipating.  This results
+from the lack of inclusion of diffusion along the membrane in Huang's
+model, which would spread out these recruitment clusters.  Experiments
+have confirmed that diffusion along the membrane does occur, albeit
+with a rate two orders of magnitude lower than that in the
+cytoplasm~\cite{meacci2005min}.  \fixme{I would really like to see an
+  estimate of the diffusivity width here.  A ``star'' from the starry
+  night effect lasts about 10 seconds, so we could just figure out how
+  far the protein would diffuse in 5 or 10 seconds.  If it comes out
+  to close to 1 micron, we can then say that we do not expect this
+  starry night effect to be observed in wild-type cells.}  \fixme{I'm
+  not sure what the following sentence means.}  Even ignoring this
+effect, however, it is clear from Fig.~\ref{image-p} that the
+stochastic simulation results in a protein distribution that is less
+spatially regular than the deterministic model predicts.  This
+naturally leads to irregularity in the temporal periodicity of the
+system, which we quantify by examining the temporal correlation
+function of the total MinD found in two opposite polar regions.
 %
@@
 deterministic model shows uniformly bipolar oscillation.  \blue{(2)}
-It's worth pointing out that this is a significant result, since for
-irregular shapes it would be reasonable to hypothesize a chaotic
-system, which would be shown by irregular determinisitic data.  From
+\fixme{We conclude that the model is \emph{not} chaotic (which would
+  show irregularity in the deterministic computation), but rather that
+  the irregularity results purely from stochastic processes.}  From
 these results and how they compare with experiment, we conclude that

### 2015-03-22 paper/plos.tex
Continued to address referee issues, recalculated correlation data, although the stochastic shape A is missing, Ill look into that Tested everything on crystal.

--- 2015-03-18 paper/plos.tex
@@
 %
-% Do not include text that is not math in the math environment. For example, CO2 will be CO\textsubscript{2}.
+% Do not include text that is not math in the math environment. For example , CO2 will be CO\textsubscript{2}.
 %
@@
     \item \blue{David.  I've added some sentences discussing the
-      starry night in the context of the membrane diffusion.  I didn't
-      say anything about a one half period allowing diffusion to smear
-      an entire pole, because it seems to contradict the second part
-      of this paragraph.  What do you think?} Lacks diffusion on the
-      membrane. Supported by Meacci 2006, which experimentally tries
-      to measure diffusion on membrane, has a tough time, but shows
-      that definitely diffuses.
-    \item Underestimates diffusion in cytoplasm by a factor of 5-6.5.
+      starry night effect and membrane diffusion blurring out the
+      stars.  I have some confusion however about the diffusion
+      lengths.}  Lacks diffusion on the membrane. Supported by Meacci
+      2006, which experimentally tries to measure diffusion on
+      membrane, has a tough time, but shows that definitely diffuses.
+    \item \blue{David} Underestimates diffusion in cytoplasm by a factor of 5-6.5.
       Supported by Meacci 2006, who concludes a rate of 16 microns
@@
       MinE.
-    \item Uses MinD-ADP -> MinD-ATP that is 3 times lower than
+    \item \blue{David} Uses MinD-ADP -> MinD-ATP that is 3 times lower than
       experimental bound. Halatek uses ADP->ATP of 1/6 s-1. They cite
@@
       s-1.
-    \item (Still debated) No evidence that DE recruits to membrane.
+    \item \blue{David} (Still debated) No evidence that DE recruits to membrane.
     \item Works in only a limited part of parameters phase space, and
@@
     Fange and Elf 2006.
-  \item Clarify (esp in conclusions) what we mean by flattening and
-    irregular shape.  ``breaking the cylindrical symmetry and
-    flattening the cells.'' versus ``breaking the mirror plane
-    symmetry of the cross-section of a flattned cell.''
+  \item \blue{David. Read the refferee report with regard to this, and
+    not sure what he wants...} Clarify (esp in conclusions) what we
+    mean by flattening and irregular shape.  ``breaking the
+    cylindrical symmetry and flattening the cells.'' versus ``breaking
+    the mirror plane symmetry of the cross-section of a flattned
+    cell.''
   \item[TODO suggestion] Switch to Halatek and Frey
@@
   \item Check order of figures and their references.
-  \item Cite biological (non-computational) works e.g. Corbin 2008.
+  \item \blue{David.  I cited the Corbin paper (although he's got a
+    typo because Corbin 2008 is after the fange 2006 paper. I could
+    cite other experimental papers, but the sentence in question
+    specifically refers to changes made to the Huang model, and the
+    papers cited are the main reasons that those changes have been
+    made.)} Cite biological (non-computational) works, that the
+    e.g. Corbin 2008.
   \end{enumerate}
@@
   \item \blue{David} Should mention more recent revisions of the model.
-  \item Fange and Elf do not use the same reaction-diffusion
+  \item \blue{David} Fange and Huang do not use the same reaction-diffusion
     equations.
-  \item Clarify statement about 1000 proteins and stochastic
-    fluctuation.  Reword about a continuum description omitting
-    information?
+  \item \blue{David.  I read the referee's note about this.  Not sure
+    what he/she wants.}  Clarify statement about 1000 proteins and
+    stochastic fluctuation.  Reword about a continuum description
+    omitting information?
   \item \blue{Done} Do not call Huang parameters ``wild type values.''  They are
     fitted parameters.
-  \item Add methods section for numerics (deterministic).
+  \item \blue{Done?  I think our additions to the Methods section
+    addressed this?}  Add methods section for numerics
+    (deterministic).
   \item \blue{Done} Add details of the linear stability analysis.
@@
 an opportunity to test MinD simulation models against more extreme
-cases than have been seen thus far.
-
+cases than have been seen thus far.  \blue{(2)} An additional
+interesting question is whether the irregularity observed by Mannik
+\emph{et al.} indicates that the MinD system can become chaotic (as in
+e.g. Ref.~\citenum{kuramoto1978diffusion}), or if this irregularity is
+the result of a stochastic but nonchaotic process.
+%
 A number of models of the MinD protein system have been developed that
@@
 %
-\blue{(5)} Several models
+\blue{(5a,b,c,d)} Several models
 \cite{fange2006noise,bonny2013membrane,halatek2012highly} modify
-Huang's original model to more accurately treat experimental findings
-published after his 2003 paper
-\cite{meacci2006mobility,loose2011min}. These models introduce slow
-diffusion along the membrane (two to three orders of magnitude slower
-than that within the cytoplasm), revise the process of MinD
-recruitment to the membrane, and change some of the constants used in
-the model. The Bonny 2013 model assumes an instantaneous nucleotide
-exchange rate, and allows MinE to remain independently attached to the
-membrane after dissasociating with MinD~\cite{bonny2013membrane}.
-%
-
-%%  A number of studies have used an approach similar in
-%% that they do not rely on the ability of MinD to move along the walls
-%% and cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
-%%   drew2005polymerization, fange2006noise, kerr2006division}, while
-%% studies have been made as well of models which rely on MinD mobility
-%% and attraction on the cell membrane~\cite{kruse2002dynamic,
-%%   howard2005cellular}.
-
+Huang's original model to more accurately treat experimental findings,
+some of which were published after his 2003 paper\blue{(15)}
+\cite{meacci2006mobility,loose2011min,corbin2002exploring}. These
+models introduce slow diffusion along the membrane (two to three
+orders of magnitude slower than that within the cytoplasm), revise the
+process of MinD recruitment to the membrane, increase the rate of
+diffusion within the cytpolasm, and decrease or assume
+instanaeous~\cite{bonny2013membrane} the nucleotide exchange rate.  In
+addition, Bonny \emph{et al.} allows MinE to remain independently
+attached to the membrane after dissasociating with
+MinD~\cite{bonny2013membrane}.
+%
 There are only on the order of 1000 MinD proteins in a given cell,
@@
 large role.  To treat this, there have been a number of variations of
-the Huang 2003 model that stochastically simulate the same \fixme{similar}
+the Huang 2003 model that stochastically simulate the similar
 reaction-diffusion equations~\cite{fange2006noise, kerr2006division}.
@@
 model~\cite{huang2003dynamic}, which has been widely
-used~\cite{hattne2005stochastic} \fixme{search for more} in both
-deterministic and stochastic variants, to study flattened cells of
-$0.4\micron$ thickness that are similar to those observed by Mannik
-\emph{et al.}~\cite{mannik2009bacterial}.  \fixme{Some weak
-  justification... it has been widely used.}
+used~\cite{hattne2005stochastic,huang2004min,kerr2006division}
+\fixme{I couldn't find too many.  Most (like Bonny and Halatek) use
+  modified versions.} in both deterministic and stochastic variants,
+to study flattened cells of $0.4\micron$ thickness that are similar to
+those observed by Mannik \emph{et al.}~\cite{mannik2009bacterial}.
+\fixme{Some weak justification... it has been widely used.}
 
@@
 platform and membrane creation tools from scratch, instead of using
-existing available software used in previous studies\fixme{cite
-  previous studies} (we believe there is value in re-creating results
-with alternative software).  Our simulations take place within a
-three-dimensional Cartesian grid that has a grid spacing of
-.05\micron, and our cell shapes are specified as the zero of an
-analytic function which can generate the geometry presented in this
-paper.  Our code is publically available on github.com~\fixme{cite
-  github account in references? Yes!}
+existing available software used in previous
+studies~\cite{bonny2013membrane,fange2006noise,halatek2012highly,kerr2006division}
+(we believe there is value in re-creating results with alternative
+software).  Our simulations take place within a three-dimensional
+Cartesian grid that has a grid spacing of .05\micron, and our cell
+shapes are specified as the zero of an analytic function which can
+generate the geometry presented in this paper.  Our code is publically
+available on github.com~\cite{git}.
 
@@
 protein density build up, as recruitment leads to clusters of MinD
-forming on the wall and then subsequently dissipating.  We attribute
-this effect to the fact that the Huang model does not include
-diffusion along the membrane, which has been experimentally verified
-yet found to be two orders of magnitude less than diffusion in the
-cytoplasm~\cite{meacci2005min}. Even ignoring this effect, however, it
-is clear from Fig.~\ref{image-p} that the stochastic simulation
-results in a protein distribution that is less spatially regular than
-the deterministic model predicts.  This naturally leads to
-irregularity in the temporal periodicity of the system, which we
-quantify by examining the temporal correlation function of the total
-MinD found in two opposite polar regions.
-%
-This correlation function, which is displayed in Fig.~\ref{corr-pill},
-is given by
+forming on the wall and then subsequently dissipating.  This results
+from the lack of inclusion of diffusion along the membrane in Huang's
+model, which would spread out these recruitment clusters.  Experiments
+have confirmed that diffusion along the membrane does occur, albeit
+with a rate two orders of magnitude lower than that in the
+cytoplasm~\cite{meacci2005min}.  The 'stars' in the effect seem to
+last for about 10 seconds. The membrane-bound proteins will travel an
+approximate distance of \fixme{see note} microns during one of these
+periods of time, enough to 'blur out' this effect in wild-type pill
+cells.  \fixme{calculating with $<x^2> = Dt$ and $D_{membrane} =
+  .16\mu^2/s m$, which is just the experimental cytoplasmic value
+  divided by 100, yields 1.2 microns, which maybe is too high for what
+  we're trying to say?  Halatek uses $D_{membrane} = .013\mu^2/s m$,
+  for which the same calculation would give .36 microns, which is
+  better.  Halatek doesn't say why he uses a value that seems to be
+  different than what Meacci claim to have found.  Halatek just says
+  it's experimentally valid and cites their work.  What to do?}
+
+We also analyze the temporal periodicity of the system, which we
+quantify with temporal correlation function of the total MinD found in
+two opposite polar regions.  This correlation function, which is
+displayed in Fig.~\ref{corr-pill}, is given by
 \begin{equation}
@@
 deterministic model shows uniformly bipolar oscillation.  \blue{(2)}
-It's worth pointing out that this is a significant result, since for
-irregular shapes it would be reasonable to hypothesize a chaotic
-system, which would be shown by irregular determinisitic data.  From
-these results and how they compare with experiment, we conclude that
-the deterministic model is inadequate to explain experimental
-observations of the locations of density maxima of the MinD protein.
+We conclude that the model is \emph{not} chaotic (which would show
+irregularity in the deterministic computation), but rather that the
+irregularity results purely from stochastic processes.  From these
+results and how they compare with experiment, we conclude that the
+deterministic model is inadequate to explain experimental observations
+of the locations of density maxima of the MinD protein.
 
@@
 experimentally, our simulations predict that MinD maxima will form in
-a spatially irregular sequence of locations.  This result builds upon
-existing results showing that this model is effective in a variety of
-wild-type and mutated cell shapes~\cite{fange2006noise, varma2008min,
-  kruse2007experimentalist}, and reinforces that the stochastic
-variation of Huang's 2003 model~\cite{fange2006noise,
-  kerr2006division} has considerable predictive power beyond the
-standard wild-type cell.  \fixme{Discuss which of these are likely to
-  map to more recent models.}
+a spatially irregular sequence of locations.  \blue{(6)}\fixme{Do you think this
+  sentence make it sounds like Fange has the same model as Huang?}
+This result builds upon existing results showing that this model and
+its derivatives are effective in a variety of wild-type and mutated
+cell shapes~\cite{fange2006noise, varma2008min,
+  kruse2007experimentalist}, and reinforces that stochastic variations
+of Huang's 2003 model~\cite{fange2006noise, kerr2006division} has
+considerable predictive power beyond the standard wild-type cell.
+\fixme{Discuss which of these are likely to map to more recent
+  models.}
 

### 2015-03-22 correlation_box.sh

@@ -2,13 +2,13 @@
 
 echo starting !
 
-run --job-name="corr randst 18.50 95.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 full_array 0.00 &
+srun --job-name="corr randst 18.50 95.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 full_array 0.00 &
 #srun --job-name="corr randst 18.50 95.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.50 18.50 95.00 15.00 exact 0.00 &
 
 srun --job-name="corr randst 18.60 94.00 full_array 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 full_array 0.00 &
 #srun --job-name="corr randst 18.60 94.00 exact 0.00" python pyplots/density-correlation.py randst 0.40 18.60 28.60 94.00 15.00 exact 0.00 &
 
-#srun --job-name="corr stad 2.35 1.32 full 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 full_array 0.00 &
+srun --job-name="corr stad 2.35 1.32 full 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 full_array 0.00 &
 #srun --job-name="corr stad 2.35 exact 0.00" python pyplots/density-correlation.py stad 0.40 2.35 1.32 0.00 15.00 exact 0.00 &
 
 srun --job-name="corr stad 2.92 1.18 full 0.00" python pyplots/density-correlation.py stad 0.40 2.92 1.18 0.00 15.00 full_array 0.00 &

### 2015-03-23 paper/plos.tex
updated periods and times of correlation plots Tested everything on crystal.

@@
     scaled to have the same initial value.  For shape \emph{A}, the
-    stochastic model shows an oscillation period of 53.1 seconds and
-    coherence time of 246 seconds, so that it takes roughly 4.6
+    stochastic model shows an oscillation period of 52 seconds and
+    coherence time of 248 seconds, so that it takes roughly 4.8
     periods for the behavior to decohere.  For the stadium \emph{A},
-    the same model shows an oscillation period of 51 seconds and
-    coherence time of 323 seconds, so that it takes roughly 6.3
+    the same model shows an oscillation period of 48.4 seconds and
+    coherence time of 634 seconds, so that it takes roughly 13
     periods for the behavior to decohere.}
@@
 factor, so that they can be directly compared against each other.  The
-stochastic simulation of shape \emph{A} has a coherence time of 4.6
+stochastic simulation of shape \emph{A} has a coherence time of 4.8
 periods, while the corresponding simulation of stadium \emph{A} has a
-coherence time of 6.3 periods.
+coherence time of 13 periods.
 %
 The correlation function for stadium \emph{B} is similar to that of
-stadium~\emph{A}, with similar coherence time (5.5 periods, not
-shown), while shape~\emph{B} exhibits a lower coherence time (2.2
+stadium~\emph{A}, with similar coherence time (8.6 periods, not
+shown), while shape~\emph{B} also exhibits a similar coherence time (4.9
 periods).  In the deterministic model, shape~\emph{B} is not precisely

### 2015-03-27 paper/plos.tex
address referees comments Tested everything on crystal.

--- 2015-03-18 paper/plos.tex
@@
   oscillations breaks down. We employ widely used stochastic and
-  deterministic models of the Min system to simulate cells with flattened
-  shapes.  The deterministic model predicts strong bipolar
+  deterministic models of the Min system to simulate cells with
+  flattened shapes.  The deterministic model predicts strong bipolar
   oscillations, in contradiction with the experimentally observed
@@
   simulations of symmetric but flattened cell shapes, and find that it
-  is the flattening rather than the asymmetry of the cell shapes that
-  causes the irregular oscillation behavior.
+  is the flattening and lateral expansion rather than the asymmetry of
+  the cell shapes that causes the irregular oscillation behavior.
 
@@
   \begin{enumerate}
-  \item \blue{Done} Add discussion of ``platform'' --- wrote our own code,
-    publically available (cite github?).
-  \item \blue{Done} Make 3D geometries available? Cite that the publically
-    available code can generate them?
-  \item Claims differential equations aren't needed.
-  \item Claims wild-type movie-ish plot not needed.
+  \item Done%% \blue{Done} Add discussion of ``platform'' --- wrote our own code,
+    %% publically available (cite github?).
+  \item Done
+    %% \blue{Done} Make 3D geometries available? Cite that the publically
+    %% available code can generate them?
+  \item Done%%Claims differential equations aren't needed.
+  \item Doen%%Claims wild-type movie-ish plot not needed.
   \item Points out problems with Huang 2003:
@@
       s-1.
-    \item (Still debated) No evidence that DE recruits to membrane.
-    \item Works in only a limited part of parameters phase space, and
-      could not account for important things like
-      temperature-independence.
+    \item \blue{David} (Still debated) No evidence that DE recruits to membrane.
+    \item Done%% Works in only a limited part of parameters phase space, and
+      %% could not account for important things like
+      %% temperature-independence.
     \end{enumerate}
-  \item \blue{Done} Height should be bigger to compare with experiment.  0.4-0.6
-    microns.  The 0.25 micron height of the cells used in this study
-    does not represent the experimental settings well. The simulations
-    are based on the flattened cell shapes reported from the
-    experiments by Mannik et al 2009 and 2012. In these experimental
-    studies, E. coli were shown to be able to grow in channels as low
-    as 0.6 micron in hard silicon structures, and no more than 0.4
-    micron (see Mannik 2009). Indeed, 0.25 micron channels were
-    constructed with PDMS ceilings, which is a rather flexible polymer
-    allowing bacteria to deform it to effectively higher
-    channels. Thus the simulations would be more realistic if
-    performed in the range of 0.4-0.6 micron thickness.
-
-    \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
-      then we and you observe it growing in a .25 micron flexible
-      channel, it presumably must be able to grow because it deformed
-      the channel to larger than .3 microns.}
-  \item \blue{David} Starry night in the wild-type cells is a problem.
-  \item Better explanation of correlation function (which is
-    interesting!).
-  \item Shape A is the interesting bit in our main figure.
-  \item Would like more analysis of stochastic locations in different
-    geometries.  Clusters?  Could add more geometries?
-  \item Bold conclusions about flattening.  Talk about both width and
-    thickness.  Compare Halatek 2012.  Wants systematically more
-    geometries again.
-  \item Is doubtful of our correlation plots relative to those of
-    Fange and Elf 2006.
-  \item Clarify (esp in conclusions) what we mean by flattening and
-    irregular shape.  ``breaking the cylindrical symmetry and
-    flattening the cells.'' versus ``breaking the mirror plane
-    symmetry of the cross-section of a flattned cell.''
-  \item[TODO suggestion] Switch to Halatek and Frey
-  \item[TODO suggestion] Thoroughly explor shape parameter space
-  \item[TODO suggestion] Check robustness of our conclusions with
-    respect to changes in (reaction-diffusion?) parameters.
-  \item Check order of figures and their references.
-  \item Cite biological (non-computational) works e.g. Corbin 2008.
+  \item Done%% \blue{Done} Height should be bigger to compare with experiment.  0.4-0.6
+    %% microns.  The 0.25 micron height of the cells used in this study
+    %% does not represent the experimental settings well. The simulations
+    %% are based on the flattened cell shapes reported from the
+    %% experiments by Mannik et al 2009 and 2012. In these experimental
+    %% studies, E. coli were shown to be able to grow in channels as low
+    %% as 0.6 micron in hard silicon structures, and no more than 0.4
+    %% micron (see Mannik 2009). Indeed, 0.25 micron channels were
+    %% constructed with PDMS ceilings, which is a rather flexible polymer
+    %% allowing bacteria to deform it to effectively higher
+    %% channels. Thus the simulations would be more realistic if
+    %% performed in the range of 0.4-0.6 micron thickness.
+
+    %% \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
+    %%   then we and you observe it growing in a .25 micron flexible
+    %%   channel, it presumably must be able to grow because it deformed
+    %%   the channel to larger than .3 microns.}
+  \item Done%%\blue{David} Starry night in the wild-type cells is a problem.
+  \item Done%%Better explanation of correlation function (which is
+    %%interesting!).
+  \item Done%%Shape A is the interesting bit in our main figure.
+  \item Done%%Would like more analysis of stochastic locations in different
+    %%geometries.  Clusters?  Could add more geometries?
+  \item Done%%Bold conclusions about flattening.  Talk about both width and
+    %% thickness.  Compare Halatek 2012.  Wants systematically more
+    %% geometries again.
+  \item Done%%Is doubtful of our correlation plots relative to those of
+    %%Fange and Elf 2006.
+  \item Done\blue{David. Read the refferee report with regard to this, and
+    not sure what he wants...} Clarify (esp in conclusions) what we
+    mean by flattening and irregular shape.  ``breaking the
+    cylindrical symmetry and flattening the cells.'' versus ``breaking
+    the mirror plane symmetry of the cross-section of a flattned
+    cell.''
+  \item Done%%[TODO suggestion] Switch to Halatek and Frey
+  \item Done%%[TODO suggestion] Thoroughly explor shape parameter space
+  \item Done%%[TODO suggestion] Check robustness of our conclusions with
+    %%respect to changes in (reaction-diffusion?) parameters.
+  \item Done%%Check order of figures and their references.
+  \item Done%%%% \blue{David.  I cited the Corbin paper (although he's got a
+    %% typo because Corbin 2008 is after the fange 2006 paper. I could
+    %% cite other experimental papers, but the sentence in question
+    %% specifically refers to changes made to the Huang model, and the
+    %% papers cited are the main reasons that those changes have been
+    %% made.)} Cite biological (non-computational) works, that the
+    %% e.g. Corbin 2008.
   \end{enumerate}
@@
   \begin{enumerate}
-  \item Nitpicks about language of deterministic model versus
+  \item Done%%Nitpicks about language of deterministic model versus
     stochastic model.  (Read carefully)
-  \item \blue{David} Explain in greater detail the obviousness (maybe) that the
-    deterministic approach doesn't have fluctuations.  RESPOND:
-    chaotic systems do deterministically result in fluctuations.
-    Explain this somewhere, and discuss triviality of the conclusion
-    that deterministic is wrong because it does not exhibit these
-    irregularities.
+  \item Done%%\blue{David} Explain in greater detail the obviousness (maybe) that the
+    %% deterministic approach doesn't have fluctuations.  RESPOND:
+    %% chaotic systems do deterministically result in fluctuations.
+    %% Explain this somewhere, and discuss triviality of the conclusion
+    %% that deterministic is wrong because it does not exhibit these
+    %% irregularities.
   \item Would like temporal averages over cell-cycle time scales.
@@
     with our stability analysis?
-  \item \blue{David} Should mention more recent revisions of the model.
-  \item Fange and Elf do not use the same reaction-diffusion
-    equations.
-  \item Clarify statement about 1000 proteins and stochastic
-    fluctuation.  Reword about a continuum description omitting
-    information?
-  \item \blue{Done} Do not call Huang parameters ``wild type values.''  They are
-    fitted parameters.
-  \item Add methods section for numerics (deterministic).
-  \item \blue{Done} Add details of the linear stability analysis.
-  \item \blue{David} Still need to fix periods on correlation plots.
-    \blue{About this point - I updated the data and it seems the
-      result is defferent from before - the stadium shapes seem to be
-      temporally correlated for much longer compared with the shape A
-      than before.}
+  \item Done%%\blue{David} Should mention more recent revisions of the model.
+  \item Done%%\blue{David} Fange and Huang do not use the same reaction-diffusion
+    %%equations.
+  \item Done%%%% \blue{David.  I read the referee's note about this.  Not sure
+    %% what he/she wants.}  Clarify statement about 1000 proteins and
+    %% stochastic fluctuation.  Reword about a continuum description
+    %% omitting information?
+  \item Done%%%% \blue{Done} Do not call Huang parameters ``wild type values.''  They are
+    %% fitted parameters.
+  \item Done%%\blue{Done?  I think our additions to the Methods section
+    %% addressed this?}  Add methods section for numerics
+    %% (deterministic).
+  \item Done%%\blue{Done} Add details of the linear stability analysis.
+  \item Done%%\blue{David} Still need to fix periods on correlation plots.
+    %% \blue{About this point - I updated the data and it seems the
+    %%   result is defferent from before - the stadium shapes seem to be
+    %%   temporally correlated for much longer compared with the shape A
+    %%   than before.}
   \end{enumerate}
@@
 an opportunity to test MinD simulation models against more extreme
-cases than have been seen thus far.  \fixme{\blue{(2)} An additional
-  interesting question is whether the irregularity observed by Mannik
-  \emph{et al.} indicates that the MinD system can become chaotic (as
-  in e.g. Ref.~\citenum{kuramoto1978diffusion}), or if this
-irregularity is the result of a stochastic but nonchaotic process.}
-\fixme{Jeff, please skim this chaos citation, which I cannot access
-  from here.}
-
+cases than have been seen thus far.  An additional interesting
+question is whether the irregularity observed by Mannik \emph{et al.}
+indicates that the MinD system can become chaotic (as in
+e.g. Ref.~\citenum{kuramoto1978diffusion}), or if this irregularity is
+the result of a stochastic but nonchaotic process.
+%
 A number of models of the MinD protein system have been developed that
@@
 %
-\blue{(5)} Several models
+
+\blue{5a,b,c,d}Several models
 \cite{fange2006noise,bonny2013membrane,halatek2012highly} modify
-Huang's original model to more accurately treat experimental findings
-published after his 2003 paper
-\cite{meacci2006mobility,loose2011min}. These models introduce slow
-diffusion along the membrane (two to three orders of magnitude slower
-than that within the cytoplasm), revise the process of MinD
-recruitment to the membrane, and change some of the constants used in
-the model.  In addition, Bonny \emph{et al.} assume an instantaneous
-nucleotide exchange rate, and allows MinE to remain independently
+Huang's original model to more accurately reflect experimental
+findings, which were published after his 2003
+paper~\cite{meacci2006mobility,loose2011min}. These models introduce
+diffusion along the membrane that is two to three orders of magnitude
+slower than that within the cytoplasm, and increase the rate of
+cytoplasmic diffusion by a factor of about five.  They also increase
+or assume instantaneous~\cite{bonny2013membrane} the nucleotide
+exchange rate.  In addition, they revise the process of MinD
+recruitment to the membrane, prohibiting MinD from attaching to
+MinD-MinE complexes there, behavior that is experimentally unresolved.
+The model of Bonny \emph{et al.} allows MinE to remain independently
 attached to the membrane after dissasociating with
@@
 
-%%  A number of studies have used an approach similar in
-%% that they do not rely on the ability of MinD to move along the walls
-%% and cluster~\cite{kruse2007experimentalist, meinhardt2001pattern,
-%%   drew2005polymerization, fange2006noise, kerr2006division}, while
-%% studies have been made as well of models which rely on MinD mobility
-%% and attraction on the cell membrane~\cite{kruse2002dynamic,
-%%   howard2005cellular}.
-
 There are only on the order of 1000 MinD proteins in a given cell,
-which means that stochastic fluctuation can be expected to play a
-large role.  To treat this, there have been a number of variations of
-the Huang 2003 model that stochastically simulate the same \fixme{similar}
-reaction-diffusion equations~\cite{fange2006noise, kerr2006division}.
-These studies largely confirm the results of Huang's deterministic
-model when applied to the wild-type, pill-shaped phenotype.  However,
-the stochastic models are slightly more successful in predicting
+which is significantly less than the number of gridpoints used in our
+simulations, suggesting that a continuum description will break down
+and stochastic variation plays a significant role.  To treat this,
+there have been a number of variations of the Huang 2003 model that
+stochastically simulate the similar reaction-diffusion
+equations~\cite{fange2006noise, kerr2006division}.  These studies
+largely confirm the results of Huang's deterministic model when
+applied to the wild-type, pill-shaped phenotype.  However, the
+stochastic models are slightly more successful in predicting
 experimentally observed oscillations in round cell
@@
 model~\cite{huang2003dynamic}, which has been widely
-used~\cite{hattne2005stochastic} \fixme{search for more} in both
+used~\cite{hattne2005stochastic,huang2004min,kerr2006division} in both
 deterministic and stochastic variants, to study flattened cells of
 $0.4\micron$ thickness that are similar to those observed by Mannik
-\emph{et al.}~\cite{mannik2009bacterial}.  \fixme{Some weak
-  justification... it has been widely used.}
+\emph{et al.}~\cite{mannik2009bacterial}.
 
@@
 primarily in the effect of cellular size and shape on the protein
-oscillations, so we follow Huang\cite{huang2003dynamic} and do not
-deviate from the \blue{(8)} parameter values used in the cited work.
+oscillations, so we use Huang's parameter
+values~\cite{huang2003dynamic}.
 
@@
 same number of proteins per unit volume.  These concentration values
-are $1273\micron^{-3}$ and $446\micron^{-3}$,
-respectively. \blue{(1,2)} We have chosen to write our own simulation
-platform and membrane creation tools from scratch, instead of using
-existing available software used in previous studies\fixme{cite
-  previous studies} (we believe there is value in re-creating results
-with alternative software).  Our simulations take place within a
-three-dimensional Cartesian grid that has a grid spacing of
-.05\micron, and our cell shapes are specified as the zero of an
-analytic function which can generate the geometry presented in this
-paper.  Our code is publically available on github.com~\fixme{cite
-  github account in references? Yes!}
+are $1273\micron^{-3}$ and $446\micron^{-3}$, respectively. We have
+written our own simulation platform and membrane creation tools from
+scratch, instead of using existing available software used in previous
+studies~\cite{bonny2013membrane,fange2006noise,halatek2012highly,kerr2006division}
+(we believe there is value in reproducing results with alternative
+software).  Our simulations take place within a three-dimensional
+Cartesian grid that has a grid spacing of .05\micron, and our cell
+shapes are specified as the zero of an analytic function which can
+generate the geometry presented in this paper.  Our code is publically
+available on github~\cite{git}, including scripts that generate the
+simulation data used in this paper.
 
@@
 
-\blue{(10)}  Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
+Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
 stability analysis on a cylindrical model which shows an upper limit
@@
 
-\blue{(5a),(7)} Both Fig.~\ref{image-p} and its associated movies (see
+\blue{(5a)} Both Fig.~\ref{image-p} and its associated movies (see
 supplementary material), show that the stochastic model exhibits a
@@
 from the lack of inclusion of diffusion along the membrane in Huang's
-model, which would spread out these recruitment clusters.  Experiments
-have confirmed that diffusion along the membrane does occur, albeit
-with a rate two orders of magnitude lower than that in the
-cytoplasm~\cite{meacci2005min}.  \fixme{I would really like to see an
-  estimate of the diffusivity width here.  A ``star'' from the starry
-  night effect lasts about 10 seconds, so we could just figure out how
-  far the protein would diffuse in 5 or 10 seconds.  If it comes out
-  to close to 1 micron, we can then say that we do not expect this
-  starry night effect to be observed in wild-type cells.}  \fixme{I'm
-  not sure what the following sentence means.}  Even ignoring this
-effect, however, it is clear from Fig.~\ref{image-p} that the
-stochastic simulation results in a protein distribution that is less
-spatially regular than the deterministic model predicts.  This
-naturally leads to irregularity in the temporal periodicity of the
-system, which we quantify by examining the temporal correlation
-function of the total MinD found in two opposite polar regions.
-%
-This correlation function, which is displayed in Fig.~\ref{corr-pill},
-is given by
+model, which would allow these recruitment clusters to spread out.
+Experiments have confirmed that diffusion along the membrane does
+occur, albeit with a rate two orders of magnitude lower than that in
+the cytoplasm~\cite{meacci2005min}.  The `stars' in the effect
+typically last for around 10 seconds. The membrane-bound proteins will
+travel a distance of around one micron during one of these periods of
+time, enough to spread out across the polar section of the one micron
+diameter wild-type pill cells.  As we see below, the flattened,
+irregular cells are large enough so that the one micron blur would not
+completely eliminate the `starry night' variation in maxima position
+effect.
+
+%% \fixme{calculating
+  %% with $<x^2> = Dt$ and $D_{membrane} = .16\mu^2/s m$, which is just
+  %% the experimental cytoplasmic value divided by 100, yields 1.2
+  %% microns, which maybe is too high for what we're trying to say?
+  %% Halatek uses $D_{membrane} = .013\mu^2/s m$, for which the same
+  %% calculation would give .36 microns, which is better.  Halatek
+  %% doesn't say why he uses a value that seems to be different than what
+  %% Meacci claim to have found.  Halatek just says it's experimentally
+  %% valid and cites their work.  What to do?}
+
+We also analyze the temporal periodicity of the system, which we
+quantify with temporal correlation function of the total MinD found in
+two opposite polar regions.  This correlation function, which is
+displayed in Fig.~\ref{corr-pill}, is given by
 \begin{equation}
@@
 
+%% \begin{figure}
+%%   \begin{center}
+%%     \includegraphics[height=6.4cm]{../data/shape-randst/0_40-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
+%%     \includegraphics[height=6.4cm]{../data/shape-stad/0_40-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
+%%   \end{center}
+%%   \caption{Temporal correlation function of the total MinD found in
+%%     two opposite polar regions of the shape \emph{A} (above) and the
+%%     stadium \emph{A} (below) cell shapes, shown against the
+%%     correlation time.  Data for both the the determinisitic and
+%%     stochastic models are shown, and the correlation functions are
+%%     scaled to have the same initial value.  For shape \emph{A}, the
+%%     stochastic model shows an oscillation period of 52 seconds and
+%%     coherence time of 248 seconds, so that it takes roughly 4.8
+%%     periods for the behavior to decohere.  For the stadium \emph{A},
+%%     the same model shows an oscillation period of 48.4 seconds and
+%%     coherence time of 634 seconds, so that it takes roughly 13
+%%     periods for the behavior to decohere.}
+%%   \label{fig:corr-pancake-A}
+%% \end{figure}
+
 \begin{figure}
   \begin{center}
-    \includegraphics[height=6.4cm]{../data/shape-randst/0_40-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
-    \includegraphics[height=6.4cm]{../data/shape-stad/0_40-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
+    \includegraphics[width=8.7cm]{../data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
+    \includegraphics[width=8.7cm]{../data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
   \end{center}
   \caption{Temporal correlation function of the total MinD found in
-    two opposite polar regions of the shape \emph{A} (above) and the
-    stadium \emph{A} (below) cell shapes, shown against the
+    two opposite polar regions of the shape \emph{B} (above) and the
+    stadium \emph{B} (below) cell shapes, shown against the
     correlation time.  Data for both the the determinisitic and
     stochastic models are shown, and the correlation functions are
-    scaled to have the same initial value.  For shape \emph{A}, the
-    stochastic model shows an oscillation period of 53.1 seconds and
-    coherence time of 246 seconds, so that it takes roughly 4.6
-    periods for the behavior to decohere.  For the stadium \emph{A},
-    the same model shows an oscillation period of 51 seconds and
-    coherence time of 323 seconds, so that it takes roughly 6.3
-    periods for the behavior to decohere.}
-  \label{fig:corr-pancake-A}
+    scaled to have the same initial value.  For shape \emph{B}, the
+    stochastic model shows an oscillation period of 58 seconds and
+    coherence time of 289 seconds, so that it takes roughly 5 periods
+    for the behavior to decohere.  For the stadium \emph{B}, the same
+    model shows an oscillation period of 51 seconds and coherence time
+    of 442 seconds, so that it takes roughly 8.6 periods for the
+    behavior to decohere.}
+  \label{fig:corr-B}
 \end{figure}
@@
 \subsection*{Comparison of Experimental and Stadium Shapes}
-
-As described in Section~\ref{sec:model-method-shapes}, we will focus
-on simulation of four illustrative flattened cell shapes: two shapes
-created to replicate those shapes observed experimentally by
-Mannik \emph{et al.}~\cite{mannik2012robustness} (shape~\emph{A} and
-shape~\emph{B}), and for comparison two symmetrical stadium shapes
-that have the identical aspect ratio, thickness and volume (stadium
-\emph{A} and stadium \emph{B}), shown in Figure~\ref{randst-plot-ave}.
-These stadium shapes enable us to distinguish between the effect of
-flattening the cell and the cell shape's irregularity and asymmetry.
-We note that shape \emph{B} is more irregular than shape \emph{A}, and
-in particular features a prominent region of concavity on its
-left-hand side.  For each of these shapes (in addition to the
-wild-type pill shape discussed previously) we have simulated in excess
-of 15000 seconds (over 4 hours) of evolution of the MinD system using
-the deterministic version of Huang's model~\cite{huang2003dynamic},
-and in excess of 100000 seconds (over 27 hours) using the stochastic
-model.
+%\label{sec:model-method-shapes}
+As described in Section~\ref{sec:model-method-shapes}, \fixme{this
+  link?} we will focus on simulation of four illustrative flattened
+cell shapes: two shapes created to replicate those shapes observed
+experimentally by Mannik \emph{et al.}~\cite{mannik2012robustness}
+(shape~\emph{A} and shape~\emph{B}), and for comparison two `stadium'
+shapes that have the identical aspect ratio, thickness and volume
+(stadium \emph{A} and stadium \emph{B}), shown in
+Figure~\ref{randst-plot-ave}.  All of the flattened cells have lost
+the rotational symmetry of the orginal pill shapes, but while
+shape~\emph{A} and shape~\emph{B} have only one mirror plane symmetry
+(that is normal to the flattened plane), stadium~\emph{A} and
+stadium~\emph{B} have three.  This allows us to distinguish between
+the effect of flattening the cell and the cell shape's irregularity
+and asymmetry.  For each of these shapes (in addition to the wild-type
+pill shape discussed previously) we have simulated in excess of 15000
+seconds (over 4 hours) of evolution of the MinD system using the
+deterministic version of Huang's model~\cite{huang2003dynamic}, and in
+excess of 100000 seconds (over 27 hours) using the stochastic model.
 
@@
 in the location of the maxima when using the stochastic model.  The
-deterministic model shows uniformly bipolar oscillation.  \blue{(2)}
-\fixme{We conclude that the model is \emph{not} chaotic (which would
-  show irregularity in the deterministic computation), but rather that
-  the irregularity results purely from stochastic processes.}  From
-these results and how they compare with experiment, we conclude that
-the deterministic model is inadequate to explain experimental
-observations of the locations of density maxima of the MinD protein.
+deterministic model shows uniformly bipolar oscillation.  We conclude
+that the model is \emph{not} chaotic (which would show irregularity in
+the deterministic computation), but rather that the irregularity
+results purely from stochastic processes.  From these results and how
+they compare with experiment, we conclude that the deterministic model
+is inadequate to explain experimental observations of the locations of
+density maxima of the MinD protein.
 
@@
 However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
-the flattening of the cell versus cell shape irregularity and
-asymmetry in developing an understanding of the origin of the
-experimentally observed behavior.  Although in the movies the stadiums
-appear to display, on average over long time scales, a somewhat more
-regular oscillation than appears in the irregular shapes \emph{A} and
-\emph{B}, the limited time range of the arrow plots (350 seconds) is
-inadequate to make this comparison.  We therefore return to the
-correlation function between the number of proteins in a segment at
-the top of the cell and the number of proteins in a segment at the
-bottom of the cell.  Fig.~\ref{fig:corr-pancake-A} shows this plot for
-shape \emph{A} and stadium \emph{A}.  E. Coli cell doubling times vary
-widely depending on environmental conditions, but will often be
-between 20 minutes to 100 minutes~\cite{pierucci1972chromosome}, while
-fluorescent microscopy experiments have shown that the FtsZ ring
-builds itself with a half life of roughly 30
-seconds~\cite{stricker2002rapid}.  Here we plot correlations of
-correlation times up to 500 seconds, a biologically relevant
-timescale.
-
-We see that both in the shape \emph{A} and stadium \emph{A}, the
+the flattening and accompying lateral expansion of the cell versus
+cell shape irregularity and asymmetry in developing an understanding
+of the origin of the experimentally observed behavior.  Although in
+the movies the stadiums appear to display, on average over long time
+scales, a somewhat more regular oscillation than appears in the
+irregular shapes \emph{A} and \emph{B}, the limited time range of the
+arrow plots (350 seconds) is inadequate to make this comparison.  We
+therefore return to the correlation function between the number of
+proteins in a segment at the top of the cell and the number of
+proteins in a segment at the bottom of the cell.
+Fig.~\ref{fig:corr-B} shows this plot for shape \emph{B} and stadium
+\emph{B}.  E. Coli cell doubling times vary widely depending on
+environmental conditions, but will often be between 20 minutes to 100
+minutes~\cite{pierucci1972chromosome}, while fluorescent microscopy
+experiments have shown that the FtsZ ring builds itself with a half
+life of roughly 30 seconds~\cite{stricker2002rapid}.  Here we plot
+correlations of correlation times up to 500 seconds, a biologically
+relevant timescale.
+
+We see that both in the shape \emph{B} and stadium \emph{B}, the
 deterministic model is perfectly periodic.  Both the deterministic and
@@
 factor, so that they can be directly compared against each other.  The
-stochastic simulation of shape \emph{A} has a coherence time of 4.6
-periods, while the corresponding simulation of stadium \emph{A} has a
-coherence time of 6.3 periods.
-%
-The correlation function for stadium \emph{B} is similar to that of
-stadium~\emph{A}, with similar coherence time (5.5 periods, not
-shown), while shape~\emph{B} exhibits a lower coherence time (2.2
-periods).  In the deterministic model, shape~\emph{B} is not precisely
-periodic on biologically relevant timescales, which is reflected in
-Fig.~\ref{randst-plot-ave}, in which the arrows describing the
-deterministic model applied to shape \emph{B} show minor maxima
-forming on the right-hand side of the cell, in contrast to the regular
-polar maxima formed by shape~\emph{A} and the two stadiums.
-%
+stochastic simulation of shape \emph{B} has a coherence time of 5
+periods, while the corresponding simulation of stadium \emph{B} has a
+coherence time of 8.6 periods.
+%
+The correlation function for stadium \emph{A} is similar to that of
+stadium~\emph{B}, with similar coherence time (13 periods, not
+shown), while shape~\emph{A} also exhibits a similar coherence time (4.9
+periods).
+%
+
 From the stochastic correlation data, we conclude that irregularity of
@@
 a spatially irregular sequence of locations.  This result builds upon
-existing results showing that this model is effective in a variety of
-wild-type and mutated cell shapes~\cite{fange2006noise, varma2008min,
-  kruse2007experimentalist}, and reinforces that the stochastic
-variation of Huang's 2003 model~\cite{fange2006noise,
-  kerr2006division} has considerable predictive power beyond the
-standard wild-type cell.  \fixme{Discuss which of these are likely to
-  map to more recent models.}
+existing results showing that this model and its variants are
+effective in a variety of wild-type and mutated cell
+shapes~\cite{fange2006noise, varma2008min, kruse2007experimentalist},
+and reinforces that stochastic variations of Huang's 2003
+model~\cite{fange2006noise, kerr2006division} has considerable
+predictive power beyond the standard wild-type cell.  \fixme{Discuss
+  which of these are likely to map to more recent models.}
 
@@
 models~\cite{kerr2006division, fange2006noise, huang2004min,
-  kruse2007experimentalist}.
+  kruse2007experimentalist}.  The regular oscillations in the
+deterministic case also allow us to conclude that the model is
+non-chaotic.  Because of their similar construction, we suspect that
+recent variants of the
+model~\cite{bonny2013membrane,fange2006noise,halatek2012highly} would
+also prove to be non-chaotic.
 
@@
 irregularity in the shape of flattened cells.  Thus we conclude that
-it is the flattening of the cells rather than their irregular shape
-that primarily causes the disruption of regular bipolar oscillation
-which is observed by Mannik \emph{et al.}~\cite{mannik2012robustness}.
-
-\begin{figure}
-  \hspace{-3cm}
-  \includegraphics[width=8.7cm]{../data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
-  \includegraphics[width=8.7cm]{../data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
-  \caption{Correlation for B shapes}
-  \label{corr-B}
-\end{figure}
+it is the flattening of the cells, and the accompying expansion in the
+tranverse direction, rather than their irregular shape that primarily
+causes the disruption of regular bipolar oscillation which is observed
+by Mannik \emph{et al.}~\cite{mannik2012robustness}.
 

### 2015-03-27 pyplots/correlation-plot.py

@@ -116,7 +116,7 @@ for i in range(1,num_plots):
     print 'period ',period
     pylab.plot(time_array,data_full[i],colors[i],label='stochastic')
     pylab.xlim(0,time_array[-1])
-    #pylab.ylim(np.amin(data_full[i]),np.amax(data_full[i]))
+    pylab.ylim(1.1*np.amin(data_full[i]),1.1*np.amax(data_full[i]))
 
 if not plot_final_version:
     pylab.plot(time_array,decay,colors[0],label='decay')
@@ -124,17 +124,21 @@ if not plot_final_version:
 pylab.title(r'%s %s $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
             % (sys.argv[1], sys.argv[5], 1/rate, period, 1/(rate*period)))
 if sys.argv[1] == 'randst' and sys.argv[5] == '95.00':
-    pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-                % (1/rate, period, 1/(rate*period)))
-    #pylab.title(r'Temporal correlation of shape A')
+    #pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+    #            % (1/rate, period, 1/(rate*period)))
+    pylab.title(r'Temporal correlation of shape A')
+elif sys.argv[1] == 'randst' and sys.argv[5] == '94.00':
+    pylab.title(r'Temporal correlation of shape B')
 elif sys.argv[1] == 'stad' and sys.argv[4] == '1.32':
-    pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-                % (1/rate, period, 1/(rate*period)))
-    #pylab.title(r'Temporal correlation of stadium A')
+    #pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+    #            % (1/rate, period, 1/(rate*period)))
+    pylab.title(r'Temporal correlation of stadium A')
+elif sys.argv[1] == 'stad' and sys.argv[4] == '1.18':
+    pylab.title(r'Temporal correlation of stadium B')
 elif sys.argv[1] == 'p':
-    pylab.title(r'pill-shaped cell, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
[…]

### 2015-03-27 paper/plos.tex
a few edits with Jeff alongside (todo is done!) Tested everything on bennet.

@@
 
-\red{Huh}
-
-\fixme{
-  First referee:
-  \begin{enumerate}
-  \item Done%% \blue{Done} Add discussion of ``platform'' --- wrote our own code,
-    %% publically available (cite github?).
-  \item Done
-    %% \blue{Done} Make 3D geometries available? Cite that the publically
-    %% available code can generate them?
-  \item Done%%Claims differential equations aren't needed.
-  \item Doen%%Claims wild-type movie-ish plot not needed.
-  \item Points out problems with Huang 2003:
-    \begin{enumerate}
-    \item \blue{David.  I've added some sentences discussing the
-      starry night effect and membrane diffusion blurring out the
-      stars.  I have some confusion however about the diffusion
-      lengths.}  Lacks diffusion on the membrane. Supported by Meacci
-      2006, which experimentally tries to measure diffusion on
-      membrane, has a tough time, but shows that definitely diffuses.
-    \item \blue{David} Underestimates diffusion in cytoplasm by a factor of 5-6.5.
-      Supported by Meacci 2006, who concludes a rate of 16 microns
-      squared per sec for MinD and 10 microns squared per sec for
-      MinE.
-    \item \blue{David} Uses MinD-ADP -> MinD-ATP that is 3 times lower than
-      experimental bound. Halatek uses ADP->ATP of 1/6 s-1. They cite
-      Meacci 2006, who state that there is a lower bound on reference
-      time of 3 seconds, so this constant has an upper bound of 1/3
-      s-1.
-    \item \blue{David} (Still debated) No evidence that DE recruits to membrane.
-    \item Done%% Works in only a limited part of parameters phase space, and
-      %% could not account for important things like
-      %% temperature-independence.
-    \end{enumerate}
-  \item Done%% \blue{Done} Height should be bigger to compare with experiment.  0.4-0.6
-    %% microns.  The 0.25 micron height of the cells used in this study
-    %% does not represent the experimental settings well. The simulations
-    %% are based on the flattened cell shapes reported from the
-    %% experiments by Mannik et al 2009 and 2012. In these experimental
-    %% studies, E. coli were shown to be able to grow in channels as low
-    %% as 0.6 micron in hard silicon structures, and no more than 0.4
-    %% micron (see Mannik 2009). Indeed, 0.25 micron channels were
-    %% constructed with PDMS ceilings, which is a rather flexible polymer
-    %% allowing bacteria to deform it to effectively higher
-    %% channels. Thus the simulations would be more realistic if
-    %% performed in the range of 0.4-0.6 micron thickness.
-
-    %% \emph{If you can't make it grow in a .3 micron (rigid) silicon channel,
-    %%   then we and you observe it growing in a .25 micron flexible
-    %%   channel, it presumably must be able to grow because it deformed
-    %%   the channel to larger than .3 microns.}
-  \item Done%%\blue{David} Starry night in the wild-type cells is a problem.
-  \item Done%%Better explanation of correlation function (which is
-    %%interesting!).
-  \item Done%%Shape A is the interesting bit in our main figure.
-  \item Done%%Would like more analysis of stochastic locations in different
-    %%geometries.  Clusters?  Could add more geometries?
-  \item Done%%Bold conclusions about flattening.  Talk about both width and
-    %% thickness.  Compare Halatek 2012.  Wants systematically more
-    %% geometries again.
-  \item Done%%Is doubtful of our correlation plots relative to those of
-    %%Fange and Elf 2006.
-  \item Done\blue{David. Read the refferee report with regard to this, and
-    not sure what he wants...} Clarify (esp in conclusions) what we
-    mean by flattening and irregular shape.  ``breaking the
-    cylindrical symmetry and flattening the cells.'' versus ``breaking
-    the mirror plane symmetry of the cross-section of a flattned
-    cell.''
-  \item Done%%[TODO suggestion] Switch to Halatek and Frey
-  \item Done%%[TODO suggestion] Thoroughly explor shape parameter space
-  \item Done%%[TODO suggestion] Check robustness of our conclusions with
-    %%respect to changes in (reaction-diffusion?) parameters.
-  \item Done%%Check order of figures and their references.
-  \item Done%%%% \blue{David.  I cited the Corbin paper (although he's got a
-    %% typo because Corbin 2008 is after the fange 2006 paper. I could
-    %% cite other experimental papers, but the sentence in question
-    %% specifically refers to changes made to the Huang model, and the
-    %% papers cited are the main reasons that those changes have been
-    %% made.)} Cite biological (non-computational) works, that the
-    %% e.g. Corbin 2008.
-  \end{enumerate}
-  Second referee:
-  \begin{enumerate}
-  \item Done%%Nitpicks about language of deterministic model versus
-    stochastic model.  (Read carefully)
-  \item Done%%\blue{David} Explain in greater detail the obviousness (maybe) that the
-    %% deterministic approach doesn't have fluctuations.  RESPOND:
-    %% chaotic systems do deterministically result in fluctuations.
-    %% Explain this somewhere, and discuss triviality of the conclusion
-    %% that deterministic is wrong because it does not exhibit these
-    %% irregularities.
-  \item Would like temporal averages over cell-cycle time scales.
-  \item More discussion of how flattening leads to spatial
-    irregularities.  Compare with large nearly spherical e. coli Shih
-    2005.  See also Halatek and Frey 2012 for rotating oscillation
-    axis due to destabilization of short modes.  How does this connect
-    with our stability analysis?
-  \item Done%%\blue{David} Should mention more recent revisions of the model.
-  \item Done%%\blue{David} Fange and Huang do not use the same reaction-diffusion
-    %%equations.
-  \item Done%%%% \blue{David.  I read the referee's note about this.  Not sure
-    %% what he/she wants.}  Clarify statement about 1000 proteins and
-    %% stochastic fluctuation.  Reword about a continuum description
-    %% omitting information?
-  \item Done%%%% \blue{Done} Do not call Huang parameters ``wild type values.''  They are
-    %% fitted parameters.
-  \item Done%%\blue{Done?  I think our additions to the Methods section
-    %% addressed this?}  Add methods section for numerics
-    %% (deterministic).
-  \item Done%%\blue{Done} Add details of the linear stability analysis.
-  \item Done%%\blue{David} Still need to fix periods on correlation plots.
-    %% \blue{About this point - I updated the data and it seems the
-    %%   result is defferent from before - the stadium shapes seem to be
-    %%   temporally correlated for much longer compared with the shape A
-    %%   than before.}
-  \end{enumerate}
-}
-
 \section*{Introduction}
@@
 
-\blue{5a,b,c,d}Several models
-\cite{fange2006noise,bonny2013membrane,halatek2012highly} modify
-Huang's original model to more accurately reflect experimental
-findings, which were published after his 2003
-paper~\cite{meacci2006mobility,loose2011min}. These models introduce
+Several models \cite{fange2006noise, bonny2013membrane,
+  halatek2012highly} modify Huang's original model to more accurately
+reflect experimental findings, which were published after his 2003
+paper~\cite{meacci2006mobility, loose2011min}. These models introduce
 diffusion along the membrane that is two to three orders of magnitude
 slower than that within the cytoplasm, and increase the rate of
-cytoplasmic diffusion by a factor of about five.  They also increase
-or assume instantaneous~\cite{bonny2013membrane} the nucleotide
-exchange rate.  In addition, they revise the process of MinD
-recruitment to the membrane, prohibiting MinD from attaching to
-MinD-MinE complexes there, behavior that is experimentally unresolved.
-The model of Bonny \emph{et al.} allows MinE to remain independently
-attached to the membrane after dissasociating with
-MinD~\cite{bonny2013membrane}.
+cytoplasmic diffusion by a factor of about five, reflecting an
+experimental measurement of these
+parameters~\cite{meacci2006mobility}.  They also increase or assume
+instantaneous~\cite{bonny2013membrane} the nucleotide exchange rate.
+In addition, they revise the process of MinD recruitment to the
+membrane, prohibiting MinD from being recruited to the membrane by
+MinD-MinE complexes, behavior that has not been observed
+experimentally.  The model of Bonny \emph{et al.} allows MinE to
+remain independently attached to the membrane after dissasociating
+with MinD~\cite{bonny2013membrane}.
 %
 
-There are only on the order of 1000 MinD proteins in a given cell,
-which is significantly less than the number of gridpoints used in our
-simulations, suggesting that a continuum description will break down
-and stochastic variation plays a significant role.  To treat this,
-there have been a number of variations of the Huang 2003 model that
-stochastically simulate the similar reaction-diffusion
-equations~\cite{fange2006noise, kerr2006division}.  These studies
-largely confirm the results of Huang's deterministic model when
-applied to the wild-type, pill-shaped phenotype.  However, the
-stochastic models are slightly more successful in predicting
-experimentally observed oscillations in round cell
-phenotypes~\cite{fange2006noise, huang2004min}, and they enable
+There are only on the order of a thousand MinD proteins in a given
+cell, which is fewer than the number of gridpoints used in our
+simulations, suggesting that the deterministic continuum
+description--which requires fractional numbers of proteins at each
+grid point---may break down, and that stochastic behavior may play a
+significant role.  To treat this, there have been a number of
+variations of the Huang 2003 model that stochastically simulate the
+similar reaction-diffusion equations~\cite{fange2006noise,
+  kerr2006division}.  These studies largely confirm the results of
+Huang's deterministic model when applied to the wild-type, pill-shaped
+phenotype.  However, the stochastic models are slightly more
+successful in predicting experimentally observed oscillations in round
+cell phenotypes~\cite{fange2006noise, huang2004min}, and they enable
 prediction of fluctuations in the predicted
@@
 
-\blue{(5a)} Both Fig.~\ref{image-p} and its associated movies (see
-supplementary material), show that the stochastic model exhibits a
-``starry night'' effect characterized by spatially fixed points of
-protein density build up, as recruitment leads to clusters of MinD
-forming on the wall and then subsequently dissipating.  This results
-from the lack of inclusion of diffusion along the membrane in Huang's
-model, which would allow these recruitment clusters to spread out.
-Experiments have confirmed that diffusion along the membrane does
-occur, albeit with a rate two orders of magnitude lower than that in
-the cytoplasm~\cite{meacci2005min}.  The `stars' in the effect
+Both Fig.~\ref{image-p} and its associated movies (see supplementary
+material), show that the stochastic model exhibits a ``starry night''
+effect characterized by spatially fixed points of protein density
+build up, as recruitment leads to clusters of MinD forming on the wall
+and then subsequently dissipating.  This effect is strengthened by the
+lack of inclusion of diffusion along the membrane in Huang's model,
+since this diffusion could allow these recruitment clusters to spread
+out.  Experiments have confirmed that diffusion along the membrane
+does occur, albeit with a rate two orders of magnitude lower than that
+in the cytoplasm~\cite{meacci2005min}.  The `stars' in the effect
 typically last for around 10 seconds. The membrane-bound proteins will
-travel a distance of around one micron during one of these periods of
-time, enough to spread out across the polar section of the one micron
-diameter wild-type pill cells.  As we see below, the flattened,
-irregular cells are large enough so that the one micron blur would not
-completely eliminate the `starry night' variation in maxima position
-effect.
+diffuse by a distance of around one micron during this time, which is
+enough to spread out across the polar section of a one micron diameter
+wild-type pill cell.  As we see below, the flattened, irregular cells
+are larger so that the one micron blur would not completely eliminate
+this `starry night' effect.
 
@@
 %\label{sec:model-method-shapes}
-As described in Section~\ref{sec:model-method-shapes}, \fixme{this
-  link?} we will focus on simulation of four illustrative flattened
-cell shapes: two shapes created to replicate those shapes observed
-experimentally by Mannik \emph{et al.}~\cite{mannik2012robustness}
-(shape~\emph{A} and shape~\emph{B}), and for comparison two `stadium'
-shapes that have the identical aspect ratio, thickness and volume
-(stadium \emph{A} and stadium \emph{B}), shown in
-Figure~\ref{randst-plot-ave}.  All of the flattened cells have lost
-the rotational symmetry of the orginal pill shapes, but while
-shape~\emph{A} and shape~\emph{B} have only one mirror plane symmetry
-(that is normal to the flattened plane), stadium~\emph{A} and
-stadium~\emph{B} have three.  This allows us to distinguish between
-the effect of flattening the cell and the cell shape's irregularity
-and asymmetry.  For each of these shapes (in addition to the wild-type
-pill shape discussed previously) we have simulated in excess of 15000
-seconds (over 4 hours) of evolution of the MinD system using the
-deterministic version of Huang's model~\cite{huang2003dynamic}, and in
-excess of 100000 seconds (over 27 hours) using the stochastic model.
+As explained above, we focus on simulation of four illustrative
+flattened cell shapes: two shapes created to replicate those shapes
+observed experimentally by Mannik \emph{et
+  al.}~\cite{mannik2012robustness} (shape~\emph{A} and
+shape~\emph{B}), and for comparison two `stadium' shapes that have the
+identical aspect ratio, thickness and volume (stadium \emph{A} and
+stadium \emph{B}), shown in Figure~\ref{randst-plot-ave}.  All of the
+flattened cells have lost the rotational symmetry of the orginal pill
+shapes, but while shape~\emph{A} and shape~\emph{B} have only one
+mirror plane symmetry (that is normal to the flattened plane),
+stadium~\emph{A} and stadium~\emph{B} have three.  This allows us to
+distinguish between the effect of flattening the cell and the cell
+shape's irregularity and asymmetry.  For each of these shapes (in
+addition to the wild-type pill shape discussed previously) we have
+simulated in excess of 15000 seconds (over 4 hours) of evolution of
+the MinD system using the deterministic version of Huang's
+model~\cite{huang2003dynamic}, and in excess of 100000 seconds (over
+27 hours) using the stochastic model.
 
@@
 model~\cite{fange2006noise, kerr2006division} has considerable
-predictive power beyond the standard wild-type cell.  \fixme{Discuss
-  which of these are likely to map to more recent models.}
-
-%
-%% We have simulated flattened cell shapes similar to those observed
-%% experimentally by Mannik \emph{et al.}, with a stochastic and a
-%% deterministic version of Huang's widely used reaction-diffusion model.
-%% %
-%% We find that the stochastic model predicts experimentally accurate
-%% qualitative behavoir in both the wild-type, pill-shaped cells (as
-%% found in previous studies~\cite{fange2006noise, varma2008min,
-%%   kruse2007experimentalist}), as well as in the new, flattened,
-%% irregularly shaped cells.  These flattened cells invariably show
-%% spatially irregular formation of maxima as has been observed
-%% experimentally.
+predictive power beyond the standard wild-type cell.
 
@@
 deterministic case also allow us to conclude that the model is
-non-chaotic.  Because of their similar construction, we suspect that
-recent variants of the
-model~\cite{bonny2013membrane,fange2006noise,halatek2012highly} would
-also prove to be non-chaotic.
+non-chaotic.  Because of their similar construction, we anticipate
+that recent variants of the model~\cite{bonny2013membrane,
+  fange2006noise, halatek2012highly} would also prove to be
+non-chaotic.
 

### 2015-03-30 paper/plos.tex
Daivd read-through edits to paper Tested everything on crystal.

--- 2015-03-27 paper/plos.tex
@@
   process is a system of proteins that oscillate between cell ends and
-  help the original cell divide along its center.  A recent
-  experiment found that by drastically deforming these cells this
-  oscillation can be disrupted.  We examine these oscillations in
-  similarly deformed cells computationally, using two widely used
-  simulation models, and find good agreement using one of them.  The
-  other model fails in a manner far more dramatic than has been
-  previously observed.  Furthermore, we find that the effect observed
-  experimentally in asymmetric and flattened cells is primarily a
-  result of the flattening, not the asymmetry.
+  help the original cell divide along its center.  A recent experiment
+  found that by drastically deforming these cells this oscillation can
+  be disrupted.  We examine these oscillations in similarly deformed
+  cells computationally, using two widely used simulation models, and
+  find good agreement using one of them.  The other model fails in a
+  manner far more dramatic than has been previously observed.
+  Furthermore, we find that the effect observed experimentally in
+  asymmetric and flattened cells is primarily a result of the
+  flattening and lateral expansion, not the asymmetry.
 
@@
 tube shapes~\cite{varma2008min}, in which the oscillations seem to
-seek out the extreme poles in the cell.  One conclusion of these
-studies has been that the MinD system robustly forms bipolar
-oscillations regardless of variations in cellular shape.
-
-However, Mannik \emph{et al.} have recently shown that there are
-limitations to this robust capability to
+seek out the extreme poles in the cell.
+%%   One conclusion of these
+%% studies has been that the MinD system robustly forms bipolar
+%% oscillations regardless of variations in cellular shape.
+Mannik \emph{et al.} have recently shown that there are limitations to
+this robust capability to
 oscillate~\cite{mannik2012robustness,mannik2009bacterial,mannik2010bacteria}. They
@@
 divide into surprisingly equal volumes, the MinD oscillations in these
-cells are irregular, both temporally and spatially. Seen with
-fluorescent microscopy, the MinD maximize in multiple locations within
-the cell, in a seemingly random sequence. These experiments allow for
-an opportunity to test MinD simulation models against more extreme
-cases than have been seen thus far.  An additional interesting
-question is whether the irregularity observed by Mannik \emph{et al.}
-indicates that the MinD system can become chaotic (as in
+cells are spatially irregular. Seen with fluorescent microscopy, the
+MinD maximize in multiple locations within the cell, in a seemingly
+random sequence. These experiments allow for an opportunity to test
+models of the MinD system against more extreme cases than have been
+seen thus far.  An additional interesting question is whether the
+irregularity observed by Mannik \emph{et al.}  indicates that the MinD
+system can become chaotic (as in
 e.g. Ref.~\citenum{kuramoto1978diffusion}), or if this irregularity is
@@
 exchange rate.  In addition, they revise the process of MinD
-recruitment to the membrane, prohibiting MinD from attaching to
-MinD-MinE complexes there, behavior that is experimentally unresolved.
-The model of Bonny \emph{et al.} allows MinE to remain independently
-attached to the membrane after dissasociating with
-MinD~\cite{bonny2013membrane}.
+recruitment to the membrane, removing recruitment of MinD to the
+membrane by MinD-MinE complexes, behavior that has not been observed
+experimentally.  The model of Bonny \emph{et al.} further more allows
+MinE to remain independently attached to the membrane after
+dissasociating with MinD~\cite{bonny2013membrane}.
 %
@@
 there have been a number of variations of the Huang 2003 model that
-stochastically simulate the similar reaction-diffusion
-equations~\cite{fange2006noise, kerr2006division}.  These studies
-largely confirm the results of Huang's deterministic model when
-applied to the wild-type, pill-shaped phenotype.  However, the
-stochastic models are slightly more successful in predicting
-experimentally observed oscillations in round cell
-phenotypes~\cite{fange2006noise, huang2004min}, and they enable
+stochastically simulate the similar reaction-diffusion equations at
+the level of individual proteins~\cite{fange2006noise,
+  kerr2006division}.  These studies largely confirm the results of
+Huang's deterministic model when applied to the wild-type, pill-shaped
+phenotype.  However, the stochastic models are slightly more
+successful in predicting experimentally observed oscillations in round
+cell phenotypes~\cite{fange2006noise, huang2004min}, and they enable
 prediction of fluctuations in the predicted
@@
 scratch, instead of using existing available software used in previous
-studies~\cite{bonny2013membrane,fange2006noise,halatek2012highly,kerr2006division}
-(we believe there is value in reproducing results with alternative
-software).  Our simulations take place within a three-dimensional
-Cartesian grid that has a grid spacing of .05\micron, and our cell
-shapes are specified as the zero of an analytic function which can
-generate the geometry presented in this paper.  Our code is publically
-available on github~\cite{git}, including scripts that generate the
-simulation data used in this paper.
+studies~\cite{bonny2013membrane,fange2006noise,halatek2012highly,kerr2006division}.
+Our simulations take place within a three-dimensional Cartesian grid
+that has a grid spacing of .05\micron, and our cell shapes are
+specified as the zero of an analytic function which can generate the
+geometry presented in this paper.  This code is publically available
+on github~\cite{git}, including scripts that generate the simulation
+data used in this paper.
 
@@
 raising uncertainty in the actual cell thickness.  Tests with pure
-silicon, non-deformable slits show that the greatest thickness for
+silicon, non-deformable slits show that the smallest thickness for
 which cells are able to penetrate is
@@
 
-Huang \emph{et al.}~\cite{huang2003dynamic} has performed a linear
+Huang \emph{et al.}~\cite{huang2003dynamic} have performed a linear
 stability analysis on a cylindrical model which shows an upper limit
@@
 from 15 to 23 seconds).  The appearance of these rings in the
-deterministic model along side their less obvious appearance in the
+deterministic model alongside their less obvious appearance in the
 stochastic model highlights an advantage of the deterministic model:
@@
 forming on the wall and then subsequently dissipating.  This results
-from the lack of inclusion of diffusion along the membrane in Huang's
-model, which would allow these recruitment clusters to spread out.
+from the omission of diffusion along the membrane from Huang's model,
+which would allow these recruitment clusters to spread out.
 Experiments have confirmed that diffusion along the membrane does
@@
 diameter wild-type pill cells.  As we see below, the flattened,
-irregular cells are large enough so that the one micron blur would not
-completely eliminate the `starry night' variation in maxima position
-effect.
+irregular cells are large enough so that the one micron blurring would
+not completely eliminate the `starry night' variation in maxima
+position effect.
 
@@
 We also analyze the temporal periodicity of the system, which we
-quantify with temporal correlation function of the total MinD found in
-two opposite polar regions.  This correlation function, which is
-displayed in Fig.~\ref{corr-pill}, is given by
+quantify with the temporal correlation function of the total MinD
+found in two opposite polar regions.  This correlation function, which
+is displayed in Fig.~\ref{corr-pill}, is given by
 \begin{equation}
@@
 indefinitely with complete coherence, indicating that its behavior is
-perfectly periodic.
+periodic.
 
@@
 the flattening and accompying lateral expansion of the cell versus
-cell shape irregularity and asymmetry in developing an understanding
-of the origin of the experimentally observed behavior.  Although in
-the movies the stadiums appear to display, on average over long time
-scales, a somewhat more regular oscillation than appears in the
-irregular shapes \emph{A} and \emph{B}, the limited time range of the
-arrow plots (350 seconds) is inadequate to make this comparison.  We
-therefore return to the correlation function between the number of
-proteins in a segment at the top of the cell and the number of
-proteins in a segment at the bottom of the cell.
-Fig.~\ref{fig:corr-B} shows this plot for shape \emph{B} and stadium
-\emph{B}.  E. Coli cell doubling times vary widely depending on
+cell shape irregularity and asymmetry in the temporal regularity of
+the oscillations.  Although in the movies the stadiums appear to
+display, on average over long time scales, a somewhat more regular
+oscillation than appears in the irregular shapes \emph{A} and
+\emph{B}, the limited time range of the arrow plots (350 seconds) is
+inadequate to make this comparison.  We therefore return to the
+correlation function between the number of proteins in a segment at
+the top of the cell and the number of proteins in a segment at the
+bottom of the cell.  Fig.~\ref{fig:corr-B} shows this plot for shape
+\emph{B} and stadium \emph{B}.  Here we plot correlations of
+correlation times up to 500 seconds, a biologically relevant
+timescale.  E. Coli cell doubling times vary widely depending on
 environmental conditions, but will often be between 20 minutes to 100
@@
 experiments have shown that the FtsZ ring builds itself with a half
-life of roughly 30 seconds~\cite{stricker2002rapid}.  Here we plot
-correlations of correlation times up to 500 seconds, a biologically
-relevant timescale.
+life of roughly 30 seconds~\cite{stricker2002rapid}.
 
@@
 The correlation function for stadium \emph{A} is similar to that of
-stadium~\emph{B}, with similar coherence time (13 periods, not
-shown), while shape~\emph{A} also exhibits a similar coherence time (4.9
-periods).
-%
-
+stadium~\emph{B}, with similar coherence time (13 periods, not shown),
+while shape~\emph{A} also exhibits a similar coherence time (4.9
+periods).  This confirms that the stadium shapes do indeed oscillate
+somewhat more regularly than the irrelgular shapes, but both are
+comparable to the wild-type pill shape.
+%
 From the stochastic correlation data, we conclude that irregularity of

### 2015-03-30 paper/plos.tex

--- 2015-03-27 paper/plos.tex
@@
 experimental measurement of these
-parameters~\cite{meacci2006mobility}.  They also increase or assume
-instantaneous~\cite{bonny2013membrane} the nucleotide exchange rate.
-In addition, they revise the process of MinD recruitment to the
-membrane, prohibiting MinD from being recruited to the membrane by
-MinD-MinE complexes, behavior that has not been observed
-experimentally.  The model of Bonny \emph{et al.} allows MinE to
-remain independently attached to the membrane after dissasociating
-with MinD~\cite{bonny2013membrane}.
+parameters~\cite{meacci2006mobility}.  They also increase
+or assume instantaneous~\cite{bonny2013membrane} the nucleotide
+exchange rate.  In addition, they revise the process of MinD
+recruitment to the membrane, removing recruitment of MinD to the
+membrane by MinD-MinE complexes, behavior that has not been observed
+experimentally.  The model of Bonny \emph{et al.} further more allows
+MinE to remain independently attached to the membrane after
+dissasociating with MinD~\cite{bonny2013membrane}.
 %
@@
 build up, as recruitment leads to clusters of MinD forming on the wall
-and then subsequently dissipating.  This effect is strengthened by the
-lack of inclusion of diffusion along the membrane in Huang's model,
-since this diffusion could allow these recruitment clusters to spread
-out.  Experiments have confirmed that diffusion along the membrane
-does occur, albeit with a rate two orders of magnitude lower than that
-in the cytoplasm~\cite{meacci2005min}.  The `stars' in the effect
-typically last for around 10 seconds. The membrane-bound proteins will
-diffuse by a distance of around one micron during this time, which is
-enough to spread out across the polar section of a one micron diameter
-wild-type pill cell.  As we see below, the flattened, irregular cells
-are larger so that the one micron blur would not completely eliminate
-this `starry night' effect.
+and then subsequently dissipating.  This results from the omission of
+diffusion along the membrane from Huang's model, which would allow
+these recruitment clusters to spread out.  Experiments have confirmed
+that diffusion along the membrane does occur, albeit with a rate two
+orders of magnitude lower than that in the
+cytoplasm~\cite{meacci2005min}.  The `stars' in the effect typically
+last for around 10 seconds. The membrane-bound proteins will diffuse
+by a distance of around one micron during this time, which is enough
+to spread out across the polar section of the one micron diameter
+wild-type pill cells.  As we see below, the flattened, irregular cells
+are large enough that this one micron blurring would not completely
+eliminate this `starry night' effect.
 
@@
 The correlation function for stadium \emph{A} is similar to that of
-stadium~\emph{B}, with similar coherence time (13 periods, not
-shown), while shape~\emph{A} also exhibits a similar coherence time (4.9
-periods).
+stadium~\emph{B}, with similar coherence time (13 periods, not shown),
+while shape~\emph{A} also exhibits a similar coherence time (4.9
+periods).  This confirms that the stadium shapes do indeed oscillate
+somewhat more regularly than the irrelgular shapes, but both are
+comparable to the wild-type pill shape.
 %
-
 From the stochastic correlation data, we conclude that irregularity of

### 2015-03-30 paper/plos.tex
an edit of a couple of bits Tested everything on bennet.

@@
 case of the stochastic model the pill exhibits coherence times of
-about 8 periods and in the case of the deterministic model oscillate
-indefinitely with complete coherence, indicating that its behavior is
+about 8 periods, indicating that the system exhibits periodic
+oscillation, with some stochastic irregularity in the period.
+%
+In contrast, in the deterministic model the pill-shaped cell exhibits
+complete coherence, indicating that its behavior is perfectly
 periodic.

### 2015-03-30 paper/plos.tex
updated correlation data Tested everything on crystal.

@@
   regulate the process of cell division by identifying the center of
-  the cell.  While this system usually exhibits robust bipolar
-  oscillations in a variety of cell shapes, recent experiments have
-  shown that when the cells are mechanically deformed into wide,
-  flattened out, irregular shapes, the spatial regularity of these
-  oscillations breaks down. We employ widely used stochastic and
-  deterministic models of the Min system to simulate cells with
-  flattened shapes.  The deterministic model predicts strong bipolar
-  oscillations, in contradiction with the experimentally observed
-  behavior, while the stochastic model, which is based on the same
-  reaction-diffusion equations, does predict spatially irregular
-  oscillations as observed in experiment.  We further report
-  simulations of symmetric but flattened cell shapes, and find that it
-  is the flattening and lateral expansion rather than the asymmetry of
-  the cell shapes that causes the irregular oscillation behavior.
+  the cell.  While this system exhibits robust bipolar oscillations in
+  wild-type cell shapes, recent experiments have shown that when the
+  cells are mechanically deformed into wide, flattened out, irregular
+  shapes, the spatial regularity of these oscillations breaks down. We
+  employ widely used stochastic and deterministic models of the Min
+  system to simulate cells with flattened shapes.  The deterministic
+  model predicts strong bipolar oscillations, in contradiction with
+  the experimentally observed behavior, while the stochastic model,
+  which is based on the same reaction-diffusion equations, does
+  predict spatially irregular oscillations as observed in experiment.
+  We further report simulations of flattened but more symmetric
+  shapes, and find that it is the flattening and lateral expansion
+  rather than the asymmetry of the cell shapes that causes the
+  irregular oscillation behavior.
 
@@
 is capable of exhibiting oscillations in round
-shapes~\cite{fange2006noise} as well as in connected three pronged
-tube shapes~\cite{varma2008min}, in which the oscillations seem to
-seek out the extreme poles in the cell.
+shapes~\cite{corbin2002exploring,fange2006noise} as well as in
+connected three pronged tube shapes~\cite{varma2008min}, in which the
+oscillations seem to seek out the extreme poles in the cell.
 %%   One conclusion of these
@@
 %
+
 A number of models of the MinD protein system have been developed that
@@
 MinE to remain independently attached to the membrane after
-dissasociating with MinD~\cite{bonny2013membrane}.
+disassociating with MinD~\cite{bonny2013membrane}.
 %
@@
 There are only on the order of a thousand MinD proteins in a given
-cell, which is fewer than the number of gridpoints used in our
+cell, which is fewer than the number of grid points used in our
 simulations, suggesting that the deterministic continuum
@@
 specified as the zero of an analytic function which can generate the
-geometry presented in this paper.  This code is publically available
+geometry presented in this paper.  This code is publicly available
 on github~\cite{git}, including scripts that generate the simulation
@@
 by a number of flattened out shapes which reflect the experiments of
-Mannik \emph{et al.}, in which bacteria are confined within a thin
+Mannik \emph{et al.}, in which bacteria are confined within thin
 slits.  These slits are fabricated with a width of .25\micron, but
@@
     stadium \emph{B} (below) cell shapes, shown against the
-    correlation time.  Data for both the the determinisitic and
+    correlation time.  Data for both the the deterministic and
     stochastic models are shown, and the correlation functions are
@@
 stadium \emph{B}), shown in Figure~\ref{randst-plot-ave}.  All of the
-flattened cells have lost the rotational symmetry of the orginal pill
+flattened cells have lost the rotational symmetry of the original pill
 shapes, but while shape~\emph{A} and shape~\emph{B} have only one
@@
 distinguish between the effect of flattening the cell and the cell
-shape's irregularity and asymmetry.  For each of these shapes (in
-addition to the wild-type pill shape discussed previously) we have
-simulated in excess of 15000 seconds (over 4 hours) of evolution of
-the MinD system using the deterministic version of Huang's
-model~\cite{huang2003dynamic}, and in excess of 100000 seconds (over
-27 hours) using the stochastic model.
+shape's irregularity and asymmetry.
+
+%% For each of these shapes (in
+%% addition to the wild-type pill shape discussed previously) we have
+%% simulated in excess of 15000 seconds (over 4 hours) of evolution of
+%% the MinD system using the deterministic version of Huang's
+%% model~\cite{huang2003dynamic}, and in excess of 100000 seconds (over
+%% 27 hours) using the stochastic model.
 
@@
 However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
-the flattening and accompying lateral expansion of the cell versus
+the flattening and accompanying lateral expansion of the cell versus
 cell shape irregularity and asymmetry in the temporal regularity of
@@
 periods).  This confirms that the stadium shapes do indeed oscillate
-somewhat more regularly than the irrelgular shapes, but both are
+somewhat more regularly than the irregular shapes, but both are
 comparable to the wild-type pill shape.
@@
 irregularity in the shape of flattened cells.  Thus we conclude that
-it is the flattening of the cells, and the accompying expansion in the
-tranverse direction, rather than their irregular shape that primarily
+it is the flattening of the cells, and the accompanying expansion in the
+transverse direction, rather than their irregular shape that primarily
 causes the disruption of regular bipolar oscillation which is observed

### 2015-03-30 movie_shell.sh

@@ -29,14 +29,14 @@ echo starting!
 # data/shape-stad/0_25-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf: pyplots/correlation-plot.py \
 
 
-srun --job-name="mov-im-create p 3.00 0.50 full 500 1000" python pyplots/movie-image-creation.py p 3.00 0.50 0.00 0.00 15.00 full_array 500.00 750.00 &
-srun --job-name="mov-im-create randst 18.60 28.60 full 500 1000" python pyplots/movie-image-creation.py randst 0.25 18.60 28.60 94.00 15.00 full_array 500.00 850.00 &
-srun --job-name="mov-im-create randst 18.50 18.50 full 500 1000" python pyplots/movie-image-creation.py randst 0.25 18.50 18.50 95.00 15.00 full_array 500.00 850.00 &
-srun --job-name="mov-im-create stad 2.92 1.18 full 500 1000" python pyplots/movie-image-creation.py stad 0.25 2.92 1.18 0.00 15.00 full_array 500.00 850.00 &
-srun --job-name="mov-im-create stad 2.35 1.32 full 500 1000" python pyplots/movie-image-creation.py stad 0.25 2.35 1.32 0.00 15.00 full_array 500.00 850.00 &
+# srun --job-name="mov-im-create p 3.00 0.50 full 500 1000" python pyplots/movie-image-creation.py p 3.00 0.50 0.00 0.00 15.00 full_array 500.00 750.00 &
+# srun --job-name="mov-im-create randst 18.60 28.60 full 500 1000" python pyplots/movie-image-creation.py randst 0.40 18.60 28.60 94.00 15.00 full_array 500.00 850.00 &
+# srun --job-name="mov-im-create randst 18.50 18.50 full 500 1000" python pyplots/movie-image-creation.py randst 0.40 18.50 18.50 95.00 15.00 full_array 500.00 850.00 &
+# srun --job-name="mov-im-create stad 2.92 1.18 full 500 1000" python pyplots/movie-image-creation.py stad 0.40 2.92 1.18 0.00 15.00 full_array 500.00 850.00 &
+# srun --job-name="mov-im-create stad 2.35 1.32 full 500 1000" python pyplots/movie-image-creation.py stad 0.40 2.35 1.32 0.00 15.00 full_array 500.00 850.00 &
 
[…]

### 2015-03-30 paper/plos.tex
updated correlation times in paper Tested everything on crystal.

@@
 %%     stochastic model shows an oscillation period of 52 seconds and
-%%     coherence time of 248 seconds, so that it takes roughly 4.8
+%%     coherence time of 288 seconds, so that it takes roughly 5.5
 %%     periods for the behavior to decohere.  For the stadium \emph{A},
 %%     the same model shows an oscillation period of 48.4 seconds and
-%%     coherence time of 634 seconds, so that it takes roughly 13
+%%     coherence time of 638 seconds, so that it takes roughly 13
 %%     periods for the behavior to decohere.}
@@
     stochastic model shows an oscillation period of 58 seconds and
-    coherence time of 289 seconds, so that it takes roughly 5 periods
+    coherence time of 306 seconds, so that it takes roughly 5.3 periods
     for the behavior to decohere.  For the stadium \emph{B}, the same
@@
 factor, so that they can be directly compared against each other.  The
-stochastic simulation of shape \emph{B} has a coherence time of 5
+stochastic simulation of shape \emph{B} has a coherence time of 5.3
 periods, while the corresponding simulation of stadium \emph{B} has a
@@
 stadium~\emph{B}, with similar coherence time (13 periods, not shown),
-while shape~\emph{A} also exhibits a similar coherence time (4.9
+while shape~\emph{A} also exhibits a similar coherence time (5.5
 periods).  This confirms that the stadium shapes do indeed oscillate

### 2015-03-30 pyplots/correlation-plot.py

@@ -124,21 +124,25 @@ if not plot_final_version:
 pylab.title(r'%s %s $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
             % (sys.argv[1], sys.argv[5], 1/rate, period, 1/(rate*period)))
 if sys.argv[1] == 'randst' and sys.argv[5] == '95.00':
-    #pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-    #            % (1/rate, period, 1/(rate*period)))
-    pylab.title(r'Temporal correlation of shape A')
+    pylab.title(r'mannik A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+               % (1/rate, period, 1/(rate*period)))
+    #pylab.title(r'Temporal correlation of shape A')
 elif sys.argv[1] == 'randst' and sys.argv[5] == '94.00':
-    pylab.title(r'Temporal correlation of shape B')
+#    pylab.title(r'Temporal correlation of shape B')
+    pylab.title(r'mannik B, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+               % (1/rate, period, 1/(rate*period)))
 elif sys.argv[1] == 'stad' and sys.argv[4] == '1.32':
-    #pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
-    #            % (1/rate, period, 1/(rate*period)))
-    pylab.title(r'Temporal correlation of stadium A')
+    pylab.title(r'stadium A, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+               % (1/rate, period, 1/(rate*period)))
+#    pylab.title(r'Temporal correlation of stadium A')
 elif sys.argv[1] == 'stad' and sys.argv[4] == '1.18':
-    pylab.title(r'Temporal correlation of stadium B')
+#    pylab.title(r'Temporal correlation of stadium B')
+    pylab.title(r'stadium B, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
+               % (1/rate, period, 1/(rate*period)))
 elif sys.argv[1] == 'p':
-    #pylab.title(r'pill-shaped cell, $\tau_c = %.3g$ sec $T = %.3g$ sec (ratio %.2g)'
[…]

### 2015-03-31 paper/plos.tex
changed one citation and one line in bib Tested everything on crystal.

@@
 orders of magnitude lower than that in the
-cytoplasm~\cite{meacci2005min}.  The `stars' in the effect typically
+cytoplasm~\cite{meacci2006mobility}.  The `stars' in the effect typically
 last for around 10 seconds. The membrane-bound proteins will diffuse

### 2015-04-01 paper/plos.tex
changed the word the Tested everything on crystal.

@@
 significant role.  To treat this, there have been a number of
-variations of the Huang 2003 model that stochastically simulate the
+variations of the Huang 2003 model that stochastically simulate
 similar reaction-diffusion equations~\cite{fange2006noise,

### 2015-04-01 paper/plos.tex
fix Mannik spelling Tested everything on bennet.

--- 2015-03-30 paper/plos.tex
@@
   flattened \emph{Escherichia coli}}
+% Disrupted Min oscillation in flattened E. coli
 }
@@
 %% oscillations regardless of variations in cellular shape.
-Mannik \emph{et al.} have recently shown that there are limitations to
+M\"annik \emph{et al.} have recently shown that there are limitations to
 this robust capability to
@@
 seen thus far.  An additional interesting question is whether the
-irregularity observed by Mannik \emph{et al.}  indicates that the MinD
+irregularity observed by M\"annik \emph{et al.}  indicates that the MinD
 system can become chaotic (as in
@@
 deterministic and stochastic variants, to study flattened cells of
-$0.4\micron$ thickness that are similar to those observed by Mannik
+$0.4\micron$ thickness that are similar to those observed by M\"annik
 \emph{et al.}~\cite{mannik2009bacterial}.
@@
 We mean to investigate the geometric limits of the Min system
-oscillations as observed by Mannik \emph{et
+oscillations as observed by M\"annik \emph{et
   al.}~\cite{mannik2012robustness}, so we have modeled the Min system
@@
 by a number of flattened out shapes which reflect the experiments of
-Mannik \emph{et al.}, in which bacteria are confined within thin
+M\"annik \emph{et al.}, in which bacteria are confined within thin
 slits.  These slits are fabricated with a width of .25\micron, but
@@
 In this paper we focus on four specific flattened cell shapes.  Two of
-these shapes replicate those published by Mannik \emph{et al.}, and
+these shapes replicate those published by M\"annik \emph{et al.}, and
 the other two are `stadium' shapes that respectively have the same
 aspect ratio, thickness, and volume as the two cell shapes
-experimentally observed by Mannik \emph{et
+experimentally observed by M\"annik \emph{et
   al.}~\cite{mannik2012robustness}.  Viewed from the top down, these
@@
 approximation we use a numerical aperture value of 1.3, which is the
-same as used by Mannik experimentally, and a wavelength of $650nm$.
+same as used by M\"annik experimentally, and a wavelength of $650nm$.
 Each frame is 2.5 seconds ahead of the last, and each image shows the
@@
     for the flattened cells is 350 seconds, which is the same
-    period of time depicted in the experimental data plots of Mannik
+    period of time depicted in the experimental data plots of M\"annik
     \emph{et al.}~\cite{mannik2012robustness}.  For the wild-type pill
@@
     useful comparison due to its shorter oscillation period.  The top
-    row shows plots published by Mannik \emph{et al.} of the MinD maxima behavior
+    row shows plots published by M\"annik \emph{et al.} of the MinD maxima behavior
     and the bottom two rows show our simulations using the stochastic
     and deterministic models, respectively.  We simulated
-    approximations to the two shapes observed by Mannik, which we call
+    approximations to the two shapes observed by M\"annik, which we call
     \emph{shape A} and \emph{shape B}.  In addition, we studied two
@@
 flattened cell shapes: two shapes created to replicate those shapes
-observed experimentally by Mannik \emph{et
+observed experimentally by M\"annik \emph{et
   al.}~\cite{mannik2012robustness} (shape~\emph{A} and
@@
 second segment to compare with the published results of
-Mannik \emph{et al.}~\cite{mannik2012robustness}, exemplified in arrow plots in
+M\"annik \emph{et al.}~\cite{mannik2012robustness}, exemplified in arrow plots in
 which the arrow heads show the location of sequential MinD maxima
@@
 %% shape, but also in very assymetrical, flatttened cells, such as those
-%% observed by Mannik.  We also examined larger and smaller versions of
+%% observed by M\"annik.  We also examined larger and smaller versions of
 %% these shapes, and found this behavior to be very robust, from the
 %% minimum size to sustain oscillation (around \fixme{???} $\mu$m) up to
-%% around twice the cell size reported by Mannik.  At larger sizes than
+%% around twice the cell size reported by M\"annik.  At larger sizes than
 %% this, less regular oscillations occur using the deterministic method,
-%% but we note that the cells reported by Mannik are already considerably
+%% but we note that the cells reported by M\"annik are already considerably
 %% larger in volume than typical wild type
@@
 causes the disruption of regular bipolar oscillation which is observed
-by Mannik \emph{et al.}~\cite{mannik2012robustness}.
+by M\"annik \emph{et al.}~\cite{mannik2012robustness}.
 

### 2015-06-08 paper/plos.tex
remove acknowledgements content. Tested everything on bennet.
add outline of comments from referees Tested everything on bennet.

@@
 \linenumbers
+
+{
+  \color{red}
+  Referee 1.
+  \begin{enumerate}
+  \item Need to better justify use of Huang.
+  \item Couldn't another deterministic model predict Mannik's results?
+  \item The stadia seem on average to be symmetric.
+  \item MINOR:
+  \item New citation for earlier observation.
+  \item A couple of clarifications of our descriptions of cited papers.
+  \item Stochastic are also important for a PNAS 2010 work.
+  \end{enumerate}
+
+  Referee 3
+  \begin{enumerate}
+  \item Skepticism about the effect of flattening, in terms of
+    coherence times in particular.
+  \item Want more clarity with regard to how we divide up the cell to
+    compute coherence times.
+  \item Starry night patterns are inconsistent with experimetns.
+    Membrane diffusion may alleviate this problem.
+  \item MINOR:
+  \item Clarification in caption.  I don't quite understand.
+  \item Figure 2 units for colormap.
+  \item Figure 4 caption needs some title for the figure, not just
+    ``We display here...''.
+  \item ``coli'' should not be capitalized.
+  \item FtsZ polymer does not form on the cell wall but near the
+    cytoplasmic side of the inner membrane.
+  \end{enumerate}
+}
 
@@
 \section*{Acknowledgments}
-Cras egestas velit mauris, eu mollis turpis pellentesque sit
-amet. Interdum et malesuada fames ac ante ipsum primis in
-faucibus. Nam id pretium nisi. Sed ac quam id nisi malesuada
-congue. Sed interdum aliquet augue, at pellentesque quam rhoncus
-vitae.
 

### 2015-06-11 paper/response-to-referees.txt
add response-to-referees.txt outlining what needs doing Tested everything on bennet.

Dear Editor,

We thank the referees for their helpful comments.  We have made a
number of revisions to our paper in response to their suggestions,
which we enumerate below, along with our response to each comment and
suggestion of the referees.  Each referee had several major concerns
and a few minor suggestions, which we will address in the order that
they were given, beginning with Referee #1.

Referee #1.

1. The largest concern of Referee #1 was our choice of Huang et al's
model for our simulations.  The referee acknowledges that we can stay
with this model, but feels that our justifaction that this model is
inadequate.  The referee objects that the fact that this model has
been widely is an inappropriate justification.  While we agree that
this alone is not a sufficient reason for studying this model, we do
believe that it is relevant: this is not some obscure older model that
we are testing, but rather the basis of all more recent models.

 FIXME NEED TO COME UP WITH MORE JUSTIFICATION? OR SIMPLY STATE THAT
 WE THINK IT IS RELEVANT?

2. As a secondary point, the referee points out we cannot conclude
that some other deterministic model could not demonstrate chaotic
behavior that explains the experimental results of Mannik et al.  We
agree that this cannot be ruled out, and have ADDED CLARIFICATION
WHERE?

3. The referee when looking at Figure 4 observes that the stadium
shapes exhibit osciallation that is largely bipolar, and expresses
doubt in our claim that the oscillations in stadium shapes are
irregular.  In particular, the referee points out that if we average
over many periods, we would find that the oscillations are indeed
bipolar.  We agree with this statement, but not with the conclusion.
Averaging the locations of the maxima would indeed miss the point of
the comparison with experiment, which is in examining the sequence of
locations of maxima.

We have EDITED WHAT? to moderate our claims.

Minor points:

4. The referee points out that MinD clusters had been considered prior
to Huang.  We have EDITED WHAT to include this reference.

5. ANOTHER EDIT TO DISCUSSION OF EARLIER WORK.

6. The referee points out that two previous works have also
demonstrated that stochastic simulations are needed in order to
explain WHAT?.  WE HAVE EDITED OUR DISCUSSION TO ILLUSTRATE THIS.

Referee #3.

7. The referee #3 also expressed doubt about our conclusion with
regard to the effect of irregular shape which we base on our stadium
models.  Unlike the previous referee, the criticism is based not on
the spatial output (Figure 4), but rather on the reported coherence
times.  We had attempted to make a distinction between spatially
irregular oscillation and temporally irregular oscillations.  This
distinction was evidently not clear, so we have ADDED AN EXPLICIT
DISCUSSION OF THE FACT THAT WE OBSERVE A GREATER DISRUPTION IN
TEMPORAL REGULARITY IN THE IRREGULARLY SHAPED CELLS.  FIXME WHAT DO WE
DO ABOUT SPATIAL IRREGULARITY?

8. The referee also questioned how the cell was divided in
order to perform the coherence time calculations, pointing out that a
smaller region could lead to a shorter coherence time.  EXPLAIN HOW WE
DIVIDE THE CELLS UP IN THIRDS BY VOLUME? IT'S AWKWARD THAT WE DON'T
DIVIDE ALONG LONG AXIS.

9. The referee points out that the "starry night" patterns are
inconsistent with experiments.  We agree with the referee that
membrane diffusion will alleviate this problem.  WE HAVE ADDED A
CLARIFICATION TO THIS EFFECT WHERE?

Minor points:

10. The referee requested a clarification to the caption of Figure 1,
which we HAVE ADDED.

11. The referee suggests that we should write $\mu m^2$ over $\mu^2$
for square microns.  We have made this change.  FIXME DO SO.

12. The referee suggested a title is needed in the caption of Figure
number 4.  WE HAVE ADDED A TITLE.

13. As requested WE HAVE CORRECTED THE CAPITALIZATION OF "E. coli".
FIXME.

14. The referee corrected us regarding the location at which the FtsZ
polymer forms, which is not on the cell wall, but rather near the
cytoplasmic side of the inner membrane.

### 2015-06-15 paper/response-to-referees.txt
assign jobs to Jeff and David
actually answer two of the referees' comments Tested everything on bennet.

@@
 
+ <Jeff gives this a quick shot!>
+
  FIXME NEED TO COME UP WITH MORE JUSTIFICATION? OR SIMPLY STATE THAT
@@
 behavior that explains the experimental results of Mannik et al.  We
-agree that this cannot be ruled out, and have ADDED CLARIFICATION
-WHERE?
+agree that this cannot be ruled out, and have added mention of this to
+our "Comparison of Experimental and Stadium Shapes", and have made
+even more tentative our suggestion in the summary that other similar
+deterministic models may also prove to be non-chaotic.
 
@@
 
+  <Jeff does this.>
+
 Minor points:
 
-4. The referee points out that MinD clusters had been considered prior
-to Huang.  We have EDITED WHAT to include this reference.
+4. The referee points out that MinD clusters had been considered by
+Kruse prior to Huang.  We thank the referee for pointing out this
+oversight, and have updated our background section to include this
+reference and more accurately reflect the historical development.
 
 5. ANOTHER EDIT TO DISCUSSION OF EARLIER WORK.
+
+  <David does this.>
 
@@
 explain WHAT?.  WE HAVE EDITED OUR DISCUSSION TO ILLUSTRATE THIS.
+
+  <David does this.>
 
@@
 
+  <Jeff does this.>
+
 8. The referee also questioned how the cell was divided in
@@
 
+  <Jeff discusses this.  David thinks it was by thirds of volume.>
+
 9. The referee points out that the "starry night" patterns are
@@
 CLARIFICATION TO THIS EFFECT WHERE?
+
+  <David>
 
@@
 
+  <Jeff>
+
 11. The referee suggests that we should write $\mu m^2$ over $\mu^2$
 for square microns.  We have made this change.  FIXME DO SO.
+
+  <David>
 
@@
 
+  <Jeff>
+
 13. As requested WE HAVE CORRECTED THE CAPITALIZATION OF "E. coli".
 FIXME.
+
+  <David>
 
@@
 cytoplasmic side of the inner membrane.
+
+  <David>

### 2015-06-15 paper/plos.tex
actually answer two of the referees' comments Tested everything on bennet.

@@
 diffusion and membrane attachment, but do not combine into compound
-states~\cite{meinhardt2001pattern}.  In 2003 Huang improved upon this
-approach with a simple and very successful simulation model based on
-MinD-MinE combination, ATPase hydrolysis, and MinD membrane attachment
-that exhibits accurate MinD oscillations in cylindrical
-cells~\cite{huang2003dynamic}. In this model cytoplasmic MinD is
-recruited to the membrane by MinD that is already clustered there
-(following observed non-linear attachment of MinD on the cell
+states~\cite{meinhardt2001pattern}.  Kruse extended this model by
+incorporating recruitment and clustering of
+MinD~\cite{kruse2002dynamic}.  In 2003 Huang improved upon Kruse's
+approach with a simple and very successful simulation model that
+incorporates MinD-MinE combination, ATPase hydrolysis, and MinD
+membrane attachment that exhibits accurate MinD oscillations in
+cylindrical cells~\cite{huang2003dynamic}. In this model cytoplasmic
+MinD is recruited to the membrane by MinD that is already clustered
+there (following observed non-linear attachment of MinD on the cell
 membrane~\cite{hu2002dynamic,shih2002division}), and is stationary
@@
 deterministic model shows uniformly bipolar oscillation.  We conclude
-that the model is \emph{not} chaotic (which would show irregularity in
-the deterministic computation), but rather that the irregularity
+that this model is \emph{not} chaotic (which would show irregularity
+in the deterministic computation), but rather that the irregularity
 results purely from stochastic processes.  From these results and how
@@
 is inadequate to explain experimental observations of the locations of
-density maxima of the MinD protein.
+density maxima of the MinD protein.  We note, however, that it is
+possible that there exists another deterministic model that does exhibit
+chaotic behavior.
 
@@
   kruse2007experimentalist}.  The regular oscillations in the
-deterministic case also allow us to conclude that the model is
+deterministic case also allow us to conclude that Huang's model is
 non-chaotic.  Because of their similar construction, we anticipate
 that recent variants of the model~\cite{bonny2013membrane,
-  fange2006noise, halatek2012highly} would also prove to be
+  fange2006noise, halatek2012highly} may also prove to be
 non-chaotic.

### 2015-06-16 paper/plos.tex
respond to one more of the referee comments Tested everything on bennet.

@@
 
-Several models \cite{fange2006noise, bonny2013membrane,
+Several models \cite{bonny2013membrane,
   halatek2012highly} modify Huang's original model to more accurately
@@
 significant role.  To treat this, there have been a number of
-variations of the Huang 2003 model that stochastically simulate
-similar reaction-diffusion equations~\cite{fange2006noise,
+applications of the Huang 2003 model that stochastically simulate the
+same reaction-diffusion equations~\cite{fange2006noise,
   kerr2006division}.  These studies largely confirm the results of
@@
 model~\cite{huang2003dynamic}, which has been widely
-used~\cite{hattne2005stochastic,huang2004min,kerr2006division} in both
+used~\cite{hattne2005stochastic,huang2004min,kerr2006division, fange2006noise} in both
 deterministic and stochastic variants, to study flattened cells of

### 2015-06-20 paper/plos.tex
first two jeff-assigned responses

@@
 model~\cite{huang2003dynamic}, which has been widely
-used~\cite{hattne2005stochastic,huang2004min,kerr2006division, fange2006noise} in both
-deterministic and stochastic variants, to study flattened cells of
-$0.4\micron$ thickness that are similar to those observed by M\"annik
-\emph{et al.}~\cite{mannik2009bacterial}.
+used~\cite{hattne2005stochastic,huang2004min,kerr2006division,
+  fange2006noise} in both deterministic and stochastic variants, to
+study flattened cells of $0.4\micron$ thickness that are similar to
+those observed by M\"annik \emph{et al.}~\cite{mannik2009bacterial}.
+\fixme{This allows us to test the performance of this important model
+  in more extreme situations than has been done previously, furthering
+  considerably our understanding of how and to what extent it breaks
+  down. It will be valuable in the future to compare these results
+  against similar tests of more recent models, in order to better
+  understand how they gain advantage.}
 
@@
 maxima, although there are locations on the edges of the cells where
-experiment shows maxima occurring that we never see in our simulations,
-suggesting that the model does not precisely reflect the experiment.
-We also note that the stadium shapes in Fig.~\ref{randst-plot-ave}
-appear to have maxima location irregularity that is qualitatively
-similar to our irregular shapes and to experiment.
+experiment shows maxima occurring that we never see in our
+simulations, suggesting that the model does not precisely reflect the
+experiment.  We also note that the stadium shapes in
+Fig.~\ref{randst-plot-ave} appear to have maxima location irregularity
+\fixme{within a small number of periods} that is
+qualitatively similar to our irregular shapes and to experiment.
 

### 2015-06-20 paper/response-to-referees.txt
respond to one more of the referee comments Tested everything on bennet.
more changes on Saturday

@@
 
-5. ANOTHER EDIT TO DISCUSSION OF EARLIER WORK.
-
-  <David does this.>
+5. Based on the referee's suggestion, we have clarified that reference
+11 does not extend Huang's model, except in that it simulates the same
+reaction-diffusion equations stochastically.
 
@@
 DISCUSSION OF THE FACT THAT WE OBSERVE A GREATER DISRUPTION IN
-TEMPORAL REGULARITY IN THE IRREGULARLY SHAPED CELLS.  FIXME WHAT DO WE
-DO ABOUT SPATIAL IRREGULARITY?
+TEMPORAL REGULARITY IN THE IRREGULARLY SHAPED CELLS.  JEFFSAYS{Changed
+the last sentence before the conclusion.  I don't think it needs much
+changing except maybe moderate our claims a bit (which I tried to
+do).}  FIXME WHAT DO WE DO ABOUT SPATIAL IRREGULARITY?
 
@@
 
-8. The referee also questioned how the cell was divided in
-order to perform the coherence time calculations, pointing out that a
-smaller region could lead to a shorter coherence time.  EXPLAIN HOW WE
-DIVIDE THE CELLS UP IN THIRDS BY VOLUME? IT'S AWKWARD THAT WE DON'T
-DIVIDE ALONG LONG AXIS.
+8. The referee also questioned how the cell was divided in order to
+perform the coherence time calculations, pointing out that a smaller
+region could lead to a shorter coherence time.  EXPLAIN HOW WE DIVIDE
+THE CELLS UP IN THIRDS BY VOLUME? IT'S AWKWARD THAT WE DON'T DIVIDE
+ALONG LONG AXIS.  JEFFSAYS{Bad news here.  It looks like I did this
+dividing up the cells by eye.  Originally the slices were used to
+created the box plots, which was only a way to visualize the data in
+smaller time domains, so there's wasn't really any disadvantage to
+doing it roughly like this (we even had the visually appealing little
+colored diagrams on the sides of the box plots).  Not sure what to say
+abou this in text.}
 
@@
 10. The referee requested a clarification to the caption of Figure 1,
-which we HAVE ADDED.
+which we HAVE ADDED. JEFFSAYS{huh?}
 

### 2015-06-20 paper/plos.tex
more changes on Saturday

@@
   \includegraphics[width=16cm]{../paper/plot-ave}
-  \caption{We display here arrows depicting successive maxima in space
-    and and time overlayed on a color plot of the total MinD density
+  \caption{Arrows depicting successive maxima in space
+    and time overlayed on a color plot of the total MinD density
     averaged over the same time period.  The simulation time covered
@@
 Fig.~\ref{randst-plot-ave} appear to have maxima location irregularity
-\fixme{within a small number of periods} that is
+\fixme{within the time domain of a small number of periods, as
+  compared to the more long term coherence discussed below,} that is
 qualitatively similar to our irregular shapes and to experiment.
@@
 From the stochastic correlation data, we conclude that irregularity of
-shape has only a moderate affect on the temporal regularity of the
-oscillatory behavior, with even the very distorted shape~\emph{B}
+shape has \fixme{a distinct yet moderate} affect on the temporal regularity of
+the oscillatory behavior, with even the very distorted shape~\emph{B}
 exhibiting only a factor of two greater decoherence.
@@
 irregularity in the shape of flattened cells.  Thus we conclude that
-it is the flattening of the cells, and the accompanying expansion in the
-transverse direction, rather than their irregular shape that primarily
-causes the disruption of regular bipolar oscillation which is observed
-by M\"annik \emph{et al.}~\cite{mannik2012robustness}.
+it is \fixme{primarily} the flattening of the cells, and the
+accompanying expansion in the transverse direction, \fixme{deleted
+  some text} that causes the disruption of regular bipolar oscillation
+which is observed by M\"annik \emph{et
+  al.}~\cite{mannik2012robustness}.
 

### 2015-06-21 paper/response-to-referees.txt
edits from talking with Jeff

@@
 believe that it is relevant: this is not some obscure older model that
-we are testing, but rather the basis of all more recent models.
-
- <Jeff gives this a quick shot!>
-
- FIXME NEED TO COME UP WITH MORE JUSTIFICATION? OR SIMPLY STATE THAT
- WE THINK IT IS RELEVANT?
+we are testing, but rather the basis of all more recent models.  We
+believe that the limitations of this model are of interest, and have
+added some discussion to the end of the introduction section
+explaining this.
 
@@
 
-We have EDITED WHAT? to moderate our claims.
+We have edited the "comparison of experimental and stadium shapes"
+section to moderate our claims regarding the spatial irregularity of the
+experimental and stadium shapes as predicted by the stochastic model.
 
-  <Jeff does this.>
+<Jeff will figure out what other places need to be changed to reflect
+this reduced claim. EDIT ELSEHWERE AND EDIT HERE!>
 
@@
 the spatial output (Figure 4), but rather on the reported coherence
-times.  We had attempted to make a distinction between spatially
-irregular oscillation and temporally irregular oscillations.  This
-distinction was evidently not clear, so we have ADDED AN EXPLICIT
-DISCUSSION OF THE FACT THAT WE OBSERVE A GREATER DISRUPTION IN
-TEMPORAL REGULARITY IN THE IRREGULARLY SHAPED CELLS.  JEFFSAYS{Changed
-the last sentence before the conclusion.  I don't think it needs much
-changing except maybe moderate our claims a bit (which I tried to
-do).}  FIXME WHAT DO WE DO ABOUT SPATIAL IRREGULARITY?
+times.  We agree with the referee that our concluding sentence
+immediately prior to the conclusion section was unjustified, and have
+edited this sentence to reflect the referee's objections.
 
-  <Jeff does this.>
+<Jeff will check if we talk about decoherence times later>
 
@@
 
-  <Jeff discusses this.  David thinks it was by thirds of volume.>
+  <Jeff needs to find out how much volume in each section! Then write
+  text explaining this...>
 
@@
 
-10. The referee requested a clarification to the caption of Figure 1,
-which we HAVE ADDED. JEFFSAYS{huh?}
-
-  <Jeff>
+10. As the referee requested, we have clarified the caption of Figure
+1, to include the fact that these reactions are for a Min system
+model that is used in this work.
 
@@
 12. The referee suggested a title is needed in the caption of Figure
-number 4.  WE HAVE ADDED A TITLE.
-
-  <Jeff>
+number 4.  We have edited the caption to begin with an appropriate
+title-like sentence fragment, rather than "We display here...".
 

### 2015-06-21 paper/plos.tex
edits from talking with Jeff

@@
 those observed by M\"annik \emph{et al.}~\cite{mannik2009bacterial}.
-\fixme{This allows us to test the performance of this important model
-  in more extreme situations than has been done previously, furthering
-  considerably our understanding of how and to what extent it breaks
-  down. It will be valuable in the future to compare these results
-  against similar tests of more recent models, in order to better
-  understand how they gain advantage.}
+This allows us to test the performance of this important model in more
+extreme situations than has been done previously, furthering our
+understanding of how and to what extent it breaks down.
 
@@
   \includegraphics[width=8.7cm]{reactions}
-  \caption{Reactions included in the model of Huang \emph{et
-      al.}~\cite{huang2003dynamic}.}\label{fig:reactions}
+  \caption{Reactions included in the Min system model of Huang
+    \emph{et al.}, which is used in this
+    work~\cite{huang2003dynamic}.}\label{fig:reactions}
 \end{figure}
@@
 
-The predictions of the stochastic model are roughly similar to the
+The predictions of the stochastic model show some similarity to the
 experimental results in terms of irregularity of the locations of
-maxima, although there are locations on the edges of the cells where
-experiment shows maxima occurring that we never see in our
-simulations, suggesting that the model does not precisely reflect the
-experiment.  We also note that the stadium shapes in
+maxima, but the stochastic model displays significantly less
+variation in the direction of oscillations than experiment, suggesting
+inadequacies in the model.  We also note that the stadium shapes in
 Fig.~\ref{randst-plot-ave} appear to have maxima location irregularity
-\fixme{within the time domain of a small number of periods, as
-  compared to the more long term coherence discussed below,} that is
-qualitatively similar to our irregular shapes and to experiment.
+that is qualitatively similar to our irregular shapes: in both
+stochastic simulations the overall oscillation is largely bipolar, but
+with irregularity in the locations of the maxima that form at each
+end.
 
@@
 From the stochastic correlation data, we conclude that irregularity of
-shape has \fixme{a distinct yet moderate} affect on the temporal regularity of
-the oscillatory behavior, with even the very distorted shape~\emph{B}
-exhibiting only a factor of two greater decoherence.
+shape leads to a decrease in temporal regularity of the oscillatory
+behavior, although even the very distorted shape~\emph{B} exhibiting
+only a factor of two greater decoherence.
 
@@
 irregularity in the shape of flattened cells.  Thus we conclude that
-it is \fixme{primarily} the flattening of the cells, and the
-accompanying expansion in the transverse direction, \fixme{deleted
-  some text} that causes the disruption of regular bipolar oscillation
-which is observed by M\"annik \emph{et
+it may be the flattening of the cells, and the accompanying
+expansion in the transverse direction, that causes the disruption of
+regular bipolar oscillation which is observed by M\"annik \emph{et
   al.}~\cite{mannik2012robustness}.

### 2015-06-26 paper/response-to-referees.txt
answer one more minor objection Tests skipped!

@@
 
-6. The referee points out that two previous works have also
-demonstrated that stochastic simulations are needed in order to
-explain WHAT?.  WE HAVE EDITED OUR DISCUSSION TO ILLUSTRATE THIS.
-
-  <David does this.>
+6. The referee points out that we failed to mention that stochastic
+simulations are needed to explain the experimentally observed
+length-dependence of fluctuations in the Min system.  We have added
+mention of this additional evidence of the importance of inclusion of
+stochastic effects, in the paragraph suggested by the referee.
 

### 2015-06-26 paper/plos.tex
answer one more minor objection Tests skipped!

@@
 
-{
-  \color{red}
-  Referee 1.
-  \begin{enumerate}
-  \item Need to better justify use of Huang.
-  \item Couldn't another deterministic model predict Mannik's results?
-  \item The stadia seem on average to be symmetric.
-  \item MINOR:
-  \item New citation for earlier observation.
-  \item A couple of clarifications of our descriptions of cited papers.
-  \item Stochastic are also important for a PNAS 2010 work.
-  \end{enumerate}
-
-  Referee 3
-  \begin{enumerate}
-  \item Skepticism about the effect of flattening, in terms of
-    coherence times in particular.
-  \item Want more clarity with regard to how we divide up the cell to
-    compute coherence times.
-  \item Starry night patterns are inconsistent with experimetns.
-    Membrane diffusion may alleviate this problem.
-  \item MINOR:
-  \item Clarification in caption.  I don't quite understand.
-  \item Figure 2 units for colormap.
-  \item Figure 4 caption needs some title for the figure, not just
-    ``We display here...''.
-  \item ``coli'' should not be capitalized.
-  \item FtsZ polymer does not form on the cell wall but near the
-    cytoplasmic side of the inner membrane.
-  \end{enumerate}
-}
-
 \section*{Introduction}
@@
 prediction of fluctuations in the predicted
-behavior~\cite{kruse2007experimentalist}.  Both deterministic and
+behavior~\cite{kruse2007experimentalist}, including the observation of
+stochastic switching in short cells instead of a transition to static
+behavior as would be predicted from a deterministic
+model~\cite{fischer2010intra}.  Both deterministic and
 stochastic models are widely used throughout systems

### 2015-06-27 paper/plos.tex
changes

@@
   which is based on the same reaction-diffusion equations, does
-  predict spatially irregular oscillations as observed in experiment.
+  predict spatially irregular oscillations as observed in experiment\fixme{, although they are generally more bipolar}.
   We further report simulations of flattened but more symmetric
-  shapes, and find that it is the flattening and lateral expansion
+  shapes, and find that it \fixme{may be?} is the flattening and lateral expansion
   rather than the asymmetry of the cell shapes that causes the
@@
 the top of the cell and the number of proteins in a segment at the
-bottom of the cell.  Fig.~\ref{fig:corr-B} shows this plot for shape
+bottom of the cell.  \fixme{this is where Ill need to add the volumes} Fig.~\ref{fig:corr-B} shows this plot for shape
 \emph{B} and stadium \emph{B}.  Here we plot correlations of
@@
 \section*{Conclusion}
-We find agreement between our stochastic simulations and experiments
+\fixme{We find a certain amount of qualitive agreement between our stochastic simulations and experiments showing disrupted MinD oscillations in asymmetric flattened E.
+coli cells.}We find agreement between our stochastic simulations and experiments
 showing disrupted bipolar MinD oscillation in asymmetric flattened
@@
 experimentally, our simulations predict that MinD maxima will form in
-a spatially irregular sequence of locations.  This result builds upon
+a spatially irregular sequence of locations, \fixme{albeit with a with more course scale bipolar regularity.}  This result builds upon
 existing results showing that this model and its variants are

### 2015-07-01 paper/response-to-referees.txt
more changes, added volumes, addressed stadium irregularity problem, and added a maybe about flattening in abstract

@@
 We have edited the "comparison of experimental and stadium shapes"
-section to moderate our claims regarding the spatial irregularity of the
+section, the conclusion, and the abstract to moderate our claims regarding the spatial irregularity of the
 experimental and stadium shapes as predicted by the stochastic model.
@@
 edited this sentence to reflect the referee's objections.
+JEFFSAYS{The only thing I could see to change in addition to the above is that 
+I added a 'maybe' to the abstract.  Don't think we need to note it.}
 
@@
 abou this in text.}
+JEFFSAYS {I figured we should do this one together because I really didn't
+know what to say.  Here's the volumes:
+shape A - left 1.29 mid 3.29 right 2.12
+shape B - left 1.41 mid 2.48 right 1.91
+stad A - left 1.91 mid 2.62 right 1.84
+stad B - left 1.88 mid 2.49 right 1.82}
 

### 2015-07-01 paper/plos.tex
more changes, added volumes, addressed stadium irregularity problem, and added a maybe about flattening in abstract

@@
   which is based on the same reaction-diffusion equations, does
-  predict spatially irregular oscillations as observed in experiment\fixme{, although they are generally more bipolar}.
+  predict spatially irregular oscillations\fixme{, although they are still somewhat more bipolar than seen in experiment}.
   We further report simulations of flattened but more symmetric
-  shapes, and find that it \fixme{may be?} is the flattening and lateral expansion
+  shapes, and find that it \fixme{may be} the flattening and lateral expansion
   rather than the asymmetry of the cell shapes that causes the
@@
 \fixme{We find a certain amount of qualitive agreement between our stochastic simulations and experiments showing disrupted MinD oscillations in asymmetric flattened E.
-coli cells.}We find agreement between our stochastic simulations and experiments
+coli cells.}  We find agreement between our stochastic simulations and experiments
 showing disrupted bipolar MinD oscillation in asymmetric flattened
@@
 experimentally, our simulations predict that MinD maxima will form in
-a spatially irregular sequence of locations, \fixme{albeit with a with more course scale bipolar regularity.}  This result builds upon
+a spatially irregular sequence of locations, \fixme{albeit with a somewhat more course scale bipolar regularity.}  This result builds upon
 existing results showing that this model and its variants are

### 2015-07-27 paper/response-to-referees.txt
fix a couple of very easy referee suggestions

@@
 
-11. The referee suggests that we should write $\mu m^2$ over $\mu^2$
-for square microns.  We have made this change.  FIXME DO SO.
-
-  <David>
+11. The referee suggests that we should consistently write $\mu m^2$
+over $\mu^2$ for square microns.  We have made this change to the plot
+that used $\mu^2$.
 
@@
 
-13. As requested WE HAVE CORRECTED THE CAPITALIZATION OF "E. coli".
-FIXME.
-
-  <David>
+13. As requested we have corrected the capitalization of "E. coli".
 

### 2015-07-27 paper/plos.tex
fix a couple of very easy referee suggestions

@@
 \section*{Author Summary}
-  When an E. Coli cell divides it must split into two relatively equal
+  When an E. coli cell divides it must split into two relatively equal
   volumes in order to survive.  One mechanism that aids in this
@@
 correlation times up to 500 seconds, a biologically relevant
-timescale.  E. Coli cell doubling times vary widely depending on
+timescale.  E. coli cell doubling times vary widely depending on
 environmental conditions, but will often be between 20 minutes to 100

### 2015-07-27 pyplots/single-image-plot.py

@@ -104,7 +104,7 @@ cax = divider.append_axes("right", "3%", pad="1%")
 # cbar = plt.colorbar(cax=cax,ticks=[0,maxval])
 # cbar.ax.set_yticklabels(['0', 'max'])
 cbar = plt.colorbar(cax=cax)
-cbar.set_label('molecules/$\mu^2$')
+cbar.set_label('molecules/$\mu m^2$')
 
 #plt.colorbar(ticks=[])
 plt.tight_layout()

### 2015-07-28 paper/plos.tex
answer one more referee comment

@@
 with lopsided volumes.  Instrumental to this process in
-\emph{Escherichia coli} is a long FtsZ polymer chain that develops on
+\emph{Escherichia coli} is a long FtsZ polymer chain that develops
+near
 the cell wall in the center region of the cell, helping dictate the

### 2015-07-30 paper/plos.tex
add clarification that starry night is not observed experimentally

@@
 build up, as recruitment leads to clusters of MinD forming on the wall
-and then subsequently dissipating.  This results from the omission of
-diffusion along the membrane from Huang's model, which would allow
-these recruitment clusters to spread out.  Experiments have confirmed
-that diffusion along the membrane does occur, albeit with a rate two
-orders of magnitude lower than that in the
-cytoplasm~\cite{meacci2006mobility}.  The `stars' in the effect typically
-last for around 10 seconds. The membrane-bound proteins will diffuse
-by a distance of around one micron during this time, which is enough
-to spread out across the polar section of the one micron diameter
-wild-type pill cells.  As we see below, the flattened, irregular cells
-are large enough that this one micron blurring would not completely
-eliminate this `starry night' effect.
+and then subsequently dissipating.  This result, which is not observed
+in experiments, stems from the omission of diffusion along the
+membrane from Huang's model, which would allow these recruitment
+clusters to spread out.  Experiments have confirmed that diffusion
+along the membrane does occur, albeit with a rate two orders of
+magnitude lower than that in the cytoplasm~\cite{meacci2006mobility}.
+The `stars' in the effect typically last for around 10 seconds. The
+membrane-bound proteins will diffuse by a distance of around one
+micron during this time, which is enough to spread out across the
+polar section of the one micron diameter wild-type pill cells.  As we
+see below, the flattened, irregular cells are large enough that this
+one micron blurring might not completely eliminate this `starry night'
+effect.
 

### 2015-08-01 paper/response-to-referees.txt
answer one more referee comment
add clarification that starry night is not observed experimentally
edits while meeting with Jeff and Rene

@@
 3. The referee when looking at Figure 4 observes that the stadium
-shapes exhibit osciallation that is largely bipolar, and expresses
+shapes exhibit oscillation that is largely bipolar, and expresses
 doubt in our claim that the oscillations in stadium shapes are
@@
 We have edited the "comparison of experimental and stadium shapes"
-section, the conclusion, and the abstract to moderate our claims regarding the spatial irregularity of the
-experimental and stadium shapes as predicted by the stochastic model.
-
-<Jeff will figure out what other places need to be changed to reflect
-this reduced claim. EDIT ELSEHWERE AND EDIT HERE!>
+section, the conclusion, and the abstract to moderate our claims
+regarding the spatial irregularity of the experimental and stadium
+shapes as predicted by the stochastic model.
 
@@
 edited this sentence to reflect the referee's objections.
-JEFFSAYS{The only thing I could see to change in addition to the above is that 
-I added a 'maybe' to the abstract.  Don't think we need to note it.}
-
-<Jeff will check if we talk about decoherence times later>
 
@@
 perform the coherence time calculations, pointing out that a smaller
-region could lead to a shorter coherence time.  EXPLAIN HOW WE DIVIDE
-THE CELLS UP IN THIRDS BY VOLUME? IT'S AWKWARD THAT WE DON'T DIVIDE
-ALONG LONG AXIS.  JEFFSAYS{Bad news here.  It looks like I did this
-dividing up the cells by eye.  Originally the slices were used to
-created the box plots, which was only a way to visualize the data in
-smaller time domains, so there's wasn't really any disadvantage to
-doing it roughly like this (we even had the visually appealing little
-colored diagrams on the sides of the box plots).  Not sure what to say
-abou this in text.}
-JEFFSAYS {I figured we should do this one together because I really didn't
-know what to say.  Here's the volumes:
-shape A - left 1.29 mid 3.29 right 2.12
-shape B - left 1.41 mid 2.48 right 1.91
-stad A - left 1.91 mid 2.62 right 1.84
-stad B - left 1.88 mid 2.49 right 1.82}
-
-  <Jeff needs to find out how much volume in each section! Then write
-  text explaining this...>
+region could lead to a shorter coherence time.  We have added an
+explanation of how we divided the cell into three sections, and gave
+numbers showing the relative volume of the sections.  These were not
+identical, and thus will have some effect on the correlation times
+computed.  However, the region volumes are roughly similar, so we do
+not expect this effect to be dramatic.
 
@@
 inconsistent with experiments.  We agree with the referee that
-membrane diffusion will alleviate this problem.  WE HAVE ADDED A
-CLARIFICATION TO THIS EFFECT WHERE?
-
-  <David>
+membrane diffusion will alleviate this problem.  We have added a
+clarification that this effect is *not* observed in experiment.
 
@@
 polymer forms, which is not on the cell wall, but rather near the
-cytoplasmic side of the inner membrane.
-
-  <David>
+cytoplasmic side of the inner membrane.  We have corrected this
+statement in the first paragraph of the introduction.

### 2015-08-01 paper/plos.tex
edits while meeting with Jeff and Rene

@@
   the experimentally observed behavior, while the stochastic model,
-  which is based on the same reaction-diffusion equations, does
-  predict spatially irregular oscillations\fixme{, although they are still somewhat more bipolar than seen in experiment}.
+  which is based on the same reaction-diffusion equations,
+  predicts more spatially irregular oscillations.
   We further report simulations of flattened but more symmetric
-  shapes, and find that it \fixme{may be} the flattening and lateral expansion
-  rather than the asymmetry of the cell shapes that causes the
-  irregular oscillation behavior.
+  shapes, which suggest that the flattening and lateral expansion may
+  contribute as much to the irregular oscillation behavior as the
+  asymmetry of the cell shapes.
 
@@
 the top of the cell and the number of proteins in a segment at the
-bottom of the cell.  \fixme{this is where Ill need to add the volumes} Fig.~\ref{fig:corr-B} shows this plot for shape
-\emph{B} and stadium \emph{B}.  Here we plot correlations of
-correlation times up to 500 seconds, a biologically relevant
-timescale.  E. coli cell doubling times vary widely depending on
-environmental conditions, but will often be between 20 minutes to 100
+bottom of the cell.  The ``top'' and ``bottom'' regions for computing
+the correlation time were established by dividing the long axis into
+thirds.  This resulted in regions at the top and bottom ranging from
+19\% to 33\% of the cell volume for shapes \emph{A} and \emph{B}, with
+the stadium shapes featuring 30\% of the volume in the top and bottom
+regions.  Fig.~\ref{fig:corr-B} shows this plot for shape \emph{B} and
+stadium \emph{B}.  Here we plot correlations of correlation times up
+to 500 seconds, a biologically relevant timescale.  E. coli cell
+doubling times vary widely depending on environmental conditions, but
+will often be between 20 minutes to 100
 minutes~\cite{pierucci1972chromosome}, while fluorescent microscopy
@@
 \section*{Conclusion}
-\fixme{We find a certain amount of qualitive agreement between our stochastic simulations and experiments showing disrupted MinD oscillations in asymmetric flattened E.
-coli cells.}  We find agreement between our stochastic simulations and experiments
-showing disrupted bipolar MinD oscillation in asymmetric flattened
-E. coli cells~\cite{mannik2012robustness}.  As observed
+We find qualitative agreement between our stochastic simulations and
+experiments showing disrupted bipolar MinD oscillation in asymmetric
+flattened E. coli cells~\cite{mannik2012robustness}.  As observed
 experimentally, our simulations predict that MinD maxima will form in
-a spatially irregular sequence of locations, \fixme{albeit with a somewhat more course scale bipolar regularity.}  This result builds upon
-existing results showing that this model and its variants are
-effective in a variety of wild-type and mutated cell
-shapes~\cite{fange2006noise, varma2008min, kruse2007experimentalist},
-and reinforces that stochastic variations of Huang's 2003
-model~\cite{fange2006noise, kerr2006division} has considerable
-predictive power beyond the standard wild-type cell.
+a spatially irregular sequence of locations, which follow an overall
+bipolar trend.  This result builds upon existing results showing that
+this model and its variants are effective in a variety of wild-type
+and mutated cell shapes~\cite{fange2006noise, varma2008min,
+  kruse2007experimentalist}, and reinforces that stochastic variations
+of Huang's 2003 model~\cite{fange2006noise, kerr2006division} has
+considerable predictive power beyond the standard wild-type cell.
 

### 2015-08-03 paper/plos.tex
add "changed" macro to highlight changes we made.

@@
 
+%\newcommand{\changed}[1]{{\color{red}#1}}
+\newcommand{\changed}[1]{}
+
 % Remove comment for double spacing
@@
   which is based on the same reaction-diffusion equations,
-  predicts more spatially irregular oscillations.
+  \changed{predicts more spatially irregular oscillations}.
   We further report simulations of flattened but more symmetric
-  shapes, which suggest that the flattening and lateral expansion may
+  shapes, \changed{which suggest that the flattening and lateral expansion may
   contribute as much to the irregular oscillation behavior as the
-  asymmetry of the cell shapes.
+  asymmetry of the cell shapes}.
 
@@
 \section*{Author Summary}
-  When an E. coli cell divides it must split into two relatively equal
+  When an E. \changed{coli} cell divides it must split into two relatively equal
   volumes in order to survive.  One mechanism that aids in this
@@
 \emph{Escherichia coli} is a long FtsZ polymer chain that develops
-near
+\changed{near}
 the cell wall in the center region of the cell, helping dictate the
@@
 diffusion and membrane attachment, but do not combine into compound
-states~\cite{meinhardt2001pattern}.  Kruse extended this model by
+states~\cite{meinhardt2001pattern}.  \changed{Kruse extended this model by
 incorporating recruitment and clustering of
 MinD~\cite{kruse2002dynamic}.  In 2003 Huang improved upon Kruse's
-approach with a simple and very successful simulation model that
+approach} with a simple and very successful simulation model that
 incorporates MinD-MinE combination, ATPase hydrolysis, and MinD
@@
 
-Several models \cite{bonny2013membrane,
-  halatek2012highly} modify Huang's original model to more accurately
+Several models \changed{\cite{bonny2013membrane,
+  halatek2012highly}} modify Huang's original model to more accurately
 reflect experimental findings, which were published after his 2003
@@
 significant role.  To treat this, there have been a number of
-applications of the Huang 2003 model that stochastically simulate the
+\changed{applications} of the Huang 2003 model that stochastically simulate the
 same reaction-diffusion equations~\cite{fange2006noise,
@@
 prediction of fluctuations in the predicted
-behavior~\cite{kruse2007experimentalist}, including the observation of
+behavior~\cite{kruse2007experimentalist}\changed{, including the observation of
 stochastic switching in short cells instead of a transition to static
 behavior as would be predicted from a deterministic
-model~\cite{fischer2010intra}.  Both deterministic and
+model~\cite{fischer2010intra}.}  Both deterministic and
 stochastic models are widely used throughout systems
@@
 model~\cite{huang2003dynamic}, which has been widely
-used~\cite{hattne2005stochastic,huang2004min,kerr2006division,
-  fange2006noise} in both deterministic and stochastic variants, to
+used~\changed{\cite{hattne2005stochastic,huang2004min,kerr2006division,
+  fange2006noise}} in both deterministic and stochastic variants, to
 study flattened cells of $0.4\micron$ thickness that are similar to
 those observed by M\"annik \emph{et al.}~\cite{mannik2009bacterial}.
-This allows us to test the performance of this important model in more
+\changed{This allows us to test the performance of this important model in more
 extreme situations than has been done previously, furthering our
-understanding of how and to what extent it breaks down.
+understanding of how and to what extent it breaks down.}
 
@@
   \includegraphics[width=8.7cm]{reactions}
-  \caption{Reactions included in the Min system model of Huang
+  \caption{Reactions included in the \changed{Min system} model of Huang
     \emph{et al.}, which is used in this
@@
 build up, as recruitment leads to clusters of MinD forming on the wall
-and then subsequently dissipating.  This result, which is not observed
+and then subsequently dissipating.  \changed{This result, which is not observed
 in experiments, stems from the omission of diffusion along the
 membrane from Huang's model, which would allow these recruitment
-clusters to spread out.  Experiments have confirmed that diffusion
+clusters to spread out.}  Experiments have confirmed that diffusion
 along the membrane does occur, albeit with a rate two orders of
@@
 see below, the flattened, irregular cells are large enough that this
-one micron blurring might not completely eliminate this `starry night'
+one micron blurring \changed{might} not completely eliminate this `starry night'
 effect.
@@
   \includegraphics[width=16cm]{../paper/plot-ave}
-  \caption{Arrows depicting successive maxima in space
+  \caption{\changed{Arrows} depicting successive maxima in space
     and time overlayed on a color plot of the total MinD density
@@
 deterministic model shows uniformly bipolar oscillation.  We conclude
-that this model is \emph{not} chaotic (which would show irregularity
+that \changed{this} model is \emph{not} chaotic (which would show irregularity
 in the deterministic computation), but rather that the irregularity
@@
 is inadequate to explain experimental observations of the locations of
-density maxima of the MinD protein.  We note, however, that it is
+density maxima of the MinD protein.  \changed{We note, however, that it is
 possible that there exists another deterministic model that does exhibit
-chaotic behavior.
+chaotic behavior.}
 
@@
 
-The predictions of the stochastic model show some similarity to the
+The predictions of the stochastic model \changed{show some} similarity to the
 experimental results in terms of irregularity of the locations of
-maxima, but the stochastic model displays significantly less
+maxima, \changed{but the stochastic model displays significantly less
 variation in the direction of oscillations than experiment, suggesting
-inadequacies in the model.  We also note that the stadium shapes in
+inadequacies in the model.}  We also note that the stadium shapes in
 Fig.~\ref{randst-plot-ave} appear to have maxima location irregularity
-that is qualitatively similar to our irregular shapes: in both
+that is qualitatively similar to our irregular shapes\changed{: in both
 stochastic simulations the overall oscillation is largely bipolar, but
 with irregularity in the locations of the maxima that form at each
-end.
+end}.
 
@@
 the top of the cell and the number of proteins in a segment at the
-bottom of the cell.  The ``top'' and ``bottom'' regions for computing
+bottom of the cell.  \changed{The ``top'' and ``bottom'' regions for computing
 the correlation time were established by dividing the long axis into
@@
 the stadium shapes featuring 30\% of the volume in the top and bottom
-regions.  Fig.~\ref{fig:corr-B} shows this plot for shape \emph{B} and
+regions.}  Fig.~\ref{fig:corr-B} shows this plot for shape \emph{B} and
 stadium \emph{B}.  Here we plot correlations of correlation times up
@@
 From the stochastic correlation data, we conclude that irregularity of
-shape leads to a decrease in temporal regularity of the oscillatory
+shape \changed{leads to a decrease} in temporal regularity of the oscillatory
 behavior, although even the very distorted shape~\emph{B} exhibiting
@@
 \section*{Conclusion}
-We find qualitative agreement between our stochastic simulations and
+We find \changed{qualitative} agreement between our stochastic simulations and
 experiments showing disrupted bipolar MinD oscillation in asymmetric
@@
 experimentally, our simulations predict that MinD maxima will form in
-a spatially irregular sequence of locations, which follow an overall
-bipolar trend.  This result builds upon existing results showing that
+a spatially irregular sequence of locations, \changed{which follow an overall
+bipolar trend}.  This result builds upon existing results showing that
 this model and its variants are effective in a variety of wild-type
@@
   kruse2007experimentalist}.  The regular oscillations in the
-deterministic case also allow us to conclude that Huang's model is
+deterministic case also allow us to conclude that \changed{Huang's} model is
 non-chaotic.  Because of their similar construction, we anticipate
 that recent variants of the model~\cite{bonny2013membrane,
-  fange2006noise, halatek2012highly} may also prove to be
+  fange2006noise, halatek2012highly} \changed{may} also prove to be
 non-chaotic.
@@
 irregularity in the shape of flattened cells.  Thus we conclude that
-it may be the flattening of the cells, and the accompanying
-expansion in the transverse direction, that causes the disruption of
+it \changed{may be} the flattening of the cells, and the accompanying
+expansion in the transverse direction, \changed{that causes} the disruption of
 regular bipolar oscillation which is observed by M\"annik \emph{et

### 2015-09-09 paper/plos.tex
remove \changed uses from last round with referees.
respond to last referees

--- 2015-08-01 paper/plos.tex
@@
 
+\newcommand{\changed}[1]{{\color{red}#1}}
+%\newcommand{\changed}[1]{}
+
 % Remove comment for double spacing
@@
 \section*{Author Summary}
-  When an E. coli cell divides it must split into two relatively equal
+  When an \changed{\emph{E. coli}} cell divides it must split into two relatively equal
   volumes in order to survive.  One mechanism that aids in this
@@
 parameters~\cite{meacci2006mobility}.  They also increase
-or assume instantaneous~\cite{bonny2013membrane} the nucleotide
-exchange rate.  In addition, they revise the process of MinD
+or assume \changed{instantaneous the nucleotide exchange
+rate~\cite{bonny2013membrane}}.  In addition, they revise the process
+of MinD
 recruitment to the membrane, removing recruitment of MinD to the
@@
 extreme situations than has been done previously, furthering our
-understanding of how and to what extent it breaks down.
+understanding of how and to what extent \changed{its predictions
+  fail}.
 
@@
 stadium \emph{B}.  Here we plot correlations of correlation times up
-to 500 seconds, a biologically relevant timescale.  E. coli cell
+to 500 seconds, a biologically relevant timescale.  \changed{\emph{E. coli}} cell
 doubling times vary widely depending on environmental conditions, but
@@
 experiments showing disrupted bipolar MinD oscillation in asymmetric
-flattened E. coli cells~\cite{mannik2012robustness}.  As observed
+flattened \changed{\emph{E. coli}} cells~\cite{mannik2012robustness}.  As observed
 experimentally, our simulations predict that MinD maxima will form in

### 2015-09-24 paper/plos-final.tex
changes for publication

--- 2015-09-09 paper/plos.tex
@@
 
-\newcommand{\changed}[1]{{\color{red}#1}}
-%\newcommand{\changed}[1]{}
+%\newcommand{\changed}[1]{{\color{red}#1}}
+\newcommand{\changed}[1]{#1}
 
@@
 system can become chaotic (as in
-e.g. Ref.~\citenum{kuramoto1978diffusion}), or if this irregularity is
+e.g. Ref.~\cite{kuramoto1978diffusion}), or if this irregularity is
 the result of a stochastic but nonchaotic process.
@@
 \begin{figure}
-  \includegraphics[width=8.7cm]{reactions}
+  %% \includegraphics[width=8.7cm]{reactions}
   \caption{Reactions included in the Min system model of Huang
@@
 We implement the reaction-diffusion model of Huang \emph{et
-  al.}~\cite{huang2003dynamic}.  Figure~\ref{fig:reactions} shows the
+  al.}~\cite{huang2003dynamic}.  Fig~\ref{fig:reactions} shows the
 reaction process.  The cytoplasmic MinD:ADP complex undergoes
@@
 \begin{figure*}
-  %\includegraphics[width=\textwidth]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/image-plot}
   \begin{center}
-    \hspace{-3.5cm}
-    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
-    \vspace{-1.5em}
-    \hspace{-3.5cm}
-    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
-    \vspace{-1.5em}
+    %% \hspace{-3.5cm}
+    %% \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-exact/plots/single-image-plot}\\
+    %% \vspace{-1.5em}
+    %% \hspace{-3.5cm}
+    %% \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/single-image-plot}
+    %% \vspace{-1.5em}
   \end{center}
@@
   \begin{center}
-    \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
+    %% \includegraphics[height=6.4cm]{../data/shape-p/3_00-0_50-0_00-0_00-15_00-full_array/plots/correlation.pdf}
   \end{center}
@@
 
-Figure~\ref{image-p} shows a series of color plots of the density of
+Fig~\ref{image-p} shows a series of color plots of the density of
 proteins at each stage of the reaction cycle. Deterministic simulation
@@
 
-Figure~\ref{image-p} begins about 300 seconds into the simulation and
+Fig~\ref{image-p} begins about 300 seconds into the simulation and
 shows one period of oscillation.  At $t=0$ there is a high
@@
 
-Both Fig.~\ref{image-p} and its associated movies (see supplementary
+Both Fig~\ref{image-p} and its associated movies (see supplementary
 material), show that the stochastic model exhibits a ``starry night''
@@
 found in two opposite polar regions.  This correlation function, which
-is displayed in Fig.~\ref{corr-pill}, is given by
+is displayed in Fig~\ref{corr-pill}, is given by
 \begin{equation}
@@
   \centering
-  \hspace{-3cm}
-  \vspace{1cm}
-  \includegraphics[width=16cm]{../paper/plot-ave}
+  %% \hspace{-3cm}
+  %% \vspace{1cm}
+  %% \includegraphics[width=16cm]{../paper/plot-ave}
   \caption{Arrows depicting successive maxima in space
@@
     area.  Finally, we display the natural pill shape, which was also
-    featured in Figs.~\ref{image-p} and~\ref{corr-pill}, with a
+    featured in Figs~\ref{image-p} and~\ref{corr-pill}, with a
     different color scale to reflect the thicker cell containing more
@@
 
-%% \begin{figure}
-%%   \begin{center}
-%%     \includegraphics[height=6.4cm]{../data/shape-randst/0_40-18_50-18_50-95_00-15_00-full_array/plots/correlation.pdf}\\
-%%     \includegraphics[height=6.4cm]{../data/shape-stad/0_40-2_35-1_32-0_00-15_00-full_array/plots/correlation.pdf}
-%%   \end{center}
-%%   \caption{Temporal correlation function of the total MinD found in
-%%     two opposite polar regions of the shape \emph{A} (above) and the
-%%     stadium \emph{A} (below) cell shapes, shown against the
-%%     correlation time.  Data for both the the determinisitic and
-%%     stochastic models are shown, and the correlation functions are
-%%     scaled to have the same initial value.  For shape \emph{A}, the
-%%     stochastic model shows an oscillation period of 52 seconds and
-%%     coherence time of 288 seconds, so that it takes roughly 5.5
-%%     periods for the behavior to decohere.  For the stadium \emph{A},
-%%     the same model shows an oscillation period of 48.4 seconds and
-%%     coherence time of 638 seconds, so that it takes roughly 13
-%%     periods for the behavior to decohere.}
-%%   \label{fig:corr-pancake-A}
-%% \end{figure}
-
 \begin{figure}
   \begin{center}
-    \includegraphics[width=8.7cm]{../data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
-    \includegraphics[width=8.7cm]{../data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
+    %% \includegraphics[width=8.7cm]{../data/shape-randst/0_40-18_60-28_60-94_00-15_00-full_array/plots/correlation.pdf}
+    %% \includegraphics[width=8.7cm]{../data/shape-stad/0_40-2_92-1_18-0_00-15_00-full_array/plots/correlation.pdf}
   \end{center}
@@
 identical aspect ratio, thickness and volume (stadium \emph{A} and
-stadium \emph{B}), shown in Figure~\ref{randst-plot-ave}.  All of the
+stadium \emph{B}), shown in Fig~\ref{randst-plot-ave}.  All of the
 flattened cells have lost the rotational symmetry of the original pill
@@
 which the arrow heads show the location of sequential MinD maxima
-within the cell (in Fig.~\ref{randst-plot-ave}).  In addition to
+within the cell (in Fig~\ref{randst-plot-ave}).  In addition to
 arrows between successive maxima in space and time, we plot as a
@@
 inadequacies in the model.  We also note that the stadium shapes in
-Fig.~\ref{randst-plot-ave} appear to have maxima location irregularity
+Fig~\ref{randst-plot-ave} appear to have maxima location irregularity
 that is qualitatively similar to our irregular shapes: in both
@@
 
-However Fig.~\ref{randst-plot-ave} leaves unclear the importance of
+However Fig~\ref{randst-plot-ave} leaves unclear the importance of
 the flattening and accompanying lateral expansion of the cell versus
@@
 the stadium shapes featuring 30\% of the volume in the top and bottom
-regions.  Fig.~\ref{fig:corr-B} shows this plot for shape \emph{B} and
+regions.  Fig~\ref{fig:corr-B} shows this plot for shape \emph{B} and
 stadium \emph{B}.  Here we plot correlations of correlation times up
@@
 
-\bibliography{paper-MinD}
+%% \bibliography{paper-MinD}
+\begin{thebibliography}{10}
+\providecommand{\url}[1]{\texttt{#1}}
+\providecommand{\urlprefix}{URL }
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
+  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
+  \urlstyle{rm}\Url}\fi
+\providecommand{\bibAnnoteFile}[1]{%
+  \IfFileExists{#1}{\begin{quotation}\noindent\textsc{Key:} #1\\
+  \textsc{Annotation:}\ \input{#1}\end{quotation}}{}}
+\providecommand{\bibAnnote}[2]{%
+  \begin{quotation}\noindent\textsc{Key:} #1\\
+  \textsc{Annotation:}\ #2\end{quotation}}
+\providecommand{\eprint}[2][]{\url{#2}}
+
+\bibitem{adams2009bacterial}
+Adams DW, Errington J (2009) Bacterial cell division: assembly, maintenance and
+  disassembly of the z ring.
+\newblock Nature Reviews Microbiology 7: 642--653.
+\bibAnnoteFile{adams2009bacterial}
+
+\bibitem{lutkenhaus2007assembly}
+Lutkenhaus J (2007) Assembly dynamics of the bacterial mincde system and
+  spatial regulation of the z ring.
+\newblock Annu Rev Biochem 76: 539--562.
+\bibAnnoteFile{lutkenhaus2007assembly}
+
+\bibitem{shen2010examination}
+Shen B, Lutkenhaus J (2010) Examination of the interaction between ftsz and
+  mincn in e. coli suggests how minc disrupts z rings.
+\newblock Molecular microbiology 75: 1285--1298.
+\bibAnnoteFile{shen2010examination}
+
+\bibitem{shapiro2009and}
+Shapiro L, McAdams HH, Losick R (2009) Why and how bacteria localize proteins.
+\newblock Science 326: 1225--1228.
+\bibAnnoteFile{shapiro2009and}
+
+\bibitem{yu1999ftsz}
+Yu XC, Margolin W (1999) Ftsz ring clusters in min and partition mutants: role
+  of both the min system and the nucleoid in regulating ftsz ring localization.
+\newblock Molecular microbiology 32: 315--326.
+\bibAnnoteFile{yu1999ftsz}
+
+\bibitem{meacci2005min}
+Meacci G, Kruse K (2005) Min-oscillations in escherichia coli induced by
+  interactions of membrane-bound proteins.
+\newblock Physical biology 2: 89.
+\bibAnnoteFile{meacci2005min}
+
+\bibitem{huang2003dynamic}
+Huang KC, Meir Y, Wingreen NS (2003) {Dynamic structures in Escherichia coli:
+  spontaneous formation of MinE rings and MinD polar zones}.
+\newblock Proceedings of the National Academy of Sciences 100: 12724--12728.
+\bibAnnoteFile{huang2003dynamic}
+
+\bibitem{kerr2006division}
+Kerr RA, Levine H, Sejnowski TJ, Rappel WJ (2006) Division accuracy in a
+  stochastic model of min oscillations in escherichia coli.
+\newblock Proceedings of the National Academy of Sciences of the United States
+  of America 103: 347--352.
+\bibAnnoteFile{kerr2006division}
+
+\bibitem{mannik2009bacterial}
+M{\"a}nnik J, Driessen R, Galajda P, Keymer JE, Dekker C (2009) Bacterial
+  growth and motility in sub-micron constrictions.
+\newblock Proceedings of the National Academy of Sciences 106: 14861--14866.
+\bibAnnoteFile{mannik2009bacterial}
+
+\bibitem{corbin2002exploring}
+Corbin BD, Yu XC, Margolin W (2002) Exploring intracellular space: function of
+  the min system in round-shaped escherichia coli.
+\newblock The EMBO journal 21: 1998--2008.
+\bibAnnoteFile{corbin2002exploring}
+
+\bibitem{fange2006noise}
+Fange D, Elf J (2006) Noise-induced min phenotypes in e. coli.
+\newblock PLoS computational biology 2: e80.
+\bibAnnoteFile{fange2006noise}
+
+\bibitem{varma2008min}
+Varma A, Huang KC, Young KD (2008) The min system as a general cell geometry
+  detection mechanism: Branch lengths in y-shaped escherichia coli cells affect
+  min oscillation patterns and division dynamics.
+\newblock Journal of bacteriology 190: 2106--2117.
+\bibAnnoteFile{varma2008min}
+
+\bibitem{mannik2012robustness}
+M{\"a}nnik J, Wu F, Hol FJ, Bisicchia P, Sherratt DJ, et~al. (2012) Robustness
+  and accuracy of cell division in escherichia coli in diverse cell shapes.
+\newblock Proceedings of the National Academy of Sciences 109: 6957--6962.
+\bibAnnoteFile{mannik2012robustness}
+
+\bibitem{mannik2010bacteria}
+M{\"a}nnik J, Sekhavati F, Keymer J, Dekker C (2010) Bacteria in submicron
+  channels and microvalves.
+\newblock Proc of MicroTAS 2010, Groningen, The Netherlands : 1346--1348.
+\bibAnnoteFile{mannik2010bacteria}
+
+\bibitem{kuramoto1978diffusion}
+Kuramoto Y (1978) Diffusion-induced chaos in reaction systems.
+\newblock Progress of Theoretical Physics Supplement 64: 346--367.
+\bibAnnoteFile{kuramoto1978diffusion}
+
+\bibitem{meinhardt2001pattern}
+Meinhardt H, de~Boer PA (2001) Pattern formation in escherichia coli: a model
+  for the pole-to-pole oscillations of min proteins and the localization of the
+  division site.
+\newblock Proceedings of the National Academy of Sciences 98: 14202--14207.
+\bibAnnoteFile{meinhardt2001pattern}
+
+\bibitem{kruse2002dynamic}
+Kruse K (2002) A dynamic model for determining the middle of< i> escherichia
+  coli</i>.
+\newblock Biophysical journal 82: 618--627.
+\bibAnnoteFile{kruse2002dynamic}
+
+\bibitem{hu2002dynamic}
+Hu Z, Gogol EP, Lutkenhaus J (2002) Dynamic assembly of mind on phospholipid
+  vesicles regulated by atp and mine.
+\newblock Proceedings of the National Academy of Sciences 99: 6761--6766.
+\bibAnnoteFile{hu2002dynamic}
+
+\bibitem{shih2002division}
+Shih YL, Fu X, King GF, Le T, Rothfield L (2002) Division site placement in e.
+  coli: mutations that prevent formation of the mine ring lead to loss of the
+  normal midcell arrest of growth of polar mind membrane domains.
+\newblock The EMBO journal 21: 3347--3357.
+\bibAnnoteFile{shih2002division}
+
+\bibitem{bonny2013membrane}
+Bonny M, Fischer-Friedrich E, Loose M, Schwille P, Kruse K (2013) Membrane
+  binding of mine allows for a comprehensive description of min-protein pattern
+  formation.
+\newblock PLoS computational biology 9: e1003347.
+\bibAnnoteFile{bonny2013membrane}
+
+\bibitem{halatek2012highly}
+Halatek J, Frey E (2012) Highly canalized mind transfer and mine sequestration
+  explain the origin of robust mincde-protein dynamics.
+\newblock Cell Reports 1: 741--752.
+\bibAnnoteFile{halatek2012highly}
+
+\bibitem{meacci2006mobility}
+Meacci G, Ries J, Fischer-Friedrich E, Kahya N, Schwille P, et~al. (2006)
+  Mobility of min-proteins in escherichia coli measured by fluorescence
+  correlation spectroscopy.
+\newblock Physical biology 3: 255.
+\bibAnnoteFile{meacci2006mobility}
+
+\bibitem{loose2011min}
+Loose M, Fischer-Friedrich E, Herold C, Kruse K, Schwille P (2011) Min protein
+  patterns emerge from rapid rebinding and membrane interaction of mine.
+\newblock Nature structural \& molecular biology 18: 577--583.
+\bibAnnoteFile{loose2011min}
+
+\bibitem{huang2004min}
+Huang KC, Wingreen NS (2004) Min-protein oscillations in round bacteria.
+\newblock Physical biology 1: 229.
+\bibAnnoteFile{huang2004min}
+
+\bibitem{kruse2007experimentalist}
+Kruse K, Howard M, Margolin W (2007) An experimentalist's guide to
+  computational modelling of the min system.
+\newblock Molecular microbiology 63: 1279--1284.
+\bibAnnoteFile{kruse2007experimentalist}
+
+\bibitem{fischer2010intra}
+Fischer-Friedrich E, Meacci G, Lutkenhaus J, Chat{\'e} H, Kruse K (2010)
+  Intra-and intercellular fluctuations in min-protein dynamics decrease with
+  cell length.
+\newblock Proceedings of the National Academy of Sciences 107: 6134--6139.
+\bibAnnoteFile{fischer2010intra}
+
+\bibitem{lawson2013spatial}
+Lawson MJ, Drawert B, Khammash M, Petzold L, Yi TM (2013) Spatial stochastic
+  dynamics enable robust cell polarization.
+\newblock PLoS computational biology 9: e1003139.
+\bibAnnoteFile{lawson2013spatial}
+
+\bibitem{robb2014stochastic}
+Robb ML, Shahrezaei V (2014) Stochastic cellular fate decision making by
+  multiple infecting lambda phage.
+\newblock PloS one 9: e103636.
+\bibAnnoteFile{robb2014stochastic}
+
+\bibitem{oguz2014stochastic}
+Oguz C, Palmisano A, Laomettachit T, Watson LT, Baumann WT, et~al. (2014) A
+  stochastic model correctly predicts changes in budding yeast cell cycle
+  dynamics upon periodic expression of cln2.
+\newblock PloS one 9: e96726.
+\bibAnnoteFile{oguz2014stochastic}
+
+\bibitem{fu2013deterministic}
+Fu G, Sabnis A, Harrison RW (2013) A deterministic-stochastic crossover
+  algorithm for simulation of complex biochemical systems.
+\newblock In: Computational Advances in Bio and Medical Sciences (ICCABS), 2013
+  IEEE 3rd International Conference on. IEEE, pp. 1--7.
+\bibAnnoteFile{fu2013deterministic}
+
+\bibitem{rudiger2014stochastic}
+R{\"u}diger S (2014) Stochastic models of intracellular calcium signals.
+\newblock Physics Reports 534: 39--87.
+\bibAnnoteFile{rudiger2014stochastic}
+
+\bibitem{hattne2005stochastic}
+Hattne J, Fange D, Elf J (2005) Stochastic reaction-diffusion simulation with
+  mesord.
+\newblock Bioinformatics 21: 2923--2924.
+\bibAnnoteFile{hattne2005stochastic}
+
+\bibitem{git}
+Schulte J, Zeto R, Roundy D (2015).
+\newblock {MinD simulation github repository}.
+\newblock \doi{10.5281/zenodo.16449}.
+\newblock \urlprefix\url{http://github.com/jeffschulte/protein}.
+\bibAnnoteFile{git}
+
+\bibitem{kraus1996crosstalk}
+Kraus M, Wolf B, Wolf B (1996) Crosstalk between cellular morphology and
+  calcium oscillation patterns insights from a stochastic computer model.
+\newblock Cell calcium 19: 461--472.
+\bibAnnoteFile{kraus1996crosstalk}
+
+\bibitem{gillespie1977exact}
+Gillespie DT (1977) Exact stochastic simulation of coupled chemical reactions.
+\newblock The journal of physical chemistry 81: 2340--2361.
+\bibAnnoteFile{gillespie1977exact}
+
+\bibitem{zhang2007gaussian}
+Zhang B, Zerubia J, Olivo-Marin JC (2007) Gaussian approximations of
+  fluorescence microscope point-spread function models.
+\newblock Applied Optics 46: 1819--1829.
+\bibAnnoteFile{zhang2007gaussian}
+
+\bibitem{pierucci1972chromosome}
+Pierucci O (1972) Chromosome replication and cell division in escherichia coli
+  at various temperatures of growth.
+\newblock Journal of bacteriology 109: 848--854.
+\bibAnnoteFile{pierucci1972chromosome}
+
+\bibitem{stricker2002rapid}
+Stricker J, Maddox P, Salmon E, Erickson HP (2002) Rapid assembly dynamics of
+  the escherichia coli ftsz-ring demonstrated by fluorescence recovery after
+  photobleaching.
+\newblock Proceedings of the National Academy of Sciences 99: 3171--3175.
+\bibAnnoteFile{stricker2002rapid}
+
+\end{thebibliography}
 

### 2015-09-24 pyplots/single-image-plot.py

@@ -110,4 +110,5 @@ cbar.set_label('molecules/$\mu m^2$')
 plt.tight_layout()
 print 'saving as', load.print_string("single-image-plot","")
 plt.savefig(load.print_string("single-image-plot",""), transparent=True)
+plt.savefig(load.print_string("single-image-plot","")[:-4]+'.eps', transparent=True)
 #plt.savefig(load.print_string("real-gauss-single-image-plot",""))

### 2015-09-25 paper/plos-final.tex
remove author summary from manuscript

@@
   asymmetry of the cell shapes.
-
-% Please keep the Author Summary between 150 and 200 words
-% Use first person. PLOS ONE authors please skip this step. 
-% Author Summary not valid for PLOS ONE submissions.   
-\section*{Author Summary}
-  When an \changed{\emph{E. coli}} cell divides it must split into two relatively equal
-  volumes in order to survive.  One mechanism that aids in this
-  process is a system of proteins that oscillate between cell ends and
-  help the original cell divide along its center.  A recent experiment
-  found that by drastically deforming these cells this oscillation can
-  be disrupted.  We examine these oscillations in similarly deformed
-  cells computationally, using two widely used simulation models, and
-  find good agreement using one of them.  The other model fails in a
-  manner far more dramatic than has been previously observed.
-  Furthermore, we find that the effect observed experimentally in
-  asymmetric and flattened cells is primarily a result of the
-  flattening and lateral expansion, not the asymmetry.
 
